### 2022-03-31 R/DeaminationAnalysis.rmd
Create DeaminationAnalysis.rmd
An R notebook for displaying results for the deamination analysis.

---
title: "R Notebook"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

```{r setup_chunk}
library(knitr)
opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5)
if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
}
```

```{r acquire_and_format_data}
deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data")
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R', "DeaminationAnalysis.R"))

# Read in the relevant data
CPDMismatchDataFilePaths = list(hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep1_mismatches.bed"),
                                hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep1_mismatches.bed"),
                                hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep1_mismatches.bed"))

sixFourMismatchDataFilePaths = list(hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep1_mismatches.bed"))

CPDMismatchData = lapply(CPDMismatchDataFilePaths, fread)
sixFourMismatchData = lapply(sixFourMismatchDataFilePaths, fread)

# Simplify the data
CPDMismatchData = lapply(CPDMismatchData, function(x) simplifyTable(filterResults(x)))
sixFourMismatchData = lapply(sixFourMismatchData, function(x) simplifyTable(filterResults(x)))

```

```{r plot_mismatch_type_frequency}

plotMismatchTypeFrequencies(CPDMismatchData$hr1, title = "CPD 1hr Mismatch Type Frequency")
plotMismatchTypeFrequencies(CPDMismatchData$hr24, title = "CPD 24hr Mismatch Type Frequency")
plotMismatchTypeFrequencies(CPDMismatchData$hr48, title = "CPD 48hr Mismatch Type Frequency")

plotMismatchTypeFrequencies(sixFourMismatchData$hr1, title = "6-4 1hr Mismatch Type Frequency")

```

```{r plot_mismatch_pos_frequency}

plotMismatchPositionFrequencies(CPDMismatchData$hr1, includedTypes = c("C>T"), 
                                title = "CPD 1hr C>T Mismatch Positions")
plotMismatchPositionFrequencies(CPDMismatchData$hr1, omittedTypes = c("C>T"), 
                                title = "CPD 1hr !C>T Mismatch Positions")

plotMismatchPositionFrequencies(CPDMismatchData$hr24, includedTypes = c("C>T"), 
                                title = "CPD 24hr C>T Mismatch Positions")
plotMismatchPositionFrequencies(CPDMismatchData$hr1, omittedTypes = c("C>T"), 
                                title = "CPD 24hr !C>T Mismatch Positions")

plotMismatchPositionFrequencies(CPDMismatchData$hr48, includedTypes = c("C>T"), 
                                title = "CPD 48hr C>T Mismatch Positions")
plotMismatchPositionFrequencies(CPDMismatchData$hr48, omittedTypes = c("C>T"), 
                                title = "CPD 48hr !C>T Mismatch Positions")

plotMismatchPositionFrequencies(sixFourMismatchData$hr1, includedTypes = c("C>T"), 
                                title = "6-4 1hr C>T Mismatch Positions")
plotMismatchPositionFrequencies(sixFourMismatchData$hr1, omittedTypes = c("C>T"), 
                                title = "6-4 1hr !C>T Mismatch Positions")

```

### 2022-04-01 R/DeaminationAnalysis.R
Various updates to analysis
- Results can now be filtered by read length
- Simplified mismatch table now includes information on read length
- Plotting functions now print results directly, so they can be used in for loops.

@@ -13,26 +13,46 @@ blankBackground = theme(panel.grid.major = element_blank(), panel.grid.minor = e
                         panel.background = element_blank(), axis.line = element_line(colour = "black"))
 
 
-# Filters the given mismatch data based the presence of 'N' and the number
-filterResults = function(mismatchData, removeRowsWithN = TRUE, maxMismatchesAllowed = 3) {
+# Filters the given mismatch data based the presence of 'N', the number of mismatches per read,
+# and read length.
+filterResults = function(mismatchData, removeRowsWithN = TRUE, maxMismatchesAllowed = NA,
+                         minReadLength = NA, maxReadLength = NA) {
+
   if (removeRowsWithN) mismatchData = mismatchData[!grepl('N', V5)]
-  mismatchData = mismatchData[str_count(V4, ':') <= maxMismatchesAllowed]
+
+  if (!is.na(maxMismatchesAllowed)) {
+    mismatchData = mismatchData[str_count(V4, ':') <= maxMismatchesAllowed]
+  }
+
+  if (!is.na(minReadLength)) {
+    mismatchData = mismatchData[V3-V2 >= minReadLength]
+  }
+
+  if (!is.na(maxReadLength)) {
+    mismatchData = mismatchData[V3-V2 <= maxReadLength]
+  }
+
+  return(mismatchData)
+
 }
 
 # Simplifies the given table of bed formatted mismatches into a smaller
-# two-column table of positions and sequence context.
+# three-column table of positions, sequence context, and read length.
 simplifyTable = function(table) {
   return(table[,list(Position = as.numeric(unlist(strsplit(V4, ':'))),
-                     Mismatch = unlist(strsplit(V5, ':')))])
+                     Mismatch = unlist(strsplit(V5, ':')),
+                     Read_Length = unlist(mapply(rep, V3-V2, lapply(strsplit(V5,':'), length))))])
 }
 
 # Displays the frequencies of each mismatch type.
 plotMismatchTypeFrequencies = function(mismatchTable, title = "Mismatch Type Frequency") {
 
-  ggplot(mismatchTable[, .N, by = Mismatch][, Freq := N/sum(N)], aes(x = Mismatch, y = Freq)) +
-    geom_bar(stat = "identity") +
-    labs(title = title, x = "Mismatch Type", y = "Frequency") +
[…]

### 2022-04-01 R/DeaminationAnalysis.rmd
Update DeaminationAnalysis.rmd

@@
 # Read in the relevant data
-CPDMismatchDataFilePaths = list(hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep1_mismatches.bed"),
+CPDMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
+CPDMismatchDataFilePaths$rep1 = list(
+  hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep1_mismatches.bed"),
+  hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep1_mismatches.bed"),
   hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep1_mismatches.bed"),
-                                hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep1_mismatches.bed"))
+  hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep1_mismatches.bed")
+)
+CPDMismatchDataFilePaths$rep2 = list(
+  hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep2_mismatches.bed"),
+  hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep2_mismatches.bed"),
+  hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep2_mismatches.bed"),
+  hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep2_mismatches.bed")
+)
 
-sixFourMismatchDataFilePaths = list(hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep1_mismatches.bed"))
+sixFourMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
+sixFourMismatchDataFilePaths$rep1 = list(
+  min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep1_mismatches.bed"),
+  min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep1_mismatches.bed"),
+  hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep1_mismatches.bed")
+)
+sixFourMismatchDataFilePaths$rep2 = list(
+  min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep2_mismatches.bed"),
+  min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep2_mismatches.bed"),
+  hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep2_mismatches.bed")
+)
 
-CPDMismatchData = lapply(CPDMismatchDataFilePaths, fread)
-sixFourMismatchData = lapply(sixFourMismatchDataFilePaths, fread)
+CPDMismatchData = lapply(CPDMismatchDataFilePaths, function(x) lapply(x, fread))
+sixFourMismatchData = lapply(sixFourMismatchDataFilePaths, function(x) lapply(x, fread))
 
 # Simplify the data
-CPDMismatchData = lapply(CPDMismatchData, function(x) simplifyTable(filterResults(x)))
-sixFourMismatchData = lapply(sixFourMismatchData, function(x) simplifyTable(filterResults(x)))
+CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
+  x, function(y) simplifyTable(filterResults(y, TRUE, 3, 20, 30))
+))
+sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
+  x, function(y) simplifyTable(filterResults(y, TRUE, 3, 20, 30))
+))
 
@@
 
-plotMismatchTypeFrequencies(CPDMismatchData$hr1, title = "CPD 1hr Mismatch Type Frequency")
-plotMismatchTypeFrequencies(CPDMismatchData$hr24, title = "CPD 24hr Mismatch Type Frequency")
-plotMismatchTypeFrequencies(CPDMismatchData$hr48, title = "CPD 48hr Mismatch Type Frequency")
+for (i in 1:length(CPDMismatchData)) {
+  for (j in 1:length(CPDMismatchData[[i]])) {
+    plotMismatchTypeFrequencies(CPDMismatchData[[i]][[j]],
+                                title = paste("CPD", names(CPDMismatchData)[i], 
+                                              names(CPDMismatchData[[i]])[j], "Mismatch Type Frequency"))
+  }
+}
 
-plotMismatchTypeFrequencies(sixFourMismatchData$hr1, title = "6-4 1hr Mismatch Type Frequency")
+for (i in 1:length(sixFourMismatchData)) {
+  for (j in 1:length(sixFourMismatchData[[i]])) {
+    plotMismatchTypeFrequencies(sixFourMismatchData[[i]][[j]],
+                                title = paste("6-4", names(sixFourMismatchData)[i], 
+                                              names(sixFourMismatchData[[i]])[j], "Mismatch Type Frequency"))
+  }
+}
 
@@
 
-plotMismatchPositionFrequencies(CPDMismatchData$hr1, includedTypes = c("C>T"), 
-                                title = "CPD 1hr C>T Mismatch Positions")
-plotMismatchPositionFrequencies(CPDMismatchData$hr1, omittedTypes = c("C>T"), 
-                                title = "CPD 1hr !C>T Mismatch Positions")
+for (i in 1:length(CPDMismatchData)) {
+  for (j in 1:length(CPDMismatchData[[i]])) {
+    plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], includedTypes = c("C>T"),
+                                    title = paste("CPD", names(CPDMismatchData)[i], 
+                                                  names(CPDMismatchData[[i]])[j], "C>T Mismatch Positions"))
+    plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], omittedTypes = c("C>T"),
+                                    title = paste("CPD", names(CPDMismatchData)[i], 
+                                                  names(CPDMismatchData[[i]])[j], "!C>T Mismatch Positions"))
+  }
+}
 
-plotMismatchPositionFrequencies(CPDMismatchData$hr24, includedTypes = c("C>T"), 
-                                title = "CPD 24hr C>T Mismatch Positions")
-plotMismatchPositionFrequencies(CPDMismatchData$hr1, omittedTypes = c("C>T"), 
-                                title = "CPD 24hr !C>T Mismatch Positions")
-
-plotMismatchPositionFrequencies(CPDMismatchData$hr48, includedTypes = c("C>T"), 
-                                title = "CPD 48hr C>T Mismatch Positions")
-plotMismatchPositionFrequencies(CPDMismatchData$hr48, omittedTypes = c("C>T"), 
-                                title = "CPD 48hr !C>T Mismatch Positions")
-
-plotMismatchPositionFrequencies(sixFourMismatchData$hr1, includedTypes = c("C>T"), 
-                                title = "6-4 1hr C>T Mismatch Positions")
-plotMismatchPositionFrequencies(sixFourMismatchData$hr1, omittedTypes = c("C>T"), 
-                                title = "6-4 1hr !C>T Mismatch Positions")
+for (i in 1:length(sixFourMismatchData)) {
+  for (j in 1:length(sixFourMismatchData[[i]])) {
+    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], includedTypes = c("C>T"),
+                                    title = paste("6-4", names(sixFourMismatchData)[i], 
+                                                  names(sixFourMismatchData[[i]])[j], "C>T Mismatch Positions"))
+    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], omittedTypes = c("C>T"),
+                                    title = paste("6-4", names(sixFourMismatchData)[i], 
+                                                  names(sixFourMismatchData[[i]])[j], "!C>T Mismatch Positions"))
+  }
+}
 

### 2022-04-01 R/DeaminationAnalysis.rmd
Update DeaminationAnalysis.rmd
Changed read length constraints

@@
 CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
-  x, function(y) simplifyTable(filterResults(y, TRUE, 3, 20, 30))
+  x, function(y) simplifyTable(filterResults(y, TRUE, 3, 23, 31))
 ))
 sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
-  x, function(y) simplifyTable(filterResults(y, TRUE, 3, 20, 30))
+  x, function(y) simplifyTable(filterResults(y, TRUE, 3, 23, 31))
 ))

### 2022-04-04 R/DeaminationAnalysis.R
Added getTandemCTMismatches
- Added function for getting tandem C>T mismatches.
- Results can also be filtered by position of the tandem mismatches.

@@ -36,12 +36,51 @@ filterResults = function(mismatchData, removeRowsWithN = TRUE, maxMismatchesAllo
 
 }
 
+
 # Simplifies the given table of bed formatted mismatches into a smaller
 # three-column table of positions, sequence context, and read length.
 simplifyTable = function(table) {
   return(table[,list(Position = as.numeric(unlist(strsplit(V4, ':'))),
                      Mismatch = unlist(strsplit(V5, ':')),
                      Read_Length = unlist(mapply(rep, V3-V2, lapply(strsplit(V5,':'), length))))])
+}
+
+
+# Determines if the given mismatch position and type data for a single read
+# contains a tandem C>T mutation.
+hasTandemCTMismatch = function(mismatchPositions, mismatchTypes) {
+
+  if (length(mismatchPositions) < 2) return(NA)
+
+  for (i in 2:length(mismatchPositions)) {
+    if (abs(mismatchPositions[i] - mismatchPositions[i-1]) == 1 &&
+        mismatchTypes[i] == "C>T" && mismatchTypes[i-1] == "C>T") return(TRUE)
+  }
+
+  return(FALSE)
+
+}
+
+
+# Finds adjacent C>T mismatches in the given table of reads.
+# Can also filter results by boundary conditions (e.g. a threePrimeBoundary of -4 will filter out
+# tandem mismatches that extend into the -3, -2, or -1 positions.)
+getTandemCTMismatches = function(table, threePrimeBoundary = NA, fivePrimeBoundary = NA) {
+
+  multiMismatchReads = table[grepl(':', V4)]
+  tandemCTMismatches = multiMismatchReads[mapply(hasTandemCTMismatch,
+                                                 lapply(V4, function(x) as.numeric(unlist(strsplit(x,':')))),
+                                                 strsplit(V5, ':'))]
+  if (!is.na(threePrimeBoundary)) {
+    tandemCTMismatches = tandemCTMismatches[sapply(strsplit(V4, ':'),
+                                                   function(x) min(as.numeric(x)) < threePrimeBoundary)]
+  }
+  if (!is.na(fivePrimeBoundary)) {
+    tandemCTMismatches = tandemCTMismatches[sapply(strsplit(V4, ':'),
+                                                   function(x) min(as.numeric(x)) > fivePrimeBoundary)]
+  }
+  return(tandemCTMismatches)
+
 }
 
 # Displays the frequencies of each mismatch type.

### 2022-04-04 R/DeaminationAnalysis.rmd
Update DeaminationAnalysis.rmd

@@
 
+# Filter the data
+CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
+  x, function(y) filterResults(y, TRUE, 3, 23, 31)
+))
+sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
+  x, function(y) filterResults(y, TRUE, 3, 23, 31)
+))
+
+# Extract tandem C>T mismatches
+
 # Simplify the data
 CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
-  x, function(y) simplifyTable(filterResults(y, TRUE, 3, 23, 31))
+  x, function(y) simplifyTable(y)
 ))
 sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
-  x, function(y) simplifyTable(filterResults(y, TRUE, 3, 23, 31))
+  x, function(y) simplifyTable(y)
 ))
@@
 
-```{r plot_mismatch_type_frequency}
-
+```{r plot_CPD_mismatch_type_frequency}
 for (i in 1:length(CPDMismatchData)) {
@@
 }
+```
 
+```{r plot_6-4_mismatch_type_frequency}
 for (i in 1:length(sixFourMismatchData)) {
@@
 
-```{r plot_mismatch_pos_frequency}
-
+```{r plot_CPD_mismatch_pos_frequency}
 for (i in 1:length(CPDMismatchData)) {
@@
 }
+```
 
+```{r plot_6-4_mismatch_pos_frequency}
 for (i in 1:length(sixFourMismatchData)) {

### 2022-04-06 R/DeaminationAnalysis.rmd
Update DeaminationAnalysis.rmd

@@
 
-# Extract tandem C>T mismatches
+# Extract and simplify tandem C>T mismatches
+CPDTandemCTMismatches = lapply(CPDMismatchData, function(x) lapply(
+  x, function(y) simplifyTable(getTandemCTMismatches(y))
+))
+sixFourTandemCTMismatches = lapply(sixFourMismatchData, function(x) lapply(
+  x, function(y) simplifyTable(getTandemCTMismatches(y))
+))
 
@@
 ```
+
+```{r plot_CPD_tandem_C>T_pos_frequency}
+for (i in 1:length(CPDTandemCTMismatches)) {
+  for (j in 1:length(CPDTandemCTMismatches[[i]])) {
+    plotMismatchPositionFrequencies(CPDTandemCTMismatches[[i]][[j]],
+                                    title = paste("CPD", names(CPDTandemCTMismatches)[i], 
+                                                  names(CPDTandemCTMismatches[[i]])[j], "Tandem C>T Mismatch Pos"))
+  }
+}
+```
+
+```{r plot_6-4_tandem_C>T_pos_frequency}
+for (i in 1:length(sixFourTandemCTMismatches)) {
+  for (j in 1:length(sixFourTandemCTMismatches[[i]])) {
+    plotMismatchPositionFrequencies(sixFourTandemCTMismatches[[i]][[j]],
+                                    title = paste("CPD", names(sixFourTandemCTMismatches)[i], 
+                                                  names(sixFourTandemCTMismatches[[i]])[j], 
+                                                  "Tandem C>T Mismatch Pos"))
+  }
+}
+```

### 2022-04-06 python/SamMismatchesToBed.py
Small tweak to naming conventions

@@ -18,10 +18,10 @@ def samMismatchesToBed(samFilePaths: List[str], verbose = False):
 
         # Create output file paths (bed file + metadata)
         if gzipped:
-            outputBedFilePath = samFilePath.rsplit('.',2)[0] + "_mismatches.bed"
+            outputBedFilePath = samFilePath.rsplit('.',2)[0] + "_mismatches_by_read.bed"
             openFunction = gzip.open
         else:
-            outputBedFilePath = samFilePath.rsplit('.',1)[0] + "_mismatches.bed"
+            outputBedFilePath = samFilePath.rsplit('.',1)[0] + "_mismatches_by_read.bed"
             openFunction = open
         metadataFilePath = outputBedFilePath.rsplit('.',1)[0] + ".metadata"
 

### 2022-04-06 python/SamBedToCustomBed.py
Create SamBedToCustomBed.py
This script takes a bed file resulting from SamMismatchesToBed.py and converts it to a more general bed format suitable for mutperiod. Also, data can be filtered based on read length, number of mismatches, the sequence of the mismatch, and the position of the mismatch within the read. Both single-base and tandem mismatches can be selected for this way.

@@ -1,0 +1,167 @@
+# This script takes a bed file resulting from SamMismatchesToBed.py and converts
+# it to a more general bed format suitable for mutperiod.
+# Also, data can be filtered based on read length, number of mismatches, the sequence of the mismatch,
+# And the position of the mismatch within the read.
+# Alternatively, this script can look for a specific type of tandem mutation at specific positions.
+import os
+from typing import List
+from benbiohelpers.TkWrappers.TkinterDialog import TkinterDialog
+from benbiohelpers.FileSystemHandling.DirectoryHandling import checkDirs
+
+
+# Given a bed file path containing information on sam read mismatches, filter the reads and mismatches
+# based on the given parameters (all "acceptable..." parameters accept a list/range as input, and if
+# any filtering parameters are passed NoneType, they will not be used in filtering at all.) and single
+# mismatches and/or tandem mismatches to a custom-bed formatted file.
+def samBedToCustomBed(samBedFilePaths: List[str], 
+                      outputSingleBaseMismatches = True, singleBaseSuffix = "_individual_mismatches",
+                      outputTandemMismatches = True, tandemSuffix = "_tandem_mismatches",
+                      acceptableReadLengths = None, maxMismatches = None, acceptableMismatchPositions = None, 
+                      acceptableMismatchSequences = None):
+
+    for samBedFilePath in samBedFilePaths:
+
+        print(f"Working in {os.path.basename(samBedFilePath)}")
+
+        # Generate the required output file paths, each within its own directory (for convenience with mutperiod).
+        inputFileDir = os.path.dirname(samBedFilePath)
+        baseFileName = os.path.basename(samBedFilePath).rsplit('.')[0].rsplit("_mismatches_by_read")[0]
+
+        if outputSingleBaseMismatches:
+            singleMismatchOutputDir = os.path.join(inputFileDir, baseFileName + singleBaseSuffix)
+            singleMismatchOutputFilePath = os.path.join(singleMismatchOutputDir, baseFileName + singleBaseSuffix + ".bed")
+            checkDirs(singleMismatchOutputDir)
+            singleMismatchOutputFile = open(singleMismatchOutputFilePath, 'w')
+        if outputTandemMismatches:
+            tandemMismatchOutputDir = os.path.join(inputFileDir, baseFileName + tandemSuffix)
+            tandemMismatchOutputFilePath = os.path.join(tandemMismatchOutputDir, baseFileName + tandemSuffix + ".bed")
+            checkDirs(tandemMismatchOutputDir)
[…]

### 2022-04-12 R/DeaminationAnalysis.rmd
Update DeaminationAnalysis.rmd

@@
 
-```{r acquire_and_format_data}
+```{r source_functions}
+source(file.path(bioinformaticsDirectory, "deamination_determination", 'R', "DeaminationAnalysis.R"))
+source(file.path(bioinformaticsDirectory, "Chromatin_Features_Analysis", "R_scripts", "PeriodicityAnalysis.R"))
+```
+
+```{r acquire_and_format_data_1}
 deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data")
-source(file.path(bioinformaticsDirectory, "deamination_determination", 'R', "DeaminationAnalysis.R"))
 
@@
     plotMismatchPositionFrequencies(sixFourTandemCTMismatches[[i]][[j]],
-                                    title = paste("CPD", names(sixFourTandemCTMismatches)[i], 
+                                    title = paste("6-4", names(sixFourTandemCTMismatches)[i], 
                                                   names(sixFourTandemCTMismatches[[i]])[j], 
@@
 ```
+
+```{r acquire_and_format_data_2}
+load(file.path(deaminationDataDirectory, "deamination_periodicity_results.rda"))
+dataSetNames = as.list(setNames(nm = mutperiodData$periodicityResults$Data_Set))
+
+```
+
+```{r periodicity_stats}
+print(mutperiodData$periodicityResults)
+```
+
+```{r CPD_rotational_periodicity_trinuc_normalized}
+parseAndPlotPeriodicity(dataSetNames$NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
+                        title = "CPD 1hr Rep1 Rotational Trinuc Norm")
+parseAndPlotPeriodicity(dataSetNames$NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
+                        title = "CPD 24hr Rep1 Rotational Trinuc Norm")
+parseAndPlotPeriodicity(dataSetNames$NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
+                        title = "CPD 48hr Rep1 Rotational Trinuc Norm")
+```
+
+```{r CPD_rotational_periodicity_XR-seq_normalized}
+parseAndPlotPeriodicity(
+  dataSetNames$NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
+  title = "CPD 1hr Rep1 Rotational XR-seq Norm")
+parseAndPlotPeriodicity(
+  dataSetNames$NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
+  title = "CPD 24hr Rep1 Rotational XR-seq Norm")
+parseAndPlotPeriodicity(
+  dataSetNames$NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
+  title = "CPD 48hr Rep1 Rotational XR-seq Norm")
+```
+
+```{r CPD_translational_periodicity_trinuc_normalized}
+parseAndPlotPeriodicity(
+  dataSetNames$`NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
+  title = "CPD 1hr Rep1 Rotational Trinuc Norm")
+parseAndPlotPeriodicity(
+  dataSetNames$`NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
+  title = "CPD 24hr Rep1 Rotational Trinuc Norm")
+parseAndPlotPeriodicity(
+  dataSetNames$`NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
+  title = "CPD 48hr Rep1 Rotational Trinuc Norm")
+```
+
+```{r CPD_translational_periodicity_XR-seq_normalized}
+parseAndPlotPeriodicity(
+  dataSetNames$`NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
+  title = "CPD 1hr Rep1 Rotational XR-seq Norm")
+parseAndPlotPeriodicity(
+  dataSetNames$`NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
+  title = "CPD 24hr Rep1 Rotational XR-seq Norm")
+parseAndPlotPeriodicity(
+  dataSetNames$`NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
+  title = "CPD 48hr Rep1 Rotational XR-seq Norm")
+```

### 2022-04-12 python/SamBedToCustomBed.py
Moved parseToIterable function to benbiohelpers

@@ -5,9 +5,9 @@
 # Alternatively, this script can look for a specific type of tandem mutation at specific positions.
 import os
 from typing import List
-import warnings
 from benbiohelpers.TkWrappers.TkinterDialog import TkinterDialog
 from benbiohelpers.FileSystemHandling.DirectoryHandling import checkDirs
+from benbiohelpers.InputParsing.ParseToIterable import parseToIterable
 
 
 # Given a bed file path containing information on sam read mismatches, filter the reads and mismatches
@@ -119,34 +119,9 @@ def main():
     
     samBedFilePaths = selections.getFilePathGroups()[0]
     
-    # Make a function for parsing input in range or list format.
-    def parseInputToIterable(input: str, rangeChar = '-', sepChar = ','):
-
-        # Remove trailing and leading whitespace
-        input = input.strip()
-
-        # If there are separator characters in the input, split it into multiple inputs,
-        # and recursively perform this function on each, concatenating the results into a single list.
-        if sepChar in input:
-            return([
-                item for inputIterable in input.split(sepChar)
-                    for item in parseInputToIterable(inputIterable, rangeChar, sepChar)
-            ])
-
-        # If there is a range separator in the input (and no separator characters),
-        # return a range object as the iterable.
-        elif rangeChar in input:
-            start, stop = input.split(rangeChar)
-            if int(stop) < int(start): warnings.warn(f"Stop comes before start in range {input}")
-            return(range(int(start),int(stop)+1))
-
-        # Otherwise, the input is a single item that just needs to be turned into an iterable and returned.
-        else:
-            return([int(input)])
-
-    acceptableReadLengths = parseInputToIterable(selections.getTextEntries()[0])
+    acceptableReadLengths = parseToIterable(selections.getTextEntries()[0])
     maxMismatches = int(selections.getTextEntries()[1])
-    acceptableMismatchPositions = parseInputToIterable(selections.getTextEntries()[2],rangeChar = '$')
+    acceptableMismatchPositions = parseToIterable(selections.getTextEntries()[2],rangeChar = '$')
     acceptableMismatchSequences = [sequence.strip() for sequence in selections.getTextEntries()[3].split(',')]
 
     if singleBaseDynSel.getControllerVar():

### 2022-04-12 R/DeaminationAnalysis.rmd
Update DeaminationAnalysis.rmd

@@
 
-```{r periodicity_stats}
-print(mutperiodData$periodicityResults)
-```
-
 ```{r CPD_rotational_periodicity_trinuc_normalized}
@@
 ```
+
+```{r acquire_and_format_data_3}
+load(file.path(deaminationDataDirectory, "TCG_deamination_periodicity_results.rda"))
+dataSetNames = as.list(setNames(nm = mutperiodData$periodicityResults$Data_Set))
+
+```
+
+```{r TCG_CPD_rotational_periodicity_trinuc_normalized}
+parseAndPlotPeriodicity(
+  dataSetNames$TCG_NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
+  title = "TCG CPD 1hr Rep1 Rotational Trinuc Norm")
+parseAndPlotPeriodicity(
+  dataSetNames$TCG_NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
+  title = "TCG CPD 24hr Rep1 Rotational Trinuc Norm")
+parseAndPlotPeriodicity(
+  dataSetNames$TCG_NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
+  title = "TCG CPD 48hr Rep1 Rotational Trinuc Norm")
+```
+
+```{r TCG_CPD_rotational_periodicity_XR-seq_normalized}
+parseAndPlotPeriodicity(
+  dataSetNames$TCG_NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
+  title = "TCG CPD 1hr Rep1 Rotational XR-seq Norm")
+parseAndPlotPeriodicity(
+  dataSetNames$TCG_NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
+  title = "TCG CPD 24hr Rep1 Rotational XR-seq Norm")
+parseAndPlotPeriodicity(
+  dataSetNames$TCG_NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
+  title = "TCG CPD 48hr Rep1 Rotational XR-seq Norm")
+```
+
+```{r TCG_CPD_translational_periodicity_trinuc_normalized}
+parseAndPlotPeriodicity(
+  dataSetNames$`TCG_NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
+  title = "TCG CPD 1hr Rep1 Rotational Trinuc Norm")
+parseAndPlotPeriodicity(
+  dataSetNames$`TCG_NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
+  title = "TCG CPD 24hr Rep1 Rotational Trinuc Norm")
+parseAndPlotPeriodicity(
+  dataSetNames$`TCG_NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
+  title = "TCG CPD 48hr Rep1 Rotational Trinuc Norm")
+```
+
+```{r TCG_CPD_translational_periodicity_XR-seq_normalized}
+parseAndPlotPeriodicity(
+  dataSetNames$`TCG_NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
+  title = "TCG_CPD 1hr Rep1 Rotational XR-seq Norm")
+parseAndPlotPeriodicity(
+  dataSetNames$`TCG_NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
+  title = "TCG CPD 24hr Rep1 Rotational XR-seq Norm")
+parseAndPlotPeriodicity(
+  dataSetNames$`TCG_NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
+  title = "TCG CPD 48hr Rep1 Rotational XR-seq Norm")
+```

### 2022-04-14 R/DeaminationAnalysis.R
Created facet plot for mismatch position
- Created a REALLY NIFTY function for plotting mismatch positions across timepoint and read length using ggplot2 facet_grid.

@@ -118,3 +118,40 @@ plotMismatchPositionFrequencies = function(mismatchTable, includedTypes = list()
   )
 
 }
+
+# Plot mismatch position using a facet plot with timepoint on one dimension and read length on the other
+plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTypes = list(), omittedTypes = list(),
+                                                    title = "Mismatch Position Frequencies") {
+
+  aggregateTable = rbindlist(lapply(seq_along(simplifiedTables),
+                                    function(i) simplifiedTables[[i]][,Timepoint := names(simplifiedTables)[i]]))
+
+  if ( length(includedTypes) > 0 && length(omittedTypes) > 0) {
+    stop("Included types and omitted types given simultaneously")
+  } else if (length(includedTypes) > 0) {
+    frequencyData = (aggregateTable[Mismatch %in% includedTypes, .N, by = list(Position,Read_Length,Timepoint)]
+                     [, Freq := N/sum(N), by = list(Read_Length, Timepoint)])
+  } else if (length(omittedTypes) > 0) {
+    frequencyData = (aggregateTable[!(Mismatch %in% omittedTypes), .N, by = list(Position,Read_Length,Timepoint)]
+                     [, Freq := N/sum(N), by = list(Read_Length, Timepoint)])
+  } else {
+    frequencyData = (aggregateTable[, .N, by = list(Position,Read_Length,Timepoint)]
+                     [, Freq := N/sum(N), by = list(Read_Length, Timepoint)])
+  }
+
+  print(
+    ggplot(frequencyData, aes(Position, Freq)) +
+      geom_bar(stat = "identity") +
+      labs(title = title, x = "3` Relative Position", y = "Relative Mismatch Frequency") +
+      blankBackground + defaultTextScaling +
+      facet_grid(Read_Length~factor(Timepoint, levels = names(simplifiedTables))) +
+      theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
+            strip.background = element_rect(color = "black", size = 1),
+            axis.text.y = element_blank(), axis.ticks.y = element_blank(),
+            strip.text.y = element_text(size = 16),
+            panel.grid.major.x = element_line(color = "red", size = 0.5, linetype = 2)) +
+      scale_y_continuous(sec.axis = dup_axis(~., name = "Read Length")) +
+      scale_x_continuous(breaks = c(0, -10, -20))
+  )
+
+}

### 2022-04-14 R/DeaminationAnalysis.rmd
Update DeaminationAnalysis.rmd

@@
 library(knitr)
-opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5)
+opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, fig.path = "Deamination_Analysis_Figures/")
 if (interactive()) {
@@
 
-```{r plot_CPD_mismatch_type_frequency}
+```{r CPD_mismatch_type_frequency}
 for (i in 1:length(CPDMismatchData)) {
@@
 
-```{r plot_6-4_mismatch_type_frequency}
+```{r 6-4_mismatch_type_frequency}
 for (i in 1:length(sixFourMismatchData)) {
@@
 
-```{r plot_CPD_mismatch_pos_frequency}
+```{r CPD_mismatch_pos_frequency}
 for (i in 1:length(CPDMismatchData)) {
@@
 
-```{r plot_6-4_mismatch_pos_frequency}
+```{r 6-4_mismatch_pos_frequency}
 for (i in 1:length(sixFourMismatchData)) {
@@
 
-```{r plot_CPD_tandem_C>T_pos_frequency}
+```{r CPD_tandem_C_to_T_pos_frequency}
 for (i in 1:length(CPDTandemCTMismatches)) {
@@
 
-```{r plot_6-4_tandem_C>T_pos_frequency}
+```{r 6-4_tandem_C_to_T_pos_frequency}
 for (i in 1:length(sixFourTandemCTMismatches)) {
@@
 }
+```
+
+```{r Facet_Mismatch_Position_Frequencies, fig.width = 9, fig.height = 5}
+plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, includedTypes = c("C>T"),
+                                         title = "CPD C>T Mismatch Pos Freq Rep1")
+plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, includedTypes = c("C>T"),
+                                         title = "CPD C>T Mismatch Pos Freq Rep2")
+plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, includedTypes = c("C>T"),
+                                         title = "6-4 C>T Mismatch Pos Freq Rep1")
+plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, includedTypes = c("C>T"),
+                                         title = "6-4 C>T Mismatch Pos Freq Rep2")
 ```

### 2022-04-15 R/DeaminationAnalysis.R
Updated functions to work with 5' ends
- Functions that display mismatch position now take a "posType" parameter to describe whether the output should be relative to the 3' or 5' end.
- Also tightened up the facet plot function

@@ -2,6 +2,9 @@ library(data.table)
 library(stringr)
 library(ggplot2)
 
+THREE_PRIME = 3
+FIVE_PRIME = 5
+
 # Default text scaling
 defaultTextScaling = theme(plot.title = element_text(size = 26, hjust = 0.5),
                            axis.title = element_text(size = 22), axis.text = element_text(size = 18),
@@ -98,7 +101,15 @@ plotMismatchTypeFrequencies = function(mismatchTable, title = "Mismatch Type Fre
 # Displays the frequencies of positions for the chosen mismatch types.
 # (Types can be chosen by inclusion or omission)
 plotMismatchPositionFrequencies = function(mismatchTable, includedTypes = list(), omittedTypes = list(),
-                                           title = "Position Frequency") {
+                                           title = "Position Frequency", posType = THREE_PRIME) {
+
+  if (posType == THREE_PRIME) {
+    xAxisLabel = "3' Relative Position"
+  } else if (posType == FIVE_PRIME) {
+    xAxisLabel = "5' Relative Position"
+    mismatchTable = copy(mismatchTable)
+    mismatchTable[, Position := Read_Length + Position + 1]
+  } else stop("Unrecognized value for posType parameter.")
 
   if ( length(includedTypes) > 0 && length(omittedTypes) > 0) {
     stop("Included types and omitted types given simultaneously")
@@ -113,7 +124,7 @@ plotMismatchPositionFrequencies = function(mismatchTable, includedTypes = list()
   print(
     ggplot(frequencyData, aes(x = Position, y = Freq)) +
       geom_bar(stat = "identity") +
-      labs(title = title, x = "3` Relative Position", y = "Frequency") +
+      labs(title = title, x = xAxisLabel, y = "Frequency") +
       blankBackground + defaultTextScaling
   )
 
@@ -121,7 +132,17 @@ plotMismatchPositionFrequencies = function(mismatchTable, includedTypes = list()
 
 # Plot mismatch position using a facet plot with timepoint on one dimension and read length on the other
 plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTypes = list(), omittedTypes = list(),
-                                                    title = "Mismatch Position Frequencies") {
+                                                    title = "Mismatch Position Frequencies", posType = THREE_PRIME) {
+
[…]

### 2022-04-15 R/DeaminationAnalysis.R
Added function for displaying position stats
This function displays the mean, median, and mode position stratified by timepoint and read length.

@@ -174,3 +174,40 @@ plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTy
   )
 
 }
+
+
+# Gets the mode. (Why isn't there a base R function for this?)
+getMode = function(values) {
+  frequencyTable = table(values)
+  return(as.numeric(names(frequencyTable)[which.max(frequencyTable)]))
+}
+
+
+# Returns a table of the mean, median, and mode positions for each read length at each time point.
+getGroupedPositionStats = function(simplifiedTables, includedTypes = list(),
+                                   omittedTypes = list(), posType = THREE_PRIME) {
+
+  if (posType == FIVE_PRIME) {
+    simplifiedTables = lapply(simplifiedTables, copy)
+    lapply(simplifiedTables, function(x) x[, Position := Read_Length + Position + 1])
+  } else if (posType != THREE_PRIME) stop("Unrecognized value for posType parameter.")
+
+  aggregateTable = rbindlist(lapply(seq_along(simplifiedTables),
+                                    function(i) simplifiedTables[[i]][,Timepoint := names(simplifiedTables)[i]]))
+
+  if ( length(includedTypes) > 0 && length(omittedTypes) > 0) {
+    stop("Included types and omitted types given simultaneously")
+  } else if (length(includedTypes) > 0) {
+    aggregateTable = aggregateTable[Mismatch %in% includedTypes]
+  } else if (length(omittedTypes) > 0) {
+    aggregateTable = aggregateTable[!(Mismatch %in% omittedTypes)]
+  }
+
+  groupedPositionStats = aggregateTable[order(Timepoint, Read_Length),
+                                        .(mean = mean(Position), median = median(Position),
+                                          mode = getMode(Position)),
+                                        by = list(Read_Length,Timepoint)]
+
+  return(groupedPositionStats)
+
+}

### 2022-04-15 R/DeaminationAnalysis.rmd
Update DeaminationAnalysis.rmd

@@
 library(knitr)
-opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, fig.path = "Deamination_Analysis_Figures/")
+opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, fig.path = "deamination_analysis_figures/")
 if (interactive()) {
@@
                                     title = paste("CPD", names(CPDMismatchData)[i], 
-                                                  names(CPDMismatchData[[i]])[j], "C>T Mismatch Positions"))
+                                                  names(CPDMismatchData[[i]])[j], "C>T Mismatch Positions"),
+                                    posType = FIVE_PRIME)
     plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], omittedTypes = c("C>T"),
@@
                                                   names(sixFourMismatchData[[i]])[j], "C>T Mismatch Positions"))
+    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], includedTypes = c("C>T"),
+                                    title = paste("6-4", names(sixFourMismatchData)[i], 
+                                                  names(sixFourMismatchData[[i]])[j], "C>T Mismatch Positions"),
+                                    posType = FIVE_PRIME)
+
     plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], omittedTypes = c("C>T"),
@@
 
-```{r CPD_tandem_C_to_T_pos_frequency}
-for (i in 1:length(CPDTandemCTMismatches)) {
-  for (j in 1:length(CPDTandemCTMismatches[[i]])) {
-    plotMismatchPositionFrequencies(CPDTandemCTMismatches[[i]][[j]],
-                                    title = paste("CPD", names(CPDTandemCTMismatches)[i], 
-                                                  names(CPDTandemCTMismatches[[i]])[j], "Tandem C>T Mismatch Pos"))
-  }
-}
-```
+# ```{r CPD_tandem_C_to_T_pos_frequency}
+# for (i in 1:length(CPDTandemCTMismatches)) {
+#   for (j in 1:length(CPDTandemCTMismatches[[i]])) {
+#     plotMismatchPositionFrequencies(CPDTandemCTMismatches[[i]][[j]],
+#                                     title = paste("CPD", names(CPDTandemCTMismatches)[i], 
+#                                                   names(CPDTandemCTMismatches[[i]])[j], "Tandem C>T Mismatch Pos"))
+#   }
+# }
+# ```
 
-```{r 6-4_tandem_C_to_T_pos_frequency}
-for (i in 1:length(sixFourTandemCTMismatches)) {
-  for (j in 1:length(sixFourTandemCTMismatches[[i]])) {
-    plotMismatchPositionFrequencies(sixFourTandemCTMismatches[[i]][[j]],
-                                    title = paste("6-4", names(sixFourTandemCTMismatches)[i], 
-                                                  names(sixFourTandemCTMismatches[[i]])[j], 
-                                                  "Tandem C>T Mismatch Pos"))
-  }
-}
-```
+# ```{r 6-4_tandem_C_to_T_pos_frequency}
+# for (i in 1:length(sixFourTandemCTMismatches)) {
+#   for (j in 1:length(sixFourTandemCTMismatches[[i]])) {
+#     plotMismatchPositionFrequencies(sixFourTandemCTMismatches[[i]][[j]],
+#                                     title = paste("6-4", names(sixFourTandemCTMismatches)[i], 
+#                                                   names(sixFourTandemCTMismatches[[i]])[j], 
+#                                                   "Tandem C>T Mismatch Pos"))
+#   }
+# }
+# ```
 
-```{r Facet_Mismatch_Position_Frequencies, fig.width = 9, fig.height = 5}
+```{r facet_mismatch_position_frequencies, fig.width = 9, fig.height = 5}
 plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, includedTypes = c("C>T"),
@@
                                          title = "CPD C>T Mismatch Pos Freq Rep2")
+plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, includedTypes = c("C>T"),
+                                         title = "CPD C>T Mismatch Pos Freq Rep1", posType = FIVE_PRIME)
+plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, includedTypes = c("C>T"),
+                                         title = "CPD C>T Mismatch Pos Freq Rep2", posType = FIVE_PRIME)
+
 plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, includedTypes = c("C>T"),
@@
                                          title = "6-4 C>T Mismatch Pos Freq Rep2")
+plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, includedTypes = c("C>T"),
+                                         title = "6-4 C>T Mismatch Pos Freq Rep1", posType = FIVE_PRIME)
+plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, includedTypes = c("C>T"),
+                                         title = "6-4 C>T Mismatch Pos Freq Rep2", posType = FIVE_PRIME)
+```
+
+```{r facet_mismatch_position_statistics}
+CPDGroupedStats = list(rep1 = list(), rep2 = list())
+CPDGroupedStats$rep1$three_prime = getGroupedPositionStats(CPDMismatchData$rep1, includedTypes = c("C>T"))
+CPDGroupedStats$rep2$three_prime = getGroupedPositionStats(CPDMismatchData$rep2, includedTypes = c("C>T"))
+CPDGroupedStats$rep1$five_prime =
+  getGroupedPositionStats(CPDMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME)
+CPDGroupedStats$rep2$five_prime =
+  getGroupedPositionStats(CPDMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME)
+
+sixFourGroupedStats = list(rep1 = list(), rep2 = list())
+sixFourGroupedStats$rep1$three_prime = getGroupedPositionStats(sixFourMismatchData$rep1, includedTypes = c("C>T"))
+sixFourGroupedStats$rep2$three_prime = getGroupedPositionStats(sixFourMismatchData$rep2, includedTypes = c("C>T"))
+sixFourGroupedStats$rep1$five_prime =
+  getGroupedPositionStats(sixFourMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME)
+sixFourGroupedStats$rep2$five_prime =
+  getGroupedPositionStats(sixFourMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME)
+
+dir.create("deamination_analysis_tables")
+
+fwrite(CPDGroupedStats$rep1$three_prime,
+       file.path("deamination_analysis_tables", "CPD_mismatch_three_prime_position_stats_rep1.tsv"),sep = '\t')
+fwrite(CPDGroupedStats$rep2$three_prime,
+       file.path("deamination_analysis_tables", "CPD_mismatch_three_prime_position_stats_rep2.tsv"),sep = '\t')
+fwrite(CPDGroupedStats$rep1$five_prime,
+       file.path("deamination_analysis_tables", "CPD_mismatch_five_prime_position_stats_rep1.tsv"),sep = '\t')
+fwrite(CPDGroupedStats$rep2$five_prime,
+       file.path("deamination_analysis_tables", "CPD_mismatch_five_prime_position_stats_rep2.tsv"),sep = '\t')
+
+fwrite(sixFourGroupedStats$rep1$three_prime,
+       file.path("deamination_analysis_tables", "6-4_mismatch_three_prime_position_stats_rep1.tsv"), sep = '\t')
+fwrite(sixFourGroupedStats$rep2$three_prime,
+       file.path("deamination_analysis_tables", "6-4_mismatch_three_prime_position_stats_rep2.tsv"), sep = '\t')
+fwrite(sixFourGroupedStats$rep1$five_prime,
+       file.path("deamination_analysis_tables", "6-4_mismatch_five_prime_position_stats_rep1.tsv"), sep = '\t')
+fwrite(sixFourGroupedStats$rep2$five_prime,
+       file.path("deamination_analysis_tables", "6-4_mismatch_five_prime_position_stats_rep2.tsv"), sep = '\t')
 ```

### 2022-04-15 R/DeaminationAnalysis.rmd
Update DeaminationAnalysis.rmd

@@
 library(knitr)
-opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, fig.path = "deamination_analysis_figures/")
+opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
+               fig.path = paste0(file.path("deamination_analysis_output","human_analysis_figures"),
+                                 .Platform$path.sep))
 if (interactive()) {
@@
 
-dir.create("deamination_analysis_tables")
+dir.create(file.path("deamination_analysis_output","human_analysis_tables"))
 

### 2022-04-15 R/HumanDeaminationAnalysis.rmd
Update HumanDeaminationAnalysis.rmd

--- 2022-04-15 R/DeaminationAnalysis.rmd
@@
 library(knitr)
-opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, fig.path = "deamination_analysis_figures/")
+opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
+               fig.path = paste0(file.path("deamination_analysis_output","human_analysis_figures"),
+                                 .Platform$file.sep))
 if (interactive()) {
@@
 ```{r acquire_and_format_data_1}
-deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data")
+deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", "human")
 
@@
 
-dir.create("deamination_analysis_tables")
+tableOutputDir = file.path("deamination_analysis_output","human_analysis_tables")
+dir.create(tableOutputDir)
 
 fwrite(CPDGroupedStats$rep1$three_prime,
-       file.path("deamination_analysis_tables", "CPD_mismatch_three_prime_position_stats_rep1.tsv"),sep = '\t')
+       file.path(tableOutputDir, "CPD_mismatch_three_prime_position_stats_rep1.tsv"),sep = '\t')
 fwrite(CPDGroupedStats$rep2$three_prime,
-       file.path("deamination_analysis_tables", "CPD_mismatch_three_prime_position_stats_rep2.tsv"),sep = '\t')
+       file.path(tableOutputDir, "CPD_mismatch_three_prime_position_stats_rep2.tsv"),sep = '\t')
 fwrite(CPDGroupedStats$rep1$five_prime,
-       file.path("deamination_analysis_tables", "CPD_mismatch_five_prime_position_stats_rep1.tsv"),sep = '\t')
+       file.path(tableOutputDir, "CPD_mismatch_five_prime_position_stats_rep1.tsv"),sep = '\t')
 fwrite(CPDGroupedStats$rep2$five_prime,
-       file.path("deamination_analysis_tables", "CPD_mismatch_five_prime_position_stats_rep2.tsv"),sep = '\t')
+       file.path(tableOutputDir, "CPD_mismatch_five_prime_position_stats_rep2.tsv"),sep = '\t')
 
 fwrite(sixFourGroupedStats$rep1$three_prime,
-       file.path("deamination_analysis_tables", "6-4_mismatch_three_prime_position_stats_rep1.tsv"), sep = '\t')
+       file.path(tableOutputDir, "6-4_mismatch_three_prime_position_stats_rep1.tsv"), sep = '\t')
 fwrite(sixFourGroupedStats$rep2$three_prime,
-       file.path("deamination_analysis_tables", "6-4_mismatch_three_prime_position_stats_rep2.tsv"), sep = '\t')
+       file.path(tableOutputDir, "6-4_mismatch_three_prime_position_stats_rep2.tsv"), sep = '\t')
 fwrite(sixFourGroupedStats$rep1$five_prime,
-       file.path("deamination_analysis_tables", "6-4_mismatch_five_prime_position_stats_rep1.tsv"), sep = '\t')
+       file.path(tableOutputDir, "6-4_mismatch_five_prime_position_stats_rep1.tsv"), sep = '\t')
 fwrite(sixFourGroupedStats$rep2$five_prime,
-       file.path("deamination_analysis_tables", "6-4_mismatch_five_prime_position_stats_rep2.tsv"), sep = '\t')
+       file.path(tableOutputDir, "6-4_mismatch_five_prime_position_stats_rep2.tsv"), sep = '\t')
 ```
@@
 ```{r acquire_and_format_data_2}
-load(file.path(deaminationDataDirectory, "deamination_periodicity_results.rda"))
+load(file.path(deaminationDataDirectory, "NHF1_deamination_periodicity_results.rda"))
 dataSetNames = as.list(setNames(nm = mutperiodData$periodicityResults$Data_Set))
@@
 ```{r acquire_and_format_data_3}
-load(file.path(deaminationDataDirectory, "TCG_deamination_periodicity_results.rda"))
+load(file.path(deaminationDataDirectory, "NHF1_TCG_deamination_periodicity_results.rda"))
 dataSetNames = as.list(setNames(nm = mutperiodData$periodicityResults$Data_Set))

### 2022-04-19 python/SamMismatchesToBed.py
Changed mismatch detection
- Changed mismatch detection process to use the XM field instead of trying to parse the MD field.
- Also fixed a bug where the location of the MD field was not determined correctly because the XS field may or may not be present.

@@ -49,10 +49,21 @@ def samMismatchesToBed(samFilePaths: List[str], verbose = False):
                     # Increment the aligned reads counter
                     alignedReadsCounter += 1
 
-                    # Using the "MD" optional field, determine if there were any mismatches.
-                    # For those those reads that don't contain mismatches (only numeric characters), skip them.
-                    mismatchDesignations = splitLine[17].rsplit(':',1)[1]
-                    if mismatchDesignations.isnumeric(): 
+                    # Find the XM and MD fields and derive information about mismatches from them.
+                    # For those those reads that don't contain mismatches, skip them.
+                    if splitLine[13].startswith("XM"):
+                        mismatchCount = int(splitLine[13].rsplit(':',1)[1])
+                        assert splitLine[17].startswith("MD"), f"MD field not found at expected location:\n{line}"
+                        mismatchDesignations = splitLine[17].rsplit(':',1)[1]
+
+                    elif splitLine[14].startswith("XM"): 
+                        mismatchCount = int(splitLine[14].rsplit(':',1)[1])
+                        assert splitLine[18].startswith("MD"), f"MD field not found at expected location:\n{line}"
+                        mismatchDesignations = splitLine[18].rsplit(':',1)[1]
+
+                    else: raise ValueError(f"XM field not at expected position:\n{line}")
+
+                    if mismatchCount == 0:
                         if verbose: print("Skipping read with no mismatches")
                         continue
 
@@ -109,9 +120,8 @@ def samMismatchesToBed(samFilePaths: List[str], verbose = False):
                                 i += 1
                                 refSeqPos += 1
 
-                    # If no mismatches were found (i.e. the MD string only referenced insertions and deletions), skip this line.
-                    # NOTE: It turns out you can also do this with the "XM" string, which just counts mismatches.
-                    if len(mismatches) == 0: continue
+                    # Ensure that the expected number of mismatches were found.
+                    assert len(mismatches) == mismatchCount, f"Expected mismatch count of {mismatchCount} but found none:\n{line}"
 
                     # Write the pertinent data for this read to the bed output file.
                     # Adjust values as necessary if the read is on the '-' strand.
@@ -125,9 +135,11 @@ def samMismatchesToBed(samFilePaths: List[str], verbose = False):
                             threePrimeMismatchPositions.append(str(pos - refSeqLength))
                             mismatchSequences.append(mismatches[pos])
 
[…]

### 2022-04-19 R/HumanDeaminationAnalysis.rmd

@@
 
+```{r plot_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
+plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, POS_DIFF,
+                         title = "CPD C>T Mismatch Pos Diff Rep1",
+                         xAxisBreaks = c(23:31))
+plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, POS_DIFF,
+                         title = "CPD C>T Mismatch Pos Diff Rep2",
+                         xAxisBreaks = c(23:31))
+
+plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, POS_DIFF,
+                         title = "6-4 C>T Mismatch Pos Diff Rep1",
+                         xAxisBreaks = c(23:31))
+plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, POS_DIFF,
+                         title = "6-4 C>T Mismatch Pos Diff Rep2",
+                         xAxisBreaks = c(23:31))
+```
+
+# ```{r plot_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
+# plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, IQR,
+#                          title = "CPD C>T Mismatch Pos Diff Rep1",
+#                          xAxisBreaks = c(23:31))
+# plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, IQR,
+#                          title = "CPD C>T Mismatch Pos Diff Rep2",
+#                          xAxisBreaks = c(23:31))
+# 
+# plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, IQR,
+#                          title = "6-4 C>T Mismatch Pos Diff Rep1",
+#                          xAxisBreaks = c(23:31))
+# plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, IQR,
+#                          title = "6-4 C>T Mismatch Pos Diff Rep2",
+#                          xAxisBreaks = c(23:31))
+# ```
+
+# ```{r plot_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
+# plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, STDEV,
+#                          title = "CPD C>T Mismatch Pos Diff Rep1",
+#                          xAxisBreaks = c(23:31))
+# plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, STDEV,
+#                          title = "CPD C>T Mismatch Pos Diff Rep2",
+#                          xAxisBreaks = c(23:31))
+# 
+# plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, STDEV,
+#                          title = "6-4 C>T Mismatch Pos Diff Rep1",
+#                          xAxisBreaks = c(23:31))
+# plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, STDEV,
+#                          title = "6-4 C>T Mismatch Pos Diff Rep2",
+#                          xAxisBreaks = c(23:31))
+# ```
+
 ```{r acquire_and_format_data_2}

### 2022-04-19 R/HumanDeaminationAnalysis.rmd
Update HumanDeaminationAnalysis.rmd

@@
 CPDMismatchDataFilePaths$rep1 = list(
-  hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep1_mismatches.bed"),
-  hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep1_mismatches.bed"),
-  hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep1_mismatches.bed"),
-  hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep1_mismatches.bed")
+  hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep1_mismatches_by_read.bed"),
+  hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep1_mismatches_by_read.bed"),
+  hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep1_mismatches_by_read.bed"),
+  hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep1_mismatches_by_read.bed")
 )
 CPDMismatchDataFilePaths$rep2 = list(
-  hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep2_mismatches.bed"),
-  hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep2_mismatches.bed"),
-  hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep2_mismatches.bed"),
-  hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep2_mismatches.bed")
+  hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep2_mismatches_by_read.bed"),
+  hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep2_mismatches_by_read.bed"),
+  hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep2_mismatches_by_read.bed"),
+  hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep2_mismatches_by_read.bed")
 )
@@
 sixFourMismatchDataFilePaths$rep1 = list(
-  min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep1_mismatches.bed"),
-  min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep1_mismatches.bed"),
-  hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep1_mismatches.bed")
+  min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep1_mismatches_by_read.bed"),
+  min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep1_mismatches_by_read.bed"),
+  hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep1_mismatches_by_read.bed")
 )
 sixFourMismatchDataFilePaths$rep2 = list(
-  min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep2_mismatches.bed"),
-  min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep2_mismatches.bed"),
-  hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep2_mismatches.bed")
+  min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep2_mismatches_by_read.bed"),
+  min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep2_mismatches_by_read.bed"),
+  hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep2_mismatches_by_read.bed")
 )
@@
   x, function(y) filterResults(y, TRUE, 3, 23, 31)
+))
+
+# Get the tables of read length vs. GC content
+CPDReadLengthVsGCData = lapply(CPDMismatchData, function(x) lapply(
+  x, getReadLengthAndGCContent
+))
+sixReadLengthVsGCData = lapply(sixFourMismatchData, function(x) lapply(
+  x, getReadLengthAndGCContent
 ))
@@
 
+```{r read_length_vs_GC_content}
+
+```
+
 ```{r acquire_and_format_data_2}
@@
 dataSetNames = as.list(setNames(nm = mutperiodData$periodicityResults$Data_Set))
-
 ```

### 2022-04-19 R/DeaminationAnalysis.R
Added function for getting read length and GC content.

@@ -86,6 +86,13 @@ getTandemCTMismatches = function(table, threePrimeBoundary = NA, fivePrimeBounda
 
 }
 
+# Computes and returns sequence length and GC content for each read in a given table.
+getReadLengthAndGCContent = function(table) {
+  return(table[,.(Length = nchar(V7),
+                  GC_Content = str_count(V7, "C|G") / (nchar(V7) - str_count(V7, 'N')) )])
+}
+
+
 # Displays the frequencies of each mismatch type.
 plotMismatchTypeFrequencies = function(mismatchTable, title = "Mismatch Type Frequency") {
 

### 2022-04-20 python/GetReadLengthVsNucleotideFrequency.py
Smol bugfix

@@ -80,7 +80,7 @@ def main():
         dialog.createTextField("Max Mismatches: ", 2, 0, defaultText = "2")
         dialog.createCheckbox("Allow N's in reads: ", 3, 0)
 
-        with dialog.createDynamicSelector(3, 0) as outputDirDynSel:
+        with dialog.createDynamicSelector(4, 0) as outputDirDynSel:
             outputDirDynSel.initCheckboxController("Specify single output dir")
             outputDirDialog = outputDirDynSel.initDisplay(True, "outputDir")
             outputDirDialog.createFileSelector("Output Directory:", 0, directory = True)

### 2022-04-20 R/HumanDeaminationAnalysis.rmd

@@
 }
+
+deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", "human")
 ```
@@
 ```{r acquire_and_format_data_1}
-deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", "human")
-
-# Read in the relevant data
+# Read in the mismatch by read data
 CPDMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
@@
 
-```{r read_length_vs_GC_content}
+```{r acquire_and_format_data_2}
+# Read in the GC content vs. read length data
+CPDReadLengthAndGCFilePaths = list(rep1 = list(), rep2 = list())
+CPDReadLengthAndGCFilePaths$rep1 = list(
+  hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep1_read_length_vs_GC_content.tsv"),
+  hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep1_read_length_vs_GC_content.tsv"),
+  hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep1_read_length_vs_GC_content.tsv"),
+  hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep1_read_length_vs_GC_content.tsv")
+)
+CPDReadLengthAndGCFilePaths$rep2 = list(
+  hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep2_read_length_vs_GC_content.tsv"),
+  hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep2_read_length_vs_GC_content.tsv"),
+  hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep2_read_length_vs_GC_content.tsv"),
+  hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep2_read_length_vs_GC_content.tsv")
+)
 
+sixFourReadLengthAndGCFilePaths = list(rep1 = list(), rep2 = list())
+sixFourReadLengthAndGCFilePaths$rep1 = list(
+  min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep1_read_length_vs_GC_content.tsv"),
+  min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep1_read_length_vs_GC_content.tsv"),
+  hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep1_read_length_vs_GC_content.tsv")
+)
+sixFourReadLengthAndGCFilePaths$rep2 = list(
+  min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep2_read_length_vs_GC_content.tsv"),
+  min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep2_read_length_vs_GC_content.tsv"),
+  hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep2_read_length_vs_GC_content.tsv")
+)
+
+CPDReadLengthAndGCData = lapply(CPDReadLengthAndGCFilePaths, function(x) lapply(x, fread))
+sixFourReadLengthAndGCData = lapply(sixFourReadLengthAndGCFilePaths, function(x) lapply(x, fread))
 ```
 
-```{r acquire_and_format_data_2}
+```{r CPD_read_length_vs_GC_content}
+for (i in 1:length(CPDReadLengthAndGCData)) {
+  for (j in 1:length(CPDReadLengthAndGCData[[i]])) {
+    plotGCContentVsReadLength(CPDReadLengthAndGCData[[i]][[j]],
+                              title = paste("CPD", names(CPDReadLengthAndGCData)[i], 
+                                            names(CPDReadLengthAndGCData[[i]])[j], "GC Content Vs Read Length"))
+  }
+}
+```
+
+```{r 6-4_read_length_vs_GC_content}
+for (i in 1:length(sixFourReadLengthAndGCData)) {
+  for (j in 1:length(sixFourReadLengthAndGCData[[i]])) {
+    plotGCContentVsReadLength(sixFourReadLengthAndGCData[[i]][[j]],
+                              title = paste("6-4", names(sixFourReadLengthAndGCData)[i], 
+                                            names(sixFourReadLengthAndGCData[[i]])[j], "GC Content Vs Read Length"))
+  }
+}
+```
+
+```{r acquire_and_format_data_3}
 load(file.path(deaminationDataDirectory, "NHF1_deamination_periodicity_results.rda"))

### 2022-04-20 R/HumanDeaminationAnalysis.rmd
Preliminary Commit

@@
 
-# Filter the data
+# Create a subset of single mismatch C>T reads.
+CPDSingleCToTMismatchData = lapply(CPDMismatchData, function(x) lapply(
+  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = 23, maxReadLength = 31)
+))
+sixFourSingleCToTMismatchData = lapply(sixFourMismatchData, function(x) lapply(
+  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = 23, maxReadLength = 31)
+))
+
+# Perform general filtering on the data
 CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
@@
 
-# Extract and simplify tandem C>T mismatches
-CPDTandemCTMismatches = lapply(CPDMismatchData, function(x) lapply(
-  x, function(y) simplifyTable(getTandemCTMismatches(y))
-))
-sixFourTandemCTMismatches = lapply(sixFourMismatchData, function(x) lapply(
-  x, function(y) simplifyTable(getTandemCTMismatches(y))
-))
+# # Extract and simplify tandem C>T mismatches
+# CPDTandemCTMismatches = lapply(CPDMismatchData, function(x) lapply(
+#   x, function(y) simplifyTable(getTandemCTMismatches(y))
+# ))
+# sixFourTandemCTMismatches = lapply(sixFourMismatchData, function(x) lapply(
+#   x, function(y) simplifyTable(getTandemCTMismatches(y))
+# ))
 
@@
   x, function(y) simplifyTable(y)
+))
+CPDSingleCToTMismatchData = lapply(CPDSingleCToTMismatchData, function(x) lapply(
+  x, function(y) simplifyTable(y, TRUE)
+))
+sixFourSingleCToTMismatchData = lapply(sixFourSingleCToTMismatchData, function(x) lapply(
+  x, function(y) simplifyTable(y, TRUE)
 ))

### 2022-04-20 R/DeaminationAnalysis.R

@@ -42,10 +42,15 @@ filterResults = function(mismatchData, removeRowsWithN = TRUE, maxMismatchesAllo
 
 # Simplifies the given table of bed formatted mismatches into a smaller
 # three-column table of positions, sequence context, and read length.
-simplifyTable = function(table) {
-  return(table[,list(Position = as.numeric(unlist(strsplit(V4, ':'))),
-                     Mismatch = unlist(strsplit(V5, ':')),
-                     Read_Length = unlist(mapply(rep, V3-V2, lapply(strsplit(V5,':'), length))))])
+simplifyTable = function(table, includeReadSequence = FALSE) {
+
+  returnTable = table[,list(Position = as.numeric(unlist(strsplit(V4, ':'))),
+                            Mismatch = unlist(strsplit(V5, ':')),
+                            Read_Length = unlist(mapply(rep, V3-V2, lapply(strsplit(V5,':'), length))))]
+  if (includeReadSequence) returnTable[, Read_Sequence := table$V7]
+
+  return(returnTable)
+
 }
 
 
@@ -264,6 +269,14 @@ plotGroupedPositionStats = function(threePrimeGroupedStats, fivePrimeGroupedStat
     scale_x_continuous(breaks = xAxisBreaks)
 
   print(groupedStatsPlot)
+
+}
+
+
+# Calculates nucleotide frequencies at individual positions in a read (relative to the specified end).
+# Takes optional arguments to add columns with additional, repeating information (e.g. read length, timepoint).
+tabulateNucleotideFrequenciesByPosition = function(data, relativePos = THREE_PRIME,
+                                                   paddingColNames = list(), paddingInfo = list()) {
 
 }
 

### 2022-04-21 R/DeaminationAnalysis.R
Added nucleotide frequency plotting
- Added a pair of functions, one for counting nucleotide frequencies across sequences and one for plotting that data stratified by read length and timepoint.
- Some other minor tweaks, comments, code positioning.

@@ -42,6 +42,8 @@ filterResults = function(mismatchData, removeRowsWithN = TRUE, maxMismatchesAllo
 
 # Simplifies the given table of bed formatted mismatches into a smaller
 # three-column table of positions, sequence context, and read length.
+# NOTE: The Read_Length field is only accurate in the absence of indels. Otherwise, it only represents
+#       the length of the aligned region in the reference genome.
 simplifyTable = function(table, includeReadSequence = FALSE) {
 
   returnTable = table[,list(Position = as.numeric(unlist(strsplit(V4, ':'))),
@@ -273,10 +275,82 @@ plotGroupedPositionStats = function(threePrimeGroupedStats, fivePrimeGroupedStat
 }
 
 
-# Calculates nucleotide frequencies at individual positions in a read (relative to the specified end).
+# Calculates nucleotide frequencies at individual positions in a set of reads (relative to the specified end).
 # Takes optional arguments to add columns with additional, repeating information (e.g. read length, timepoint).
-tabulateNucleotideFrequenciesByPosition = function(data, relativePos = THREE_PRIME,
+tabulateNucleotideFrequenciesByPosition = function(sequences, posType = THREE_PRIME,
                                                    paddingColNames = list(), paddingInfo = list()) {
+
+  maxStringLength = max(nchar(sequences))
+  if (posType == THREE_PRIME) {
+    positions = -1:-maxStringLength
+  } else if (posType == FIVE_PRIME) {
+    positions = 1:maxStringLength
+  } else stop("Unrecognized value for posType parameter.")
+
+  nucFreqByPosition = data.table(Position = rep(positions, 4),
+                                 Nucleotide = unlist(lapply(c('A','C','G','T'),
+                                                            function(x) rep(x, maxStringLength))),
+                                 Frequency = unlist(lapply(c('A','C','G','T'), function(x) {
+                                   lapply(positions, function(y) {
+                                     nucleotides = str_sub(sequences, y, y)
+                                     return(sum(nucleotides == x) / sum(nucleotides != ''))
+                                   })
+                                 }))
+                                 )
+
+  mapply(function(x,y) nucFreqByPosition[, eval(x) := y], paddingColNames, paddingInfo)
+
+  return(nucFreqByPosition)
+
+}
+
+
[…]

### 2022-04-21 R/HumanDeaminationAnalysis.rmd
Update HumanDeaminationAnalysis.rmd

@@
 
-# Get the tables of read length vs. GC content
-CPDReadLengthVsGCData = lapply(CPDMismatchData, function(x) lapply(
-  x, getReadLengthAndGCContent
-))
-sixReadLengthVsGCData = lapply(sixFourMismatchData, function(x) lapply(
-  x, getReadLengthAndGCContent
-))
+# # Get the tables of read length vs. GC content
+# CPDReadLengthVsGCData = lapply(CPDMismatchData, function(x) lapply(
+#   x, getReadLengthAndGCContent
+# ))
+# sixReadLengthVsGCData = lapply(sixFourMismatchData, function(x) lapply(
+#   x, getReadLengthAndGCContent
+# ))
 
@@
 
-```{r plot_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
+```{r position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
 plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, POS_DIFF,
@@
 
-# ```{r plot_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
+# ```{r plot_stats_across_read_lengths, fig.width = 9, fig.height = 5}
 # plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, IQR,
@@
 
-# ```{r plot_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
-# plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, STDEV,
-#                          title = "CPD C>T Mismatch Pos Diff Rep1",
-#                          xAxisBreaks = c(23:31))
-# plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, STDEV,
-#                          title = "CPD C>T Mismatch Pos Diff Rep2",
-#                          xAxisBreaks = c(23:31))
+```{r purine_vs_pyrimidine_frequencies_across_read_length, fig.width = 11, fig.height = 5}
+
+plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep1, THREE_PRIME,
+                               title = "CPD Rep1 3' Nuc Freq",
+                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep2, THREE_PRIME,
+                               title = "CPD Rep2 3' Nuc Freq",
+                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep1, FIVE_PRIME,
+                               title = "CPD Rep1 5' Nuc Freq",
+                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep2, FIVE_PRIME,
+                               title = "CPD Rep2 5' Nuc Freq",
+                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+
+plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep1, THREE_PRIME,
+                               title = "6-4 Rep1 3' Nuc Freq",
+                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep2, THREE_PRIME,
+                               title = "6-4 Rep2 3' Nuc Freq",
+                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep1, FIVE_PRIME,
+                               title = "6-4 Rep1 5' Nuc Freq",
+                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep2, FIVE_PRIME,
+                               title = "6-4 Rep2 5' Nuc Freq",
+                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+
+```
+
+# ```{r acquire_and_format_data_2}
+# # Read in the GC content vs. read length data
+# CPDReadLengthAndGCFilePaths = list(rep1 = list(), rep2 = list())
+# CPDReadLengthAndGCFilePaths$rep1 = list(
+#   hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep1_read_length_vs_GC_content.tsv"),
+#   hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep1_read_length_vs_GC_content.tsv"),
+#   hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep1_read_length_vs_GC_content.tsv"),
+#   hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep1_read_length_vs_GC_content.tsv")
+# )
+# CPDReadLengthAndGCFilePaths$rep2 = list(
+#   hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep2_read_length_vs_GC_content.tsv"),
+#   hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep2_read_length_vs_GC_content.tsv"),
+#   hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep2_read_length_vs_GC_content.tsv"),
+#   hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep2_read_length_vs_GC_content.tsv")
+# )
 # 
-# plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, STDEV,
-#                          title = "6-4 C>T Mismatch Pos Diff Rep1",
-#                          xAxisBreaks = c(23:31))
-# plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, STDEV,
-#                          title = "6-4 C>T Mismatch Pos Diff Rep2",
-#                          xAxisBreaks = c(23:31))
+# sixFourReadLengthAndGCFilePaths = list(rep1 = list(), rep2 = list())
+# sixFourReadLengthAndGCFilePaths$rep1 = list(
+#   min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep1_read_length_vs_GC_content.tsv"),
+#   min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep1_read_length_vs_GC_content.tsv"),
+#   hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep1_read_length_vs_GC_content.tsv")
+# )
+# sixFourReadLengthAndGCFilePaths$rep2 = list(
+#   min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep2_read_length_vs_GC_content.tsv"),
+#   min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep2_read_length_vs_GC_content.tsv"),
+#   hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep2_read_length_vs_GC_content.tsv")
+# )
+# 
+# CPDReadLengthAndGCData = lapply(CPDReadLengthAndGCFilePaths, function(x) lapply(x, fread))
+# sixFourReadLengthAndGCData = lapply(sixFourReadLengthAndGCFilePaths, function(x) lapply(x, fread))
 # ```
 
-```{r acquire_and_format_data_2}
-# Read in the GC content vs. read length data
-CPDReadLengthAndGCFilePaths = list(rep1 = list(), rep2 = list())
-CPDReadLengthAndGCFilePaths$rep1 = list(
-  hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep1_read_length_vs_GC_content.tsv"),
-  hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep1_read_length_vs_GC_content.tsv"),
-  hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep1_read_length_vs_GC_content.tsv"),
-  hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep1_read_length_vs_GC_content.tsv")
-)
-CPDReadLengthAndGCFilePaths$rep2 = list(
-  hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep2_read_length_vs_GC_content.tsv"),
-  hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep2_read_length_vs_GC_content.tsv"),
-  hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep2_read_length_vs_GC_content.tsv"),
-  hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep2_read_length_vs_GC_content.tsv")
-)
-
-sixFourReadLengthAndGCFilePaths = list(rep1 = list(), rep2 = list())
-sixFourReadLengthAndGCFilePaths$rep1 = list(
-  min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep1_read_length_vs_GC_content.tsv"),
-  min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep1_read_length_vs_GC_content.tsv"),
-  hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep1_read_length_vs_GC_content.tsv")
-)
-sixFourReadLengthAndGCFilePaths$rep2 = list(
-  min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep2_read_length_vs_GC_content.tsv"),
-  min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep2_read_length_vs_GC_content.tsv"),
-  hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep2_read_length_vs_GC_content.tsv")
-)
-
-CPDReadLengthAndGCData = lapply(CPDReadLengthAndGCFilePaths, function(x) lapply(x, fread))
-sixFourReadLengthAndGCData = lapply(sixFourReadLengthAndGCFilePaths, function(x) lapply(x, fread))
-```
-
-```{r CPD_read_length_vs_GC_content}
-for (i in 1:length(CPDReadLengthAndGCData)) {
-  for (j in 1:length(CPDReadLengthAndGCData[[i]])) {
-    plotGCContentVsReadLength(CPDReadLengthAndGCData[[i]][[j]],
-                              title = paste("CPD", names(CPDReadLengthAndGCData)[i], 
-                                            names(CPDReadLengthAndGCData[[i]])[j], "GC Content Vs Read Length"))
-  }
-}
-```
-
-```{r 6-4_read_length_vs_GC_content}
-for (i in 1:length(sixFourReadLengthAndGCData)) {
-  for (j in 1:length(sixFourReadLengthAndGCData[[i]])) {
-    plotGCContentVsReadLength(sixFourReadLengthAndGCData[[i]][[j]],
-                              title = paste("6-4", names(sixFourReadLengthAndGCData)[i], 
-                                            names(sixFourReadLengthAndGCData[[i]])[j], "GC Content Vs Read Length"))
-  }
-}
-```
+# ```{r CPD_read_length_vs_GC_content}
+# for (i in 1:length(CPDReadLengthAndGCData)) {
+#   for (j in 1:length(CPDReadLengthAndGCData[[i]])) {
+#     plotGCContentVsReadLength(CPDReadLengthAndGCData[[i]][[j]],
+#                               title = paste("CPD", names(CPDReadLengthAndGCData)[i], 
+#                                             names(CPDReadLengthAndGCData[[i]])[j], "GC Content Vs Read Length"))
+#   }
+# }
+# ```
+# 
+# 
+# ```{r 6-4_read_length_vs_GC_content}
+# for (i in 1:length(sixFourReadLengthAndGCData)) {
+#   for (j in 1:length(sixFourReadLengthAndGCData[[i]])) {
+#     plotGCContentVsReadLength(sixFourReadLengthAndGCData[[i]][[j]],
+#                               title = paste("6-4", names(sixFourReadLengthAndGCData)[i], 
+#                                             names(sixFourReadLengthAndGCData[[i]])[j], "GC Content Vs Read Length"))
+#   }
+# }
+# ```
 
@@
 
-```{r acquire_and_format_data_3}
+```{r acquire_and_format_data_4}
 load(file.path(deaminationDataDirectory, "NHF1_TCG_deamination_periodicity_results.rda"))

### 2022-04-21 python/SamMismatchesToBed.py
Added options for indels and output directory
- Reads with indels can now be omitted from output.
- A single, custom output directory can be specified.

@@ -8,7 +8,7 @@ from benbiohelpers.DNA_SequenceHandling import reverseCompliment
 
 strandFromIsReverseComplement = {True:'-', False:'+'}
 
-def samMismatchesToBed(samFilePaths: List[str], verbose = False):
+def samMismatchesToBed(samFilePaths: List[str], omitIndels = True, outputDir = None, verbose = False):
     
     for samFilePath in samFilePaths:
 
@@ -17,15 +17,17 @@ def samMismatchesToBed(samFilePaths: List[str], verbose = False):
         gzipped = samFilePath.endswith(".gz")
 
         # Create output file paths (bed file + metadata)
+        if outputDir is None: outputDir = os.path.dirname(samFilePath)
+
         if gzipped:
-            outputBedFilePath = samFilePath.rsplit('.',2)[0] + "_mismatches_by_read.bed"
+            outputBedFileBasename = os.path.basename(samFilePath).rsplit('.',2)[0] + "_mismatches_by_read.bed"
             openFunction = gzip.open
         else:
-            outputBedFilePath = samFilePath.rsplit('.',1)[0] + "_mismatches_by_read.bed"
+            outputBedFileBasename = os.path.basename(samFilePath).rsplit('.',1)[0] + "_mismatches_by_read.bed"
             openFunction = open
+
+        outputBedFilePath = os.path.join(outputDir, outputBedFileBasename)
         metadataFilePath = outputBedFilePath.rsplit('.',1)[0] + ".metadata"
-
-
 
         # Read through the sam file line by line, looking for mismatches and recording them.
         alignedReadsCounter = 0
@@ -67,6 +69,12 @@ def samMismatchesToBed(samFilePaths: List[str], verbose = False):
                         if verbose: print("Skipping read with no mismatches")
                         continue
 
+                    # Get the cigar string and determine if the read should be skipped for the presence of indels.
+                    cigarString = splitLine[5]
+                    if omitIndels and ('I' in cigarString or 'D' in cigarString):
+                        if verbose: print("Skipping read with indel")
+                        continue
+
                     # Get the sequence (and determine if it should actually be the reverse compliment).
                     readSequence = splitLine[9]
                     isReverseCompliment = bool(int(splitLine[1]) & 0b10000)
@@ -74,7 +82,6 @@ def samMismatchesToBed(samFilePaths: List[str], verbose = False):
[…]

### 2022-04-21 R/DeaminationAnalysis.R
Added mismatch stratification by position
- These functions stratify simplified mismatch data by the position of the mismatch.
- The cutoffs for acceptable position can be modulated by read length if desired.

@@ -56,6 +56,45 @@ simplifyTable = function(table, includeReadSequence = FALSE) {
 }
 
 
+# Takes a simplified table of mismatches and filters them based on the position of the mismatch
+filterMismatchesByPosition = function(mismatchTable, minPos, maxPos, posType) {
+
+  if (posType == THREE_PRIME) {
+    positions = mismatchTable$Position
+  } else if (posType == FIVE_PRIME) {
+    positions = mismatchTable$Read_Length + mismatchTable$Position + 1
+  } else stop("Unrecognized value for posType parameter.")
+
+  return(mismatchTable[positions >= minPos & positions <= maxPos])
+
+}
+
+
+# Takes a simplified table of mismatches and filters them based on the position of the mismatch.
+# Unlike the filterMismatchesByPosition function, min and max positions are dynamic based on read length.
+# (This function is actually still used under the hood.)
+# See constant tables below for examples of how to format the posConstraintsByReadLength table.
+filterMismatchesByPositionAndReadLength = function(mismatchTable, posConstraintsByReadLength) {
+
+  return(rbindlist(mapply( function(readLength, minPos, maxPos) {
+    filterMismatchesByPosition(mismatchTable[Read_Length == readLength], minPos, maxPos, THREE_PRIME)
+  },
+  posConstraintsByReadLength$Read_Length,
+  posConstraintsByReadLength$Min_Pos,
+  posConstraintsByReadLength$Max_Pos,
+  SIMPLIFY = FALSE)))
+
+}
+
+
+HUMAN_THREE_PRIME_POS_CONSTRAINTS = data.table(Read_Length = c(23, 24, 25, 26, 27, 28, 29, 30, 31),
+                                               Max_Pos = c(-3, -3, -4, -5, -5, -6, -6, -6, -6),
+                                               Min_Pos = c(-9, -9, -10, -10, -10, -11, -11, -12, -12))
+# HUMAN_FIVE_PRIME_POS_CONSTRAINTS = copy(HUMAN_THREE_PRIME_POS_CONSTRAINTS)
+# HUMAN_FIVE_PRIME_POS_CONSTRAINTS[, Max_Pos := Read_Length + Max_Pos + 1]
+# HUMAN_FIVE_PRIME_POS_CONSTRAINTS[, Min_Pos := Read_Length + Min_Pos + 1]
+
+
 # Determines if the given mismatch position and type data for a single read
 # contains a tandem C>T mutation.
 hasTandemCTMismatch = function(mismatchPositions, mismatchTypes) {

### 2022-04-21 R/HumanDeaminationAnalysis.rmd
Update HumanDeaminationAnalysis.rmd

@@
 CPDMismatchDataFilePaths$rep1 = list(
-  hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep1_mismatches_by_read.bed"),
-  hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep1_mismatches_by_read.bed"),
-  hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep1_mismatches_by_read.bed"),
-  hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep1_mismatches_by_read.bed")
+  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_1h_Rep1_mismatches_by_read.bed"),
+  hr8 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_8h_Rep1_mismatches_by_read.bed"),
+  hr24 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_24h_Rep1_mismatches_by_read.bed"),
+  hr48 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_48h_Rep1_mismatches_by_read.bed")
 )
 CPDMismatchDataFilePaths$rep2 = list(
-  hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep2_mismatches_by_read.bed"),
-  hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep2_mismatches_by_read.bed"),
-  hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep2_mismatches_by_read.bed"),
-  hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep2_mismatches_by_read.bed")
+  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_1h_Rep2_mismatches_by_read.bed"),
+  hr8 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_8h_Rep2_mismatches_by_read.bed"),
+  hr24 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_24h_Rep2_mismatches_by_read.bed"),
+  hr48 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_48h_Rep2_mismatches_by_read.bed")
 )
@@
 sixFourMismatchDataFilePaths$rep1 = list(
-  min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep1_mismatches_by_read.bed"),
-  min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep1_mismatches_by_read.bed"),
-  hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep1_mismatches_by_read.bed")
+  min5 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_5min_Rep1_mismatches_by_read.bed"),
+  min20 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_20min_Rep1_mismatches_by_read.bed"),
+  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_1h_Rep1_mismatches_by_read.bed")
 )
 sixFourMismatchDataFilePaths$rep2 = list(
-  min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep2_mismatches_by_read.bed"),
-  min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep2_mismatches_by_read.bed"),
-  hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep2_mismatches_by_read.bed")
+  min5 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_5min_Rep2_mismatches_by_read.bed"),
+  min20 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_20min_Rep2_mismatches_by_read.bed"),
+  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_1h_Rep2_mismatches_by_read.bed")
 )
@@
 tableOutputDir = file.path("deamination_analysis_output","human_analysis_tables")
-dir.create(tableOutputDir)
+dir.create(tableOutputDir, recursive = TRUE)
 
@@
 
+```{r purine_vs_pyrimidine_frequencies_first_quartile_mismatch_pos, fig.width = 11, fig.height = 5}
+
+plotNucFreqVsReadLengthBarPlot(rbindlist(lapply(CPDSingleCToTMismatchData$rep1,
+                               THREE_PRIME, title = "CPD Rep1 3' Nuc Freq",
+                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep2,
+                               THREE_PRIME, title = "CPD Rep2 3' Nuc Freq",
+                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep1,
+                               FIVE_PRIME, title = "CPD Rep1 5' Nuc Freq",
+                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep2,
+                               FIVE_PRIME, title = "CPD Rep2 5' Nuc Freq",
+                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+
+plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep1, THREE_PRIME,
+                               title = "6-4 Rep1 3' Nuc Freq",
+                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep2, THREE_PRIME,
+                               title = "6-4 Rep2 3' Nuc Freq",
+                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep1, FIVE_PRIME,
+                               title = "6-4 Rep1 5' Nuc Freq",
+                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep2, FIVE_PRIME,
+                               title = "6-4 Rep2 5' Nuc Freq",
+                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+
+```
+
 # ```{r acquire_and_format_data_2}
@@
 ```{r acquire_and_format_data_3}
-load(file.path(deaminationDataDirectory, "NHF1_deamination_periodicity_results.rda"))
+load(file.path(deaminationDataDirectory, "periodicity_results", "NHF1_deamination_periodicity_results.rda"))
 dataSetNames = as.list(setNames(nm = mutperiodData$periodicityResults$Data_Set))
@@
 ```{r acquire_and_format_data_4}
-load(file.path(deaminationDataDirectory, "NHF1_TCG_deamination_periodicity_results.rda"))
+load(file.path(deaminationDataDirectory, "periodicity_results", "NHF1_TCG_deamination_periodicity_results.rda"))
 dataSetNames = as.list(setNames(nm = mutperiodData$periodicityResults$Data_Set))

### 2022-04-22 R/DeaminationAnalysis.R
Added quartile functions

@@ -95,6 +95,15 @@ HUMAN_THREE_PRIME_POS_CONSTRAINTS = data.table(Read_Length = c(23, 24, 25, 26, 2
 # HUMAN_FIVE_PRIME_POS_CONSTRAINTS[, Min_Pos := Read_Length + Min_Pos + 1]
 
 
+# The following functions get the first or last quartile of a data.table sorted by position.
+getFirstPositionQuartile = function(table) {
+  return(table[order(Position)][1:(dim(table)[1]/4)])
+}
+getLastPositionQuartile = function(table) {
+  return(table[order(Position)][(dim(table)[1]*3/4):dim(table)[1]])
+}
+
+
 # Determines if the given mismatch position and type data for a single read
 # contains a tandem C>T mutation.
 hasTandemCTMismatch = function(mismatchPositions, mismatchTypes) {

### 2022-04-22 R/HumanDeaminationAnalysis.rmd
Update HumanDeaminationAnalysis.rmd

@@
 ```{r purine_vs_pyrimidine_frequencies_across_read_length, fig.width = 11, fig.height = 5}
-
 plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep1, THREE_PRIME,
                                title = "CPD Rep1 3' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
 plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep2, THREE_PRIME,
                                title = "CPD Rep2 3' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
 plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep1, FIVE_PRIME,
                                title = "CPD Rep1 5' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
 plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep2, FIVE_PRIME,
                                title = "CPD Rep2 5' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
 
@@
                                title = "6-4 Rep1 3' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
 plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep2, THREE_PRIME,
                                title = "6-4 Rep2 3' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
 plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep1, FIVE_PRIME,
                                title = "6-4 Rep1 5' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
 plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep2, FIVE_PRIME,
                                title = "6-4 Rep2 5' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
+```
 
+```{r filter_by_mismatch_pos_and_read_length}
+CPDFilteredSingleCToTMismatchData = lapply(CPDSingleCToTMismatchData, function(x) {
+  lapply(x, filterMismatchesByPositionAndReadLength, HUMAN_THREE_PRIME_POS_CONSTRAINTS)
+})
+sixFourFilteredSingleCToTMismatchData = lapply(sixFourSingleCToTMismatchData, function(x) {
+  lapply(x, filterMismatchesByPositionAndReadLength, HUMAN_THREE_PRIME_POS_CONSTRAINTS)
+})
 ```
@@
 
-plotNucFreqVsReadLengthBarPlot(rbindlist(lapply(CPDSingleCToTMismatchData$rep1,
-                               THREE_PRIME, title = "CPD Rep1 3' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep2,
-                               THREE_PRIME, title = "CPD Rep2 3' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep1,
-                               FIVE_PRIME, title = "CPD Rep1 5' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep2,
-                               FIVE_PRIME, title = "CPD Rep2 5' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(lapply(CPDFilteredSingleCToTMismatchData$rep1, getFirstPositionQuartile),
+                               THREE_PRIME, title = "CPD Rep1 1st Quartile Nuc Freq",
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(lapply(CPDFilteredSingleCToTMismatchData$rep2, getFirstPositionQuartile),
+                               THREE_PRIME, title = "CPD Rep2 1st Quartile Nuc Freq",
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
 
-plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep1, THREE_PRIME,
-                               title = "6-4 Rep1 3' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep2, THREE_PRIME,
-                               title = "6-4 Rep2 3' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep1, FIVE_PRIME,
-                               title = "6-4 Rep1 5' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep2, FIVE_PRIME,
-                               title = "6-4 Rep2 5' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(lapply(sixFourFilteredSingleCToTMismatchData$rep1, getFirstPositionQuartile),
+                               THREE_PRIME, title = "6-4 Rep1 1st Quartile Nuc Freq",
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(lapply(sixFourFilteredSingleCToTMismatchData$rep2, getFirstPositionQuartile),
+                               THREE_PRIME, title = "6-4 Rep2 1st Quartile Nuc Freq",
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
+```
 
+```{r purine_vs_pyrimidine_frequencies_last_quartile_mismatch_pos, fig.width = 11, fig.height = 5}
+
+plotNucFreqVsReadLengthBarPlot(lapply(CPDFilteredSingleCToTMismatchData$rep1, getLastPositionQuartile),
+                               THREE_PRIME, title = "CPD Rep1 4th Quartile Nuc Freq",
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(lapply(CPDFilteredSingleCToTMismatchData$rep2, getLastPositionQuartile),
+                               THREE_PRIME, title = "CPD Rep2 4th Quartile Nuc Freq",
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
+
+plotNucFreqVsReadLengthBarPlot(lapply(sixFourFilteredSingleCToTMismatchData$rep1, getLastPositionQuartile),
+                               THREE_PRIME, title = "6-4 Rep1 4th Quartile Nuc Freq",
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(lapply(sixFourFilteredSingleCToTMismatchData$rep2, getLastPositionQuartile),
+                               THREE_PRIME, title = "6-4 Rep2 4th Quartile Nuc Freq",
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
 ```

### 2022-04-22 R/DeaminationAnalysis.R
Restructured nucleotide frequency functions
- Added a function for tabulating nucleotide frequencies with a list of tables, stratified by timepoint.
- Added an independent function for combining nucleotide frequencies.
- Because of the above changes, the nucleotide frequency plotting function now takes a nucleotide frequency table directly as a parameter instead of generating it on the fly.

@@ -353,8 +353,45 @@ tabulateNucleotideFrequenciesByPosition = function(sequences, posType = THREE_PR
 }
 
 
+tabulateNucFreqByPosTimepointAndLength = function(simplifiedTablesByTimepoint, posType = THREE_PRIME,
+                                                  combineNucleotides = list(), combinedNames = list()) {
+
+  # First, stratify the data by length and timepoint,
+  # calculating relative nucleotide frequencies within each category.
+  nucFreqTable = rbindlist(lapply(seq_along(simplifiedTablesByTimepoint), function(i) {
+    rbindlist(lapply(unique(simplifiedTablesByTimepoint[[i]]$Read_Length), function(x) {
+      tabulateNucleotideFrequenciesByPosition(simplifiedTablesByTimepoint[[i]][Read_Length == x]$Read_Sequence,
+                                              posType, paddingColNames = c("Read_Length", "Timepoint"),
+                                              paddingInfo = c(x, names(simplifiedTablesByTimepoint)[i]))
+    }))
+  }))
+
+  # Next, perform any transformations on the frequencies as specified by the "combine" parameters.
+  # For example, convert to counts of Purines and pyrimidines.
+  if (length(combineNucleotides) > 0) {
+    nucFreqTable = combineNucleotideFrequencies(nucFreqTable, combineNucleotides, combinedNames)
+  }
+
+  return(nucFreqTable)
+
+}
+
+
+# Calculates frequencies as a combination of individual nucleotide frequencies.
+# For example, calculates purine frequencies by combining 'A' and 'G' nucleotides.
+combineNucleotideFrequencies = function(frequencyData, combineNucleotides = list(), combinedNames = list()) {
+
+  return(rbindlist(mapply(function(x,y) {
+    frequencyData[sapply(Nucleotide, grepl, x),
+                   .(Frequency = sum(Frequency), Nucleotide = y),
+                   by = list(Position, Read_Length, Timepoint)]
+  }, combineNucleotides, combinedNames, SIMPLIFY = FALSE)))
+
+}
+
+
 # Plot nucleotide frequencies (overlapping bar plot?) for a series of read lengths.
-plotNucFreqVsReadLengthBarPlot = function(simplifiedTablesByTimepoint, posType,
+plotNucFreqVsReadLengthBarPlot = function(nucFreqTable, posType = THREE_PRIME,
                                           title = "Nuc Freq by Length and Timepoint",
[…]

### 2022-04-22 R/HumanDeaminationAnalysis.rmd
Update HumanDeaminationAnalysis.rmd

--- 2022-04-21 R/HumanDeaminationAnalysis.rmd
@@
 
+```{r filter_by_mismatch_pos_and_read_length}
+CPDPeakCToTMismatchData = lapply(CPDSingleCToTMismatchData, function(x) {
+  lapply(x, filterMismatchesByPositionAndReadLength, HUMAN_THREE_PRIME_POS_CONSTRAINTS)
+})
+CPDFirstQPeakCToTMismatchData = lapply(CPDPeakCToTMismatchData, function(x) {
+  lapply(x, getFirstPositionQuartile)
+})
+CPDLastQPeakCToTMismatchData = lapply(CPDPeakCToTMismatchData, function(x) {
+  lapply(x, getLastPositionQuartile)
+})
+
+sixFourPeakCToTMismatchData = lapply(sixFourSingleCToTMismatchData, function(x) {
+  lapply(x, filterMismatchesByPositionAndReadLength, HUMAN_THREE_PRIME_POS_CONSTRAINTS)
+})
+sixFourFirstQPeakCToTMismatchData = lapply(sixFourPeakCToTMismatchData, function(x) {
+  lapply(x, getFirstPositionQuartile)
+})
+sixFourLastQPeakCToTMismatchData = lapply(sixFourPeakCToTMismatchData, function(x) {
+  lapply(x, getLastPositionQuartile)
+})
+```
+
+```{r generate_frequency_data}
+CPDSingleCToTNucFreq = lapply(CPDSingleCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
+CPDFirstQPeakCToTNucFreq = lapply(CPDFirstQPeakCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
+CPDLastQPeakCToTNucFreq = lapply(CPDLastQPeakCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
+
+sixFourSingleCToTNucFreq = lapply(sixFourSingleCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
+sixFourFirstQPeakCToTNucFreq = lapply(sixFourFirstQPeakCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
+sixFourLastQPeakCToTNucFreq = lapply(sixFourLastQPeakCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
+```
+
 ```{r purine_vs_pyrimidine_frequencies_across_read_length, fig.width = 11, fig.height = 5}
+plotNucFreqVsReadLengthBarPlot(CPDSingleCToTNucFreq$rep1, title = "CPD Rep1 3' Nuc Freq",
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(CPDSingleCToTNucFreq$rep2, title = "CPD Rep2 3' Nuc Freq",
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
 
-plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep1, THREE_PRIME,
-                               title = "CPD Rep1 3' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep2, THREE_PRIME,
-                               title = "CPD Rep2 3' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep1, FIVE_PRIME,
-                               title = "CPD Rep1 5' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep2, FIVE_PRIME,
-                               title = "CPD Rep2 5' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
-
-plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep1, THREE_PRIME,
-                               title = "6-4 Rep1 3' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep2, THREE_PRIME,
-                               title = "6-4 Rep2 3' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep1, FIVE_PRIME,
-                               title = "6-4 Rep1 5' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep2, FIVE_PRIME,
-                               title = "6-4 Rep2 5' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
-
+plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTNucFreq$rep1, title = "6-4 Rep1 3' Nuc Freq",
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTNucFreq$rep2, title = "6-4 Rep2 3' Nuc Freq",
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
 ```
@@
 ```{r purine_vs_pyrimidine_frequencies_first_quartile_mismatch_pos, fig.width = 11, fig.height = 5}
+plotNucFreqVsReadLengthBarPlot(CPDFirstQPeakCToTNucFreq$rep1, title = "CPD Rep1 1st Quartile Nuc Freq",
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(CPDFirstQPeakCToTNucFreq$rep2, title = "CPD Rep2 1st Quartile Nuc Freq",
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
 
-plotNucFreqVsReadLengthBarPlot(rbindlist(lapply(CPDSingleCToTMismatchData$rep1,
-                               THREE_PRIME, title = "CPD Rep1 3' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep2,
-                               THREE_PRIME, title = "CPD Rep2 3' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep1,
-                               FIVE_PRIME, title = "CPD Rep1 5' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(CPDSingleCToTMismatchData$rep2,
-                               FIVE_PRIME, title = "CPD Rep2 5' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(sixFourFirstQPeakCToTNucFreq$rep1, title = "6-4 Rep1 1st Quartile Nuc Freq",
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(sixFourFirstQPeakCToTNucFreq$rep2, title = "6-4 Rep2 1st Quartile Nuc Freq",
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
+```
 
-plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep1, THREE_PRIME,
-                               title = "6-4 Rep1 3' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep2, THREE_PRIME,
-                               title = "6-4 Rep2 3' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep1, FIVE_PRIME,
-                               title = "6-4 Rep1 5' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTMismatchData$rep2, FIVE_PRIME,
-                               title = "6-4 Rep2 5' Nuc Freq",
-                               combineNucleotides = c("AG","CG"), combinedNames = c("Purine","Pyrimidine"))
+```{r purine_vs_pyrimidine_frequencies_last_quartile_mismatch_pos, fig.width = 11, fig.height = 5}
+plotNucFreqVsReadLengthBarPlot(CPDLastQPeakCToTNucFreq$rep1, title = "CPD Rep1 4th Quartile Nuc Freq",
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(CPDLastQPeakCToTNucFreq$rep2, title = "CPD Rep2 4th Quartile Nuc Freq",
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
 
+plotNucFreqVsReadLengthBarPlot(sixFourLastQPeakCToTNucFreq$rep1, title = "6-4 Rep1 4th Quartile Nuc Freq",
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
+plotNucFreqVsReadLengthBarPlot(sixFourLastQPeakCToTNucFreq$rep2, title = "6-4 Rep2 4th Quartile Nuc Freq",
+                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
 ```

### 2022-04-27 R/HumanDeaminationAnalysis.rmd
Update HumanDeaminationAnalysis.rmd

@@
                                     title = paste("CPD", names(CPDMismatchData)[i], 
-                                                  names(CPDMismatchData[[i]])[j], "C>T Mismatch Positions"),
-                                    posType = FIVE_PRIME)
+                                                  names(CPDMismatchData[[i]])[j], "C>T Mismatch Positions"))
     plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], omittedTypes = c("C>T"),

### 2022-05-03 R/HumanDeaminationAnalysis_DEPRECATED.rmd
Reorganized human deamination analyses
- Split the main deamination analysis notebook into three separate notebooks outlining different parts of the analysis: Initial validation and positional analysis, read length and cut site analysis, and periodicity analysis

- Any analyses that had been deemed extraneous were also cut out during this move. There are still present, commented out, in the original document, now named "HumanDeaminationAnalysis_DEPRECATED.rmd"

--- 2022-04-27 R/HumanDeaminationAnalysis.rmd
@@
 
-```{r acquire_and_format_data_1}
-# Read in the mismatch by read data
+```{r get_file_paths_1}
+# Get file paths for the mismatch by read data
 CPDMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
@@
 
+# Also create a flattened list of file paths for use in caching.
+flattenedMismatchReadsFilePaths = c(unlist(CPDMismatchDataFilePaths), unlist(sixFourMismatchDataFilePaths))
+```
+
+```{r setup_caching_1}
+drosophilaMutperiodData = file.path(drosophilaDataDir, "full_color_domain_analysis_combined_5.rda")
+knitr::opts_template$set(mismatchReadsCaching = list(
+  cache = TRUE, cache.extra = na.fail(tools::md5sum(flattenedMismatchReadsFilePaths))
+))
+```
+
+```{r acquire_and_format_data_1, opts.label = "mismatchReadsCaching"}
 CPDMismatchData = lapply(CPDMismatchDataFilePaths, function(x) lapply(x, fread))
@@
 
-```{r CPD_mismatch_type_frequency}
+```{r CPD_mismatch_type_frequency, opts.label = "mismatchReadsCaching"}
 for (i in 1:length(CPDMismatchData)) {
@@
 
-```{r 6-4_mismatch_type_frequency}
+```{r 6-4_mismatch_type_frequency, opts.label = "mismatchReadsCaching"}
 for (i in 1:length(sixFourMismatchData)) {
@@
 
-```{r CPD_mismatch_pos_frequency}
+```{r CPD_mismatch_pos_frequency, opts.label = "mismatchReadsCaching"}
 for (i in 1:length(CPDMismatchData)) {
@@
 
-```{r 6-4_mismatch_pos_frequency}
+```{r 6-4_mismatch_pos_frequency, opts.label = "mismatchReadsCaching"}
 for (i in 1:length(sixFourMismatchData)) {
@@
 
-```{r facet_mismatch_position_frequencies, fig.width = 9, fig.height = 5}
+```{r facet_mismatch_position_frequencies, fig.width = 9, fig.height = 5, opts.label = "mismatchReadsCaching"}
 plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, includedTypes = c("C>T"),
@@
 
-```{r facet_mismatch_position_statistics}
+```{r facet_mismatch_position_statistics, opts.label = "mismatchReadsCaching"}
 CPDGroupedStats = list(rep1 = list(), rep2 = list())
@@
 
-```{r position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
+```{r position_differences_across_read_lengths, fig.width = 9, fig.height = 5, opts.label = "mismatchReadsCaching"}
 plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, POS_DIFF,
@@
 
-```{r filter_by_mismatch_pos_and_read_length}
+```{r filter_by_mismatch_pos_and_read_length, opts.label = "mismatchReadsCaching"}
 CPDPeakCToTMismatchData = lapply(CPDSingleCToTMismatchData, function(x) {
@@
 
-```{r generate_frequency_data}
+```{r generate_nucleotide_frequency_data, opts.label = "mismatchReadsCaching"}
 CPDSingleCToTNucFreq = lapply(CPDSingleCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
@@
 
-```{r purine_vs_pyrimidine_frequencies_across_read_length, fig.width = 11, fig.height = 5}
+```{r purine_vs_pyrimidine_frequencies_across_read_length, fig.width = 11, fig.height = 5, opts.label = "mismatchReadsCaching"}
 plotNucFreqVsReadLengthBarPlot(CPDSingleCToTNucFreq$rep1, title = "CPD Rep1 3' Nuc Freq",
@@
 
-```{r purine_vs_pyrimidine_frequencies_first_quartile_mismatch_pos, fig.width = 11, fig.height = 5}
+```{r purine_vs_pyrimidine_frequencies_first_quartile_mismatch_pos, fig.width = 11, fig.height = 5, opts.label = "mismatchReadsCaching"}
 plotNucFreqVsReadLengthBarPlot(CPDFirstQPeakCToTNucFreq$rep1, title = "CPD Rep1 1st Quartile Nuc Freq",
@@
 
-```{r purine_vs_pyrimidine_frequencies_last_quartile_mismatch_pos, fig.width = 11, fig.height = 5}
+```{r purine_vs_pyrimidine_frequencies_last_quartile_mismatch_pos, fig.width = 11, fig.height = 5, opts.label = "mismatchReadsCaching"}
 plotNucFreqVsReadLengthBarPlot(CPDLastQPeakCToTNucFreq$rep1, title = "CPD Rep1 4th Quartile Nuc Freq",

### 2022-05-03 R/HumanDeaminationPeriodicityAnalysis.rmd
Reorganized human deamination analyses
- Split the main deamination analysis notebook into three separate notebooks outlining different parts of the analysis: Initial validation and positional analysis, read length and cut site analysis, and periodicity analysis

- Any analyses that had been deemed extraneous were also cut out during this move. There are still present, commented out, in the original document, now named "HumanDeaminationAnalysis_DEPRECATED.rmd"

--- 2022-04-27 R/HumanDeaminationAnalysis.rmd
@@
 ---
-title: "R Notebook"
+title: "Human Deamination Periodicity Analysis"
+author: "Ben Morledge-Hampton"
+date: "5/2/2022"
 output: html_document
@@
 ```{r source_functions}
-source(file.path(bioinformaticsDirectory, "deamination_determination", 'R', "DeaminationAnalysis.R"))
 source(file.path(bioinformaticsDirectory, "Chromatin_Features_Analysis", "R_scripts", "PeriodicityAnalysis.R"))
@@
 ```{r acquire_and_format_data_1}
-# Read in the mismatch by read data
-CPDMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
-CPDMismatchDataFilePaths$rep1 = list(
-  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_1h_Rep1_mismatches_by_read.bed"),
-  hr8 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_8h_Rep1_mismatches_by_read.bed"),
-  hr24 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_24h_Rep1_mismatches_by_read.bed"),
-  hr48 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_48h_Rep1_mismatches_by_read.bed")
-)
-CPDMismatchDataFilePaths$rep2 = list(
-  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_1h_Rep2_mismatches_by_read.bed"),
-  hr8 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_8h_Rep2_mismatches_by_read.bed"),
-  hr24 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_24h_Rep2_mismatches_by_read.bed"),
-  hr48 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_48h_Rep2_mismatches_by_read.bed")
-)
-
-sixFourMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
-sixFourMismatchDataFilePaths$rep1 = list(
-  min5 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_5min_Rep1_mismatches_by_read.bed"),
-  min20 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_20min_Rep1_mismatches_by_read.bed"),
-  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_1h_Rep1_mismatches_by_read.bed")
-)
-sixFourMismatchDataFilePaths$rep2 = list(
-  min5 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_5min_Rep2_mismatches_by_read.bed"),
-  min20 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_20min_Rep2_mismatches_by_read.bed"),
-  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_1h_Rep2_mismatches_by_read.bed")
-)
-
-CPDMismatchData = lapply(CPDMismatchDataFilePaths, function(x) lapply(x, fread))
-sixFourMismatchData = lapply(sixFourMismatchDataFilePaths, function(x) lapply(x, fread))
-
-# Create a subset of single mismatch C>T reads.
-CPDSingleCToTMismatchData = lapply(CPDMismatchData, function(x) lapply(
-  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = 23, maxReadLength = 31)
-))
-sixFourSingleCToTMismatchData = lapply(sixFourMismatchData, function(x) lapply(
-  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = 23, maxReadLength = 31)
-))
-
-# Perform general filtering on the data
-CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
-  x, function(y) filterResults(y, TRUE, 3, 23, 31)
-))
-sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
-  x, function(y) filterResults(y, TRUE, 3, 23, 31)
-))
-
-# # Get the tables of read length vs. GC content
-# CPDReadLengthVsGCData = lapply(CPDMismatchData, function(x) lapply(
-#   x, getReadLengthAndGCContent
-# ))
-# sixReadLengthVsGCData = lapply(sixFourMismatchData, function(x) lapply(
-#   x, getReadLengthAndGCContent
-# ))
-
-# # Extract and simplify tandem C>T mismatches
-# CPDTandemCTMismatches = lapply(CPDMismatchData, function(x) lapply(
-#   x, function(y) simplifyTable(getTandemCTMismatches(y))
-# ))
-# sixFourTandemCTMismatches = lapply(sixFourMismatchData, function(x) lapply(
-#   x, function(y) simplifyTable(getTandemCTMismatches(y))
-# ))
-
-# Simplify the data
-CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
-  x, function(y) simplifyTable(y)
-))
-sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
-  x, function(y) simplifyTable(y)
-))
-CPDSingleCToTMismatchData = lapply(CPDSingleCToTMismatchData, function(x) lapply(
-  x, function(y) simplifyTable(y, TRUE)
-))
-sixFourSingleCToTMismatchData = lapply(sixFourSingleCToTMismatchData, function(x) lapply(
-  x, function(y) simplifyTable(y, TRUE)
-))
-
-```
-
-```{r CPD_mismatch_type_frequency}
-for (i in 1:length(CPDMismatchData)) {
-  for (j in 1:length(CPDMismatchData[[i]])) {
-    plotMismatchTypeFrequencies(CPDMismatchData[[i]][[j]],
-                                title = paste("CPD", names(CPDMismatchData)[i], 
-                                              names(CPDMismatchData[[i]])[j], "Mismatch Type Frequency"))
-  }
-}
-```
-
-```{r 6-4_mismatch_type_frequency}
-for (i in 1:length(sixFourMismatchData)) {
-  for (j in 1:length(sixFourMismatchData[[i]])) {
-    plotMismatchTypeFrequencies(sixFourMismatchData[[i]][[j]],
-                                title = paste("6-4", names(sixFourMismatchData)[i], 
-                                              names(sixFourMismatchData[[i]])[j], "Mismatch Type Frequency"))
-  }
-}
-
-```
-
-```{r CPD_mismatch_pos_frequency}
-for (i in 1:length(CPDMismatchData)) {
-  for (j in 1:length(CPDMismatchData[[i]])) {
-    plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], includedTypes = c("C>T"),
-                                    title = paste("CPD", names(CPDMismatchData)[i], 
-                                                  names(CPDMismatchData[[i]])[j], "C>T Mismatch Positions"))
-    plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], omittedTypes = c("C>T"),
-                                    title = paste("CPD", names(CPDMismatchData)[i], 
-                                                  names(CPDMismatchData[[i]])[j], "!C>T Mismatch Positions"))
-  }
-}
-```
-
-```{r 6-4_mismatch_pos_frequency}
-for (i in 1:length(sixFourMismatchData)) {
-  for (j in 1:length(sixFourMismatchData[[i]])) {
-    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], includedTypes = c("C>T"),
-                                    title = paste("6-4", names(sixFourMismatchData)[i], 
-                                                  names(sixFourMismatchData[[i]])[j], "C>T Mismatch Positions"))
-    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], includedTypes = c("C>T"),
-                                    title = paste("6-4", names(sixFourMismatchData)[i], 
-                                                  names(sixFourMismatchData[[i]])[j], "C>T Mismatch Positions"),
-                                    posType = FIVE_PRIME)
-
-    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], omittedTypes = c("C>T"),
-                                    title = paste("6-4", names(sixFourMismatchData)[i], 
-                                                  names(sixFourMismatchData[[i]])[j], "!C>T Mismatch Positions"))
-  }
-}
-
-```
-
-# ```{r CPD_tandem_C_to_T_pos_frequency}
-# for (i in 1:length(CPDTandemCTMismatches)) {
-#   for (j in 1:length(CPDTandemCTMismatches[[i]])) {
-#     plotMismatchPositionFrequencies(CPDTandemCTMismatches[[i]][[j]],
-#                                     title = paste("CPD", names(CPDTandemCTMismatches)[i], 
-#                                                   names(CPDTandemCTMismatches[[i]])[j], "Tandem C>T Mismatch Pos"))
-#   }
-# }
-# ```
-
-# ```{r 6-4_tandem_C_to_T_pos_frequency}
-# for (i in 1:length(sixFourTandemCTMismatches)) {
-#   for (j in 1:length(sixFourTandemCTMismatches[[i]])) {
-#     plotMismatchPositionFrequencies(sixFourTandemCTMismatches[[i]][[j]],
-#                                     title = paste("6-4", names(sixFourTandemCTMismatches)[i], 
-#                                                   names(sixFourTandemCTMismatches[[i]])[j], 
-#                                                   "Tandem C>T Mismatch Pos"))
-#   }
-# }
-# ```
-
-```{r facet_mismatch_position_frequencies, fig.width = 9, fig.height = 5}
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, includedTypes = c("C>T"),
-                                         title = "CPD C>T Mismatch Pos Freq Rep1")
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, includedTypes = c("C>T"),
-                                         title = "CPD C>T Mismatch Pos Freq Rep2")
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, includedTypes = c("C>T"),
-                                         title = "CPD C>T Mismatch Pos Freq Rep1", posType = FIVE_PRIME)
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, includedTypes = c("C>T"),
-                                         title = "CPD C>T Mismatch Pos Freq Rep2", posType = FIVE_PRIME)
-
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, includedTypes = c("C>T"),
-                                         title = "6-4 C>T Mismatch Pos Freq Rep1")
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, includedTypes = c("C>T"),
-                                         title = "6-4 C>T Mismatch Pos Freq Rep2")
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, includedTypes = c("C>T"),
-                                         title = "6-4 C>T Mismatch Pos Freq Rep1", posType = FIVE_PRIME)
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, includedTypes = c("C>T"),
-                                         title = "6-4 C>T Mismatch Pos Freq Rep2", posType = FIVE_PRIME)
-```
-
-```{r facet_mismatch_position_statistics}
-CPDGroupedStats = list(rep1 = list(), rep2 = list())
-CPDGroupedStats$rep1$three_prime = getGroupedPositionStats(CPDMismatchData$rep1, includedTypes = c("C>T"))
-CPDGroupedStats$rep2$three_prime = getGroupedPositionStats(CPDMismatchData$rep2, includedTypes = c("C>T"))
-CPDGroupedStats$rep1$five_prime =
-  getGroupedPositionStats(CPDMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME)
-CPDGroupedStats$rep2$five_prime =
-  getGroupedPositionStats(CPDMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME)
-
-sixFourGroupedStats = list(rep1 = list(), rep2 = list())
-sixFourGroupedStats$rep1$three_prime = getGroupedPositionStats(sixFourMismatchData$rep1, includedTypes = c("C>T"))
-sixFourGroupedStats$rep2$three_prime = getGroupedPositionStats(sixFourMismatchData$rep2, includedTypes = c("C>T"))
-sixFourGroupedStats$rep1$five_prime =
-  getGroupedPositionStats(sixFourMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME)
-sixFourGroupedStats$rep2$five_prime =
-  getGroupedPositionStats(sixFourMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME)
-
-tableOutputDir = file.path("deamination_analysis_output","human_analysis_tables")
-dir.create(tableOutputDir, recursive = TRUE)
-
-fwrite(CPDGroupedStats$rep1$three_prime,
-       file.path(tableOutputDir, "CPD_mismatch_three_prime_position_stats_rep1.tsv"),sep = '\t')
-fwrite(CPDGroupedStats$rep2$three_prime,
-       file.path(tableOutputDir, "CPD_mismatch_three_prime_position_stats_rep2.tsv"),sep = '\t')
-fwrite(CPDGroupedStats$rep1$five_prime,
-       file.path(tableOutputDir, "CPD_mismatch_five_prime_position_stats_rep1.tsv"),sep = '\t')
-fwrite(CPDGroupedStats$rep2$five_prime,
-       file.path(tableOutputDir, "CPD_mismatch_five_prime_position_stats_rep2.tsv"),sep = '\t')
-
-fwrite(sixFourGroupedStats$rep1$three_prime,
-       file.path(tableOutputDir, "6-4_mismatch_three_prime_position_stats_rep1.tsv"), sep = '\t')
-fwrite(sixFourGroupedStats$rep2$three_prime,
-       file.path(tableOutputDir, "6-4_mismatch_three_prime_position_stats_rep2.tsv"), sep = '\t')
-fwrite(sixFourGroupedStats$rep1$five_prime,
-       file.path(tableOutputDir, "6-4_mismatch_five_prime_position_stats_rep1.tsv"), sep = '\t')
-fwrite(sixFourGroupedStats$rep2$five_prime,
-       file.path(tableOutputDir, "6-4_mismatch_five_prime_position_stats_rep2.tsv"), sep = '\t')
-```
-
-```{r position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
-plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, POS_DIFF,
-                         title = "CPD C>T Mismatch Pos Diff Rep1",
-                         xAxisBreaks = c(23:31))
-plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, POS_DIFF,
-                         title = "CPD C>T Mismatch Pos Diff Rep2",
-                         xAxisBreaks = c(23:31))
-
-plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, POS_DIFF,
-                         title = "6-4 C>T Mismatch Pos Diff Rep1",
-                         xAxisBreaks = c(23:31))
-plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, POS_DIFF,
-                         title = "6-4 C>T Mismatch Pos Diff Rep2",
-                         xAxisBreaks = c(23:31))
-```
-
-# ```{r plot_stats_across_read_lengths, fig.width = 9, fig.height = 5}
-# plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, IQR,
-#                          title = "CPD C>T Mismatch Pos Diff Rep1",
-#                          xAxisBreaks = c(23:31))
-# plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, IQR,
-#                          title = "CPD C>T Mismatch Pos Diff Rep2",
-#                          xAxisBreaks = c(23:31))
-# 
-# plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, IQR,
-#                          title = "6-4 C>T Mismatch Pos Diff Rep1",
-#                          xAxisBreaks = c(23:31))
-# plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, IQR,
-#                          title = "6-4 C>T Mismatch Pos Diff Rep2",
-#                          xAxisBreaks = c(23:31))
-# ```
-
-```{r filter_by_mismatch_pos_and_read_length}
-CPDPeakCToTMismatchData = lapply(CPDSingleCToTMismatchData, function(x) {
-  lapply(x, filterMismatchesByPositionAndReadLength, HUMAN_THREE_PRIME_POS_CONSTRAINTS)
-})
-CPDFirstQPeakCToTMismatchData = lapply(CPDPeakCToTMismatchData, function(x) {
-  lapply(x, getFirstPositionQuartile)
-})
-CPDLastQPeakCToTMismatchData = lapply(CPDPeakCToTMismatchData, function(x) {
-  lapply(x, getLastPositionQuartile)
-})
-
-sixFourPeakCToTMismatchData = lapply(sixFourSingleCToTMismatchData, function(x) {
-  lapply(x, filterMismatchesByPositionAndReadLength, HUMAN_THREE_PRIME_POS_CONSTRAINTS)
-})
-sixFourFirstQPeakCToTMismatchData = lapply(sixFourPeakCToTMismatchData, function(x) {
-  lapply(x, getFirstPositionQuartile)
-})
-sixFourLastQPeakCToTMismatchData = lapply(sixFourPeakCToTMismatchData, function(x) {
-  lapply(x, getLastPositionQuartile)
-})
-```
-
-```{r generate_frequency_data}
-CPDSingleCToTNucFreq = lapply(CPDSingleCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
-CPDFirstQPeakCToTNucFreq = lapply(CPDFirstQPeakCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
-CPDLastQPeakCToTNucFreq = lapply(CPDLastQPeakCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
-
-sixFourSingleCToTNucFreq = lapply(sixFourSingleCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
-sixFourFirstQPeakCToTNucFreq = lapply(sixFourFirstQPeakCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
-sixFourLastQPeakCToTNucFreq = lapply(sixFourLastQPeakCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
-```
-
-```{r purine_vs_pyrimidine_frequencies_across_read_length, fig.width = 11, fig.height = 5}
-plotNucFreqVsReadLengthBarPlot(CPDSingleCToTNucFreq$rep1, title = "CPD Rep1 3' Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(CPDSingleCToTNucFreq$rep2, title = "CPD Rep2 3' Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-
-plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTNucFreq$rep1, title = "6-4 Rep1 3' Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTNucFreq$rep2, title = "6-4 Rep2 3' Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-```
-
-```{r purine_vs_pyrimidine_frequencies_first_quartile_mismatch_pos, fig.width = 11, fig.height = 5}
-plotNucFreqVsReadLengthBarPlot(CPDFirstQPeakCToTNucFreq$rep1, title = "CPD Rep1 1st Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(CPDFirstQPeakCToTNucFreq$rep2, title = "CPD Rep2 1st Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-
-plotNucFreqVsReadLengthBarPlot(sixFourFirstQPeakCToTNucFreq$rep1, title = "6-4 Rep1 1st Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(sixFourFirstQPeakCToTNucFreq$rep2, title = "6-4 Rep2 1st Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-```
-
-```{r purine_vs_pyrimidine_frequencies_last_quartile_mismatch_pos, fig.width = 11, fig.height = 5}
-plotNucFreqVsReadLengthBarPlot(CPDLastQPeakCToTNucFreq$rep1, title = "CPD Rep1 4th Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(CPDLastQPeakCToTNucFreq$rep2, title = "CPD Rep2 4th Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-
-plotNucFreqVsReadLengthBarPlot(sixFourLastQPeakCToTNucFreq$rep1, title = "6-4 Rep1 4th Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(sixFourLastQPeakCToTNucFreq$rep2, title = "6-4 Rep2 4th Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-```
-
-# ```{r acquire_and_format_data_2}
-# # Read in the GC content vs. read length data
-# CPDReadLengthAndGCFilePaths = list(rep1 = list(), rep2 = list())
-# CPDReadLengthAndGCFilePaths$rep1 = list(
-#   hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep1_read_length_vs_GC_content.tsv"),
-#   hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep1_read_length_vs_GC_content.tsv"),
-#   hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep1_read_length_vs_GC_content.tsv"),
-#   hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep1_read_length_vs_GC_content.tsv")
-# )
-# CPDReadLengthAndGCFilePaths$rep2 = list(
-#   hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep2_read_length_vs_GC_content.tsv"),
-#   hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep2_read_length_vs_GC_content.tsv"),
-#   hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep2_read_length_vs_GC_content.tsv"),
-#   hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep2_read_length_vs_GC_content.tsv")
-# )
-# 
-# sixFourReadLengthAndGCFilePaths = list(rep1 = list(), rep2 = list())
-# sixFourReadLengthAndGCFilePaths$rep1 = list(
-#   min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep1_read_length_vs_GC_content.tsv"),
-#   min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep1_read_length_vs_GC_content.tsv"),
-#   hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep1_read_length_vs_GC_content.tsv")
-# )
-# sixFourReadLengthAndGCFilePaths$rep2 = list(
-#   min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep2_read_length_vs_GC_content.tsv"),
-#   min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep2_read_length_vs_GC_content.tsv"),
-#   hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep2_read_length_vs_GC_content.tsv")
-# )
-# 
-# CPDReadLengthAndGCData = lapply(CPDReadLengthAndGCFilePaths, function(x) lapply(x, fread))
-# sixFourReadLengthAndGCData = lapply(sixFourReadLengthAndGCFilePaths, function(x) lapply(x, fread))
-# ```
-
-# ```{r CPD_read_length_vs_GC_content}
-# for (i in 1:length(CPDReadLengthAndGCData)) {
-#   for (j in 1:length(CPDReadLengthAndGCData[[i]])) {
-#     plotGCContentVsReadLength(CPDReadLengthAndGCData[[i]][[j]],
-#                               title = paste("CPD", names(CPDReadLengthAndGCData)[i], 
-#                                             names(CPDReadLengthAndGCData[[i]])[j], "GC Content Vs Read Length"))
-#   }
-# }
-# ```
-# 
-# 
-# ```{r 6-4_read_length_vs_GC_content}
-# for (i in 1:length(sixFourReadLengthAndGCData)) {
-#   for (j in 1:length(sixFourReadLengthAndGCData[[i]])) {
-#     plotGCContentVsReadLength(sixFourReadLengthAndGCData[[i]][[j]],
-#                               title = paste("6-4", names(sixFourReadLengthAndGCData)[i], 
-#                                             names(sixFourReadLengthAndGCData[[i]])[j], "GC Content Vs Read Length"))
-#   }
-# }
-# ```
-
-```{r acquire_and_format_data_3}
 load(file.path(deaminationDataDirectory, "periodicity_results", "NHF1_deamination_periodicity_results.rda"))
@@
 
-```{r acquire_and_format_data_4}
+```{r acquire_and_format_data_2}
 load(file.path(deaminationDataDirectory, "periodicity_results", "NHF1_TCG_deamination_periodicity_results.rda"))

### 2022-05-03 R/HumanDeaminationPositioningAnalysis.rmd
Reorganized human deamination analyses
- Split the main deamination analysis notebook into three separate notebooks outlining different parts of the analysis: Initial validation and positional analysis, read length and cut site analysis, and periodicity analysis

- Any analyses that had been deemed extraneous were also cut out during this move. There are still present, commented out, in the original document, now named "HumanDeaminationAnalysis_DEPRECATED.rmd"

--- 2022-04-27 R/HumanDeaminationAnalysis.rmd
@@
 ---
-title: "R Notebook"
+title: "Human Deamination Positioning Analysis"
+author: "Ben Morledge-Hampton"
+date: "5/2/2022"
 output: html_document
@@
 source(file.path(bioinformaticsDirectory, "deamination_determination", 'R', "DeaminationAnalysis.R"))
-source(file.path(bioinformaticsDirectory, "Chromatin_Features_Analysis", "R_scripts", "PeriodicityAnalysis.R"))
 ```
 
-```{r acquire_and_format_data_1}
-# Read in the mismatch by read data
+```{r get_file_paths}
+# Get file paths for the mismatch by read data
 CPDMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
@@
 )
+```
 
+```{r acquire_and_format_data}
 CPDMismatchData = lapply(CPDMismatchDataFilePaths, function(x) lapply(x, fread))
 sixFourMismatchData = lapply(sixFourMismatchDataFilePaths, function(x) lapply(x, fread))
-
-# Create a subset of single mismatch C>T reads.
-CPDSingleCToTMismatchData = lapply(CPDMismatchData, function(x) lapply(
-  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = 23, maxReadLength = 31)
-))
-sixFourSingleCToTMismatchData = lapply(sixFourMismatchData, function(x) lapply(
-  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = 23, maxReadLength = 31)
-))
 
@@
 
-# # Get the tables of read length vs. GC content
-# CPDReadLengthVsGCData = lapply(CPDMismatchData, function(x) lapply(
-#   x, getReadLengthAndGCContent
-# ))
-# sixReadLengthVsGCData = lapply(sixFourMismatchData, function(x) lapply(
-#   x, getReadLengthAndGCContent
-# ))
-
-# # Extract and simplify tandem C>T mismatches
-# CPDTandemCTMismatches = lapply(CPDMismatchData, function(x) lapply(
-#   x, function(y) simplifyTable(getTandemCTMismatches(y))
-# ))
-# sixFourTandemCTMismatches = lapply(sixFourMismatchData, function(x) lapply(
-#   x, function(y) simplifyTable(getTandemCTMismatches(y))
-# ))
-
 # Simplify the data
 CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
-  x, function(y) simplifyTable(y)
+  x, function(y) simplifyTable(y, includeTrinucleotideContext = TRUE)
 ))
 sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
-  x, function(y) simplifyTable(y)
+  x, function(y) simplifyTable(y, includeTrinucleotideContext = TRUE)
 ))
-CPDSingleCToTMismatchData = lapply(CPDSingleCToTMismatchData, function(x) lapply(
-  x, function(y) simplifyTable(y, TRUE)
-))
-sixFourSingleCToTMismatchData = lapply(sixFourSingleCToTMismatchData, function(x) lapply(
-  x, function(y) simplifyTable(y, TRUE)
-))
-
 ```
@@
 }
-
 ```
@@
 }
-
 ```
 
-# ```{r CPD_tandem_C_to_T_pos_frequency}
-# for (i in 1:length(CPDTandemCTMismatches)) {
-#   for (j in 1:length(CPDTandemCTMismatches[[i]])) {
-#     plotMismatchPositionFrequencies(CPDTandemCTMismatches[[i]][[j]],
-#                                     title = paste("CPD", names(CPDTandemCTMismatches)[i], 
-#                                                   names(CPDTandemCTMismatches[[i]])[j], "Tandem C>T Mismatch Pos"))
-#   }
-# }
-# ```
+```{r CPD_trinucleotide_context_analysis}
+for (i in 1:length(CPDMismatchData)) {
+  for (j in 1:length(CPDMismatchData[[i]])) {
+    plotTrinucleotideContext(CPDMismatchData[[i]][[j]], includedTypes = c("C>T"),
+                             title = paste("CPD", names(CPDMismatchData)[i], names(CPDMismatchData[[i]])[j],
+                                           "C>T Mismatch Trinuc Context"))
+  }
+}
+```
 
-# ```{r 6-4_tandem_C_to_T_pos_frequency}
-# for (i in 1:length(sixFourTandemCTMismatches)) {
-#   for (j in 1:length(sixFourTandemCTMismatches[[i]])) {
-#     plotMismatchPositionFrequencies(sixFourTandemCTMismatches[[i]][[j]],
-#                                     title = paste("6-4", names(sixFourTandemCTMismatches)[i], 
-#                                                   names(sixFourTandemCTMismatches[[i]])[j], 
-#                                                   "Tandem C>T Mismatch Pos"))
-#   }
-# }
-# ```
+```{r 6-4_trinucleotide_context_analysis}
+for (i in 1:length(sixFourMismatchData)) {
+  for (j in 1:length(sixFourMismatchData[[i]])) {
+    plotTrinucleotideContext(sixFourMismatchData[[i]][[j]], includedTypes = c("C>T"),
+                             title = paste("6-4", names(sixFourMismatchData)[i], names(sixFourMismatchData[[i]])[j],
+                                           "C>T Mismatch Trinuc Context"))
+  }
+}
+```
 
@@
 ```
-
-# ```{r plot_stats_across_read_lengths, fig.width = 9, fig.height = 5}
-# plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, IQR,
-#                          title = "CPD C>T Mismatch Pos Diff Rep1",
-#                          xAxisBreaks = c(23:31))
-# plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, IQR,
-#                          title = "CPD C>T Mismatch Pos Diff Rep2",
-#                          xAxisBreaks = c(23:31))
-# 
-# plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, IQR,
-#                          title = "6-4 C>T Mismatch Pos Diff Rep1",
-#                          xAxisBreaks = c(23:31))
-# plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, IQR,
-#                          title = "6-4 C>T Mismatch Pos Diff Rep2",
-#                          xAxisBreaks = c(23:31))
-# ```
-
-```{r filter_by_mismatch_pos_and_read_length}
-CPDPeakCToTMismatchData = lapply(CPDSingleCToTMismatchData, function(x) {
-  lapply(x, filterMismatchesByPositionAndReadLength, HUMAN_THREE_PRIME_POS_CONSTRAINTS)
-})
-CPDFirstQPeakCToTMismatchData = lapply(CPDPeakCToTMismatchData, function(x) {
-  lapply(x, getFirstPositionQuartile)
-})
-CPDLastQPeakCToTMismatchData = lapply(CPDPeakCToTMismatchData, function(x) {
-  lapply(x, getLastPositionQuartile)
-})
-
-sixFourPeakCToTMismatchData = lapply(sixFourSingleCToTMismatchData, function(x) {
-  lapply(x, filterMismatchesByPositionAndReadLength, HUMAN_THREE_PRIME_POS_CONSTRAINTS)
-})
-sixFourFirstQPeakCToTMismatchData = lapply(sixFourPeakCToTMismatchData, function(x) {
-  lapply(x, getFirstPositionQuartile)
-})
-sixFourLastQPeakCToTMismatchData = lapply(sixFourPeakCToTMismatchData, function(x) {
-  lapply(x, getLastPositionQuartile)
-})
-```
-
-```{r generate_frequency_data}
-CPDSingleCToTNucFreq = lapply(CPDSingleCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
-CPDFirstQPeakCToTNucFreq = lapply(CPDFirstQPeakCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
-CPDLastQPeakCToTNucFreq = lapply(CPDLastQPeakCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
-
-sixFourSingleCToTNucFreq = lapply(sixFourSingleCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
-sixFourFirstQPeakCToTNucFreq = lapply(sixFourFirstQPeakCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
-sixFourLastQPeakCToTNucFreq = lapply(sixFourLastQPeakCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
-```
-
-```{r purine_vs_pyrimidine_frequencies_across_read_length, fig.width = 11, fig.height = 5}
-plotNucFreqVsReadLengthBarPlot(CPDSingleCToTNucFreq$rep1, title = "CPD Rep1 3' Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(CPDSingleCToTNucFreq$rep2, title = "CPD Rep2 3' Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-
-plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTNucFreq$rep1, title = "6-4 Rep1 3' Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTNucFreq$rep2, title = "6-4 Rep2 3' Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-```
-
-```{r purine_vs_pyrimidine_frequencies_first_quartile_mismatch_pos, fig.width = 11, fig.height = 5}
-plotNucFreqVsReadLengthBarPlot(CPDFirstQPeakCToTNucFreq$rep1, title = "CPD Rep1 1st Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(CPDFirstQPeakCToTNucFreq$rep2, title = "CPD Rep2 1st Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-
-plotNucFreqVsReadLengthBarPlot(sixFourFirstQPeakCToTNucFreq$rep1, title = "6-4 Rep1 1st Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(sixFourFirstQPeakCToTNucFreq$rep2, title = "6-4 Rep2 1st Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-```
-
-```{r purine_vs_pyrimidine_frequencies_last_quartile_mismatch_pos, fig.width = 11, fig.height = 5}
-plotNucFreqVsReadLengthBarPlot(CPDLastQPeakCToTNucFreq$rep1, title = "CPD Rep1 4th Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(CPDLastQPeakCToTNucFreq$rep2, title = "CPD Rep2 4th Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-
-plotNucFreqVsReadLengthBarPlot(sixFourLastQPeakCToTNucFreq$rep1, title = "6-4 Rep1 4th Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(sixFourLastQPeakCToTNucFreq$rep2, title = "6-4 Rep2 4th Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-```
-
-# ```{r acquire_and_format_data_2}
-# # Read in the GC content vs. read length data
-# CPDReadLengthAndGCFilePaths = list(rep1 = list(), rep2 = list())
-# CPDReadLengthAndGCFilePaths$rep1 = list(
-#   hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep1_read_length_vs_GC_content.tsv"),
-#   hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep1_read_length_vs_GC_content.tsv"),
-#   hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep1_read_length_vs_GC_content.tsv"),
-#   hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep1_read_length_vs_GC_content.tsv")
-# )
-# CPDReadLengthAndGCFilePaths$rep2 = list(
-#   hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep2_read_length_vs_GC_content.tsv"),
-#   hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep2_read_length_vs_GC_content.tsv"),
-#   hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep2_read_length_vs_GC_content.tsv"),
-#   hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep2_read_length_vs_GC_content.tsv")
-# )
-# 
-# sixFourReadLengthAndGCFilePaths = list(rep1 = list(), rep2 = list())
-# sixFourReadLengthAndGCFilePaths$rep1 = list(
-#   min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep1_read_length_vs_GC_content.tsv"),
-#   min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep1_read_length_vs_GC_content.tsv"),
-#   hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep1_read_length_vs_GC_content.tsv")
-# )
-# sixFourReadLengthAndGCFilePaths$rep2 = list(
-#   min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep2_read_length_vs_GC_content.tsv"),
-#   min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep2_read_length_vs_GC_content.tsv"),
-#   hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep2_read_length_vs_GC_content.tsv")
-# )
-# 
-# CPDReadLengthAndGCData = lapply(CPDReadLengthAndGCFilePaths, function(x) lapply(x, fread))
-# sixFourReadLengthAndGCData = lapply(sixFourReadLengthAndGCFilePaths, function(x) lapply(x, fread))
-# ```
-
-# ```{r CPD_read_length_vs_GC_content}
-# for (i in 1:length(CPDReadLengthAndGCData)) {
-#   for (j in 1:length(CPDReadLengthAndGCData[[i]])) {
-#     plotGCContentVsReadLength(CPDReadLengthAndGCData[[i]][[j]],
-#                               title = paste("CPD", names(CPDReadLengthAndGCData)[i], 
-#                                             names(CPDReadLengthAndGCData[[i]])[j], "GC Content Vs Read Length"))
-#   }
-# }
-# ```
-# 
-# 
-# ```{r 6-4_read_length_vs_GC_content}
-# for (i in 1:length(sixFourReadLengthAndGCData)) {
-#   for (j in 1:length(sixFourReadLengthAndGCData[[i]])) {
-#     plotGCContentVsReadLength(sixFourReadLengthAndGCData[[i]][[j]],
-#                               title = paste("6-4", names(sixFourReadLengthAndGCData)[i], 
-#                                             names(sixFourReadLengthAndGCData[[i]])[j], "GC Content Vs Read Length"))
-#   }
-# }
-# ```
-
-```{r acquire_and_format_data_3}
-load(file.path(deaminationDataDirectory, "periodicity_results", "NHF1_deamination_periodicity_results.rda"))
-dataSetNames = as.list(setNames(nm = mutperiodData$periodicityResults$Data_Set))
-```
-
-```{r CPD_rotational_periodicity_trinuc_normalized}
-parseAndPlotPeriodicity(dataSetNames$NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
-                        title = "CPD 1hr Rep1 Rotational Trinuc Norm")
-parseAndPlotPeriodicity(dataSetNames$NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
-                        title = "CPD 24hr Rep1 Rotational Trinuc Norm")
-parseAndPlotPeriodicity(dataSetNames$NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
-                        title = "CPD 48hr Rep1 Rotational Trinuc Norm")
-```
-
-```{r CPD_rotational_periodicity_XR-seq_normalized}
-parseAndPlotPeriodicity(
-  dataSetNames$NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
-  title = "CPD 1hr Rep1 Rotational XR-seq Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
-  title = "CPD 24hr Rep1 Rotational XR-seq Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
-  title = "CPD 48hr Rep1 Rotational XR-seq Norm")
-```
-
-```{r CPD_translational_periodicity_trinuc_normalized}
-parseAndPlotPeriodicity(
-  dataSetNames$`NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
-  title = "CPD 1hr Rep1 Rotational Trinuc Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$`NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
-  title = "CPD 24hr Rep1 Rotational Trinuc Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$`NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
-  title = "CPD 48hr Rep1 Rotational Trinuc Norm")
-```
-
-```{r CPD_translational_periodicity_XR-seq_normalized}
-parseAndPlotPeriodicity(
-  dataSetNames$`NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
-  title = "CPD 1hr Rep1 Rotational XR-seq Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$`NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
-  title = "CPD 24hr Rep1 Rotational XR-seq Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$`NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
-  title = "CPD 48hr Rep1 Rotational XR-seq Norm")
-```
-
-```{r acquire_and_format_data_4}
-load(file.path(deaminationDataDirectory, "periodicity_results", "NHF1_TCG_deamination_periodicity_results.rda"))
-dataSetNames = as.list(setNames(nm = mutperiodData$periodicityResults$Data_Set))
-
-```
-
-```{r TCG_CPD_rotational_periodicity_trinuc_normalized}
-parseAndPlotPeriodicity(
-  dataSetNames$TCG_NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
-  title = "TCG CPD 1hr Rep1 Rotational Trinuc Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$TCG_NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
-  title = "TCG CPD 24hr Rep1 Rotational Trinuc Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$TCG_NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
-  title = "TCG CPD 48hr Rep1 Rotational Trinuc Norm")
-```
-
-```{r TCG_CPD_rotational_periodicity_XR-seq_normalized}
-parseAndPlotPeriodicity(
-  dataSetNames$TCG_NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
-  title = "TCG CPD 1hr Rep1 Rotational XR-seq Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$TCG_NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
-  title = "TCG CPD 24hr Rep1 Rotational XR-seq Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$TCG_NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
-  title = "TCG CPD 48hr Rep1 Rotational XR-seq Norm")
-```
-
-```{r TCG_CPD_translational_periodicity_trinuc_normalized}
-parseAndPlotPeriodicity(
-  dataSetNames$`TCG_NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
-  title = "TCG CPD 1hr Rep1 Rotational Trinuc Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$`TCG_NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
-  title = "TCG CPD 24hr Rep1 Rotational Trinuc Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$`TCG_NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
-  title = "TCG CPD 48hr Rep1 Rotational Trinuc Norm")
-```
-
-```{r TCG_CPD_translational_periodicity_XR-seq_normalized}
-parseAndPlotPeriodicity(
-  dataSetNames$`TCG_NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
-  title = "TCG_CPD 1hr Rep1 Rotational XR-seq Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$`TCG_NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
-  title = "TCG CPD 24hr Rep1 Rotational XR-seq Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$`TCG_NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
-  title = "TCG CPD 48hr Rep1 Rotational XR-seq Norm")
-```

### 2022-05-03 R/HumanDeaminationReadLengthAnalysis.rmd
Reorganized human deamination analyses
- Split the main deamination analysis notebook into three separate notebooks outlining different parts of the analysis: Initial validation and positional analysis, read length and cut site analysis, and periodicity analysis

- Any analyses that had been deemed extraneous were also cut out during this move. There are still present, commented out, in the original document, now named "HumanDeaminationAnalysis_DEPRECATED.rmd"

--- 2022-04-27 R/HumanDeaminationAnalysis.rmd
@@
 ---
-title: "R Notebook"
+title: "Human Deamination Read Length Analysis"
+author: "Ben Morledge-Hampton"
+date: "5/2/2022"
 output: html_document
@@
 )
+```
 
+```{r acquire_and_format_data}
 CPDMismatchData = lapply(CPDMismatchDataFilePaths, function(x) lapply(x, fread))
@@
 
-# Perform general filtering on the data
-CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
-  x, function(y) filterResults(y, TRUE, 3, 23, 31)
-))
-sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
-  x, function(y) filterResults(y, TRUE, 3, 23, 31)
-))
-
-# # Get the tables of read length vs. GC content
-# CPDReadLengthVsGCData = lapply(CPDMismatchData, function(x) lapply(
-#   x, getReadLengthAndGCContent
-# ))
-# sixReadLengthVsGCData = lapply(sixFourMismatchData, function(x) lapply(
-#   x, getReadLengthAndGCContent
-# ))
-
-# # Extract and simplify tandem C>T mismatches
-# CPDTandemCTMismatches = lapply(CPDMismatchData, function(x) lapply(
-#   x, function(y) simplifyTable(getTandemCTMismatches(y))
-# ))
-# sixFourTandemCTMismatches = lapply(sixFourMismatchData, function(x) lapply(
-#   x, function(y) simplifyTable(getTandemCTMismatches(y))
-# ))
-
 # Simplify the data
-CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
-  x, function(y) simplifyTable(y)
-))
-sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
-  x, function(y) simplifyTable(y)
-))
 CPDSingleCToTMismatchData = lapply(CPDSingleCToTMismatchData, function(x) lapply(
@@
 ```
-
-```{r CPD_mismatch_type_frequency}
-for (i in 1:length(CPDMismatchData)) {
-  for (j in 1:length(CPDMismatchData[[i]])) {
-    plotMismatchTypeFrequencies(CPDMismatchData[[i]][[j]],
-                                title = paste("CPD", names(CPDMismatchData)[i], 
-                                              names(CPDMismatchData[[i]])[j], "Mismatch Type Frequency"))
-  }
-}
-```
-
-```{r 6-4_mismatch_type_frequency}
-for (i in 1:length(sixFourMismatchData)) {
-  for (j in 1:length(sixFourMismatchData[[i]])) {
-    plotMismatchTypeFrequencies(sixFourMismatchData[[i]][[j]],
-                                title = paste("6-4", names(sixFourMismatchData)[i], 
-                                              names(sixFourMismatchData[[i]])[j], "Mismatch Type Frequency"))
-  }
-}
-
-```
-
-```{r CPD_mismatch_pos_frequency}
-for (i in 1:length(CPDMismatchData)) {
-  for (j in 1:length(CPDMismatchData[[i]])) {
-    plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], includedTypes = c("C>T"),
-                                    title = paste("CPD", names(CPDMismatchData)[i], 
-                                                  names(CPDMismatchData[[i]])[j], "C>T Mismatch Positions"))
-    plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], omittedTypes = c("C>T"),
-                                    title = paste("CPD", names(CPDMismatchData)[i], 
-                                                  names(CPDMismatchData[[i]])[j], "!C>T Mismatch Positions"))
-  }
-}
-```
-
-```{r 6-4_mismatch_pos_frequency}
-for (i in 1:length(sixFourMismatchData)) {
-  for (j in 1:length(sixFourMismatchData[[i]])) {
-    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], includedTypes = c("C>T"),
-                                    title = paste("6-4", names(sixFourMismatchData)[i], 
-                                                  names(sixFourMismatchData[[i]])[j], "C>T Mismatch Positions"))
-    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], includedTypes = c("C>T"),
-                                    title = paste("6-4", names(sixFourMismatchData)[i], 
-                                                  names(sixFourMismatchData[[i]])[j], "C>T Mismatch Positions"),
-                                    posType = FIVE_PRIME)
-
-    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], omittedTypes = c("C>T"),
-                                    title = paste("6-4", names(sixFourMismatchData)[i], 
-                                                  names(sixFourMismatchData[[i]])[j], "!C>T Mismatch Positions"))
-  }
-}
-
-```
-
-# ```{r CPD_tandem_C_to_T_pos_frequency}
-# for (i in 1:length(CPDTandemCTMismatches)) {
-#   for (j in 1:length(CPDTandemCTMismatches[[i]])) {
-#     plotMismatchPositionFrequencies(CPDTandemCTMismatches[[i]][[j]],
-#                                     title = paste("CPD", names(CPDTandemCTMismatches)[i], 
-#                                                   names(CPDTandemCTMismatches[[i]])[j], "Tandem C>T Mismatch Pos"))
-#   }
-# }
-# ```
-
-# ```{r 6-4_tandem_C_to_T_pos_frequency}
-# for (i in 1:length(sixFourTandemCTMismatches)) {
-#   for (j in 1:length(sixFourTandemCTMismatches[[i]])) {
-#     plotMismatchPositionFrequencies(sixFourTandemCTMismatches[[i]][[j]],
-#                                     title = paste("6-4", names(sixFourTandemCTMismatches)[i], 
-#                                                   names(sixFourTandemCTMismatches[[i]])[j], 
-#                                                   "Tandem C>T Mismatch Pos"))
-#   }
-# }
-# ```
-
-```{r facet_mismatch_position_frequencies, fig.width = 9, fig.height = 5}
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, includedTypes = c("C>T"),
-                                         title = "CPD C>T Mismatch Pos Freq Rep1")
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, includedTypes = c("C>T"),
-                                         title = "CPD C>T Mismatch Pos Freq Rep2")
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, includedTypes = c("C>T"),
-                                         title = "CPD C>T Mismatch Pos Freq Rep1", posType = FIVE_PRIME)
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, includedTypes = c("C>T"),
-                                         title = "CPD C>T Mismatch Pos Freq Rep2", posType = FIVE_PRIME)
-
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, includedTypes = c("C>T"),
-                                         title = "6-4 C>T Mismatch Pos Freq Rep1")
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, includedTypes = c("C>T"),
-                                         title = "6-4 C>T Mismatch Pos Freq Rep2")
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, includedTypes = c("C>T"),
-                                         title = "6-4 C>T Mismatch Pos Freq Rep1", posType = FIVE_PRIME)
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, includedTypes = c("C>T"),
-                                         title = "6-4 C>T Mismatch Pos Freq Rep2", posType = FIVE_PRIME)
-```
-
-```{r facet_mismatch_position_statistics}
-CPDGroupedStats = list(rep1 = list(), rep2 = list())
-CPDGroupedStats$rep1$three_prime = getGroupedPositionStats(CPDMismatchData$rep1, includedTypes = c("C>T"))
-CPDGroupedStats$rep2$three_prime = getGroupedPositionStats(CPDMismatchData$rep2, includedTypes = c("C>T"))
-CPDGroupedStats$rep1$five_prime =
-  getGroupedPositionStats(CPDMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME)
-CPDGroupedStats$rep2$five_prime =
-  getGroupedPositionStats(CPDMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME)
-
-sixFourGroupedStats = list(rep1 = list(), rep2 = list())
-sixFourGroupedStats$rep1$three_prime = getGroupedPositionStats(sixFourMismatchData$rep1, includedTypes = c("C>T"))
-sixFourGroupedStats$rep2$three_prime = getGroupedPositionStats(sixFourMismatchData$rep2, includedTypes = c("C>T"))
-sixFourGroupedStats$rep1$five_prime =
-  getGroupedPositionStats(sixFourMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME)
-sixFourGroupedStats$rep2$five_prime =
-  getGroupedPositionStats(sixFourMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME)
-
-tableOutputDir = file.path("deamination_analysis_output","human_analysis_tables")
-dir.create(tableOutputDir, recursive = TRUE)
-
-fwrite(CPDGroupedStats$rep1$three_prime,
-       file.path(tableOutputDir, "CPD_mismatch_three_prime_position_stats_rep1.tsv"),sep = '\t')
-fwrite(CPDGroupedStats$rep2$three_prime,
-       file.path(tableOutputDir, "CPD_mismatch_three_prime_position_stats_rep2.tsv"),sep = '\t')
-fwrite(CPDGroupedStats$rep1$five_prime,
-       file.path(tableOutputDir, "CPD_mismatch_five_prime_position_stats_rep1.tsv"),sep = '\t')
-fwrite(CPDGroupedStats$rep2$five_prime,
-       file.path(tableOutputDir, "CPD_mismatch_five_prime_position_stats_rep2.tsv"),sep = '\t')
-
-fwrite(sixFourGroupedStats$rep1$three_prime,
-       file.path(tableOutputDir, "6-4_mismatch_three_prime_position_stats_rep1.tsv"), sep = '\t')
-fwrite(sixFourGroupedStats$rep2$three_prime,
-       file.path(tableOutputDir, "6-4_mismatch_three_prime_position_stats_rep2.tsv"), sep = '\t')
-fwrite(sixFourGroupedStats$rep1$five_prime,
-       file.path(tableOutputDir, "6-4_mismatch_five_prime_position_stats_rep1.tsv"), sep = '\t')
-fwrite(sixFourGroupedStats$rep2$five_prime,
-       file.path(tableOutputDir, "6-4_mismatch_five_prime_position_stats_rep2.tsv"), sep = '\t')
-```
-
-```{r position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
-plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, POS_DIFF,
-                         title = "CPD C>T Mismatch Pos Diff Rep1",
-                         xAxisBreaks = c(23:31))
-plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, POS_DIFF,
-                         title = "CPD C>T Mismatch Pos Diff Rep2",
-                         xAxisBreaks = c(23:31))
-
-plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, POS_DIFF,
-                         title = "6-4 C>T Mismatch Pos Diff Rep1",
-                         xAxisBreaks = c(23:31))
-plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, POS_DIFF,
-                         title = "6-4 C>T Mismatch Pos Diff Rep2",
-                         xAxisBreaks = c(23:31))
-```
-
-# ```{r plot_stats_across_read_lengths, fig.width = 9, fig.height = 5}
-# plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, IQR,
-#                          title = "CPD C>T Mismatch Pos Diff Rep1",
-#                          xAxisBreaks = c(23:31))
-# plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, IQR,
-#                          title = "CPD C>T Mismatch Pos Diff Rep2",
-#                          xAxisBreaks = c(23:31))
-# 
-# plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, IQR,
-#                          title = "6-4 C>T Mismatch Pos Diff Rep1",
-#                          xAxisBreaks = c(23:31))
-# plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, IQR,
-#                          title = "6-4 C>T Mismatch Pos Diff Rep2",
-#                          xAxisBreaks = c(23:31))
-# ```
 
@@
 
-```{r generate_frequency_data}
+```{r generate_nucleotide_frequency_data}
 CPDSingleCToTNucFreq = lapply(CPDSingleCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
@@
 ```
-
-# ```{r acquire_and_format_data_2}
-# # Read in the GC content vs. read length data
-# CPDReadLengthAndGCFilePaths = list(rep1 = list(), rep2 = list())
-# CPDReadLengthAndGCFilePaths$rep1 = list(
-#   hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep1_read_length_vs_GC_content.tsv"),
-#   hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep1_read_length_vs_GC_content.tsv"),
-#   hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep1_read_length_vs_GC_content.tsv"),
-#   hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep1_read_length_vs_GC_content.tsv")
-# )
-# CPDReadLengthAndGCFilePaths$rep2 = list(
-#   hr1 = file.path(deaminationDataDirectory, "NHF1_CPD_1h_Rep2_read_length_vs_GC_content.tsv"),
-#   hr8 = file.path(deaminationDataDirectory, "NHF1_CPD_8h_Rep2_read_length_vs_GC_content.tsv"),
-#   hr24 = file.path(deaminationDataDirectory, "NHF1_CPD_24h_Rep2_read_length_vs_GC_content.tsv"),
-#   hr48 = file.path(deaminationDataDirectory, "NHF1_CPD_48h_Rep2_read_length_vs_GC_content.tsv")
-# )
-# 
-# sixFourReadLengthAndGCFilePaths = list(rep1 = list(), rep2 = list())
-# sixFourReadLengthAndGCFilePaths$rep1 = list(
-#   min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep1_read_length_vs_GC_content.tsv"),
-#   min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep1_read_length_vs_GC_content.tsv"),
-#   hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep1_read_length_vs_GC_content.tsv")
-# )
-# sixFourReadLengthAndGCFilePaths$rep2 = list(
-#   min5 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_5min_Rep2_read_length_vs_GC_content.tsv"),
-#   min20 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_20min_Rep2_read_length_vs_GC_content.tsv"),
-#   hr1 = file.path(deaminationDataDirectory, "NHF1_6-4-PP_1h_Rep2_read_length_vs_GC_content.tsv")
-# )
-# 
-# CPDReadLengthAndGCData = lapply(CPDReadLengthAndGCFilePaths, function(x) lapply(x, fread))
-# sixFourReadLengthAndGCData = lapply(sixFourReadLengthAndGCFilePaths, function(x) lapply(x, fread))
-# ```
-
-# ```{r CPD_read_length_vs_GC_content}
-# for (i in 1:length(CPDReadLengthAndGCData)) {
-#   for (j in 1:length(CPDReadLengthAndGCData[[i]])) {
-#     plotGCContentVsReadLength(CPDReadLengthAndGCData[[i]][[j]],
-#                               title = paste("CPD", names(CPDReadLengthAndGCData)[i], 
-#                                             names(CPDReadLengthAndGCData[[i]])[j], "GC Content Vs Read Length"))
-#   }
-# }
-# ```
-# 
-# 
-# ```{r 6-4_read_length_vs_GC_content}
-# for (i in 1:length(sixFourReadLengthAndGCData)) {
-#   for (j in 1:length(sixFourReadLengthAndGCData[[i]])) {
-#     plotGCContentVsReadLength(sixFourReadLengthAndGCData[[i]][[j]],
-#                               title = paste("6-4", names(sixFourReadLengthAndGCData)[i], 
-#                                             names(sixFourReadLengthAndGCData[[i]])[j], "GC Content Vs Read Length"))
-#   }
-# }
-# ```
-
-```{r acquire_and_format_data_3}
-load(file.path(deaminationDataDirectory, "periodicity_results", "NHF1_deamination_periodicity_results.rda"))
-dataSetNames = as.list(setNames(nm = mutperiodData$periodicityResults$Data_Set))
-```
-
-```{r CPD_rotational_periodicity_trinuc_normalized}
-parseAndPlotPeriodicity(dataSetNames$NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
-                        title = "CPD 1hr Rep1 Rotational Trinuc Norm")
-parseAndPlotPeriodicity(dataSetNames$NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
-                        title = "CPD 24hr Rep1 Rotational Trinuc Norm")
-parseAndPlotPeriodicity(dataSetNames$NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
-                        title = "CPD 48hr Rep1 Rotational Trinuc Norm")
-```
-
-```{r CPD_rotational_periodicity_XR-seq_normalized}
-parseAndPlotPeriodicity(
-  dataSetNames$NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
-  title = "CPD 1hr Rep1 Rotational XR-seq Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
-  title = "CPD 24hr Rep1 Rotational XR-seq Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
-  title = "CPD 48hr Rep1 Rotational XR-seq Norm")
-```
-
-```{r CPD_translational_periodicity_trinuc_normalized}
-parseAndPlotPeriodicity(
-  dataSetNames$`NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
-  title = "CPD 1hr Rep1 Rotational Trinuc Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$`NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
-  title = "CPD 24hr Rep1 Rotational Trinuc Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$`NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
-  title = "CPD 48hr Rep1 Rotational Trinuc Norm")
-```
-
-```{r CPD_translational_periodicity_XR-seq_normalized}
-parseAndPlotPeriodicity(
-  dataSetNames$`NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
-  title = "CPD 1hr Rep1 Rotational XR-seq Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$`NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
-  title = "CPD 24hr Rep1 Rotational XR-seq Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$`NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
-  title = "CPD 48hr Rep1 Rotational XR-seq Norm")
-```
-
-```{r acquire_and_format_data_4}
-load(file.path(deaminationDataDirectory, "periodicity_results", "NHF1_TCG_deamination_periodicity_results.rda"))
-dataSetNames = as.list(setNames(nm = mutperiodData$periodicityResults$Data_Set))
-
-```
-
-```{r TCG_CPD_rotational_periodicity_trinuc_normalized}
-parseAndPlotPeriodicity(
-  dataSetNames$TCG_NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
-  title = "TCG CPD 1hr Rep1 Rotational Trinuc Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$TCG_NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
-  title = "TCG CPD 24hr Rep1 Rotational Trinuc Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$TCG_NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_normalized,
-  title = "TCG CPD 48hr Rep1 Rotational Trinuc Norm")
-```
-
-```{r TCG_CPD_rotational_periodicity_XR-seq_normalized}
-parseAndPlotPeriodicity(
-  dataSetNames$TCG_NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
-  title = "TCG CPD 1hr Rep1 Rotational XR-seq Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$TCG_NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
-  title = "TCG CPD 24hr Rep1 Rotational XR-seq Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$TCG_NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_normalized,
-  title = "TCG CPD 48hr Rep1 Rotational XR-seq Norm")
-```
-
-```{r TCG_CPD_translational_periodicity_trinuc_normalized}
-parseAndPlotPeriodicity(
-  dataSetNames$`TCG_NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
-  title = "TCG CPD 1hr Rep1 Rotational Trinuc Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$`TCG_NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
-  title = "TCG CPD 24hr Rep1 Rotational Trinuc Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$`TCG_NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_trinuc_nuc-group_normalized`,
-  title = "TCG CPD 48hr Rep1 Rotational Trinuc Norm")
-```
-
-```{r TCG_CPD_translational_periodicity_XR-seq_normalized}
-parseAndPlotPeriodicity(
-  dataSetNames$`TCG_NHF1_CPD_1h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
-  title = "TCG_CPD 1hr Rep1 Rotational XR-seq Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$`TCG_NHF1_CPD_24h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
-  title = "TCG CPD 24hr Rep1 Rotational XR-seq Norm")
-parseAndPlotPeriodicity(
-  dataSetNames$`TCG_NHF1_CPD_48h_Rep1_individual_mismatches_MNase_map_intergenic_custom_context_nuc-group_normalized`,
-  title = "TCG CPD 48hr Rep1 Rotational XR-seq Norm")
-```

### 2022-05-03 R/DeaminationAnalysis.R
Trinucleotide context deriving and plotting
- Added a parameter to the simplifyTable function which adds a column to the output table containing trinucleotide context of the reference sequence.
- Also fixed a bug where read sequence would not be accurate for reads with multiple mismatches.
- Added function for plotting trinucleotide context.

@@ -44,12 +44,23 @@ filterResults = function(mismatchData, removeRowsWithN = TRUE, maxMismatchesAllo
 # three-column table of positions, sequence context, and read length.
 # NOTE: The Read_Length field is only accurate in the absence of indels. Otherwise, it only represents
 #       the length of the aligned region in the reference genome.
-simplifyTable = function(table, includeReadSequence = FALSE) {
+simplifyTable = function(table, includeReadSequence = FALSE, includeTrinucleotideContext = FALSE) {
 
   returnTable = table[,list(Position = as.numeric(unlist(strsplit(V4, ':'))),
                             Mismatch = unlist(strsplit(V5, ':')),
                             Read_Length = unlist(mapply(rep, V3-V2, lapply(strsplit(V5,':'), length))))]
-  if (includeReadSequence) returnTable[, Read_Sequence := table$V7]
+
+  if (includeReadSequence || includeTrinucleotideContext) {
+    returnTable[, Read_Sequence := unlist(mapply(rep, table$V7, lapply(strsplit(table$V5,':'), length)))]
+  }
+
+  if (includeTrinucleotideContext) {
+    returnTable[abs(Position) > 1 & abs(Position) < Read_Length,
+                Trinuc_Context := paste0(str_sub(Read_Sequence, Position - 1, Position - 1),
+                                         str_sub(Mismatch, 1, 1),
+                                         str_sub(Read_Sequence, Position + 1, Position + 1))]
+    if (!includeReadSequence) returnTable[, Read_Sequence := NULL]
+  }
 
   return(returnTable)
 
@@ -319,6 +330,33 @@ plotGroupedPositionStats = function(threePrimeGroupedStats, fivePrimeGroupedStat
     scale_x_continuous(breaks = xAxisBreaks)
 
   print(groupedStatsPlot)
+
+}
+
+
+# Plots the trinucleotide context for a set of mismatches
+plotTrinucleotideContext = function(simplifiedMismatchTable, includedTypes = list(), omittedTypes = list(),
+                                    title = "Trinucleotide Context") {
+
+  if ( length(includedTypes) > 0 && length(omittedTypes) > 0) {
+    stop("Included types and omitted types given simultaneously")
+  } else if (length(includedTypes) > 0) {
+    simplifiedMismatchTable = simplifiedMismatchTable[Mismatch %in% includedTypes]
[…]

### 2022-05-06 R/DeaminationAnalysis.R
Accommodations for expanded sequence context
- Several functions have had an "expansionOffset" parameter added to them to adjust for additional sequence context that has shifted the position of the mismatch in the read sequence.
- The simplifyTable function now uses the number of nucleotides in the read sequence to determine read length. This actually makes it more robust to indels in the absence of expanded context.
- Added a function for orienting data so that the mismatch position is on the 5' or 3' border of the read sequence.
- Adapted nucleotide frequency plotting to display the cut site

@@ -41,14 +41,22 @@ filterResults = function(mismatchData, removeRowsWithN = TRUE, maxMismatchesAllo
 
 
 # Simplifies the given table of bed formatted mismatches into a smaller
-# three-column table of positions, sequence context, and read length.
-# NOTE: The Read_Length field is only accurate in the absence of indels. Otherwise, it only represents
-#       the length of the aligned region in the reference genome.
-simplifyTable = function(table, includeReadSequence = FALSE, includeTrinucleotideContext = FALSE) {
+# three-column table of positions, sequence context, and read length and optionally,
+# read sequence and trinuc context.
+# The expansionOffset parameter is used to change the Position and Read_Length values
+# relative to the number of expanded bases for the read. As a result, Read_Length should still reflect the
+# original read length, but Position will change to reflect the mismatch's position in the new sequence
+# NOTE: In the event that the read contains expanded sequence context information, that information
+#       no longer reflects the read sequence and instead reflects an expansion of the corresponding reference
+#       genome sequence. This also means that if the read sequence contained any indels, the Read_Length field will
+#       be inaccurate and the Position field MAY be inaccurate, even with the expansionOffset parameter.
+simplifyTable = function(table, includeReadSequence = FALSE, includeTrinucleotideContext = FALSE,
+                         expansionOffset = 0) {
 
-  returnTable = table[,list(Position = as.numeric(unlist(strsplit(V4, ':'))),
+  returnTable = table[,list(Position = as.numeric(unlist(strsplit(V4, ':'))) - expansionOffset,
                             Mismatch = unlist(strsplit(V5, ':')),
-                            Read_Length = unlist(mapply(rep, V3-V2, lapply(strsplit(V5,':'), length))))]
+                            Read_Length = unlist(mapply(rep, nchar(V7)-2*expansionOffset,
+                                                        lapply(strsplit(V5,':'), length))))]
 
   if (includeReadSequence || includeTrinucleotideContext) {
     returnTable[, Read_Sequence := unlist(mapply(rep, table$V7, lapply(strsplit(table$V5,':'), length)))]
@@ -68,12 +76,12 @@ simplifyTable = function(table, includeReadSequence = FALSE, includeTrinucleotid
 
 
[…]

### 2022-05-06 R/HumanDeaminationReadLengthAnalysis.rmd
Update HumanDeaminationReadLengthAnalysis.rmd

@@
 
-```{r get_file_paths}
+```{r get_file_paths_1}
 # Get file paths for the mismatch by read data
@@
 
-```{r acquire_and_format_data}
+```{r acquire_and_format_data_1}
 CPDMismatchData = lapply(CPDMismatchDataFilePaths, function(x) lapply(x, fread))
@@
 
-```{r filter_by_mismatch_pos_and_read_length}
+```{r filter_by_mismatch_pos_and_read_length_1}
 CPDPeakCToTMismatchData = lapply(CPDSingleCToTMismatchData, function(x) {
@@
 
-```{r generate_nucleotide_frequency_data}
+```{r generate_nucleotide_frequency_data_1}
 CPDSingleCToTNucFreq = lapply(CPDSingleCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
@@
 ```
+
+```{r get_file_paths_2}
+# Get file paths for the expanded mismatch by read data
+expandedCPDMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
+expandedCPDMismatchDataFilePaths$rep1 = list(
+  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read",
+                  "NHF1_CPD_1h_Rep1_mismatches_by_read_3bp_expanded.bed"),
+  hr8 = file.path(deaminationDataDirectory, "mismatches_by_read",
+                  "NHF1_CPD_8h_Rep1_mismatches_by_read_3bp_expanded.bed"),
+  hr24 = file.path(deaminationDataDirectory, "mismatches_by_read",
+                   "NHF1_CPD_24h_Rep1_mismatches_by_read_3bp_expanded.bed"),
+  hr48 = file.path(deaminationDataDirectory, "mismatches_by_read",
+                   "NHF1_CPD_48h_Rep1_mismatches_by_read_3bp_expanded.bed")
+)
+expandedCPDMismatchDataFilePaths$rep2 = list(
+  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read",
+                  "NHF1_CPD_1h_Rep2_mismatches_by_read_3bp_expanded.bed"),
+  hr8 = file.path(deaminationDataDirectory, "mismatches_by_read",
+                  "NHF1_CPD_8h_Rep2_mismatches_by_read_3bp_expanded.bed"),
+  hr24 = file.path(deaminationDataDirectory, "mismatches_by_read",
+                   "NHF1_CPD_24h_Rep2_mismatches_by_read_3bp_expanded.bed"),
+  hr48 = file.path(deaminationDataDirectory, "mismatches_by_read",
+                   "NHF1_CPD_48h_Rep2_mismatches_by_read_3bp_expanded.bed")
+)
+
+expandedSixFourMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
+expandedSixFourMismatchDataFilePaths$rep1 = list(
+  min5 = file.path(deaminationDataDirectory, "mismatches_by_read",
+                   "NHF1_6-4-PP_5min_Rep1_mismatches_by_read_3bp_expanded.bed"),
+  min20 = file.path(deaminationDataDirectory, "mismatches_by_read",
+                    "NHF1_6-4-PP_20min_Rep1_mismatches_by_read_3bp_expanded.bed"),
+  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read",
+                  "NHF1_6-4-PP_1h_Rep1_mismatches_by_read_3bp_expanded.bed")
+)
+expandedSixFourMismatchDataFilePaths$rep2 = list(
+  min5 = file.path(deaminationDataDirectory, "mismatches_by_read",
+                   "NHF1_6-4-PP_5min_Rep2_mismatches_by_read_3bp_expanded.bed"),
+  min20 = file.path(deaminationDataDirectory, "mismatches_by_read",
+                    "NHF1_6-4-PP_20min_Rep2_mismatches_by_read_3bp_expanded.bed"),
+  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read",
+                  "NHF1_6-4-PP_1h_Rep2_mismatches_by_read_3bp_expanded.bed")
+)
+```
+
+```{r acquire_and_format_data_2}
+expandedCPDSingleCToTMismatchData = lapply(expandedCPDMismatchDataFilePaths, function(x) lapply(x, fread))
+expandedSixFourSingleCToTMismatchData = lapply(expandedSixFourMismatchDataFilePaths, function(x) lapply(x, fread))
+expansionOffset = 3
+
+# Create a subset of single mismatch C>T reads.
+expandedCPDSingleCToTMismatchData = lapply(expandedCPDSingleCToTMismatchData, function(x) lapply(
+  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = 23, maxReadLength = 31)
+))
+expandedSixFourSingleCToTMismatchData = lapply(expandedSixFourSingleCToTMismatchData, function(x) lapply(
+  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = 23, maxReadLength = 31)
+))
+
+# Simplify the data
+expandedCPDSingleCToTMismatchData = lapply(expandedCPDSingleCToTMismatchData, function(x) lapply(
+  x, function(y) simplifyTable(y, TRUE, expansionOffset = expansionOffset)
+))
+expandedSixFourSingleCToTMismatchData = lapply(expandedSixFourSingleCToTMismatchData, function(x) lapply(
+  x, function(y) simplifyTable(y, TRUE, expansionOffset = expansionOffset)
+))
+
+# Further filter data by read position based on length
+expandedCPDSingleCToTMismatchData = lapply(expandedCPDSingleCToTMismatchData, function(x) {
+  lapply(x, filterMismatchesByPositionAndReadLength, HUMAN_THREE_PRIME_POS_CONSTRAINTS, expansionOffset)
+})
+
+expandedSixFourSingleCToTMismatchData = lapply(expandedSixFourSingleCToTMismatchData, function(x) {
+  lapply(x, filterMismatchesByPositionAndReadLength, HUMAN_THREE_PRIME_POS_CONSTRAINTS, expansionOffset)
+})
+```
+
+```{r orient_data_to_mismatch_positions}
+threePrimeMismatchAnchoredCPDData = lapply(expandedCPDSingleCToTMismatchData, function(x) {
+  lapply(x, orientDataToMismatch, THREE_PRIME, expansionOffset)
+})
+fivePrimeMismatchAnchoredCPDData = lapply(expandedCPDSingleCToTMismatchData, function(x) {
+  lapply(x, orientDataToMismatch, FIVE_PRIME, expansionOffset)
+})
+
+threePrimeMismatchAnchoredSixFourData = lapply(expandedSixFourSingleCToTMismatchData, function(x) {
+  lapply(x, orientDataToMismatch, THREE_PRIME, expansionOffset)
+})
+fivePrimeMismatchAnchoredSixFourData = lapply(expandedSixFourSingleCToTMismatchData, function(x) {
+  lapply(x, orientDataToMismatch, FIVE_PRIME, expansionOffset)
+})
+```
+
+```{r generate_nucleotide_frequency_data_2}
+threePrimeMismatchCPDNucFreq = lapply(threePrimeMismatchAnchoredCPDData, tabulateNucFreqByPosTimepointAndLength)
+fivePrimeMismatchCPDNucFreq = lapply(fivePrimeMismatchAnchoredCPDData,
+                                     tabulateNucFreqByPosTimepointAndLength, posType = FIVE_PRIME)
+
+threePrimeMismatchSixFourNucFreq = lapply(threePrimeMismatchAnchoredSixFourData,
+                                          tabulateNucFreqByPosTimepointAndLength)
+fivePrimeMismatchSixFourNucFreq = lapply(fivePrimeMismatchAnchoredSixFourData,
+                                         tabulateNucFreqByPosTimepointAndLength, posType = FIVE_PRIME)
+```
+
+```{r CPD_mismatch__anchored_nucleotide_frequencies, fig.width = 11, fig.height = 7}
+plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
+                               title = "CPD 3' Anchored Nucleotide Frequencies Rep1",
+                               secondaryYAxisLabel = "5' Cut Site Distance",
+                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep2, 
+                               title = "CPD 3' Anchored Nucleotide Frequencies Rep2",
+                               secondaryYAxisLabel = "5' Cut Site Distance",
+                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+
+plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
+                               title = "CPD 5' Anchored Nucleotide Frequencies Rep1",
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
+                               title = "CPD 5' Anchored Nucleotide Frequencies Rep2",
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+```
+
+```{r CPD_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 7}
+plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
+                               title = "CPD 3' Anchored Purine Frequencies Rep1",
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep2, 
+                               title = "CPD 3' Anchored Purine Frequencies Rep2",
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+
+plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
+                               title = "CPD 5' Anchored Purine Frequencies Rep1",
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
+                               title = "CPD 5' Anchored Purine Frequencies Rep2",
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+```

### 2022-05-11 R/HumanDeaminationReadLengthAnalysis.rmd
Update HumanDeaminationReadLengthAnalysis.rmd
Removed previous "non-lesion-anchored" analysis.

@@
 
-```{r get_file_paths_1}
-# Get file paths for the mismatch by read data
-CPDMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
-CPDMismatchDataFilePaths$rep1 = list(
-  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_1h_Rep1_mismatches_by_read.bed"),
-  hr8 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_8h_Rep1_mismatches_by_read.bed"),
-  hr24 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_24h_Rep1_mismatches_by_read.bed"),
-  hr48 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_48h_Rep1_mismatches_by_read.bed")
-)
-CPDMismatchDataFilePaths$rep2 = list(
-  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_1h_Rep2_mismatches_by_read.bed"),
-  hr8 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_8h_Rep2_mismatches_by_read.bed"),
-  hr24 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_24h_Rep2_mismatches_by_read.bed"),
-  hr48 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_CPD_48h_Rep2_mismatches_by_read.bed")
-)
+```{r get_file_paths}
+expansionOffset = 10
 
-sixFourMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
-sixFourMismatchDataFilePaths$rep1 = list(
-  min5 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_5min_Rep1_mismatches_by_read.bed"),
-  min20 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_20min_Rep1_mismatches_by_read.bed"),
-  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_1h_Rep1_mismatches_by_read.bed")
-)
-sixFourMismatchDataFilePaths$rep2 = list(
-  min5 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_5min_Rep2_mismatches_by_read.bed"),
-  min20 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_20min_Rep2_mismatches_by_read.bed"),
-  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read", "NHF1_6-4-PP_1h_Rep2_mismatches_by_read.bed")
-)
-```
-
-```{r acquire_and_format_data_1}
-CPDMismatchData = lapply(CPDMismatchDataFilePaths, function(x) lapply(x, fread))
-sixFourMismatchData = lapply(sixFourMismatchDataFilePaths, function(x) lapply(x, fread))
-
-# Create a subset of single mismatch C>T reads.
-CPDSingleCToTMismatchData = lapply(CPDMismatchData, function(x) lapply(
-  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = 23, maxReadLength = 31)
-))
-sixFourSingleCToTMismatchData = lapply(sixFourMismatchData, function(x) lapply(
-  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = 23, maxReadLength = 31)
-))
-
-# Simplify the data
-CPDSingleCToTMismatchData = lapply(CPDSingleCToTMismatchData, function(x) lapply(
-  x, function(y) simplifyTable(y, TRUE)
-))
-sixFourSingleCToTMismatchData = lapply(sixFourSingleCToTMismatchData, function(x) lapply(
-  x, function(y) simplifyTable(y, TRUE)
-))
-
-```
-
-```{r filter_by_mismatch_pos_and_read_length_1}
-CPDPeakCToTMismatchData = lapply(CPDSingleCToTMismatchData, function(x) {
-  lapply(x, filterMismatchesByPositionAndReadLength, HUMAN_THREE_PRIME_POS_CONSTRAINTS)
-})
-CPDFirstQPeakCToTMismatchData = lapply(CPDPeakCToTMismatchData, function(x) {
-  lapply(x, getFirstPositionQuartile)
-})
-CPDLastQPeakCToTMismatchData = lapply(CPDPeakCToTMismatchData, function(x) {
-  lapply(x, getLastPositionQuartile)
-})
-
-sixFourPeakCToTMismatchData = lapply(sixFourSingleCToTMismatchData, function(x) {
-  lapply(x, filterMismatchesByPositionAndReadLength, HUMAN_THREE_PRIME_POS_CONSTRAINTS)
-})
-sixFourFirstQPeakCToTMismatchData = lapply(sixFourPeakCToTMismatchData, function(x) {
-  lapply(x, getFirstPositionQuartile)
-})
-sixFourLastQPeakCToTMismatchData = lapply(sixFourPeakCToTMismatchData, function(x) {
-  lapply(x, getLastPositionQuartile)
-})
-```
-
-```{r generate_nucleotide_frequency_data_1}
-CPDSingleCToTNucFreq = lapply(CPDSingleCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
-CPDFirstQPeakCToTNucFreq = lapply(CPDFirstQPeakCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
-CPDLastQPeakCToTNucFreq = lapply(CPDLastQPeakCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
-
-sixFourSingleCToTNucFreq = lapply(sixFourSingleCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
-sixFourFirstQPeakCToTNucFreq = lapply(sixFourFirstQPeakCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
-sixFourLastQPeakCToTNucFreq = lapply(sixFourLastQPeakCToTMismatchData, tabulateNucFreqByPosTimepointAndLength)
-```
-
-```{r purine_vs_pyrimidine_frequencies_across_read_length, fig.width = 11, fig.height = 5}
-plotNucFreqVsReadLengthBarPlot(CPDSingleCToTNucFreq$rep1, title = "CPD Rep1 3' Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(CPDSingleCToTNucFreq$rep2, title = "CPD Rep2 3' Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-
-plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTNucFreq$rep1, title = "6-4 Rep1 3' Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(sixFourSingleCToTNucFreq$rep2, title = "6-4 Rep2 3' Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-```
-
-```{r purine_vs_pyrimidine_frequencies_first_quartile_mismatch_pos, fig.width = 11, fig.height = 5}
-plotNucFreqVsReadLengthBarPlot(CPDFirstQPeakCToTNucFreq$rep1, title = "CPD Rep1 1st Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(CPDFirstQPeakCToTNucFreq$rep2, title = "CPD Rep2 1st Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-
-plotNucFreqVsReadLengthBarPlot(sixFourFirstQPeakCToTNucFreq$rep1, title = "6-4 Rep1 1st Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(sixFourFirstQPeakCToTNucFreq$rep2, title = "6-4 Rep2 1st Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-```
-
-```{r purine_vs_pyrimidine_frequencies_last_quartile_mismatch_pos, fig.width = 11, fig.height = 5}
-plotNucFreqVsReadLengthBarPlot(CPDLastQPeakCToTNucFreq$rep1, title = "CPD Rep1 4th Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(CPDLastQPeakCToTNucFreq$rep2, title = "CPD Rep2 4th Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-
-plotNucFreqVsReadLengthBarPlot(sixFourLastQPeakCToTNucFreq$rep1, title = "6-4 Rep1 4th Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-plotNucFreqVsReadLengthBarPlot(sixFourLastQPeakCToTNucFreq$rep2, title = "6-4 Rep2 4th Quartile Nuc Freq",
-                               combineNucleotides = c("AG","CT"), combinedNames = c("Purine","Pyrimidine"))
-```
-
-```{r get_file_paths_2}
 # Get file paths for the expanded mismatch by read data
@@
   hr1 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                  "NHF1_CPD_1h_Rep1_mismatches_by_read_3bp_expanded.bed"),
+                  paste0("NHF1_CPD_1h_Rep1_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
   hr8 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                  "NHF1_CPD_8h_Rep1_mismatches_by_read_3bp_expanded.bed"),
+                  paste0("NHF1_CPD_8h_Rep1_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
   hr24 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                   "NHF1_CPD_24h_Rep1_mismatches_by_read_3bp_expanded.bed"),
+                   paste0("NHF1_CPD_24h_Rep1_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
   hr48 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                   "NHF1_CPD_48h_Rep1_mismatches_by_read_3bp_expanded.bed")
+                   paste0("NHF1_CPD_48h_Rep1_mismatches_by_read_",expansionOffset,"bp_expanded.bed"))
 )
@@
   hr1 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                  "NHF1_CPD_1h_Rep2_mismatches_by_read_3bp_expanded.bed"),
+                  paste0("NHF1_CPD_1h_Rep2_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
   hr8 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                  "NHF1_CPD_8h_Rep2_mismatches_by_read_3bp_expanded.bed"),
+                  paste0("NHF1_CPD_8h_Rep2_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
   hr24 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                   "NHF1_CPD_24h_Rep2_mismatches_by_read_3bp_expanded.bed"),
+                   paste0("NHF1_CPD_24h_Rep2_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
   hr48 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                   "NHF1_CPD_48h_Rep2_mismatches_by_read_3bp_expanded.bed")
+                   paste0("NHF1_CPD_48h_Rep2_mismatches_by_read_",expansionOffset,"bp_expanded.bed"))
 )
@@
   min5 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                   "NHF1_6-4-PP_5min_Rep1_mismatches_by_read_3bp_expanded.bed"),
+                   paste0("NHF1_6-4-PP_5min_Rep1_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
   min20 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                    "NHF1_6-4-PP_20min_Rep1_mismatches_by_read_3bp_expanded.bed"),
+                    paste0("NHF1_6-4-PP_20min_Rep1_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
   hr1 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                  "NHF1_6-4-PP_1h_Rep1_mismatches_by_read_3bp_expanded.bed")
+                  paste0("NHF1_6-4-PP_1h_Rep1_mismatches_by_read_",expansionOffset,"bp_expanded.bed"))
 )
@@
   min5 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                   "NHF1_6-4-PP_5min_Rep2_mismatches_by_read_3bp_expanded.bed"),
+                   paste0("NHF1_6-4-PP_5min_Rep2_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
   min20 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                    "NHF1_6-4-PP_20min_Rep2_mismatches_by_read_3bp_expanded.bed"),
+                    paste0("NHF1_6-4-PP_20min_Rep2_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
   hr1 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                  "NHF1_6-4-PP_1h_Rep2_mismatches_by_read_3bp_expanded.bed")
+                  paste0("NHF1_6-4-PP_1h_Rep2_mismatches_by_read_",expansionOffset,"bp_expanded.bed"))
 )
@@
 
-```{r acquire_and_format_data_2}
+```{r acquire_and_format_data}
 expandedCPDSingleCToTMismatchData = lapply(expandedCPDMismatchDataFilePaths, function(x) lapply(x, fread))
 expandedSixFourSingleCToTMismatchData = lapply(expandedSixFourMismatchDataFilePaths, function(x) lapply(x, fread))
-expansionOffset = 3
 
@@
 
-```{r generate_nucleotide_frequency_data_2}
+```{r generate_nucleotide_frequency_data}
 threePrimeMismatchCPDNucFreq = lapply(threePrimeMismatchAnchoredCPDData, tabulateNucFreqByPosTimepointAndLength)
@@
 ```
+
+```{r CPD_mismatch__anchored_nucleotide_frequencies, fig.width = 11, fig.height = 7}
+plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
+                               title = "6-4 3' Anchored Nucleotide Frequencies Rep1",
+                               secondaryYAxisLabel = "5' Cut Site Distance",
+                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
+                               title = "6-4 3' Anchored Nucleotide Frequencies Rep2",
+                               secondaryYAxisLabel = "5' Cut Site Distance",
+                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+
+plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep1, 
+                               title = "6-4 5' Anchored Nucleotide Frequencies Rep1",
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep2, 
+                               title = "6-4 5' Anchored Nucleotide Frequencies Rep2",
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+```
+
+```{r CPD_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 7}
+plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
+                               title = "6-4 3' Anchored Purine Frequencies Rep1",
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
+                               title = "6-4 3' Anchored Purine Frequencies Rep2",
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+
+plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep1, 
+                               title = "6-4 5' Anchored Purine Frequencies Rep1",
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep2, 
+                               title = "6-4 5' Anchored Purine Frequencies Rep2",
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+```
+
+```{r compute_sequence_enrichment}
+threePrimeMMAnchoredCPDEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
+  setNames(lapply(seq_along(mismatchDataRep), function(i) {
+    getSequenceEnrichmentByReadLengthAndPos(mismatchDataRep[[i]],
+                                            nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
+                                            c("CG","CA","TG","TA"))
+  }), names(mismatchDataRep))
+}, threePrimeMismatchAnchoredCPDData, threePrimeMismatchCPDNucFreq, SIMPLIFY = FALSE)
+
+fivePrimeMMAnchoredCPDEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
+  setNames(lapply(seq_along(mismatchDataRep), function(i) {
+    getSequenceEnrichmentByReadLengthAndPos(mismatchDataRep[[i]],
+                                            nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
+                                            c("TGG"), posType = FIVE_PRIME)
+  }), names(mismatchDataRep))
+}, fivePrimeMismatchAnchoredCPDData, fivePrimeMismatchCPDNucFreq, SIMPLIFY = FALSE)
+
+threePrimeMMAnchoredSixFourEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
+  setNames(lapply(seq_along(mismatchDataRep), function(i) {
+    getSequenceEnrichmentByReadLengthAndPos(mismatchDataRep[[i]],
+                                            nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
+                                            c("CG","CA","TG","TA"))
+  }), names(mismatchDataRep))
+}, threePrimeMismatchAnchoredSixFourData, threePrimeMismatchSixFourNucFreq, SIMPLIFY = FALSE)
+
+fivePrimeMMAnchoredSixFourEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
+  setNames(lapply(seq_along(mismatchDataRep), function(i) {
+    getSequenceEnrichmentByReadLengthAndPos(mismatchDataRep[[i]],
+                                            nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
+                                            c("TGG"), posType = FIVE_PRIME)
+  }), names(mismatchDataRep))
+}, fivePrimeMismatchAnchoredSixFourData, fivePrimeMismatchSixFourNucFreq, SIMPLIFY = FALSE)
+```
+
+```{r plot_CPD_sequence_enrichment, fig.width = 11, fig.height = 7}
+plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment$rep1,
+                       title = "CPD 3' Anchored YR Enrichment Rep1", secondaryYAxisLabel = "5' Cut Site Distance",
+                       showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
+                       querySequences = c("CG","CA","TG","TA"))
+plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment$rep2,
+                       title = "CPD 3' Anchored YR Enrichment Rep2", secondaryYAxisLabel = "5' Cut Site Distance",
+                       showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
+                       querySequences = c("CG","CA","TG","TA"))
+
+plotSequenceEnrichment(fivePrimeMMAnchoredCPDEnrichment$rep1,
+                       title = "CPD 5' Anchored TGG Enrichment Rep1", secondaryYAxisLabel = "3' Cut Site Distance",
+                       showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
+                       querySequences = c("TGG"))
+plotSequenceEnrichment(fivePrimeMMAnchoredCPDEnrichment$rep2,
+                       title = "CPD 5' Anchored TGG Enrichment Rep2", secondaryYAxisLabel = "3' Cut Site Distance",
+                       showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
+                       querySequences = c("TGG"))
+```
+
+```{r enrichment_test_1}
+for (i in 1:5) {
+  testTable = data.table(Read_Length = 9,
+                         Read_Sequence = replicate(1000, paste0(sample(c('A','C','G','T'), 9, TRUE), collapse = '')))
+  testTableNucFreq = tabulateNucFreqByPosTimepointAndLength(testTable)
+  testEnrichment = getSequenceEnrichmentByReadLengthAndPos(testTable, testTableNucFreq, c("CG","CA","TG","TA"))
+  plotSequenceEnrichment(testEnrichment, title = "CPD 3' Anchored YR Enrichment Rep1")
+}
+```
+
+```{r enrichment_test_2}
+for (i in 1:5) {
+  testTable = data.table(Read_Length = 9,
+                         Read_Sequence = replicate(1000,
+                                                   paste0(sample(c(rep('A',6),rep('C',4),rep('G',4),rep('T',6)),
+                                                                 9, TRUE), collapse = '')))
+  testTableNucFreq = tabulateNucFreqByPosTimepointAndLength(testTable)
+  testEnrichment = getSequenceEnrichmentByReadLengthAndPos(testTable, testTableNucFreq, c("CG","CA","TG","TA"))
+  plotSequenceEnrichment(testEnrichment, title = "CPD 3' Anchored YR Enrichment Rep1")
+}
+```

### 2022-05-11 R/DeaminationAnalysis.R
Added sequence enrichment functions
Added two functions:
- One for determining sequence enrichment across read length and positions.
- One for plotting these values, potentially across timepoints as well.

@@ -561,6 +561,124 @@ orientDataToMismatch = function(simplifiedTable, posType, expansionOffset = 0) {
 }
 
 
+# Given a specific nucleotide sequence, determine its observed vs. expected frequency in a set of reads
+# based on their sequences and position-specific nucleotide frequencies (may need to be subset by timepoint)
+getSequenceEnrichmentByReadLengthAndPos = function(readSequencesTable, expectedNucleotideFrequencies,
+                                                   querySequences, posType = THREE_PRIME) {
+
+  maxQueryLength = max(nchar(querySequences))
+
+  # Iterate through all the different read lengths present in the given table(s),
+  # Calculating expected and observed frequencies across all the query sequences at each position
+  # NOTE: In order to determine what positions to iterate through, the following code assumes that
+  #       all read sequences under a specific read length actually have that length.
+  return(rbindlist(lapply(unique(readSequencesTable$Read_Length), function(readLength) {
+
+    sequences = readSequencesTable[Read_Length == readLength]$Read_Sequence
+    readLengthSpecificNucFreq = expectedNucleotideFrequencies[Read_Length == readLength]
+    if (posType == THREE_PRIME) {
+      positions = -nchar(sequences[1]):(-1 - maxQueryLength + 1)
+    } else if (posType == FIVE_PRIME) {
+      positions = 1:(nchar(sequences[1]) - maxQueryLength + 1)
+    } else stop("Unrecognized value for posType parameter.")
+
+    enrichmentValues = sapply(positions, function(position) {
+
+      expectedFrequency = sum(sapply(querySequences, function(querySequence) {
+        prod(sapply(1:nchar(querySequence), function(i) {
+          readLengthSpecificNucFreq[Position == position + i - 1 &
+                                    Nucleotide == str_sub(querySequence, i, i)]$Frequency
+        }))
+      }))
+
+      observedFrequency = sum(sapply(querySequences, function(querySequence) {
+        sum(str_sub(sequences, position, position + nchar(querySequence) - 1) == querySequence)/length(sequences)
+      }))
+
+      # Add pseudo counts to avoid dividing by or taking the log (during plotting) of 0.
+      pseudoCount = 1/length(sequences)
+      observedFrequency = observedFrequency + pseudoCount
[…]

### 2022-05-11 R/DeaminationAnalysis.R
Sequence frequency without normalization
- Adapted the getSequenceEnrichmentByReadLengthAndPos function to optionally compute simple sequence frequency instead. This is achieved by not supplying an argument for the expectedNucleotideFrequencies parameter.
- Added a function for plotting sequence frequencies.

@@ -561,10 +561,11 @@ orientDataToMismatch = function(simplifiedTable, posType, expansionOffset = 0) {
 }
 
 
-# Given a specific nucleotide sequence, determine its observed vs. expected frequency in a set of reads
-# based on their sequences and position-specific nucleotide frequencies (may need to be subset by timepoint)
-getSequenceEnrichmentByReadLengthAndPos = function(readSequencesTable, expectedNucleotideFrequencies,
-                                                   querySequences, posType = THREE_PRIME) {
+# Given one or more nucleotide sequences, determine their frequency in a set of reads
+# across position and read length (may need to be subset by timepoint).
+# Optionally, a table of nucleotide frequencies may be provided to normalize by.
+getSequenceFreqByReadLengthAndPos = function(readSequencesTable, expectedNucleotideFrequencies = NULL,
+                                             querySequences = c("TGG"), posType = THREE_PRIME) {
 
   maxQueryLength = max(nchar(querySequences))
 
@@ -575,37 +576,46 @@ getSequenceEnrichmentByReadLengthAndPos = function(readSequencesTable, expectedN
   return(rbindlist(lapply(unique(readSequencesTable$Read_Length), function(readLength) {
 
     sequences = readSequencesTable[Read_Length == readLength]$Read_Sequence
-    readLengthSpecificNucFreq = expectedNucleotideFrequencies[Read_Length == readLength]
+    if (!is.null(expectedNucleotideFrequencies)) {
+      readLengthSpecificNucFreq = expectedNucleotideFrequencies[Read_Length == readLength]
+    }
     if (posType == THREE_PRIME) {
       positions = -nchar(sequences[1]):(-1 - maxQueryLength + 1)
     } else if (posType == FIVE_PRIME) {
       positions = 1:(nchar(sequences[1]) - maxQueryLength + 1)
     } else stop("Unrecognized value for posType parameter.")
 
-    enrichmentValues = sapply(positions, function(position) {
-
-      expectedFrequency = sum(sapply(querySequences, function(querySequence) {
-        prod(sapply(1:nchar(querySequence), function(i) {
-          readLengthSpecificNucFreq[Position == position + i - 1 &
-                                    Nucleotide == str_sub(querySequence, i, i)]$Frequency
-        }))
-      }))
+    frequencies = sapply(positions, function(position) {
 
[…]

### 2022-05-11 R/DeaminationAnalysis.R
Bugfix and tweak
- Changed default parameter for querySequences to be "TGG". (Is this a bad idea?)
- Fixed a bug where the three prime cut site was shifted due to positions that don't have a sequence frequency associated with them.

@@ -628,7 +628,7 @@ plotSequenceEnrichment = function(enrichmentTablesByTimepoint, posType = THREE_P
                                   yAxisLabel = expression("log"[2]*"(Enrichment)"),
                                   secondaryYAxisLabel = "Read Length", yStripFontSize = 16, yAxisTickTextSize = 8,
                                   showThreePrimeCutSite = FALSE, showFivePrimeCutSite = FALSE,
-                                  querySequences = list('A'), expansionOffset = 0) {
+                                  querySequences = c("TGG"), expansionOffset = 0) {
 
   if (posType == THREE_PRIME) {
     xAxisLabel = "3' Relative Position"
@@ -673,7 +673,8 @@ plotSequenceEnrichment = function(enrichmentTablesByTimepoint, posType = THREE_P
 
   if (showThreePrimeCutSite) {
     plot = plot + geom_vline(aes(xintercept = Cut_Site_Pos),
-                             fullEnrichmentTable[,.(Cut_Site_Pos = max(Position) - expansionOffset + 1.5),
+                             fullEnrichmentTable[,.(Cut_Site_Pos = max(Position) - expansionOffset +
+                                                                   maxQueryLength - 0.5),
                                                  by = list(Read_Length, Timepoint)],
                              linetype = "dashed")
   }

### 2022-05-11 R/HumanDeaminationReadLengthAnalysis.rmd
Update HumanDeaminationReadLengthAnalysis.rmd

@@
 
-```{r CPD_mismatch__anchored_nucleotide_frequencies, fig.width = 11, fig.height = 7}
+```{r 6-4_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 7}
 plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
@@
 
-```{r CPD_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 7}
+```{r 6-4_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 7}
 plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
@@
   setNames(lapply(seq_along(mismatchDataRep), function(i) {
-    getSequenceEnrichmentByReadLengthAndPos(mismatchDataRep[[i]],
+    getSequenceFreqByReadLengthAndPos(mismatchDataRep[[i]],
                                       nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
@@
 
-```{r plot_CPD_sequence_enrichment, fig.width = 11, fig.height = 7}
+```{r CPD_sequence_enrichment, fig.width = 11, fig.height = 7}
 plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment$rep1,
@@
 plotSequenceEnrichment(fivePrimeMMAnchoredCPDEnrichment$rep2,
+                       title = "CPD 5' Anchored TGG Enrichment Rep2", secondaryYAxisLabel = "3' Cut Site Distance",
+                       showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
+                       querySequences = c("TGG"))
+```
+
+```{r 6-4_sequence_enrichment, fig.width = 11, fig.height = 7}
+plotSequenceEnrichment(threePrimeMMAnchoredSixFourEnrichment$rep1,
+                       title = "CPD 3' Anchored YR Enrichment Rep1", secondaryYAxisLabel = "5' Cut Site Distance",
+                       showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
+                       querySequences = c("CG","CA","TG","TA"))
+plotSequenceEnrichment(threePrimeMMAnchoredSixFourEnrichment$rep2,
+                       title = "CPD 3' Anchored YR Enrichment Rep2", secondaryYAxisLabel = "5' Cut Site Distance",
+                       showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
+                       querySequences = c("CG","CA","TG","TA"))
+
+plotSequenceEnrichment(fivePrimeMMAnchoredSixFourEnrichment$rep1,
+                       title = "CPD 5' Anchored TGG Enrichment Rep1", secondaryYAxisLabel = "3' Cut Site Distance",
+                       showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
+                       querySequences = c("TGG"))
+plotSequenceEnrichment(fivePrimeMMAnchoredSixFourEnrichment$rep2,
                        title = "CPD 5' Anchored TGG Enrichment Rep2", secondaryYAxisLabel = "3' Cut Site Distance",
@@
 ```
+
+```{r compute_sequence_frequencies}
+threePrimeMMAnchoredCPDSeqFreq = lapply(threePrimeMismatchAnchoredCPDData, function(mismatchDataRep) {
+  lapply(mismatchDataRep, function(mismatchData) {
+    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("CG","CA","TG","TA"))
+  })
+})
+
+fivePrimeMMAnchoredCPDSeqFreq = lapply(fivePrimeMismatchAnchoredCPDData, function(mismatchDataRep) {
+  lapply(mismatchDataRep, function(mismatchData) {
+    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("TGG"), posType = FIVE_PRIME)
+  })
+})
+
+threePrimeMMAnchoredSixFourSeqFreq = lapply(threePrimeMismatchAnchoredSixFourData, function(mismatchDataRep) {
+  lapply(mismatchDataRep, function(mismatchData) {
+    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("CG","CA","TG","TA"))
+  })
+})
+
+fivePrimeMMAnchoredSixFourSeqFreq = lapply(fivePrimeMismatchAnchoredSixFourData, function(mismatchDataRep) {
+  lapply(mismatchDataRep, function(mismatchData) {
+    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("TGG"), posType = FIVE_PRIME)
+  })
+})
+```
+
+```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 7}
+plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq$rep1,
+                        title = "CPD 3' Anchored YR Frequency Rep1", secondaryYAxisLabel = "5' Cut Site Distance",
+                        showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
+                        querySequences = c("CG","CA","TG","TA"))
+plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq$rep2,
+                        title = "CPD 3' Anchored YR Frequency Rep2", secondaryYAxisLabel = "5' Cut Site Distance",
+                        showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
+                        querySequences = c("CG","CA","TG","TA"))
+
+plotSequenceFrequencies(fivePrimeMMAnchoredCPDSeqFreq$rep1,
+                        title = "CPD 5' Anchored TGG Frequency Rep1", secondaryYAxisLabel = "3' Cut Site Distance",
+                        showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
+                        querySequences = c("TGG"))
+plotSequenceFrequencies(fivePrimeMMAnchoredCPDSeqFreq$rep2,
+                        title = "CPD 5' Anchored TGG Frequency Rep2", secondaryYAxisLabel = "3' Cut Site Distance",
+                        showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
+                        querySequences = c("TGG"))
+```
+
+```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 7}
+plotSequenceFrequencies(threePrimeMMAnchoredSixFourSeqFreq$rep1,
+                        title = "CPD 3' Anchored YR Frequency Rep1", secondaryYAxisLabel = "5' Cut Site Distance",
+                        showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
+                        querySequences = c("CG","CA","TG","TA"))
+plotSequenceFrequencies(threePrimeMMAnchoredSixFourSeqFreq$rep2,
+                        title = "CPD 3' Anchored YR Frequency Rep2", secondaryYAxisLabel = "5' Cut Site Distance",
+                        showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
+                        querySequences = c("CG","CA","TG","TA"))
+
+plotSequenceFrequencies(fivePrimeMMAnchoredSixFourSeqFreq$rep1,
+                        title = "CPD 5' Anchored TGG Frequency Rep1", secondaryYAxisLabel = "3' Cut Site Distance",
+                        showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
+                        querySequences = c("TGG"))
+plotSequenceFrequencies(fivePrimeMMAnchoredSixFourSeqFreq$rep2,
+                        title = "CPD 5' Anchored TGG Frequency Rep2", secondaryYAxisLabel = "3' Cut Site Distance",
+                        showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
+                        querySequences = c("TGG"))
+```

### 2022-05-11 R/HumanDeaminationReadLengthAnalysis.rmd
Update HumanDeaminationReadLengthAnalysis.rmd

@@
   testTableNucFreq = tabulateNucFreqByPosTimepointAndLength(testTable)
-  testEnrichment = getSequenceEnrichmentByReadLengthAndPos(testTable, testTableNucFreq, c("CG","CA","TG","TA"))
+  testEnrichment = getSequenceFreqByReadLengthAndPos(testTable, testTableNucFreq, c("CG","CA","TG","TA"))
   plotSequenceEnrichment(testEnrichment, title = "CPD 3' Anchored YR Enrichment Rep1")

### 2022-05-16 R/DeaminationAnchoredExcisionSiteAnalysis.R
Renamed strand orientation constants

@@ -2,8 +2,8 @@ library(data.table)
 library(stringr)
 library(ggplot2)
 
-THREE_PRIME = 3
-FIVE_PRIME = 5
+THREE_PRIME = "three_prime"
+FIVE_PRIME = "five_prime"
 
 # Default text scaling
 defaultTextScaling = theme(plot.title = element_text(size = 26, hjust = 0.5),
@@ -20,14 +20,14 @@ blankBackground = theme(panel.grid.major = element_blank(), panel.grid.minor = e
 # Takes optional arguments to add columns with additional, repeating information (e.g. read length, timepoint).
 tabulateNucleotideFrequenciesByPosition = function(sequences, posType = THREE_PRIME,
                                                    paddingColNames = list(), paddingInfo = list()) {
-  
+
   maxStringLength = max(nchar(sequences))
   if (posType == THREE_PRIME) {
     positions = -1:-maxStringLength
   } else if (posType == FIVE_PRIME) {
     positions = 1:maxStringLength
   } else stop("Unrecognized value for posType parameter.")
-  
+
   nucFreqByPosition = data.table(Position = rep(positions, 4),
                                  Nucleotide = unlist(lapply(c('A','C','G','T'),
                                                             function(x) rep(x, maxStringLength))),
@@ -38,62 +38,62 @@ tabulateNucleotideFrequenciesByPosition = function(sequences, posType = THREE_PR
                                    })
                                  }))
   )
-  
+
   mapply(function(x,y) nucFreqByPosition[, eval(x) := y], paddingColNames, paddingInfo)
-  
+
   return(nucFreqByPosition)
-  
+
 }
 
 
 tabulateNucFreqByPosTimepointAndLength = function(simplifiedTablesByTimepoint, posType = THREE_PRIME,
                                                   combineNucleotides = list(), combinedNames = list()) {
-  
+
   #If passed a single data.table, wrap it in a list.
   if (is.data.table(simplifiedTablesByTimepoint)){
     simplifiedTablesByTimepoint = list(simplifiedTablesByTimepoint)
     noTimepoints = TRUE
   } else noTimepoints = FALSE
-  
+
   # First, stratify the data by length and timepoint (optional),
   # calculating relative nucleotide frequencies within each category.
   nucFreqTable = rbindlist(lapply(seq_along(simplifiedTablesByTimepoint), function(i) {
[…]

### 2022-05-16 R/DeaminationSequenceAndPositionAnalysis.R

@@ -2,8 +2,8 @@ library(data.table)
 library(stringr)
 library(ggplot2)
 
-THREE_PRIME = 3
-FIVE_PRIME = 5
+THREE_PRIME = "three_prime"
+FIVE_PRIME = "five_prime"
 
 # Default text scaling
 defaultTextScaling = theme(plot.title = element_text(size = 26, hjust = 0.5),
@@ -25,21 +25,21 @@ getReadLengthAndGCContent = function(table) {
 
 # Displays the frequencies of each mismatch type.
 plotMismatchTypeFrequencies = function(mismatchTable, title = "Mismatch Type Frequency") {
-  
+
   print(
     ggplot(mismatchTable[, .N, by = Mismatch][, Freq := N/sum(N)], aes(x = Mismatch, y = Freq)) +
       geom_bar(stat = "identity") +
       labs(title = title, x = "Mismatch Type", y = "Frequency") +
       blankBackground + defaultTextScaling + theme(axis.text = element_text(size = 15))
   )
-  
+
 }
 
 # Displays the frequencies of positions for the chosen mismatch types.
 # (Types can be chosen by inclusion or omission)
 plotMismatchPositionFrequencies = function(mismatchTable, includedTypes = list(), omittedTypes = list(),
                                            title = "Position Frequency", posType = THREE_PRIME) {
-  
+
   if (posType == THREE_PRIME) {
     xAxisLabel = "3' Relative Position"
   } else if (posType == FIVE_PRIME) {
@@ -47,7 +47,7 @@ plotMismatchPositionFrequencies = function(mismatchTable, includedTypes = list()
     mismatchTable = copy(mismatchTable)
     mismatchTable[, Position := Read_Length + Position + 1]
   } else stop("Unrecognized value for posType parameter.")
-  
+
   if ( length(includedTypes) > 0 && length(omittedTypes) > 0) {
     stop("Included types and omitted types given simultaneously")
   } else if (length(includedTypes) > 0) {
@@ -57,14 +57,14 @@ plotMismatchPositionFrequencies = function(mismatchTable, includedTypes = list()
   } else {
     frequencyData = mismatchTable[, .N, by = Position][, Freq := N/sum(N)]
   }
-  
+
   print(
     ggplot(frequencyData, aes(x = Position, y = Freq)) +
       geom_bar(stat = "identity") +
       labs(title = title, x = xAxisLabel, y = "Frequency") +
       blankBackground + defaultTextScaling
   )
-  
+
 }
 
[…]

### 2022-05-16 R/UsefulFileSystemFunctions.R
Create UsefulFileSystemFunctions.R
This script is used to generate file paths in a more standardized manner.

@@ -1,0 +1,39 @@
+library(stringr)
+
+# A list containing the strings designated to files containing a specific type of data.
+dataTypeStrings =
+  list(mismatchesByRead = "mismatches_by_read",
+       simplifiedMismatches = "simplified_mismatches",
+       mismatchPositionStats = "mismatch_position_stats",
+       nucleosomePeriodicity = "deamination_periodicity_results",
+       nucleotideFrequencyData = "nucleotide_frequencies",
+       sequenceEnrichment = "sequence_enrichment",
+       sequenceFrequency = "sequence_frequency")
+
+generateFilePath = function(directory, dataTypeString, fileExtension,
+                            cellType = NA, lesion = NA, timepoint = NA, repitition = NA,
+                            includedMismatches = character(), omittedMismatches = character(),
+                            strandPolarity = NA, anchored = F, sequence = NA, expansionNum = NA,
+                            additionalInformation = character()) {
+
+  if ( length(includedMismatches) > 0 && length(omittedMismatches) > 0) {
+    stop("Included mismatches and omitted mismatches given simultaneously")
+  }
+
+  includedMismatches = lapply(includedMismatches, function(x) str_replace(x, '>', "_to_"))
+  omittedMismatches = lapply(omittedMismatches, function(x) str_replace(x, '>', "_to_"))
+
+  if (!is.na(expansionNum)) expansionText = paste0(expansionNum,"bp_expanded")
+  else expansionText = NA
+
+  if (anchored) anchoredText = "anchored"
+  else anchoredText = NA
+
+  basenameParts = c(cellType, lesion, timepoint, repitition, includedMismatches, omittedMismatches, "omitted",
+                    strandPolarity, anchoredText, sequence, additionalInformation, dataTypeString, expansionText)
+  if (length(omittedMismatches) == 0) basenameParts[5+length(includedMismatches)] = NA
+  basenameParts = basenameParts[!is.na(basenameParts)]
+
+  return(file.path(directory,paste0(paste(basenameParts,collapse = '_'),fileExtension)))
+
+}

### 2022-05-16 R/NHF1DeaminationAnchoredExcisionSiteDataGeneration.rmd
Notebook OVERHAUL
- Things were way too messy... They could still be better, but this is definitely a step up without spending an exorbitant amount of time restructuring.
- Individual analysis files have been split into two parts (where relevant): Data generation and figure generation. This should allow for more frequent iterating over the specifics of figures.
- File path generation is now standardized using the new UsefulFileSystemFunctions script
- Implemented general standardizations to parameters that are likely to change as we introduce more data. (E.g. cell type and timepoints).

---
title: "NHF1 Deamination Anchored Excision Site Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

```{r setup_chunk}
library(knitr)

expansionOffset = 10
cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)

opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5,
               fig.path = paste0(file.path("deamination_analysis_output", cellType,
                                           "deamination_anchored_excision_site_figures"),
                                 .Platform$file.sep))
if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
}

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
mismatchesByReadDirectory = file.path(deaminationDataDirectory, "mismatches_by_read")
deaminationExcisionSiteDataDirectory = file.path(deaminationDataDirectory, "excision_site_analysis")
dir.create(deaminationExcisionSiteDataDirectory, showWarnings = FALSE, recursive = TRUE)
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationParseAndFilter.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationAnchoredExcisionSiteAnalysis.R"))
```

```{r read_expanded_mismatch_data}
# Get file paths for the expanded mismatch by read data
CPDMismatchData = list(rep1 = CPDTimepoints,
                       rep2 = CPDTimepoints)
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    CPDMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
      repitition = names(CPDMismatchData)[i], expansionNum = expansionOffset
      ))
  }
}

sixFourMismatchData = list(rep1 = sixFourTimepoints,
                           rep2 = sixFourTimepoints)
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "6-4-PP", timepoint = names(sixFourMismatchData[[i]])[j],
      repitition = names(sixFourMismatchData)[i], expansionNum = expansionOffset
      ))
  }
}
```

```{r generate_simplified_and_filtered_mismatch_data}
# Filter the reads by length and mismatch type (single C>T).
CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = 23, maxReadLength = 31)
))
sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = 23, maxReadLength = 31)
))

# Simplify the data
CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
  x, function(y) simplifyTable(y, TRUE, expansionOffset = expansionOffset)
))
sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
  x, function(y) simplifyTable(y, TRUE, expansionOffset = expansionOffset)
))

# Determine the peak positions to filter on for each read length in each data set.
CPDPeakPositions = lapply(CPDMismatchData, function(x) lapply(
  x, getPeakPositionsByReadLength, expansionOffset
))
sixFourPeakPositions = lapply(sixFourMismatchData, function(x) lapply(
  x, getPeakPositionsByReadLength, expansionOffset
))

# Further filter data by read position based on length
CPDMismatchData = mapply(function(CPDMismatchDataRep, CPDPeakPositionsRep) mapply(
  filterMismatchesByPositionAndReadLength, CPDMismatchDataRep, CPDPeakPositionsRep,
  expansionOffset, SIMPLIFY = FALSE
), CPDMismatchData, CPDPeakPositions, SIMPLIFY = FALSE)
sixFourMismatchData = mapply(function(sixFourMismatchDataRep, sixFourPeakPositionsRep) mapply(
  filterMismatchesByPositionAndReadLength, sixFourMismatchDataRep, sixFourPeakPositionsRep,
  expansionOffset, SIMPLIFY = FALSE
), sixFourMismatchData, sixFourPeakPositions, SIMPLIFY = FALSE)
```

```{r orient_data_to_mismatch_positions}
# NOTE: The assignments to null are there so that the garbage collector can free up memory, and
#       I can still switch to new variable names for organizational purposes.
threePrimeMismatchAnchoredCPDData = lapply(CPDMismatchData, function(x) {
  lapply(x, orientDataToMismatch, THREE_PRIME, expansionOffset)
})
fivePrimeMismatchAnchoredCPDData = lapply(CPDMismatchData, function(x) {
  lapply(x, orientDataToMismatch, FIVE_PRIME, expansionOffset)
})
CPDMismatchData = NULL

threePrimeMismatchAnchoredSixFourData = lapply(sixFourMismatchData, function(x) {
  lapply(x, orientDataToMismatch, THREE_PRIME, expansionOffset)
})
fivePrimeMismatchAnchoredSixFourData = lapply(sixFourMismatchData, function(x) {
  lapply(x, orientDataToMismatch, FIVE_PRIME, expansionOffset)
})
sixFourMismatchData = NULL
```

```{r generate_and_write_nucleotide_frequency_data}
threePrimeMismatchCPDNucFreq = lapply(threePrimeMismatchAnchoredCPDData, tabulateNucFreqByPosTimepointAndLength)
for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
  fwrite(threePrimeMismatchCPDNucFreq[[i]], sep = '\t', file = generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "CPD", repitition = names(threePrimeMismatchCPDNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE
  ))
}

fivePrimeMismatchCPDNucFreq = lapply(fivePrimeMismatchAnchoredCPDData,
                                     tabulateNucFreqByPosTimepointAndLength, posType = FIVE_PRIME)
for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
  fwrite(fivePrimeMismatchCPDNucFreq[[i]], sep = '\t', file = generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMismatchCPDNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE
  ))
}

threePrimeMismatchSixFourNucFreq = lapply(threePrimeMismatchAnchoredSixFourData,
                                          tabulateNucFreqByPosTimepointAndLength)
for (i in seq_along(threePrimeMismatchSixFourNucFreq)) {
  fwrite(threePrimeMismatchSixFourNucFreq[[i]], sep = '\t', file = generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "6-4", repitition = names(threePrimeMismatchSixFourNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE
  ))
}

fivePrimeMismatchSixFourNucFreq = lapply(fivePrimeMismatchAnchoredSixFourData,
                                         tabulateNucFreqByPosTimepointAndLength, posType = FIVE_PRIME)
for (i in seq_along(fivePrimeMismatchSixFourNucFreq)) {
  fwrite(fivePrimeMismatchSixFourNucFreq[[i]], sep = '\t', file = generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMismatchSixFourNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE
  ))
}
```

```{r generate_and_write_sequence_enrichment}
threePrimeMMAnchoredCPDEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
  setNames(lapply(seq_along(mismatchDataRep), function(i) {
    getSequenceFreqByReadLengthAndPos(mismatchDataRep[[i]],
                                      nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
                                      c("CG","CA","TG","TA"))
  }), names(mismatchDataRep))
}, threePrimeMismatchAnchoredCPDData, threePrimeMismatchCPDNucFreq, SIMPLIFY = FALSE)
for (i in seq_along(threePrimeMMAnchoredCPDEnrichment)) {
  for (j in seq_along(threePrimeMMAnchoredCPDEnrichment[[i]])) {
    fwrite(threePrimeMMAnchoredCPDEnrichment[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(threePrimeMMAnchoredCPDEnrichment)[i],
      timepoint = names(threePrimeMMAnchoredCPDEnrichment[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR"
    ))
  }
}

fivePrimeMMAnchoredCPDEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
  setNames(lapply(seq_along(mismatchDataRep), function(i) {
    getSequenceFreqByReadLengthAndPos(mismatchDataRep[[i]],
                                      nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
                                      c("TGG"), posType = FIVE_PRIME)
  }), names(mismatchDataRep))
}, fivePrimeMismatchAnchoredCPDData, fivePrimeMismatchCPDNucFreq, SIMPLIFY = FALSE)
for (i in seq_along(fivePrimeMMAnchoredCPDEnrichment)) {
  for (j in seq_along(fivePrimeMMAnchoredCPDEnrichment[[i]])) {
    fwrite(fivePrimeMMAnchoredCPDEnrichment[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMMAnchoredCPDEnrichment)[i],
      timepoint = names(fivePrimeMMAnchoredCPDEnrichment[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG"
    ))
  }
}

threePrimeMMAnchoredSixFourEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
  setNames(lapply(seq_along(mismatchDataRep), function(i) {
    getSequenceFreqByReadLengthAndPos(mismatchDataRep[[i]],
                                      nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
                                      c("CG","CA","TG","TA"))
  }), names(mismatchDataRep))
}, threePrimeMismatchAnchoredSixFourData, threePrimeMismatchSixFourNucFreq, SIMPLIFY = FALSE)
for (i in seq_along(threePrimeMMAnchoredSixFourEnrichment)) {
  for (j in seq_along(threePrimeMMAnchoredSixFourEnrichment[[i]])) {
    fwrite(threePrimeMMAnchoredSixFourEnrichment[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(threePrimeMMAnchoredSixFourEnrichment)[i],
      timepoint = names(threePrimeMMAnchoredSixFourEnrichment[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR"
    ))
  }
}

fivePrimeMMAnchoredSixFourEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
  setNames(lapply(seq_along(mismatchDataRep), function(i) {
    getSequenceFreqByReadLengthAndPos(mismatchDataRep[[i]],
                                      nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
                                      c("TGG"), posType = FIVE_PRIME)
  }), names(mismatchDataRep))
}, fivePrimeMismatchAnchoredSixFourData, fivePrimeMismatchSixFourNucFreq, SIMPLIFY = FALSE)
for (i in seq_along(fivePrimeMMAnchoredSixFourEnrichment)) {
  for (j in seq_along(fivePrimeMMAnchoredSixFourEnrichment[[i]])) {
    fwrite(fivePrimeMMAnchoredSixFourEnrichment[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMMAnchoredSixFourEnrichment)[i],
      timepoint = names(fivePrimeMMAnchoredSixFourEnrichment[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG"
    ))
  }
}
```

```{r generate_and_write_sequence_frequencies}
threePrimeMMAnchoredCPDSeqFreq = lapply(threePrimeMismatchAnchoredCPDData, function(mismatchDataRep) {
  lapply(mismatchDataRep, function(mismatchData) {
    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("CG","CA","TG","TA"))
  })
})
for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
  for (j in seq_along(threePrimeMMAnchoredCPDSeqFreq[[i]])) {
    fwrite(threePrimeMMAnchoredCPDSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(threePrimeMMAnchoredCPDSeqFreq)[i],
      timepoint = names(threePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR"
    ))
  }
}

fivePrimeMMAnchoredCPDSeqFreq = lapply(fivePrimeMismatchAnchoredCPDData, function(mismatchDataRep) {
  lapply(mismatchDataRep, function(mismatchData) {
    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("TGG"), posType = FIVE_PRIME)
  })
})
for (i in seq_along(fivePrimeMMAnchoredCPDSeqFreq)) {
  for (j in seq_along(fivePrimeMMAnchoredCPDSeqFreq[[i]])) {
    fwrite(fivePrimeMMAnchoredCPDSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMMAnchoredCPDSeqFreq)[i],
      timepoint = names(fivePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG"
    ))
  }
}

threePrimeMMAnchoredSixFourSeqFreq = lapply(threePrimeMismatchAnchoredSixFourData, function(mismatchDataRep) {
  lapply(mismatchDataRep, function(mismatchData) {
    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("CG","CA","TG","TA"))
  })
})
for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
  for (j in seq_along(threePrimeMMAnchoredSixFourSeqFreq[[i]])) {
    fwrite(threePrimeMMAnchoredSixFourSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(threePrimeMMAnchoredSixFourSeqFreq)[i],
      timepoint = names(threePrimeMMAnchoredSixFourSeqFreq[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR"
    ))
  }
}

fivePrimeMMAnchoredSixFourSeqFreq = lapply(fivePrimeMismatchAnchoredSixFourData, function(mismatchDataRep) {
  lapply(mismatchDataRep, function(mismatchData) {
    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("TGG"), posType = FIVE_PRIME)
  })
})
for (i in seq_along(fivePrimeMMAnchoredSixFourSeqFreq)) {
  for (j in seq_along(fivePrimeMMAnchoredSixFourSeqFreq[[i]])) {
    fwrite(fivePrimeMMAnchoredSixFourSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMMAnchoredSixFourSeqFreq)[i],
      timepoint = names(fivePrimeMMAnchoredSixFourSeqFreq[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG"
    ))
  }
}
```

### 2022-05-16 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
Notebook OVERHAUL
- Things were way too messy... They could still be better, but this is definitely a step up without spending an exorbitant amount of time restructuring.
- Individual analysis files have been split into two parts (where relevant): Data generation and figure generation. This should allow for more frequent iterating over the specifics of figures.
- File path generation is now standardized using the new UsefulFileSystemFunctions script
- Implemented general standardizations to parameters that are likely to change as we introduce more data. (E.g. cell type and timepoints).

--- 2022-05-11 R/HumanDeaminationReadLengthAnalysis.rmd
@@
 ---
-title: "Human Deamination Read Length Analysis"
+title: "NHF1 Deamination Anchored Excision Site Figure Generation"
 author: "Ben Morledge-Hampton"
@@
 library(knitr)
+
+expansionOffset = 10
+cellType = "NHF1"
+CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
+sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
+
 opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
-               fig.path = paste0(file.path("deamination_analysis_output","human_analysis_figures"),
+               fig.path = paste0(file.path("deamination_analysis_output", cellType,
+                                           "deamination_anchored_excision_site_figures"),
                                  .Platform$file.sep))
@@
 
-deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", "human")
+deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
+deaminationExcisionSiteDataDirectory = file.path(deaminationDataDirectory, "excision_site_analysis")
 ```
@@
 ```{r source_functions}
-source(file.path(bioinformaticsDirectory, "deamination_determination", 'R', "DeaminationAnalysis.R"))
+source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
+                 "UsefulFileSystemFunctions.R"))
+source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
+                 "DeaminationAnchoredExcisionSiteAnalysis.R"))
 ```
 
-```{r get_file_paths}
-expansionOffset = 10
+```{r read_nucleotide_frequency_data}
+threePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL)
+for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
+  threePrimeMismatchCPDNucFreq[[i]] = fread(generateFilePath(
+    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    cellType = cellType, lesion = "CPD", repitition = names(threePrimeMismatchCPDNucFreq)[i],
+    strandPolarity = "three_prime", anchored = TRUE
+  ))
+}
 
-# Get file paths for the expanded mismatch by read data
-expandedCPDMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
-expandedCPDMismatchDataFilePaths$rep1 = list(
-  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                  paste0("NHF1_CPD_1h_Rep1_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
-  hr8 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                  paste0("NHF1_CPD_8h_Rep1_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
-  hr24 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                   paste0("NHF1_CPD_24h_Rep1_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
-  hr48 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                   paste0("NHF1_CPD_48h_Rep1_mismatches_by_read_",expansionOffset,"bp_expanded.bed"))
-)
-expandedCPDMismatchDataFilePaths$rep2 = list(
-  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                  paste0("NHF1_CPD_1h_Rep2_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
-  hr8 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                  paste0("NHF1_CPD_8h_Rep2_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
-  hr24 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                   paste0("NHF1_CPD_24h_Rep2_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
-  hr48 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                   paste0("NHF1_CPD_48h_Rep2_mismatches_by_read_",expansionOffset,"bp_expanded.bed"))
-)
+fivePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL)
+for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
+  fivePrimeMismatchCPDNucFreq[[i]] = fread(generateFilePath(
+    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMismatchCPDNucFreq)[i],
+    strandPolarity = "five_prime", anchored = TRUE
+  ))
+}
 
-expandedSixFourMismatchDataFilePaths = list(rep1 = list(), rep2 = list())
-expandedSixFourMismatchDataFilePaths$rep1 = list(
-  min5 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                   paste0("NHF1_6-4-PP_5min_Rep1_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
-  min20 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                    paste0("NHF1_6-4-PP_20min_Rep1_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
-  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                  paste0("NHF1_6-4-PP_1h_Rep1_mismatches_by_read_",expansionOffset,"bp_expanded.bed"))
-)
-expandedSixFourMismatchDataFilePaths$rep2 = list(
-  min5 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                   paste0("NHF1_6-4-PP_5min_Rep2_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
-  min20 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                    paste0("NHF1_6-4-PP_20min_Rep2_mismatches_by_read_",expansionOffset,"bp_expanded.bed")),
-  hr1 = file.path(deaminationDataDirectory, "mismatches_by_read",
-                  paste0("NHF1_6-4-PP_1h_Rep2_mismatches_by_read_",expansionOffset,"bp_expanded.bed"))
-)
+threePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL)
+for (i in seq_along(threePrimeMismatchSixFourNucFreq)) {
+  threePrimeMismatchSixFourNucFreq[[i]] = fread(generateFilePath(
+    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    cellType = cellType, lesion = "6-4", repitition = names(threePrimeMismatchSixFourNucFreq)[i],
+    strandPolarity = "three_prime", anchored = TRUE
+  ))
+}
+
+fivePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL)
+for (i in seq_along(fivePrimeMismatchSixFourNucFreq)) {
+  fivePrimeMismatchSixFourNucFreq[[i]] = fread(generateFilePath(
+    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMismatchSixFourNucFreq)[i],
+    strandPolarity = "five_prime", anchored = TRUE
+  ))
+}
 ```
 
-```{r acquire_and_format_data}
-expandedCPDSingleCToTMismatchData = lapply(expandedCPDMismatchDataFilePaths, function(x) lapply(x, fread))
-expandedSixFourSingleCToTMismatchData = lapply(expandedSixFourMismatchDataFilePaths, function(x) lapply(x, fread))
-
-# Create a subset of single mismatch C>T reads.
-expandedCPDSingleCToTMismatchData = lapply(expandedCPDSingleCToTMismatchData, function(x) lapply(
-  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = 23, maxReadLength = 31)
-))
-expandedSixFourSingleCToTMismatchData = lapply(expandedSixFourSingleCToTMismatchData, function(x) lapply(
-  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = 23, maxReadLength = 31)
-))
-
-# Simplify the data
-expandedCPDSingleCToTMismatchData = lapply(expandedCPDSingleCToTMismatchData, function(x) lapply(
-  x, function(y) simplifyTable(y, TRUE, expansionOffset = expansionOffset)
-))
-expandedSixFourSingleCToTMismatchData = lapply(expandedSixFourSingleCToTMismatchData, function(x) lapply(
-  x, function(y) simplifyTable(y, TRUE, expansionOffset = expansionOffset)
-))
-
-# Further filter data by read position based on length
-expandedCPDSingleCToTMismatchData = lapply(expandedCPDSingleCToTMismatchData, function(x) {
-  lapply(x, filterMismatchesByPositionAndReadLength, HUMAN_THREE_PRIME_POS_CONSTRAINTS, expansionOffset)
-})
-
-expandedSixFourSingleCToTMismatchData = lapply(expandedSixFourSingleCToTMismatchData, function(x) {
-  lapply(x, filterMismatchesByPositionAndReadLength, HUMAN_THREE_PRIME_POS_CONSTRAINTS, expansionOffset)
-})
-```
-
-```{r orient_data_to_mismatch_positions}
-threePrimeMismatchAnchoredCPDData = lapply(expandedCPDSingleCToTMismatchData, function(x) {
-  lapply(x, orientDataToMismatch, THREE_PRIME, expansionOffset)
-})
-fivePrimeMismatchAnchoredCPDData = lapply(expandedCPDSingleCToTMismatchData, function(x) {
-  lapply(x, orientDataToMismatch, FIVE_PRIME, expansionOffset)
-})
-
-threePrimeMismatchAnchoredSixFourData = lapply(expandedSixFourSingleCToTMismatchData, function(x) {
-  lapply(x, orientDataToMismatch, THREE_PRIME, expansionOffset)
-})
-fivePrimeMismatchAnchoredSixFourData = lapply(expandedSixFourSingleCToTMismatchData, function(x) {
-  lapply(x, orientDataToMismatch, FIVE_PRIME, expansionOffset)
-})
-```
-
-```{r generate_nucleotide_frequency_data}
-threePrimeMismatchCPDNucFreq = lapply(threePrimeMismatchAnchoredCPDData, tabulateNucFreqByPosTimepointAndLength)
-fivePrimeMismatchCPDNucFreq = lapply(fivePrimeMismatchAnchoredCPDData,
-                                     tabulateNucFreqByPosTimepointAndLength, posType = FIVE_PRIME)
-
-threePrimeMismatchSixFourNucFreq = lapply(threePrimeMismatchAnchoredSixFourData,
-                                          tabulateNucFreqByPosTimepointAndLength)
-fivePrimeMismatchSixFourNucFreq = lapply(fivePrimeMismatchAnchoredSixFourData,
-                                         tabulateNucFreqByPosTimepointAndLength, posType = FIVE_PRIME)
-```
-
-```{r CPD_mismatch__anchored_nucleotide_frequencies, fig.width = 11, fig.height = 7}
+```{r CPD_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 7}
 plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
@@
 
-```{r compute_sequence_enrichment}
-threePrimeMMAnchoredCPDEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
-  setNames(lapply(seq_along(mismatchDataRep), function(i) {
-    getSequenceFreqByReadLengthAndPos(mismatchDataRep[[i]],
-                                      nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
-                                      c("CG","CA","TG","TA"))
-  }), names(mismatchDataRep))
-}, threePrimeMismatchAnchoredCPDData, threePrimeMismatchCPDNucFreq, SIMPLIFY = FALSE)
+```{r read_sequence_enrichment_data}
+threePrimeMMAnchoredCPDEnrichment = list(rep1 = CPDTimepoints,
+                                         rep2 = CPDTimepoints)
+for (i in seq_along(threePrimeMMAnchoredCPDEnrichment)) {
+  for (j in seq_along(threePrimeMMAnchoredCPDEnrichment[[i]])) {
+    threePrimeMMAnchoredCPDEnrichment[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
+      cellType = cellType, lesion = "CPD", repitition = names(threePrimeMMAnchoredCPDEnrichment)[i],
+      timepoint = names(threePrimeMMAnchoredCPDEnrichment[[i]])[j], strandPolarity = "three_prime",
+      anchored = TRUE, sequence = "YR"
+    ))
+  }
+}
 
-fivePrimeMMAnchoredCPDEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
-  setNames(lapply(seq_along(mismatchDataRep), function(i) {
-    getSequenceFreqByReadLengthAndPos(mismatchDataRep[[i]],
-                                      nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
-                                      c("TGG"), posType = FIVE_PRIME)
-  }), names(mismatchDataRep))
-}, fivePrimeMismatchAnchoredCPDData, fivePrimeMismatchCPDNucFreq, SIMPLIFY = FALSE)
+fivePrimeMMAnchoredCPDEnrichment = list(rep1 = CPDTimepoints,
+                                        rep2 = CPDTimepoints)
+for (i in seq_along(fivePrimeMMAnchoredCPDEnrichment)) {
+  for (j in seq_along(fivePrimeMMAnchoredCPDEnrichment[[i]])) {
+    fivePrimeMMAnchoredCPDEnrichment[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
+      cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMMAnchoredCPDEnrichment)[i],
+      timepoint = names(fivePrimeMMAnchoredCPDEnrichment[[i]])[j], strandPolarity = "five_prime",
+      anchored = TRUE, sequence = "TGG"
+    ))
+  }
+}
 
-threePrimeMMAnchoredSixFourEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
-  setNames(lapply(seq_along(mismatchDataRep), function(i) {
-    getSequenceFreqByReadLengthAndPos(mismatchDataRep[[i]],
-                                      nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
-                                      c("CG","CA","TG","TA"))
-  }), names(mismatchDataRep))
-}, threePrimeMismatchAnchoredSixFourData, threePrimeMismatchSixFourNucFreq, SIMPLIFY = FALSE)
+threePrimeMMAnchoredSixFourEnrichment = list(rep1 = sixFourTimepoints,
+                                             rep2 = sixFourTimepoints)
+for (i in seq_along(threePrimeMMAnchoredSixFourEnrichment)) {
+  for (j in seq_along(threePrimeMMAnchoredSixFourEnrichment[[i]])) {
+    threePrimeMMAnchoredSixFourEnrichment[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
+      cellType = cellType, lesion = "6-4", repitition = names(threePrimeMMAnchoredSixFourEnrichment)[i],
+      timepoint = names(threePrimeMMAnchoredSixFourEnrichment[[i]])[j], strandPolarity = "three_prime",
+      anchored = TRUE, sequence = "YR"
+    ))
+  }
+}
 
-fivePrimeMMAnchoredSixFourEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
-  setNames(lapply(seq_along(mismatchDataRep), function(i) {
-    getSequenceFreqByReadLengthAndPos(mismatchDataRep[[i]],
-                                      nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
-                                      c("TGG"), posType = FIVE_PRIME)
-  }), names(mismatchDataRep))
-}, fivePrimeMismatchAnchoredSixFourData, fivePrimeMismatchSixFourNucFreq, SIMPLIFY = FALSE)
+fivePrimeMMAnchoredSixFourEnrichment = list(rep1 = sixFourTimepoints,
+                                            rep2 = sixFourTimepoints)
+for (i in seq_along(fivePrimeMMAnchoredSixFourEnrichment)) {
+  for (j in seq_along(fivePrimeMMAnchoredSixFourEnrichment[[i]])) {
+    fivePrimeMMAnchoredSixFourEnrichment[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
+      cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMMAnchoredSixFourEnrichment)[i],
+      timepoint = names(fivePrimeMMAnchoredSixFourEnrichment[[i]])[j], strandPolarity = "five_prime",
+      anchored = TRUE, sequence = "TGG"
+    ))
+  }
+}
 ```
@@
 plotSequenceEnrichment(threePrimeMMAnchoredSixFourEnrichment$rep1,
-                       title = "CPD 3' Anchored YR Enrichment Rep1", secondaryYAxisLabel = "5' Cut Site Distance",
+                       title = "6-4 3' Anchored YR Enrichment Rep1", secondaryYAxisLabel = "5' Cut Site Distance",
                        showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
@@
 plotSequenceEnrichment(threePrimeMMAnchoredSixFourEnrichment$rep2,
-                       title = "CPD 3' Anchored YR Enrichment Rep2", secondaryYAxisLabel = "5' Cut Site Distance",
+                       title = "6-4 3' Anchored YR Enrichment Rep2", secondaryYAxisLabel = "5' Cut Site Distance",
                        showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
@@
 plotSequenceEnrichment(fivePrimeMMAnchoredSixFourEnrichment$rep1,
-                       title = "CPD 5' Anchored TGG Enrichment Rep1", secondaryYAxisLabel = "3' Cut Site Distance",
+                       title = "6-4 5' Anchored TGG Enrichment Rep1", secondaryYAxisLabel = "3' Cut Site Distance",
                        showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
@@
 plotSequenceEnrichment(fivePrimeMMAnchoredSixFourEnrichment$rep2,
-                       title = "CPD 5' Anchored TGG Enrichment Rep2", secondaryYAxisLabel = "3' Cut Site Distance",
+                       title = "6-4 5' Anchored TGG Enrichment Rep2", secondaryYAxisLabel = "3' Cut Site Distance",
                        showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
@@
 
-```{r compute_sequence_frequencies}
-threePrimeMMAnchoredCPDSeqFreq = lapply(threePrimeMismatchAnchoredCPDData, function(mismatchDataRep) {
-  lapply(mismatchDataRep, function(mismatchData) {
-    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("CG","CA","TG","TA"))
-  })
-})
+```{r read_sequence_frequency_data}
+threePrimeMMAnchoredCPDSeqFreq = list(rep1 = CPDTimepoints,
+                                      rep2 = CPDTimepoints)
+for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
+  for (j in seq_along(threePrimeMMAnchoredCPDSeqFreq[[i]])) {
+    threePrimeMMAnchoredCPDSeqFreq[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      cellType = cellType, lesion = "CPD", repitition = names(threePrimeMMAnchoredCPDSeqFreq)[i],
+      timepoint = names(threePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "three_prime",
+      anchored = TRUE, sequence = "YR"
+    ))
+  }
+}
 
-fivePrimeMMAnchoredCPDSeqFreq = lapply(fivePrimeMismatchAnchoredCPDData, function(mismatchDataRep) {
-  lapply(mismatchDataRep, function(mismatchData) {
-    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("TGG"), posType = FIVE_PRIME)
-  })
-})
+fivePrimeMMAnchoredCPDSeqFreq = list(rep1 = CPDTimepoints,
+                                     rep2 = CPDTimepoints)
+for (i in seq_along(fivePrimeMMAnchoredCPDSeqFreq)) {
+  for (j in seq_along(fivePrimeMMAnchoredCPDSeqFreq[[i]])) {
+    fivePrimeMMAnchoredCPDSeqFreq[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMMAnchoredCPDSeqFreq)[i],
+      timepoint = names(fivePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "five_prime",
+      anchored = TRUE, sequence = "TGG"
+    ))
+  }
+}
 
-threePrimeMMAnchoredSixFourSeqFreq = lapply(threePrimeMismatchAnchoredSixFourData, function(mismatchDataRep) {
-  lapply(mismatchDataRep, function(mismatchData) {
-    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("CG","CA","TG","TA"))
-  })
-})
+threePrimeMMAnchoredSixFourSeqFreq = list(rep1 = sixFourTimepoints,
+                                          rep2 = sixFourTimepoints)
+for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
+  for (j in seq_along(threePrimeMMAnchoredSixFourSeqFreq[[i]])) {
+    threePrimeMMAnchoredSixFourSeqFreq[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      cellType = cellType, lesion = "6-4", repitition = names(threePrimeMMAnchoredSixFourSeqFreq)[i],
+      timepoint = names(threePrimeMMAnchoredSixFourSeqFreq[[i]])[j], strandPolarity = "three_prime",
+      anchored = TRUE, sequence = "YR"
+    ))
+  }
+}
 
-fivePrimeMMAnchoredSixFourSeqFreq = lapply(fivePrimeMismatchAnchoredSixFourData, function(mismatchDataRep) {
-  lapply(mismatchDataRep, function(mismatchData) {
-    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("TGG"), posType = FIVE_PRIME)
-  })
-})
+fivePrimeMMAnchoredSixFourSeqFreq = list(rep1 = sixFourTimepoints,
+                                         rep2 = sixFourTimepoints)
+for (i in seq_along(fivePrimeMMAnchoredSixFourSeqFreq)) {
+  for (j in seq_along(fivePrimeMMAnchoredSixFourSeqFreq[[i]])) {
+    fivePrimeMMAnchoredSixFourSeqFreq[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMMAnchoredSixFourSeqFreq)[i],
+      timepoint = names(fivePrimeMMAnchoredSixFourSeqFreq[[i]])[j], strandPolarity = "five_prime",
+      anchored = TRUE, sequence = "TGG"
+    ))
+  }
+}
 ```
@@
 plotSequenceFrequencies(threePrimeMMAnchoredSixFourSeqFreq$rep1,
-                        title = "CPD 3' Anchored YR Frequency Rep1", secondaryYAxisLabel = "5' Cut Site Distance",
+                        title = "6-4 3' Anchored YR Frequency Rep1", secondaryYAxisLabel = "5' Cut Site Distance",
                         showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
@@
 plotSequenceFrequencies(threePrimeMMAnchoredSixFourSeqFreq$rep2,
-                        title = "CPD 3' Anchored YR Frequency Rep2", secondaryYAxisLabel = "5' Cut Site Distance",
+                        title = "6-4 3' Anchored YR Frequency Rep2", secondaryYAxisLabel = "5' Cut Site Distance",
                         showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
@@
 plotSequenceFrequencies(fivePrimeMMAnchoredSixFourSeqFreq$rep1,
-                        title = "CPD 5' Anchored TGG Frequency Rep1", secondaryYAxisLabel = "3' Cut Site Distance",
+                        title = "6-4 5' Anchored TGG Frequency Rep1", secondaryYAxisLabel = "3' Cut Site Distance",
                         showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
@@
 plotSequenceFrequencies(fivePrimeMMAnchoredSixFourSeqFreq$rep2,
-                        title = "CPD 5' Anchored TGG Frequency Rep2", secondaryYAxisLabel = "3' Cut Site Distance",
+                        title = "6-4 5' Anchored TGG Frequency Rep2", secondaryYAxisLabel = "3' Cut Site Distance",
                         showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,

### 2022-05-16 R/NHF1DeaminationPeriodicityAnalysis.rmd
Notebook OVERHAUL
- Things were way too messy... They could still be better, but this is definitely a step up without spending an exorbitant amount of time restructuring.
- Individual analysis files have been split into two parts (where relevant): Data generation and figure generation. This should allow for more frequent iterating over the specifics of figures.
- File path generation is now standardized using the new UsefulFileSystemFunctions script
- Implemented general standardizations to parameters that are likely to change as we introduce more data. (E.g. cell type and timepoints).

--- 2022-05-03 R/HumanDeaminationPeriodicityAnalysis.rmd
@@
 ---
-title: "Human Deamination Periodicity Analysis"
+title: "NHF1 Deamination Periodicity Analysis"
 author: "Ben Morledge-Hampton"
@@
 library(knitr)
+
+cellType = "NHF1"
+
 opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
-               fig.path = paste0(file.path("deamination_analysis_output","human_analysis_figures"),
+               fig.path = paste0(file.path("deamination_analysis_output", cellType,
+                                           "deamination_periodicity_figures"),
                                  .Platform$file.sep))
@@
 
-deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", "human")
+deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
+deaminationPeriodicityDataDirectory = file.path(deaminationDataDirectory, "nucleosome_periodicity")
 ```
@@
 ```{r source_functions}
+source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
+                 "UsefulFileSystemFunctions.R"))
 source(file.path(bioinformaticsDirectory, "Chromatin_Features_Analysis", "R_scripts", "PeriodicityAnalysis.R"))
@@
 
-```{r acquire_and_format_data_1}
-load(file.path(deaminationDataDirectory, "periodicity_results", "NHF1_deamination_periodicity_results.rda"))
+```{r read_periodicity_data_1}
+load(generateFilePath(deaminationPeriodicityDataDirectory, dataTypeStrings$nucleosomePeriodicity, ".rda",
+                      cellType = cellType))
 dataSetNames = as.list(setNames(nm = mutperiodData$periodicityResults$Data_Set))
@@
 ```{r acquire_and_format_data_2}
-load(file.path(deaminationDataDirectory, "periodicity_results", "NHF1_TCG_deamination_periodicity_results.rda"))
+load(generateFilePath(deaminationPeriodicityDataDirectory, dataTypeStrings$nucleosomePeriodicity, ".rda",
+                      cellType = cellType, includedMismatches = "TCG"))
 dataSetNames = as.list(setNames(nm = mutperiodData$periodicityResults$Data_Set))
-
 ```

### 2022-05-16 R/NHF1DeaminationSequenceAndPositionDataGeneration.rmd
Notebook OVERHAUL
- Things were way too messy... They could still be better, but this is definitely a step up without spending an exorbitant amount of time restructuring.
- Individual analysis files have been split into two parts (where relevant): Data generation and figure generation. This should allow for more frequent iterating over the specifics of figures.
- File path generation is now standardized using the new UsefulFileSystemFunctions script
- Implemented general standardizations to parameters that are likely to change as we introduce more data. (E.g. cell type and timepoints).

---
title: "NHF1 Deamination Sequence and Position Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

```{r setup_chunk}
library(knitr)

cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
}

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
mismatchesByReadDirectory = file.path(deaminationDataDirectory, "mismatches_by_read")
deaminationSequenceAndPositionDataDirectory = file.path(deaminationDataDirectory,"sequence_and_position_analysis")
dir.create(deaminationSequenceAndPositionDataDirectory, recursive = TRUE, showWarnings = FALSE)
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationParseAndFilter.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationSequenceAndPositionAnalysis.R"))
```

```{r read_mismatch_data}
# Get file paths for the mismatch by read data
CPDMismatchData = list(rep1 = CPDTimepoints,
                       rep2 = CPDTimepoints)
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    CPDMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
      repitition = names(CPDMismatchData)[i]
      ))
  }
}

sixFourMismatchData = list(rep1 = sixFourTimepoints,
                           rep2 = sixFourTimepoints)
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "6-4-PP", timepoint = names(sixFourMismatchData[[i]])[j],
      repitition = names(sixFourMismatchData)[i]
      ))
  }
}
```

```{r generate_and_write_simplified_and_filtered_mismatch_data}
# Perform general filtering on the data
CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
  x, function(y) filterResults(y, TRUE, 3, 23, 31)
))
sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
  x, function(y) filterResults(y, TRUE, 3, 23, 31)
))

# Simplify the data
CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
  x, function(y) simplifyTable(y, includeTrinucleotideContext = TRUE)
))
sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
  x, function(y) simplifyTable(y, includeTrinucleotideContext = TRUE)
))

for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    fwrite(CPDMismatchData[[i]][[j]], sep = '\t',
           file = generateFilePath(
             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
             cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
             repitition = names(CPDMismatchData)[i]
           ))
  }
}

for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    fwrite(sixFourMismatchData[[i]][[j]], sep = '\t',
           file = generateFilePath(
             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
             cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
             repitition = names(sixFourMismatchData)[i]
           ))
  }
}
```

```{r generate_and_write_mismatch_position_statistics_by_read_length_and_timepoint}
CPDGroupedStats = list(rep1 = list(), rep2 = list())
CPDGroupedStats$rep1$three_prime = getGroupedPositionStats(CPDMismatchData$rep1, includedTypes = c("C>T"))
CPDGroupedStats$rep2$three_prime = getGroupedPositionStats(CPDMismatchData$rep2, includedTypes = c("C>T"))
CPDGroupedStats$rep1$five_prime =
  getGroupedPositionStats(CPDMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME)
CPDGroupedStats$rep2$five_prime =
  getGroupedPositionStats(CPDMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME)

sixFourGroupedStats = list(rep1 = list(), rep2 = list())
sixFourGroupedStats$rep1$three_prime = getGroupedPositionStats(sixFourMismatchData$rep1, includedTypes = c("C>T"))
sixFourGroupedStats$rep2$three_prime = getGroupedPositionStats(sixFourMismatchData$rep2, includedTypes = c("C>T"))
sixFourGroupedStats$rep1$five_prime =
  getGroupedPositionStats(sixFourMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME)
sixFourGroupedStats$rep2$five_prime =
  getGroupedPositionStats(sixFourMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME)

for (i in seq_along(CPDGroupedStats)) {
  for (j in seq_along(CPDGroupedStats[[i]])) {
    fwrite(CPDGroupedStats[[i]][[j]], sep = '\t',
           file = generateFilePath(
             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
             cellType = cellType, lesion = "CPD", repitition = names(CPDGroupedStats)[i],
             strandPolarity = names(CPDGroupedStats[[i]])[j]
           ))
  }
}

for (i in seq_along(sixFourGroupedStats)) {
  for (j in seq_along(sixFourGroupedStats[[i]])) {
    fwrite(sixFourGroupedStats[[i]][[j]], sep = '\t',
           file = generateFilePath(
             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
             cellType = cellType, lesion = "6-4", repitition = names(sixFourGroupedStats)[i],
             strandPolarity = names(sixFourGroupedStats[[i]])[j]
           ))
  }
}
```

### 2022-05-16 R/NHF1DeaminationSequenceAndPositionFigureGeneration.rmd
Notebook OVERHAUL
- Things were way too messy... They could still be better, but this is definitely a step up without spending an exorbitant amount of time restructuring.
- Individual analysis files have been split into two parts (where relevant): Data generation and figure generation. This should allow for more frequent iterating over the specifics of figures.
- File path generation is now standardized using the new UsefulFileSystemFunctions script
- Implemented general standardizations to parameters that are likely to change as we introduce more data. (E.g. cell type and timepoints).

---
title: "NHF1 Deamination Sequence and Position Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

```{r setup_chunk}
library(knitr)

cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)

opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
               fig.path = paste0(file.path("deamination_analysis_output",cellType,
                                           "deamination_sequence_and_position_figures"),
                                 .Platform$file.sep))
if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
}

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
deaminationSequenceAndPositionDataDirectory = file.path(deaminationDataDirectory,"sequence_and_position_analysis")
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationSequenceAndPositionAnalysis.R"))
```

```{r read_simplified_mismatch_data}
# Get file paths for the mismatch by read data
CPDMismatchData = list(rep1 = CPDTimepoints,
                       rep2 = CPDTimepoints)
for (i in seq_along(CPDMismatchData)) {
  for (j in seq_along(CPDMismatchData[[i]])) {
    CPDMismatchData[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
      cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
      repitition = names(CPDMismatchData)[i]
    ))
  }
}

sixFourMismatchData = list(rep1 = sixFourTimepoints,
                           rep2 = sixFourTimepoints)
for (i in seq_along(sixFourMismatchData)) {
  for (j in seq_along(sixFourMismatchData[[i]])) {
    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
      cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
      repitition = names(sixFourMismatchData)[i]
    ))
  }
}
```

```{r CPD_mismatch_type_frequency}
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    plotMismatchTypeFrequencies(CPDMismatchData[[i]][[j]],
                                title = paste("CPD", names(CPDMismatchData)[i], 
                                              names(CPDMismatchData[[i]])[j], "Mismatch Type Frequency"))
  }
}
```

```{r 6-4_mismatch_type_frequency}
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    plotMismatchTypeFrequencies(sixFourMismatchData[[i]][[j]],
                                title = paste("6-4", names(sixFourMismatchData)[i], 
                                              names(sixFourMismatchData[[i]])[j], "Mismatch Type Frequency"))
  }
}
```

```{r CPD_mismatch_pos_frequency}
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], includedTypes = c("C>T"),
                                    title = paste("CPD", names(CPDMismatchData)[i], 
                                                  names(CPDMismatchData[[i]])[j], "C>T Mismatch Positions"))
    plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], omittedTypes = c("C>T"),
                                    title = paste("CPD", names(CPDMismatchData)[i], 
                                                  names(CPDMismatchData[[i]])[j], "!C>T Mismatch Positions"))
  }
}
```

```{r 6-4_mismatch_pos_frequency}
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], includedTypes = c("C>T"),
                                    title = paste("6-4", names(sixFourMismatchData)[i], 
                                                  names(sixFourMismatchData[[i]])[j], "C>T Mismatch Positions"))
    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], omittedTypes = c("C>T"),
                                    title = paste("6-4", names(sixFourMismatchData)[i], 
                                                  names(sixFourMismatchData[[i]])[j], "!C>T Mismatch Positions"))
  }
}
```

```{r CPD_trinucleotide_context_analysis}
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    plotTrinucleotideContext(CPDMismatchData[[i]][[j]], includedTypes = c("C>T"),
                             title = paste("CPD", names(CPDMismatchData)[i], names(CPDMismatchData[[i]])[j],
                                           "C>T Mismatch Trinuc Context"))
  }
}
```

```{r 6-4_trinucleotide_context_analysis}
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    plotTrinucleotideContext(sixFourMismatchData[[i]][[j]], includedTypes = c("C>T"),
                             title = paste("6-4", names(sixFourMismatchData)[i], names(sixFourMismatchData[[i]])[j],
                                           "C>T Mismatch Trinuc Context"))
  }
}
```

```{r CPD_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, includedTypes = c("C>T"),
                                         title = "CPD C>T Mismatch Pos Freq Rep1")
plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, includedTypes = c("C>T"),
                                         title = "CPD C>T Mismatch Pos Freq Rep2")
plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, includedTypes = c("C>T"),
                                         title = "CPD C>T Mismatch Pos Freq Rep1", posType = FIVE_PRIME)
plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, includedTypes = c("C>T"),
                                         title = "CPD C>T Mismatch Pos Freq Rep2", posType = FIVE_PRIME)
```

```{r 6-4_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, includedTypes = c("C>T"),
                                         title = "6-4 C>T Mismatch Pos Freq Rep1")
plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, includedTypes = c("C>T"),
                                         title = "6-4 C>T Mismatch Pos Freq Rep2")
plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, includedTypes = c("C>T"),
                                         title = "6-4 C>T Mismatch Pos Freq Rep1", posType = FIVE_PRIME)
plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, includedTypes = c("C>T"),
                                         title = "6-4 C>T Mismatch Pos Freq Rep2", posType = FIVE_PRIME)
```

```{r read_mismatch_position_statistics}
CPDGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
                       rep2 = list(three_prime = NULL, five_prime = NULL))
for (i in seq_along(CPDGroupedStats)) {
  for (j in seq_along(CPDGroupedStats[[i]])) {
    CPDGroupedStats[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDGroupedStats)[i],
      strandPolarity = names(CPDGroupedStats[[i]])[j]
    ))
  }
}

sixFourGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
                           rep2 = list(three_prime = NULL, five_prime = NULL))
for (i in seq_along(sixFourGroupedStats)) {
  for (j in seq_along(sixFourGroupedStats[[i]])) {
    sixFourGroupedStats[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourGroupedStats)[i],
      strandPolarity = names(sixFourGroupedStats[[i]])[j]
    ))
  }
}
```

```{r CPD_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, POS_DIFF,
                         title = "CPD C>T Mismatch Pos Diff Rep1",
                         xAxisBreaks = c(23:31))
plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, POS_DIFF,
                         title = "CPD C>T Mismatch Pos Diff Rep2",
                         xAxisBreaks = c(23:31))
```

```{r 6-4_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, POS_DIFF,
                         title = "6-4 C>T Mismatch Pos Diff Rep1",
                         xAxisBreaks = c(23:31))
plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, POS_DIFF,
                         title = "6-4 C>T Mismatch Pos Diff Rep2",
                         xAxisBreaks = c(23:31))
```

### 2022-05-19 R/NHF1DeaminationAnchoredExcisionSiteDataGeneration.rmd
R notebook updates
- General updates to existing R notebooks
- Added two new notebooks for general read analysis (Looking at sequence frequencies associated with mispriming).

@@
 }
+if (is.na(bioinformaticsDirectory)) stop("No bioinformatics directory given.")
 

### 2022-05-19 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
R notebook updates
- General updates to existing R notebooks
- Added two new notebooks for general read analysis (Looking at sequence frequencies associated with mispriming).

@@
 sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
+filtering = character()
 

### 2022-05-19 R/NHF1DeaminationSequenceAndPositionFigureGeneration.rmd
R notebook updates
- General updates to existing R notebooks
- Added two new notebooks for general read analysis (Looking at sequence frequencies associated with mispriming).

@@
 
+```{r CPD_read_length_distributions}
+plotReadLengthFrequencies(CPDMismatchData$rep1, title = "CPD Read Length Freq Rep 1")
+plotReadLengthFrequencies(CPDMismatchData$rep2, title = "CPD Read Length Freq Rep 2")
+```
+
+```{r 6-4_read_length_distributions}
+plotReadLengthFrequencies(sixFourMismatchData$rep1, title = "6-4 Read Length Freq Rep 1")
+plotReadLengthFrequencies(sixFourMismatchData$rep2, title = "6-4 Read Length Freq Rep 2")
+```
+
 ```{r read_mismatch_position_statistics}

### 2022-05-19 R/NHF1GeneralReadSequenceDataGeneration.rmd
R notebook updates
- General updates to existing R notebooks
- Added two new notebooks for general read analysis (Looking at sequence frequencies associated with mispriming).

---
title: "NHF1 General Read Sequence Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

```{r setup_chunk}
library(knitr)

expansionOffset = 10
cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
}

if (is.na(bioinformaticsDirectory)) stop("No bioinformatics directory given.")

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
generalReadSequenceDataDirectory = file.path(deaminationDataDirectory, "general_read_sequences")
dir.create(generalReadSequenceDataDirectory, showWarnings = FALSE, recursive = TRUE)
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationAnchoredExcisionSiteAnalysis.R"))
```

```{r define_all_that_and_a_bag_of_chips_function}
singleFileFullAnalysis = function(lesion, repitition, timepoint) {
  readData = fread(generateFilePath(
    generalReadSequenceDataDirectory, dataTypeStrings$alignedReads, ".bed",
    cellType = cellType, lesion = lesion, timepoint = timepoint,
    repitition = repitition, expansionNum = expansionOffset
  ))
  readData = data.table(Read_Length = nchar(readData$V7)-expansionOffset*2, Read_Sequence = readData$V7)
  readData = readData[Read_Length >= 23 & Read_Length <= 31]

  for (sequence in c("TGG","CGA")) {
    seqFreq = getSequenceFreqByReadLengthAndPos(readData, querySequences = c(sequence))
    fwrite(seqFreq, sep = '\t', file = generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = lesion, repitition = repitition,
      timepoint = timepoint, sequence = sequence
    ))
  }
}
```

```{r compute_and_write_CPD_sequence_frequency}
for (repitition in c("rep1", "rep2")) {
  for (timepoint in names(CPDTimepoints)) {
    singleFileFullAnalysis("CPD", repitition, timepoint)
  }
}
```

```{r compute_and_write_6-4_sequence_frequency}
for (repitition in c("rep1", "rep2")) {
  for (timepoint in names(sixFourTimepoints)) {
    singleFileFullAnalysis("6-4", repitition, timepoint)
  }
}
```

### 2022-05-19 R/NHF1GeneralReadSequenceFigureGeneration.rmd
R notebook updates
- General updates to existing R notebooks
- Added two new notebooks for general read analysis (Looking at sequence frequencies associated with mispriming).

---
title: "NHF1 General Read Sequence Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

```{r setup_chunk}
library(knitr)

expansionOffset = 10
cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)

opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5,
               fig.path = paste0(file.path("deamination_analysis_output", cellType,
                                           "general_read_analysis_figures"),
                                 .Platform$file.sep))
if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
}

if (is.na(bioinformaticsDirectory)) stop("No bioinformatics directory given.")

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
generalReadSequenceDataDirectory = file.path(deaminationDataDirectory, "general_read_sequences")
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationAnchoredExcisionSiteAnalysis.R"))
```

```{r read_sequence_frequencies}
CPDTGGSeqFreq = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
for (i in seq_along(CPDTGGSeqFreq)) {
  for (j in seq_along(CPDTGGSeqFreq[[i]])) {
    CPDTGGSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDTGGSeqFreq)[i],
      timepoint = names(CPDTGGSeqFreq[[i]])[j], sequence = "TGG"
    ))
  }
}

CPDCGASeqFreq = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
for (i in seq_along(CPDCGASeqFreq)) {
  for (j in seq_along(CPDCGASeqFreq[[i]])) {
    CPDCGASeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDCGASeqFreq)[i],
      timepoint = names(CPDCGASeqFreq[[i]])[j], sequence = "CGA"
    ))
  }
}

sixFourTGGSeqFreq = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
for (i in seq_along(sixFourTGGSeqFreq)) {
  for (j in seq_along(sixFourTGGSeqFreq[[i]])) {
    sixFourTGGSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourTGGSeqFreq)[i],
      timepoint = names(sixFourTGGSeqFreq[[i]])[j], sequence = "TGG"
    ))
  }
}

sixFourCGASeqFreq = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
for (i in seq_along(sixFourCGASeqFreq)) {
  for (j in seq_along(sixFourCGASeqFreq[[i]])) {
    sixFourCGASeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourCGASeqFreq)[i],
      timepoint = names(sixFourCGASeqFreq[[i]])[j], sequence = "CGA"
    ))
  }
}
```

```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 7}
plotSequenceFrequencies(CPDTGGSeqFreq$rep1,
                        title = "CPD TGG Frequencies Rep1", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))
plotSequenceFrequencies(CPDTGGSeqFreq$rep2,
                        title = "CPD TGG Frequencies Rep2", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))

plotSequenceFrequencies(CPDCGASeqFreq$rep1,
                        title = "CPD CGA Frequencies Rep1", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("CGA"))
plotSequenceFrequencies(CPDCGASeqFreq$rep2,
                        title = "CPD CGA Frequencies Rep2", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("CGA"))
```

```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 7}
plotSequenceFrequencies(sixFourTGGSeqFreq$rep1,
                        title = "6-4 TGG Frequencies Rep1", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))
plotSequenceFrequencies(sixFourTGGSeqFreq$rep2,
                        title = "6-4 TGG Frequencies Rep2", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))

plotSequenceFrequencies(sixFourCGASeqFreq$rep1,
                        title = "6-4 CGA Frequencies Rep1", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("CGA"))
plotSequenceFrequencies(sixFourCGASeqFreq$rep2,
                        title = "6-4 CGA Frequencies Rep2", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("CGA"))
```

### 2022-05-19 R/DeaminationSequenceAndPositionAnalysis.R

@@ -128,6 +128,48 @@ plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTy
 }
 
 
+# Plot read length frequencies across timepoint (optional).
+# Input should be a list of data.tables with names as timepoint information, or a single data.table
+# to construct a plot without timepoint information.
+plotReadLengthFrequencies = function(simplifiedTables, title = "Read Length Frequencies") {
+
+  xAxisBreaks = c(23,27,31)
+
+  #If passed a single data.table, wrap it in a list.
+  if (is.data.table(simplifiedTables)) {
+    simplifiedTables = list(None = simplifiedTables)
+    noTimepointInfo = TRUE
+  } else noTimepointInfo = FALSE
+
+  aggregateTable = rbindlist(lapply(seq_along(simplifiedTables),
+                                    function(i) simplifiedTables[[i]][,Timepoint := names(simplifiedTables)[i]]))
+
+  readLengthFrequencies = (aggregateTable[, .N, by = list(Read_Length,Timepoint)]
+                                         [, Freq := N/sum(N), by = list(Timepoint)])
+  maxFrequency = round(max(readLengthFrequencies$Freq), digits = 2)
+  yAxisBreaks = c(0, maxFrequency/2, maxFrequency)
+
+  plot = ggplot(readLengthFrequencies, aes(Read_Length, Freq)) +
+    geom_bar(stat = "identity") +
+    labs(title = title, x = "Read_Length", y = "Frequency") +
+    blankBackground + defaultTextScaling
+
+  if (!noTimepointInfo) {
+    plot = plot + facet_grid(cols = vars(Timepoint))
+  }
+
+  plot = plot +
+    theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
+          strip.background = element_rect(color = "black", size = 1),
+          axis.text.y = element_text(size = 16), strip.text.y = element_text(size = 16)) +
+    scale_x_continuous(breaks = xAxisBreaks) +
+    scale_y_continuous(breaks = yAxisBreaks)
+
+  print(plot)
+
+}
+
+
 # Gets the mode. (Why isn't there a base R function for this?)
 getMode = function(values) {
   frequencyTable = table(values)

### 2022-05-19 R/UsefulFileSystemFunctions.R
UFSF theory-crafting

@@ -1,4 +1,5 @@
 library(stringr)
+library(data.table)
 
 # A list containing the strings designated to files containing a specific type of data.
 dataTypeStrings =
@@ -39,3 +40,23 @@ generateFilePath = function(directory, dataTypeString, fileExtension,
   return(file.path(directory,paste0(paste(basenameParts,collapse = '_'),fileExtension)))
 
 }
+
+
+# Reads in data using fread and the generateFilePath function, but with a twist:
+# Parameters can be passed as lists, and when they are, the returned data object
+# will be a list (potentially a list of lists) with names/tiers corresponding to the different parameters.
+# NOTE: Currently only supports stratification by timepoint and repitition.
+# NOTE NOTE: This really would be easier with a class structure for data objects.
+readData = function(directory, dataTypeString, fileExtension,
+                    cellType = NA, lesion = NA, timepoint = NA, repitition = NA,
+                    includedMismatches = character(), omittedMismatches = character(),
+                    strandPolarity = NA, anchored = F, sequence = NA, expansionNum = NA,
+                    additionalInformation = character(), filterText = NA) {
+
+}
+
+
+# Writes data using the given parameters, but with a fun and exciting twist:
+# If the input data is in list format with names corresponding to parameters,
+# ?????? How will this work ??????
+

### 2022-05-20 R/NHF1DeaminationAnchoredExcisionSiteDataGeneration.rmd
I should have made more intermediate commits
- Added options for filtering (e.g. TGG filtering) as knitting parameters and interactive input.
- Changed mismatch frequency peak calling process to utilize individual positions' z-scores.
- Integrated mismatch frequency z-scores into mismatch frequency plotting.
- Lots of other bugfixes and tweaks. Hopefully the whole project is in a steady-state right now.

--- 2022-05-16 R/NHF1DeaminationAnchoredExcisionSiteDataGeneration.rmd
@@
     choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
+  filtering:
+    label: "Filtering"
+    value: NONE
+    input: select
+    choices: [NONE, TGG_filtered]
 ---
@@
 
-opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5,
-               fig.path = paste0(file.path("deamination_analysis_output", cellType,
-                                           "deamination_anchored_excision_site_figures"),
-                                 .Platform$file.sep))
 if (interactive()) {
   bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
+  filtering = readline("Filtering identifier (Input nothing for no filtering):")
+  if (filtering == '') filtering = character()
 } else {
   bioinformaticsDirectory = params$bioinformaticsDirectory
+  filtering = params$filtering
+  if (filtering == "NONE") filtering = character()
 }
+if (is.na(bioinformaticsDirectory)) stop("No bioinformatics directory given.")
 
@@
 mismatchesByReadDirectory = file.path(deaminationDataDirectory, "mismatches_by_read")
+deaminationSequenceAndPositionDataDirectory = file.path(deaminationDataDirectory,"sequence_and_position_analysis")
 deaminationExcisionSiteDataDirectory = file.path(deaminationDataDirectory, "excision_site_analysis")
@@
       cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
-      repitition = names(CPDMismatchData)[i], expansionNum = expansionOffset
+      repitition = names(CPDMismatchData)[i], expansionNum = expansionOffset, filtering = filtering
       ))
@@
       cellType = cellType, lesion = "6-4-PP", timepoint = names(sixFourMismatchData[[i]])[j],
-      repitition = names(sixFourMismatchData)[i], expansionNum = expansionOffset
+      repitition = names(sixFourMismatchData)[i], expansionNum = expansionOffset, filtering = filtering
       ))
@@
 
-# Determine the peak positions to filter on for each read length in each data set.
-CPDPeakPositions = lapply(CPDMismatchData, function(x) lapply(
-  x, getPeakPositionsByReadLength, expansionOffset
+# Read mismatch frequency z-scores.
+CPDMMFreqZScores = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
+for (i in seq_along(CPDMMFreqZScores)) {
+  for (j in seq_along(CPDMMFreqZScores[[i]])) {
+    CPDMMFreqZScores[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+      cellType = cellType, lesion = "CPD", repitition = names(CPDMMFreqZScores)[i],
+      timepoint = names(CPDMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
     ))
-sixFourPeakPositions = lapply(sixFourMismatchData, function(x) lapply(
-  x, getPeakPositionsByReadLength, expansionOffset
+  }
+}
+
+sixFourMMFreqZScores = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
+for (i in seq_along(sixFourMMFreqZScores)) {
+  for (j in seq_along(sixFourMMFreqZScores[[i]])) {
+    sixFourMMFreqZScores[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+      cellType = cellType, lesion = "6-4", repitition = names(sixFourMMFreqZScores)[i],
+      timepoint = names(sixFourMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
     ))
+  }
+}
 
 # Further filter data by read position based on length
-CPDMismatchData = mapply(function(CPDMismatchDataRep, CPDPeakPositionsRep) mapply(
-  filterMismatchesByPositionAndReadLength, CPDMismatchDataRep, CPDPeakPositionsRep,
-  expansionOffset, SIMPLIFY = FALSE
-), CPDMismatchData, CPDPeakPositions, SIMPLIFY = FALSE)
-sixFourMismatchData = mapply(function(sixFourMismatchDataRep, sixFourPeakPositionsRep) mapply(
-  filterMismatchesByPositionAndReadLength, sixFourMismatchDataRep, sixFourPeakPositionsRep,
-  expansionOffset, SIMPLIFY = FALSE
-), sixFourMismatchData, sixFourPeakPositions, SIMPLIFY = FALSE)
+CPDMismatchData = mapply(function(CPDMismatchDataRep, CPDMMFreqZScoreRep) mapply(
+  filterMismatchesByPositionAndReadLength, CPDMismatchDataRep, CPDMMFreqZScoreRep,
+  expansionOffset = expansionOffset, SIMPLIFY = FALSE
+), CPDMismatchData, CPDMMFreqZScores, SIMPLIFY = FALSE)
+sixFourMismatchData = mapply(function(sixFourMismatchDataRep, sixFourMMFreqZScoreRep) mapply(
+  filterMismatchesByPositionAndReadLength, sixFourMismatchDataRep, sixFourMMFreqZScoreRep,
+  expansionOffset = expansionOffset, SIMPLIFY = FALSE
+), sixFourMismatchData, sixFourMMFreqZScores, SIMPLIFY = FALSE)
 ```
@@
     cellType = cellType, lesion = "CPD", repitition = names(threePrimeMismatchCPDNucFreq)[i],
-    strandPolarity = "three_prime", anchored = TRUE
+    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering
   ))
@@
     cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMismatchCPDNucFreq)[i],
-    strandPolarity = "five_prime", anchored = TRUE
+    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering
   ))
@@
     cellType = cellType, lesion = "6-4", repitition = names(threePrimeMismatchSixFourNucFreq)[i],
-    strandPolarity = "three_prime", anchored = TRUE
+    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering
   ))
@@
     cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMismatchSixFourNucFreq)[i],
-    strandPolarity = "five_prime", anchored = TRUE
+    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering
   ))
@@
       timepoint = names(threePrimeMMAnchoredCPDEnrichment[[i]])[j], strandPolarity = "three_prime",
-      anchored = TRUE, sequence = "YR"
+      anchored = TRUE, sequence = "YR", filtering = filtering
     ))
@@
       timepoint = names(fivePrimeMMAnchoredCPDEnrichment[[i]])[j], strandPolarity = "five_prime",
-      anchored = TRUE, sequence = "TGG"
+      anchored = TRUE, sequence = "TGG", filtering = filtering
     ))
@@
       timepoint = names(threePrimeMMAnchoredSixFourEnrichment[[i]])[j], strandPolarity = "three_prime",
-      anchored = TRUE, sequence = "YR"
+      anchored = TRUE, sequence = "YR", filtering = filtering
     ))
@@
       timepoint = names(fivePrimeMMAnchoredSixFourEnrichment[[i]])[j], strandPolarity = "five_prime",
-      anchored = TRUE, sequence = "TGG"
+      anchored = TRUE, sequence = "TGG", filtering = filtering
     ))
@@
       timepoint = names(threePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "three_prime",
-      anchored = TRUE, sequence = "YR"
+      anchored = TRUE, sequence = "YR", filtering = filtering
     ))
@@
       timepoint = names(fivePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "five_prime",
-      anchored = TRUE, sequence = "TGG"
+      anchored = TRUE, sequence = "TGG", filtering = filtering
     ))
@@
       timepoint = names(threePrimeMMAnchoredSixFourSeqFreq[[i]])[j], strandPolarity = "three_prime",
-      anchored = TRUE, sequence = "YR"
+      anchored = TRUE, sequence = "YR", filtering = filtering
     ))
@@
       timepoint = names(fivePrimeMMAnchoredSixFourSeqFreq[[i]])[j], strandPolarity = "five_prime",
-      anchored = TRUE, sequence = "TGG"
+      anchored = TRUE, sequence = "TGG", filtering = filtering
     ))

### 2022-05-20 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
I should have made more intermediate commits
- Added options for filtering (e.g. TGG filtering) as knitting parameters and interactive input.
- Changed mismatch frequency peak calling process to utilize individual positions' z-scores.
- Integrated mismatch frequency z-scores into mismatch frequency plotting.
- Lots of other bugfixes and tweaks. Hopefully the whole project is in a steady-state right now.

--- 2022-05-16 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
@@
 
+if (interactive()) {
+  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
+  filtering = readline("Filtering identifier (Input nothing for no filtering):")
+  if (filtering == '') filtering = character()
+} else {
+  bioinformaticsDirectory = params$bioinformaticsDirectory
+  filtering = params$filtering
+  if (filtering == "NONE") filtering = character()
+}
+if (length(filtering) > 0) {
+  titleCaseFiltering = tools::toTitleCase(gsub('_', ' ', filtering))
+} else titleCaseFiltering = character()
+
 opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
                fig.path = paste0(file.path("deamination_analysis_output", cellType,
-                                           "deamination_anchored_excision_site_figures"),
+                                           paste(c(filtering,"deamination_anchored_excision_site_figures"), collapse = '_')),
                                  .Platform$file.sep))
-if (interactive()) {
-  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
-} else {
-  bioinformaticsDirectory = params$bioinformaticsDirectory
-}
 
@@
 plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
-                               title = "CPD 3' Anchored Nucleotide Frequencies Rep1",
+                               title = paste(c("CPD", titleCaseFiltering, "3' Anchored Nuc Freq Rep1"), collapse = ' '),
                                secondaryYAxisLabel = "5' Cut Site Distance",
@@
 plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep2, 
-                               title = "CPD 3' Anchored Nucleotide Frequencies Rep2",
+                               title = paste(c("CPD", titleCaseFiltering, "3' Anchored Nuc Freq Rep2"), collapse = ' '),
                                secondaryYAxisLabel = "5' Cut Site Distance",
@@
 plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
-                               title = "CPD 5' Anchored Nucleotide Frequencies Rep1",
+                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Nuc Freq Rep1"), collapse = ' '),
                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
@@
 plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
-                               title = "CPD 5' Anchored Nucleotide Frequencies Rep2",
+                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Nuc Freq Rep2"), collapse = ' '),
                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
@@
 plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
-                               title = "CPD 3' Anchored Purine Frequencies Rep1",
+                               title = paste(c("CPD", titleCaseFiltering, "3' Anchored Purine Freq Rep1"), collapse = ' '),
                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
@@
 plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep2, 
-                               title = "CPD 3' Anchored Purine Frequencies Rep2",
+                               title = paste(c("CPD", titleCaseFiltering, "3' Anchored Purine Freq Rep2"), collapse = ' '),
                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
@@
 plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
-                               title = "CPD 5' Anchored Purine Frequencies Rep1",
+                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Purine Freq Rep1"), collapse = ' '),
                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
@@
 plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
-                               title = "CPD 5' Anchored Purine Frequencies Rep2",
+                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Purine Freq Rep2"), collapse = ' '),
                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
@@
 plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
-                               title = "6-4 3' Anchored Nucleotide Frequencies Rep1",
+                               title = paste(c("6-4", titleCaseFiltering, "3' Anchored Nuc Freq Rep1"), collapse = ' '),
                                secondaryYAxisLabel = "5' Cut Site Distance",
@@
 plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
-                               title = "6-4 3' Anchored Nucleotide Frequencies Rep2",
+                               title = paste(c("6-4", titleCaseFiltering, "3' Anchored Nuc Freq Rep2"), collapse = ' '),
                                secondaryYAxisLabel = "5' Cut Site Distance",
@@
 plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep1, 
-                               title = "6-4 5' Anchored Nucleotide Frequencies Rep1",
+                               title = paste(c("6-4", titleCaseFiltering, "5' Anchored Nuc Freq Rep1"), collapse = ' '),
                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
@@
 plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep2, 
-                               title = "6-4 5' Anchored Nucleotide Frequencies Rep2",
+                               title = paste(c("6-4", titleCaseFiltering, "5' Anchored Nuc Freq Rep2"), collapse = ' '),
                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
@@
 plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
-                               title = "6-4 3' Anchored Purine Frequencies Rep1",
+                               title = paste(c("6-4", titleCaseFiltering, "3' Anchored Purine Freq Rep1"), collapse = ' '),
                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
@@
 plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
-                               title = "6-4 3' Anchored Purine Frequencies Rep2",
+                               title = paste(c("6-4", titleCaseFiltering, "3' Anchored Purine Freq Rep2"), collapse = ' '),
                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
@@
 plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep1, 
-                               title = "6-4 5' Anchored Purine Frequencies Rep1",
+                               title = paste(c("6-4", titleCaseFiltering, "5' Anchored Purine Freq Rep1"), collapse = ' '),
                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
@@
 plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep2, 
-                               title = "6-4 5' Anchored Purine Frequencies Rep2",
+                               title = paste(c("6-4", titleCaseFiltering, "5' Anchored Purine Freq Rep2"), collapse = ' '),
                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
@@
 plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment$rep1,
-                       title = "CPD 3' Anchored YR Enrichment Rep1", secondaryYAxisLabel = "5' Cut Site Distance",
-                       showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
-                       querySequences = c("CG","CA","TG","TA"))
+                       title = paste(c("CPD", titleCaseFiltering, "3' Anchored YR Enrichment Rep1"), collapse = ' '),
+                       secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                       expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
 plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment$rep2,
-                       title = "CPD 3' Anchored YR Enrichment Rep2", secondaryYAxisLabel = "5' Cut Site Distance",
-                       showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
-                       querySequences = c("CG","CA","TG","TA"))
+                       title = paste(c("CPD", titleCaseFiltering, "3' Anchored YR Enrichment Rep2"), collapse = ' '),
+                       secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                       expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
 
 plotSequenceEnrichment(fivePrimeMMAnchoredCPDEnrichment$rep1,
-                       title = "CPD 5' Anchored TGG Enrichment Rep1", secondaryYAxisLabel = "3' Cut Site Distance",
-                       showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
-                       querySequences = c("TGG"))
+                       title = paste(c("CPD", titleCaseFiltering, "5' Anchored TGG Enrichment Rep1"), collapse = ' '),
+                       secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
+                       expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
 plotSequenceEnrichment(fivePrimeMMAnchoredCPDEnrichment$rep2,
-                       title = "CPD 5' Anchored TGG Enrichment Rep2", secondaryYAxisLabel = "3' Cut Site Distance",
-                       showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
-                       querySequences = c("TGG"))
+                       title = paste(c("CPD", titleCaseFiltering, "5' Anchored TGG Enrichment Rep2"), collapse = ' '),
+                       secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
+                       expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
 ```
@@
 plotSequenceEnrichment(threePrimeMMAnchoredSixFourEnrichment$rep1,
-                       title = "6-4 3' Anchored YR Enrichment Rep1", secondaryYAxisLabel = "5' Cut Site Distance",
-                       showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
-                       querySequences = c("CG","CA","TG","TA"))
+                       title = paste(c("6-4", titleCaseFiltering, "3' Anchored YR Enrichment Rep1"), collapse = ' '),
+                       secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                       expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
 plotSequenceEnrichment(threePrimeMMAnchoredSixFourEnrichment$rep2,
-                       title = "6-4 3' Anchored YR Enrichment Rep2", secondaryYAxisLabel = "5' Cut Site Distance",
-                       showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
-                       querySequences = c("CG","CA","TG","TA"))
+                       title = paste(c("6-4", titleCaseFiltering, "3' Anchored YR Enrichment Rep2"), collapse = ' '),
+                       secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                       expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
 
 plotSequenceEnrichment(fivePrimeMMAnchoredSixFourEnrichment$rep1,
-                       title = "6-4 5' Anchored TGG Enrichment Rep1", secondaryYAxisLabel = "3' Cut Site Distance",
-                       showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
-                       querySequences = c("TGG"))
+                       title = paste(c("6-4", titleCaseFiltering, "5' Anchored TGG Enrichment Rep1"), collapse = ' '),
+                       secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
+                       expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
 plotSequenceEnrichment(fivePrimeMMAnchoredSixFourEnrichment$rep2,
-                       title = "6-4 5' Anchored TGG Enrichment Rep2", secondaryYAxisLabel = "3' Cut Site Distance",
-                       showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
-                       querySequences = c("TGG"))
+                       title = paste(c("6-4", titleCaseFiltering, "5' Anchored TGG Enrichment Rep2"), collapse = ' '),
+                       secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
+                       expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
 ```
@@
 ```{r enrichment_test_1}
-for (i in 1:5) {
-  testTable = data.table(Read_Length = 9,
-                         Read_Sequence = replicate(1000, paste0(sample(c('A','C','G','T'), 9, TRUE), collapse = '')))
-  testTableNucFreq = tabulateNucFreqByPosTimepointAndLength(testTable)
-  testEnrichment = getSequenceFreqByReadLengthAndPos(testTable, testTableNucFreq, c("CG","CA","TG","TA"))
-  plotSequenceEnrichment(testEnrichment, title = "CPD 3' Anchored YR Enrichment Rep1")
-}
+# for (i in 1:5) {
+#   testTable = data.table(Read_Length = 9,
+#                          Read_Sequence = replicate(1000, paste0(sample(c('A','C','G','T'), 9, TRUE), collapse = '')))
+#   testTableNucFreq = tabulateNucFreqByPosTimepointAndLength(testTable)
+#   testEnrichment = getSequenceFreqByReadLengthAndPos(testTable, testTableNucFreq, c("CG","CA","TG","TA"))
+#   plotSequenceEnrichment(testEnrichment, title = "CPD 3' Anchored YR Enrichment Rep1")
+# }
 ```
@@
 ```{r enrichment_test_2}
-for (i in 1:5) {
-  testTable = data.table(Read_Length = 9,
-                         Read_Sequence = replicate(1000,
-                                                   paste0(sample(c(rep('A',6),rep('C',4),rep('G',4),rep('T',6)),
-                                                                 9, TRUE), collapse = '')))
-  testTableNucFreq = tabulateNucFreqByPosTimepointAndLength(testTable)
-  testEnrichment = getSequenceFreqByReadLengthAndPos(testTable, testTableNucFreq, c("CG","CA","TG","TA"))
-  plotSequenceEnrichment(testEnrichment, title = "CPD 3' Anchored YR Enrichment Rep1")
-}
+# for (i in 1:5) {
+#   testTable = data.table(Read_Length = 9,
+#                          Read_Sequence = replicate(1000,
+#                                                    paste0(sample(c(rep('A',6),rep('C',4),rep('G',4),rep('T',6)),
+#                                                                  9, TRUE), collapse = '')))
+#   testTableNucFreq = tabulateNucFreqByPosTimepointAndLength(testTable)
+#   testEnrichment = getSequenceFreqByReadLengthAndPos(testTable, testTableNucFreq, c("CG","CA","TG","TA"))
+#   plotSequenceEnrichment(testEnrichment, title = "CPD 3' Anchored YR Enrichment Rep1")
+# }
 ```
@@
 plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq$rep1,
-                        title = "CPD 3' Anchored YR Frequency Rep1", secondaryYAxisLabel = "5' Cut Site Distance",
-                        showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
-                        querySequences = c("CG","CA","TG","TA"))
+                        title = paste(c("CPD", titleCaseFiltering, "3' Anchored YR Freq Rep1"), collapse = ' '),
+                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
 plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq$rep2,
-                        title = "CPD 3' Anchored YR Frequency Rep2", secondaryYAxisLabel = "5' Cut Site Distance",
-                        showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
-                        querySequences = c("CG","CA","TG","TA"))
+                        title = paste(c("CPD", titleCaseFiltering, "3' Anchored YR Freq Rep2"), collapse = ' '),
+                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
 
 plotSequenceFrequencies(fivePrimeMMAnchoredCPDSeqFreq$rep1,
-                        title = "CPD 5' Anchored TGG Frequency Rep1", secondaryYAxisLabel = "3' Cut Site Distance",
-                        showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
-                        querySequences = c("TGG"))
+                        title = paste(c("CPD", titleCaseFiltering, "5' Anchored TGG Freq Rep1"), collapse = ' '),
+                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
+                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
 plotSequenceFrequencies(fivePrimeMMAnchoredCPDSeqFreq$rep2,
-                        title = "CPD 5' Anchored TGG Frequency Rep2", secondaryYAxisLabel = "3' Cut Site Distance",
-                        showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
-                        querySequences = c("TGG"))
+                        title = paste(c("CPD", titleCaseFiltering, "5' Anchored TGG Freq Rep2"), collapse = ' '),
+                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
+                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
 ```
@@
 plotSequenceFrequencies(threePrimeMMAnchoredSixFourSeqFreq$rep1,
-                        title = "6-4 3' Anchored YR Frequency Rep1", secondaryYAxisLabel = "5' Cut Site Distance",
-                        showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
-                        querySequences = c("CG","CA","TG","TA"))
+                        title = paste(c("6-4", titleCaseFiltering, "3' Anchored YR Freq Rep1"), collapse = ' '),
+                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
 plotSequenceFrequencies(threePrimeMMAnchoredSixFourSeqFreq$rep2,
-                        title = "6-4 3' Anchored YR Frequency Rep2", secondaryYAxisLabel = "5' Cut Site Distance",
-                        showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
-                        querySequences = c("CG","CA","TG","TA"))
+                        title = paste(c("6-4", titleCaseFiltering, "3' Anchored YR Freq Rep2"), collapse = ' '),
+                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
 
 plotSequenceFrequencies(fivePrimeMMAnchoredSixFourSeqFreq$rep1,
-                        title = "6-4 5' Anchored TGG Frequency Rep1", secondaryYAxisLabel = "3' Cut Site Distance",
-                        showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
-                        querySequences = c("TGG"))
+                        title = paste(c("6-4", titleCaseFiltering, "5' Anchored TGG Freq Rep1"), collapse = ' '),
+                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
+                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
 plotSequenceFrequencies(fivePrimeMMAnchoredSixFourSeqFreq$rep2,
-                        title = "6-4 5' Anchored TGG Frequency Rep2", secondaryYAxisLabel = "3' Cut Site Distance",
-                        showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
-                        querySequences = c("TGG"))
+                        title = paste(c("6-4", titleCaseFiltering, "5' Anchored TGG Freq Rep2"), collapse = ' '),
+                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
+                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
 ```

### 2022-05-20 R/NHF1DeaminationSequenceAndPositionDataGeneration.rmd
I should have made more intermediate commits
- Added options for filtering (e.g. TGG filtering) as knitting parameters and interactive input.
- Changed mismatch frequency peak calling process to utilize individual positions' z-scores.
- Integrated mismatch frequency z-scores into mismatch frequency plotting.
- Lots of other bugfixes and tweaks. Hopefully the whole project is in a steady-state right now.

--- 2022-05-16 R/NHF1DeaminationSequenceAndPositionDataGeneration.rmd
@@
 sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
+expansionOffset = 0
 
@@
   bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
+  filtering = readline("Filtering identifier (Input nothing for no filtering):")
+  if (filtering == '') filtering = character()
 } else {
   bioinformaticsDirectory = params$bioinformaticsDirectory
+  filtering = params$filtering
+  if (filtering == "NONE") filtering = character()
 }
+if (is.na(bioinformaticsDirectory)) stop("No bioinformatics directory given.")
 
@@
       cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
-      repitition = names(CPDMismatchData)[i]
+      repitition = names(CPDMismatchData)[i], filtering = filtering
       ))
@@
       cellType = cellType, lesion = "6-4-PP", timepoint = names(sixFourMismatchData[[i]])[j],
-      repitition = names(sixFourMismatchData)[i]
+      repitition = names(sixFourMismatchData)[i], filtering = filtering
       ))
@@
 
+# Write the simplified mismatch data
 for (i in 1:length(CPDMismatchData)) {
@@
              cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
-             repitition = names(CPDMismatchData)[i]
+             repitition = names(CPDMismatchData)[i], filtering = filtering
            ))
@@
              cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
-             repitition = names(sixFourMismatchData)[i]
+             repitition = names(sixFourMismatchData)[i], filtering = filtering
+           ))
+  }
+}
+```
+
+```{r generate_and_write_mismatch_frequency_z-scores}
+# Don't forget to subset by C>T mismatches!
+CPDMMFreqZScores = lapply(CPDMismatchData, function(x) lapply(
+  x, function(y) {
+    getMismatchFrequencyZScoreByPosAndReadLength(y[Mismatch == "C>T"], expansionOffset)
+  }
+))
+sixFourMMFreqZScores = lapply(sixFourMismatchData, function(x) lapply(
+  x, function(y) {
+    getMismatchFrequencyZScoreByPosAndReadLength(y[Mismatch == "C>T"], expansionOffset)
+  }
+))
+
+for (i in seq_along(CPDMMFreqZScores)) {
+  for (j in seq_along(CPDMMFreqZScores[[i]])) {
+    fwrite(CPDMMFreqZScores[[i]][[j]], sep = '\t', file = generateFilePath(
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+      cellType = cellType, lesion = "CPD", repitition = names(CPDMMFreqZScores)[i],
+      timepoint = names(CPDMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
+    ))
+  }
+}
+
+for (i in seq_along(sixFourMMFreqZScores)) {
+  for (j in seq_along(sixFourMMFreqZScores[[i]])) {
+    fwrite(sixFourMMFreqZScores[[i]][[j]], sep = '\t', file = generateFilePath(
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+      cellType = cellType, lesion = "6-4", repitition = names(sixFourMMFreqZScores)[i],
+      timepoint = names(sixFourMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
     ))
@@
              cellType = cellType, lesion = "CPD", repitition = names(CPDGroupedStats)[i],
-             strandPolarity = names(CPDGroupedStats[[i]])[j]
+             strandPolarity = names(CPDGroupedStats[[i]])[j], filtering = filtering
            ))
@@
              cellType = cellType, lesion = "6-4", repitition = names(sixFourGroupedStats)[i],
-             strandPolarity = names(sixFourGroupedStats[[i]])[j]
+             strandPolarity = names(sixFourGroupedStats[[i]])[j], filtering = filtering
            ))

### 2022-05-20 R/NHF1DeaminationSequenceAndPositionFigureGeneration.rmd
I should have made more intermediate commits
- Added options for filtering (e.g. TGG filtering) as knitting parameters and interactive input.
- Changed mismatch frequency peak calling process to utilize individual positions' z-scores.
- Integrated mismatch frequency z-scores into mismatch frequency plotting.
- Lots of other bugfixes and tweaks. Hopefully the whole project is in a steady-state right now.

--- 2022-05-16 R/NHF1DeaminationSequenceAndPositionFigureGeneration.rmd
@@
 
+if (interactive()) {
+  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
+  filtering = readline("Filtering identifier (Input nothing for no filtering):")
+  if (filtering == '') filtering = character()
+} else {
+  bioinformaticsDirectory = params$bioinformaticsDirectory
+  filtering = params$filtering
+  if (filtering == "NONE") filtering = character()
+}
+if (length(filtering) > 0) {
+  titleCaseFiltering = tools::toTitleCase(gsub('_', ' ', filtering))
+} else titleCaseFiltering = character()
+
 opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
                fig.path = paste0(file.path("deamination_analysis_output",cellType,
-                                           "deamination_sequence_and_position_figures"),
+                                           paste(c(filtering,"deamination_sequence_and_position_figures"), collapse = '_')),
                                  .Platform$file.sep))
-if (interactive()) {
-  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
-} else {
-  bioinformaticsDirectory = params$bioinformaticsDirectory
-}
 
@@
       cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
-      repitition = names(CPDMismatchData)[i]
+      repitition = names(CPDMismatchData)[i], filtering = filtering
     ))
@@
       cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
-      repitition = names(sixFourMismatchData)[i]
+      repitition = names(sixFourMismatchData)[i], filtering = filtering
     ))
@@
     plotMismatchTypeFrequencies(CPDMismatchData[[i]][[j]],
-                                title = paste("CPD", names(CPDMismatchData)[i], 
-                                              names(CPDMismatchData[[i]])[j], "Mismatch Type Frequency"))
+                                title = paste(c("CPD", titleCaseFiltering, names(CPDMismatchData)[i], 
+                                                names(CPDMismatchData[[i]])[j], "Mismatch Type Frequency"),
+                                              collapse = ' '))
   }
@@
     plotMismatchTypeFrequencies(sixFourMismatchData[[i]][[j]],
-                                title = paste("6-4", names(sixFourMismatchData)[i], 
-                                              names(sixFourMismatchData[[i]])[j], "Mismatch Type Frequency"))
+                                title = paste(c("6-4", titleCaseFiltering, names(sixFourMismatchData)[i], 
+                                                names(sixFourMismatchData[[i]])[j], "Mismatch Type Frequency"),
+                                              collapse = ' '))
   }
@@
     plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], includedTypes = c("C>T"),
-                                    title = paste("CPD", names(CPDMismatchData)[i], 
-                                                  names(CPDMismatchData[[i]])[j], "C>T Mismatch Positions"))
+                                    title = paste(c("CPD", titleCaseFiltering, names(CPDMismatchData)[i], 
+                                                    names(CPDMismatchData[[i]])[j], "C>T Mismatch Positions"),
+                                                  collapse = ' '))
     plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], omittedTypes = c("C>T"),
-                                    title = paste("CPD", names(CPDMismatchData)[i], 
-                                                  names(CPDMismatchData[[i]])[j], "!C>T Mismatch Positions"))
+                                    title = paste(c("CPD", titleCaseFiltering, names(CPDMismatchData)[i], 
+                                                    names(CPDMismatchData[[i]])[j], "!C>T Mismatch Positions"),
+                                                  collapse = ' '))
   }
@@
     plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], includedTypes = c("C>T"),
-                                    title = paste("6-4", names(sixFourMismatchData)[i], 
-                                                  names(sixFourMismatchData[[i]])[j], "C>T Mismatch Positions"))
+                                    title = paste(c("6-4", titleCaseFiltering, names(sixFourMismatchData)[i], 
+                                                    names(sixFourMismatchData[[i]])[j], "C>T Mismatch Positions"),
+                                                  collapse = ' '))
     plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], omittedTypes = c("C>T"),
-                                    title = paste("6-4", names(sixFourMismatchData)[i], 
-                                                  names(sixFourMismatchData[[i]])[j], "!C>T Mismatch Positions"))
+                                    title = paste(c("6-4", titleCaseFiltering, names(sixFourMismatchData)[i], 
+                                                    names(sixFourMismatchData[[i]])[j], "!C>T Mismatch Positions"),
+                                                  collapse = ' '))
   }
@@
     plotTrinucleotideContext(CPDMismatchData[[i]][[j]], includedTypes = c("C>T"),
-                             title = paste("CPD", names(CPDMismatchData)[i], names(CPDMismatchData[[i]])[j],
-                                           "C>T Mismatch Trinuc Context"))
+                             title = paste(c("CPD", titleCaseFiltering, names(CPDMismatchData)[i],
+                                             names(CPDMismatchData[[i]])[j], "C>T Mismatch Trinuc Context"),
+                                           collapse = ' '))
   }
@@
     plotTrinucleotideContext(sixFourMismatchData[[i]][[j]], includedTypes = c("C>T"),
-                             title = paste("6-4", names(sixFourMismatchData)[i], names(sixFourMismatchData[[i]])[j],
-                                           "C>T Mismatch Trinuc Context"))
+                             title = paste(c("6-4", titleCaseFiltering, names(sixFourMismatchData)[i],
+                                             names(sixFourMismatchData[[i]])[j], "C>T Mismatch Trinuc Context"),
+                                           collapse = ' '))
+  }
+}
+```
+
+```{r read_mismatch_frequency_z-score_tables}
+CPDMMFreqZScores = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
+for (i in seq_along(CPDMMFreqZScores)) {
+  for (j in seq_along(CPDMMFreqZScores[[i]])) {
+    CPDMMFreqZScores[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+      cellType = cellType, lesion = "CPD", repitition = names(CPDMMFreqZScores)[i],
+      timepoint = names(CPDMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
+    ))
+  }
+}
+
+sixFourMMFreqZScores = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
+for (i in seq_along(sixFourMMFreqZScores)) {
+  for (j in seq_along(sixFourMMFreqZScores[[i]])) {
+    sixFourMMFreqZScores[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+      cellType = cellType, lesion = "6-4", repitition = names(sixFourMMFreqZScores)[i],
+      timepoint = names(sixFourMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
+    ))
   }
@@
 plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, includedTypes = c("C>T"),
-                                         title = "CPD C>T Mismatch Pos Freq Rep1")
+                                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
+                                                       collapse = ' '),
+                                         zScoreTables = CPDMMFreqZScores$rep1)
 plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, includedTypes = c("C>T"),
-                                         title = "CPD C>T Mismatch Pos Freq Rep2")
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, includedTypes = c("C>T"),
-                                         title = "CPD C>T Mismatch Pos Freq Rep1", posType = FIVE_PRIME)
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, includedTypes = c("C>T"),
-                                         title = "CPD C>T Mismatch Pos Freq Rep2", posType = FIVE_PRIME)
+                                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
+                                                       collapse = ' '),
+                                         zScoreTables = CPDMMFreqZScores$rep2)
+plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME,
+                                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
+                                                       collapse = ' '),
+                                         zScoreTables = CPDMMFreqZScores$rep1)
+plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME,
+                                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
+                                                       collapse = ' '),
+                                         zScoreTables = CPDMMFreqZScores$rep2)
 ```
@@
 plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, includedTypes = c("C>T"),
-                                         title = "6-4 C>T Mismatch Pos Freq Rep1")
+                                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
+                                                       collapse = ' '),
+                                         zScoreTables = sixFourMMFreqZScores$rep1)
 plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, includedTypes = c("C>T"),
-                                         title = "6-4 C>T Mismatch Pos Freq Rep2")
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, includedTypes = c("C>T"),
-                                         title = "6-4 C>T Mismatch Pos Freq Rep1", posType = FIVE_PRIME)
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, includedTypes = c("C>T"),
-                                         title = "6-4 C>T Mismatch Pos Freq Rep2", posType = FIVE_PRIME)
+                                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
+                                                       collapse = ' '),
+                                         zScoreTables = sixFourMMFreqZScores$rep2)
+plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME,
+                                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
+                                                       collapse = ' '),
+                                         zScoreTables = sixFourMMFreqZScores$rep1)
+plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME,
+                                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
+                                                       collapse = ' '),
+                                         zScoreTables = sixFourMMFreqZScores$rep2)
+```
+
+```{r CPD_read_length_distributions}
+plotReadLengthFrequencies(CPDMismatchData$rep1,
+                          title = paste(c("CPD", titleCaseFiltering, "Read Length Freq Rep 1"), collapse = ' '))
+plotReadLengthFrequencies(CPDMismatchData$rep2,
+                          title = paste(c("CPD", titleCaseFiltering, "Read Length Freq Rep 2"), collapse = ' '))
+```
+
+```{r 6-4_read_length_distributions}
+plotReadLengthFrequencies(sixFourMismatchData$rep1,
+                          title = paste(c("6-4", titleCaseFiltering, "Read Length Freq Rep 1"), collapse = ' '))
+plotReadLengthFrequencies(sixFourMismatchData$rep2,
+                          title = paste(c("6-4", titleCaseFiltering, "Read Length Freq Rep 2"), collapse = ' '))
 ```
@@
       cellType = cellType, lesion = "CPD", repitition = names(CPDGroupedStats)[i],
-      strandPolarity = names(CPDGroupedStats[[i]])[j]
+      strandPolarity = names(CPDGroupedStats[[i]])[j], filtering = filtering
     ))
@@
       cellType = cellType, lesion = "6-4", repitition = names(sixFourGroupedStats)[i],
-      strandPolarity = names(sixFourGroupedStats[[i]])[j]
+      strandPolarity = names(sixFourGroupedStats[[i]])[j], filtering = filtering
     ))
@@
 plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, POS_DIFF,
-                         title = "CPD C>T Mismatch Pos Diff Rep1",
+                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Diff Rep1"), collapse = ' '),
                          xAxisBreaks = c(23:31))
 plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, POS_DIFF,
-                         title = "CPD C>T Mismatch Pos Diff Rep2",
+                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Diff Rep2"), collapse = ' '),
                          xAxisBreaks = c(23:31))
@@
 plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, POS_DIFF,
-                         title = "6-4 C>T Mismatch Pos Diff Rep1",
+                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Diff Rep1"), collapse = ' '),
                          xAxisBreaks = c(23:31))
 plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, POS_DIFF,
-                         title = "6-4 C>T Mismatch Pos Diff Rep2",
+                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Diff Rep2"), collapse = ' '),
                          xAxisBreaks = c(23:31))

### 2022-05-20 R/DeaminationAnchoredExcisionSiteAnalysis.R

@@ -6,7 +6,7 @@ THREE_PRIME = "three_prime"
 FIVE_PRIME = "five_prime"
 
 # Default text scaling
-defaultTextScaling = theme(plot.title = element_text(size = 26, hjust = 0.5),
+defaultTextScaling = theme(plot.title = element_text(size = 22, hjust = 0.5),
                            axis.title = element_text(size = 22), axis.text = element_text(size = 18),
                            legend.title = element_text(size = 22), legend.text = element_text(size = 18),
                            strip.text = element_text(size = 22))
@@ -261,7 +261,7 @@ plotSequenceEnrichment = function(enrichmentTablesByTimepoint, posType = THREE_P
   # If passed a single data.table, no timepoint information is present.
   # Otherwise, combine the given tables into one agggregate table.
   if (is.data.table(enrichmentTablesByTimepoint)) {
-    fullEnrichmentTable = copy(enrichmentTablesByTimepoint)[,Timepoint := NA]
+    fullEnrichmentTable = copy(enrichmentTablesByTimepoint)[,Timepoint := "NONE"]
   } else {
     fullEnrichmentTable = rbindlist(lapply(seq_along(enrichmentTablesByTimepoint), function(i) {
       copy(enrichmentTablesByTimepoint[[i]])[,Timepoint := names(enrichmentTablesByTimepoint)[i]]
@@ -275,7 +275,7 @@ plotSequenceEnrichment = function(enrichmentTablesByTimepoint, posType = THREE_P
     labs(title = title, x = xAxisLabel, y = yAxisLabel) +
     blankBackground + defaultTextScaling
 
-  if (all(is.na(fullEnrichmentTable$Timepoint))) {
+  if (all(fullEnrichmentTable$Timepoint == "NONE")) {
     plot = plot + facet_grid(rows = vars(Read_Length))
   } else {
     plot = plot + facet_grid(Read_Length~factor(Timepoint, levels = unique(fullEnrichmentTable$Timepoint)))
@@ -328,7 +328,7 @@ plotSequenceFrequencies = function(seqFreqTablesByTimepoint, posType = THREE_PRI
   # If passed a single data.table, no timepoint information is present.
   # Otherwise, combine the given tables into one agggregate table.
   if (is.data.table(seqFreqTablesByTimepoint)) {
[…]

### 2022-05-20 R/DeaminationParseAndFilter.R

@@ -1,9 +1,19 @@
 library(data.table)
 library(stringr)
+library(ggplot2)
 
 THREE_PRIME = "three_prime"
 FIVE_PRIME = "five_prime"
 
+# Default text scaling
+defaultTextScaling = theme(plot.title = element_text(size = 22, hjust = 0.5),
+                           axis.title = element_text(size = 22), axis.text = element_text(size = 18),
+                           legend.title = element_text(size = 22), legend.text = element_text(size = 18),
+                           strip.text = element_text(size = 22))
+
+# Blank background theme
+blankBackground = theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+                        panel.background = element_blank(), axis.line = element_line(colour = "black"))
 
 # Filters the given mismatch data based the presence of 'N', the number of mismatches per read,
 # and read length.
@@ -64,45 +74,26 @@ simplifyTable = function(table, includeReadSequence = FALSE, includeTrinucleotid
 }
 
 
-# Takes a simplified table of mismatches and filters them based on the position of the mismatch
-filterMismatchesByPosition = function(mismatchTable, minPos, maxPos, posType, expansionOffset = 0) {
-
-  if (posType == THREE_PRIME) {
-    positions = mismatchTable$Position + expansionOffset
-  } else if (posType == FIVE_PRIME) {
-    positions = mismatchTable$Read_Length + mismatchTable$Position + 1 - expansionOffset
-  } else stop("Unrecognized value for posType parameter.")
-
-  return(mismatchTable[positions >= minPos & positions <= maxPos])
-
-}
-
-
 # Takes a simplified table of mismatches and filters them based on the position of the mismatch.
-# Unlike the filterMismatchesByPosition function, min and max positions are dynamic based on read length.
-# (This function is actually still used under the hood.)
-# See constant tables below for examples of how to format the posConstraintsByReadLength table.
-filterMismatchesByPositionAndReadLength = function(mismatchTable, posConstraintsByReadLength,
-                                                   expansionOffset = 0) {
+# Valid positions are defined using a zscore table that is stratified by both position and read length.
[…]

### 2022-05-20 R/DeaminationSequenceAndPositionAnalysis.R

@@ -6,7 +6,7 @@ THREE_PRIME = "three_prime"
 FIVE_PRIME = "five_prime"
 
 # Default text scaling
-defaultTextScaling = theme(plot.title = element_text(size = 26, hjust = 0.5),
+defaultTextScaling = theme(plot.title = element_text(size = 22, hjust = 0.5),
                            axis.title = element_text(size = 22), axis.text = element_text(size = 18),
                            legend.title = element_text(size = 22), legend.text = element_text(size = 18),
                            strip.text = element_text(size = 22))
@@ -71,13 +71,22 @@ plotMismatchPositionFrequencies = function(mismatchTable, includedTypes = list()
 # Input should be a list of data.tables with names as timepoint information, or a single data.table
 # to construct a plot without timepoint information.
 plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTypes = list(), omittedTypes = list(),
-                                                    title = "Mismatch Position Frequencies", posType = THREE_PRIME) {
+                                                    title = "Mismatch Position Frequencies", posType = THREE_PRIME,
+                                                    zScoreTables = NULL, zScoreCutoff = 4) {
 
   #If passed a single data.table, wrap it in a list.
   if (is.data.table(simplifiedTables)) {
-    simplifiedTables = list(None = simplifiedTables)
-    noTimepointInfo = TRUE
-  } else noTimepointInfo = FALSE
+    simplifiedTables = list(NONE = simplifiedTables)
+  }
+  simplifiedTables = lapply(simplifiedTables, copy)
+  noTimepointInfo = all(names(simplifiedTables) == "NONE")
+
+  if (!is.null(zScoreTables)) {
+    zScoreTables = lapply(zScoreTables, copy)
+    if (is.data.table(zScoreTables)) {
+      zScoreTables = list(None = zScoreTables)
+    }
+  }
 
   if (posType == THREE_PRIME) {
     xAxisLabel = "3' Relative Position"
@@ -87,26 +96,44 @@ plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTy
     xAxisBreaks = c(0, 10, 20)
     simplifiedTables = lapply(simplifiedTables, copy)
     lapply(simplifiedTables, function(x) x[, Position := Read_Length + Position + 1])
+    if (!is.null(zScoreTables)) {
[…]

### 2022-05-20 R/UsefulFileSystemFunctions.R

@@ -10,13 +10,14 @@ dataTypeStrings =
        nucleotideFrequencyData = "nucleotide_frequencies",
        sequenceEnrichment = "sequence_enrichment",
        sequenceFrequency = "sequence_frequency",
-       alignedReads = "aligned_reads")
+       alignedReads = "aligned_reads",
+       mismatchFrequencyZScores = "mismatch_frequency_z-scores")
 
 generateFilePath = function(directory, dataTypeString, fileExtension,
                             cellType = NA, lesion = NA, timepoint = NA, repitition = NA,
                             includedMismatches = character(), omittedMismatches = character(),
                             strandPolarity = NA, anchored = F, sequence = NA, expansionNum = NA,
-                            additionalInformation = character(), filterText = NA) {
+                            additionalInformation = character(), filtering = NA) {
 
   if ( length(includedMismatches) > 0 && length(omittedMismatches) > 0) {
     stop("Included mismatches and omitted mismatches given simultaneously")
@@ -25,7 +26,7 @@ generateFilePath = function(directory, dataTypeString, fileExtension,
   includedMismatches = lapply(includedMismatches, function(x) str_replace(x, '>', "_to_"))
   omittedMismatches = lapply(omittedMismatches, function(x) str_replace(x, '>', "_to_"))
 
-  if (!is.na(expansionNum)) expansionText = paste0(expansionNum,"bp_expanded")
+  if (!is.na(expansionNum) && expansionNum > 0) expansionText = paste0(expansionNum,"bp_expanded")
   else expansionText = NA
 
   if (anchored) anchoredText = "anchored"
@@ -33,7 +34,7 @@ generateFilePath = function(directory, dataTypeString, fileExtension,
 
   basenameParts = c(cellType, lesion, timepoint, repitition, includedMismatches, omittedMismatches, "omitted",
                     strandPolarity, anchoredText, sequence, additionalInformation, dataTypeString, expansionText,
-                    filterText)
+                    filtering)
   if (length(omittedMismatches) == 0) basenameParts[5+length(includedMismatches)] = NA
   basenameParts = basenameParts[!is.na(basenameParts)]
 

### 2022-05-23 R/NHF1GeneralReadSequenceDataGeneration.rmd
Update Notebooks
Loosened read length constraints and added read length frequency plotting to general read analysis.

@@
   readData = data.table(Read_Length = nchar(readData$V7)-expansionOffset*2, Read_Sequence = readData$V7)
-  readData = readData[Read_Length >= 23 & Read_Length <= 31]
+  readData = readData[Read_Length >= 20 & Read_Length <= 31]
 

### 2022-05-23 R/NHF1GeneralReadSequenceFigureGeneration.rmd
Update Notebooks
Loosened read length constraints and added read length frequency plotting to general read analysis.

@@
                  "UsefulFileSystemFunctions.R"))
+source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
+                 "DeaminationSequenceAndPositionAnalysis.R"))
 source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
@@
 ```
+
+```{r read_length_frequencies_plotting_function}
+readAndPlotReadLengthFrequencies = function(lesion, repitition, timepoints) {
+
+  readData = timepoints
+  for (i in seq_along(readData)) {
+    readData[[i]] = fread(generateFilePath(
+      generalReadSequenceDataDirectory, dataTypeStrings$alignedReads, ".bed",
+      cellType = cellType, lesion = lesion, timepoint = names(readData)[i],
+      repitition = repitition, expansionNum = expansionOffset
+    ))
+    readData[[i]] = data.table(Read_Length = nchar(readData[[i]]$V7)-expansionOffset*2,
+                               Timepoint = names(readData)[i])
+    readData[[i]] = readData[[i]][Read_Length >= 20 & Read_Length <= 31]
+  }
+
+  plotReadLengthFrequencies(readData,
+                            title = paste(c(lesion, "Read Length Freq",
+                                            tools::toTitleCase(repitition)),
+                                          collapse = ' '))
+
+}
+```
+
+```{r CPD_read_length_frequencies}
+readAndPlotReadLengthFrequencies("CPD", "rep1", CPDTimepoints)
+readAndPlotReadLengthFrequencies("CPD", "rep2", CPDTimepoints)
+```
+
+```{r 6-4_read_length_frequencies}
+plotReadLengthFrequencies("6-4", "rep1", sixFourTimepoints)
+plotReadLengthFrequencies("6-4", "rep2", sixFourTimepoints)
+```

### 2022-05-24 R/DeaminationAnchoredExcisionSiteAnalysis.R
Small plotting changes
- Removed extraneous right axis ticks.
- Switched axis labels for read length frequency plotting to default.

@@ -355,6 +355,7 @@ plotSequenceFrequencies = function(seqFreqTablesByTimepoint, posType = THREE_PRI
     theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
           strip.background = element_rect(color = "black", size = 1),
           axis.text.y = element_text(size = 12),
+          axis.text.y.right = element_blank(), axis.ticks.y.right = element_blank(),
           strip.text.y = element_text(size = yStripFontSize)) +
     coord_cartesian(ylim = c(0,maxFrequency*1.2)) +
     scale_y_continuous(sec.axis = dup_axis(~., name = secondaryYAxisLabel), breaks = yAxisBreaks) +

### 2022-05-24 R/DeaminationSequenceAndPositionAnalysis.R

@@ -161,8 +161,6 @@ plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTy
 # to construct a plot without timepoint information.
 plotReadLengthFrequencies = function(simplifiedTables, title = "Read Length Frequencies") {
 
-  xAxisBreaks = c(23,27,31)
-
   #If passed a single data.table, wrap it in a list.
   if (is.data.table(simplifiedTables)) {
     simplifiedTables = list(None = simplifiedTables)
@@ -190,7 +188,6 @@ plotReadLengthFrequencies = function(simplifiedTables, title = "Read Length Freq
     theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
           strip.background = element_rect(color = "black", size = 1),
           axis.text.y = element_text(size = 16), strip.text.y = element_text(size = 16)) +
-    scale_x_continuous(breaks = xAxisBreaks) +
     scale_y_continuous(breaks = yAxisBreaks)
 
   print(plot)

### 2022-05-24 R/NHF1GeneralReadSequenceDataGeneration.rmd
Update R notebooks

@@
   readData = data.table(Read_Length = nchar(readData$V7)-expansionOffset*2, Read_Sequence = readData$V7)
-  readData = readData[Read_Length >= 20 & Read_Length <= 31]
+  readData = readData[Read_Length >= 15 & Read_Length <= 31]
 

### 2022-05-24 R/NHF1GeneralReadSequenceFigureGeneration.rmd
Update R notebooks

@@
 
-```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 7}
+```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 10}
 plotSequenceFrequencies(CPDTGGSeqFreq$rep1,
@@
 
-```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 7}
+```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 10}
 plotSequenceFrequencies(sixFourTGGSeqFreq$rep1,
@@
                                Timepoint = names(readData)[i])
-    readData[[i]] = readData[[i]][Read_Length >= 20 & Read_Length <= 31]
+    readData[[i]] = readData[[i]][Read_Length >= 15 & Read_Length <= 31]
   }
@@
 ```{r 6-4_read_length_frequencies}
-plotReadLengthFrequencies("6-4", "rep1", sixFourTimepoints)
-plotReadLengthFrequencies("6-4", "rep2", sixFourTimepoints)
+readAndPlotReadLengthFrequencies("6-4", "rep1", sixFourTimepoints)
+readAndPlotReadLengthFrequencies("6-4", "rep2", sixFourTimepoints)
 ```

### 2022-05-24 R/NHF1DeaminationAnchoredExcisionSiteDataGeneration.rmd
Implemented constants for min/max read length

@@
 sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
+minReadLength = 22; maxReadLength = 30
 
@@
 CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
-  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = 23, maxReadLength = 31)
+  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = minReadLength, maxReadLength = maxReadLength)
 ))
 sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
-  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = 23, maxReadLength = 31)
+  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = minReadLength, maxReadLength = maxReadLength)
 ))

### 2022-05-24 R/NHF1DeaminationSequenceAndPositionDataGeneration.rmd
Implemented constants for min/max read length

@@
 expansionOffset = 0
+minReadLength = 22; maxReadLength = 30
 
@@
 CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
-  x, function(y) filterResults(y, TRUE, 3, 23, 31)
+  x, function(y) filterResults(y, TRUE, 3, minReadLength, maxReadLength)
 ))
 sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
-  x, function(y) filterResults(y, TRUE, 3, 23, 31)
+  x, function(y) filterResults(y, TRUE, 3, minReadLength, maxReadLength)
 ))

### 2022-05-24 R/NHF1DeaminationSequenceAndPositionFigureGeneration.rmd
Implemented constants for min/max read length

@@
                          title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Diff Rep1"), collapse = ' '),
-                         xAxisBreaks = c(23:31))
+                         xAxisBreaks = c(minReadLength:maxReadLength))
 plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, POS_DIFF,
                          title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Diff Rep2"), collapse = ' '),
-                         xAxisBreaks = c(23:31))
+                         xAxisBreaks = c(minReadLength:maxReadLength))
 ```
@@
                          title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Diff Rep1"), collapse = ' '),
-                         xAxisBreaks = c(23:31))
+                         xAxisBreaks = c(minReadLength:maxReadLength))
 plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, POS_DIFF,
                          title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Diff Rep2"), collapse = ' '),
-                         xAxisBreaks = c(23:31))
+                         xAxisBreaks = c(minReadLength:maxReadLength))
 ```

### 2022-05-24 R/NHF1GeneralReadSequenceDataGeneration.rmd
Implemented constants for min/max read length

@@
   readData = data.table(Read_Length = nchar(readData$V7)-expansionOffset*2, Read_Sequence = readData$V7)
-  readData = readData[Read_Length >= 15 & Read_Length <= 31]
+  readData = readData[Read_Length >= minReadLength-7 & Read_Length <= maxReadLength]
 

### 2022-05-24 R/NHF1GeneralReadSequenceFigureGeneration.rmd
Implemented constants for min/max read length

@@
                                Timepoint = names(readData)[i])
-    readData[[i]] = readData[[i]][Read_Length >= 15 & Read_Length <= 31]
+    readData[[i]] = readData[[i]][Read_Length >= minReadLength-7 & Read_Length <= maxReadLength]
   }

### 2022-05-25 R/DeaminationAnchoredExcisionSiteAnalysis.R
Various plotting tweaks
- Tweaks to axis bounds, tick marks, text size, etc.
- Also, tweaked vertical lines in mismatch frequency facet plot.

@@ -104,14 +104,12 @@ plotNucFreqVsReadLengthBarPlot = function(nucFreqTable, posType = THREE_PRIME,
                                           yStripFontSize = 16,
                                           combineNucleotides = list(), combinedNames = list(),
                                           showThreePrimeCutSite = FALSE, showFivePrimeCutSite = FALSE,
-                                          expansionOffset = 0) {
+                                          expansionOffset = 0, xAxisBreaks = -3:3*10) {
 
   if (posType == THREE_PRIME) {
     xAxisLabel = "3' Relative Position"
-    xAxisBreaks = c(0, -10, -20, -30)
   } else if (posType == FIVE_PRIME) {
     xAxisLabel = "5' Relative Position"
-    xAxisBreaks = c(0, 10, 20, 30)
   } else stop("Unrecognized value for posType parameter.")
 
   if (length(combineNucleotides) > 0) {
@@ -132,10 +130,11 @@ plotNucFreqVsReadLengthBarPlot = function(nucFreqTable, posType = THREE_PRIME,
   plot = plot +
     theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
           strip.background = element_rect(color = "black", size = 1),
-          axis.text.y = element_blank(), axis.ticks.y = element_blank(),
+          axis.text.y.right = element_blank(), axis.ticks.y.right = element_blank(),
+          axis.text.y.left = element_text(size = 10),
           strip.text.y = element_text(size = yStripFontSize)) +
-    coord_cartesian(ylim = c(0,1)) +
-    scale_y_continuous(sec.axis = dup_axis(~., name = secondaryYAxisLabel)) +
+    coord_cartesian(ylim = c(0,1.2)) +
+    scale_y_continuous(sec.axis = dup_axis(~., name = secondaryYAxisLabel), breaks = c(0, 0.5, 1)) +
     scale_x_continuous(breaks = xAxisBreaks)
 
   if (length(unique(nucFreqTable$Nucleotide)) == 1) {
@@ -248,14 +247,12 @@ plotSequenceEnrichment = function(enrichmentTablesByTimepoint, posType = THREE_P
                                   yAxisLabel = expression("log"[2]*"(Enrichment)"),
                                   secondaryYAxisLabel = "Read Length", yStripFontSize = 16, yAxisTickTextSize = 8,
                                   showThreePrimeCutSite = FALSE, showFivePrimeCutSite = FALSE,
[…]

### 2022-05-25 R/DeaminationSequenceAndPositionAnalysis.R

@@ -72,7 +72,7 @@ plotMismatchPositionFrequencies = function(mismatchTable, includedTypes = list()
 # to construct a plot without timepoint information.
 plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTypes = list(), omittedTypes = list(),
                                                     title = "Mismatch Position Frequencies", posType = THREE_PRIME,
-                                                    zScoreTables = NULL, zScoreCutoff = 4) {
+                                                    zScoreTables = NULL, zScoreCutoff = 4, xAxisBreaks = -3:3*10) {
 
   #If passed a single data.table, wrap it in a list.
   if (is.data.table(simplifiedTables)) {
@@ -90,10 +90,8 @@ plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTy
 
   if (posType == THREE_PRIME) {
     xAxisLabel = "3' Relative Position"
-    xAxisBreaks = c(0, -10, -20)
   } else if (posType == FIVE_PRIME) {
     xAxisLabel = "5' Relative Position"
-    xAxisBreaks = c(0, 10, 20)
     simplifiedTables = lapply(simplifiedTables, copy)
     lapply(simplifiedTables, function(x) x[, Position := Read_Length + Position + 1])
     if (!is.null(zScoreTables)) {
@@ -114,6 +112,8 @@ plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTy
 
   groupedPositionFrequencies = (aggregateMismatchesTable[, .N, by = list(Position,Read_Length,Timepoint)]
                                 [, Frequency := N/sum(N), by = list(Read_Length, Timepoint)])
+  modePosition = getMode(aggregateMismatchesTable$Position)
+
   if (!is.null(zScoreTables)) {
     aggregateZScoreTable = rbindlist(lapply(seq_along(zScoreTables),
                                             function(i) zScoreTables[[i]][,Timepoint := names(zScoreTables)[i]]))
@@ -146,8 +146,8 @@ plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTy
     theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
           strip.background = element_rect(color = "black", size = 1),
           axis.text.y = element_blank(), axis.ticks.y = element_blank(),
-          strip.text.y = element_text(size = 16),
[…]

### 2022-05-25 R/NHF1DeaminationAnchoredExcisionSiteDataGeneration.rmd
Notebook updates
- Several changes, mostly aesthetic
- Notable: Changed z-score filtering to use CPD z-scores for 6-4 filtering

@@
 # Further filter data by read position based on length
+# NOTE: 6-4 data uses CPD z-scores for filtering.
 CPDMismatchData = mapply(function(CPDMismatchDataRep, CPDMMFreqZScoreRep) mapply(
@@
 ), CPDMismatchData, CPDMMFreqZScores, SIMPLIFY = FALSE)
-sixFourMismatchData = mapply(function(sixFourMismatchDataRep, sixFourMMFreqZScoreRep) mapply(
-  filterMismatchesByPositionAndReadLength, sixFourMismatchDataRep, sixFourMMFreqZScoreRep,
-  expansionOffset = expansionOffset, SIMPLIFY = FALSE
-), sixFourMismatchData, sixFourMMFreqZScores, SIMPLIFY = FALSE)
+sixFourMismatchData = lapply(sixFourMismatchData, function(sixFourMismatchDataRep) {
+  lapply(sixFourMismatchDataRep, filterMismatchesByPositionAndReadLength,
+         CPDMMFreqZScores[[1]][[1]], expansionOffset = expansionOffset)
+})
 ```

### 2022-05-25 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
Notebook updates
- Several changes, mostly aesthetic
- Notable: Changed z-score filtering to use CPD z-scores for 6-4 filtering

@@
 
-```{r CPD_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 7}
+```{r CPD_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
 plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
@@
 
-```{r CPD_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 7}
+```{r CPD_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
 plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
@@
 
-```{r 6-4_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 7}
+```{r 6-4_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
 plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
@@
 
-```{r 6-4_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 7}
+```{r 6-4_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
 plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
@@
 
-```{r CPD_sequence_enrichment, fig.width = 11, fig.height = 7}
+```{r CPD_sequence_enrichment, fig.width = 11, fig.height = 9}
 plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment$rep1,
@@
 
-```{r 6-4_sequence_enrichment, fig.width = 11, fig.height = 7}
+```{r 6-4_sequence_enrichment, fig.width = 11, fig.height = 9}
 plotSequenceEnrichment(threePrimeMMAnchoredSixFourEnrichment$rep1,
@@
 
-```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 7}
+```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 9}
 plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq$rep1,
@@
 
-```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 7}
+```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 9}
 plotSequenceFrequencies(threePrimeMMAnchoredSixFourSeqFreq$rep1,

### 2022-05-26 R/NHF1DeaminationSequenceAndPositionDataGeneration.rmd
Fixed bug that previously wasn't actually fixed
Turns out the problem with NA's was in fwrite. Annoying.

@@
   for (j in 1:length(CPDMismatchData[[i]])) {
-    fwrite(CPDMismatchData[[i]][[j]], sep = '\t',
+    fwrite(CPDMismatchData[[i]][[j]], sep = '\t', na = "NA",
            file = generateFilePath(
@@
   for (j in 1:length(sixFourMismatchData[[i]])) {
-    fwrite(sixFourMismatchData[[i]][[j]], sep = '\t',
+    fwrite(sixFourMismatchData[[i]][[j]], sep = '\t', na = "NA",
            file = generateFilePath(

### 2022-05-26 R/DeaminationParseAndFilter.R

@@ -66,7 +66,6 @@ simplifyTable = function(table, includeReadSequence = FALSE, includeTrinucleotid
                 Trinuc_Context := paste0(str_sub(Read_Sequence, Position - 1, Position - 1),
                                          str_sub(Mismatch, 1, 1),
                                          str_sub(Read_Sequence, Position + 1, Position + 1))]
-    returnTable[nchar(Trinuc_Context) == 0, Trinuc_Context := NA]
     if (!includeReadSequence) returnTable[, Read_Sequence := NULL]
   }
 

### 2022-05-31 R/DeaminationAnchoredExcisionSiteAnalysis.R
More robust handling of data without timepoints

@@ -51,9 +51,9 @@ tabulateNucFreqByPosTimepointAndLength = function(simplifiedTablesByTimepoint, p
 
   #If passed a single data.table, wrap it in a list.
   if (is.data.table(simplifiedTablesByTimepoint)){
-    simplifiedTablesByTimepoint = list(simplifiedTablesByTimepoint)
-    noTimepoints = TRUE
-  } else noTimepoints = FALSE
+    simplifiedTablesByTimepoint = list(NONE = simplifiedTables)
+  }
+  noTimepoints = all(names(simplifiedTablesByTimepoint) == "NONE")
 
   # First, stratify the data by length and timepoint (optional),
   # calculating relative nucleotide frequencies within each category.
@@ -61,7 +61,7 @@ tabulateNucFreqByPosTimepointAndLength = function(simplifiedTablesByTimepoint, p
     rbindlist(lapply(unique(simplifiedTablesByTimepoint[[i]]$Read_Length), function(x) {
 
       if (noTimepoints) {
-        paddingInfo = list(x, NA)
+        paddingInfo = list(x, "NONE")
       } else {
         paddingInfo = list(x, names(simplifiedTablesByTimepoint)[i])
       }
@@ -126,7 +126,7 @@ plotNucFreqVsReadLengthBarPlot = function(nucFreqTable, posType = THREE_PRIME,
     labs(title = title, x = xAxisLabel, y = yAxisLabel) +
     blankBackground + defaultTextScaling
 
-  if (all(is.na(nucFreqTable$Timepoint))) {
+  if (all(nucFreqTable$Timepoint == "NONE")) {
     plot = plot + facet_grid(rows = vars(Read_Length))
   } else {
     plot = plot + facet_grid(Read_Length~factor(Timepoint, levels = unique(nucFreqTable$Timepoint)))

### 2022-05-31 R/DeaminationSequenceAndPositionAnalysis.R

@@ -163,9 +163,9 @@ plotReadLengthFrequencies = function(simplifiedTables, title = "Read Length Freq
 
   #If passed a single data.table, wrap it in a list.
   if (is.data.table(simplifiedTables)) {
-    simplifiedTables = list(None = simplifiedTables)
-    noTimepointInfo = TRUE
-  } else noTimepointInfo = FALSE
+    simplifiedTables = list(NONE = simplifiedTables)
+  }
+  noTimepointInfo = all(names(simplifiedTables) == "NONE")
 
   aggregateTable = rbindlist(lapply(seq_along(simplifiedTables),
                                     function(i) simplifiedTables[[i]][,Timepoint := names(simplifiedTables)[i]]))
@@ -280,9 +280,9 @@ plotGroupedPositionStats = function(threePrimeGroupedStats, fivePrimeGroupedStat
     labs(title = title, x = "Read Length", y = stat) +
     scale_x_continuous(breaks = xAxisBreaks)
 
-  if (all(aggregateData$Timepoint == "None")) {
+  if (all(aggregateData$Timepoint == "NONE")) {
     groupedStatsPlot = groupedStatsPlot +
-      scale_color_grey() + theme(legend.position = "none")
+      scale_color_grey(guide = "none")
   } else groupedStatsPlot = groupedStatsPlot + scale_color_brewer(palette = "Set1")
 
   print(groupedStatsPlot)

### 2022-05-31 R/UsefulFileSystemFunctions.R
Reordered file path pieces

@@ -35,8 +35,8 @@ generateFilePath = function(directory, dataTypeString, fileExtension,
   else anchoredText = NA
 
   basenameParts = c(cellType, lesion, timepoint, repitition, includedMismatches, omittedMismatches, "omitted",
-                    strandPolarity, anchoredText, sequence, additionalInformation, dataTypeString, expansionText,
-                    filtering)
+                    strandPolarity, anchoredText, sequence, dataTypeString, expansionText, filtering,
+                    additionalInformation)
   if (length(omittedMismatches) == 0) basenameParts[5+length(includedMismatches)] = NA
   basenameParts = basenameParts[!is.na(basenameParts)]
 

### 2022-05-31 R/DrosophilaDeaminationAnchoredExcisionSiteDataGeneration.rmd
Created drosophila notebooks

--- 2022-05-20 R/NHF1DeaminationAnchoredExcisionSiteDataGeneration.rmd
@@
 ---
-title: "NHF1 Deamination Anchored Excision Site Data Generation"
+title: "Dm Deamination Anchored Excision Site Data Generation"
 author: "Ben Morledge-Hampton"
@@
 expansionOffset = 10
-cellType = "NHF1"
-CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
-sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
+cellType = "Dm"
+CPDTimepoints = list(`10m` = NULL, `30m` = NULL, `8h` = NULL, `16h` = NULL, `24h` = NULL)
+minReadLength = 23; maxReadLength = 32
 
@@
 }
-
-sixFourMismatchData = list(rep1 = sixFourTimepoints,
-                           rep2 = sixFourTimepoints)
-for (i in 1:length(sixFourMismatchData)) {
-  for (j in 1:length(sixFourMismatchData[[i]])) {
-    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
-      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
-      cellType = cellType, lesion = "6-4-PP", timepoint = names(sixFourMismatchData[[i]])[j],
-      repitition = names(sixFourMismatchData)[i], expansionNum = expansionOffset, filtering = filtering
-      ))
-  }
-}
 ```
@@
 CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
-  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = 23, maxReadLength = 31)
-))
-sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
-  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = 23, maxReadLength = 31)
+  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = minReadLength, maxReadLength = maxReadLength)
 ))
@@
 CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
-  x, function(y) simplifyTable(y, TRUE, expansionOffset = expansionOffset)
-))
-sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
   x, function(y) simplifyTable(y, TRUE, expansionOffset = expansionOffset)
@@
 
-sixFourMMFreqZScores = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
-for (i in seq_along(sixFourMMFreqZScores)) {
-  for (j in seq_along(sixFourMMFreqZScores[[i]])) {
-    sixFourMMFreqZScores[[i]][[j]] = fread(generateFilePath(
-      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
-      cellType = cellType, lesion = "6-4", repitition = names(sixFourMMFreqZScores)[i],
-      timepoint = names(sixFourMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
-    ))
-  }
-}
-
 # Further filter data by read position based on length
@@
 ), CPDMismatchData, CPDMMFreqZScores, SIMPLIFY = FALSE)
-sixFourMismatchData = mapply(function(sixFourMismatchDataRep, sixFourMMFreqZScoreRep) mapply(
-  filterMismatchesByPositionAndReadLength, sixFourMismatchDataRep, sixFourMMFreqZScoreRep,
-  expansionOffset = expansionOffset, SIMPLIFY = FALSE
-), sixFourMismatchData, sixFourMMFreqZScores, SIMPLIFY = FALSE)
 ```
@@
 ```{r orient_data_to_mismatch_positions}
-# NOTE: The assignments to null are there so that the garbage collector can free up memory, and
+# NOTE: The assignment to null is there so that the garbage collector can free up memory, and
 #       I can still switch to new variable names for organizational purposes.
@@
 CPDMismatchData = NULL
-
-threePrimeMismatchAnchoredSixFourData = lapply(sixFourMismatchData, function(x) {
-  lapply(x, orientDataToMismatch, THREE_PRIME, expansionOffset)
-})
-fivePrimeMismatchAnchoredSixFourData = lapply(sixFourMismatchData, function(x) {
-  lapply(x, orientDataToMismatch, FIVE_PRIME, expansionOffset)
-})
-sixFourMismatchData = NULL
 ```
@@
     cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMismatchCPDNucFreq)[i],
-    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering
-  ))
-}
-
-threePrimeMismatchSixFourNucFreq = lapply(threePrimeMismatchAnchoredSixFourData,
-                                          tabulateNucFreqByPosTimepointAndLength)
-for (i in seq_along(threePrimeMismatchSixFourNucFreq)) {
-  fwrite(threePrimeMismatchSixFourNucFreq[[i]], sep = '\t', file = generateFilePath(
-    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
-    cellType = cellType, lesion = "6-4", repitition = names(threePrimeMismatchSixFourNucFreq)[i],
-    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering
-  ))
-}
-
-fivePrimeMismatchSixFourNucFreq = lapply(fivePrimeMismatchAnchoredSixFourData,
-                                         tabulateNucFreqByPosTimepointAndLength, posType = FIVE_PRIME)
-for (i in seq_along(fivePrimeMismatchSixFourNucFreq)) {
-  fwrite(fivePrimeMismatchSixFourNucFreq[[i]], sep = '\t', file = generateFilePath(
-    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
-    cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMismatchSixFourNucFreq)[i],
     strandPolarity = "five_prime", anchored = TRUE, filtering = filtering
@@
 }
-
-threePrimeMMAnchoredSixFourEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
-  setNames(lapply(seq_along(mismatchDataRep), function(i) {
-    getSequenceFreqByReadLengthAndPos(mismatchDataRep[[i]],
-                                      nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
-                                      c("CG","CA","TG","TA"))
-  }), names(mismatchDataRep))
-}, threePrimeMismatchAnchoredSixFourData, threePrimeMismatchSixFourNucFreq, SIMPLIFY = FALSE)
-for (i in seq_along(threePrimeMMAnchoredSixFourEnrichment)) {
-  for (j in seq_along(threePrimeMMAnchoredSixFourEnrichment[[i]])) {
-    fwrite(threePrimeMMAnchoredSixFourEnrichment[[i]][[j]], sep = '\t', file = generateFilePath(
-      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
-      cellType = cellType, lesion = "6-4", repitition = names(threePrimeMMAnchoredSixFourEnrichment)[i],
-      timepoint = names(threePrimeMMAnchoredSixFourEnrichment[[i]])[j], strandPolarity = "three_prime",
-      anchored = TRUE, sequence = "YR", filtering = filtering
-    ))
-  }
-}
-
-fivePrimeMMAnchoredSixFourEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
-  setNames(lapply(seq_along(mismatchDataRep), function(i) {
-    getSequenceFreqByReadLengthAndPos(mismatchDataRep[[i]],
-                                      nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
-                                      c("TGG"), posType = FIVE_PRIME)
-  }), names(mismatchDataRep))
-}, fivePrimeMismatchAnchoredSixFourData, fivePrimeMismatchSixFourNucFreq, SIMPLIFY = FALSE)
-for (i in seq_along(fivePrimeMMAnchoredSixFourEnrichment)) {
-  for (j in seq_along(fivePrimeMMAnchoredSixFourEnrichment[[i]])) {
-    fwrite(fivePrimeMMAnchoredSixFourEnrichment[[i]][[j]], sep = '\t', file = generateFilePath(
-      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
-      cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMMAnchoredSixFourEnrichment)[i],
-      timepoint = names(fivePrimeMMAnchoredSixFourEnrichment[[i]])[j], strandPolarity = "five_prime",
-      anchored = TRUE, sequence = "TGG", filtering = filtering
-    ))
-  }
-}
 ```
@@
 }
-
-threePrimeMMAnchoredSixFourSeqFreq = lapply(threePrimeMismatchAnchoredSixFourData, function(mismatchDataRep) {
-  lapply(mismatchDataRep, function(mismatchData) {
-    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("CG","CA","TG","TA"))
-  })
-})
-for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
-  for (j in seq_along(threePrimeMMAnchoredSixFourSeqFreq[[i]])) {
-    fwrite(threePrimeMMAnchoredSixFourSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
-      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
-      cellType = cellType, lesion = "6-4", repitition = names(threePrimeMMAnchoredSixFourSeqFreq)[i],
-      timepoint = names(threePrimeMMAnchoredSixFourSeqFreq[[i]])[j], strandPolarity = "three_prime",
-      anchored = TRUE, sequence = "YR", filtering = filtering
-    ))
-  }
-}
-
-fivePrimeMMAnchoredSixFourSeqFreq = lapply(fivePrimeMismatchAnchoredSixFourData, function(mismatchDataRep) {
-  lapply(mismatchDataRep, function(mismatchData) {
-    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("TGG"), posType = FIVE_PRIME)
-  })
-})
-for (i in seq_along(fivePrimeMMAnchoredSixFourSeqFreq)) {
-  for (j in seq_along(fivePrimeMMAnchoredSixFourSeqFreq[[i]])) {
-    fwrite(fivePrimeMMAnchoredSixFourSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
-      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
-      cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMMAnchoredSixFourSeqFreq)[i],
-      timepoint = names(fivePrimeMMAnchoredSixFourSeqFreq[[i]])[j], strandPolarity = "five_prime",
-      anchored = TRUE, sequence = "TGG", filtering = filtering
-    ))
-  }
-}
 ```

### 2022-05-31 R/DrosophilaDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Created drosophila notebooks

--- 2022-05-25 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
@@
 ---
-title: "NHF1 Deamination Anchored Excision Site Figure Generation"
+title: "Dm Deamination Anchored Excision Site Figure Generation"
 author: "Ben Morledge-Hampton"
@@
     cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMismatchCPDNucFreq)[i],
-    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering
-  ))
-}
-
-threePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL)
-for (i in seq_along(threePrimeMismatchSixFourNucFreq)) {
-  threePrimeMismatchSixFourNucFreq[[i]] = fread(generateFilePath(
-    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
-    cellType = cellType, lesion = "6-4", repitition = names(threePrimeMismatchSixFourNucFreq)[i],
-    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering
-  ))
-}
-
-fivePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL)
-for (i in seq_along(fivePrimeMismatchSixFourNucFreq)) {
-  fivePrimeMismatchSixFourNucFreq[[i]] = fread(generateFilePath(
-    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
-    cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMismatchSixFourNucFreq)[i],
     strandPolarity = "five_prime", anchored = TRUE, filtering = filtering
@@
 
-```{r 6-4_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
-                               title = paste(c("6-4", titleCaseFiltering, "3' Anchored Nuc Freq Rep1"), collapse = ' '),
-                               secondaryYAxisLabel = "5' Cut Site Distance",
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
-                               title = paste(c("6-4", titleCaseFiltering, "3' Anchored Nuc Freq Rep2"), collapse = ' '),
-                               secondaryYAxisLabel = "5' Cut Site Distance",
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep1, 
-                               title = paste(c("6-4", titleCaseFiltering, "5' Anchored Nuc Freq Rep1"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep2, 
-                               title = paste(c("6-4", titleCaseFiltering, "5' Anchored Nuc Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-```
-
-```{r 6-4_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
-                               title = paste(c("6-4", titleCaseFiltering, "3' Anchored Purine Freq Rep1"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
-                               title = paste(c("6-4", titleCaseFiltering, "3' Anchored Purine Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep1, 
-                               title = paste(c("6-4", titleCaseFiltering, "5' Anchored Purine Freq Rep1"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep2, 
-                               title = paste(c("6-4", titleCaseFiltering, "5' Anchored Purine Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-```
-
 ```{r read_sequence_enrichment_data}
@@
 }
-
-threePrimeMMAnchoredSixFourEnrichment = list(rep1 = sixFourTimepoints,
-                                             rep2 = sixFourTimepoints)
-for (i in seq_along(threePrimeMMAnchoredSixFourEnrichment)) {
-  for (j in seq_along(threePrimeMMAnchoredSixFourEnrichment[[i]])) {
-    threePrimeMMAnchoredSixFourEnrichment[[i]][[j]] = fread(generateFilePath(
-      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
-      cellType = cellType, lesion = "6-4", repitition = names(threePrimeMMAnchoredSixFourEnrichment)[i],
-      timepoint = names(threePrimeMMAnchoredSixFourEnrichment[[i]])[j], strandPolarity = "three_prime",
-      anchored = TRUE, sequence = "YR", filtering = filtering
-    ))
-  }
-}
-
-fivePrimeMMAnchoredSixFourEnrichment = list(rep1 = sixFourTimepoints,
-                                            rep2 = sixFourTimepoints)
-for (i in seq_along(fivePrimeMMAnchoredSixFourEnrichment)) {
-  for (j in seq_along(fivePrimeMMAnchoredSixFourEnrichment[[i]])) {
-    fivePrimeMMAnchoredSixFourEnrichment[[i]][[j]] = fread(generateFilePath(
-      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
-      cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMMAnchoredSixFourEnrichment)[i],
-      timepoint = names(fivePrimeMMAnchoredSixFourEnrichment[[i]])[j], strandPolarity = "five_prime",
-      anchored = TRUE, sequence = "TGG", filtering = filtering
-    ))
-  }
-}
 ```
@@
                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
-```
-
-```{r 6-4_sequence_enrichment, fig.width = 11, fig.height = 9}
-plotSequenceEnrichment(threePrimeMMAnchoredSixFourEnrichment$rep1,
-                       title = paste(c("6-4", titleCaseFiltering, "3' Anchored YR Enrichment Rep1"), collapse = ' '),
-                       secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
-                       expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
-plotSequenceEnrichment(threePrimeMMAnchoredSixFourEnrichment$rep2,
-                       title = paste(c("6-4", titleCaseFiltering, "3' Anchored YR Enrichment Rep2"), collapse = ' '),
-                       secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
-                       expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
-
-plotSequenceEnrichment(fivePrimeMMAnchoredSixFourEnrichment$rep1,
-                       title = paste(c("6-4", titleCaseFiltering, "5' Anchored TGG Enrichment Rep1"), collapse = ' '),
-                       secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
-                       expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
-plotSequenceEnrichment(fivePrimeMMAnchoredSixFourEnrichment$rep2,
-                       title = paste(c("6-4", titleCaseFiltering, "5' Anchored TGG Enrichment Rep2"), collapse = ' '),
-                       secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
-                       expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
-```
-
-```{r enrichment_test_1}
-# for (i in 1:5) {
-#   testTable = data.table(Read_Length = 9,
-#                          Read_Sequence = replicate(1000, paste0(sample(c('A','C','G','T'), 9, TRUE), collapse = '')))
-#   testTableNucFreq = tabulateNucFreqByPosTimepointAndLength(testTable)
-#   testEnrichment = getSequenceFreqByReadLengthAndPos(testTable, testTableNucFreq, c("CG","CA","TG","TA"))
-#   plotSequenceEnrichment(testEnrichment, title = "CPD 3' Anchored YR Enrichment Rep1")
-# }
-```
-
-```{r enrichment_test_2}
-# for (i in 1:5) {
-#   testTable = data.table(Read_Length = 9,
-#                          Read_Sequence = replicate(1000,
-#                                                    paste0(sample(c(rep('A',6),rep('C',4),rep('G',4),rep('T',6)),
-#                                                                  9, TRUE), collapse = '')))
-#   testTableNucFreq = tabulateNucFreqByPosTimepointAndLength(testTable)
-#   testEnrichment = getSequenceFreqByReadLengthAndPos(testTable, testTableNucFreq, c("CG","CA","TG","TA"))
-#   plotSequenceEnrichment(testEnrichment, title = "CPD 3' Anchored YR Enrichment Rep1")
-# }
 ```
@@
 }
-
-threePrimeMMAnchoredSixFourSeqFreq = list(rep1 = sixFourTimepoints,
-                                          rep2 = sixFourTimepoints)
-for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
-  for (j in seq_along(threePrimeMMAnchoredSixFourSeqFreq[[i]])) {
-    threePrimeMMAnchoredSixFourSeqFreq[[i]][[j]] = fread(generateFilePath(
-      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
-      cellType = cellType, lesion = "6-4", repitition = names(threePrimeMMAnchoredSixFourSeqFreq)[i],
-      timepoint = names(threePrimeMMAnchoredSixFourSeqFreq[[i]])[j], strandPolarity = "three_prime",
-      anchored = TRUE, sequence = "YR", filtering = filtering
-    ))
-  }
-}
-
-fivePrimeMMAnchoredSixFourSeqFreq = list(rep1 = sixFourTimepoints,
-                                         rep2 = sixFourTimepoints)
-for (i in seq_along(fivePrimeMMAnchoredSixFourSeqFreq)) {
-  for (j in seq_along(fivePrimeMMAnchoredSixFourSeqFreq[[i]])) {
-    fivePrimeMMAnchoredSixFourSeqFreq[[i]][[j]] = fread(generateFilePath(
-      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
-      cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMMAnchoredSixFourSeqFreq)[i],
-      timepoint = names(fivePrimeMMAnchoredSixFourSeqFreq[[i]])[j], strandPolarity = "five_prime",
-      anchored = TRUE, sequence = "TGG", filtering = filtering
-    ))
-  }
-}
 ```
@@
 ```
-
-```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 9}
-plotSequenceFrequencies(threePrimeMMAnchoredSixFourSeqFreq$rep1,
-                        title = paste(c("6-4", titleCaseFiltering, "3' Anchored YR Freq Rep1"), collapse = ' '),
-                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
-                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
-plotSequenceFrequencies(threePrimeMMAnchoredSixFourSeqFreq$rep2,
-                        title = paste(c("6-4", titleCaseFiltering, "3' Anchored YR Freq Rep2"), collapse = ' '),
-                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
-                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
-
-plotSequenceFrequencies(fivePrimeMMAnchoredSixFourSeqFreq$rep1,
-                        title = paste(c("6-4", titleCaseFiltering, "5' Anchored TGG Freq Rep1"), collapse = ' '),
-                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
-                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
-plotSequenceFrequencies(fivePrimeMMAnchoredSixFourSeqFreq$rep2,
-                        title = paste(c("6-4", titleCaseFiltering, "5' Anchored TGG Freq Rep2"), collapse = ' '),
-                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
-                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
-```

### 2022-05-31 R/DrosophilaDeaminationSequenceAndPositionDataGeneration.rmd
Created drosophila notebooks

--- 2022-05-20 R/NHF1DeaminationSequenceAndPositionDataGeneration.rmd
@@
 ---
-title: "NHF1 Deamination Sequence and Position Data Generation"
+title: "Dm Deamination Sequence and Position Data Generation"
 author: "Ben Morledge-Hampton"
@@
 
-cellType = "NHF1"
-CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
-sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
 expansionOffset = 0
+cellType = "Dm"
+CPDTimepoints = list(`10m` = NULL, `30m` = NULL, `8h` = NULL, `16h` = NULL, `24h` = NULL)
+minReadLength = 23; maxReadLength = 32
 
@@
 }
-
-sixFourMismatchData = list(rep1 = sixFourTimepoints,
-                           rep2 = sixFourTimepoints)
-for (i in 1:length(sixFourMismatchData)) {
-  for (j in 1:length(sixFourMismatchData[[i]])) {
-    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
-      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
-      cellType = cellType, lesion = "6-4-PP", timepoint = names(sixFourMismatchData[[i]])[j],
-      repitition = names(sixFourMismatchData)[i], filtering = filtering
-      ))
-  }
-}
 ```
@@
 CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
-  x, function(y) filterResults(y, TRUE, 3, 23, 31)
-))
-sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
-  x, function(y) filterResults(y, TRUE, 3, 23, 31)
+  x, function(y) filterResults(y, TRUE, 3, minReadLength, maxReadLength)
 ))
@@
 ))
-sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
-  x, function(y) simplifyTable(y, includeTrinucleotideContext = TRUE)
-))
 
@@
              repitition = names(CPDMismatchData)[i], filtering = filtering
-           ))
-  }
-}
-
-for (i in 1:length(sixFourMismatchData)) {
-  for (j in 1:length(sixFourMismatchData[[i]])) {
-    fwrite(sixFourMismatchData[[i]][[j]], sep = '\t',
-           file = generateFilePath(
-             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
-             cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
-             repitition = names(sixFourMismatchData)[i], filtering = filtering
            ))
@@
 CPDMMFreqZScores = lapply(CPDMismatchData, function(x) lapply(
-  x, function(y) {
-    getMismatchFrequencyZScoreByPosAndReadLength(y[Mismatch == "C>T"], expansionOffset)
-  }
-))
-sixFourMMFreqZScores = lapply(sixFourMismatchData, function(x) lapply(
   x, function(y) {
@@
 }
-
-for (i in seq_along(sixFourMMFreqZScores)) {
-  for (j in seq_along(sixFourMMFreqZScores[[i]])) {
-    fwrite(sixFourMMFreqZScores[[i]][[j]], sep = '\t', file = generateFilePath(
-      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
-      cellType = cellType, lesion = "6-4", repitition = names(sixFourMMFreqZScores)[i],
-      timepoint = names(sixFourMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
-    ))
-  }
-}
 ```
@@
 
-sixFourGroupedStats = list(rep1 = list(), rep2 = list())
-sixFourGroupedStats$rep1$three_prime = getGroupedPositionStats(sixFourMismatchData$rep1, includedTypes = c("C>T"))
-sixFourGroupedStats$rep2$three_prime = getGroupedPositionStats(sixFourMismatchData$rep2, includedTypes = c("C>T"))
-sixFourGroupedStats$rep1$five_prime =
-  getGroupedPositionStats(sixFourMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME)
-sixFourGroupedStats$rep2$five_prime =
-  getGroupedPositionStats(sixFourMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME)
-
 for (i in seq_along(CPDGroupedStats)) {
@@
 }
-
-for (i in seq_along(sixFourGroupedStats)) {
-  for (j in seq_along(sixFourGroupedStats[[i]])) {
-    fwrite(sixFourGroupedStats[[i]][[j]], sep = '\t',
-           file = generateFilePath(
-             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
-             cellType = cellType, lesion = "6-4", repitition = names(sixFourGroupedStats)[i],
-             strandPolarity = names(sixFourGroupedStats[[i]])[j], filtering = filtering
-           ))
-  }
-}
 ```

### 2022-05-31 R/DrosophilaDeaminationSequenceAndPositionFigureGeneration.rmd
Created drosophila notebooks

--- 2022-05-24 R/NHF1DeaminationSequenceAndPositionFigureGeneration.rmd
@@
 ---
-title: "NHF1 Deamination Sequence and Position Figure Generation"
+title: "Dm Deamination Sequence and Position Figure Generation"
 author: "Ben Morledge-Hampton"
@@
 
-cellType = "NHF1"
-CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
-sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
-minReadLength = 22; maxReadLength = 30
+cellType = "Dm"
+CPDTimepoints = list(`10m` = NULL, `30m` = NULL, `8h` = NULL, `16h` = NULL, `24h` = NULL)
+minReadLength = 23; maxReadLength = 32
 
@@
 }
-
-sixFourMismatchData = list(rep1 = sixFourTimepoints,
-                           rep2 = sixFourTimepoints)
-for (i in seq_along(sixFourMismatchData)) {
-  for (j in seq_along(sixFourMismatchData[[i]])) {
-    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
-      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
-      cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
-      repitition = names(sixFourMismatchData)[i], filtering = filtering
-    ))
-  }
-}
 ```
@@
                                                 names(CPDMismatchData[[i]])[j], "Mismatch Type Frequency"),
-                                              collapse = ' '))
-  }
-}
-```
-
-```{r 6-4_mismatch_type_frequency}
-for (i in 1:length(sixFourMismatchData)) {
-  for (j in 1:length(sixFourMismatchData[[i]])) {
-    plotMismatchTypeFrequencies(sixFourMismatchData[[i]][[j]],
-                                title = paste(c("6-4", titleCaseFiltering, names(sixFourMismatchData)[i], 
-                                                names(sixFourMismatchData[[i]])[j], "Mismatch Type Frequency"),
                                               collapse = ' '))
@@
 
-```{r 6-4_mismatch_pos_frequency}
-for (i in 1:length(sixFourMismatchData)) {
-  for (j in 1:length(sixFourMismatchData[[i]])) {
-    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], includedTypes = c("C>T"),
-                                    title = paste(c("6-4", titleCaseFiltering, names(sixFourMismatchData)[i], 
-                                                    names(sixFourMismatchData[[i]])[j], "C>T Mismatch Positions"),
-                                                  collapse = ' '))
-    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], omittedTypes = c("C>T"),
-                                    title = paste(c("6-4", titleCaseFiltering, names(sixFourMismatchData)[i], 
-                                                    names(sixFourMismatchData[[i]])[j], "!C>T Mismatch Positions"),
-                                                  collapse = ' '))
-  }
-}
-```
-
 ```{r CPD_trinucleotide_context_analysis}
@@
                                              names(CPDMismatchData[[i]])[j], "C>T Mismatch Trinuc Context"),
-                                           collapse = ' '))
-  }
-}
-```
-
-```{r 6-4_trinucleotide_context_analysis}
-for (i in 1:length(sixFourMismatchData)) {
-  for (j in 1:length(sixFourMismatchData[[i]])) {
-    plotTrinucleotideContext(sixFourMismatchData[[i]][[j]], includedTypes = c("C>T"),
-                             title = paste(c("6-4", titleCaseFiltering, names(sixFourMismatchData)[i],
-                                             names(sixFourMismatchData[[i]])[j], "C>T Mismatch Trinuc Context"),
                                            collapse = ' '))
@@
       timepoint = names(CPDMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
-    ))
-  }
-}
-
-sixFourMMFreqZScores = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
-for (i in seq_along(sixFourMMFreqZScores)) {
-  for (j in seq_along(sixFourMMFreqZScores[[i]])) {
-    sixFourMMFreqZScores[[i]][[j]] = fread(generateFilePath(
-      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
-      cellType = cellType, lesion = "6-4", repitition = names(sixFourMMFreqZScores)[i],
-      timepoint = names(sixFourMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
     ))
@@
 
-```{r 6-4_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, includedTypes = c("C>T"),
-                                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
-                                                       collapse = ' '),
-                                         zScoreTables = sixFourMMFreqZScores$rep1)
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, includedTypes = c("C>T"),
-                                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
-                                                       collapse = ' '),
-                                         zScoreTables = sixFourMMFreqZScores$rep2)
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME,
-                                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
-                                                       collapse = ' '),
-                                         zScoreTables = sixFourMMFreqZScores$rep1)
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME,
-                                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
-                                                       collapse = ' '),
-                                         zScoreTables = sixFourMMFreqZScores$rep2)
-```
-
 ```{r CPD_read_length_distributions}
@@
                           title = paste(c("CPD", titleCaseFiltering, "Read Length Freq Rep 2"), collapse = ' '))
-```
-
-```{r 6-4_read_length_distributions}
-plotReadLengthFrequencies(sixFourMismatchData$rep1,
-                          title = paste(c("6-4", titleCaseFiltering, "Read Length Freq Rep 1"), collapse = ' '))
-plotReadLengthFrequencies(sixFourMismatchData$rep2,
-                          title = paste(c("6-4", titleCaseFiltering, "Read Length Freq Rep 2"), collapse = ' '))
 ```
@@
 }
-
-sixFourGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
-                           rep2 = list(three_prime = NULL, five_prime = NULL))
-for (i in seq_along(sixFourGroupedStats)) {
-  for (j in seq_along(sixFourGroupedStats[[i]])) {
-    sixFourGroupedStats[[i]][[j]] = fread(generateFilePath(
-      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
-      cellType = cellType, lesion = "6-4", repitition = names(sixFourGroupedStats)[i],
-      strandPolarity = names(sixFourGroupedStats[[i]])[j], filtering = filtering
-    ))
-  }
-}
 ```
@@
 ```
-
-```{r 6-4_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
-plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, POS_DIFF,
-                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Diff Rep1"), collapse = ' '),
-                         xAxisBreaks = c(minReadLength:maxReadLength))
-plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, POS_DIFF,
-                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Diff Rep2"), collapse = ' '),
-                         xAxisBreaks = c(minReadLength:maxReadLength))
-```

### 2022-05-31 R/DrosophilaGeneralReadSequenceDataGeneration.rmd
Created drosophila notebooks

--- 2022-05-24 R/NHF1GeneralReadSequenceDataGeneration.rmd
@@
 ---
-title: "NHF1 General Read Sequence Data Generation"
+title: "Dm General Read Sequence Data Generation"
 author: "Ben Morledge-Hampton"
@@
 expansionOffset = 10
-cellType = "NHF1"
-CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
-sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
-minReadLength = 22; maxReadLength = 30
+cellType = "Dm"
+CPDTimepoints = list(`10m` = NULL, `30m` = NULL, `8h` = NULL, `16h` = NULL, `24h` = NULL)
+minReadLength = 23; maxReadLength = 32
 
@@
 ```
-
-```{r compute_and_write_6-4_sequence_frequency}
-for (repitition in c("rep1", "rep2")) {
-  for (timepoint in names(sixFourTimepoints)) {
-    singleFileFullAnalysis("6-4", repitition, timepoint)
-  }
-}
-```

### 2022-05-31 R/DrosophilaGeneralReadSequenceFigureGeneration.rmd
Created drosophila notebooks

--- 2022-05-24 R/NHF1GeneralReadSequenceFigureGeneration.rmd
@@
 ---
-title: "NHF1 General Read Sequence Figure Generation"
+title: "Dm General Read Sequence Figure Generation"
 author: "Ben Morledge-Hampton"
@@
 }
-
-sixFourTGGSeqFreq = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
-for (i in seq_along(sixFourTGGSeqFreq)) {
-  for (j in seq_along(sixFourTGGSeqFreq[[i]])) {
-    sixFourTGGSeqFreq[[i]][[j]] = fread(generateFilePath(
-      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
-      cellType = cellType, lesion = "6-4", repitition = names(sixFourTGGSeqFreq)[i],
-      timepoint = names(sixFourTGGSeqFreq[[i]])[j], sequence = "TGG"
-    ))
-  }
-}
-
-sixFourCGASeqFreq = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
-for (i in seq_along(sixFourCGASeqFreq)) {
-  for (j in seq_along(sixFourCGASeqFreq[[i]])) {
-    sixFourCGASeqFreq[[i]][[j]] = fread(generateFilePath(
-      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
-      cellType = cellType, lesion = "6-4", repitition = names(sixFourCGASeqFreq)[i],
-      timepoint = names(sixFourCGASeqFreq[[i]])[j], sequence = "CGA"
-    ))
-  }
-}
 ```
@@
                         title = "CPD CGA Frequencies Rep2", expansionOffset = expansionOffset,
-                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
-                        querySequences = c("CGA"))
-```
-
-```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 10}
-plotSequenceFrequencies(sixFourTGGSeqFreq$rep1,
-                        title = "6-4 TGG Frequencies Rep1", expansionOffset = expansionOffset,
-                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
-                        querySequences = c("TGG"))
-plotSequenceFrequencies(sixFourTGGSeqFreq$rep2,
-                        title = "6-4 TGG Frequencies Rep2", expansionOffset = expansionOffset,
-                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
-                        querySequences = c("TGG"))
-
-plotSequenceFrequencies(sixFourCGASeqFreq$rep1,
-                        title = "6-4 CGA Frequencies Rep1", expansionOffset = expansionOffset,
-                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
-                        querySequences = c("CGA"))
-plotSequenceFrequencies(sixFourCGASeqFreq$rep2,
-                        title = "6-4 CGA Frequencies Rep2", expansionOffset = expansionOffset,
                         showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
@@
 ```
-
-```{r 6-4_read_length_frequencies}
-readAndPlotReadLengthFrequencies("6-4", "rep1", sixFourTimepoints)
-readAndPlotReadLengthFrequencies("6-4", "rep2", sixFourTimepoints)
-```

### 2022-05-31 R/ArabidopsisDeaminationAnchoredExcisionSiteDataGeneration.rmd
Added Arabidopsis notebooks

--- 2022-05-31 R/DrosophilaDeaminationAnchoredExcisionSiteDataGeneration.rmd
@@
 ---
-title: "Dm Deamination Anchored Excision Site Data Generation"
+title: "Arabidopsis Deamination Anchored Excision Site Data Generation"
 author: "Ben Morledge-Hampton"
@@
 expansionOffset = 10
-cellType = "Dm"
-CPDTimepoints = list(`10m` = NULL, `30m` = NULL, `8h` = NULL, `16h` = NULL, `24h` = NULL)
-minReadLength = 23; maxReadLength = 32
+cellType = "Arabidopsis"
+CPDTimepoints = list(`ZT2` = NULL, `ZT14` = NULL)
+minReadLength = 24; maxReadLength = 30
 

### 2022-05-31 R/ArabidopsisDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Added Arabidopsis notebooks

--- 2022-05-31 R/DrosophilaDeaminationAnchoredExcisionSiteFigureGeneration.rmd
@@
 ---
-title: "Dm Deamination Anchored Excision Site Figure Generation"
+title: "Arabidopsis Deamination Anchored Excision Site Figure Generation"
 author: "Ben Morledge-Hampton"

### 2022-05-31 R/ArabidopsisDeaminationSequenceAndPositionDataGeneration.rmd
Added Arabidopsis notebooks

--- 2022-05-31 R/DrosophilaDeaminationSequenceAndPositionDataGeneration.rmd
@@
 ---
-title: "Dm Deamination Sequence and Position Data Generation"
+title: "Arabidopsis Deamination Sequence and Position Data Generation"
 author: "Ben Morledge-Hampton"
@@
 expansionOffset = 0
-cellType = "Dm"
-CPDTimepoints = list(`10m` = NULL, `30m` = NULL, `8h` = NULL, `16h` = NULL, `24h` = NULL)
-minReadLength = 23; maxReadLength = 32
+cellType = "Arabidopsis"
+CPDTimepoints = list(`ZT2` = NULL, `ZT14` = NULL)
+minReadLength = 24; maxReadLength = 30
 

### 2022-05-31 R/ArabidopsisDeaminationSequenceAndPositionFigureGeneration.rmd
Added Arabidopsis notebooks

--- 2022-05-31 R/DrosophilaDeaminationSequenceAndPositionFigureGeneration.rmd
@@
 ---
-title: "Dm Deamination Sequence and Position Figure Generation"
+title: "Arabidopsis Deamination Sequence and Position Figure Generation"
 author: "Ben Morledge-Hampton"
@@
 
-cellType = "Dm"
-CPDTimepoints = list(`10m` = NULL, `30m` = NULL, `8h` = NULL, `16h` = NULL, `24h` = NULL)
-minReadLength = 23; maxReadLength = 32
+cellType = "Arabidopsis"
+CPDTimepoints = list(`ZT2` = NULL, `ZT14` = NULL)
+minReadLength = 24; maxReadLength = 30
 

### 2022-05-31 R/ArabidopsisGeneralReadSequenceDataGeneration.rmd
Added Arabidopsis notebooks

--- 2022-05-31 R/DrosophilaGeneralReadSequenceDataGeneration.rmd
@@
 ---
-title: "Dm General Read Sequence Data Generation"
+title: "Arabidopsis General Read Sequence Data Generation"
 author: "Ben Morledge-Hampton"

### 2022-05-31 R/ArabidopsisGeneralReadSequenceFigureGeneration.rmd
Added Arabidopsis notebooks

--- 2022-05-31 R/DrosophilaGeneralReadSequenceFigureGeneration.rmd
@@
 ---
-title: "Dm General Read Sequence Figure Generation"
+title: "Arabidopsis General Read Sequence Figure Generation"
 author: "Ben Morledge-Hampton"

### 2022-05-31 R/CS-BDeaminationAnchoredExcisionSiteDataGeneration.rmd
Added CS-B notebooks

--- 2022-05-25 R/NHF1DeaminationAnchoredExcisionSiteDataGeneration.rmd
@@
 ---
-title: "NHF1 Deamination Anchored Excision Site Data Generation"
+title: "CS-B Deamination Anchored Excision Site Data Generation"
 author: "Ben Morledge-Hampton"
@@
 expansionOffset = 10
-cellType = "NHF1"
-CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
-sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
+cellType = "CS-B"
+CPDTimepoints = list(`1h` = NULL)
+sixFourTimepoints = list(`1h` = NULL)
 minReadLength = 22; maxReadLength = 30
@@
       mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
-      cellType = cellType, lesion = "6-4-PP", timepoint = names(sixFourMismatchData[[i]])[j],
+      cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
       repitition = names(sixFourMismatchData)[i], expansionNum = expansionOffset, filtering = filtering

### 2022-05-31 R/CS-BDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Added CS-B notebooks

--- 2022-05-25 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
@@
 ---
-title: "NHF1 Deamination Anchored Excision Site Figure Generation"
+title: "CS-B Deamination Anchored Excision Site Figure Generation"
 author: "Ben Morledge-Hampton"
@@
 expansionOffset = 10
-cellType = "NHF1"
-CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
-sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
+cellType = "CS-B"
+CPDTimepoints = list(`1h` = NULL)
+sixFourTimepoints = list(`1h` = NULL)
 

### 2022-05-31 R/CS-BDeaminationSequenceAndPositionDataGeneration.rmd
Added CS-B notebooks

--- 2022-05-26 R/NHF1DeaminationSequenceAndPositionDataGeneration.rmd
@@
 ---
-title: "NHF1 Deamination Sequence and Position Data Generation"
+title: "CS-B Deamination Sequence and Position Data Generation"
 author: "Ben Morledge-Hampton"
@@
 
-cellType = "NHF1"
-CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
-sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
+cellType = "CS-B"
+CPDTimepoints = list(`1h` = NULL)
+sixFourTimepoints = list(`1h` = NULL)
 expansionOffset = 0
@@
       mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
-      cellType = cellType, lesion = "6-4-PP", timepoint = names(sixFourMismatchData[[i]])[j],
+      cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
       repitition = names(sixFourMismatchData)[i], filtering = filtering

### 2022-05-31 R/CS-BDeaminationSequenceAndPositionFigureGeneration.rmd
Added CS-B notebooks

--- 2022-05-24 R/NHF1DeaminationSequenceAndPositionFigureGeneration.rmd
@@
 ---
-title: "NHF1 Deamination Sequence and Position Figure Generation"
+title: "CS-B Deamination Sequence and Position Figure Generation"
 author: "Ben Morledge-Hampton"
@@
 
-cellType = "NHF1"
-CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
-sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
+cellType = "CS-B"
+CPDTimepoints = list(`1h` = NULL)
+sixFourTimepoints = list(`1h` = NULL)
 minReadLength = 22; maxReadLength = 30

### 2022-05-31 R/CS-BGeneralReadSequenceDataGeneration.rmd
Added CS-B notebooks

--- 2022-05-24 R/NHF1GeneralReadSequenceDataGeneration.rmd
@@
 ---
-title: "NHF1 General Read Sequence Data Generation"
+title: "CS-B General Read Sequence Data Generation"
 author: "Ben Morledge-Hampton"

### 2022-05-31 R/CS-BGeneralReadSequenceFigureGeneration.rmd
Added CS-B notebooks

--- 2022-05-24 R/NHF1GeneralReadSequenceFigureGeneration.rmd
@@
 ---
-title: "NHF1 General Read Sequence Figure Generation"
+title: "CS-B General Read Sequence Figure Generation"
 author: "Ben Morledge-Hampton"

### 2022-05-31 R/DeaminationParseAndFilter.R
Added Z-score parameter for noise positions

@@ -93,7 +93,8 @@ filterMismatchesByPositionAndReadLength = function(mismatchTable, posZScoreByRea
 # Z scores are calculated relative to a background defined as the first 10 positions on the 5' end (which
 # should just be noise).
 # NOTE: Positions are assumed to be given relative to the three prime end (negative values)
-getMismatchFrequencyZScoreByPosAndReadLength = function(simplifiedMismatchData, expansionOffset) {
+getMismatchFrequencyZScoreByPosAndReadLength = function(simplifiedMismatchData, expansionOffset,
+                                                        noisePositions = 10) {
 
   # First, get position frequencies for each read length.
   mismatchPositionFrequencies = simplifiedMismatchData[, .N, by = list(Position,Read_Length)]
@@ -105,7 +106,8 @@ getMismatchFrequencyZScoreByPosAndReadLength = function(simplifiedMismatchData, 
 
     # Determine the cutoff value based on the background.
     relevantPositionFrequencies = mismatchPositionFrequencies[Read_Length == readLength]
-    background = relevantPositionFrequencies[Position >= -readLength & Position < -readLength + 10, Frequency]
+    background = relevantPositionFrequencies[Position >= -readLength & Position < -readLength + noisePositions,
+                                             Frequency]
     backgroundMean = mean(background)
     backgroundSD = sd(background)
 

### 2022-05-31 R/EcoliWTDeaminationAnchoredExcisionSiteDataGeneration.rmd
Added E coli notebooks

--- 2022-05-31 R/ArabidopsisDeaminationAnchoredExcisionSiteDataGeneration.rmd
@@
 ---
-title: "Arabidopsis Deamination Anchored Excision Site Data Generation"
+title: "E coli WT Deamination Anchored Excision Site Data Generation"
 author: "Ben Morledge-Hampton"
@@
 expansionOffset = 10
-cellType = "Arabidopsis"
-CPDTimepoints = list(`ZT2` = NULL, `ZT14` = NULL)
-minReadLength = 24; maxReadLength = 30
+cellType = "E_coli_WT"
+CPDTimepoints = list(`5min` = NULL)
+minReadLength = 11; maxReadLength = 13
 

### 2022-05-31 R/EcoliWTDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Added E coli notebooks

--- 2022-05-31 R/ArabidopsisDeaminationAnchoredExcisionSiteFigureGeneration.rmd
@@
 ---
-title: "Arabidopsis Deamination Anchored Excision Site Figure Generation"
+title: "E coli WT Deamination Anchored Excision Site Figure Generation"
 author: "Ben Morledge-Hampton"

### 2022-05-31 R/EcoliWTDeaminationSequenceAndPositionDataGeneration.rmd
Added E coli notebooks

--- 2022-05-31 R/ArabidopsisDeaminationSequenceAndPositionDataGeneration.rmd
@@
 ---
-title: "Arabidopsis Deamination Sequence and Position Data Generation"
+title: "E coli WT Deamination Sequence and Position Data Generation"
 author: "Ben Morledge-Hampton"
@@
 expansionOffset = 0
-cellType = "Arabidopsis"
-CPDTimepoints = list(`ZT2` = NULL, `ZT14` = NULL)
-minReadLength = 24; maxReadLength = 30
+cellType = "E_coli_WT"
+CPDTimepoints = list(`5min` = NULL)
+minReadLength = 11; maxReadLength = 13
 
@@
   x, function(y) {
-    getMismatchFrequencyZScoreByPosAndReadLength(y[Mismatch == "C>T"], expansionOffset)
+    getMismatchFrequencyZScoreByPosAndReadLength(y[Mismatch == "C>T"], expansionOffset, noisePositions = 5)
   }

### 2022-05-31 R/EcoliWTDeaminationSequenceAndPositionFigureGeneration.rmd
Added E coli notebooks

--- 2022-05-31 R/ArabidopsisDeaminationSequenceAndPositionFigureGeneration.rmd
@@
 ---
-title: "Arabidopsis Deamination Sequence and Position Figure Generation"
+title: "E coli WT Deamination Sequence and Position Figure Generation"
 author: "Ben Morledge-Hampton"
@@
 
-cellType = "Arabidopsis"
-CPDTimepoints = list(`ZT2` = NULL, `ZT14` = NULL)
-minReadLength = 24; maxReadLength = 30
+cellType = "E_coli_WT"
+CPDTimepoints = list(`5min` = NULL)
+minReadLength = 11; maxReadLength = 13
 

### 2022-05-31 R/EcoliWTGeneralReadSequenceDataGeneration.rmd
Added E coli notebooks

--- 2022-05-31 R/CS-BGeneralReadSequenceDataGeneration.rmd
@@
 ---
-title: "CS-B General Read Sequence Data Generation"
+title: "E coli WT General Read Sequence Data Generation"
 author: "Ben Morledge-Hampton"
@@
 expansionOffset = 10
-cellType = "CS-B"
-CPDTimepoints = list(`1h` = NULL)
-sixFourTimepoints = list(`1h` = NULL)
-minReadLength = 22; maxReadLength = 30
+cellType = "E_coli_WT"
+CPDTimepoints = list(`5min` = NULL)
+minReadLength = 11; maxReadLength = 13
 

### 2022-05-31 R/EcoliWTGeneralReadSequenceFigureGeneration.rmd
Added E coli notebooks

--- 2022-05-31 R/ArabidopsisGeneralReadSequenceFigureGeneration.rmd
@@
 ---
-title: "Arabidopsis General Read Sequence Figure Generation"
+title: "E coli WT General Read Sequence Figure Generation"
 author: "Ben Morledge-Hampton"

### 2022-05-31 R/GM12878DeaminationAnchoredExcisionSiteFigureGeneration.rmd
Added GM12878 cisplatin notebooks

---
title: "GM12878 Deamination Anchored Excision Site Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

```{r setup_chunk}
library(knitr)

expansionOffset = 10
cellType = "GM12878"
CisplatinTimepoints = list(`90min` = NULL)
minReadLength = 22; maxReadLength = 30

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
  filtering = readline("Filtering identifier (Input nothing for no filtering):")
  if (filtering == '') filtering = character()
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
  filtering = params$filtering
  if (filtering == "NONE") filtering = character()
}
if (length(filtering) > 0) {
  titleCaseFiltering = tools::toTitleCase(gsub('_', ' ', filtering))
} else titleCaseFiltering = character()

opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
               fig.path = paste0(file.path("deamination_analysis_output", cellType,
                                           paste(c(filtering,"deamination_anchored_excision_site_figures"), collapse = '_')),
                                 .Platform$file.sep))

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
deaminationExcisionSiteDataDirectory = file.path(deaminationDataDirectory, "excision_site_analysis")
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationAnchoredExcisionSiteAnalysis.R"))
```

```{r read_nucleotide_frequency_data}
threePrimeMismatchCisplatinNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(threePrimeMismatchCisplatinNucFreq)) {
  threePrimeMismatchCisplatinNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMismatchCisplatinNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering
  ))
}

fivePrimeMismatchCisplatinNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(fivePrimeMismatchCisplatinNucFreq)) {
  fivePrimeMismatchCisplatinNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMismatchCisplatinNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering
  ))
}
```

```{r cisplatin_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq$rep1, 
                               title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored Nuc Freq Rep1"), collapse = ' '),
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq$rep2, 
                               title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored Nuc Freq Rep2"), collapse = ' '),
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq$rep1, 
                               title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored Nuc Freq Rep1"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq$rep2, 
                               title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored Nuc Freq Rep2"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
```

```{r cisplatin_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq$rep1, 
                               title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored Purine Freq Rep1"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq$rep2, 
                               title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored Purine Freq Rep2"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq$rep1, 
                               title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored Purine Freq Rep1"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq$rep2, 
                               title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored Purine Freq Rep2"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
```

```{r read_sequence_enrichment_data}
threePrimeMMAnchoredCisplatinEnrichment = list(rep1 = CisplatinTimepoints,
                                               rep2 = CisplatinTimepoints)
for (i in seq_along(threePrimeMMAnchoredCisplatinEnrichment)) {
  for (j in seq_along(threePrimeMMAnchoredCisplatinEnrichment[[i]])) {
    threePrimeMMAnchoredCisplatinEnrichment[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMMAnchoredCisplatinEnrichment)[i],
      timepoint = names(threePrimeMMAnchoredCisplatinEnrichment[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering
    ))
  }
}

fivePrimeMMAnchoredCisplatinEnrichment = list(rep1 = CisplatinTimepoints,
                                              rep2 = CisplatinTimepoints)
for (i in seq_along(fivePrimeMMAnchoredCisplatinEnrichment)) {
  for (j in seq_along(fivePrimeMMAnchoredCisplatinEnrichment[[i]])) {
    fivePrimeMMAnchoredCisplatinEnrichment[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMMAnchoredCisplatinEnrichment)[i],
      timepoint = names(fivePrimeMMAnchoredCisplatinEnrichment[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering
    ))
  }
}
```

```{r cisplatin_sequence_enrichment, fig.width = 11, fig.height = 9}
plotSequenceEnrichment(threePrimeMMAnchoredCisplatinEnrichment$rep1,
                       title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored YR Enrichment Rep1"), collapse = ' '),
                       secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                       expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
plotSequenceEnrichment(threePrimeMMAnchoredCisplatinEnrichment$rep2,
                       title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored YR Enrichment Rep2"), collapse = ' '),
                       secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                       expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))

plotSequenceEnrichment(fivePrimeMMAnchoredCisplatinEnrichment$rep1,
                       title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored TGG Enrichment Rep1"), collapse = ' '),
                       secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                       expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
plotSequenceEnrichment(fivePrimeMMAnchoredCisplatinEnrichment$rep2,
                       title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored TGG Enrichment Rep2"), collapse = ' '),
                       secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                       expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
```

```{r read_sequence_frequency_data}
threePrimeMMAnchoredCisplatinSeqFreq = list(rep1 = CisplatinTimepoints,
                                            rep2 = CisplatinTimepoints)
for (i in seq_along(threePrimeMMAnchoredCisplatinSeqFreq)) {
  for (j in seq_along(threePrimeMMAnchoredCisplatinSeqFreq[[i]])) {
    threePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMMAnchoredCisplatinSeqFreq)[i],
      timepoint = names(threePrimeMMAnchoredCisplatinSeqFreq[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering
    ))
  }
}

fivePrimeMMAnchoredCisplatinSeqFreq = list(rep1 = CisplatinTimepoints,
                                           rep2 = CisplatinTimepoints)
for (i in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq)) {
  for (j in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq[[i]])) {
    fivePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMMAnchoredCisplatinSeqFreq)[i],
      timepoint = names(fivePrimeMMAnchoredCisplatinSeqFreq[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering
    ))
  }
}
```

```{r cisplatin_sequence_frequencies, fig.width = 11, fig.height = 9}
plotSequenceFrequencies(threePrimeMMAnchoredCisplatinSeqFreq$rep1,
                        title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored YR Freq Rep1"), collapse = ' '),
                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
plotSequenceFrequencies(threePrimeMMAnchoredCisplatinSeqFreq$rep2,
                        title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored YR Freq Rep2"), collapse = ' '),
                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))

plotSequenceFrequencies(fivePrimeMMAnchoredCisplatinSeqFreq$rep1,
                        title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored TGG Freq Rep1"), collapse = ' '),
                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
plotSequenceFrequencies(fivePrimeMMAnchoredCisplatinSeqFreq$rep2,
                        title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored TGG Freq Rep2"), collapse = ' '),
                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
```

### 2022-05-31 R/GM12878DeaminationSequenceAndPositionDataGeneration.rmd
Added GM12878 cisplatin notebooks

---
title: "GM12878 Deamination Sequence and Position Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

```{r setup_chunk}
library(knitr)

expansionOffset = 0
cellType = "GM12878"
CisplatinTimepoints = list(`90min` = NULL)
minReadLength = 22; maxReadLength = 30

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
  filtering = readline("Filtering identifier (Input nothing for no filtering):")
  if (filtering == '') filtering = character()
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
  filtering = params$filtering
  if (filtering == "NONE") filtering = character()
}
if (is.na(bioinformaticsDirectory)) stop("No bioinformatics directory given.")

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
mismatchesByReadDirectory = file.path(deaminationDataDirectory, "mismatches_by_read")
deaminationSequenceAndPositionDataDirectory = file.path(deaminationDataDirectory,"sequence_and_position_analysis")
dir.create(deaminationSequenceAndPositionDataDirectory, recursive = TRUE, showWarnings = FALSE)
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationParseAndFilter.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationSequenceAndPositionAnalysis.R"))
```

```{r read_mismatch_data}
# Get file paths for the mismatch by read data
CisplatinMismatchData = list(rep1 = CisplatinTimepoints,
                             rep2 = CisplatinTimepoints)
for (i in 1:length(CisplatinMismatchData)) {
  for (j in 1:length(CisplatinMismatchData[[i]])) {
    CisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "cisplatin", timepoint = names(CisplatinMismatchData[[i]])[j],
      repitition = names(CisplatinMismatchData)[i], filtering = filtering
      ))
  }
}
```

```{r generate_and_write_simplified_and_filtered_mismatch_data}
# Perform general filtering on the data
CisplatinMismatchData = lapply(CisplatinMismatchData, function(x) lapply(
  x, function(y) filterResults(y, TRUE, 3, minReadLength, maxReadLength)
))

# Simplify the data
CisplatinMismatchData = lapply(CisplatinMismatchData, function(x) lapply(
  x, function(y) simplifyTable(y, includeTrinucleotideContext = TRUE)
))

# Write the simplified mismatch data
for (i in 1:length(CisplatinMismatchData)) {
  for (j in 1:length(CisplatinMismatchData[[i]])) {
    fwrite(CisplatinMismatchData[[i]][[j]], sep = '\t', na = "NA",
           file = generateFilePath(
             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
             cellType = cellType, lesion = "cisplatin", timepoint = names(CisplatinMismatchData[[i]])[j],
             repitition = names(CisplatinMismatchData)[i], filtering = filtering
           ))
  }
}
```

```{r generate_and_write_mismatch_frequency_z-scores}
# Don't forget to subset by C>T mismatches!
CisplatinMMFreqZScores = lapply(CisplatinMismatchData, function(x) lapply(
  x, function(y) {
    getMismatchFrequencyZScoreByPosAndReadLength(y[Mismatch == "C>T"], expansionOffset)
  }
))

for (i in seq_along(CisplatinMMFreqZScores)) {
  for (j in seq_along(CisplatinMMFreqZScores[[i]])) {
    fwrite(CisplatinMMFreqZScores[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(CisplatinMMFreqZScores)[i],
      timepoint = names(CisplatinMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
    ))
  }
}
```

```{r generate_and_write_mismatch_position_statistics_by_read_length_and_timepoint}
CisplatinGroupedStats = list(rep1 = list(), rep2 = list())
CisplatinGroupedStats$rep1$three_prime = getGroupedPositionStats(CisplatinMismatchData$rep1, includedTypes = c("C>T"))
CisplatinGroupedStats$rep2$three_prime = getGroupedPositionStats(CisplatinMismatchData$rep2, includedTypes = c("C>T"))
CisplatinGroupedStats$rep1$five_prime =
  getGroupedPositionStats(CisplatinMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME)
CisplatinGroupedStats$rep2$five_prime =
  getGroupedPositionStats(CisplatinMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME)

for (i in seq_along(CisplatinGroupedStats)) {
  for (j in seq_along(CisplatinGroupedStats[[i]])) {
    fwrite(CisplatinGroupedStats[[i]][[j]], sep = '\t',
           file = generateFilePath(
             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
             cellType = cellType, lesion = "cisplatin", repitition = names(CisplatinGroupedStats)[i],
             strandPolarity = names(CisplatinGroupedStats[[i]])[j], filtering = filtering
           ))
  }
}
```

### 2022-05-31 R/GM12878DeaminationSequenceAndPositionFigureGeneration.rmd
Added GM12878 cisplatin notebooks

---
title: "GM12878 Deamination Sequence and Position Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

```{r setup_chunk}
library(knitr)

cellType = "GM12878"
CisplatinTimepoints = list(`90min` = NULL)
minReadLength = 22; maxReadLength = 30

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
  filtering = readline("Filtering identifier (Input nothing for no filtering):")
  if (filtering == '') filtering = character()
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
  filtering = params$filtering
  if (filtering == "NONE") filtering = character()
}
if (length(filtering) > 0) {
  titleCaseFiltering = tools::toTitleCase(gsub('_', ' ', filtering))
} else titleCaseFiltering = character()

opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
               fig.path = paste0(file.path("deamination_analysis_output",cellType,
                                           paste(c(filtering,"deamination_sequence_and_position_figures"), collapse = '_')),
                                 .Platform$file.sep))

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
deaminationSequenceAndPositionDataDirectory = file.path(deaminationDataDirectory,"sequence_and_position_analysis")
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationSequenceAndPositionAnalysis.R"))
```

```{r read_simplified_mismatch_data}
# Get file paths for the mismatch by read data
CisplatinMismatchData = list(rep1 = CisplatinTimepoints,
                             rep2 = CisplatinTimepoints)
for (i in seq_along(CisplatinMismatchData)) {
  for (j in seq_along(CisplatinMismatchData[[i]])) {
    CisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
      cellType = cellType, lesion = "cisplatin", timepoint = names(CisplatinMismatchData[[i]])[j],
      repitition = names(CisplatinMismatchData)[i], filtering = filtering
    ))
  }
}
```

```{r cisplatin_mismatch_type_frequency}
for (i in 1:length(CisplatinMismatchData)) {
  for (j in 1:length(CisplatinMismatchData[[i]])) {
    plotMismatchTypeFrequencies(CisplatinMismatchData[[i]][[j]],
                                title = paste(c("cisplatin", titleCaseFiltering, names(CisplatinMismatchData)[i], 
                                                names(CisplatinMismatchData[[i]])[j], "Mismatch Type Frequency"),
                                              collapse = ' '))
  }
}
```

```{r cisplatin_mismatch_pos_frequency}
for (i in 1:length(CisplatinMismatchData)) {
  for (j in 1:length(CisplatinMismatchData[[i]])) {
    plotMismatchPositionFrequencies(CisplatinMismatchData[[i]][[j]], includedTypes = c("C>T"),
                                    title = paste(c("cisplatin", titleCaseFiltering, names(CisplatinMismatchData)[i], 
                                                    names(CisplatinMismatchData[[i]])[j], "C>T Mismatch Positions"),
                                                  collapse = ' '))
    plotMismatchPositionFrequencies(CisplatinMismatchData[[i]][[j]], omittedTypes = c("C>T"),
                                    title = paste(c("cisplatin", titleCaseFiltering, names(CisplatinMismatchData)[i], 
                                                    names(CisplatinMismatchData[[i]])[j], "!C>T Mismatch Positions"),
                                                  collapse = ' '))
  }
}
```

```{r cisplatin_trinucleotide_context_analysis}
for (i in 1:length(CisplatinMismatchData)) {
  for (j in 1:length(CisplatinMismatchData[[i]])) {
    plotTrinucleotideContext(CisplatinMismatchData[[i]][[j]], includedTypes = c("C>T"),
                             title = paste(c("cisplatin", titleCaseFiltering, names(CisplatinMismatchData)[i],
                                             names(CisplatinMismatchData[[i]])[j], "C>T Mismatch Trinuc Context"),
                                           collapse = ' '))
  }
}
```

```{r read_mismatch_frequency_z-score_tables}
CisplatinMMFreqZScores = list(rep1 = CisplatinTimepoints, rep2 = CisplatinTimepoints)
for (i in seq_along(CisplatinMMFreqZScores)) {
  for (j in seq_along(CisplatinMMFreqZScores[[i]])) {
    CisplatinMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(CisplatinMMFreqZScores)[i],
      timepoint = names(CisplatinMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
    ))
  }
}
```

```{r cisplatin_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
plotPositionAcrossTimepointAndReadLength(CisplatinMismatchData$rep1, includedTypes = c("C>T"),
                                         title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
                                                       collapse = ' '),
                                         zScoreTables = CisplatinMMFreqZScores$rep1)
plotPositionAcrossTimepointAndReadLength(CisplatinMismatchData$rep2, includedTypes = c("C>T"),
                                         title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
                                                       collapse = ' '),
                                         zScoreTables = CisplatinMMFreqZScores$rep2)
plotPositionAcrossTimepointAndReadLength(CisplatinMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME,
                                         title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
                                                       collapse = ' '),
                                         zScoreTables = CisplatinMMFreqZScores$rep1)
plotPositionAcrossTimepointAndReadLength(CisplatinMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME,
                                         title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
                                                       collapse = ' '),
                                         zScoreTables = CisplatinMMFreqZScores$rep2)
```

```{r cisplatin_read_length_distributions}
plotReadLengthFrequencies(CisplatinMismatchData$rep1,
                          title = paste(c("cisplatin", titleCaseFiltering, "Read Length Freq Rep 1"), collapse = ' '))
plotReadLengthFrequencies(CisplatinMismatchData$rep2,
                          title = paste(c("cisplatin", titleCaseFiltering, "Read Length Freq Rep 2"), collapse = ' '))
```

```{r read_mismatch_position_statistics}
CisplatinGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
                             rep2 = list(three_prime = NULL, five_prime = NULL))
for (i in seq_along(CisplatinGroupedStats)) {
  for (j in seq_along(CisplatinGroupedStats[[i]])) {
    CisplatinGroupedStats[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(CisplatinGroupedStats)[i],
      strandPolarity = names(CisplatinGroupedStats[[i]])[j], filtering = filtering
    ))
  }
}
```

```{r cisplatin_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
plotGroupedPositionStats(CisplatinGroupedStats$rep1$three_prime, CisplatinGroupedStats$rep1$five_prime, POS_DIFF,
                         title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Diff Rep1"), collapse = ' '),
                         xAxisBreaks = c(minReadLength:maxReadLength))
plotGroupedPositionStats(CisplatinGroupedStats$rep2$three_prime, CisplatinGroupedStats$rep2$five_prime, POS_DIFF,
                         title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Diff Rep2"), collapse = ' '),
                         xAxisBreaks = c(minReadLength:maxReadLength))
```

### 2022-05-31 R/GM12878GeneralReadSequenceDataGeneration.rmd
Added GM12878 cisplatin notebooks

--- 2022-05-31 R/EcoliWTGeneralReadSequenceDataGeneration.rmd
@@
 ---
-title: "E coli WT General Read Sequence Data Generation"
+title: "GM12878 General Read Sequence Data Generation"
 author: "Ben Morledge-Hampton"
@@
 expansionOffset = 10
-cellType = "E_coli_WT"
-CPDTimepoints = list(`5min` = NULL)
-minReadLength = 11; maxReadLength = 13
+cellType = "GM12878"
+CisplatinTimepoints = list(`90min` = NULL)
+minReadLength = 22; maxReadLength = 30
 
@@
 
-```{r compute_and_write_CPD_sequence_frequency}
+```{r compute_and_write_cisplatin_sequence_frequency}
 for (repitition in c("rep1", "rep2")) {
-  for (timepoint in names(CPDTimepoints)) {
-    singleFileFullAnalysis("CPD", repitition, timepoint)
+  for (timepoint in names(CisplatinTimepoints)) {
+    singleFileFullAnalysis("cisplatin", repitition, timepoint)
   }

### 2022-05-31 R/GM12878GeneralReadSequenceFigureGeneration.rmd
Added GM12878 cisplatin notebooks

--- 2022-05-31 R/EcoliWTGeneralReadSequenceFigureGeneration.rmd
@@
 ---
-title: "E coli WT General Read Sequence Figure Generation"
+title: "GM12878 General Read Sequence Figure Generation"
 author: "Ben Morledge-Hampton"
@@
 ```{r read_sequence_frequencies}
-CPDTGGSeqFreq = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
-for (i in seq_along(CPDTGGSeqFreq)) {
-  for (j in seq_along(CPDTGGSeqFreq[[i]])) {
-    CPDTGGSeqFreq[[i]][[j]] = fread(generateFilePath(
+CisplatinTGGSeqFreq = list(rep1 = CisplatinTimepoints, rep2 = CisplatinTimepoints)
+for (i in seq_along(CisplatinTGGSeqFreq)) {
+  for (j in seq_along(CisplatinTGGSeqFreq[[i]])) {
+    CisplatinTGGSeqFreq[[i]][[j]] = fread(generateFilePath(
       directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
-      cellType = cellType, lesion = "CPD", repitition = names(CPDTGGSeqFreq)[i],
-      timepoint = names(CPDTGGSeqFreq[[i]])[j], sequence = "TGG"
+      cellType = cellType, lesion = "cisplatin", repitition = names(CisplatinTGGSeqFreq)[i],
+      timepoint = names(CisplatinTGGSeqFreq[[i]])[j], sequence = "TGG"
     ))
@@
 
-CPDCGASeqFreq = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
-for (i in seq_along(CPDCGASeqFreq)) {
-  for (j in seq_along(CPDCGASeqFreq[[i]])) {
-    CPDCGASeqFreq[[i]][[j]] = fread(generateFilePath(
+CisplatinCGASeqFreq = list(rep1 = CisplatinTimepoints, rep2 = CisplatinTimepoints)
+for (i in seq_along(CisplatinCGASeqFreq)) {
+  for (j in seq_along(CisplatinCGASeqFreq[[i]])) {
+    CisplatinCGASeqFreq[[i]][[j]] = fread(generateFilePath(
       directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
-      cellType = cellType, lesion = "CPD", repitition = names(CPDCGASeqFreq)[i],
-      timepoint = names(CPDCGASeqFreq[[i]])[j], sequence = "CGA"
+      cellType = cellType, lesion = "cisplatin", repitition = names(CisplatinCGASeqFreq)[i],
+      timepoint = names(CisplatinCGASeqFreq[[i]])[j], sequence = "CGA"
     ))
@@
 
-```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 10}
-plotSequenceFrequencies(CPDTGGSeqFreq$rep1,
-                        title = "CPD TGG Frequencies Rep1", expansionOffset = expansionOffset,
+```{r cisplatin_sequence_frequencies, fig.width = 11, fig.height = 10}
+plotSequenceFrequencies(CisplatinTGGSeqFreq$rep1,
+                        title = "cisplatin TGG Frequencies Rep1", expansionOffset = expansionOffset,
                         showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                         querySequences = c("TGG"))
-plotSequenceFrequencies(CPDTGGSeqFreq$rep2,
-                        title = "CPD TGG Frequencies Rep2", expansionOffset = expansionOffset,
+plotSequenceFrequencies(CisplatinTGGSeqFreq$rep2,
+                        title = "cisplatin TGG Frequencies Rep2", expansionOffset = expansionOffset,
                         showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
@@
 
-plotSequenceFrequencies(CPDCGASeqFreq$rep1,
-                        title = "CPD CGA Frequencies Rep1", expansionOffset = expansionOffset,
+plotSequenceFrequencies(CisplatinCGASeqFreq$rep1,
+                        title = "cisplatin CGA Frequencies Rep1", expansionOffset = expansionOffset,
                         showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                         querySequences = c("CGA"))
-plotSequenceFrequencies(CPDCGASeqFreq$rep2,
-                        title = "CPD CGA Frequencies Rep2", expansionOffset = expansionOffset,
+plotSequenceFrequencies(CisplatinCGASeqFreq$rep2,
+                        title = "cisplatin CGA Frequencies Rep2", expansionOffset = expansionOffset,
                         showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
@@
 
-```{r CPD_read_length_frequencies}
-readAndPlotReadLengthFrequencies("CPD", "rep1", CPDTimepoints)
-readAndPlotReadLengthFrequencies("CPD", "rep2", CPDTimepoints)
+```{r cisplatin_read_length_frequencies}
+readAndPlotReadLengthFrequencies("cisplatin", "rep1", CisplatinTimepoints)
+readAndPlotReadLengthFrequencies("cisplatin", "rep2", CisplatinTimepoints)
 ```

### 2022-06-01 R/XP-CDeaminationAnchoredExcisionSiteDataGeneration.rmd
Added XP-C notebooks

--- 2022-05-31 R/CS-BDeaminationAnchoredExcisionSiteDataGeneration.rmd
@@
 ---
-title: "CS-B Deamination Anchored Excision Site Data Generation"
+title: "XP-C Deamination Anchored Excision Site Data Generation"
 author: "Ben Morledge-Hampton"
@@
 expansionOffset = 10
-cellType = "CS-B"
+cellType = "XP-C"
 CPDTimepoints = list(`1h` = NULL)

### 2022-06-01 R/XP-CDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Added XP-C notebooks

--- 2022-05-31 R/CS-BDeaminationAnchoredExcisionSiteFigureGeneration.rmd
@@
 ---
-title: "CS-B Deamination Anchored Excision Site Figure Generation"
+title: "XP-C Deamination Anchored Excision Site Figure Generation"
 author: "Ben Morledge-Hampton"
@@
 expansionOffset = 10
-cellType = "CS-B"
+cellType = "XP-C"
 CPDTimepoints = list(`1h` = NULL)
 sixFourTimepoints = list(`1h` = NULL)
+minReadLength = 22; maxReadLength = 30
 

### 2022-06-01 R/XP-CDeaminationSequenceAndPositionDataGeneration.rmd
Added XP-C notebooks

--- 2022-05-31 R/CS-BDeaminationSequenceAndPositionDataGeneration.rmd
@@
 ---
-title: "CS-B Deamination Sequence and Position Data Generation"
+title: "XP-C Deamination Sequence and Position Data Generation"
 author: "Ben Morledge-Hampton"
@@
 
-cellType = "CS-B"
+expansionOffset = 0
+cellType = "XP-C"
 CPDTimepoints = list(`1h` = NULL)
 sixFourTimepoints = list(`1h` = NULL)
-expansionOffset = 0
 minReadLength = 22; maxReadLength = 30

### 2022-06-01 R/XP-CDeaminationSequenceAndPositionFigureGeneration.rmd
Added XP-C notebooks

--- 2022-05-31 R/CS-BDeaminationSequenceAndPositionFigureGeneration.rmd
@@
 ---
-title: "CS-B Deamination Sequence and Position Figure Generation"
+title: "XP-C Deamination Sequence and Position Figure Generation"
 author: "Ben Morledge-Hampton"
@@
 
-cellType = "CS-B"
+cellType = "XP-C"
 CPDTimepoints = list(`1h` = NULL)

### 2022-06-01 R/XP-CGeneralReadSequenceDataGeneration.rmd
Added XP-C notebooks

--- 2022-05-31 R/CS-BGeneralReadSequenceDataGeneration.rmd
@@
 ---
-title: "CS-B General Read Sequence Data Generation"
+title: "XP-C General Read Sequence Data Generation"
 author: "Ben Morledge-Hampton"

### 2022-06-01 R/XP-CGeneralReadSequenceFigureGeneration.rmd
Added XP-C notebooks

--- 2022-05-31 R/CS-BGeneralReadSequenceFigureGeneration.rmd
@@
 ---
-title: "CS-B General Read Sequence Figure Generation"
+title: "XP-C General Read Sequence Figure Generation"
 author: "Ben Morledge-Hampton"

### 2022-06-01 R/GM12878DeaminationAnchoredExcisionSiteDataGeneration.rmd
Forgot this GM12878 notebook

---
title: "GM12878 Deamination Anchored Excision Site Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

```{r setup_chunk}
library(knitr)

expansionOffset = 10
cellType = "GM12878"
CisplatinTimepoints = list(`90min` = NULL)
minReadLength = 22; maxReadLength = 30

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
  filtering = readline("Filtering identifier (Input nothing for no filtering):")
  if (filtering == '') filtering = character()
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
  filtering = params$filtering
  if (filtering == "NONE") filtering = character()
}
if (is.na(bioinformaticsDirectory)) stop("No bioinformatics directory given.")

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
NHF1DeaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", "NHF1")
mismatchesByReadDirectory = file.path(deaminationDataDirectory, "mismatches_by_read")
deaminationSequenceAndPositionDataDirectory = file.path(deaminationDataDirectory,"sequence_and_position_analysis")
NHF1DeaminationSequenceAndPositionDataDirectory = file.path(NHF1DeaminationDataDirectory,"sequence_and_position_analysis")
deaminationExcisionSiteDataDirectory = file.path(deaminationDataDirectory, "excision_site_analysis")
dir.create(deaminationExcisionSiteDataDirectory, showWarnings = FALSE, recursive = TRUE)
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationParseAndFilter.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationAnchoredExcisionSiteAnalysis.R"))
```

```{r read_expanded_mismatch_data}
# Get file paths for the expanded mismatch by read data
CisplatinMismatchData = list(rep1 = CisplatinTimepoints,
                             rep2 = CisplatinTimepoints)
for (i in 1:length(CisplatinMismatchData)) {
  for (j in 1:length(CisplatinMismatchData[[i]])) {
    CisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "cisplatin", timepoint = names(CisplatinMismatchData[[i]])[j],
      repitition = names(CisplatinMismatchData)[i], expansionNum = expansionOffset, filtering = filtering
      ))
  }
}
```

```{r generate_simplified_and_filtered_mismatch_data}
# Filter the reads by length and mismatch type (single C>T).
CisplatinMismatchData = lapply(CisplatinMismatchData, function(x) lapply(
  x, function(y) filterResults(y[V5 == "C>T"], minReadLength = minReadLength, maxReadLength = maxReadLength)
))

# Simplify the data
CisplatinMismatchData = lapply(CisplatinMismatchData, function(x) lapply(
  x, function(y) simplifyTable(y, TRUE, expansionOffset = expansionOffset)
))

# Read mismatch frequency z-scores.
# NOTE: Using NHF1 CPD scores. Otherwise, data will be too tightly constrained.
NHF1CPDMMFreqZScores = fread(generateFilePath(
      directory = NHF1DeaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = "NHF1", lesion = "CPD", repitition = "rep1",
      timepoint = "1h", filtering = filtering, includedMismatches = c("C>T")
))

# Further filter data by read position based on length
CisplatinMismatchData = lapply(CisplatinMismatchData, function(CisplatinMismatchDataRep) {
  lapply(CisplatinMismatchDataRep, filterMismatchesByPositionAndReadLength,
         NHF1CPDMMFreqZScores, expansionOffset = expansionOffset)
})
```

```{r orient_data_to_mismatch_positions}
# NOTE: The assignment to null is there so that the garbage collector can free up memory, and
#       I can still switch to new variable names for organizational purposes.
threePrimeMismatchAnchoredCisplatinData = lapply(CisplatinMismatchData, function(x) {
  lapply(x, orientDataToMismatch, THREE_PRIME, expansionOffset)
})
fivePrimeMismatchAnchoredCisplatinData = lapply(CisplatinMismatchData, function(x) {
  lapply(x, orientDataToMismatch, FIVE_PRIME, expansionOffset)
})
CisplatinMismatchData = NULL
```

```{r generate_and_write_nucleotide_frequency_data}
threePrimeMismatchCisplatinNucFreq = lapply(threePrimeMismatchAnchoredCisplatinData, tabulateNucFreqByPosTimepointAndLength)
for (i in seq_along(threePrimeMismatchCisplatinNucFreq)) {
  fwrite(threePrimeMismatchCisplatinNucFreq[[i]], sep = '\t', file = generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMismatchCisplatinNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering
  ))
}

fivePrimeMismatchCisplatinNucFreq = lapply(fivePrimeMismatchAnchoredCisplatinData,
                                           tabulateNucFreqByPosTimepointAndLength, posType = FIVE_PRIME)
for (i in seq_along(fivePrimeMismatchCisplatinNucFreq)) {
  fwrite(fivePrimeMismatchCisplatinNucFreq[[i]], sep = '\t', file = generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMismatchCisplatinNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering
  ))
}
```

```{r generate_and_write_sequence_enrichment}
threePrimeMMAnchoredCisplatinEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
  setNames(lapply(seq_along(mismatchDataRep), function(i) {
    getSequenceFreqByReadLengthAndPos(mismatchDataRep[[i]],
                                      nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
                                      c("CG","CA","TG","TA"))
  }), names(mismatchDataRep))
}, threePrimeMismatchAnchoredCisplatinData, threePrimeMismatchCisplatinNucFreq, SIMPLIFY = FALSE)
for (i in seq_along(threePrimeMMAnchoredCisplatinEnrichment)) {
  for (j in seq_along(threePrimeMMAnchoredCisplatinEnrichment[[i]])) {
    fwrite(threePrimeMMAnchoredCisplatinEnrichment[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMMAnchoredCisplatinEnrichment)[i],
      timepoint = names(threePrimeMMAnchoredCisplatinEnrichment[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering
    ))
  }
}

fivePrimeMMAnchoredCisplatinEnrichment = mapply(function(mismatchDataRep, nucFreqRep) {
  setNames(lapply(seq_along(mismatchDataRep), function(i) {
    getSequenceFreqByReadLengthAndPos(mismatchDataRep[[i]],
                                      nucFreqRep[Timepoint == names(mismatchDataRep)[i]],
                                      c("TGG"), posType = FIVE_PRIME)
  }), names(mismatchDataRep))
}, fivePrimeMismatchAnchoredCisplatinData, fivePrimeMismatchCisplatinNucFreq, SIMPLIFY = FALSE)
for (i in seq_along(fivePrimeMMAnchoredCisplatinEnrichment)) {
  for (j in seq_along(fivePrimeMMAnchoredCisplatinEnrichment[[i]])) {
    fwrite(fivePrimeMMAnchoredCisplatinEnrichment[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMMAnchoredCisplatinEnrichment)[i],
      timepoint = names(fivePrimeMMAnchoredCisplatinEnrichment[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering
    ))
  }
}
```

```{r generate_and_write_sequence_frequencies}
threePrimeMMAnchoredCisplatinSeqFreq = lapply(threePrimeMismatchAnchoredCisplatinData, function(mismatchDataRep) {
  lapply(mismatchDataRep, function(mismatchData) {
    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("CG","CA","TG","TA"))
  })
})
for (i in seq_along(threePrimeMMAnchoredCisplatinSeqFreq)) {
  for (j in seq_along(threePrimeMMAnchoredCisplatinSeqFreq[[i]])) {
    fwrite(threePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMMAnchoredCisplatinSeqFreq)[i],
      timepoint = names(threePrimeMMAnchoredCisplatinSeqFreq[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering
    ))
  }
}

fivePrimeMMAnchoredCisplatinSeqFreq = lapply(fivePrimeMismatchAnchoredCisplatinData, function(mismatchDataRep) {
  lapply(mismatchDataRep, function(mismatchData) {
    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("TGG"), posType = FIVE_PRIME)
  })
})
for (i in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq)) {
  for (j in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq[[i]])) {
    fwrite(fivePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMMAnchoredCisplatinSeqFreq)[i],
      timepoint = names(fivePrimeMMAnchoredCisplatinSeqFreq[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering
    ))
  }
}
```

### 2022-06-01 R/YeastDeaminationAnchoredExcisionSiteDataGeneration.rmd
Added yeast notebooks

--- 2022-06-01 R/XP-CDeaminationAnchoredExcisionSiteDataGeneration.rmd
@@
 ---
-title: "XP-C Deamination Anchored Excision Site Data Generation"
+title: "Yeast Deamination Anchored Excision Site Data Generation"
 author: "Ben Morledge-Hampton"
@@
 expansionOffset = 10
-cellType = "XP-C"
-CPDTimepoints = list(`1h` = NULL)
-sixFourTimepoints = list(`1h` = NULL)
-minReadLength = 22; maxReadLength = 30
+cellType = "yeast"
+CPDTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
+sixFourTimepoints = list(`5min` = NULL, `20min` = NULL)
+minReadLength = 22; maxReadLength = 25
 

### 2022-06-01 R/YeastDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Added yeast notebooks

--- 2022-05-31 R/CS-BDeaminationAnchoredExcisionSiteFigureGeneration.rmd
@@
 ---
-title: "CS-B Deamination Anchored Excision Site Figure Generation"
+title: "Yeast Deamination Anchored Excision Site Figure Generation"
 author: "Ben Morledge-Hampton"
@@
 expansionOffset = 10
-cellType = "CS-B"
-CPDTimepoints = list(`1h` = NULL)
-sixFourTimepoints = list(`1h` = NULL)
+cellType = "yeast"
+CPDTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
+sixFourTimepoints = list(`5min` = NULL, `20min` = NULL)
+minReadLength = 22; maxReadLength = 25
 

### 2022-06-01 R/YeastDeaminationSequenceAndPositionDataGeneration.rmd
Added yeast notebooks

--- 2022-06-01 R/XP-CDeaminationSequenceAndPositionDataGeneration.rmd
@@
 ---
-title: "XP-C Deamination Sequence and Position Data Generation"
+title: "Yeast Deamination Sequence and Position Data Generation"
 author: "Ben Morledge-Hampton"
@@
 expansionOffset = 0
-cellType = "XP-C"
-CPDTimepoints = list(`1h` = NULL)
-sixFourTimepoints = list(`1h` = NULL)
-minReadLength = 22; maxReadLength = 30
+cellType = "yeast"
+CPDTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
+sixFourTimepoints = list(`5min` = NULL, `20min` = NULL)
+minReadLength = 22; maxReadLength = 25
 

### 2022-06-01 R/YeastDeaminationSequenceAndPositionFigureGeneration.rmd
Added yeast notebooks

--- 2022-06-01 R/XP-CDeaminationSequenceAndPositionFigureGeneration.rmd
@@
 ---
-title: "XP-C Deamination Sequence and Position Figure Generation"
+title: "Yeast Deamination Sequence and Position Figure Generation"
 author: "Ben Morledge-Hampton"
@@
 
-cellType = "XP-C"
-CPDTimepoints = list(`1h` = NULL)
-sixFourTimepoints = list(`1h` = NULL)
-minReadLength = 22; maxReadLength = 30
+cellType = "yeast"
+CPDTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
+sixFourTimepoints = list(`5min` = NULL, `20min` = NULL)
+minReadLength = 22; maxReadLength = 25
 

### 2022-06-01 R/YeastGeneralReadSequenceDataGeneration.rmd
Added yeast notebooks

--- 2022-06-01 R/XP-CGeneralReadSequenceDataGeneration.rmd
@@
 ---
-title: "XP-C General Read Sequence Data Generation"
+title: "Yeast General Read Sequence Data Generation"
 author: "Ben Morledge-Hampton"

### 2022-06-01 R/YeastGeneralReadSequenceFigureGeneration.rmd
Added yeast notebooks

--- 2022-06-01 R/XP-CGeneralReadSequenceFigureGeneration.rmd
@@
 ---
-title: "XP-C General Read Sequence Figure Generation"
+title: "Yeast General Read Sequence Figure Generation"
 author: "Ben Morledge-Hampton"

### 2022-06-03 R/CS-BDeaminationSequenceAndPositionFigureGeneration.rmd
Added options for y-axis breaks to pos freq facet plots

@@
                                                        collapse = ' '),
-                                         zScoreTables = CPDMMFreqZScores$rep1)
+                                         zScoreTables = CPDMMFreqZScores$rep1, yAxisBreaks = c(0, 0.16, 0.32))
 plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, includedTypes = c("C>T"),
@@
                                                        collapse = ' '),
-                                         zScoreTables = CPDMMFreqZScores$rep2)
+                                         zScoreTables = CPDMMFreqZScores$rep2, yAxisBreaks = c(0, 0.16, 0.32))
 plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME,
@@
                                                        collapse = ' '),
-                                         zScoreTables = CPDMMFreqZScores$rep1)
+                                         zScoreTables = CPDMMFreqZScores$rep1, yAxisBreaks = c(0, 0.16, 0.32))
 plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME,
@@
                                                        collapse = ' '),
-                                         zScoreTables = CPDMMFreqZScores$rep2)
+                                         zScoreTables = CPDMMFreqZScores$rep2, yAxisBreaks = c(0, 0.16, 0.32))
 ```

### 2022-06-03 R/DeaminationSequenceAndPositionAnalysis.R

@@ -4,6 +4,7 @@ library(ggplot2)
 
 THREE_PRIME = "three_prime"
 FIVE_PRIME = "five_prime"
+HALF_MAX = "half_max"
 
 # Default text scaling
 defaultTextScaling = theme(plot.title = element_text(size = 22, hjust = 0.5),
@@ -72,7 +73,8 @@ plotMismatchPositionFrequencies = function(mismatchTable, includedTypes = list()
 # to construct a plot without timepoint information.
 plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTypes = list(), omittedTypes = list(),
                                                     title = "Mismatch Position Frequencies", posType = THREE_PRIME,
-                                                    zScoreTables = NULL, zScoreCutoff = 4, xAxisBreaks = -3:3*10) {
+                                                    zScoreTables = NULL, zScoreCutoff = 4, xAxisBreaks = -3:3*10,
+                                                    yAxisBreaks = NULL) {
 
   #If passed a single data.table, wrap it in a list.
   if (is.data.table(simplifiedTables)) {
@@ -141,14 +143,27 @@ plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTy
     plot = plot + facet_grid(Read_Length~factor(Timepoint, levels = names(simplifiedTables)))
   }
 
+  if (is.null(yAxisBreaks)) {
+    plot = plot + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank()) +
+      scale_y_continuous(sec.axis = dup_axis(~., name = "Read Length"))
+  } else if (length(yAxisBreaks) == 1 && yAxisBreaks == HALF_MAX) {
+    maxFrequency = round(max(groupedPositionFrequencies$Frequency), digits = 2)
+    yAxisBreaks = c(0, maxFrequency/2, maxFrequency)
+    plot = plot + theme(axis.text.y = element_text(size = 10)) +
+      scale_y_continuous(breaks = yAxisBreaks, sec.axis = dup_axis(~., name = "Read Length"),) +
+      coord_cartesian(ylim = (c(0, maxFrequency*1.2)))
+  } else {
+    plot = plot + theme(axis.text.y = element_text(size = 10)) +
+      scale_y_continuous(breaks = yAxisBreaks, sec.axis = dup_axis(~., name = "Read Length"),) +
+      coord_cartesian(ylim = c(min(yAxisBreaks), max(yAxisBreaks) * 1.2))
+  }
 
   plot = plot +
[…]

### 2022-06-06 R/DeaminationAnchoredExcisionSiteAnalysis.R
Patches to allow for half-base positions

@@ -168,14 +168,23 @@ plotNucFreqVsReadLengthBarPlot = function(nucFreqTable, posType = THREE_PRIME,
 
 # This function takes a table of mismatch data for whole reads and returns a table of
 # that same data for one side of that data, anchored on the mismatch
-orientDataToMismatch = function(simplifiedTable, posType, expansionOffset = 0) {
+orientDataToMismatch = function(simplifiedTable, posType, expansionOffset = 0, halfPositions = FALSE) {
 
   if (posType == THREE_PRIME) {
-    sequences = str_sub(simplifiedTable$Read_Sequence,
-                        -nchar(simplifiedTable$Read_Sequence), simplifiedTable$Position)
+    if (halfPositions) {
+      sequences = str_sub(simplifiedTable$Read_Sequence,
+                          -nchar(simplifiedTable$Read_Sequence), simplifiedTable$Position - 0.5)
+    } else {
+      sequences = str_sub(simplifiedTable$Read_Sequence,
+                          -nchar(simplifiedTable$Read_Sequence), simplifiedTable$Position)
+    }
     position = -1
   } else if (posType == FIVE_PRIME) {
-    sequences = str_sub(simplifiedTable$Read_Sequence, simplifiedTable$Position, -1)
+    if (halfPositions) {
+      sequences = str_sub(simplifiedTable$Read_Sequence, simplifiedTable$Position + 0.5, -1)
+    } else {
+      sequences = str_sub(simplifiedTable$Read_Sequence, simplifiedTable$Position, -1)
+    }
     position = 1
   } else stop("Unrecognized value for posType parameter.")
 

### 2022-06-06 R/DeaminationParseAndFilter.R

@@ -52,7 +52,7 @@ filterResults = function(mismatchData, removeRowsWithN = TRUE, maxMismatchesAllo
 simplifyTable = function(table, includeReadSequence = FALSE, includeTrinucleotideContext = FALSE,
                          expansionOffset = 0) {
 
-  returnTable = table[,list(Position = as.numeric(unlist(strsplit(V4, ':'))) - expansionOffset,
+  returnTable = table[,list(Position = as.numeric(unlist(strsplit(as.character(V4), ':'))) - expansionOffset,
                             Mismatch = unlist(strsplit(V5, ':')),
                             Read_Length = unlist(mapply(rep, nchar(V7)-2*expansionOffset,
                                                         lapply(strsplit(V5,':'), length))))]

### 2022-06-06 R/NHF1TandemDeaminationDataGeneration.rmd
Created NHF1 tandem deamination notebooks

---
title: "NHF1 Tandem Deamination Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
  mismatchType:
    label: "Mismatch Type"
    value: CC>TT
    input: select
    choices: [CC>TT, GG>AA]
---

```{r setup_chunk}
library(knitr)
library(stringr)

cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL)
sixFourTimepoints = list(`1h` = NULL)
expansionOffset = 10
minReadLength = 22; maxReadLength = 30

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
  filtering = readline("Filtering identifier (Input nothing for no filtering):")
  if (filtering == '') filtering = character()
  mismatchType = readline("Tandem mismatch type:")
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
  filtering = params$filtering
  if (filtering == "NONE") filtering = character()
  mismatchType = params$mismatchType
}
if (is.na(bioinformaticsDirectory)) stop("No bioinformatics directory given.")

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
tandemDeaminationDataDirectory = file.path(deaminationDataDirectory,
                                           paste(str_replace(mismatchType, '>', "_to_"),
                                                 "tandem_deaminations", sep = '_'))
dir.create(tandemDeaminationDataDirectory, recursive = TRUE, showWarnings = FALSE)
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationParseAndFilter.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationSequenceAndPositionAnalysis.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationAnchoredExcisionSiteAnalysis.R"))
```

```{r read_mismatch_data}
# Get file paths for the mismatch by read data
CPDMismatchData = list(rep1 = CPDTimepoints,
                       rep2 = CPDTimepoints)
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    CPDMismatchData[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
      repitition = names(CPDMismatchData)[i], filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}

sixFourMismatchData = list(rep1 = sixFourTimepoints,
                           rep2 = sixFourTimepoints)
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "6-4-PP", timepoint = names(sixFourMismatchData[[i]])[j],
      repitition = names(sixFourMismatchData)[i], filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}
```

```{r generate_and_write_simplified_and_filtered_mismatch_data}
# Perform general filtering on the data
CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
  x, function(y) filterResults(y, TRUE, 1, minReadLength, maxReadLength)
))
sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
  x, function(y) filterResults(y, TRUE, 1, minReadLength, maxReadLength)
))

# Simplify the data
CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
  x, function(y) simplifyTable(y)
))
sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
  x, function(y) simplifyTable(y)
))

# Write the simplified mismatch data
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    fwrite(CPDMismatchData[[i]][[j]], sep = '\t', na = "NA",
           file = generateFilePath(
             tandemDeaminationDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
             cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
             repitition = names(CPDMismatchData)[i], filtering = filtering,
             includedMismatches = mismatchType
           ))
  }
}

for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    fwrite(sixFourMismatchData[[i]][[j]], sep = '\t', na = "NA",
           file = generateFilePath(
             tandemDeaminationDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
             cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
             repitition = names(sixFourMismatchData)[i], filtering = filtering,
             includedMismatches = mismatchType
           ))
  }
}
```

```{r generate_and_write_mismatch_frequency_z-scores}
CPDMMFreqZScores = lapply(CPDMismatchData, function(x) lapply(
  x, function(y) {
    getMismatchFrequencyZScoreByPosAndReadLength(y, 0)
  }
))
sixFourMMFreqZScores = lapply(sixFourMismatchData, function(x) lapply(
  x, function(y) {
    getMismatchFrequencyZScoreByPosAndReadLength(y, 0)
  }
))

for (i in seq_along(CPDMMFreqZScores)) {
  for (j in seq_along(CPDMMFreqZScores[[i]])) {
    fwrite(CPDMMFreqZScores[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDMMFreqZScores)[i],
      timepoint = names(CPDMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c(mismatchType)
    ))
  }
}

for (i in seq_along(sixFourMMFreqZScores)) {
  for (j in seq_along(sixFourMMFreqZScores[[i]])) {
    fwrite(sixFourMMFreqZScores[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourMMFreqZScores)[i],
      timepoint = names(sixFourMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c(mismatchType)
    ))
  }
}
```

```{r generate_and_write_mismatch_position_statistics_by_read_length_and_timepoint}
CPDGroupedStats = list(rep1 = list(), rep2 = list())
CPDGroupedStats$rep1$three_prime = getGroupedPositionStats(CPDMismatchData$rep1)
CPDGroupedStats$rep2$three_prime = getGroupedPositionStats(CPDMismatchData$rep2)
CPDGroupedStats$rep1$five_prime = getGroupedPositionStats(CPDMismatchData$rep1, posType = FIVE_PRIME)
CPDGroupedStats$rep2$five_prime = getGroupedPositionStats(CPDMismatchData$rep2, posType = FIVE_PRIME)

sixFourGroupedStats = list(rep1 = list(), rep2 = list())
sixFourGroupedStats$rep1$three_prime = getGroupedPositionStats(sixFourMismatchData$rep1)
sixFourGroupedStats$rep2$three_prime = getGroupedPositionStats(sixFourMismatchData$rep2)
sixFourGroupedStats$rep1$five_prime =
  getGroupedPositionStats(sixFourMismatchData$rep1, posType = FIVE_PRIME)
sixFourGroupedStats$rep2$five_prime =
  getGroupedPositionStats(sixFourMismatchData$rep2, posType = FIVE_PRIME)

for (i in seq_along(CPDGroupedStats)) {
  for (j in seq_along(CPDGroupedStats[[i]])) {
    fwrite(CPDGroupedStats[[i]][[j]], sep = '\t',
           file = generateFilePath(
             tandemDeaminationDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
             cellType = cellType, lesion = "CPD", repitition = names(CPDGroupedStats)[i],
             strandPolarity = names(CPDGroupedStats[[i]])[j], filtering = filtering,
             includedMismatches = mismatchType
           ))
  }
}

for (i in seq_along(sixFourGroupedStats)) {
  for (j in seq_along(sixFourGroupedStats[[i]])) {
    fwrite(sixFourGroupedStats[[i]][[j]], sep = '\t',
           file = generateFilePath(
             tandemDeaminationDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
             cellType = cellType, lesion = "6-4", repitition = names(sixFourGroupedStats)[i],
             strandPolarity = names(sixFourGroupedStats[[i]])[j], filtering = filtering,
             includedMismatches = mismatchType
           ))
  }
}
```

EXCISION SITE ANALYSIS STARTS HERE

```{r read_expanded_mismatch_data}
# Get file paths for the expanded mismatch by read data
CPDMismatchData = list(rep1 = CPDTimepoints,
                       rep2 = CPDTimepoints)
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    CPDMismatchData[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
      repitition = names(CPDMismatchData)[i], expansionNum = expansionOffset, filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}

sixFourMismatchData = list(rep1 = sixFourTimepoints,
                           rep2 = sixFourTimepoints)
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "6-4-PP", timepoint = names(sixFourMismatchData[[i]])[j],
      repitition = names(sixFourMismatchData)[i], expansionNum = expansionOffset, filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}
```

```{r generate_simplified_and_filtered_mismatch_data}
# Filter the reads by length and mismatch type (single C>T).
CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
  x, function(y) filterResults(y, minReadLength = minReadLength, maxReadLength = maxReadLength)
))
sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
  x, function(y) filterResults(y, minReadLength = minReadLength, maxReadLength = maxReadLength)
))

# Simplify the data
CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
  x, function(y) simplifyTable(y, TRUE, expansionOffset = expansionOffset)
))
sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
  x, function(y) simplifyTable(y, TRUE, expansionOffset = expansionOffset)
))

# Read mismatch frequency z-scores.
CPDMMFreqZScores = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
for (i in seq_along(CPDMMFreqZScores)) {
  for (j in seq_along(CPDMMFreqZScores[[i]])) {
    CPDMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDMMFreqZScores)[i],
      timepoint = names(CPDMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

sixFourMMFreqZScores = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
for (i in seq_along(sixFourMMFreqZScores)) {
  for (j in seq_along(sixFourMMFreqZScores[[i]])) {
    sixFourMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourMMFreqZScores)[i],
      timepoint = names(sixFourMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

# Further filter data by read position based on length
# NOTE: 6-4 data uses CPD z-scores for filtering.
CPDMismatchData = mapply(function(CPDMismatchDataRep, CPDMMFreqZScoreRep) mapply(
  filterMismatchesByPositionAndReadLength, CPDMismatchDataRep, CPDMMFreqZScoreRep,
  expansionOffset = expansionOffset, SIMPLIFY = FALSE
), CPDMismatchData, CPDMMFreqZScores, SIMPLIFY = FALSE)
sixFourMismatchData = lapply(sixFourMismatchData, function(sixFourMismatchDataRep) {
  lapply(sixFourMismatchDataRep, filterMismatchesByPositionAndReadLength,
         CPDMMFreqZScores[[1]][[1]], expansionOffset = expansionOffset)
})
```

```{r orient_data_to_mismatch_positions}
# NOTE: The assignments to null are there so that the garbage collector can free up memory, and
#       I can still switch to new variable names for organizational purposes.
threePrimeMismatchAnchoredCPDData = lapply(CPDMismatchData, function(x) {
  lapply(x, orientDataToMismatch, THREE_PRIME, expansionOffset, TRUE)
})
fivePrimeMismatchAnchoredCPDData = lapply(CPDMismatchData, function(x) {
  lapply(x, orientDataToMismatch, FIVE_PRIME, expansionOffset, TRUE)
})
CPDMismatchData = NULL

threePrimeMismatchAnchoredSixFourData = lapply(sixFourMismatchData, function(x) {
  lapply(x, orientDataToMismatch, THREE_PRIME, expansionOffset, TRUE)
})
fivePrimeMismatchAnchoredSixFourData = lapply(sixFourMismatchData, function(x) {
  lapply(x, orientDataToMismatch, FIVE_PRIME, expansionOffset, TRUE)
})
sixFourMismatchData = NULL
```

```{r generate_and_write_nucleotide_frequency_data}
threePrimeMismatchCPDNucFreq = lapply(threePrimeMismatchAnchoredCPDData, tabulateNucFreqByPosTimepointAndLength)
for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
  fwrite(threePrimeMismatchCPDNucFreq[[i]], sep = '\t', file = generateFilePath(
    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "CPD", repitition = names(threePrimeMismatchCPDNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}

fivePrimeMismatchCPDNucFreq = lapply(fivePrimeMismatchAnchoredCPDData,
                                     tabulateNucFreqByPosTimepointAndLength, posType = FIVE_PRIME)
for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
  fwrite(fivePrimeMismatchCPDNucFreq[[i]], sep = '\t', file = generateFilePath(
    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMismatchCPDNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}

threePrimeMismatchSixFourNucFreq = lapply(threePrimeMismatchAnchoredSixFourData,
                                          tabulateNucFreqByPosTimepointAndLength)
for (i in seq_along(threePrimeMismatchSixFourNucFreq)) {
  fwrite(threePrimeMismatchSixFourNucFreq[[i]], sep = '\t', file = generateFilePath(
    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "6-4", repitition = names(threePrimeMismatchSixFourNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}

fivePrimeMismatchSixFourNucFreq = lapply(fivePrimeMismatchAnchoredSixFourData,
                                         tabulateNucFreqByPosTimepointAndLength, posType = FIVE_PRIME)
for (i in seq_along(fivePrimeMismatchSixFourNucFreq)) {
  fwrite(fivePrimeMismatchSixFourNucFreq[[i]], sep = '\t', file = generateFilePath(
    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMismatchSixFourNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}
```

```{r generate_and_write_sequence_frequencies}
threePrimeMMAnchoredCPDSeqFreq = lapply(threePrimeMismatchAnchoredCPDData, function(mismatchDataRep) {
  lapply(mismatchDataRep, function(mismatchData) {
    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("CG","CA","TG","TA"))
  })
})
for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
  for (j in seq_along(threePrimeMMAnchoredCPDSeqFreq[[i]])) {
    fwrite(threePrimeMMAnchoredCPDSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(threePrimeMMAnchoredCPDSeqFreq)[i],
      timepoint = names(threePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

fivePrimeMMAnchoredCPDSeqFreq = lapply(fivePrimeMismatchAnchoredCPDData, function(mismatchDataRep) {
  lapply(mismatchDataRep, function(mismatchData) {
    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("TGG"), posType = FIVE_PRIME)
  })
})
for (i in seq_along(fivePrimeMMAnchoredCPDSeqFreq)) {
  for (j in seq_along(fivePrimeMMAnchoredCPDSeqFreq[[i]])) {
    fwrite(fivePrimeMMAnchoredCPDSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMMAnchoredCPDSeqFreq)[i],
      timepoint = names(fivePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

threePrimeMMAnchoredSixFourSeqFreq = lapply(threePrimeMismatchAnchoredSixFourData, function(mismatchDataRep) {
  lapply(mismatchDataRep, function(mismatchData) {
    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("CG","CA","TG","TA"))
  })
})
for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
  for (j in seq_along(threePrimeMMAnchoredSixFourSeqFreq[[i]])) {
    fwrite(threePrimeMMAnchoredSixFourSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(threePrimeMMAnchoredSixFourSeqFreq)[i],
      timepoint = names(threePrimeMMAnchoredSixFourSeqFreq[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

fivePrimeMMAnchoredSixFourSeqFreq = lapply(fivePrimeMismatchAnchoredSixFourData, function(mismatchDataRep) {
  lapply(mismatchDataRep, function(mismatchData) {
    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("TGG"), posType = FIVE_PRIME)
  })
})
for (i in seq_along(fivePrimeMMAnchoredSixFourSeqFreq)) {
  for (j in seq_along(fivePrimeMMAnchoredSixFourSeqFreq[[i]])) {
    fwrite(fivePrimeMMAnchoredSixFourSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMMAnchoredSixFourSeqFreq)[i],
      timepoint = names(fivePrimeMMAnchoredSixFourSeqFreq[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

### 2022-06-06 R/NHF1TandemDeaminationFigureGeneration.rmd
Created NHF1 tandem deamination notebooks

---
title: "NHF1 Tandem Deamination Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
  mismatchType:
    label: "Mismatch Type"
    value: CC>TT
    input: select
    choices: [CC>TT, GG>AA]
---

```{r setup_chunk}
library(knitr)

cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL)
sixFourTimepoints = list(`1h` = NULL)
minReadLength = 22; maxReadLength = 30

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
  filtering = readline("Filtering identifier (Input nothing for no filtering):")
  if (filtering == '') filtering = character()
  mismatchType = readline("Tandem mismatch type:")
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
  filtering = params$filtering
  if (filtering == "NONE") filtering = character()
  mismatchType = params$mismatchType
}
if (length(filtering) > 0) {
  titleCaseFiltering = tools::toTitleCase(gsub('_', ' ', filtering))
} else titleCaseFiltering = character()
titleCaseMismatchType = tools::toTitleCase(gsub('>', " To ", mismatchType))

opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
               fig.path = paste0(file.path("deamination_analysis_output",cellType,
                                           paste(c(filtering,
                                                   gsub('>', "_to_", mismatchType),
                                                   "tandem_deamination_figures"), collapse = '_')),
                                 .Platform$file.sep))

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
tandemDeaminationDataDirectory = file.path(deaminationDataDirectory,
                                           paste(str_replace(mismatchType, '>', "_to_"),
                                                 "tandem_deaminations", sep = '_'))
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationSequenceAndPositionAnalysis.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationAnchoredExcisionSiteAnalysis.R"))
```

```{r read_simplified_mismatch_data}
# Get file paths for the mismatch by read data
CPDMismatchData = list(rep1 = CPDTimepoints,
                       rep2 = CPDTimepoints)
for (i in seq_along(CPDMismatchData)) {
  for (j in seq_along(CPDMismatchData[[i]])) {
    CPDMismatchData[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
      cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
      repitition = names(CPDMismatchData)[i], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

sixFourMismatchData = list(rep1 = sixFourTimepoints,
                           rep2 = sixFourTimepoints)
for (i in seq_along(sixFourMismatchData)) {
  for (j in seq_along(sixFourMismatchData[[i]])) {
    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
      cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
      repitition = names(sixFourMismatchData)[i], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

```{r CPD_mismatch_pos_frequency}
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]],
                                    title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
                                                    names(CPDMismatchData)[i], 
                                                    names(CPDMismatchData[[i]])[j], "Mismatch Pos"),
                                                  collapse = ' '))
  }
}
```

```{r 6-4_mismatch_pos_frequency}
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]],
                                    title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
                                                    names(sixFourMismatchData)[i], 
                                                    names(sixFourMismatchData[[i]])[j], "Mismatch Pos"),
                                                  collapse = ' '))
  }
}
```

```{r read_mismatch_frequency_z-score_tables}
CPDMMFreqZScores = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
for (i in seq_along(CPDMMFreqZScores)) {
  for (j in seq_along(CPDMMFreqZScores[[i]])) {
    CPDMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDMMFreqZScores)[i],
      timepoint = names(CPDMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

sixFourMMFreqZScores = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
for (i in seq_along(sixFourMMFreqZScores)) {
  for (j in seq_along(sixFourMMFreqZScores[[i]])) {
    sixFourMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourMMFreqZScores)[i],
      timepoint = names(sixFourMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

```{r CPD_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1,
                                         title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
                                                         "Mismatch Pos Freq Rep1"),
                                                       collapse = ' '),
                                         zScoreTables = CPDMMFreqZScores$rep1)
plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2,
                                         title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
                                                         "Mismatch Pos Freq Rep2"),
                                                       collapse = ' '),
                                         zScoreTables = CPDMMFreqZScores$rep2)
plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, posType = FIVE_PRIME,
                                         title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
                                                         "Mismatch Pos Freq Rep1"),
                                                       collapse = ' '),
                                         zScoreTables = CPDMMFreqZScores$rep1)
plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, posType = FIVE_PRIME,
                                         title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
                                                         "Mismatch Pos Freq Rep2"),
                                                       collapse = ' '),
                                         zScoreTables = CPDMMFreqZScores$rep2)
```

```{r 6-4_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1,
                                         title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
                                                         "Mismatch Pos Freq Rep1"),
                                                       collapse = ' '),
                                         zScoreTables = sixFourMMFreqZScores$rep1)
plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2,
                                         title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
                                                         "Mismatch Pos Freq Rep2"),
                                                       collapse = ' '),
                                         zScoreTables = sixFourMMFreqZScores$rep2)
plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, posType = FIVE_PRIME,
                                         title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
                                                         "Mismatch Pos Freq Rep1"),
                                                       collapse = ' '),
                                         zScoreTables = sixFourMMFreqZScores$rep1)
plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, posType = FIVE_PRIME,
                                         title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
                                                         "Mismatch Pos Freq Rep2"),
                                                       collapse = ' '),
                                         zScoreTables = sixFourMMFreqZScores$rep2)
```

```{r CPD_read_length_distributions}
plotReadLengthFrequencies(CPDMismatchData$rep1,
                          title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
                                          "Read Length Freq Rep1"), collapse = ' '))
plotReadLengthFrequencies(CPDMismatchData$rep2,
                          title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
                                          "Read Length Freq Rep2"), collapse = ' '))
```

```{r 6-4_read_length_distributions}
plotReadLengthFrequencies(sixFourMismatchData$rep1,
                          title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
                                          "Read Length Freq Rep1"), collapse = ' '))
plotReadLengthFrequencies(sixFourMismatchData$rep2,
                          title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
                                          "Read Length Freq Rep2"), collapse = ' '))
```

```{r read_mismatch_position_statistics}
CPDGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
                       rep2 = list(three_prime = NULL, five_prime = NULL))
for (i in seq_along(CPDGroupedStats)) {
  for (j in seq_along(CPDGroupedStats[[i]])) {
    CPDGroupedStats[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDGroupedStats)[i],
      strandPolarity = names(CPDGroupedStats[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

sixFourGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
                           rep2 = list(three_prime = NULL, five_prime = NULL))
for (i in seq_along(sixFourGroupedStats)) {
  for (j in seq_along(sixFourGroupedStats[[i]])) {
    sixFourGroupedStats[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourGroupedStats)[i],
      strandPolarity = names(sixFourGroupedStats[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

```{r CPD_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, POS_DIFF,
                         title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
                                         "Mismatch Pos Diff Rep1"), collapse = ' '),
                         xAxisBreaks = c(minReadLength:maxReadLength))
plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, POS_DIFF,
                         title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
                                         "Mismatch Pos Diff Rep2"), collapse = ' '),
                         xAxisBreaks = c(minReadLength:maxReadLength))
```

```{r 6-4_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, POS_DIFF,
                         title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
                                         "Mismatch Pos Diff Rep1"), collapse = ' '),
                         xAxisBreaks = c(minReadLength:maxReadLength))
plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, POS_DIFF,
                         title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
                                         "Mismatch Pos Diff Rep2"), collapse = ' '),
                         xAxisBreaks = c(minReadLength:maxReadLength))
```

### 2022-06-08 R/DeaminationSequenceAndPositionAnalysis.R
Updated mismatch position frequency facet plot
Better spacing on x-axis to avoid overlapping text.

@@ -92,8 +92,10 @@ plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTy
 
   if (posType == THREE_PRIME) {
     xAxisLabel = "3' Relative Position"
+    xlim = c(min(xAxisBreaks)*1.1,0)
   } else if (posType == FIVE_PRIME) {
     xAxisLabel = "5' Relative Position"
+    xlim = c(0, max(xAxisBreaks)*1.1)
     simplifiedTables = lapply(simplifiedTables, copy)
     lapply(simplifiedTables, function(x) x[, Position := Read_Length + Position + 1])
     if (!is.null(zScoreTables)) {
@@ -151,7 +153,7 @@ plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTy
     yAxisBreaks = c(0, maxFrequency/2, maxFrequency)
     plot = plot + theme(axis.text.y = element_text(size = 10)) +
       scale_y_continuous(breaks = yAxisBreaks, sec.axis = dup_axis(~., name = "Read Length"),) +
-      coord_cartesian(ylim = (c(0, maxFrequency*1.2)))
+      coord_cartesian(ylim = c(0, maxFrequency*1.2))
   } else {
     plot = plot + theme(axis.text.y = element_text(size = 10)) +
       scale_y_continuous(breaks = yAxisBreaks, sec.axis = dup_axis(~., name = "Read Length"),) +
@@ -164,7 +166,8 @@ plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTy
           axis.text.y.right = element_blank(), axis.ticks.y.right = element_blank(),
           strip.text.y = element_text(size = 16)) +
     geom_vline(xintercept = modePosition) +
-    scale_x_continuous(breaks = xAxisBreaks)
+    scale_x_continuous(breaks = xAxisBreaks) +
+    coord_cartesian(xlim = xlim)
 
   print(plot)
 

### 2022-06-08 R/NHF1TandemDeaminationDataGeneration.rmd
Finished NHF1 tandem deamination notebooks

@@
 cellType = "NHF1"
-CPDTimepoints = list(`1h` = NULL)
-sixFourTimepoints = list(`1h` = NULL)
+CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
+sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
 expansionOffset = 10

### 2022-06-08 R/NHF1TandemDeaminationFigureGeneration.rmd
Finished NHF1 tandem deamination notebooks

@@
 library(knitr)
+library(stringr)
 
+expansionOffset = 10
 cellType = "NHF1"
-CPDTimepoints = list(`1h` = NULL)
-sixFourTimepoints = list(`1h` = NULL)
+CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
+sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
 minReadLength = 22; maxReadLength = 30
@@
 ```
+
+EXCISION SITE FIGURE GENERATION STARTS HERE
+
+```{r read_nucleotide_frequency_data}
+threePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL)
+for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
+  threePrimeMismatchCPDNucFreq[[i]] = fread(generateFilePath(
+    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    cellType = cellType, lesion = "CPD", repitition = names(threePrimeMismatchCPDNucFreq)[i],
+    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
+  ))
+}
+
+fivePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL)
+for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
+  fivePrimeMismatchCPDNucFreq[[i]] = fread(generateFilePath(
+    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMismatchCPDNucFreq)[i],
+    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
+  ))
+}
+
+threePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL)
+for (i in seq_along(threePrimeMismatchSixFourNucFreq)) {
+  threePrimeMismatchSixFourNucFreq[[i]] = fread(generateFilePath(
+    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    cellType = cellType, lesion = "6-4", repitition = names(threePrimeMismatchSixFourNucFreq)[i],
+    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
+  ))
+}
+
+fivePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL)
+for (i in seq_along(fivePrimeMismatchSixFourNucFreq)) {
+  fivePrimeMismatchSixFourNucFreq[[i]] = fread(generateFilePath(
+    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMismatchSixFourNucFreq)[i],
+    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
+  ))
+}
+```
+
+```{r CPD_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
+plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
+                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                               "3' Anchored Nuc Freq Rep1"), collapse = ' '),
+                               secondaryYAxisLabel = "5' Cut Site Distance",
+                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep2, 
+                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                               "3' Anchored Nuc Freq Rep2"), collapse = ' '),
+                               secondaryYAxisLabel = "5' Cut Site Distance",
+                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+
+plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
+                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                               "5' Anchored Nuc Freq Rep1"), collapse = ' '),
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
+                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                               "5' Anchored Nuc Freq Rep2"), collapse = ' '),
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+```
+
+```{r CPD_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
+plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
+                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                               "3' Anchored Purine Freq Rep1"), collapse = ' '),
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep2, 
+                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                               "3' Anchored Purine Freq Rep2"), collapse = ' '),
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+
+plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
+                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                               "5' Anchored Purine Freq Rep1"), collapse = ' '),
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
+                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                               "5' Anchored Purine Freq Rep2"), collapse = ' '),
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+```
+
+```{r 6-4_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
+plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
+                               title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
+                                               "3' Anchored Nuc Freq Rep1"), collapse = ' '),
+                               secondaryYAxisLabel = "5' Cut Site Distance",
+                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
+                               title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
+                                               "3' Anchored Nuc Freq Rep2"), collapse = ' '),
+                               secondaryYAxisLabel = "5' Cut Site Distance",
+                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+
+plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep1, 
+                               title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
+                                               "5' Anchored Nuc Freq Rep1"), collapse = ' '),
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep2, 
+                               title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
+                                               "5' Anchored Nuc Freq Rep2"), collapse = ' '),
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+```
+
+```{r 6-4_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
+plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
+                               title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
+                                               "3' Anchored Purine Freq Rep1"), collapse = ' '),
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
+                               title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
+                                               "3' Anchored Purine Freq Rep2"), collapse = ' '),
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+
+plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep1, 
+                               title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
+                                               "5' Anchored Purine Freq Rep1"), collapse = ' '),
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep2, 
+                               title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
+                                               "5' Anchored Purine Freq Rep2"), collapse = ' '),
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+```
+
+```{r read_sequence_frequency_data}
+threePrimeMMAnchoredCPDSeqFreq = list(rep1 = CPDTimepoints,
+                                      rep2 = CPDTimepoints)
+for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
+  for (j in seq_along(threePrimeMMAnchoredCPDSeqFreq[[i]])) {
+    threePrimeMMAnchoredCPDSeqFreq[[i]][[j]] = fread(generateFilePath(
+      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      cellType = cellType, lesion = "CPD", repitition = names(threePrimeMMAnchoredCPDSeqFreq)[i],
+      timepoint = names(threePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "three_prime",
+      anchored = TRUE, sequence = "YR", filtering = filtering, includedMismatches = mismatchType
+    ))
+  }
+}
+
+fivePrimeMMAnchoredCPDSeqFreq = list(rep1 = CPDTimepoints,
+                                     rep2 = CPDTimepoints)
+for (i in seq_along(fivePrimeMMAnchoredCPDSeqFreq)) {
+  for (j in seq_along(fivePrimeMMAnchoredCPDSeqFreq[[i]])) {
+    fivePrimeMMAnchoredCPDSeqFreq[[i]][[j]] = fread(generateFilePath(
+      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMMAnchoredCPDSeqFreq)[i],
+      timepoint = names(fivePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "five_prime",
+      anchored = TRUE, sequence = "TGG", filtering = filtering, includedMismatches = mismatchType
+    ))
+  }
+}
+
+threePrimeMMAnchoredSixFourSeqFreq = list(rep1 = sixFourTimepoints,
+                                          rep2 = sixFourTimepoints)
+for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
+  for (j in seq_along(threePrimeMMAnchoredSixFourSeqFreq[[i]])) {
+    threePrimeMMAnchoredSixFourSeqFreq[[i]][[j]] = fread(generateFilePath(
+      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      cellType = cellType, lesion = "6-4", repitition = names(threePrimeMMAnchoredSixFourSeqFreq)[i],
+      timepoint = names(threePrimeMMAnchoredSixFourSeqFreq[[i]])[j], strandPolarity = "three_prime",
+      anchored = TRUE, sequence = "YR", filtering = filtering, includedMismatches = mismatchType
+    ))
+  }
+}
+
+fivePrimeMMAnchoredSixFourSeqFreq = list(rep1 = sixFourTimepoints,
+                                         rep2 = sixFourTimepoints)
+for (i in seq_along(fivePrimeMMAnchoredSixFourSeqFreq)) {
+  for (j in seq_along(fivePrimeMMAnchoredSixFourSeqFreq[[i]])) {
+    fivePrimeMMAnchoredSixFourSeqFreq[[i]][[j]] = fread(generateFilePath(
+      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMMAnchoredSixFourSeqFreq)[i],
+      timepoint = names(fivePrimeMMAnchoredSixFourSeqFreq[[i]])[j], strandPolarity = "five_prime",
+      anchored = TRUE, sequence = "TGG", filtering = filtering, includedMismatches = mismatchType
+    ))
+  }
+}
+```
+
+```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 9}
+plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq$rep1,
+                        title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                        "3' Anchored YR Freq Rep1"), collapse = ' '),
+                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
+plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq$rep2,
+                        title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                        "3' Anchored YR Freq Rep2"), collapse = ' '),
+                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
+
+plotSequenceFrequencies(fivePrimeMMAnchoredCPDSeqFreq$rep1,
+                        title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                        "5' Anchored TGG Freq Rep1"), collapse = ' '),
+                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
+                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
+plotSequenceFrequencies(fivePrimeMMAnchoredCPDSeqFreq$rep2,
+                        title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                        "5' Anchored TGG Freq Rep2"), collapse = ' '),
+                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
+                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
+```
+
+```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 9}
+plotSequenceFrequencies(threePrimeMMAnchoredSixFourSeqFreq$rep1,
+                        title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
+                                        "3' Anchored YR Freq Rep1"), collapse = ' '),
+                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
+plotSequenceFrequencies(threePrimeMMAnchoredSixFourSeqFreq$rep2,
+                        title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
+                                        "3' Anchored YR Freq Rep2"), collapse = ' '),
+                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
+
+plotSequenceFrequencies(fivePrimeMMAnchoredSixFourSeqFreq$rep1,
+                        title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
+                                        "5' Anchored TGG Freq Rep1"), collapse = ' '),
+                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
+                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
+plotSequenceFrequencies(fivePrimeMMAnchoredSixFourSeqFreq$rep2,
+                        title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
+                                        "5' Anchored TGG Freq Rep2"), collapse = ' '),
+                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
+                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
+```

### 2022-06-08 R/DeaminationAnchoredExcisionSiteAnalysis.R
Functions are more robust to empty input.

@@ -79,7 +79,12 @@ tabulateNucFreqByPosTimepointAndLength = function(simplifiedTablesByTimepoint, p
     nucFreqTable = combineNucleotideFrequencies(nucFreqTable, combineNucleotides, combinedNames)
   }
 
-  return(nucFreqTable)
+  if (dim(nucFreqTable)[1] > 0) {
+    return(nucFreqTable)
+  } else {
+    return(data.table(Position = numeric(), Nucleotide = character(),
+                      Read_Length = numeric(), Timepoint = character()))
+  }
 
 }
 
@@ -170,6 +175,10 @@ plotNucFreqVsReadLengthBarPlot = function(nucFreqTable, posType = THREE_PRIME,
 # that same data for one side of that data, anchored on the mismatch
 orientDataToMismatch = function(simplifiedTable, posType, expansionOffset = 0, halfPositions = FALSE) {
 
+  # Check to see if the input table is empty. If it is, return an empty table.
+  if (dim(simplifiedTable)[1] == 0) return(data.table(Position = numeric(), Mismatch = character(),
+                                                      Read_Length = numeric(), Read_Sequence = character()))
+
   if (posType == THREE_PRIME) {
     if (halfPositions) {
       sequences = str_sub(simplifiedTable$Read_Sequence,
@@ -206,7 +215,7 @@ getSequenceFreqByReadLengthAndPos = function(readSequencesTable, expectedNucleot
   # Calculating expected and observed frequencies across all the query sequences at each position
   # NOTE: In order to determine what positions to iterate through, the following code assumes that
   #       all read sequences under a specific read length actually have that length.
-  return(rbindlist(lapply(unique(readSequencesTable$Read_Length), function(readLength) {
+  seqFreqTable = rbindlist(lapply(unique(readSequencesTable$Read_Length), function(readLength) {
 
     sequences = readSequencesTable[Read_Length == readLength]$Read_Sequence
     if (!is.null(expectedNucleotideFrequencies)) {
@@ -250,7 +259,17 @@ getSequenceFreqByReadLengthAndPos = function(readSequencesTable, expectedNucleot
       return(data.table(Position = positions, Read_Length = readLength, Frequency = frequencies))
     }
 
-  })))
+  }))
+
+  if (dim(seqFreqTable)[1] > 0) {
+    return(seqFreqTable)
+  } else {
+    if (!is.null(expectedNucleotideFrequencies)) {
[…]

### 2022-06-08 R/ArabidopsisTandemDeaminationDataGeneration.rmd
Created Arabidopsis tandem deamination notebooks

--- 2022-06-06 R/NHF1TandemDeaminationDataGeneration.rmd
@@
 ---
-title: "NHF1 Tandem Deamination Data Generation"
+title: "Arabidopsis Tandem Deamination Data Generation"
 author: "Ben Morledge-Hampton"
@@
 
-cellType = "NHF1"
-CPDTimepoints = list(`1h` = NULL)
-sixFourTimepoints = list(`1h` = NULL)
 expansionOffset = 10
-minReadLength = 22; maxReadLength = 30
+cellType = "Arabidopsis"
+CPDTimepoints = list(`ZT2` = NULL, `ZT14` = NULL)
+minReadLength = 24; maxReadLength = 30
 
@@
 }
-
-sixFourMismatchData = list(rep1 = sixFourTimepoints,
-                           rep2 = sixFourTimepoints)
-for (i in 1:length(sixFourMismatchData)) {
-  for (j in 1:length(sixFourMismatchData[[i]])) {
-    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
-      tandemDeaminationDataDirectory, dataTypeStrings$mismatchesByRead, ".bed",
-      cellType = cellType, lesion = "6-4-PP", timepoint = names(sixFourMismatchData[[i]])[j],
-      repitition = names(sixFourMismatchData)[i], filtering = filtering,
-      includedMismatches = mismatchType
-      ))
-  }
-}
 ```
@@
 ))
-sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
-  x, function(y) filterResults(y, TRUE, 1, minReadLength, maxReadLength)
-))
 
@@
 CPDMismatchData = lapply(CPDMismatchData, function(x) lapply(
-  x, function(y) simplifyTable(y)
-))
-sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
   x, function(y) simplifyTable(y)
@@
 }
-
-for (i in 1:length(sixFourMismatchData)) {
-  for (j in 1:length(sixFourMismatchData[[i]])) {
-    fwrite(sixFourMismatchData[[i]][[j]], sep = '\t', na = "NA",
-           file = generateFilePath(
-             tandemDeaminationDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
-             cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
-             repitition = names(sixFourMismatchData)[i], filtering = filtering,
-             includedMismatches = mismatchType
-           ))
-  }
-}
 ```
@@
 CPDMMFreqZScores = lapply(CPDMismatchData, function(x) lapply(
-  x, function(y) {
-    getMismatchFrequencyZScoreByPosAndReadLength(y, 0)
-  }
-))
-sixFourMMFreqZScores = lapply(sixFourMismatchData, function(x) lapply(
   x, function(y) {
@@
 }
-
-for (i in seq_along(sixFourMMFreqZScores)) {
-  for (j in seq_along(sixFourMMFreqZScores[[i]])) {
-    fwrite(sixFourMMFreqZScores[[i]][[j]], sep = '\t', file = generateFilePath(
-      directory = tandemDeaminationDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
-      cellType = cellType, lesion = "6-4", repitition = names(sixFourMMFreqZScores)[i],
-      timepoint = names(sixFourMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c(mismatchType)
-    ))
-  }
-}
 ```
@@
 
-sixFourGroupedStats = list(rep1 = list(), rep2 = list())
-sixFourGroupedStats$rep1$three_prime = getGroupedPositionStats(sixFourMismatchData$rep1)
-sixFourGroupedStats$rep2$three_prime = getGroupedPositionStats(sixFourMismatchData$rep2)
-sixFourGroupedStats$rep1$five_prime =
-  getGroupedPositionStats(sixFourMismatchData$rep1, posType = FIVE_PRIME)
-sixFourGroupedStats$rep2$five_prime =
-  getGroupedPositionStats(sixFourMismatchData$rep2, posType = FIVE_PRIME)
-
 for (i in seq_along(CPDGroupedStats)) {
@@
              strandPolarity = names(CPDGroupedStats[[i]])[j], filtering = filtering,
-             includedMismatches = mismatchType
-           ))
-  }
-}
-
-for (i in seq_along(sixFourGroupedStats)) {
-  for (j in seq_along(sixFourGroupedStats[[i]])) {
-    fwrite(sixFourGroupedStats[[i]][[j]], sep = '\t',
-           file = generateFilePath(
-             tandemDeaminationDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
-             cellType = cellType, lesion = "6-4", repitition = names(sixFourGroupedStats)[i],
-             strandPolarity = names(sixFourGroupedStats[[i]])[j], filtering = filtering,
              includedMismatches = mismatchType
@@
 }
-
-sixFourMismatchData = list(rep1 = sixFourTimepoints,
-                           rep2 = sixFourTimepoints)
-for (i in 1:length(sixFourMismatchData)) {
-  for (j in 1:length(sixFourMismatchData[[i]])) {
-    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
-      tandemDeaminationDataDirectory, dataTypeStrings$mismatchesByRead, ".bed",
-      cellType = cellType, lesion = "6-4-PP", timepoint = names(sixFourMismatchData[[i]])[j],
-      repitition = names(sixFourMismatchData)[i], expansionNum = expansionOffset, filtering = filtering,
-      includedMismatches = mismatchType
-      ))
-  }
-}
 ```
@@
 ))
-sixFourMismatchData = lapply(sixFourMismatchData, function(x) lapply(
-  x, function(y) filterResults(y, minReadLength = minReadLength, maxReadLength = maxReadLength)
-))
 
@@
 
-sixFourMMFreqZScores = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
-for (i in seq_along(sixFourMMFreqZScores)) {
-  for (j in seq_along(sixFourMMFreqZScores[[i]])) {
-    sixFourMMFreqZScores[[i]][[j]] = fread(generateFilePath(
-      directory = tandemDeaminationDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
-      cellType = cellType, lesion = "6-4", repitition = names(sixFourMMFreqZScores)[i],
-      timepoint = names(sixFourMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = mismatchType
-    ))
-  }
-}
-
 # Further filter data by read position based on length
@@
 ), CPDMismatchData, CPDMMFreqZScores, SIMPLIFY = FALSE)
-sixFourMismatchData = lapply(sixFourMismatchData, function(sixFourMismatchDataRep) {
-  lapply(sixFourMismatchDataRep, filterMismatchesByPositionAndReadLength,
-         CPDMMFreqZScores[[1]][[1]], expansionOffset = expansionOffset)
-})
 ```
@@
 CPDMismatchData = NULL
-
-threePrimeMismatchAnchoredSixFourData = lapply(sixFourMismatchData, function(x) {
-  lapply(x, orientDataToMismatch, THREE_PRIME, expansionOffset, TRUE)
-})
-fivePrimeMismatchAnchoredSixFourData = lapply(sixFourMismatchData, function(x) {
-  lapply(x, orientDataToMismatch, FIVE_PRIME, expansionOffset, TRUE)
-})
-sixFourMismatchData = NULL
 ```
@@
     cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMismatchCPDNucFreq)[i],
-    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
-  ))
-}
-
-threePrimeMismatchSixFourNucFreq = lapply(threePrimeMismatchAnchoredSixFourData,
-                                          tabulateNucFreqByPosTimepointAndLength)
-for (i in seq_along(threePrimeMismatchSixFourNucFreq)) {
-  fwrite(threePrimeMismatchSixFourNucFreq[[i]], sep = '\t', file = generateFilePath(
-    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
-    cellType = cellType, lesion = "6-4", repitition = names(threePrimeMismatchSixFourNucFreq)[i],
-    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
-  ))
-}
-
-fivePrimeMismatchSixFourNucFreq = lapply(fivePrimeMismatchAnchoredSixFourData,
-                                         tabulateNucFreqByPosTimepointAndLength, posType = FIVE_PRIME)
-for (i in seq_along(fivePrimeMismatchSixFourNucFreq)) {
-  fwrite(fivePrimeMismatchSixFourNucFreq[[i]], sep = '\t', file = generateFilePath(
-    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
-    cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMismatchSixFourNucFreq)[i],
     strandPolarity = "five_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
@@
 }
-
-threePrimeMMAnchoredSixFourSeqFreq = lapply(threePrimeMismatchAnchoredSixFourData, function(mismatchDataRep) {
-  lapply(mismatchDataRep, function(mismatchData) {
-    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("CG","CA","TG","TA"))
-  })
-})
-for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
-  for (j in seq_along(threePrimeMMAnchoredSixFourSeqFreq[[i]])) {
-    fwrite(threePrimeMMAnchoredSixFourSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
-      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
-      cellType = cellType, lesion = "6-4", repitition = names(threePrimeMMAnchoredSixFourSeqFreq)[i],
-      timepoint = names(threePrimeMMAnchoredSixFourSeqFreq[[i]])[j], strandPolarity = "three_prime",
-      anchored = TRUE, sequence = "YR", filtering = filtering, includedMismatches = mismatchType
-    ))
-  }
-}
-
-fivePrimeMMAnchoredSixFourSeqFreq = lapply(fivePrimeMismatchAnchoredSixFourData, function(mismatchDataRep) {
-  lapply(mismatchDataRep, function(mismatchData) {
-    getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("TGG"), posType = FIVE_PRIME)
-  })
-})
-for (i in seq_along(fivePrimeMMAnchoredSixFourSeqFreq)) {
-  for (j in seq_along(fivePrimeMMAnchoredSixFourSeqFreq[[i]])) {
-    fwrite(fivePrimeMMAnchoredSixFourSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
-      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
-      cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMMAnchoredSixFourSeqFreq)[i],
-      timepoint = names(fivePrimeMMAnchoredSixFourSeqFreq[[i]])[j], strandPolarity = "five_prime",
-      anchored = TRUE, sequence = "TGG", filtering = filtering, includedMismatches = mismatchType
-    ))
-  }
-}
 ```

### 2022-06-08 R/ArabidopsisTandemDeaminationFigureGeneration.rmd
Created Arabidopsis tandem deamination notebooks

--- 2022-06-06 R/NHF1TandemDeaminationFigureGeneration.rmd
@@
 ---
-title: "NHF1 Tandem Deamination Figure Generation"
+title: "Arabidopsis Tandem Deamination Figure Generation"
 author: "Ben Morledge-Hampton"
@@
 library(knitr)
+library(stringr)
 
-cellType = "NHF1"
-CPDTimepoints = list(`1h` = NULL)
-sixFourTimepoints = list(`1h` = NULL)
-minReadLength = 22; maxReadLength = 30
+expansionOffset = 10
+cellType = "Arabidopsis"
+CPDTimepoints = list(`ZT2` = NULL, `ZT14` = NULL)
+minReadLength = 24; maxReadLength = 30
 
@@
 }
-
-sixFourMismatchData = list(rep1 = sixFourTimepoints,
-                           rep2 = sixFourTimepoints)
-for (i in seq_along(sixFourMismatchData)) {
-  for (j in seq_along(sixFourMismatchData[[i]])) {
-    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
-      tandemDeaminationDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
-      cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
-      repitition = names(sixFourMismatchData)[i], filtering = filtering, includedMismatches = mismatchType
-    ))
-  }
-}
 ```
@@
 
-```{r 6-4_mismatch_pos_frequency}
-for (i in 1:length(sixFourMismatchData)) {
-  for (j in 1:length(sixFourMismatchData[[i]])) {
-    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]],
-                                    title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                                    names(sixFourMismatchData)[i], 
-                                                    names(sixFourMismatchData[[i]])[j], "Mismatch Pos"),
-                                                  collapse = ' '))
-  }
-}
-```
-
 ```{r read_mismatch_frequency_z-score_tables}
@@
       timepoint = names(CPDMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = mismatchType
-    ))
-  }
-}
-
-sixFourMMFreqZScores = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
-for (i in seq_along(sixFourMMFreqZScores)) {
-  for (j in seq_along(sixFourMMFreqZScores[[i]])) {
-    sixFourMMFreqZScores[[i]][[j]] = fread(generateFilePath(
-      directory = tandemDeaminationDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
-      cellType = cellType, lesion = "6-4", repitition = names(sixFourMMFreqZScores)[i],
-      timepoint = names(sixFourMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = mismatchType
     ))
@@
 
-```{r 6-4_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1,
-                                         title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                                         "Mismatch Pos Freq Rep1"),
-                                                       collapse = ' '),
-                                         zScoreTables = sixFourMMFreqZScores$rep1)
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2,
-                                         title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                                         "Mismatch Pos Freq Rep2"),
-                                                       collapse = ' '),
-                                         zScoreTables = sixFourMMFreqZScores$rep2)
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, posType = FIVE_PRIME,
-                                         title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                                         "Mismatch Pos Freq Rep1"),
-                                                       collapse = ' '),
-                                         zScoreTables = sixFourMMFreqZScores$rep1)
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, posType = FIVE_PRIME,
-                                         title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                                         "Mismatch Pos Freq Rep2"),
-                                                       collapse = ' '),
-                                         zScoreTables = sixFourMMFreqZScores$rep2)
-```
-
 ```{r CPD_read_length_distributions}
@@
                           title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                          "Read Length Freq Rep2"), collapse = ' '))
-```
-
-```{r 6-4_read_length_distributions}
-plotReadLengthFrequencies(sixFourMismatchData$rep1,
-                          title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                          "Read Length Freq Rep1"), collapse = ' '))
-plotReadLengthFrequencies(sixFourMismatchData$rep2,
-                          title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
                                           "Read Length Freq Rep2"), collapse = ' '))
@@
       strandPolarity = names(CPDGroupedStats[[i]])[j], filtering = filtering, includedMismatches = mismatchType
-    ))
-  }
-}
-
-sixFourGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
-                           rep2 = list(three_prime = NULL, five_prime = NULL))
-for (i in seq_along(sixFourGroupedStats)) {
-  for (j in seq_along(sixFourGroupedStats[[i]])) {
-    sixFourGroupedStats[[i]][[j]] = fread(generateFilePath(
-      tandemDeaminationDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
-      cellType = cellType, lesion = "6-4", repitition = names(sixFourGroupedStats)[i],
-      strandPolarity = names(sixFourGroupedStats[[i]])[j], filtering = filtering, includedMismatches = mismatchType
     ))
@@
 
-```{r 6-4_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
-plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, POS_DIFF,
-                         title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                         "Mismatch Pos Diff Rep1"), collapse = ' '),
-                         xAxisBreaks = c(minReadLength:maxReadLength))
-plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, POS_DIFF,
-                         title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                         "Mismatch Pos Diff Rep2"), collapse = ' '),
-                         xAxisBreaks = c(minReadLength:maxReadLength))
+EXCISION SITE FIGURE GENERATION STARTS HERE
+
+```{r read_nucleotide_frequency_data}
+threePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL)
+for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
+  threePrimeMismatchCPDNucFreq[[i]] = fread(generateFilePath(
+    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    cellType = cellType, lesion = "CPD", repitition = names(threePrimeMismatchCPDNucFreq)[i],
+    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
+  ))
+}
+
+fivePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL)
+for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
+  fivePrimeMismatchCPDNucFreq[[i]] = fread(generateFilePath(
+    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMismatchCPDNucFreq)[i],
+    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
+  ))
+}
 ```
+
+```{r CPD_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
+plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
+                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                               "3' Anchored Nuc Freq Rep1"), collapse = ' '),
+                               secondaryYAxisLabel = "5' Cut Site Distance",
+                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep2, 
+                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                               "3' Anchored Nuc Freq Rep2"), collapse = ' '),
+                               secondaryYAxisLabel = "5' Cut Site Distance",
+                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+
+plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
+                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                               "5' Anchored Nuc Freq Rep1"), collapse = ' '),
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
+                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                               "5' Anchored Nuc Freq Rep2"), collapse = ' '),
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+```
+
+```{r CPD_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
+plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
+                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                               "3' Anchored Purine Freq Rep1"), collapse = ' '),
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep2, 
+                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                               "3' Anchored Purine Freq Rep2"), collapse = ' '),
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+
+plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
+                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                               "5' Anchored Purine Freq Rep1"), collapse = ' '),
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
+                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                               "5' Anchored Purine Freq Rep2"), collapse = ' '),
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+```
+
+```{r read_sequence_frequency_data}
+threePrimeMMAnchoredCPDSeqFreq = list(rep1 = CPDTimepoints,
+                                      rep2 = CPDTimepoints)
+for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
+  for (j in seq_along(threePrimeMMAnchoredCPDSeqFreq[[i]])) {
+    threePrimeMMAnchoredCPDSeqFreq[[i]][[j]] = fread(generateFilePath(
+      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      cellType = cellType, lesion = "CPD", repitition = names(threePrimeMMAnchoredCPDSeqFreq)[i],
+      timepoint = names(threePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "three_prime",
+      anchored = TRUE, sequence = "YR", filtering = filtering, includedMismatches = mismatchType
+    ))
+  }
+}
+
+fivePrimeMMAnchoredCPDSeqFreq = list(rep1 = CPDTimepoints,
+                                     rep2 = CPDTimepoints)
+for (i in seq_along(fivePrimeMMAnchoredCPDSeqFreq)) {
+  for (j in seq_along(fivePrimeMMAnchoredCPDSeqFreq[[i]])) {
+    fivePrimeMMAnchoredCPDSeqFreq[[i]][[j]] = fread(generateFilePath(
+      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMMAnchoredCPDSeqFreq)[i],
+      timepoint = names(fivePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "five_prime",
+      anchored = TRUE, sequence = "TGG", filtering = filtering, includedMismatches = mismatchType
+    ))
+  }
+}
+```
+
+```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 9}
+plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq$rep1,
+                        title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                        "3' Anchored YR Freq Rep1"), collapse = ' '),
+                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
+plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq$rep2,
+                        title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                        "3' Anchored YR Freq Rep2"), collapse = ' '),
+                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
+
+plotSequenceFrequencies(fivePrimeMMAnchoredCPDSeqFreq$rep1,
+                        title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                        "5' Anchored TGG Freq Rep1"), collapse = ' '),
+                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
+                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
+plotSequenceFrequencies(fivePrimeMMAnchoredCPDSeqFreq$rep2,
+                        title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                        "5' Anchored TGG Freq Rep2"), collapse = ' '),
+                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
+                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
+```

### 2022-06-08 R/CS-BTandemDeaminationDataGeneration.rmd
Created CS-B tandem deamination notebooks

--- 2022-06-06 R/NHF1TandemDeaminationDataGeneration.rmd
@@
 ---
-title: "NHF1 Tandem Deamination Data Generation"
+title: "CS-B Tandem Deamination Data Generation"
 author: "Ben Morledge-Hampton"
@@
 
-cellType = "NHF1"
+cellType = "CS-B"
 CPDTimepoints = list(`1h` = NULL)
@@
       tandemDeaminationDataDirectory, dataTypeStrings$mismatchesByRead, ".bed",
-      cellType = cellType, lesion = "6-4-PP", timepoint = names(sixFourMismatchData[[i]])[j],
+      cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
       repitition = names(sixFourMismatchData)[i], filtering = filtering,
@@
       tandemDeaminationDataDirectory, dataTypeStrings$mismatchesByRead, ".bed",
-      cellType = cellType, lesion = "6-4-PP", timepoint = names(sixFourMismatchData[[i]])[j],
+      cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
       repitition = names(sixFourMismatchData)[i], expansionNum = expansionOffset, filtering = filtering,

### 2022-06-08 R/CS-BTandemDeaminationFigureGeneration.rmd
Created CS-B tandem deamination notebooks

--- 2022-06-08 R/NHF1TandemDeaminationFigureGeneration.rmd
@@
 ---
-title: "NHF1 Tandem Deamination Figure Generation"
+title: "CS-B Tandem Deamination Figure Generation"
 author: "Ben Morledge-Hampton"

### 2022-06-08 R/GM12878TandemDeaminationDataGeneration.rmd
Created GM12878 tandem deamination notebooks

---
title: "NHF1 Tandem Deamination Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
  mismatchType:
    label: "Mismatch Type"
    value: CC>TT
    input: select
    choices: [CC>TT, GG>AA]
---

```{r setup_chunk}
library(knitr)
library(stringr)

expansionOffset = 10
cellType = "GM12878"
cisplatinTimepoints = list(`90min` = NULL)
minReadLength = 22; maxReadLength = 30

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
  filtering = readline("Filtering identifier (Input nothing for no filtering):")
  if (filtering == '') filtering = character()
  mismatchType = readline("Tandem mismatch type:")
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
  filtering = params$filtering
  if (filtering == "NONE") filtering = character()
  mismatchType = params$mismatchType
}
if (is.na(bioinformaticsDirectory)) stop("No bioinformatics directory given.")

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
tandemDeaminationDataDirectory = file.path(deaminationDataDirectory,
                                           paste(str_replace(mismatchType, '>', "_to_"),
                                                 "tandem_deaminations", sep = '_'))
dir.create(tandemDeaminationDataDirectory, recursive = TRUE, showWarnings = FALSE)
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationParseAndFilter.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationSequenceAndPositionAnalysis.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationAnchoredExcisionSiteAnalysis.R"))
```

```{r read_mismatch_data}
# Get file paths for the mismatch by read data
cisplatinMismatchData = list(rep1 = cisplatinTimepoints,
                             rep2 = cisplatinTimepoints)
for (i in 1:length(cisplatinMismatchData)) {
  for (j in 1:length(cisplatinMismatchData[[i]])) {
    cisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "cisplatin", timepoint = names(cisplatinMismatchData[[i]])[j],
      repitition = names(cisplatinMismatchData)[i], filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}
```

```{r generate_and_write_simplified_and_filtered_mismatch_data}
# Perform general filtering on the data
cisplatinMismatchData = lapply(cisplatinMismatchData, function(x) lapply(
  x, function(y) filterResults(y, TRUE, 1, minReadLength, maxReadLength)
))

# Simplify the data
cisplatinMismatchData = lapply(cisplatinMismatchData, function(x) lapply(
  x, function(y) simplifyTable(y)
))

# Write the simplified mismatch data
for (i in 1:length(cisplatinMismatchData)) {
  for (j in 1:length(cisplatinMismatchData[[i]])) {
    fwrite(cisplatinMismatchData[[i]][[j]], sep = '\t', na = "NA",
           file = generateFilePath(
             tandemDeaminationDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
             cellType = cellType, lesion = "cisplatin", timepoint = names(cisplatinMismatchData[[i]])[j],
             repitition = names(cisplatinMismatchData)[i], filtering = filtering,
             includedMismatches = mismatchType
           ))
  }
}
```

```{r generate_and_write_mismatch_frequency_z-scores}
cisplatinMMFreqZScores = lapply(cisplatinMismatchData, function(x) lapply(
  x, function(y) {
    getMismatchFrequencyZScoreByPosAndReadLength(y, 0)
  }
))

for (i in seq_along(cisplatinMMFreqZScores)) {
  for (j in seq_along(cisplatinMMFreqZScores[[i]])) {
    fwrite(cisplatinMMFreqZScores[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinMMFreqZScores)[i],
      timepoint = names(cisplatinMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c(mismatchType)
    ))
  }
}
```

```{r generate_and_write_mismatch_position_statistics_by_read_length_and_timepoint}
cisplatinGroupedStats = list(rep1 = list(), rep2 = list())
cisplatinGroupedStats$rep1$three_prime = getGroupedPositionStats(cisplatinMismatchData$rep1)
cisplatinGroupedStats$rep2$three_prime = getGroupedPositionStats(cisplatinMismatchData$rep2)
cisplatinGroupedStats$rep1$five_prime = getGroupedPositionStats(cisplatinMismatchData$rep1, posType = FIVE_PRIME)
cisplatinGroupedStats$rep2$five_prime = getGroupedPositionStats(cisplatinMismatchData$rep2, posType = FIVE_PRIME)

for (i in seq_along(cisplatinGroupedStats)) {
  for (j in seq_along(cisplatinGroupedStats[[i]])) {
    fwrite(cisplatinGroupedStats[[i]][[j]], sep = '\t',
           file = generateFilePath(
             tandemDeaminationDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
             cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinGroupedStats)[i],
             strandPolarity = names(cisplatinGroupedStats[[i]])[j], filtering = filtering,
             includedMismatches = mismatchType
           ))
  }
}
```

EXCISION SITE ANALYSIS STARTS HERE

```{r read_expanded_mismatch_data}
# Get file paths for the expanded mismatch by read data
cisplatinMismatchData = list(rep1 = cisplatinTimepoints,
                             rep2 = cisplatinTimepoints)
for (i in 1:length(cisplatinMismatchData)) {
  for (j in 1:length(cisplatinMismatchData[[i]])) {
    cisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "cisplatin", timepoint = names(cisplatinMismatchData[[i]])[j],
      repitition = names(cisplatinMismatchData)[i], expansionNum = expansionOffset, filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}
```

```{r generate_simplified_and_filtered_mismatch_data}
# Filter the reads by length and mismatch type (single C>T).
cisplatinMismatchData = lapply(cisplatinMismatchData, function(x) lapply(
  x, function(y) filterResults(y, minReadLength = minReadLength, maxReadLength = maxReadLength)
))

# Simplify the data
cisplatinMismatchData = lapply(cisplatinMismatchData, function(x) lapply(
  x, function(y) simplifyTable(y, TRUE, expansionOffset = expansionOffset)
))

# Read mismatch frequency z-scores.
cisplatinMMFreqZScores = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints)
for (i in seq_along(cisplatinMMFreqZScores)) {
  for (j in seq_along(cisplatinMMFreqZScores[[i]])) {
    cisplatinMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinMMFreqZScores)[i],
      timepoint = names(cisplatinMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

# Further filter data by read position based on length
cisplatinMismatchData = mapply(function(cisplatinMismatchDataRep, cisplatinMMFreqZScoreRep) mapply(
  filterMismatchesByPositionAndReadLength, cisplatinMismatchDataRep, cisplatinMMFreqZScoreRep,
  expansionOffset = expansionOffset, SIMPLIFY = FALSE
), cisplatinMismatchData, cisplatinMMFreqZScores, SIMPLIFY = FALSE)
```

```{r orient_data_to_mismatch_positions}
# NOTE: The assignments to null are there so that the garbage collector can free up memory, and
#       I can still switch to new variable names for organizational purposes.
threePrimeMismatchAnchoredCisplatinData = lapply(cisplatinMismatchData, function(x) {
  lapply(x, orientDataToMismatch, THREE_PRIME, expansionOffset, TRUE)
})
fivePrimeMismatchAnchoredCisplatinData = lapply(cisplatinMismatchData, function(x) {
  lapply(x, orientDataToMismatch, FIVE_PRIME, expansionOffset, TRUE)
})
cisplatinMismatchData = NULL
```

```{r generate_and_write_nucleotide_frequency_data}
threePrimeMismatchCisplatinNucFreq = lapply(threePrimeMismatchAnchoredCisplatinData,
                                            tabulateNucFreqByPosTimepointAndLength)
for (i in seq_along(threePrimeMismatchCisplatinNucFreq)) {
  fwrite(threePrimeMismatchCisplatinNucFreq[[i]], sep = '\t', file = generateFilePath(
    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMismatchCisplatinNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}

fivePrimeMismatchCisplatinNucFreq = lapply(fivePrimeMismatchAnchoredCisplatinData,
                                           tabulateNucFreqByPosTimepointAndLength, posType = FIVE_PRIME)
for (i in seq_along(fivePrimeMismatchCisplatinNucFreq)) {
  fwrite(fivePrimeMismatchCisplatinNucFreq[[i]], sep = '\t', file = generateFilePath(
    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMismatchCisplatinNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}
```

```{r generate_and_write_sequence_frequencies}
threePrimeMMAnchoredCisplatinSeqFreq = lapply(
  threePrimeMismatchAnchoredCisplatinData,function(mismatchDataRep) {
    lapply(mismatchDataRep, function(mismatchData) {
      getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("CG","CA","TG","TA"))
    })
  }
)
for (i in seq_along(threePrimeMMAnchoredCisplatinSeqFreq)) {
  for (j in seq_along(threePrimeMMAnchoredCisplatinSeqFreq[[i]])) {
    fwrite(threePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMMAnchoredCisplatinSeqFreq)[i],
      timepoint = names(threePrimeMMAnchoredCisplatinSeqFreq[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

fivePrimeMMAnchoredCisplatinSeqFreq = lapply(
  fivePrimeMismatchAnchoredCisplatinData, function(mismatchDataRep) {
    lapply(mismatchDataRep, function(mismatchData) {
      getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("TGG"), posType = FIVE_PRIME)
    })
  }
)
for (i in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq)) {
  for (j in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq[[i]])) {
    fwrite(fivePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMMAnchoredCisplatinSeqFreq)[i],
      timepoint = names(fivePrimeMMAnchoredCisplatinSeqFreq[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

### 2022-06-08 R/GM12878TandemDeaminationFigureGeneration.rmd
Created GM12878 tandem deamination notebooks

---
title: "NHF1 Tandem Deamination Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
  mismatchType:
    label: "Mismatch Type"
    value: CC>TT
    input: select
    choices: [CC>TT, GG>AA]
---

```{r setup_chunk}
library(knitr)
library(stringr)

expansionOffset = 10
cellType = "GM12878"
cisplatinTimepoints = list(`90min` = NULL)
minReadLength = 22; maxReadLength = 30

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
  filtering = readline("Filtering identifier (Input nothing for no filtering):")
  if (filtering == '') filtering = character()
  mismatchType = readline("Tandem mismatch type:")
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
  filtering = params$filtering
  if (filtering == "NONE") filtering = character()
  mismatchType = params$mismatchType
}
if (length(filtering) > 0) {
  titleCaseFiltering = tools::toTitleCase(gsub('_', ' ', filtering))
} else titleCaseFiltering = character()
titleCaseMismatchType = tools::toTitleCase(gsub('>', " To ", mismatchType))

opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
               fig.path = paste0(file.path("deamination_analysis_output",cellType,
                                           paste(c(filtering,
                                                   gsub('>', "_to_", mismatchType),
                                                   "tandem_deamination_figures"), collapse = '_')),
                                 .Platform$file.sep))

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
tandemDeaminationDataDirectory = file.path(deaminationDataDirectory,
                                           paste(str_replace(mismatchType, '>', "_to_"),
                                                 "tandem_deaminations", sep = '_'))
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationSequenceAndPositionAnalysis.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationAnchoredExcisionSiteAnalysis.R"))
```

```{r read_simplified_mismatch_data}
# Get file paths for the mismatch by read data
cisplatinMismatchData = list(rep1 = cisplatinTimepoints,
                             rep2 = cisplatinTimepoints)
for (i in seq_along(cisplatinMismatchData)) {
  for (j in seq_along(cisplatinMismatchData[[i]])) {
    cisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
      cellType = cellType, lesion = "cisplatin", timepoint = names(cisplatinMismatchData[[i]])[j],
      repitition = names(cisplatinMismatchData)[i], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

```{r cisplatin_mismatch_pos_frequency}
for (i in 1:length(cisplatinMismatchData)) {
  for (j in 1:length(cisplatinMismatchData[[i]])) {
    plotMismatchPositionFrequencies(cisplatinMismatchData[[i]][[j]],
                                    title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
                                                    names(cisplatinMismatchData)[i], 
                                                    names(cisplatinMismatchData[[i]])[j], "Mismatch Pos"),
                                                  collapse = ' '))
  }
}
```

```{r read_mismatch_frequency_z-score_tables}
cisplatinMMFreqZScores = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints)
for (i in seq_along(cisplatinMMFreqZScores)) {
  for (j in seq_along(cisplatinMMFreqZScores[[i]])) {
    cisplatinMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinMMFreqZScores)[i],
      timepoint = names(cisplatinMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

```{r cisplatin_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
plotPositionAcrossTimepointAndReadLength(cisplatinMismatchData$rep1,
                                         title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
                                                         "Mismatch Pos Freq Rep1"),
                                                       collapse = ' '),
                                         zScoreTables = cisplatinMMFreqZScores$rep1)
plotPositionAcrossTimepointAndReadLength(cisplatinMismatchData$rep2,
                                         title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
                                                         "Mismatch Pos Freq Rep2"),
                                                       collapse = ' '),
                                         zScoreTables = cisplatinMMFreqZScores$rep2)
plotPositionAcrossTimepointAndReadLength(cisplatinMismatchData$rep1, posType = FIVE_PRIME,
                                         title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
                                                         "Mismatch Pos Freq Rep1"),
                                                       collapse = ' '),
                                         zScoreTables = cisplatinMMFreqZScores$rep1)
plotPositionAcrossTimepointAndReadLength(cisplatinMismatchData$rep2, posType = FIVE_PRIME,
                                         title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
                                                         "Mismatch Pos Freq Rep2"),
                                                       collapse = ' '),
                                         zScoreTables = cisplatinMMFreqZScores$rep2)
```

```{r cisplatin_read_length_distributions}
plotReadLengthFrequencies(cisplatinMismatchData$rep1,
                          title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
                                          "Read Length Freq Rep1"), collapse = ' '))
plotReadLengthFrequencies(cisplatinMismatchData$rep2,
                          title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
                                          "Read Length Freq Rep2"), collapse = ' '))
```

```{r read_mismatch_position_statistics}
cisplatinGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
                             rep2 = list(three_prime = NULL, five_prime = NULL))
for (i in seq_along(cisplatinGroupedStats)) {
  for (j in seq_along(cisplatinGroupedStats[[i]])) {
    cisplatinGroupedStats[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinGroupedStats)[i],
      strandPolarity = names(cisplatinGroupedStats[[i]])[j], filtering = filtering,
      includedMismatches = mismatchType
    ))
  }
}
```

```{r cisplatin_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
plotGroupedPositionStats(cisplatinGroupedStats$rep1$three_prime, cisplatinGroupedStats$rep1$five_prime, POS_DIFF,
                         title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
                                         "Mismatch Pos Diff Rep1"), collapse = ' '),
                         xAxisBreaks = c(minReadLength:maxReadLength))
plotGroupedPositionStats(cisplatinGroupedStats$rep2$three_prime, cisplatinGroupedStats$rep2$five_prime, POS_DIFF,
                         title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
                                         "Mismatch Pos Diff Rep2"), collapse = ' '),
                         xAxisBreaks = c(minReadLength:maxReadLength))
```

EXCISION SITE FIGURE GENERATION STARTS HERE

```{r read_nucleotide_frequency_data}
threePrimeMismatchCisplatinNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(threePrimeMismatchCisplatinNucFreq)) {
  threePrimeMismatchCisplatinNucFreq[[i]] = fread(generateFilePath(
    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMismatchCisplatinNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}

fivePrimeMismatchCisplatinNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(fivePrimeMismatchCisplatinNucFreq)) {
  fivePrimeMismatchCisplatinNucFreq[[i]] = fread(generateFilePath(
    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMismatchCisplatinNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}
```

```{r cisplatin_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq$rep1, 
                               title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
                                               "3' Anchored Nuc Freq Rep1"), collapse = ' '),
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq$rep2, 
                               title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
                                               "3' Anchored Nuc Freq Rep2"), collapse = ' '),
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq$rep1, 
                               title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
                                               "5' Anchored Nuc Freq Rep1"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq$rep2, 
                               title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
                                               "5' Anchored Nuc Freq Rep2"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
```

```{r cisplatin_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq$rep1, 
                               title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
                                               "3' Anchored Purine Freq Rep1"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq$rep2, 
                               title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
                                               "3' Anchored Purine Freq Rep2"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq$rep1, 
                               title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
                                               "5' Anchored Purine Freq Rep1"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq$rep2, 
                               title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
                                               "5' Anchored Purine Freq Rep2"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
```

```{r read_sequence_frequency_data}
threePrimeMMAnchoredCisplatinSeqFreq = list(rep1 = cisplatinTimepoints,
                                            rep2 = cisplatinTimepoints)
for (i in seq_along(threePrimeMMAnchoredCisplatinSeqFreq)) {
  for (j in seq_along(threePrimeMMAnchoredCisplatinSeqFreq[[i]])) {
    threePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMMAnchoredCisplatinSeqFreq)[i],
      timepoint = names(threePrimeMMAnchoredCisplatinSeqFreq[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

fivePrimeMMAnchoredCisplatinSeqFreq = list(rep1 = cisplatinTimepoints,
                                           rep2 = cisplatinTimepoints)
for (i in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq)) {
  for (j in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq[[i]])) {
    fivePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMMAnchoredCisplatinSeqFreq)[i],
      timepoint = names(fivePrimeMMAnchoredCisplatinSeqFreq[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

```{r cisplatin_sequence_frequencies, fig.width = 11, fig.height = 9}
plotSequenceFrequencies(threePrimeMMAnchoredCisplatinSeqFreq$rep1,
                        title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
                                        "3' Anchored YR Freq Rep1"), collapse = ' '),
                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
plotSequenceFrequencies(threePrimeMMAnchoredCisplatinSeqFreq$rep2,
                        title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
                                        "3' Anchored YR Freq Rep2"), collapse = ' '),
                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))

plotSequenceFrequencies(fivePrimeMMAnchoredCisplatinSeqFreq$rep1,
                        title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
                                        "5' Anchored TGG Freq Rep1"), collapse = ' '),
                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
plotSequenceFrequencies(fivePrimeMMAnchoredCisplatinSeqFreq$rep2,
                        title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
                                        "5' Anchored TGG Freq Rep2"), collapse = ' '),
                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
```

### 2022-06-08 R/XP-CTandemDeaminationDataGeneration.rmd
Created XP-C tandem deamination notebooks

--- 2022-06-08 R/CS-BTandemDeaminationDataGeneration.rmd
@@
 ---
-title: "CS-B Tandem Deamination Data Generation"
+title: "XP-C Tandem Deamination Data Generation"
 author: "Ben Morledge-Hampton"

### 2022-06-08 R/XP-CTandemDeaminationFigureGeneration.rmd
Created XP-C tandem deamination notebooks

--- 2022-06-08 R/CS-BTandemDeaminationFigureGeneration.rmd
@@
 ---
-title: "CS-B Tandem Deamination Figure Generation"
+title: "XP-C Tandem Deamination Figure Generation"
 author: "Ben Morledge-Hampton"

### 2022-06-08 R/YeastTandemDeaminationDataGeneration.rmd
Created yeast tandem deamination notebooks

--- 2022-06-08 R/XP-CTandemDeaminationDataGeneration.rmd
@@
 ---
-title: "XP-C Tandem Deamination Data Generation"
+title: "Yeast Tandem Deamination Data Generation"
 author: "Ben Morledge-Hampton"
@@
 
-cellType = "XP-C"
-CPDTimepoints = list(`1h` = NULL)
-sixFourTimepoints = list(`1h` = NULL)
 expansionOffset = 10
-minReadLength = 22; maxReadLength = 30
+cellType = "yeast"
+CPDTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
+sixFourTimepoints = list(`5min` = NULL, `20min` = NULL)
+minReadLength = 22; maxReadLength = 25
 

### 2022-06-08 R/YeastTandemDeaminationFigureGeneration.rmd
Created yeast tandem deamination notebooks

--- 2022-06-08 R/XP-CTandemDeaminationFigureGeneration.rmd
@@
 ---
-title: "XP-C Tandem Deamination Figure Generation"
+title: "Yeast Tandem Deamination Figure Generation"
 author: "Ben Morledge-Hampton"

### 2022-06-13 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
Changes to axis bounds

@@
                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+```
+
+```{r CPD_mismatch_anchored_nucleotide_frequencies_filtered, fig.width = 11, fig.height = 8}
+min3PrimeCutSiteDistance = 1
+max3PrimeCutSiteDistance = 12
+
+plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
+                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Nuc Freq Rep1"), collapse = ' '),
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset,
+                               minReadLength = min3PrimeCutSiteDistance, maxReadLength = max3PrimeCutSiteDistance)
+plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
+                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Nuc Freq Rep2"), collapse = ' '),
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset,
+                               minReadLength = min3PrimeCutSiteDistance, maxReadLength = max3PrimeCutSiteDistance)
 ```

### 2022-06-13 R/NHF1GeneralReadSequenceFigureGeneration.rmd
Changes to axis bounds

@@
 
+```{r CPD_sequence_frequencies_filtered, fig.width = 11, fig.height = 9}
+minReadLength = 18
+plotSequenceFrequencies(CPDTGGSeqFreq$rep1,
+                        title = "CPD TGG Frequencies Rep1", expansionOffset = expansionOffset,
+                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
+                        querySequences = c("TGG"), minReadLength = minReadLength)
+plotSequenceFrequencies(CPDTGGSeqFreq$rep2,
+                        title = "CPD TGG Frequencies Rep2", expansionOffset = expansionOffset,
+                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
+                        querySequences = c("TGG"), minReadLength = minReadLength)
+
+plotSequenceFrequencies(CPDCGASeqFreq$rep1,
+                        title = "CPD CGA Frequencies Rep1", expansionOffset = expansionOffset,
+                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
+                        querySequences = c("CGA"), minReadLength = minReadLength)
+plotSequenceFrequencies(CPDCGASeqFreq$rep2,
+                        title = "CPD CGA Frequencies Rep2", expansionOffset = expansionOffset,
+                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
+                        querySequences = c("CGA"), minReadLength = minReadLength)
+```
+
 ```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 10}

### 2022-06-13 R/ArabidopsisTandemDeaminationDataGeneration.rmd
Refactored tandem deamination directory names
Refactored tandem deamination directory names to accompany directory changes which put tandem deamination data back into the same directories as other mismatch data.

@@
 deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
-tandemDeaminationDataDirectory = file.path(deaminationDataDirectory,
-                                           paste(str_replace(mismatchType, '>', "_to_"),
-                                                 "tandem_deaminations", sep = '_'))
-dir.create(tandemDeaminationDataDirectory, recursive = TRUE, showWarnings = FALSE)
+mismatchesByReadDirectory = file.path(deaminationDataDirectory, "mismatches_by_read")
+deaminationSequenceAndPositionDataDirectory = file.path(deaminationDataDirectory,"sequence_and_position_analysis")
+deaminationExcisionSiteDataDirectory = file.path(deaminationDataDirectory, "excision_site_analysis")
+dir.create(deaminationSequenceAndPositionDataDirectory, showWarnings = FALSE, recursive = TRUE)
+dir.create(deaminationExcisionSiteDataDirectory, showWarnings = FALSE, recursive = TRUE)
 ```
@@
     CPDMismatchData[[i]][[j]] = fread(generateFilePath(
-      tandemDeaminationDataDirectory, dataTypeStrings$mismatchesByRead, ".bed",
+      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
       cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
@@
            file = generateFilePath(
-             tandemDeaminationDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
              cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
@@
     fwrite(CPDMMFreqZScores[[i]][[j]], sep = '\t', file = generateFilePath(
-      directory = tandemDeaminationDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
       cellType = cellType, lesion = "CPD", repitition = names(CPDMMFreqZScores)[i],
@@
            file = generateFilePath(
-             tandemDeaminationDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
+             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
              cellType = cellType, lesion = "CPD", repitition = names(CPDGroupedStats)[i],
@@
     CPDMMFreqZScores[[i]][[j]] = fread(generateFilePath(
-      directory = tandemDeaminationDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
       cellType = cellType, lesion = "CPD", repitition = names(CPDMMFreqZScores)[i],
@@
   fwrite(threePrimeMismatchCPDNucFreq[[i]], sep = '\t', file = generateFilePath(
-    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
     cellType = cellType, lesion = "CPD", repitition = names(threePrimeMismatchCPDNucFreq)[i],
@@
   fwrite(fivePrimeMismatchCPDNucFreq[[i]], sep = '\t', file = generateFilePath(
-    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
     cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMismatchCPDNucFreq)[i],
@@
     fwrite(threePrimeMMAnchoredCPDSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
-      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
       cellType = cellType, lesion = "CPD", repitition = names(threePrimeMMAnchoredCPDSeqFreq)[i],
@@
     fwrite(fivePrimeMMAnchoredCPDSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
-      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
       cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMMAnchoredCPDSeqFreq)[i],

### 2022-06-13 R/ArabidopsisTandemDeaminationFigureGeneration.rmd
Refactored tandem deamination directory names
Refactored tandem deamination directory names to accompany directory changes which put tandem deamination data back into the same directories as other mismatch data.

@@
 deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
-tandemDeaminationDataDirectory = file.path(deaminationDataDirectory,
-                                           paste(str_replace(mismatchType, '>', "_to_"),
-                                                 "tandem_deaminations", sep = '_'))
+deaminationSequenceAndPositionDataDirectory = file.path(deaminationDataDirectory,"sequence_and_position_analysis")
+deaminationExcisionSiteDataDirectory = file.path(deaminationDataDirectory, "excision_site_analysis")
 ```
@@
     CPDMismatchData[[i]][[j]] = fread(generateFilePath(
-      tandemDeaminationDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
       cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
@@
     CPDGroupedStats[[i]][[j]] = fread(generateFilePath(
-      tandemDeaminationDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
+      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
       cellType = cellType, lesion = "CPD", repitition = names(CPDGroupedStats)[i],
@@
   threePrimeMismatchCPDNucFreq[[i]] = fread(generateFilePath(
-    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
     cellType = cellType, lesion = "CPD", repitition = names(threePrimeMismatchCPDNucFreq)[i],
@@
   fivePrimeMismatchCPDNucFreq[[i]] = fread(generateFilePath(
-    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
     cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMismatchCPDNucFreq)[i],
@@
     threePrimeMMAnchoredCPDSeqFreq[[i]][[j]] = fread(generateFilePath(
-      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
       cellType = cellType, lesion = "CPD", repitition = names(threePrimeMMAnchoredCPDSeqFreq)[i],
@@
     fivePrimeMMAnchoredCPDSeqFreq[[i]][[j]] = fread(generateFilePath(
-      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
       cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMMAnchoredCPDSeqFreq)[i],

### 2022-06-13 R/CS-BTandemDeaminationDataGeneration.rmd
Refactored tandem deamination directory names
Refactored tandem deamination directory names to accompany directory changes which put tandem deamination data back into the same directories as other mismatch data.

@@
     sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
-      tandemDeaminationDataDirectory, dataTypeStrings$mismatchesByRead, ".bed",
+      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
       cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
@@
            file = generateFilePath(
-             tandemDeaminationDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
              cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
@@
     fwrite(sixFourMMFreqZScores[[i]][[j]], sep = '\t', file = generateFilePath(
-      directory = tandemDeaminationDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
       cellType = cellType, lesion = "6-4", repitition = names(sixFourMMFreqZScores)[i],
@@
            file = generateFilePath(
-             tandemDeaminationDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
+             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
              cellType = cellType, lesion = "6-4", repitition = names(sixFourGroupedStats)[i],
@@
     sixFourMMFreqZScores[[i]][[j]] = fread(generateFilePath(
-      directory = tandemDeaminationDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
       cellType = cellType, lesion = "6-4", repitition = names(sixFourMMFreqZScores)[i],
@@
   fwrite(threePrimeMismatchSixFourNucFreq[[i]], sep = '\t', file = generateFilePath(
-    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
     cellType = cellType, lesion = "6-4", repitition = names(threePrimeMismatchSixFourNucFreq)[i],
@@
   fwrite(fivePrimeMismatchSixFourNucFreq[[i]], sep = '\t', file = generateFilePath(
-    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
     cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMismatchSixFourNucFreq)[i],
@@
     fwrite(threePrimeMMAnchoredSixFourSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
-      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
       cellType = cellType, lesion = "6-4", repitition = names(threePrimeMMAnchoredSixFourSeqFreq)[i],
@@
     fwrite(fivePrimeMMAnchoredSixFourSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
-      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
       cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMMAnchoredSixFourSeqFreq)[i],

### 2022-06-13 R/CS-BTandemDeaminationFigureGeneration.rmd
Refactored tandem deamination directory names
Refactored tandem deamination directory names to accompany directory changes which put tandem deamination data back into the same directories as other mismatch data.

@@
     sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
-      tandemDeaminationDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
       cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
@@
     sixFourGroupedStats[[i]][[j]] = fread(generateFilePath(
-      tandemDeaminationDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
+      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
       cellType = cellType, lesion = "6-4", repitition = names(sixFourGroupedStats)[i],
@@
   threePrimeMismatchSixFourNucFreq[[i]] = fread(generateFilePath(
-    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
     cellType = cellType, lesion = "6-4", repitition = names(threePrimeMismatchSixFourNucFreq)[i],
@@
   fivePrimeMismatchSixFourNucFreq[[i]] = fread(generateFilePath(
-    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
     cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMismatchSixFourNucFreq)[i],
@@
     threePrimeMMAnchoredSixFourSeqFreq[[i]][[j]] = fread(generateFilePath(
-      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
       cellType = cellType, lesion = "6-4", repitition = names(threePrimeMMAnchoredSixFourSeqFreq)[i],
@@
     fivePrimeMMAnchoredSixFourSeqFreq[[i]][[j]] = fread(generateFilePath(
-      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
       cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMMAnchoredSixFourSeqFreq)[i],

### 2022-06-13 R/GM12878TandemDeaminationDataGeneration.rmd
Refactored tandem deamination directory names
Refactored tandem deamination directory names to accompany directory changes which put tandem deamination data back into the same directories as other mismatch data.

@@
     cisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
-      tandemDeaminationDataDirectory, dataTypeStrings$mismatchesByRead, ".bed",
+      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
       cellType = cellType, lesion = "cisplatin", timepoint = names(cisplatinMismatchData[[i]])[j],
@@
            file = generateFilePath(
-             tandemDeaminationDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
              cellType = cellType, lesion = "cisplatin", timepoint = names(cisplatinMismatchData[[i]])[j],
@@
     fwrite(cisplatinMMFreqZScores[[i]][[j]], sep = '\t', file = generateFilePath(
-      directory = tandemDeaminationDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
       cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinMMFreqZScores)[i],
@@
            file = generateFilePath(
-             tandemDeaminationDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
+             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
              cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinGroupedStats)[i],
@@
     cisplatinMMFreqZScores[[i]][[j]] = fread(generateFilePath(
-      directory = tandemDeaminationDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
       cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinMMFreqZScores)[i],
@@
   fwrite(threePrimeMismatchCisplatinNucFreq[[i]], sep = '\t', file = generateFilePath(
-    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
     cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMismatchCisplatinNucFreq)[i],
@@
   fwrite(fivePrimeMismatchCisplatinNucFreq[[i]], sep = '\t', file = generateFilePath(
-    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
     cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMismatchCisplatinNucFreq)[i],
@@
     fwrite(threePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
-      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
       cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMMAnchoredCisplatinSeqFreq)[i],
@@
     fwrite(fivePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
-      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
       cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMMAnchoredCisplatinSeqFreq)[i],

### 2022-06-13 R/GM12878TandemDeaminationFigureGeneration.rmd
Refactored tandem deamination directory names
Refactored tandem deamination directory names to accompany directory changes which put tandem deamination data back into the same directories as other mismatch data.

@@
     cisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
-      tandemDeaminationDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
       cellType = cellType, lesion = "cisplatin", timepoint = names(cisplatinMismatchData[[i]])[j],
@@
     cisplatinGroupedStats[[i]][[j]] = fread(generateFilePath(
-      tandemDeaminationDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
+      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
       cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinGroupedStats)[i],
@@
   threePrimeMismatchCisplatinNucFreq[[i]] = fread(generateFilePath(
-    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
     cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMismatchCisplatinNucFreq)[i],
@@
   fivePrimeMismatchCisplatinNucFreq[[i]] = fread(generateFilePath(
-    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
     cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMismatchCisplatinNucFreq)[i],
@@
     threePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]] = fread(generateFilePath(
-      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
       cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMMAnchoredCisplatinSeqFreq)[i],
@@
     fivePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]] = fread(generateFilePath(
-      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
       cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMMAnchoredCisplatinSeqFreq)[i],

### 2022-06-13 R/NHF1TandemDeaminationDataGeneration.rmd
Refactored tandem deamination directory names
Refactored tandem deamination directory names to accompany directory changes which put tandem deamination data back into the same directories as other mismatch data.

@@
     sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
-      tandemDeaminationDataDirectory, dataTypeStrings$mismatchesByRead, ".bed",
-      cellType = cellType, lesion = "6-4-PP", timepoint = names(sixFourMismatchData[[i]])[j],
+      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
+      cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
       repitition = names(sixFourMismatchData)[i], filtering = filtering,
@@
     sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
-      tandemDeaminationDataDirectory, dataTypeStrings$mismatchesByRead, ".bed",
-      cellType = cellType, lesion = "6-4-PP", timepoint = names(sixFourMismatchData[[i]])[j],
+      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
+      cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
       repitition = names(sixFourMismatchData)[i], expansionNum = expansionOffset, filtering = filtering,

### 2022-06-14 R/ArabidopsisDeaminationAnchoredExcisionSiteDataGeneration.rmd
Update Arabidopsis Notebooks
- Support for all_reps
- Read length counting occurs during data generation

@@
 # Get file paths for the expanded mismatch by read data
-CPDMismatchData = list(rep1 = CPDTimepoints,
-                       rep2 = CPDTimepoints)
+CPDMismatchData = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
 for (i in 1:length(CPDMismatchData)) {
@@
 # Read mismatch frequency z-scores.
-CPDMMFreqZScores = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
+CPDMMFreqZScores = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
 for (i in seq_along(CPDMMFreqZScores)) {

### 2022-06-14 R/ArabidopsisDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Update Arabidopsis Notebooks
- Support for all_reps
- Read length counting occurs during data generation

@@
 CPDTimepoints = list(`ZT2` = NULL, `ZT14` = NULL)
+repNames = c("rep1", "rep2", "all_reps")
 minReadLength = 24; maxReadLength = 30
@@
 ```{r read_nucleotide_frequency_data}
-threePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL)
+threePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL, all_reps = NULL)
 for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
@@
 
-fivePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL)
+fivePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL, all_reps = NULL)
 for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
@@
 ```{r CPD_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
-                               title = paste(c("CPD", titleCaseFiltering, "3' Anchored Nuc Freq Rep1"), collapse = ' '),
+for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq[[i]], 
+                                 title = paste(c("CPD", titleCaseFiltering, "3' Anchored Nuc Freq", repNames[i]), collapse = ' '),
                                  secondaryYAxisLabel = "5' Cut Site Distance",
                                  posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep2, 
-                               title = paste(c("CPD", titleCaseFiltering, "3' Anchored Nuc Freq Rep2"), collapse = ' '),
-                               secondaryYAxisLabel = "5' Cut Site Distance",
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
 
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
-                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Nuc Freq Rep1"), collapse = ' '),
+for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]], 
+                                 title = paste(c("CPD", titleCaseFiltering, "5' Anchored Nuc Freq", repNames[i]), collapse = ' '),
                                  yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                                  posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
-                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Nuc Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
 ```
@@
 ```{r CPD_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
-                               title = paste(c("CPD", titleCaseFiltering, "3' Anchored Purine Freq Rep1"), collapse = ' '),
+for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq[[i]], 
+                                 title = paste(c("CPD", titleCaseFiltering, "3' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                  yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
@@
                                  posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep2, 
-                               title = paste(c("CPD", titleCaseFiltering, "3' Anchored Purine Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
 
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
-                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Purine Freq Rep1"), collapse = ' '),
+for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]], 
+                                 title = paste(c("CPD", titleCaseFiltering, "5' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                  yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
@@
                                  posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
-                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Purine Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
 ```
@@
 ```{r read_sequence_enrichment_data}
-threePrimeMMAnchoredCPDEnrichment = list(rep1 = CPDTimepoints,
-                                         rep2 = CPDTimepoints)
+threePrimeMMAnchoredCPDEnrichment = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
 for (i in seq_along(threePrimeMMAnchoredCPDEnrichment)) {
@@
 
-fivePrimeMMAnchoredCPDEnrichment = list(rep1 = CPDTimepoints,
-                                        rep2 = CPDTimepoints)
+fivePrimeMMAnchoredCPDEnrichment = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
 for (i in seq_along(fivePrimeMMAnchoredCPDEnrichment)) {
@@
 ```{r CPD_sequence_enrichment, fig.width = 11, fig.height = 9}
-plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment$rep1,
-                       title = paste(c("CPD", titleCaseFiltering, "3' Anchored YR Enrichment Rep1"), collapse = ' '),
+for (i in seq_along(threePrimeMMAnchoredCPDEnrichment)) {
+  plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment[[i]],
+                         title = paste(c("CPD", titleCaseFiltering, "3' Anchored YR Enrichment", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
-plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment$rep2,
-                       title = paste(c("CPD", titleCaseFiltering, "3' Anchored YR Enrichment Rep2"), collapse = ' '),
-                       secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
-                       expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
+}
 
-plotSequenceEnrichment(fivePrimeMMAnchoredCPDEnrichment$rep1,
-                       title = paste(c("CPD", titleCaseFiltering, "5' Anchored TGG Enrichment Rep1"), collapse = ' '),
+for (i in seq_along(fivePrimeMMAnchoredCPDEnrichment)) {
+  plotSequenceEnrichment(fivePrimeMMAnchoredCPDEnrichment[[i]],
+                         title = paste(c("CPD", titleCaseFiltering, "5' Anchored TGG Enrichment", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
-plotSequenceEnrichment(fivePrimeMMAnchoredCPDEnrichment$rep2,
-                       title = paste(c("CPD", titleCaseFiltering, "5' Anchored TGG Enrichment Rep2"), collapse = ' '),
-                       secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
-                       expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
+}
 ```
@@
 ```{r read_sequence_frequency_data}
-threePrimeMMAnchoredCPDSeqFreq = list(rep1 = CPDTimepoints,
-                                      rep2 = CPDTimepoints)
+threePrimeMMAnchoredCPDSeqFreq = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
 for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
@@
 
-fivePrimeMMAnchoredCPDSeqFreq = list(rep1 = CPDTimepoints,
-                                     rep2 = CPDTimepoints)
+fivePrimeMMAnchoredCPDSeqFreq = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
 for (i in seq_along(fivePrimeMMAnchoredCPDSeqFreq)) {
@@
 ```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 9}
-plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq$rep1,
-                        title = paste(c("CPD", titleCaseFiltering, "3' Anchored YR Freq Rep1"), collapse = ' '),
+for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]],
+                          title = paste(c("CPD", titleCaseFiltering, "3' Anchored YR Freq", repNames[i]), collapse = ' '),
                           secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                           expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
-plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq$rep2,
-                        title = paste(c("CPD", titleCaseFiltering, "3' Anchored YR Freq Rep2"), collapse = ' '),
-                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
-                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
+}
 
-plotSequenceFrequencies(fivePrimeMMAnchoredCPDSeqFreq$rep1,
-                        title = paste(c("CPD", titleCaseFiltering, "5' Anchored TGG Freq Rep1"), collapse = ' '),
+for (i in seq_along(fivePrimeMMAnchoredCPDSeqFreq)) {
+  plotSequenceFrequencies(fivePrimeMMAnchoredCPDSeqFreq[[i]],
+                          title = paste(c("CPD", titleCaseFiltering, "5' Anchored TGG Freq", repNames[i]), collapse = ' '),
                           secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                           expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
-plotSequenceFrequencies(fivePrimeMMAnchoredCPDSeqFreq$rep2,
-                        title = paste(c("CPD", titleCaseFiltering, "5' Anchored TGG Freq Rep2"), collapse = ' '),
-                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
-                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
+}
 ```

### 2022-06-14 R/ArabidopsisDeaminationSequenceAndPositionDataGeneration.rmd
Update Arabidopsis Notebooks
- Support for all_reps
- Read length counting occurs during data generation

@@
 # Get file paths for the mismatch by read data
-CPDMismatchData = list(rep1 = CPDTimepoints,
-                       rep2 = CPDTimepoints)
+CPDMismatchData = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
 for (i in 1:length(CPDMismatchData)) {
@@
 
+```{r generate_and_write_read_length_counts}
+CPDReadLengthCounts = lapply(CPDMismatchData, function(x) lapply(
+  x, function(y) {
+    y[, .N, by = Read_Length][order(Read_Length)]
+  }
+))
+
+for (i in seq_along(CPDReadLengthCounts)) {
+  for (j in seq_along(CPDReadLengthCounts[[i]])) {
+    fwrite(CPDReadLengthCounts[[i]][[j]], sep = '\t', file = generateFilePath(
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
+      cellType = cellType, lesion = "CPD", repitition = names(CPDReadLengthCounts)[i],
+      timepoint = names(CPDReadLengthCounts[[i]])[j], filtering = filtering
+    ))
+  }
+}
+```
+
 ```{r generate_and_write_mismatch_position_statistics_by_read_length_and_timepoint}
-CPDGroupedStats = list(rep1 = list(), rep2 = list())
-CPDGroupedStats$rep1$three_prime = getGroupedPositionStats(CPDMismatchData$rep1, includedTypes = c("C>T"))
-CPDGroupedStats$rep2$three_prime = getGroupedPositionStats(CPDMismatchData$rep2, includedTypes = c("C>T"))
-CPDGroupedStats$rep1$five_prime =
-  getGroupedPositionStats(CPDMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME)
-CPDGroupedStats$rep2$five_prime =
-  getGroupedPositionStats(CPDMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME)
+CPDGroupedStats = list(rep1 = list(), rep2 = list(), all_reps = list())
+for (i in seq_along(CPDGroupedStats)) {
+  CPDGroupedStats[[i]]$three_prime = getGroupedPositionStats(CPDMismatchData[[i]], includedTypes = c("C>T"))
+  CPDGroupedStats[[i]]$five_prime =
+    getGroupedPositionStats(CPDMismatchData[[i]], includedTypes = c("C>T"), posType = FIVE_PRIME)
+}
 

### 2022-06-14 R/ArabidopsisDeaminationSequenceAndPositionFigureGeneration.rmd
Update Arabidopsis Notebooks
- Support for all_reps
- Read length counting occurs during data generation

@@
 # Get file paths for the mismatch by read data
-CPDMismatchData = list(rep1 = CPDTimepoints,
-                       rep2 = CPDTimepoints)
+CPDMismatchData = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
 for (i in seq_along(CPDMismatchData)) {
@@
 ```{r read_mismatch_frequency_z-score_tables}
-CPDMMFreqZScores = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
+CPDMMFreqZScores = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
 for (i in seq_along(CPDMMFreqZScores)) {
@@
 ```{r CPD_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, includedTypes = c("C>T"),
-                                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
+for (i in seq_along(CPDMismatchData)) {
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]], includedTypes = c("C>T"),
+                                           title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Freq", repNames[i]),
                                                          collapse = ' '),
-                                         zScoreTables = CPDMMFreqZScores$rep1)
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, includedTypes = c("C>T"),
-                                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
+                                           zScoreTables = CPDMMFreqZScores[[i]])
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]], includedTypes = c("C>T"), posType = FIVE_PRIME,
+                                           title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Freq", repNames[i]),
                                                          collapse = ' '),
-                                         zScoreTables = CPDMMFreqZScores$rep2)
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME,
-                                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
-                                                       collapse = ' '),
-                                         zScoreTables = CPDMMFreqZScores$rep1)
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME,
-                                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
-                                                       collapse = ' '),
-                                         zScoreTables = CPDMMFreqZScores$rep2)
+                                           zScoreTables = CPDMMFreqZScores[[i]])
+}
+```
+
+```{r read_read_length_counts}
+CPDReadLengthCounts = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
+for (i in seq_along(CPDReadLengthCounts)) {
+  for (j in seq_along(CPDReadLengthCounts[[i]])) {
+    CPDReadLengthCounts[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
+      cellType = cellType, lesion = "CPD", repitition = names(CPDReadLengthCounts)[i],
+      timepoint = names(CPDReadLengthCounts[[i]])[j], filtering = filtering
+    ))
+  }
+}
 ```
@@
 ```{r CPD_read_length_distributions}
-plotReadLengthFrequencies(CPDMismatchData$rep1,
-                          title = paste(c("CPD", titleCaseFiltering, "Read Length Freq Rep 1"), collapse = ' '))
-plotReadLengthFrequencies(CPDMismatchData$rep2,
-                          title = paste(c("CPD", titleCaseFiltering, "Read Length Freq Rep 2"), collapse = ' '))
+for (i in seq_along(CPDReadLengthCounts)) {
+  plotReadLengthFrequencies(CPDReadLengthCounts[[i]],
+                            title = paste(c("CPD", titleCaseFiltering, "Read Length Freq", repNames[i]), collapse = ' '))
+}
 ```
@@
 CPDGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
-                       rep2 = list(three_prime = NULL, five_prime = NULL))
+                       rep2 = list(three_prime = NULL, five_prime = NULL),
+                       all_reps = list(three_prime = NULL, five_prime = NULL))
 for (i in seq_along(CPDGroupedStats)) {
@@
 ```{r CPD_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
-plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, POS_DIFF,
-                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Diff Rep1"), collapse = ' '),
+for (i in seq_along(CPDGroupedStats)) {
+  plotGroupedPositionStats(CPDGroupedStats[[i]]$three_prime, CPDGroupedStats[[i]]$five_prime, POS_DIFF,
+                           title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Diff", repNames[i]), collapse = ' '),
                            xAxisBreaks = c(minReadLength:maxReadLength))
-plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, POS_DIFF,
-                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Diff Rep2"), collapse = ' '),
-                         xAxisBreaks = c(minReadLength:maxReadLength))
+}
 ```

### 2022-06-14 R/ArabidopsisGeneralReadSequenceDataGeneration.rmd
Update Arabidopsis Notebooks
- Support for all_reps
- Read length counting occurs during data generation

@@
 
+  readLengthCounts = readData[, .N, by = Read_Length][order(Read_Length)]
+  fwrite(readLengthCounts, sep = '\t', file = generateFilePath(
+    directory = generalReadSequenceDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
+    cellType = cellType, lesion = lesion, repitition = repitition, timepoint = timepoint
+  ))
+
   for (sequence in c("TGG","CGA")) {
@@
 ```{r compute_and_write_CPD_sequence_frequency}
-for (repitition in c("rep1", "rep2")) {
+for (repitition in c("rep1", "rep2", "all_reps")) {
   for (timepoint in names(CPDTimepoints)) {

### 2022-06-14 R/ArabidopsisGeneralReadSequenceFigureGeneration.rmd
Update Arabidopsis Notebooks
- Support for all_reps
- Read length counting occurs during data generation

@@
 ```{r read_sequence_frequencies}
-CPDTGGSeqFreq = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
+CPDTGGSeqFreq = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
 for (i in seq_along(CPDTGGSeqFreq)) {
@@
 
-CPDCGASeqFreq = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
+CPDCGASeqFreq = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
 for (i in seq_along(CPDCGASeqFreq)) {
@@
 ```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 10}
-plotSequenceFrequencies(CPDTGGSeqFreq$rep1,
-                        title = "CPD TGG Frequencies Rep1", expansionOffset = expansionOffset,
-                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
-                        querySequences = c("TGG"))
-plotSequenceFrequencies(CPDTGGSeqFreq$rep2,
-                        title = "CPD TGG Frequencies Rep2", expansionOffset = expansionOffset,
-                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
-                        querySequences = c("TGG"))
+for (i in seq_along(CPDTGGSeqFreq)) {
+  plotSequenceFrequencies(CPDTGGSeqFreq[[i]],
+                          title = paste("CPD TGG Frequencies", repNames[i]),
+                          expansionOffset = expansionOffset, showThreePrimeCutSite = TRUE,
+                          showFivePrimeCutSite = TRUE, querySequences = c("TGG"))
+}
 
-plotSequenceFrequencies(CPDCGASeqFreq$rep1,
-                        title = "CPD CGA Frequencies Rep1", expansionOffset = expansionOffset,
+for (i in seq_along(CPDCGASeqFreq)) {
+  plotSequenceFrequencies(CPDCGASeqFreq[[i]],
+                          title = paste("CPD CGA Frequencies", repNames[i]), expansionOffset = expansionOffset,
                           showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                           querySequences = c("CGA"))
-plotSequenceFrequencies(CPDCGASeqFreq$rep2,
-                        title = "CPD CGA Frequencies Rep2", expansionOffset = expansionOffset,
-                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
-                        querySequences = c("CGA"))
+}
 ```
@@
 
-  readData = timepoints
-  for (i in seq_along(readData)) {
-    readData[[i]] = fread(generateFilePath(
-      generalReadSequenceDataDirectory, dataTypeStrings$alignedReads, ".bed",
-      cellType = cellType, lesion = lesion, timepoint = names(readData)[i],
-      repitition = repitition, expansionNum = expansionOffset
+  readLengthCountsByTimepoint = timepoints
+  for (i in seq_along(readLengthCountsByTimepoint)) {
+    readLengthCountsByTimepoint[[i]] = fread(generateFilePath(
+      generalReadSequenceDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
+      cellType = cellType, lesion = lesion, timepoint = names(readLengthCountsByTimepoint)[i],
+      repitition = repitition
     ))
-    readData[[i]] = data.table(Read_Length = nchar(readData[[i]]$V7)-expansionOffset*2,
-                               Timepoint = names(readData)[i])
-    readData[[i]] = readData[[i]][Read_Length >= minReadLength-7 & Read_Length <= maxReadLength]
   }
 
-  plotReadLengthFrequencies(readData,
-                            title = paste(c(lesion, "Read Length Freq",
-                                            tools::toTitleCase(repitition)),
-                                          collapse = ' '))
+  plotReadLengthFrequencies(readLengthCountsByTimepoint,
+                            title = paste(lesion, "Read Length Freq", repitition))
 
@@
 ```{r CPD_read_length_frequencies}
-readAndPlotReadLengthFrequencies("CPD", "rep1", CPDTimepoints)
-readAndPlotReadLengthFrequencies("CPD", "rep2", CPDTimepoints)
+for (rep in repNames) {
+  readAndPlotReadLengthFrequencies("CPD", rep, CPDTimepoints)
+}
 ```

### 2022-06-14 R/ArabidopsisTandemDeaminationDataGeneration.rmd
Update Arabidopsis Notebooks
- Support for all_reps
- Read length counting occurs during data generation

@@
 
+```{r generate_and_write_read_length_counts}
+CPDReadLengthCounts = lapply(CPDMismatchData, function(x) lapply(
+  x, function(y) {
+    y[, .N, by = Read_Length][order(Read_Length)]
+  }
+))
+
+for (i in seq_along(CPDReadLengthCounts)) {
+  for (j in seq_along(CPDReadLengthCounts[[i]])) {
+    fwrite(CPDReadLengthCounts[[i]][[j]], sep = '\t', file = generateFilePath(
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
+      cellType = cellType, lesion = "CPD", repitition = names(CPDReadLengthCounts)[i],
+      timepoint = names(CPDReadLengthCounts[[i]])[j], filtering = filtering, includedMismatches = mismatchType
+    ))
+  }
+}
+```
+
 ```{r generate_and_write_mismatch_position_statistics_by_read_length_and_timepoint}
-CPDGroupedStats = list(rep1 = list(), rep2 = list())
-CPDGroupedStats$rep1$three_prime = getGroupedPositionStats(CPDMismatchData$rep1)
-CPDGroupedStats$rep2$three_prime = getGroupedPositionStats(CPDMismatchData$rep2)
-CPDGroupedStats$rep1$five_prime = getGroupedPositionStats(CPDMismatchData$rep1, posType = FIVE_PRIME)
-CPDGroupedStats$rep2$five_prime = getGroupedPositionStats(CPDMismatchData$rep2, posType = FIVE_PRIME)
+CPDGroupedStats = list(rep1 = list(), rep2 = list(), all_reps = list())
+for (i in seq_along(CPDGroupedStats)) {
+  CPDGroupedStats[[i]]$three_prime = getGroupedPositionStats(CPDMismatchData[[i]])
+  CPDGroupedStats[[i]]$five_prime = getGroupedPositionStats(CPDMismatchData[[i]], posType = FIVE_PRIME)
+}
 

### 2022-06-14 R/ArabidopsisTandemDeaminationFigureGeneration.rmd
Update Arabidopsis Notebooks
- Support for all_reps
- Read length counting occurs during data generation

@@
 ```{r CPD_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1,
+for (i in seq_along(CPDMismatchData)) {
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]],
                                            title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                                         "Mismatch Pos Freq Rep1"),
+                                                           "Mismatch Pos Freq", repNames[i]),
                                                          collapse = ' '),
-                                         zScoreTables = CPDMMFreqZScores$rep1)
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2,
+                                           zScoreTables = CPDMMFreqZScores[[i]])
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]], posType = FIVE_PRIME,
                                            title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                                         "Mismatch Pos Freq Rep2"),
+                                                           "Mismatch Pos Freq", repNames[i]),
                                                          collapse = ' '),
-                                         zScoreTables = CPDMMFreqZScores$rep2)
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, posType = FIVE_PRIME,
-                                         title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                                         "Mismatch Pos Freq Rep1"),
-                                                       collapse = ' '),
-                                         zScoreTables = CPDMMFreqZScores$rep1)
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, posType = FIVE_PRIME,
-                                         title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                                         "Mismatch Pos Freq Rep2"),
-                                                       collapse = ' '),
-                                         zScoreTables = CPDMMFreqZScores$rep2)
+                                           zScoreTables = CPDMMFreqZScores[[i]])
+}
+```
+
+```{r read_read_length_counts}
+CPDReadLengthCounts = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
+for (i in seq_along(CPDReadLengthCounts)) {
+  for (j in seq_along(CPDReadLengthCounts[[i]])) {
+    CPDReadLengthCounts[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
+      cellType = cellType, lesion = "CPD", repitition = names(CPDReadLengthCounts)[i],
+      timepoint = names(CPDReadLengthCounts[[i]])[j], filtering = filtering, includedMismatches = mismatchType
+    ))
+  }
+}
 ```
@@
 ```{r CPD_read_length_distributions}
-plotReadLengthFrequencies(CPDMismatchData$rep1,
+for (i in seq_along(CPDReadLengthCounts)) {
+  plotReadLengthFrequencies(CPDReadLengthCounts[[i]],
                             title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                          "Read Length Freq Rep1"), collapse = ' '))
-plotReadLengthFrequencies(CPDMismatchData$rep2,
-                          title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                          "Read Length Freq Rep2"), collapse = ' '))
+                                            "Read Length Freq", repNames[i]), collapse = ' '))
+}
 ```
@@
 ```{r CPD_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
-plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, POS_DIFF,
+for (i in seq_along(CPDGroupedStats)) {
+  plotGroupedPositionStats(CPDGroupedStats[[i]]$three_prime, CPDGroupedStats[[i]]$five_prime, POS_DIFF,
                            title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                         "Mismatch Pos Diff Rep1"), collapse = ' '),
+                                           "Mismatch Pos Diff", repNames[i]), collapse = ' '),
                            xAxisBreaks = c(minReadLength:maxReadLength))
-plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, POS_DIFF,
-                         title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                         "Mismatch Pos Diff Rep2"), collapse = ' '),
-                         xAxisBreaks = c(minReadLength:maxReadLength))
+}
 ```
@@
 ```{r CPD_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
+for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq[[i]], 
                                  title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                               "3' Anchored Nuc Freq Rep1"), collapse = ' '),
+                                                 "3' Anchored Nuc Freq", repNames[i]), collapse = ' '),
                                  secondaryYAxisLabel = "5' Cut Site Distance",
                                  posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep2, 
+}
+
+for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]], 
                                  title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                               "3' Anchored Nuc Freq Rep2"), collapse = ' '),
-                               secondaryYAxisLabel = "5' Cut Site Distance",
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
-                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                               "5' Anchored Nuc Freq Rep1"), collapse = ' '),
+                                                 "5' Anchored Nuc Freq", repNames[i]), collapse = ' '),
                                  yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                                  posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
-                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                               "5' Anchored Nuc Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
 ```
@@
 ```{r CPD_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
+for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq[[i]], 
                                  title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                               "3' Anchored Purine Freq Rep1"), collapse = ' '),
+                                                 "3' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                  yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
@@
                                  posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep2, 
+}
+
+for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]], 
                                  title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                               "3' Anchored Purine Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
-                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                               "5' Anchored Purine Freq Rep1"), collapse = ' '),
+                                                 "5' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                  yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
@@
                                  posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
-                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                               "5' Anchored Purine Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
 ```
@@
 ```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 9}
-plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq$rep1,
+for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]],
                           title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                        "3' Anchored YR Freq Rep1"), collapse = ' '),
+                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
                           secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                           expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
-plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq$rep2,
+}
+
+for (i in seq_along(fivePrimeMMAnchoredCPDSeqFreq)) {
+  plotSequenceFrequencies(fivePrimeMMAnchoredCPDSeqFreq[[i]],
                           title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                        "3' Anchored YR Freq Rep2"), collapse = ' '),
-                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
-                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
-
-plotSequenceFrequencies(fivePrimeMMAnchoredCPDSeqFreq$rep1,
-                        title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                        "5' Anchored TGG Freq Rep1"), collapse = ' '),
+                                          "5' Anchored TGG Freq", repNames[i]), collapse = ' '),
                           secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                           expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
-plotSequenceFrequencies(fivePrimeMMAnchoredCPDSeqFreq$rep2,
-                        title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                        "5' Anchored TGG Freq Rep2"), collapse = ' '),
-                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
-                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
+}
 ```

### 2022-06-14 R/DeaminationSequenceAndPositionAnalysis.R
Update read length frequency plotting
Function now expects a table of read length counts not just read data.

@@ -177,19 +177,18 @@ plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTy
 # Plot read length frequencies across timepoint (optional).
 # Input should be a list of data.tables with names as timepoint information, or a single data.table
 # to construct a plot without timepoint information.
-plotReadLengthFrequencies = function(simplifiedTables, title = "Read Length Frequencies") {
+plotReadLengthFrequencies = function(readLengthCountTables, title = "Read Length Frequencies") {
 
   #If passed a single data.table, wrap it in a list.
-  if (is.data.table(simplifiedTables)) {
-    simplifiedTables = list(NONE = simplifiedTables)
+  if (is.data.table(readLengthCountTables)) {
+    readLengthCountTables = list(NONE = readLengthCountTables)
   }
-  noTimepointInfo = all(names(simplifiedTables) == "NONE")
+  noTimepointInfo = all(names(readLengthCountTables) == "NONE")
 
-  aggregateTable = rbindlist(lapply(seq_along(simplifiedTables),
-                                    function(i) simplifiedTables[[i]][,Timepoint := names(simplifiedTables)[i]]))
+  aggregateTable = rbindlist(lapply(seq_along(readLengthCountTables),
+                                    function(i) readLengthCountTables[[i]][,Timepoint := names(readLengthCountTables)[i]]))
 
-  readLengthFrequencies = (aggregateTable[, .N, by = list(Read_Length,Timepoint)]
-                                         [, Freq := N/sum(N), by = list(Timepoint)])
+  readLengthFrequencies = (aggregateTable[, Freq := N/sum(N), by = list(Timepoint)])
   maxFrequency = round(max(readLengthFrequencies$Freq), digits = 2)
   yAxisBreaks = c(0, maxFrequency/2, maxFrequency)
 
@@ -199,7 +198,7 @@ plotReadLengthFrequencies = function(simplifiedTables, title = "Read Length Freq
     blankBackground + defaultTextScaling
 
   if (!noTimepointInfo) {
-    plot = plot + facet_grid(cols = vars(factor(Timepoint, levels = names(simplifiedTables))))
+    plot = plot + facet_grid(cols = vars(factor(Timepoint, levels = names(readLengthCountTables))))
   }
 
   plot = plot +

### 2022-06-14 R/DrosophilaDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Update Drosophila notebooks
- Support for all_reps
- Read length counting occurs during data generation

@@
 CPDTimepoints = list(`10m` = NULL, `30m` = NULL, `8h` = NULL, `16h` = NULL, `24h` = NULL)
+repNames = c("rep1", "rep2", "all_reps")
 minReadLength = 23; maxReadLength = 32

### 2022-06-14 R/EcoliWTDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Update E coli notebooks
- Support for all_reps
- Read length counting occurs during data generation

@@
 CPDTimepoints = list(`5min` = NULL)
+repNames = c("rep1", "rep2", "all_reps")
 minReadLength = 11; maxReadLength = 13

### 2022-06-14 R/GM12878DeaminationAnchoredExcisionSiteDataGeneration.rmd
Update cisplatin notebooks
- Support for all_reps
- Read length counting occurs during data generation

@@
 cellType = "GM12878"
-CisplatinTimepoints = list(`90min` = NULL)
+cisplatinTimepoints = list(`90min` = NULL)
 minReadLength = 22; maxReadLength = 30
@@
 # Get file paths for the expanded mismatch by read data
-CisplatinMismatchData = list(rep1 = CisplatinTimepoints,
-                             rep2 = CisplatinTimepoints)
-for (i in 1:length(CisplatinMismatchData)) {
-  for (j in 1:length(CisplatinMismatchData[[i]])) {
-    CisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
+cisplatinMismatchData = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
+for (i in 1:length(cisplatinMismatchData)) {
+  for (j in 1:length(cisplatinMismatchData[[i]])) {
+    cisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
       mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
-      cellType = cellType, lesion = "cisplatin", timepoint = names(CisplatinMismatchData[[i]])[j],
-      repitition = names(CisplatinMismatchData)[i], expansionNum = expansionOffset, filtering = filtering
+      cellType = cellType, lesion = "cisplatin", timepoint = names(cisplatinMismatchData[[i]])[j],
+      repitition = names(cisplatinMismatchData)[i], expansionNum = expansionOffset, filtering = filtering
       ))
@@
 # Filter the reads by length and mismatch type (single C>T).
-CisplatinMismatchData = lapply(CisplatinMismatchData, function(x) lapply(
+cisplatinMismatchData = lapply(cisplatinMismatchData, function(x) lapply(
   x, function(y) filterResults(y[V5 == "C>T"], minReadLength = minReadLength, maxReadLength = maxReadLength)
@@
 # Simplify the data
-CisplatinMismatchData = lapply(CisplatinMismatchData, function(x) lapply(
+cisplatinMismatchData = lapply(cisplatinMismatchData, function(x) lapply(
   x, function(y) simplifyTable(y, TRUE, expansionOffset = expansionOffset)
@@
 # Read mismatch frequency z-scores.
-# NOTE: Using NHF1 CPD scores. Otherwise, data will be too tightly constrained.
-NHF1CPDMMFreqZScores = fread(generateFilePath(
-      directory = NHF1DeaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
-      cellType = "NHF1", lesion = "CPD", repitition = "rep1",
-      timepoint = "1h", filtering = filtering, includedMismatches = c("C>T")
+cisplatinMMFreqZScores = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
+for (i in seq_along(cisplatinMMFreqZScores)) {
+  for (j in seq_along(cisplatinMMFreqZScores[[i]])) {
+    cisplatinMMFreqZScores[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinMMFreqZScores)[i],
+      timepoint = names(cisplatinMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
     ))
+  }
+}
 
 # Further filter data by read position based on length
-CisplatinMismatchData = lapply(CisplatinMismatchData, function(CisplatinMismatchDataRep) {
-  lapply(CisplatinMismatchDataRep, filterMismatchesByPositionAndReadLength,
-         NHF1CPDMMFreqZScores, expansionOffset = expansionOffset)
-})
+cisplatinMismatchData = mapply(function(cisplatinMismatchDataRep, cisplatinMMFreqZScoreRep) mapply(
+  filterMismatchesByPositionAndReadLength, cisplatinMismatchDataRep, cisplatinMMFreqZScoreRep,
+  expansionOffset = expansionOffset, SIMPLIFY = FALSE
+), cisplatinMismatchData, cisplatinMMFreqZScores, SIMPLIFY = FALSE)
 ```
@@
 #       I can still switch to new variable names for organizational purposes.
-threePrimeMismatchAnchoredCisplatinData = lapply(CisplatinMismatchData, function(x) {
+threePrimeMismatchAnchoredCisplatinData = lapply(cisplatinMismatchData, function(x) {
   lapply(x, orientDataToMismatch, THREE_PRIME, expansionOffset)
 })
-fivePrimeMismatchAnchoredCisplatinData = lapply(CisplatinMismatchData, function(x) {
+fivePrimeMismatchAnchoredCisplatinData = lapply(cisplatinMismatchData, function(x) {
   lapply(x, orientDataToMismatch, FIVE_PRIME, expansionOffset)
 })
-CisplatinMismatchData = NULL
+cisplatinMismatchData = NULL
 ```

### 2022-06-14 R/GM12878DeaminationAnchoredExcisionSiteFigureGeneration.rmd
Update cisplatin notebooks
- Support for all_reps
- Read length counting occurs during data generation

@@
 cellType = "GM12878"
-CisplatinTimepoints = list(`90min` = NULL)
+cisplatinTimepoints = list(`90min` = NULL)
+repNames = c("rep1", "rep2", "all_reps")
 minReadLength = 22; maxReadLength = 30
@@
 ```{r read_nucleotide_frequency_data}
-threePrimeMismatchCisplatinNucFreq = list(rep1 = NULL, rep2 = NULL)
+threePrimeMismatchCisplatinNucFreq = list(rep1 = NULL, rep2 = NULL, all_reps = NULL)
 for (i in seq_along(threePrimeMismatchCisplatinNucFreq)) {
@@
 
-fivePrimeMismatchCisplatinNucFreq = list(rep1 = NULL, rep2 = NULL)
+fivePrimeMismatchCisplatinNucFreq = list(rep1 = NULL, rep2 = NULL, all_reps = NULL)
 for (i in seq_along(fivePrimeMismatchCisplatinNucFreq)) {
@@
 ```{r cisplatin_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq$rep1, 
-                               title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored Nuc Freq Rep1"), collapse = ' '),
+for (i in seq_along(threePrimeMismatchCisplatinNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq[[i]], 
+                                 title = paste(c("cisplatin", titleCaseFiltering,
+                                                 "3' Anchored Nuc Freq", repNames[i]), collapse = ' '),
                                  secondaryYAxisLabel = "5' Cut Site Distance",
                                  posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq$rep2, 
-                               title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored Nuc Freq Rep2"), collapse = ' '),
-                               secondaryYAxisLabel = "5' Cut Site Distance",
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
 
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq$rep1, 
-                               title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored Nuc Freq Rep1"), collapse = ' '),
+for (i in seq_along(fivePrimeMismatchCisplatinNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq[[i]], 
+                                 title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored Nuc Freq", repNames[i]), collapse = ' '),
                                  yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                                  posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq$rep2, 
-                               title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored Nuc Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
 ```
@@
 ```{r cisplatin_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq$rep1, 
-                               title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored Purine Freq Rep1"), collapse = ' '),
+for (i in seq_along(threePrimeMismatchCisplatinNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq[[i]], 
+                                 title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                  yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
@@
                                  posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq$rep2, 
-                               title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored Purine Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
 
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq$rep1, 
-                               title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored Purine Freq Rep1"), collapse = ' '),
+for (i in seq_along(fivePrimeMismatchCisplatinNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq[[i]], 
+                                 title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                  yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
@@
                                  posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq$rep2, 
-                               title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored Purine Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
 ```
@@
 ```{r read_sequence_enrichment_data}
-threePrimeMMAnchoredCisplatinEnrichment = list(rep1 = CisplatinTimepoints,
-                                               rep2 = CisplatinTimepoints)
+threePrimeMMAnchoredCisplatinEnrichment = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
 for (i in seq_along(threePrimeMMAnchoredCisplatinEnrichment)) {
@@
 
-fivePrimeMMAnchoredCisplatinEnrichment = list(rep1 = CisplatinTimepoints,
-                                              rep2 = CisplatinTimepoints)
+fivePrimeMMAnchoredCisplatinEnrichment = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
 for (i in seq_along(fivePrimeMMAnchoredCisplatinEnrichment)) {
@@
 ```{r cisplatin_sequence_enrichment, fig.width = 11, fig.height = 9}
-plotSequenceEnrichment(threePrimeMMAnchoredCisplatinEnrichment$rep1,
-                       title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored YR Enrichment Rep1"), collapse = ' '),
+for (i in seq_along(threePrimeMMAnchoredCisplatinEnrichment)) {
+  plotSequenceEnrichment(threePrimeMMAnchoredCisplatinEnrichment[[i]],
+                         title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored YR Enrichment", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
-plotSequenceEnrichment(threePrimeMMAnchoredCisplatinEnrichment$rep2,
-                       title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored YR Enrichment Rep2"), collapse = ' '),
-                       secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
-                       expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
+}
 
-plotSequenceEnrichment(fivePrimeMMAnchoredCisplatinEnrichment$rep1,
-                       title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored TGG Enrichment Rep1"), collapse = ' '),
+for (i in seq_along(fivePrimeMMAnchoredCisplatinEnrichment)) {
+  plotSequenceEnrichment(fivePrimeMMAnchoredCisplatinEnrichment[[i]],
+                         title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored TGG Enrichment", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
-plotSequenceEnrichment(fivePrimeMMAnchoredCisplatinEnrichment$rep2,
-                       title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored TGG Enrichment Rep2"), collapse = ' '),
-                       secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
-                       expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
+}
 ```
@@
 ```{r read_sequence_frequency_data}
-threePrimeMMAnchoredCisplatinSeqFreq = list(rep1 = CisplatinTimepoints,
-                                            rep2 = CisplatinTimepoints)
+threePrimeMMAnchoredCisplatinSeqFreq = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
 for (i in seq_along(threePrimeMMAnchoredCisplatinSeqFreq)) {
@@
 
-fivePrimeMMAnchoredCisplatinSeqFreq = list(rep1 = CisplatinTimepoints,
-                                           rep2 = CisplatinTimepoints)
+fivePrimeMMAnchoredCisplatinSeqFreq = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
 for (i in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq)) {
@@
 ```{r cisplatin_sequence_frequencies, fig.width = 11, fig.height = 9}
-plotSequenceFrequencies(threePrimeMMAnchoredCisplatinSeqFreq$rep1,
-                        title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored YR Freq Rep1"), collapse = ' '),
+for (i in seq_along(threePrimeMMAnchoredCisplatinSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredCisplatinSeqFreq[[i]],
+                          title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored YR Freq", repNames[i]), collapse = ' '),
                           secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                           expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
-plotSequenceFrequencies(threePrimeMMAnchoredCisplatinSeqFreq$rep2,
-                        title = paste(c("cisplatin", titleCaseFiltering, "3' Anchored YR Freq Rep2"), collapse = ' '),
-                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
-                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
+}
 
-plotSequenceFrequencies(fivePrimeMMAnchoredCisplatinSeqFreq$rep1,
-                        title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored TGG Freq Rep1"), collapse = ' '),
+for (i in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq)) {
+  plotSequenceFrequencies(fivePrimeMMAnchoredCisplatinSeqFreq[[i]],
+                          title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored TGG Freq", repNames[i]), collapse = ' '),
                           secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                           expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
-plotSequenceFrequencies(fivePrimeMMAnchoredCisplatinSeqFreq$rep2,
-                        title = paste(c("cisplatin", titleCaseFiltering, "5' Anchored TGG Freq Rep2"), collapse = ' '),
-                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
-                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
+}
 ```

### 2022-06-14 R/GM12878DeaminationSequenceAndPositionDataGeneration.rmd
Update cisplatin notebooks
- Support for all_reps
- Read length counting occurs during data generation

@@
 # Get file paths for the mismatch by read data
-CisplatinMismatchData = list(rep1 = CisplatinTimepoints,
-                             rep2 = CisplatinTimepoints)
-for (i in 1:length(CisplatinMismatchData)) {
-  for (j in 1:length(CisplatinMismatchData[[i]])) {
-    CisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
+cisplatinMismatchData = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
+for (i in 1:length(cisplatinMismatchData)) {
+  for (j in 1:length(cisplatinMismatchData[[i]])) {
+    cisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
       mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
-      cellType = cellType, lesion = "cisplatin", timepoint = names(CisplatinMismatchData[[i]])[j],
-      repitition = names(CisplatinMismatchData)[i], filtering = filtering
+      cellType = cellType, lesion = "cisplatin", timepoint = names(cisplatinMismatchData[[i]])[j],
+      repitition = names(cisplatinMismatchData)[i], filtering = filtering
       ))
@@
 # Perform general filtering on the data
-CisplatinMismatchData = lapply(CisplatinMismatchData, function(x) lapply(
+cisplatinMismatchData = lapply(cisplatinMismatchData, function(x) lapply(
   x, function(y) filterResults(y, TRUE, 3, minReadLength, maxReadLength)
@@
 # Simplify the data
-CisplatinMismatchData = lapply(CisplatinMismatchData, function(x) lapply(
+cisplatinMismatchData = lapply(cisplatinMismatchData, function(x) lapply(
   x, function(y) simplifyTable(y, includeTrinucleotideContext = TRUE)
@@
 # Write the simplified mismatch data
-for (i in 1:length(CisplatinMismatchData)) {
-  for (j in 1:length(CisplatinMismatchData[[i]])) {
-    fwrite(CisplatinMismatchData[[i]][[j]], sep = '\t', na = "NA",
+for (i in 1:length(cisplatinMismatchData)) {
+  for (j in 1:length(cisplatinMismatchData[[i]])) {
+    fwrite(cisplatinMismatchData[[i]][[j]], sep = '\t', na = "NA",
            file = generateFilePath(
              deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
-             cellType = cellType, lesion = "cisplatin", timepoint = names(CisplatinMismatchData[[i]])[j],
-             repitition = names(CisplatinMismatchData)[i], filtering = filtering
+             cellType = cellType, lesion = "cisplatin", timepoint = names(cisplatinMismatchData[[i]])[j],
+             repitition = names(cisplatinMismatchData)[i], filtering = filtering
            ))
@@
 # Don't forget to subset by C>T mismatches!
-CisplatinMMFreqZScores = lapply(CisplatinMismatchData, function(x) lapply(
+cisplatinMMFreqZScores = lapply(cisplatinMismatchData, function(x) lapply(
   x, function(y) {
@@
 
-for (i in seq_along(CisplatinMMFreqZScores)) {
-  for (j in seq_along(CisplatinMMFreqZScores[[i]])) {
-    fwrite(CisplatinMMFreqZScores[[i]][[j]], sep = '\t', file = generateFilePath(
+for (i in seq_along(cisplatinMMFreqZScores)) {
+  for (j in seq_along(cisplatinMMFreqZScores[[i]])) {
+    fwrite(cisplatinMMFreqZScores[[i]][[j]], sep = '\t', file = generateFilePath(
       directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
-      cellType = cellType, lesion = "cisplatin", repitition = names(CisplatinMMFreqZScores)[i],
-      timepoint = names(CisplatinMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
+      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinMMFreqZScores)[i],
+      timepoint = names(cisplatinMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
+    ))
+  }
+}
+```
+
+```{r generate_and_write_read_length_counts}
+cisplatinReadLengthCounts = lapply(cisplatinMismatchData, function(x) lapply(
+  x, function(y) {
+    y[, .N, by = Read_Length][order(Read_Length)]
+  }
+))
+
+for (i in seq_along(cisplatinReadLengthCounts)) {
+  for (j in seq_along(cisplatinReadLengthCounts[[i]])) {
+    fwrite(cisplatinReadLengthCounts[[i]][[j]], sep = '\t', file = generateFilePath(
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
+      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinReadLengthCounts)[i],
+      timepoint = names(cisplatinReadLengthCounts[[i]])[j], filtering = filtering
     ))
@@
 ```{r generate_and_write_mismatch_position_statistics_by_read_length_and_timepoint}
-CisplatinGroupedStats = list(rep1 = list(), rep2 = list())
-CisplatinGroupedStats$rep1$three_prime = getGroupedPositionStats(CisplatinMismatchData$rep1, includedTypes = c("C>T"))
-CisplatinGroupedStats$rep2$three_prime = getGroupedPositionStats(CisplatinMismatchData$rep2, includedTypes = c("C>T"))
-CisplatinGroupedStats$rep1$five_prime =
-  getGroupedPositionStats(CisplatinMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME)
-CisplatinGroupedStats$rep2$five_prime =
-  getGroupedPositionStats(CisplatinMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME)
+cisplatinGroupedStats = list(rep1 = list(), rep2 = list(), all_reps = list())
+for (i in seq_along(cisplatinGroupedStats)) {
+  cisplatinGroupedStats[[i]]$three_prime = getGroupedPositionStats(cisplatinMismatchData[[i]], includedTypes = c("C>T"))
+  cisplatinGroupedStats[[i]]$five_prime =
+    getGroupedPositionStats(cisplatinMismatchData[[i]], includedTypes = c("C>T"), posType = FIVE_PRIME)
+}
 
-for (i in seq_along(CisplatinGroupedStats)) {
-  for (j in seq_along(CisplatinGroupedStats[[i]])) {
-    fwrite(CisplatinGroupedStats[[i]][[j]], sep = '\t',
+for (i in seq_along(cisplatinGroupedStats)) {
+  for (j in seq_along(cisplatinGroupedStats[[i]])) {
+    fwrite(cisplatinGroupedStats[[i]][[j]], sep = '\t',
            file = generateFilePath(
              deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
-             cellType = cellType, lesion = "cisplatin", repitition = names(CisplatinGroupedStats)[i],
-             strandPolarity = names(CisplatinGroupedStats[[i]])[j], filtering = filtering
+             cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinGroupedStats)[i],
+             strandPolarity = names(cisplatinGroupedStats[[i]])[j], filtering = filtering
            ))

### 2022-06-14 R/GM12878DeaminationSequenceAndPositionFigureGeneration.rmd
Update cisplatin notebooks
- Support for all_reps
- Read length counting occurs during data generation

@@
 # Get file paths for the mismatch by read data
-CisplatinMismatchData = list(rep1 = CisplatinTimepoints,
-                             rep2 = CisplatinTimepoints)
-for (i in seq_along(CisplatinMismatchData)) {
-  for (j in seq_along(CisplatinMismatchData[[i]])) {
-    CisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
+cisplatinMismatchData = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
+for (i in seq_along(cisplatinMismatchData)) {
+  for (j in seq_along(cisplatinMismatchData[[i]])) {
+    cisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
       deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
-      cellType = cellType, lesion = "cisplatin", timepoint = names(CisplatinMismatchData[[i]])[j],
-      repitition = names(CisplatinMismatchData)[i], filtering = filtering
+      cellType = cellType, lesion = "cisplatin", timepoint = names(cisplatinMismatchData[[i]])[j],
+      repitition = names(cisplatinMismatchData)[i], filtering = filtering
     ))
@@
 ```{r cisplatin_mismatch_type_frequency}
-for (i in 1:length(CisplatinMismatchData)) {
-  for (j in 1:length(CisplatinMismatchData[[i]])) {
-    plotMismatchTypeFrequencies(CisplatinMismatchData[[i]][[j]],
-                                title = paste(c("cisplatin", titleCaseFiltering, names(CisplatinMismatchData)[i], 
-                                                names(CisplatinMismatchData[[i]])[j], "Mismatch Type Frequency"),
+for (i in 1:length(cisplatinMismatchData)) {
+  for (j in 1:length(cisplatinMismatchData[[i]])) {
+    plotMismatchTypeFrequencies(cisplatinMismatchData[[i]][[j]],
+                                title = paste(c("cisplatin", titleCaseFiltering, names(cisplatinMismatchData)[i], 
+                                                names(cisplatinMismatchData[[i]])[j], "Mismatch Type Frequency"),
                                               collapse = ' '))
@@
 ```{r cisplatin_mismatch_pos_frequency}
-for (i in 1:length(CisplatinMismatchData)) {
-  for (j in 1:length(CisplatinMismatchData[[i]])) {
-    plotMismatchPositionFrequencies(CisplatinMismatchData[[i]][[j]], includedTypes = c("C>T"),
-                                    title = paste(c("cisplatin", titleCaseFiltering, names(CisplatinMismatchData)[i], 
-                                                    names(CisplatinMismatchData[[i]])[j], "C>T Mismatch Positions"),
+for (i in 1:length(cisplatinMismatchData)) {
+  for (j in 1:length(cisplatinMismatchData[[i]])) {
+    plotMismatchPositionFrequencies(cisplatinMismatchData[[i]][[j]], includedTypes = c("C>T"),
+                                    title = paste(c("cisplatin", titleCaseFiltering, names(cisplatinMismatchData)[i], 
+                                                    names(cisplatinMismatchData[[i]])[j], "C>T Mismatch Positions"),
                                                   collapse = ' '))
-    plotMismatchPositionFrequencies(CisplatinMismatchData[[i]][[j]], omittedTypes = c("C>T"),
-                                    title = paste(c("cisplatin", titleCaseFiltering, names(CisplatinMismatchData)[i], 
-                                                    names(CisplatinMismatchData[[i]])[j], "!C>T Mismatch Positions"),
+    plotMismatchPositionFrequencies(cisplatinMismatchData[[i]][[j]], omittedTypes = c("C>T"),
+                                    title = paste(c("cisplatin", titleCaseFiltering, names(cisplatinMismatchData)[i], 
+                                                    names(cisplatinMismatchData[[i]])[j], "!C>T Mismatch Positions"),
                                                   collapse = ' '))
@@
 ```{r cisplatin_trinucleotide_context_analysis}
-for (i in 1:length(CisplatinMismatchData)) {
-  for (j in 1:length(CisplatinMismatchData[[i]])) {
-    plotTrinucleotideContext(CisplatinMismatchData[[i]][[j]], includedTypes = c("C>T"),
-                             title = paste(c("cisplatin", titleCaseFiltering, names(CisplatinMismatchData)[i],
-                                             names(CisplatinMismatchData[[i]])[j], "C>T Mismatch Trinuc Context"),
+for (i in 1:length(cisplatinMismatchData)) {
+  for (j in 1:length(cisplatinMismatchData[[i]])) {
+    plotTrinucleotideContext(cisplatinMismatchData[[i]][[j]], includedTypes = c("C>T"),
+                             title = paste(c("cisplatin", titleCaseFiltering, names(cisplatinMismatchData)[i],
+                                             names(cisplatinMismatchData[[i]])[j], "C>T Mismatch Trinuc Context"),
                                            collapse = ' '))
@@
 ```{r read_mismatch_frequency_z-score_tables}
-CisplatinMMFreqZScores = list(rep1 = CisplatinTimepoints, rep2 = CisplatinTimepoints)
-for (i in seq_along(CisplatinMMFreqZScores)) {
-  for (j in seq_along(CisplatinMMFreqZScores[[i]])) {
-    CisplatinMMFreqZScores[[i]][[j]] = fread(generateFilePath(
+cisplatinMMFreqZScores = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
+for (i in seq_along(cisplatinMMFreqZScores)) {
+  for (j in seq_along(cisplatinMMFreqZScores[[i]])) {
+    cisplatinMMFreqZScores[[i]][[j]] = fread(generateFilePath(
       directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
-      cellType = cellType, lesion = "cisplatin", repitition = names(CisplatinMMFreqZScores)[i],
-      timepoint = names(CisplatinMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
+      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinMMFreqZScores)[i],
+      timepoint = names(cisplatinMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
     ))
@@
 ```{r cisplatin_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
-plotPositionAcrossTimepointAndReadLength(CisplatinMismatchData$rep1, includedTypes = c("C>T"),
-                                         title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
+for (i in seq_along(cisplatinMismatchData)) {
+  plotPositionAcrossTimepointAndReadLength(cisplatinMismatchData[[i]], includedTypes = c("C>T"),
+                                           title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Freq", repNames[i]),
                                                          collapse = ' '),
-                                         zScoreTables = CisplatinMMFreqZScores$rep1)
-plotPositionAcrossTimepointAndReadLength(CisplatinMismatchData$rep2, includedTypes = c("C>T"),
-                                         title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
+                                           zScoreTables = cisplatinMMFreqZScores[[i]])
+  plotPositionAcrossTimepointAndReadLength(cisplatinMismatchData[[i]], includedTypes = c("C>T"), posType = FIVE_PRIME,
+                                           title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Freq", repNames[i]),
                                                          collapse = ' '),
-                                         zScoreTables = CisplatinMMFreqZScores$rep2)
-plotPositionAcrossTimepointAndReadLength(CisplatinMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME,
-                                         title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
-                                                       collapse = ' '),
-                                         zScoreTables = CisplatinMMFreqZScores$rep1)
-plotPositionAcrossTimepointAndReadLength(CisplatinMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME,
-                                         title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
-                                                       collapse = ' '),
-                                         zScoreTables = CisplatinMMFreqZScores$rep2)
+                                           zScoreTables = cisplatinMMFreqZScores[[i]])
+}
+```
+
+```{r read_read_length_counts}
+cisplatinReadLengthCounts = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
+for (i in seq_along(cisplatinReadLengthCounts)) {
+  for (j in seq_along(cisplatinReadLengthCounts[[i]])) {
+    cisplatinReadLengthCounts[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
+      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinReadLengthCounts)[i],
+      timepoint = names(cisplatinReadLengthCounts[[i]])[j], filtering = filtering
+    ))
+  }
+}
 ```
@@
 ```{r cisplatin_read_length_distributions}
-plotReadLengthFrequencies(CisplatinMismatchData$rep1,
-                          title = paste(c("cisplatin", titleCaseFiltering, "Read Length Freq Rep 1"), collapse = ' '))
-plotReadLengthFrequencies(CisplatinMismatchData$rep2,
-                          title = paste(c("cisplatin", titleCaseFiltering, "Read Length Freq Rep 2"), collapse = ' '))
+for (i in seq_along(cisplatinReadLengthCounts)) {
+  plotReadLengthFrequencies(cisplatinReadLengthCounts[[i]],
+                            title = paste(c("cisplatin", titleCaseFiltering, "Read Length Freq", repNames[i]), collapse = ' '))
+}
 ```
@@
 ```{r read_mismatch_position_statistics}
-CisplatinGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
-                             rep2 = list(three_prime = NULL, five_prime = NULL))
-for (i in seq_along(CisplatinGroupedStats)) {
-  for (j in seq_along(CisplatinGroupedStats[[i]])) {
-    CisplatinGroupedStats[[i]][[j]] = fread(generateFilePath(
+cisplatinGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
+                             rep2 = list(three_prime = NULL, five_prime = NULL),
+                             all_reps = list(three_prime = NULL, five_prime = NULL))
+for (i in seq_along(cisplatinGroupedStats)) {
+  for (j in seq_along(cisplatinGroupedStats[[i]])) {
+    cisplatinGroupedStats[[i]][[j]] = fread(generateFilePath(
       deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
-      cellType = cellType, lesion = "cisplatin", repitition = names(CisplatinGroupedStats)[i],
-      strandPolarity = names(CisplatinGroupedStats[[i]])[j], filtering = filtering
+      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinGroupedStats)[i],
+      strandPolarity = names(cisplatinGroupedStats[[i]])[j], filtering = filtering
     ))
@@
 ```{r cisplatin_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
-plotGroupedPositionStats(CisplatinGroupedStats$rep1$three_prime, CisplatinGroupedStats$rep1$five_prime, POS_DIFF,
-                         title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Diff Rep1"), collapse = ' '),
+for (i in seq_along(cisplatinGroupedStats)) {
+  plotGroupedPositionStats(cisplatinGroupedStats[[i]]$three_prime, cisplatinGroupedStats[[i]]$five_prime, POS_DIFF,
+                           title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Diff", repNames[i]), collapse = ' '),
                            xAxisBreaks = c(minReadLength:maxReadLength))
-plotGroupedPositionStats(CisplatinGroupedStats$rep2$three_prime, CisplatinGroupedStats$rep2$five_prime, POS_DIFF,
-                         title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Diff Rep2"), collapse = ' '),
-                         xAxisBreaks = c(minReadLength:maxReadLength))
+}
 ```

### 2022-06-14 R/GM12878GeneralReadSequenceDataGeneration.rmd
Update cisplatin notebooks
- Support for all_reps
- Read length counting occurs during data generation

@@
 ```{r compute_and_write_cisplatin_sequence_frequency}
-for (repitition in c("rep1", "rep2")) {
-  for (timepoint in names(CisplatinTimepoints)) {
+for (repitition in repNames) {
+  for (timepoint in names(cisplatinTimepoints)) {
     singleFileFullAnalysis("cisplatin", repitition, timepoint)

### 2022-06-14 R/GM12878GeneralReadSequenceFigureGeneration.rmd
Update cisplatin notebooks
- Support for all_reps
- Read length counting occurs during data generation

@@
 ```{r read_sequence_frequencies}
-CisplatinTGGSeqFreq = list(rep1 = CisplatinTimepoints, rep2 = CisplatinTimepoints)
-for (i in seq_along(CisplatinTGGSeqFreq)) {
-  for (j in seq_along(CisplatinTGGSeqFreq[[i]])) {
-    CisplatinTGGSeqFreq[[i]][[j]] = fread(generateFilePath(
+CPDTGGSeqFreq = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
+for (i in seq_along(CPDTGGSeqFreq)) {
+  for (j in seq_along(CPDTGGSeqFreq[[i]])) {
+    CPDTGGSeqFreq[[i]][[j]] = fread(generateFilePath(
       directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
-      cellType = cellType, lesion = "cisplatin", repitition = names(CisplatinTGGSeqFreq)[i],
-      timepoint = names(CisplatinTGGSeqFreq[[i]])[j], sequence = "TGG"
+      cellType = cellType, lesion = "cisplatin", repitition = names(CPDTGGSeqFreq)[i],
+      timepoint = names(CPDTGGSeqFreq[[i]])[j], sequence = "TGG"
     ))
@@
 
-CisplatinCGASeqFreq = list(rep1 = CisplatinTimepoints, rep2 = CisplatinTimepoints)
-for (i in seq_along(CisplatinCGASeqFreq)) {
-  for (j in seq_along(CisplatinCGASeqFreq[[i]])) {
-    CisplatinCGASeqFreq[[i]][[j]] = fread(generateFilePath(
+CPDCGASeqFreq = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
+for (i in seq_along(CPDCGASeqFreq)) {
+  for (j in seq_along(CPDCGASeqFreq[[i]])) {
+    CPDCGASeqFreq[[i]][[j]] = fread(generateFilePath(
       directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
-      cellType = cellType, lesion = "cisplatin", repitition = names(CisplatinCGASeqFreq)[i],
-      timepoint = names(CisplatinCGASeqFreq[[i]])[j], sequence = "CGA"
+      cellType = cellType, lesion = "cisplatin", repitition = names(CPDCGASeqFreq)[i],
+      timepoint = names(CPDCGASeqFreq[[i]])[j], sequence = "CGA"
     ))
@@
 ```{r cisplatin_sequence_frequencies, fig.width = 11, fig.height = 10}
-plotSequenceFrequencies(CisplatinTGGSeqFreq$rep1,
-                        title = "cisplatin TGG Frequencies Rep1", expansionOffset = expansionOffset,
-                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
-                        querySequences = c("TGG"))
-plotSequenceFrequencies(CisplatinTGGSeqFreq$rep2,
-                        title = "cisplatin TGG Frequencies Rep2", expansionOffset = expansionOffset,
-                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
-                        querySequences = c("TGG"))
+for (i in seq_along(CPDTGGSeqFreq)) {
+  plotSequenceFrequencies(CPDTGGSeqFreq[[i]],
+                          title = paste("Cisplatin TGG Frequencies", repNames[i]),
+                          expansionOffset = expansionOffset, showThreePrimeCutSite = TRUE,
+                          showFivePrimeCutSite = TRUE, querySequences = c("TGG"))
+}
 
-plotSequenceFrequencies(CisplatinCGASeqFreq$rep1,
-                        title = "cisplatin CGA Frequencies Rep1", expansionOffset = expansionOffset,
+for (i in seq_along(CPDCGASeqFreq)) {
+  plotSequenceFrequencies(CPDCGASeqFreq[[i]],
+                          title = paste("Cisplatin CGA Frequencies", repNames[i]), expansionOffset = expansionOffset,
                           showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                           querySequences = c("CGA"))
-plotSequenceFrequencies(CisplatinCGASeqFreq$rep2,
-                        title = "cisplatin CGA Frequencies Rep2", expansionOffset = expansionOffset,
-                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
-                        querySequences = c("CGA"))
+}
 ```
@@
 ```{r cisplatin_read_length_frequencies}
-readAndPlotReadLengthFrequencies("cisplatin", "rep1", CisplatinTimepoints)
-readAndPlotReadLengthFrequencies("cisplatin", "rep2", CisplatinTimepoints)
+for (rep in repNames) {
+  readAndPlotReadLengthFrequencies("cisplatin", rep, cisplatinTimepoints)
+}
 ```

### 2022-06-14 R/GM12878TandemDeaminationDataGeneration.rmd
Update cisplatin notebooks
- Support for all_reps
- Read length counting occurs during data generation

@@
 # Get file paths for the mismatch by read data
-cisplatinMismatchData = list(rep1 = cisplatinTimepoints,
-                             rep2 = cisplatinTimepoints)
+cisplatinMismatchData = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
 for (i in 1:length(cisplatinMismatchData)) {
@@
 
+```{r generate_and_write_read_length_counts}
+cisplatinReadLengthCounts = lapply(cisplatinMismatchData, function(x) lapply(
+  x, function(y) {
+    y[, .N, by = Read_Length][order(Read_Length)]
+  }
+))
+
+for (i in seq_along(cisplatinReadLengthCounts)) {
+  for (j in seq_along(cisplatinReadLengthCounts[[i]])) {
+    fwrite(cisplatinReadLengthCounts[[i]][[j]], sep = '\t', file = generateFilePath(
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
+      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinReadLengthCounts)[i],
+      timepoint = names(cisplatinReadLengthCounts[[i]])[j], filtering = filtering, includedMismatches = mismatchType
+    ))
+  }
+}
+```
+
 ```{r generate_and_write_mismatch_position_statistics_by_read_length_and_timepoint}
-cisplatinGroupedStats = list(rep1 = list(), rep2 = list())
-cisplatinGroupedStats$rep1$three_prime = getGroupedPositionStats(cisplatinMismatchData$rep1)
-cisplatinGroupedStats$rep2$three_prime = getGroupedPositionStats(cisplatinMismatchData$rep2)
-cisplatinGroupedStats$rep1$five_prime = getGroupedPositionStats(cisplatinMismatchData$rep1, posType = FIVE_PRIME)
-cisplatinGroupedStats$rep2$five_prime = getGroupedPositionStats(cisplatinMismatchData$rep2, posType = FIVE_PRIME)
+cisplatinGroupedStats = list(rep1 = list(), rep2 = list(), all_reps = list())
+for (i in seq_along(cisplatinGroupedStats)) {
+  cisplatinGroupedStats[[i]]$three_prime = getGroupedPositionStats(cisplatinMismatchData[[i]])
+  cisplatinGroupedStats[[i]]$five_prime = getGroupedPositionStats(cisplatinMismatchData[[i]], posType = FIVE_PRIME)
+}
 
@@
 # Get file paths for the expanded mismatch by read data
-cisplatinMismatchData = list(rep1 = cisplatinTimepoints,
-                             rep2 = cisplatinTimepoints)
+cisplatinMismatchData = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
 for (i in 1:length(cisplatinMismatchData)) {
@@
 # Read mismatch frequency z-scores.
-cisplatinMMFreqZScores = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints)
+cisplatinMMFreqZScores = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
 for (i in seq_along(cisplatinMMFreqZScores)) {
@@
 ```{r generate_and_write_nucleotide_frequency_data}
-threePrimeMismatchCisplatinNucFreq = lapply(threePrimeMismatchAnchoredCisplatinData,
-                                            tabulateNucFreqByPosTimepointAndLength)
+threePrimeMismatchCisplatinNucFreq = lapply(threePrimeMismatchAnchoredCisplatinData, tabulateNucFreqByPosTimepointAndLength)
 for (i in seq_along(threePrimeMismatchCisplatinNucFreq)) {
@@
 ```{r generate_and_write_sequence_frequencies}
-threePrimeMMAnchoredCisplatinSeqFreq = lapply(
-  threePrimeMismatchAnchoredCisplatinData,function(mismatchDataRep) {
+threePrimeMMAnchoredCisplatinSeqFreq = lapply(threePrimeMismatchAnchoredCisplatinData, function(mismatchDataRep) {
   lapply(mismatchDataRep, function(mismatchData) {
@@
   })
-  }
-)
+})
 for (i in seq_along(threePrimeMMAnchoredCisplatinSeqFreq)) {
@@
 
-fivePrimeMMAnchoredCisplatinSeqFreq = lapply(
-  fivePrimeMismatchAnchoredCisplatinData, function(mismatchDataRep) {
+fivePrimeMMAnchoredCisplatinSeqFreq = lapply(fivePrimeMismatchAnchoredCisplatinData, function(mismatchDataRep) {
   lapply(mismatchDataRep, function(mismatchData) {
@@
   })
-  }
-)
+})
 for (i in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq)) {

### 2022-06-14 R/GM12878TandemDeaminationFigureGeneration.rmd
Update cisplatin notebooks
- Support for all_reps
- Read length counting occurs during data generation

@@
 cisplatinTimepoints = list(`90min` = NULL)
+repNames = c("rep1", "rep2", "all_reps")
 minReadLength = 22; maxReadLength = 30
@@
 # Get file paths for the mismatch by read data
-cisplatinMismatchData = list(rep1 = cisplatinTimepoints,
-                             rep2 = cisplatinTimepoints)
+cisplatinMismatchData = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
 for (i in seq_along(cisplatinMismatchData)) {
@@
 ```{r read_mismatch_frequency_z-score_tables}
-cisplatinMMFreqZScores = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints)
+cisplatinMMFreqZScores = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
 for (i in seq_along(cisplatinMMFreqZScores)) {
@@
 ```{r cisplatin_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
-plotPositionAcrossTimepointAndReadLength(cisplatinMismatchData$rep1,
+for (i in seq_along(cisplatinMismatchData)) {
+  plotPositionAcrossTimepointAndReadLength(cisplatinMismatchData[[i]],
                                            title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
-                                                         "Mismatch Pos Freq Rep1"),
+                                                           "Mismatch Pos Freq", repNames[i]),
                                                          collapse = ' '),
-                                         zScoreTables = cisplatinMMFreqZScores$rep1)
-plotPositionAcrossTimepointAndReadLength(cisplatinMismatchData$rep2,
+                                           zScoreTables = cisplatinMMFreqZScores[[i]])
+  plotPositionAcrossTimepointAndReadLength(cisplatinMismatchData[[i]], posType = FIVE_PRIME,
                                            title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
-                                                         "Mismatch Pos Freq Rep2"),
+                                                           "Mismatch Pos Freq", repNames[i]),
                                                          collapse = ' '),
-                                         zScoreTables = cisplatinMMFreqZScores$rep2)
-plotPositionAcrossTimepointAndReadLength(cisplatinMismatchData$rep1, posType = FIVE_PRIME,
-                                         title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
-                                                         "Mismatch Pos Freq Rep1"),
-                                                       collapse = ' '),
-                                         zScoreTables = cisplatinMMFreqZScores$rep1)
-plotPositionAcrossTimepointAndReadLength(cisplatinMismatchData$rep2, posType = FIVE_PRIME,
-                                         title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
-                                                         "Mismatch Pos Freq Rep2"),
-                                                       collapse = ' '),
-                                         zScoreTables = cisplatinMMFreqZScores$rep2)
+                                           zScoreTables = cisplatinMMFreqZScores[[i]])
+}
+```
+
+```{r read_read_length_counts}
+cisplatinReadLengthCounts = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
+for (i in seq_along(cisplatinReadLengthCounts)) {
+  for (j in seq_along(cisplatinReadLengthCounts[[i]])) {
+    cisplatinReadLengthCounts[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
+      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinReadLengthCounts)[i],
+      timepoint = names(cisplatinReadLengthCounts[[i]])[j], filtering = filtering, includedMismatches = mismatchType
+    ))
+  }
+}
 ```
@@
 ```{r cisplatin_read_length_distributions}
-plotReadLengthFrequencies(cisplatinMismatchData$rep1,
+for (i in seq_along(cisplatinReadLengthCounts)) {
+  plotReadLengthFrequencies(cisplatinReadLengthCounts[[i]],
                             title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
-                                          "Read Length Freq Rep1"), collapse = ' '))
-plotReadLengthFrequencies(cisplatinMismatchData$rep2,
-                          title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
-                                          "Read Length Freq Rep2"), collapse = ' '))
+                                            "Read Length Freq", repNames[i]), collapse = ' '))
+}
 ```
@@
 cisplatinGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
-                             rep2 = list(three_prime = NULL, five_prime = NULL))
+                             rep2 = list(three_prime = NULL, five_prime = NULL),
+                             all_reps = list(three_prime = NULL, five_prime = NULL))
 for (i in seq_along(cisplatinGroupedStats)) {
@@
       cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinGroupedStats)[i],
-      strandPolarity = names(cisplatinGroupedStats[[i]])[j], filtering = filtering,
-      includedMismatches = mismatchType
+      strandPolarity = names(cisplatinGroupedStats[[i]])[j], filtering = filtering, includedMismatches = mismatchType
     ))
@@
 ```{r cisplatin_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
-plotGroupedPositionStats(cisplatinGroupedStats$rep1$three_prime, cisplatinGroupedStats$rep1$five_prime, POS_DIFF,
+for (i in seq_along(cisplatinGroupedStats)) {
+  plotGroupedPositionStats(cisplatinGroupedStats[[i]]$three_prime, cisplatinGroupedStats[[i]]$five_prime, POS_DIFF,
                            title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
-                                         "Mismatch Pos Diff Rep1"), collapse = ' '),
+                                           "Mismatch Pos Diff", repNames[i]), collapse = ' '),
                            xAxisBreaks = c(minReadLength:maxReadLength))
-plotGroupedPositionStats(cisplatinGroupedStats$rep2$three_prime, cisplatinGroupedStats$rep2$five_prime, POS_DIFF,
-                         title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
-                                         "Mismatch Pos Diff Rep2"), collapse = ' '),
-                         xAxisBreaks = c(minReadLength:maxReadLength))
+}
 ```
@@
 ```{r cisplatin_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq$rep1, 
+for (i in seq_along(threePrimeMismatchCisplatinNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq[[i]], 
                                  title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
-                                               "3' Anchored Nuc Freq Rep1"), collapse = ' '),
+                                                 "3' Anchored Nuc Freq", repNames[i]), collapse = ' '),
                                  secondaryYAxisLabel = "5' Cut Site Distance",
                                  posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq$rep2, 
+}
+
+for (i in seq_along(fivePrimeMismatchCisplatinNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq[[i]], 
                                  title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
-                                               "3' Anchored Nuc Freq Rep2"), collapse = ' '),
-                               secondaryYAxisLabel = "5' Cut Site Distance",
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq$rep1, 
-                               title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
-                                               "5' Anchored Nuc Freq Rep1"), collapse = ' '),
+                                                 "5' Anchored Nuc Freq", repNames[i]), collapse = ' '),
                                  yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                                  posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq$rep2, 
-                               title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
-                                               "5' Anchored Nuc Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
 ```
@@
 ```{r cisplatin_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq$rep1, 
+for (i in seq_along(threePrimeMismatchCisplatinNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq[[i]], 
                                  title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
-                                               "3' Anchored Purine Freq Rep1"), collapse = ' '),
+                                                 "3' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                  yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
@@
                                  posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCisplatinNucFreq$rep2, 
+}
+
+for (i in seq_along(fivePrimeMismatchCisplatinNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq[[i]], 
                                  title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
-                                               "3' Anchored Purine Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq$rep1, 
-                               title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
-                                               "5' Anchored Purine Freq Rep1"), collapse = ' '),
+                                                 "5' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                  yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
@@
                                  posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCisplatinNucFreq$rep2, 
-                               title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
-                                               "5' Anchored Purine Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
 ```
@@
 ```{r read_sequence_frequency_data}
-threePrimeMMAnchoredCisplatinSeqFreq = list(rep1 = cisplatinTimepoints,
-                                            rep2 = cisplatinTimepoints)
+threePrimeMMAnchoredCisplatinSeqFreq = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
 for (i in seq_along(threePrimeMMAnchoredCisplatinSeqFreq)) {
@@
 
-fivePrimeMMAnchoredCisplatinSeqFreq = list(rep1 = cisplatinTimepoints,
-                                           rep2 = cisplatinTimepoints)
+fivePrimeMMAnchoredCisplatinSeqFreq = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
 for (i in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq)) {
@@
 ```{r cisplatin_sequence_frequencies, fig.width = 11, fig.height = 9}
-plotSequenceFrequencies(threePrimeMMAnchoredCisplatinSeqFreq$rep1,
+for (i in seq_along(threePrimeMMAnchoredCisplatinSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredCisplatinSeqFreq[[i]],
                           title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
-                                        "3' Anchored YR Freq Rep1"), collapse = ' '),
+                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
                           secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                           expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
-plotSequenceFrequencies(threePrimeMMAnchoredCisplatinSeqFreq$rep2,
+}
+
+for (i in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq)) {
+  plotSequenceFrequencies(fivePrimeMMAnchoredCisplatinSeqFreq[[i]],
                           title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
-                                        "3' Anchored YR Freq Rep2"), collapse = ' '),
-                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
-                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
-
-plotSequenceFrequencies(fivePrimeMMAnchoredCisplatinSeqFreq$rep1,
-                        title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
-                                        "5' Anchored TGG Freq Rep1"), collapse = ' '),
+                                          "5' Anchored TGG Freq", repNames[i]), collapse = ' '),
                           secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                           expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
-plotSequenceFrequencies(fivePrimeMMAnchoredCisplatinSeqFreq$rep2,
-                        title = paste(c("cisplatin", titleCaseFiltering, titleCaseMismatchType,
-                                        "5' Anchored TGG Freq Rep2"), collapse = ' '),
-                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
-                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
+}
 ```

### 2022-06-15 R/NHF1DeaminationAnchoredExcisionSiteDataGeneration.rmd
Update NHF1 notebooks
- Support for all_reps
- Read length counting occurs during data generation
- Temporarily removed chunks with adjusted y-axis from minimum read length filtering

@@
 
-sixFourMismatchData = list(rep1 = sixFourTimepoints,
-                           rep2 = sixFourTimepoints)
+sixFourMismatchData = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints, all_reps = sixFourTimepoints)
 for (i in 1:length(sixFourMismatchData)) {
@@
 
-sixFourMMFreqZScores = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
+sixFourMMFreqZScores = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints, all_reps = sixFourTimepoints)
 for (i in seq_along(sixFourMMFreqZScores)) {

### 2022-06-15 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
Update NHF1 notebooks
- Support for all_reps
- Read length counting occurs during data generation
- Temporarily removed chunks with adjusted y-axis from minimum read length filtering

--- 2022-05-25 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
@@
 sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
+repNames = c("rep1", "rep2", "all_reps")
 
@@
 
-threePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL)
+threePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL, all_reps = NULL)
 for (i in seq_along(threePrimeMismatchSixFourNucFreq)) {
@@
 
-fivePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL)
+fivePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL, all_reps = NULL)
 for (i in seq_along(fivePrimeMismatchSixFourNucFreq)) {
@@
 ```{r CPD_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
-                               title = paste(c("CPD", titleCaseFiltering, "3' Anchored Nuc Freq Rep1"), collapse = ' '),
+for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq[[i]], 
+                                 title = paste(c("CPD", titleCaseFiltering,
+                                                 "3' Anchored Nuc Freq", repNames[i]), collapse = ' '),
                                  secondaryYAxisLabel = "5' Cut Site Distance",
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep2, 
-                               title = paste(c("CPD", titleCaseFiltering, "3' Anchored Nuc Freq Rep2"), collapse = ' '),
-                               secondaryYAxisLabel = "5' Cut Site Distance",
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+                                 posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
+                                 expansionOffset = expansionOffset)
+}
 
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
-                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Nuc Freq Rep1"), collapse = ' '),
+for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]], 
+                                 title = paste(c("CPD", titleCaseFiltering,
+                                                 "5' Anchored Nuc Freq", repNames[i]), collapse = ' '),
                                  yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
-                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Nuc Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
+                                 expansionOffset = expansionOffset)
+}
 ```
@@
 ```{r CPD_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
-                               title = paste(c("CPD", titleCaseFiltering, "3' Anchored Purine Freq Rep1"), collapse = ' '),
+for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq[[i]], 
+                                 title = paste(c("CPD", titleCaseFiltering,
+                                                 "3' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                  yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                                  combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep2, 
-                               title = paste(c("CPD", titleCaseFiltering, "3' Anchored Purine Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+                                 posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
+                                 expansionOffset = expansionOffset)
+}
 
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
-                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Purine Freq Rep1"), collapse = ' '),
+for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]], 
+                                 title = paste(c("CPD", titleCaseFiltering,
+                                                 "5' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                  yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                                  combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
-                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Purine Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
+                                 expansionOffset = expansionOffset)
+}
 ```
@@
 ```{r 6-4_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
-                               title = paste(c("6-4", titleCaseFiltering, "3' Anchored Nuc Freq Rep1"), collapse = ' '),
+for (i in seq_along(threePrimeMismatchSixFourNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq[[i]], 
+                                 title = paste(c("6-4", titleCaseFiltering,
+                                                 "3' Anchored Nuc Freq", repNames[i]), collapse = ' '),
                                  secondaryYAxisLabel = "5' Cut Site Distance",
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
-                               title = paste(c("6-4", titleCaseFiltering, "3' Anchored Nuc Freq Rep2"), collapse = ' '),
-                               secondaryYAxisLabel = "5' Cut Site Distance",
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+                                 posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
+                                 expansionOffset = expansionOffset)
+}
 
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep1, 
-                               title = paste(c("6-4", titleCaseFiltering, "5' Anchored Nuc Freq Rep1"), collapse = ' '),
+for (i in seq_along(fivePrimeMismatchSixFourNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq[[i]], 
+                                 title = paste(c("6-4", titleCaseFiltering,
+                                                 "5' Anchored Nuc Freq", repNames[i]), collapse = ' '),
                                  yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep2, 
-                               title = paste(c("6-4", titleCaseFiltering, "5' Anchored Nuc Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
+                                 expansionOffset = expansionOffset)
+}
 ```
@@
 ```{r 6-4_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
-                               title = paste(c("6-4", titleCaseFiltering, "3' Anchored Purine Freq Rep1"), collapse = ' '),
+for (i in seq_along(threePrimeMismatchSixFourNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq[[i]], 
+                                 title = paste(c("6-4", titleCaseFiltering,
+                                                 "3' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                  yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                                  combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
-                               title = paste(c("6-4", titleCaseFiltering, "3' Anchored Purine Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+                                 posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
+                                 expansionOffset = expansionOffset)
+}
 
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep1, 
-                               title = paste(c("6-4", titleCaseFiltering, "5' Anchored Purine Freq Rep1"), collapse = ' '),
+for (i in seq_along(fivePrimeMismatchSixFourNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq[[i]], 
+                                 title = paste(c("6-4", titleCaseFiltering,
+                                                 "5' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                  yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                                  combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep2, 
-                               title = paste(c("6-4", titleCaseFiltering, "5' Anchored Purine Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
+                                 expansionOffset = expansionOffset)
+}
 ```
@@
 
-threePrimeMMAnchoredSixFourEnrichment = list(rep1 = sixFourTimepoints,
-                                             rep2 = sixFourTimepoints)
+threePrimeMMAnchoredSixFourEnrichment = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints,
+                                             all_reps = sixFourTimepoints)
 for (i in seq_along(threePrimeMMAnchoredSixFourEnrichment)) {
@@
 
-fivePrimeMMAnchoredSixFourEnrichment = list(rep1 = sixFourTimepoints,
-                                            rep2 = sixFourTimepoints)
+fivePrimeMMAnchoredSixFourEnrichment = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints,
+                                            all_reps = sixFourTimepoints)
 for (i in seq_along(fivePrimeMMAnchoredSixFourEnrichment)) {
@@
 ```{r CPD_sequence_enrichment, fig.width = 11, fig.height = 9}
-plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment$rep1,
-                       title = paste(c("CPD", titleCaseFiltering, "3' Anchored YR Enrichment Rep1"), collapse = ' '),
+for (i in seq_along(threePrimeMMAnchoredCPDEnrichment)) {
+  plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment[[i]],
+                         title = paste(c("CPD", titleCaseFiltering,
+                                         "3' Anchored YR Enrichment", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
-plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment$rep2,
-                       title = paste(c("CPD", titleCaseFiltering, "3' Anchored YR Enrichment Rep2"), collapse = ' '),
-                       secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
-                       expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
+}
 
-plotSequenceEnrichment(fivePrimeMMAnchoredCPDEnrichment$rep1,
-                       title = paste(c("CPD", titleCaseFiltering, "5' Anchored TGG Enrichment Rep1"), collapse = ' '),
+for (i in seq_along(fivePrimeMMAnchoredCPDEnrichment)) {
+  plotSequenceEnrichment(fivePrimeMMAnchoredCPDEnrichment[[i]],
+                         title = paste(c("CPD", titleCaseFiltering,
+                                         "5' Anchored TGG Enrichment", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
-plotSequenceEnrichment(fivePrimeMMAnchoredCPDEnrichment$rep2,
-                       title = paste(c("CPD", titleCaseFiltering, "5' Anchored TGG Enrichment Rep2"), collapse = ' '),
-                       secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
-                       expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
+}
 ```
@@
 ```{r 6-4_sequence_enrichment, fig.width = 11, fig.height = 9}
-plotSequenceEnrichment(threePrimeMMAnchoredSixFourEnrichment$rep1,
-                       title = paste(c("6-4", titleCaseFiltering, "3' Anchored YR Enrichment Rep1"), collapse = ' '),
+for (i in seq_along(threePrimeMMAnchoredSixFourEnrichment)) {
+  plotSequenceEnrichment(threePrimeMMAnchoredSixFourEnrichment[[i]],
+                         title = paste(c("6-4", titleCaseFiltering,
+                                         "3' Anchored YR Enrichment", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
-plotSequenceEnrichment(threePrimeMMAnchoredSixFourEnrichment$rep2,
-                       title = paste(c("6-4", titleCaseFiltering, "3' Anchored YR Enrichment Rep2"), collapse = ' '),
-                       secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
-                       expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
+}
 
-plotSequenceEnrichment(fivePrimeMMAnchoredSixFourEnrichment$rep1,
-                       title = paste(c("6-4", titleCaseFiltering, "5' Anchored TGG Enrichment Rep1"), collapse = ' '),
+for (i in seq_along(fivePrimeMMAnchoredSixFourEnrichment)) {
+  plotSequenceEnrichment(fivePrimeMMAnchoredSixFourEnrichment[[i]],
+                         title = paste(c("6-4", titleCaseFiltering,
+                                         "5' Anchored TGG Enrichment", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
-plotSequenceEnrichment(fivePrimeMMAnchoredSixFourEnrichment$rep2,
-                       title = paste(c("6-4", titleCaseFiltering, "5' Anchored TGG Enrichment Rep2"), collapse = ' '),
-                       secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
-                       expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
+}
 ```
@@
 
-threePrimeMMAnchoredSixFourSeqFreq = list(rep1 = sixFourTimepoints,
-                                          rep2 = sixFourTimepoints)
+threePrimeMMAnchoredSixFourSeqFreq = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints,
+                                          all_reps = sixFourTimepoints)
 for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
@@
 
-fivePrimeMMAnchoredSixFourSeqFreq = list(rep1 = sixFourTimepoints,
-                                         rep2 = sixFourTimepoints)
+fivePrimeMMAnchoredSixFourSeqFreq = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints,
+                                         all_reps = sixFourTimepoints)
 for (i in seq_along(fivePrimeMMAnchoredSixFourSeqFreq)) {
@@
 ```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 9}
-plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq$rep1,
-                        title = paste(c("CPD", titleCaseFiltering, "3' Anchored YR Freq Rep1"), collapse = ' '),
+for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]],
+                          title = paste(c("CPD", titleCaseFiltering,
+                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
                           secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                           expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
-plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq$rep2,
-                        title = paste(c("CPD", titleCaseFiltering, "3' Anchored YR Freq Rep2"), collapse = ' '),
-                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
-                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
+}
 
-plotSequenceFrequencies(fivePrimeMMAnchoredCPDSeqFreq$rep1,
-                        title = paste(c("CPD", titleCaseFiltering, "5' Anchored TGG Freq Rep1"), collapse = ' '),
+for (i in seq_along(fivePrimeMMAnchoredCPDSeqFreq)) {
+  plotSequenceFrequencies(fivePrimeMMAnchoredCPDSeqFreq[[i]],
+                          title = paste(c("CPD", titleCaseFiltering,
+                                          "5' Anchored TGG Freq", repNames[i]), collapse = ' '),
                           secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                           expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
-plotSequenceFrequencies(fivePrimeMMAnchoredCPDSeqFreq$rep2,
-                        title = paste(c("CPD", titleCaseFiltering, "5' Anchored TGG Freq Rep2"), collapse = ' '),
-                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
-                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
+}
 ```
@@
 ```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 9}
-plotSequenceFrequencies(threePrimeMMAnchoredSixFourSeqFreq$rep1,
-                        title = paste(c("6-4", titleCaseFiltering, "3' Anchored YR Freq Rep1"), collapse = ' '),
+for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredSixFourSeqFreq[[i]],
+                          title = paste(c("6-4", titleCaseFiltering,
+                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
                           secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                           expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
-plotSequenceFrequencies(threePrimeMMAnchoredSixFourSeqFreq$rep2,
-                        title = paste(c("6-4", titleCaseFiltering, "3' Anchored YR Freq Rep2"), collapse = ' '),
-                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
-                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
+}
 
-plotSequenceFrequencies(fivePrimeMMAnchoredSixFourSeqFreq$rep1,
-                        title = paste(c("6-4", titleCaseFiltering, "5' Anchored TGG Freq Rep1"), collapse = ' '),
+for (i in seq_along(fivePrimeMMAnchoredSixFourSeqFreq)) {
+  plotSequenceFrequencies(fivePrimeMMAnchoredSixFourSeqFreq[[i]],
+                          title = paste(c("6-4", titleCaseFiltering,
+                                          "5' Anchored TGG Freq", repNames[i]), collapse = ' '),
                           secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                           expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
-plotSequenceFrequencies(fivePrimeMMAnchoredSixFourSeqFreq$rep2,
-                        title = paste(c("6-4", titleCaseFiltering, "5' Anchored TGG Freq Rep2"), collapse = ' '),
-                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
-                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
+}
 ```

### 2022-06-15 R/NHF1DeaminationSequenceAndPositionDataGeneration.rmd
Update NHF1 notebooks
- Support for all_reps
- Read length counting occurs during data generation
- Temporarily removed chunks with adjusted y-axis from minimum read length filtering

@@
 
+```{r generate_and_write_read_length_counts}
+CPDReadLengthCounts = lapply(CPDMismatchData, function(x) lapply(
+  x, function(y) {
+    y[, .N, by = Read_Length][order(Read_Length)]
+  }
+))
+
+sixFourReadLengthCounts = lapply(sixFourMismatchData, function(x) lapply(
+  x, function(y) {
+    y[, .N, by = Read_Length][order(Read_Length)]
+  }
+))
+
+for (i in seq_along(CPDReadLengthCounts)) {
+  for (j in seq_along(CPDReadLengthCounts[[i]])) {
+    fwrite(CPDReadLengthCounts[[i]][[j]], sep = '\t', file = generateFilePath(
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
+      cellType = cellType, lesion = "CPD", repitition = names(CPDReadLengthCounts)[i],
+      timepoint = names(CPDReadLengthCounts[[i]])[j], filtering = filtering
+    ))
+  }
+}
+
+for (i in seq_along(sixFourReadLengthCounts)) {
+  for (j in seq_along(sixFourReadLengthCounts[[i]])) {
+    fwrite(sixFourReadLengthCounts[[i]][[j]], sep = '\t', file = generateFilePath(
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
+      cellType = cellType, lesion = "6-4", repitition = names(sixFourReadLengthCounts)[i],
+      timepoint = names(sixFourReadLengthCounts[[i]])[j], filtering = filtering
+    ))
+  }
+}
+```
+
 ```{r generate_and_write_mismatch_position_statistics_by_read_length_and_timepoint}
-CPDGroupedStats = list(rep1 = list(), rep2 = list())
-CPDGroupedStats$rep1$three_prime = getGroupedPositionStats(CPDMismatchData$rep1, includedTypes = c("C>T"))
-CPDGroupedStats$rep2$three_prime = getGroupedPositionStats(CPDMismatchData$rep2, includedTypes = c("C>T"))
-CPDGroupedStats$rep1$five_prime =
-  getGroupedPositionStats(CPDMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME)
-CPDGroupedStats$rep2$five_prime =
-  getGroupedPositionStats(CPDMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME)
+CPDGroupedStats = list(rep1 = list(), rep2 = list(), all_reps = list())
+for (i in seq_along(CPDGroupedStats)) {
+  CPDGroupedStats[[i]]$three_prime = getGroupedPositionStats(CPDMismatchData[[i]], includedTypes = c("C>T"))
+  CPDGroupedStats[[i]]$five_prime =
+    getGroupedPositionStats(CPDMismatchData[[i]], includedTypes = c("C>T"), posType = FIVE_PRIME)
+}
 
-sixFourGroupedStats = list(rep1 = list(), rep2 = list())
-sixFourGroupedStats$rep1$three_prime = getGroupedPositionStats(sixFourMismatchData$rep1, includedTypes = c("C>T"))
-sixFourGroupedStats$rep2$three_prime = getGroupedPositionStats(sixFourMismatchData$rep2, includedTypes = c("C>T"))
-sixFourGroupedStats$rep1$five_prime =
-  getGroupedPositionStats(sixFourMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME)
-sixFourGroupedStats$rep2$five_prime =
-  getGroupedPositionStats(sixFourMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME)
+sixFourGroupedStats = list(rep1 = list(), rep2 = list(), all_reps = list())
+for (i in seq_along(sixFourGroupedStats)) {
+  sixFourGroupedStats[[i]]$three_prime = getGroupedPositionStats(sixFourMismatchData[[i]], includedTypes = c("C>T"))
+  sixFourGroupedStats[[i]]$five_prime =
+    getGroupedPositionStats(sixFourMismatchData[[i]], includedTypes = c("C>T"), posType = FIVE_PRIME)
+}
 

### 2022-06-15 R/NHF1DeaminationSequenceAndPositionFigureGeneration.rmd
Update NHF1 notebooks
- Support for all_reps
- Read length counting occurs during data generation
- Temporarily removed chunks with adjusted y-axis from minimum read length filtering

--- 2022-05-20 R/NHF1DeaminationSequenceAndPositionFigureGeneration.rmd
@@
 sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
+repNames = c("rep1", "rep2", "all_reps")
+minReadLength = 22; maxReadLength = 30
 
@@
 
-sixFourMismatchData = list(rep1 = sixFourTimepoints,
-                           rep2 = sixFourTimepoints)
+sixFourMismatchData = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints, all_reps = sixFourTimepoints)
 for (i in seq_along(sixFourMismatchData)) {
@@
 ```{r CPD_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, includedTypes = c("C>T"),
-                                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
-                                                       collapse = ' '),
-                                         zScoreTables = CPDMMFreqZScores$rep1)
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, includedTypes = c("C>T"),
-                                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
-                                                       collapse = ' '),
-                                         zScoreTables = CPDMMFreqZScores$rep2)
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME,
-                                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
-                                                       collapse = ' '),
-                                         zScoreTables = CPDMMFreqZScores$rep1)
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME,
-                                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
-                                                       collapse = ' '),
-                                         zScoreTables = CPDMMFreqZScores$rep2)
+for (i in seq_along(CPDMismatchData)) {
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]], includedTypes = c("C>T"),
+                                           title = paste(c("CPD", titleCaseFiltering,
+                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
+                                           zScoreTables = CPDMMFreqZScores[[i]])
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]], includedTypes = c("C>T"), posType = FIVE_PRIME,
+                                           title = paste(c("CPD", titleCaseFiltering,
+                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
+                                           zScoreTables = CPDMMFreqZScores[[i]])
+}
 ```
@@
 ```{r 6-4_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, includedTypes = c("C>T"),
-                                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
-                                                       collapse = ' '),
-                                         zScoreTables = sixFourMMFreqZScores$rep1)
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, includedTypes = c("C>T"),
-                                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
-                                                       collapse = ' '),
-                                         zScoreTables = sixFourMMFreqZScores$rep2)
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME,
-                                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
-                                                       collapse = ' '),
-                                         zScoreTables = sixFourMMFreqZScores$rep1)
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME,
-                                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
-                                                       collapse = ' '),
-                                         zScoreTables = sixFourMMFreqZScores$rep2)
+for (i in seq_along(sixFourMismatchData)) {
+  plotPositionAcrossTimepointAndReadLength(sixFourMismatchData[[i]], includedTypes = c("C>T"),
+                                           title = paste(c("6-4", titleCaseFiltering,
+                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
+                                           zScoreTables = sixFourMMFreqZScores[[i]])
+  plotPositionAcrossTimepointAndReadLength(sixFourMismatchData[[i]], includedTypes = c("C>T"), posType = FIVE_PRIME,
+                                           title = paste(c("6-4", titleCaseFiltering,
+                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
+                                           zScoreTables = sixFourMMFreqZScores[[i]])
+}
+```
+
+```{r read_read_length_counts}
+CPDReadLengthCounts = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
+for (i in seq_along(CPDReadLengthCounts)) {
+  for (j in seq_along(CPDReadLengthCounts[[i]])) {
+    CPDReadLengthCounts[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
+      cellType = cellType, lesion = "CPD", repitition = names(CPDReadLengthCounts)[i],
+      timepoint = names(CPDReadLengthCounts[[i]])[j], filtering = filtering
+    ))
+  }
+}
+
+sixFourReadLengthCounts = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints, all_reps = sixFourTimepoints)
+for (i in seq_along(sixFourReadLengthCounts)) {
+  for (j in seq_along(sixFourReadLengthCounts[[i]])) {
+    sixFourReadLengthCounts[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
+      cellType = cellType, lesion = "6-4", repitition = names(sixFourReadLengthCounts)[i],
+      timepoint = names(sixFourReadLengthCounts[[i]])[j], filtering = filtering
+    ))
+  }
+}
 ```
@@
 ```{r CPD_read_length_distributions}
-plotReadLengthFrequencies(CPDMismatchData$rep1,
-                          title = paste(c("CPD", titleCaseFiltering, "Read Length Freq Rep 1"), collapse = ' '))
-plotReadLengthFrequencies(CPDMismatchData$rep2,
-                          title = paste(c("CPD", titleCaseFiltering, "Read Length Freq Rep 2"), collapse = ' '))
+for (i in seq_along(CPDReadLengthCounts)) {
+  plotReadLengthFrequencies(CPDReadLengthCounts[[i]],
+                            title = paste(c("CPD", titleCaseFiltering,
+                                            "Read Length Freq", repNames[i]), collapse = ' '))
+}
 ```
@@
 ```{r 6-4_read_length_distributions}
-plotReadLengthFrequencies(sixFourMismatchData$rep1,
-                          title = paste(c("6-4", titleCaseFiltering, "Read Length Freq Rep 1"), collapse = ' '))
-plotReadLengthFrequencies(sixFourMismatchData$rep2,
-                          title = paste(c("6-4", titleCaseFiltering, "Read Length Freq Rep 2"), collapse = ' '))
+for (i in seq_along(sixFourReadLengthCounts)) {
+  plotReadLengthFrequencies(sixFourReadLengthCounts[[i]],
+                            title = paste(c("6-4", titleCaseFiltering,
+                                            "Read Length Freq", repNames[i]), collapse = ' '))
+}
 ```
@@
 sixFourGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
-                           rep2 = list(three_prime = NULL, five_prime = NULL))
+                           rep2 = list(three_prime = NULL, five_prime = NULL),
+                           all_reps = list(three_prime = NULL, five_prime = NULL))
 for (i in seq_along(sixFourGroupedStats)) {
@@
 ```{r CPD_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
-plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, POS_DIFF,
-                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Diff Rep1"), collapse = ' '),
-                         xAxisBreaks = c(23:31))
-plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, POS_DIFF,
-                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Diff Rep2"), collapse = ' '),
-                         xAxisBreaks = c(23:31))
+for (i in seq_along(CPDGroupedStats)) {
+  plotGroupedPositionStats(CPDGroupedStats[[i]]$three_prime, CPDGroupedStats[[i]]$five_prime, POS_DIFF,
+                           title = paste(c("CPD", titleCaseFiltering,
+                                           "C>T Mismatch Pos Diff", repNames[i]), collapse = ' '),
+                           xAxisBreaks = c(minReadLength:maxReadLength))
+}
 ```
@@
 ```{r 6-4_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
-plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, POS_DIFF,
-                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Diff Rep1"), collapse = ' '),
-                         xAxisBreaks = c(23:31))
-plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, POS_DIFF,
-                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Diff Rep2"), collapse = ' '),
-                         xAxisBreaks = c(23:31))
+for (i in seq_along(sixFourGroupedStats)) {
+plotGroupedPositionStats(sixFourGroupedStats[[i]]$three_prime, sixFourGroupedStats[[i]]$five_prime, POS_DIFF,
+                         title = paste(c("6-4", titleCaseFiltering,
+                                         "C>T Mismatch Pos Diff", repNames[i]), collapse = ' '),
+                         xAxisBreaks = c(minReadLength:maxReadLength))
+}
 ```

### 2022-06-15 R/NHF1GeneralReadSequenceDataGeneration.rmd
Update NHF1 notebooks
- Support for all_reps
- Read length counting occurs during data generation
- Temporarily removed chunks with adjusted y-axis from minimum read length filtering

@@
 sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
+repNames = c("rep1", "rep2", "all_reps")
 minReadLength = 22; maxReadLength = 30
@@
 ```{r compute_and_write_CPD_sequence_frequency}
-for (repitition in c("rep1", "rep2")) {
+for (repitition in repNames) {
   for (timepoint in names(CPDTimepoints)) {
@@
 ```{r compute_and_write_6-4_sequence_frequency}
-for (repitition in c("rep1", "rep2")) {
+for (repitition in repNames) {
   for (timepoint in names(sixFourTimepoints)) {

### 2022-06-15 R/NHF1GeneralReadSequenceFigureGeneration.rmd
Update NHF1 notebooks
- Support for all_reps
- Read length counting occurs during data generation
- Temporarily removed chunks with adjusted y-axis from minimum read length filtering

--- 2022-05-24 R/NHF1GeneralReadSequenceFigureGeneration.rmd
@@
 
-sixFourTGGSeqFreq = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
+sixFourTGGSeqFreq = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints, all_reps = sixFourTimepoints)
 for (i in seq_along(sixFourTGGSeqFreq)) {
@@
 
-sixFourCGASeqFreq = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
+sixFourCGASeqFreq = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints, all_reps = sixFourTimepoints)
 for (i in seq_along(sixFourCGASeqFreq)) {
@@
 ```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 10}
-plotSequenceFrequencies(CPDTGGSeqFreq$rep1,
-                        title = "CPD TGG Frequencies Rep1", expansionOffset = expansionOffset,
+for (i in seq_along(CPDTGGSeqFreq)) {
+  plotSequenceFrequencies(CPDTGGSeqFreq[[i]],
+                          title = "CPD TGG Frequencies", repNames[i], expansionOffset = expansionOffset,
                           showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                           querySequences = c("TGG"))
-plotSequenceFrequencies(CPDTGGSeqFreq$rep2,
-                        title = "CPD TGG Frequencies Rep2", expansionOffset = expansionOffset,
-                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
-                        querySequences = c("TGG"))
+}
 
-plotSequenceFrequencies(CPDCGASeqFreq$rep1,
-                        title = "CPD CGA Frequencies Rep1", expansionOffset = expansionOffset,
+for (i in seq_along(CPDCGASeqFreq)) {
+  plotSequenceFrequencies(CPDCGASeqFreq[[i]],
+                          title = "CPD CGA Frequencies", repNames[i], expansionOffset = expansionOffset,
                           showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                           querySequences = c("CGA"))
-plotSequenceFrequencies(CPDCGASeqFreq$rep2,
-                        title = "CPD CGA Frequencies Rep2", expansionOffset = expansionOffset,
-                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
-                        querySequences = c("CGA"))
+}
 ```
@@
 ```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 10}
-plotSequenceFrequencies(sixFourTGGSeqFreq$rep1,
-                        title = "6-4 TGG Frequencies Rep1", expansionOffset = expansionOffset,
+for (i in seq_along(sixFourTGGSeqFreq)) {
+  plotSequenceFrequencies(sixFourTGGSeqFreq[[i]],
+                          title = "6-4 TGG Frequencies", repNames[i], expansionOffset = expansionOffset,
                           showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                           querySequences = c("TGG"))
-plotSequenceFrequencies(sixFourTGGSeqFreq$rep2,
-                        title = "6-4 TGG Frequencies Rep2", expansionOffset = expansionOffset,
-                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
-                        querySequences = c("TGG"))
+}
 
-plotSequenceFrequencies(sixFourCGASeqFreq$rep1,
-                        title = "6-4 CGA Frequencies Rep1", expansionOffset = expansionOffset,
+for (i in seq_along(sixFourCGASeqFreq)) {
+  plotSequenceFrequencies(sixFourCGASeqFreq[[i]],
+                          title = "6-4 CGA Frequencies", repNames[i], expansionOffset = expansionOffset,
                           showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                           querySequences = c("CGA"))
-plotSequenceFrequencies(sixFourCGASeqFreq$rep2,
-                        title = "6-4 CGA Frequencies Rep2", expansionOffset = expansionOffset,
-                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
-                        querySequences = c("CGA"))
+}
 ```
@@
 
-  readData = timepoints
-  for (i in seq_along(readData)) {
-    readData[[i]] = fread(generateFilePath(
-      generalReadSequenceDataDirectory, dataTypeStrings$alignedReads, ".bed",
-      cellType = cellType, lesion = lesion, timepoint = names(readData)[i],
-      repitition = repitition, expansionNum = expansionOffset
+  readLengthCountsByTimepoint = timepoints
+  for (i in seq_along(readLengthCountsByTimepoint)) {
+    readLengthCountsByTimepoint[[i]] = fread(generateFilePath(
+      generalReadSequenceDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
+      cellType = cellType, lesion = lesion, timepoint = names(readLengthCountsByTimepoint)[i],
+      repitition = repitition
     ))
-    readData[[i]] = data.table(Read_Length = nchar(readData[[i]]$V7)-expansionOffset*2,
-                               Timepoint = names(readData)[i])
-    readData[[i]] = readData[[i]][Read_Length >= 15 & Read_Length <= 31]
   }
 
-  plotReadLengthFrequencies(readData,
-                            title = paste(c(lesion, "Read Length Freq",
-                                            tools::toTitleCase(repitition)),
-                                          collapse = ' '))
+  plotReadLengthFrequencies(readLengthCountsByTimepoint,
+                            title = paste(lesion, "Read Length Freq", repitition))
 
@@
 ```{r 6-4_read_length_frequencies}
-readAndPlotReadLengthFrequencies("6-4", "rep1", sixFourTimepoints)
-readAndPlotReadLengthFrequencies("6-4", "rep2", sixFourTimepoints)
+for (rep in repNames) {
+readAndPlotReadLengthFrequencies("6-4", rep, sixFourTimepoints)
+}
 ```

### 2022-06-15 R/NHF1TandemDeaminationDataGeneration.rmd
Update NHF1 notebooks
- Support for all_reps
- Read length counting occurs during data generation
- Temporarily removed chunks with adjusted y-axis from minimum read length filtering

@@
 
+```{r generate_and_write_read_length_counts}
+CPDReadLengthCounts = lapply(CPDMismatchData, function(x) lapply(
+  x, function(y) {
+    y[, .N, by = Read_Length][order(Read_Length)]
+  }
+))
+
+sixFourReadLengthCounts = lapply(sixFourMismatchData, function(x) lapply(
+  x, function(y) {
+    y[, .N, by = Read_Length][order(Read_Length)]
+  }
+))
+
+for (i in seq_along(CPDReadLengthCounts)) {
+  for (j in seq_along(CPDReadLengthCounts[[i]])) {
+    fwrite(CPDReadLengthCounts[[i]][[j]], sep = '\t', file = generateFilePath(
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
+      cellType = cellType, lesion = "CPD", repitition = names(CPDReadLengthCounts)[i],
+      timepoint = names(CPDReadLengthCounts[[i]])[j], filtering = filtering, includedMismatches = mismatchType
+    ))
+  }
+}
+
+for (i in seq_along(sixFourReadLengthCounts)) {
+  for (j in seq_along(sixFourReadLengthCounts[[i]])) {
+    fwrite(sixFourReadLengthCounts[[i]][[j]], sep = '\t', file = generateFilePath(
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
+      cellType = cellType, lesion = "6-4", repitition = names(sixFourReadLengthCounts)[i],
+      timepoint = names(sixFourReadLengthCounts[[i]])[j], filtering = filtering, includedMismatches = mismatchType
+    ))
+  }
+}
+```
+
 ```{r generate_and_write_mismatch_position_statistics_by_read_length_and_timepoint}
-CPDGroupedStats = list(rep1 = list(), rep2 = list())
-CPDGroupedStats$rep1$three_prime = getGroupedPositionStats(CPDMismatchData$rep1)
-CPDGroupedStats$rep2$three_prime = getGroupedPositionStats(CPDMismatchData$rep2)
-CPDGroupedStats$rep1$five_prime = getGroupedPositionStats(CPDMismatchData$rep1, posType = FIVE_PRIME)
-CPDGroupedStats$rep2$five_prime = getGroupedPositionStats(CPDMismatchData$rep2, posType = FIVE_PRIME)
+CPDGroupedStats = list(rep1 = list(), rep2 = list(), all_reps = list())
+for (i in seq_along(CPDGroupedStats)) {
+  CPDGroupedStats[[i]]$three_prime = getGroupedPositionStats(CPDMismatchData[[i]])
+  CPDGroupedStats[[i]]$five_prime = getGroupedPositionStats(CPDMismatchData[[i]], posType = FIVE_PRIME)
+}
 
-sixFourGroupedStats = list(rep1 = list(), rep2 = list())
-sixFourGroupedStats$rep1$three_prime = getGroupedPositionStats(sixFourMismatchData$rep1)
-sixFourGroupedStats$rep2$three_prime = getGroupedPositionStats(sixFourMismatchData$rep2)
-sixFourGroupedStats$rep1$five_prime =
-  getGroupedPositionStats(sixFourMismatchData$rep1, posType = FIVE_PRIME)
-sixFourGroupedStats$rep2$five_prime =
-  getGroupedPositionStats(sixFourMismatchData$rep2, posType = FIVE_PRIME)
+sixFourGroupedStats = list(rep1 = list(), rep2 = list(), all_reps = list())
+for (i in seq_along(sixFourGroupedStats)) {
+  sixFourGroupedStats[[i]]$three_prime = getGroupedPositionStats(sixFourMismatchData[[i]])
+  sixFourGroupedStats[[i]]$five_prime =
+    getGroupedPositionStats(sixFourMismatchData[[i]], posType = FIVE_PRIME)
+}
 

### 2022-06-15 R/NHF1TandemDeaminationFigureGeneration.rmd
Update NHF1 notebooks
- Support for all_reps
- Read length counting occurs during data generation
- Temporarily removed chunks with adjusted y-axis from minimum read length filtering

--- 2022-06-06 R/NHF1TandemDeaminationFigureGeneration.rmd
@@
 library(knitr)
+library(stringr)
 
+expansionOffset = 10
 cellType = "NHF1"
-CPDTimepoints = list(`1h` = NULL)
-sixFourTimepoints = list(`1h` = NULL)
+CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
+sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
+repNames = c("rep1", "rep2", "all_reps")
 minReadLength = 22; maxReadLength = 30
@@
 ```{r CPD_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1,
+for (i in seq_along(CPDMismatchData)) {
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]],
                                            title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                                         "Mismatch Pos Freq Rep1"),
+                                                           "Mismatch Pos Freq", repNames[i]),
                                                          collapse = ' '),
-                                         zScoreTables = CPDMMFreqZScores$rep1)
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2,
+                                           zScoreTables = CPDMMFreqZScores[[i]])
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]], posType = FIVE_PRIME,
                                            title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                                         "Mismatch Pos Freq Rep2"),
+                                                           "Mismatch Pos Freq", repNames[i]),
                                                          collapse = ' '),
-                                         zScoreTables = CPDMMFreqZScores$rep2)
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep1, posType = FIVE_PRIME,
-                                         title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                                         "Mismatch Pos Freq Rep1"),
-                                                       collapse = ' '),
-                                         zScoreTables = CPDMMFreqZScores$rep1)
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData$rep2, posType = FIVE_PRIME,
-                                         title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                                         "Mismatch Pos Freq Rep2"),
-                                                       collapse = ' '),
-                                         zScoreTables = CPDMMFreqZScores$rep2)
+                                           zScoreTables = CPDMMFreqZScores[[i]])
+}
 ```
@@
 ```{r 6-4_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1,
+for (i in seq_along(sixFourMismatchData)) {
+  plotPositionAcrossTimepointAndReadLength(sixFourMismatchData[[i]],
                                            title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                                         "Mismatch Pos Freq Rep1"),
+                                                           "Mismatch Pos Freq", repNames[i]),
                                                          collapse = ' '),
-                                         zScoreTables = sixFourMMFreqZScores$rep1)
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2,
+                                           zScoreTables = sixFourMMFreqZScores[[i]])
+  plotPositionAcrossTimepointAndReadLength(sixFourMismatchData[[i]], posType = FIVE_PRIME,
                                            title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                                         "Mismatch Pos Freq Rep2"),
+                                                           "Mismatch Pos Freq", repNames[i]),
                                                          collapse = ' '),
-                                         zScoreTables = sixFourMMFreqZScores$rep2)
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, posType = FIVE_PRIME,
-                                         title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                                         "Mismatch Pos Freq Rep1"),
-                                                       collapse = ' '),
-                                         zScoreTables = sixFourMMFreqZScores$rep1)
-plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, posType = FIVE_PRIME,
-                                         title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                                         "Mismatch Pos Freq Rep2"),
-                                                       collapse = ' '),
-                                         zScoreTables = sixFourMMFreqZScores$rep2)
+                                           zScoreTables = sixFourMMFreqZScores[[i]])
+}
+```
+
+```{r read_read_length_counts}
+CPDReadLengthCounts = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
+for (i in seq_along(CPDReadLengthCounts)) {
+  for (j in seq_along(CPDReadLengthCounts[[i]])) {
+    CPDReadLengthCounts[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
+      cellType = cellType, lesion = "CPD", repitition = names(CPDReadLengthCounts)[i],
+      timepoint = names(CPDReadLengthCounts[[i]])[j], filtering = filtering, includedMismatches = mismatchType
+    ))
+  }
+}
+
+sixFourReadLengthCounts = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints, all_reps = sixFourTimepoints)
+for (i in seq_along(sixFourReadLengthCounts)) {
+  for (j in seq_along(sixFourReadLengthCounts[[i]])) {
+    sixFourReadLengthCounts[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
+      cellType = cellType, lesion = "6-4", repitition = names(sixFourReadLengthCounts)[i],
+      timepoint = names(sixFourReadLengthCounts[[i]])[j], filtering = filtering, includedMismatches = mismatchType
+    ))
+  }
+}
 ```
@@
 ```{r 6-4_read_length_distributions}
-plotReadLengthFrequencies(sixFourMismatchData$rep1,
+for (i in seq_along(sixFourReadLengthCounts)) {
+  plotReadLengthFrequencies(sixFourReadLengthCounts[[i]],
                             title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                          "Read Length Freq Rep1"), collapse = ' '))
-plotReadLengthFrequencies(sixFourMismatchData$rep2,
-                          title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                          "Read Length Freq Rep2"), collapse = ' '))
+                                            "Read Length Freq", repNames[i]), collapse = ' '))
+}
 ```
@@
 ```{r 6-4_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
-plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, POS_DIFF,
+for (i in seq_along(sixFourGroupedStats)) {
+  plotGroupedPositionStats(sixFourGroupedStats[[i]]$three_prime, sixFourGroupedStats[[i]]$five_prime, POS_DIFF,
                            title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                         "Mismatch Pos Diff Rep1"), collapse = ' '),
+                                           "Mismatch Pos Diff", repNames[i]), collapse = ' '),
                            xAxisBreaks = c(minReadLength:maxReadLength))
-plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, POS_DIFF,
+}
+```
+
+EXCISION SITE FIGURE GENERATION STARTS HERE
+
+```{r read_nucleotide_frequency_data}
+threePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL, all_reps = NULL)
+for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
+  threePrimeMismatchCPDNucFreq[[i]] = fread(generateFilePath(
+    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    cellType = cellType, lesion = "CPD", repitition = names(threePrimeMismatchCPDNucFreq)[i],
+    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
+  ))
+}
+
+fivePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL, all_reps = NULL)
+for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
+  fivePrimeMismatchCPDNucFreq[[i]] = fread(generateFilePath(
+    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMismatchCPDNucFreq)[i],
+    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
+  ))
+}
+
+threePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL, all_reps = NULL)
+for (i in seq_along(threePrimeMismatchSixFourNucFreq)) {
+  threePrimeMismatchSixFourNucFreq[[i]] = fread(generateFilePath(
+    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    cellType = cellType, lesion = "6-4", repitition = names(threePrimeMismatchSixFourNucFreq)[i],
+    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
+  ))
+}
+
+fivePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL, all_reps = NULL)
+for (i in seq_along(fivePrimeMismatchSixFourNucFreq)) {
+  fivePrimeMismatchSixFourNucFreq[[i]] = fread(generateFilePath(
+    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+    cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMismatchSixFourNucFreq)[i],
+    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
+  ))
+}
+```
+
+```{r CPD_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
+for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq[[i]], 
+                                 title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                                 "3' Anchored Nuc Freq", repNames[i]), collapse = ' '),
+                                 secondaryYAxisLabel = "5' Cut Site Distance", posType = THREE_PRIME,
+                                 showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
+
+for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]], 
+                                 title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                                 "5' Anchored Nuc Freq", repNames[i]), collapse = ' '),
+                                 secondaryYAxisLabel = "3' Cut Site Distance", posType = FIVE_PRIME,
+                                 showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
+```
+
+```{r CPD_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
+for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq[[i]], 
+                                 title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                                 "3' Anchored Purine Freq", repNames[i]), collapse = ' '),
+                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
+                                 combineNucleotides = c("AG"), combinedNames = c("Purine"), posType = THREE_PRIME,
+                                 showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
+
+for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]], 
+                                 title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                                 "5' Anchored Purine Freq", repNames[i]), collapse = ' '),
+                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                                 combineNucleotides = c("AG"), combinedNames = c("Purine"), posType = FIVE_PRIME,
+                                 showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
+```
+
+```{r 6-4_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
+for (i in seq_along(threePrimeMismatchSixFourNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq[[i]], 
                                  title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                         "Mismatch Pos Diff Rep2"), collapse = ' '),
-                         xAxisBreaks = c(minReadLength:maxReadLength))
+                                                 "3' Anchored Nuc Freq", repNames[i]), collapse = ' '),
+                                 secondaryYAxisLabel = "5' Cut Site Distance", posType = THREE_PRIME,
+                                 showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
+
+for (i in seq_along(fivePrimeMismatchSixFourNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq[[i]], 
+                                 title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
+                                                 "5' Anchored Nuc Freq", repNames[i]), collapse = ' '),
+                                 secondaryYAxisLabel = "3' Cut Site Distance", posType = FIVE_PRIME,
+                                 showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
 ```
+
+```{r 6-4_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
+for (i in seq_along(threePrimeMismatchSixFourNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq[[i]], 
+                                 title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
+                                                 "3' Anchored Purine Freq", repNames[i]), collapse = ' '),
+                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
+                                 combineNucleotides = c("AG"), combinedNames = c("Purine"), posType = THREE_PRIME,
+                                 showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
+
+for (i in seq_along(fivePrimeMismatchSixFourNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq[[i]], 
+                                 title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
+                                                 "5' Anchored Purine Freq", repNames[i]), collapse = ' '),
+                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                                 combineNucleotides = c("AG"), combinedNames = c("Purine"), posType = FIVE_PRIME,
+                                 showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
+```
+
+```{r read_sequence_frequency_data}
+threePrimeMMAnchoredCPDSeqFreq = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
+for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
+  for (j in seq_along(threePrimeMMAnchoredCPDSeqFreq[[i]])) {
+    threePrimeMMAnchoredCPDSeqFreq[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      cellType = cellType, lesion = "CPD", repitition = names(threePrimeMMAnchoredCPDSeqFreq)[i],
+      timepoint = names(threePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "three_prime",
+      anchored = TRUE, sequence = "YR", filtering = filtering, includedMismatches = mismatchType
+    ))
+  }
+}
+
+fivePrimeMMAnchoredCPDSeqFreq = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints, all_reps = CPDTimepoints)
+for (i in seq_along(fivePrimeMMAnchoredCPDSeqFreq)) {
+  for (j in seq_along(fivePrimeMMAnchoredCPDSeqFreq[[i]])) {
+    fivePrimeMMAnchoredCPDSeqFreq[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMMAnchoredCPDSeqFreq)[i],
+      timepoint = names(fivePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "five_prime",
+      anchored = TRUE, sequence = "TGG", filtering = filtering, includedMismatches = mismatchType
+    ))
+  }
+}
+
+threePrimeMMAnchoredSixFourSeqFreq = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints,
+                                          all_reps = sixFourTimepoints)
+for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
+  for (j in seq_along(threePrimeMMAnchoredSixFourSeqFreq[[i]])) {
+    threePrimeMMAnchoredSixFourSeqFreq[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      cellType = cellType, lesion = "6-4", repitition = names(threePrimeMMAnchoredSixFourSeqFreq)[i],
+      timepoint = names(threePrimeMMAnchoredSixFourSeqFreq[[i]])[j], strandPolarity = "three_prime",
+      anchored = TRUE, sequence = "YR", filtering = filtering, includedMismatches = mismatchType
+    ))
+  }
+}
+
+fivePrimeMMAnchoredSixFourSeqFreq = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints,
+                                         all_reps = sixFourTimepoints)
+for (i in seq_along(fivePrimeMMAnchoredSixFourSeqFreq)) {
+  for (j in seq_along(fivePrimeMMAnchoredSixFourSeqFreq[[i]])) {
+    fivePrimeMMAnchoredSixFourSeqFreq[[i]][[j]] = fread(generateFilePath(
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMMAnchoredSixFourSeqFreq)[i],
+      timepoint = names(fivePrimeMMAnchoredSixFourSeqFreq[[i]])[j], strandPolarity = "five_prime",
+      anchored = TRUE, sequence = "TGG", filtering = filtering, includedMismatches = mismatchType
+    ))
+  }
+}
+```
+
+```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 9}
+for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]],
+                          title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
+                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
+}
+
+for (i in seq_along(fivePrimeMMAnchoredCPDSeqFreq)) {
+  plotSequenceFrequencies(fivePrimeMMAnchoredCPDSeqFreq[[i]],
+                          title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                          "5' Anchored TGG Freq", repNames[i]), collapse = ' '),
+                          secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
+                          expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
+}
+```
+
+```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 9}
+for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredSixFourSeqFreq[[i]],
+                          title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
+                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
+                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
+}
+
+for (i in seq_along(fivePrimeMMAnchoredSixFourSeqFreq)) {
+  plotSequenceFrequencies(fivePrimeMMAnchoredSixFourSeqFreq[[i]],
+                          title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
+                                          "5' Anchored TGG Freq", repNames[i]), collapse = ' '),
+                          secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
+                          expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
+}
+```

### 2022-06-15 R/CS-BDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Update CS-B notebooks
- Support for all_reps
- Read length counting occurs during data generation

@@
 sixFourTimepoints = list(`1h` = NULL)
+repNames = c("rep1", "rep2", "all_reps")
 

### 2022-06-15 R/CS-BDeaminationSequenceAndPositionFigureGeneration.rmd
Update CS-B notebooks
- Support for all_reps
- Read length counting occurs during data generation

--- 2022-05-31 R/CS-BDeaminationSequenceAndPositionFigureGeneration.rmd
@@
 sixFourTimepoints = list(`1h` = NULL)
+repNames = c("rep1", "rep2", "all_reps")
 minReadLength = 22; maxReadLength = 30
@@
 ```{r CPD_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
-plotGroupedPositionStats(CPDGroupedStats$rep1$three_prime, CPDGroupedStats$rep1$five_prime, POS_DIFF,
-                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Diff Rep1"), collapse = ' '),
+for (i in seq_along(CPDGroupedStats)) {
+  plotGroupedPositionStats(CPDGroupedStats[[i]]$three_prime, CPDGroupedStats[[i]]$five_prime, POS_DIFF,
+                           title = paste(c("CPD", titleCaseFiltering,
+                                           "C>T Mismatch Pos Diff", repNames[i]), collapse = ' '),
                            xAxisBreaks = c(minReadLength:maxReadLength))
-plotGroupedPositionStats(CPDGroupedStats$rep2$three_prime, CPDGroupedStats$rep2$five_prime, POS_DIFF,
-                         title = paste(c("CPD", titleCaseFiltering, "C>T Mismatch Pos Diff Rep2"), collapse = ' '),
-                         xAxisBreaks = c(minReadLength:maxReadLength))
+}
 ```
@@
 ```{r 6-4_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
-plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, POS_DIFF,
-                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Diff Rep1"), collapse = ' '),
+for (i in seq_along(sixFourGroupedStats)) {
+plotGroupedPositionStats(sixFourGroupedStats[[i]]$three_prime, sixFourGroupedStats[[i]]$five_prime, POS_DIFF,
+                         title = paste(c("6-4", titleCaseFiltering,
+                                         "C>T Mismatch Pos Diff", repNames[i]), collapse = ' '),
                          xAxisBreaks = c(minReadLength:maxReadLength))
-plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, POS_DIFF,
-                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Diff Rep2"), collapse = ' '),
-                         xAxisBreaks = c(minReadLength:maxReadLength))
+}
 ```

### 2022-06-15 R/CS-BTandemDeaminationFigureGeneration.rmd
Update CS-B notebooks
- Support for all_reps
- Read length counting occurs during data generation

@@
 ```{r 6-4_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
-plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, POS_DIFF,
+for (i in seq_along(sixFourGroupedStats)) {
+  plotGroupedPositionStats(sixFourGroupedStats[[i]]$three_prime, sixFourGroupedStats[[i]]$five_prime, POS_DIFF,
                            title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                         "Mismatch Pos Diff Rep1"), collapse = ' '),
+                                           "Mismatch Pos Diff", repNames[i]), collapse = ' '),
                            xAxisBreaks = c(minReadLength:maxReadLength))
-plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, POS_DIFF,
-                         title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                         "Mismatch Pos Diff Rep2"), collapse = ' '),
-                         xAxisBreaks = c(minReadLength:maxReadLength))
+}
 ```
@@
 ```{r CPD_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
+for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq[[i]], 
                                  title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                               "3' Anchored Nuc Freq Rep1"), collapse = ' '),
-                               secondaryYAxisLabel = "5' Cut Site Distance",
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep2, 
+                                                 "3' Anchored Nuc Freq", repNames[i]), collapse = ' '),
+                                 secondaryYAxisLabel = "5' Cut Site Distance", posType = THREE_PRIME,
+                                 showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
+
+for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]], 
                                  title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                               "3' Anchored Nuc Freq Rep2"), collapse = ' '),
-                               secondaryYAxisLabel = "5' Cut Site Distance",
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
-                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                               "5' Anchored Nuc Freq Rep1"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
-                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                               "5' Anchored Nuc Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+                                                 "5' Anchored Nuc Freq", repNames[i]), collapse = ' '),
+                                 secondaryYAxisLabel = "3' Cut Site Distance", posType = FIVE_PRIME,
+                                 showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
 ```
@@
 ```{r CPD_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
+for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq[[i]], 
                                  title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                               "3' Anchored Purine Freq Rep1"), collapse = ' '),
+                                                 "3' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                  yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep2, 
+                                 combineNucleotides = c("AG"), combinedNames = c("Purine"), posType = THREE_PRIME,
+                                 showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
+
+for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]], 
                                  title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                               "3' Anchored Purine Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
-                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                               "5' Anchored Purine Freq Rep1"), collapse = ' '),
+                                                 "5' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                  yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
-                               title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
-                                               "5' Anchored Purine Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+                                 combineNucleotides = c("AG"), combinedNames = c("Purine"), posType = FIVE_PRIME,
+                                 showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
 ```
@@
 ```{r 6-4_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
+for (i in seq_along(threePrimeMismatchSixFourNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq[[i]], 
                                  title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                               "3' Anchored Nuc Freq Rep1"), collapse = ' '),
-                               secondaryYAxisLabel = "5' Cut Site Distance",
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
+                                                 "3' Anchored Nuc Freq", repNames[i]), collapse = ' '),
+                                 secondaryYAxisLabel = "5' Cut Site Distance", posType = THREE_PRIME,
+                                 showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
+
+for (i in seq_along(fivePrimeMismatchSixFourNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq[[i]], 
                                  title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                               "3' Anchored Nuc Freq Rep2"), collapse = ' '),
-                               secondaryYAxisLabel = "5' Cut Site Distance",
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep1, 
-                               title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                               "5' Anchored Nuc Freq Rep1"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep2, 
-                               title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                               "5' Anchored Nuc Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+                                                 "5' Anchored Nuc Freq", repNames[i]), collapse = ' '),
+                                 secondaryYAxisLabel = "3' Cut Site Distance", posType = FIVE_PRIME,
+                                 showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
 ```
@@
 ```{r 6-4_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
+for (i in seq_along(threePrimeMismatchSixFourNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq[[i]], 
                                  title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                               "3' Anchored Purine Freq Rep1"), collapse = ' '),
+                                                 "3' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                  yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
+                                 combineNucleotides = c("AG"), combinedNames = c("Purine"), posType = THREE_PRIME,
+                                 showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
+
+for (i in seq_along(fivePrimeMismatchSixFourNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq[[i]], 
                                  title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                               "3' Anchored Purine Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep1, 
-                               title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                               "5' Anchored Purine Freq Rep1"), collapse = ' '),
+                                                 "5' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                  yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
-plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep2, 
-                               title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                               "5' Anchored Purine Freq Rep2"), collapse = ' '),
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+                                 combineNucleotides = c("AG"), combinedNames = c("Purine"), posType = FIVE_PRIME,
+                                 showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
+}
 ```
@@
 ```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 9}
-plotSequenceFrequencies(threePrimeMMAnchoredSixFourSeqFreq$rep1,
+for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredSixFourSeqFreq[[i]],
                           title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                        "3' Anchored YR Freq Rep1"), collapse = ' '),
+                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
                           secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                           expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
-plotSequenceFrequencies(threePrimeMMAnchoredSixFourSeqFreq$rep2,
+}
+
+for (i in seq_along(fivePrimeMMAnchoredSixFourSeqFreq)) {
+  plotSequenceFrequencies(fivePrimeMMAnchoredSixFourSeqFreq[[i]],
                           title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                        "3' Anchored YR Freq Rep2"), collapse = ' '),
-                        secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
-                        expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
-
-plotSequenceFrequencies(fivePrimeMMAnchoredSixFourSeqFreq$rep1,
-                        title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                        "5' Anchored TGG Freq Rep1"), collapse = ' '),
+                                          "5' Anchored TGG Freq", repNames[i]), collapse = ' '),
                           secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                           expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
-plotSequenceFrequencies(fivePrimeMMAnchoredSixFourSeqFreq$rep2,
-                        title = paste(c("6-4", titleCaseFiltering, titleCaseMismatchType,
-                                        "5' Anchored TGG Freq Rep2"), collapse = ' '),
-                        secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
-                        expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
+}
 ```

### 2022-06-15 R/YeastDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Update yeast notebooks
- Support for all_reps
- Read length counting occurs during data generation

@@
 sixFourTimepoints = list(`5min` = NULL, `20min` = NULL)
+repNames = c("rep1", "rep2", "all_reps")
 minReadLength = 22; maxReadLength = 25

### 2022-06-15 R/CS-BGeneralReadSequenceFigureGeneration.rmd
Title text bugfix
Title was not pasted and was instead given as two arguments... Whoops!

@@
 for (i in seq_along(CPDTGGSeqFreq)) {
-  plotSequenceFrequencies(CPDTGGSeqFreq[[i]],
-                          title = "CPD TGG Frequencies", repNames[i], expansionOffset = expansionOffset,
-                          showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
-                          querySequences = c("TGG"))
+  plotSequenceFrequencies(CPDTGGSeqFreq[[i]], title = paste("CPD TGG Frequencies", repNames[i]),
+                          expansionOffset = expansionOffset, showThreePrimeCutSite = TRUE,
+                          showFivePrimeCutSite = TRUE, querySequences = c("TGG"))
 }
@@
 for (i in seq_along(CPDCGASeqFreq)) {
-  plotSequenceFrequencies(CPDCGASeqFreq[[i]],
-                          title = "CPD CGA Frequencies", repNames[i], expansionOffset = expansionOffset,
-                          showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
-                          querySequences = c("CGA"))
+  plotSequenceFrequencies(CPDCGASeqFreq[[i]], title = paste("CPD CGA Frequencies", repNames[i]),
+                          expansionOffset = expansionOffset, showThreePrimeCutSite = TRUE,
+                          showFivePrimeCutSite = TRUE, querySequences = c("CGA"))
 }
@@
 for (i in seq_along(sixFourTGGSeqFreq)) {
-  plotSequenceFrequencies(sixFourTGGSeqFreq[[i]],
-                          title = "6-4 TGG Frequencies", repNames[i], expansionOffset = expansionOffset,
-                          showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
-                          querySequences = c("TGG"))
+  plotSequenceFrequencies(sixFourTGGSeqFreq[[i]], title = paste("6-4 TGG Frequencies", repNames[i]),
+                          expansionOffset = expansionOffset, showThreePrimeCutSite = TRUE,
+                          showFivePrimeCutSite = TRUE, querySequences = c("TGG"))
 }
@@
 for (i in seq_along(sixFourCGASeqFreq)) {
-  plotSequenceFrequencies(sixFourCGASeqFreq[[i]],
-                          title = "6-4 CGA Frequencies", repNames[i], expansionOffset = expansionOffset,
-                          showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
-                          querySequences = c("CGA"))
+  plotSequenceFrequencies(sixFourCGASeqFreq[[i]], title = paste("6-4 CGA Frequencies", repNames[i]),
+                          expansionOffset = expansionOffset, showThreePrimeCutSite = TRUE,
+                          showFivePrimeCutSite = TRUE, querySequences = c("CGA"))
 }

### 2022-06-15 R/CS-BDeaminationSequenceAndPositionFigureGeneration.rmd
Restored custom plotting options
These options were lost during the refactoring for combined repetitions.

@@
                                                            "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
-                                           zScoreTables = CPDMMFreqZScores[[i]])
+                                           zScoreTables = CPDMMFreqZScores[[i]], yAxisBreaks = c(0, 0.16, 0.32))
   plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]], includedTypes = c("C>T"), posType = FIVE_PRIME,
@@
                                                            "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
-                                           zScoreTables = CPDMMFreqZScores[[i]])
+                                           zScoreTables = CPDMMFreqZScores[[i]], yAxisBreaks = c(0, 0.16, 0.32))
 }

### 2022-06-15 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
Restored custom plotting options
These options were lost during the refactoring for combined repetitions.

@@
                                  expansionOffset = expansionOffset)
+}
+```
+
+```{r CPD_mismatch_anchored_nucleotide_frequencies_filtered, fig.width = 11, fig.height = 8}
+min3PrimeCutSiteDistance = 1
+max3PrimeCutSiteDistance = 12
+
+for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]], 
+                                 title = paste(c("CPD", titleCaseFiltering,
+                                                 "5' Anchored Nuc Freq", repNames[i]), collapse = ' '),
+                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
+                                 expansionOffset = expansionOffset,
+                                 minReadLength = min3PrimeCutSiteDistance, maxReadLength = max3PrimeCutSiteDistance)
 }

### 2022-06-15 R/NHF1GeneralReadSequenceFigureGeneration.rmd
Restored custom plotting options
These options were lost during the refactoring for combined repetitions.

@@
 
+```{r CPD_sequence_frequencies_filtered, fig.width = 11, fig.height = 9}
+minReadLength = 18
+for (i in seq_along(CPDTGGSeqFreq)) {
+  plotSequenceFrequencies(CPDTGGSeqFreq[[i]], title = paste("CPD TGG Frequencies", repNames[i]),
+                          expansionOffset = expansionOffset, showThreePrimeCutSite = TRUE,
+                          showFivePrimeCutSite = TRUE, querySequences = c("TGG"), minReadLength = minReadLength)
+}
+
+for (i in seq_along(CPDCGASeqFreq)) {
+  plotSequenceFrequencies(CPDCGASeqFreq[[i]], title = paste("CPD CGA Frequencies", repNames[i]),
+                          expansionOffset = expansionOffset, showThreePrimeCutSite = TRUE,
+                          showFivePrimeCutSite = TRUE, querySequences = c("CGA"), minReadLength = minReadLength)
+}
+```
+
 ```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 10}

### 2022-06-15 R/DeaminationSequenceAndPositionAnalysis.R
More intelligent plot coloring and legend

@@ -300,7 +300,9 @@ plotGroupedPositionStats = function(threePrimeGroupedStats, fivePrimeGroupedStat
   if (all(aggregateData$Timepoint == "NONE")) {
     groupedStatsPlot = groupedStatsPlot +
       scale_color_grey(guide = "none")
-  } else groupedStatsPlot = groupedStatsPlot + scale_color_brewer(palette = "Set1")
+  } else if (length(unique(aggregateData$Timepoint)) == 1) {
+    groupedStatsPlot = groupedStatsPlot + scale_color_grey()
+  } groupedStatsPlot = groupedStatsPlot + scale_color_brewer(palette = "Set1")
 
   print(groupedStatsPlot)
 

### 2022-06-15 R/ArabidopsisDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Added various filtered plots

@@
 ```
+
+```{r CPD_sequence_frequencies_filtered, fig.width = 5, fig.height = 8}
+min5PrimeCutSiteDistance = 15
+max5PrimeCutSiteDistance = 25
+for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]]$ZT2,
+                          title = paste(c("CPD", titleCaseFiltering,
+                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
+                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
+                          minReadLength = min5PrimeCutSiteDistance,
+                          max5PrimeCutSiteDistance = max5PrimeCutSiteDistance)
+}
+```

### 2022-06-15 R/ArabidopsisDeaminationSequenceAndPositionFigureGeneration.rmd
Added various filtered plots

@@
 
+```{r CPD_mismatch_position_frequencies_by_read_length_filtered, fig.width = 5, fig.height = 5}
+for (i in seq_along(CPDMismatchData)) {
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]$`ZT2`, includedTypes = c("C>T"),
+                                           title = paste(c("CPD", titleCaseFiltering,
+                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
+                                           zScoreTables = CPDMMFreqZScores[[i]])
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]$`ZT2`, includedTypes = c("C>T"),
+                                           title = paste(c("CPD", titleCaseFiltering,
+                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
+                                           zScoreTables = CPDMMFreqZScores[[i]], posType = FIVE_PRIME)
+}
+```
+
 ```{r read_read_length_counts}
@@
 ```
+
+```{r CPD_position_differences_across_read_lengths_filtered, fig.width = 9, fig.height = 5}
+for (i in seq_along(CPDGroupedStats)) {
+  plotGroupedPositionStats(CPDGroupedStats[[i]]$three_prime[Timepoint == "ZT2"],
+                           CPDGroupedStats[[i]]$five_prime[Timepoint == "ZT2"],
+                           POS_DIFF, title = paste(c("CPD", titleCaseFiltering,
+                                                     "C>T Mismatch Pos Diff", repNames[i]), collapse = ' '),
+                           xAxisBreaks = c(minReadLength:maxReadLength))
+}
+```

### 2022-06-15 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
Added various filtered plots

@@
 
+```{r CPD_mismatch_anchored_nucleotide_frequencies_filtered_x2, fig.width = 5, fig.height = 8}
+min3PrimeCutSiteDistance = 1
+max3PrimeCutSiteDistance = 12
+
+for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]][Timepoint == "1h"], 
+                                 title = paste(c("CPD", titleCaseFiltering,
+                                                 "5' Anchored Nuc Freq", repNames[i]), collapse = ' '),
+                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
+                                 expansionOffset = expansionOffset,
+                                 minReadLength = min3PrimeCutSiteDistance, maxReadLength = max3PrimeCutSiteDistance)
+}
+```
+
 ```{r CPD_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
@@
                                  expansionOffset = expansionOffset)
+}
+```
+
+```{r CPD_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
+min5PrimeCutSiteDistance = 13
+max5PrimeCutSiteDistance = 25
+
+for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]], 
+                                 title = paste(c("CPD", titleCaseFiltering,
+                                                 "5' Anchored Purine Freq", repNames[i]), collapse = ' '),
+                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                                 combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
+                                 expansionOffset = expansionOffset,
+                                 minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
+}
+```
+
+```{r CPD_mismatch_anchored_purine_frequencies_x2, fig.width = 5, fig.height = 9}
+min5PrimeCutSiteDistance = 13
+max5PrimeCutSiteDistance = 25
+
+for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]][Timepoint == "1h"], 
+                                 title = paste(c("CPD", titleCaseFiltering,
+                                                 "5' Anchored Purine Freq", repNames[i]), collapse = ' '),
+                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                                 combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
+                                 expansionOffset = expansionOffset,
+                                 minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
 }
@@
 
+```{r CPD_sequence_frequencies_filtered, fig.width = 11, fig.height = 8}
+min5PrimeCutSiteDistance = 13
+max5PrimeCutSiteDistance = 25
+for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]],
+                          title = paste(c("CPD", titleCaseFiltering,
+                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
+                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
+                          minReadLength = min5PrimeCutSiteDistance,
+                          max5PrimeCutSiteDistance = max5PrimeCutSiteDistance)
+}
+```
+
+```{r CPD_sequence_frequencies_filtered_x2, fig.width = 5, fig.height = 8}
+min5PrimeCutSiteDistance = 13
+max5PrimeCutSiteDistance = 25
+for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]]$`1h`,
+                          title = paste(c("CPD", titleCaseFiltering,
+                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
+                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
+                          minReadLength = min5PrimeCutSiteDistance,
+                          max5PrimeCutSiteDistance = max5PrimeCutSiteDistance)
+}
+```
+
 ```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 9}

### 2022-06-15 R/NHF1DeaminationSequenceAndPositionFigureGeneration.rmd
Added various filtered plots

@@
 
+```{r CPD_mismatch_position_frequencies_by_read_length_filtered, fig.width = 5, fig.height = 5}
+for (i in seq_along(CPDMismatchData)) {
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]$`1h`, includedTypes = c("C>T"),
+                                           title = paste(c("CPD", titleCaseFiltering,
+                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
+                                           zScoreTables = CPDMMFreqZScores[[i]])
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]$`1h`, includedTypes = c("C>T"), posType = FIVE_PRIME,
+                                           title = paste(c("CPD", titleCaseFiltering,
+                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
+                                           zScoreTables = CPDMMFreqZScores[[i]])
+}
+```
+
 ```{r 6-4_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
@@
 
+```{r CPD_position_differences_across_read_lengths_filtered, fig.width = 9, fig.height = 5}
+for (i in seq_along(CPDGroupedStats)) {
+  plotGroupedPositionStats(CPDGroupedStats[[i]]$three_prime[Timepoint == "1h"],
+                           CPDGroupedStats[[i]]$five_prime[Timepoint == "1h"],
+                           POS_DIFF, title = paste(c("CPD", titleCaseFiltering,
+                                                     "C>T Mismatch Pos Diff", repNames[i]), collapse = ' '),
+                           xAxisBreaks = c(minReadLength:maxReadLength))
+}
+```
+
 ```{r 6-4_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}

### 2022-06-15 R/NHF1GeneralReadSequenceFigureGeneration.rmd
Added various filtered plots

@@
 
+```{r CPD_sequence_frequencies_filtered_x2, fig.width = 5, fig.height = 9}
+minReadLength = 18
+for (i in seq_along(CPDTGGSeqFreq)) {
+  plotSequenceFrequencies(CPDTGGSeqFreq[[i]]$`1h`, title = paste("CPD TGG Frequencies", repNames[i]),
+                          expansionOffset = expansionOffset, showThreePrimeCutSite = TRUE,
+                          showFivePrimeCutSite = TRUE, querySequences = c("TGG"), minReadLength = minReadLength)
+}
+
+for (i in seq_along(CPDCGASeqFreq)) {
+  plotSequenceFrequencies(CPDCGASeqFreq[[i]]$`1h`, title = paste("CPD CGA Frequencies", repNames[i]),
+                          expansionOffset = expansionOffset, showThreePrimeCutSite = TRUE,
+                          showFivePrimeCutSite = TRUE, querySequences = c("CGA"), minReadLength = minReadLength)
+}
+```
+
 ```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 10}

### 2022-06-15 R/YeastDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Added various filtered plots

@@
 
+```{r CPD_sequence_frequencies_filtered, fig.width = 11, fig.height = 8}
+min5PrimeCutSiteDistance = 11
+max5PrimeCutSiteDistance = 19
+for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]],
+                          title = paste(c("CPD", titleCaseFiltering,
+                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
+                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
+                          minReadLength = min5PrimeCutSiteDistance,
+                          max5PrimeCutSiteDistance = max5PrimeCutSiteDistance)
+}
+```
+
+```{r CPD_sequence_frequencies_filtered_x2, fig.width = 5, fig.height = 8}
+min5PrimeCutSiteDistance = 11
+max5PrimeCutSiteDistance = 19
+for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]]$`20min`,
+                          title = paste(c("CPD", titleCaseFiltering,
+                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
+                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
+                          minReadLength = min5PrimeCutSiteDistance,
+                          max5PrimeCutSiteDistance = max5PrimeCutSiteDistance)
+}
+```
+
 ```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 9}

### 2022-06-15 R/YeastDeaminationSequenceAndPositionFigureGeneration.rmd
Added various filtered plots

@@
 
+```{r CPD_mismatch_position_frequencies_by_read_length_filtered, fig.width = 5, fig.height = 5}
+for (i in seq_along(CPDMismatchData)) {
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]$`20min`, includedTypes = c("C>T"),
+                                           title = paste(c("CPD", titleCaseFiltering,
+                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
+                                           zScoreTables = CPDMMFreqZScores[[i]])
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]$`20min`, includedTypes = c("C>T"),
+                                           title = paste(c("CPD", titleCaseFiltering,
+                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
+                                           zScoreTables = CPDMMFreqZScores[[i]], posType = FIVE_PRIME)
+}
+```
+
 ```{r 6-4_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
@@
 
+```{r CPD_position_differences_across_read_lengths_filtered, fig.width = 9, fig.height = 5}
+for (i in seq_along(CPDGroupedStats)) {
+  plotGroupedPositionStats(CPDGroupedStats[[i]]$three_prime[Timepoint == "20min"],
+                           CPDGroupedStats[[i]]$five_prime[Timepoint == "20min"],
+                           POS_DIFF, title = paste(c("CPD", titleCaseFiltering,
+                                                     "C>T Mismatch Pos Diff", repNames[i]), collapse = ' '),
+                           xAxisBreaks = c(minReadLength:maxReadLength))
+}
+```
+
 ```{r 6-4_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}

### 2022-06-16 R/DeaminationSequenceAndPositionAnalysis.R
Bugfixes
- Fixed missing "else" statement
- Fixed a bug where a smaller mismatch table would produce NA's when paired with a larger z-score table. (Made it an inner join)

@@ -123,7 +123,7 @@ plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTy
                                             function(i) zScoreTables[[i]][,Timepoint := names(zScoreTables)[i]]))
     setkey(groupedPositionFrequencies,Position,Read_Length,Timepoint)
     setkey(aggregateZScoreTable,Position,Read_Length,Timepoint)
-    groupedPositionFrequencies = groupedPositionFrequencies[aggregateZScoreTable]
+    groupedPositionFrequencies = groupedPositionFrequencies[aggregateZScoreTable, nomatch = NULL]
     groupedPositionFrequencies[,Meets_Cutoff := Z_Score >= zScoreCutoff]
   }
 
@@ -302,7 +302,7 @@ plotGroupedPositionStats = function(threePrimeGroupedStats, fivePrimeGroupedStat
       scale_color_grey(guide = "none")
   } else if (length(unique(aggregateData$Timepoint)) == 1) {
     groupedStatsPlot = groupedStatsPlot + scale_color_grey()
-  } groupedStatsPlot = groupedStatsPlot + scale_color_brewer(palette = "Set1")
+  } else groupedStatsPlot = groupedStatsPlot + scale_color_brewer(palette = "Set1")
 
   print(groupedStatsPlot)
 

### 2022-06-16 R/ArabidopsisDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Various tweaks, bugfixes, and additional filtering

--- 2022-06-14 R/ArabidopsisDeaminationAnchoredExcisionSiteFigureGeneration.rmd
@@
 ```
+
+```{r CPD_sequence_frequencies_filtered, fig.width = 11, fig.height = 8}
+min5PrimeCutSiteDistance = 15
+max5PrimeCutSiteDistance = 25
+for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]],
+                          title = paste(c("CPD", titleCaseFiltering,
+                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
+                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
+                          minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
+}
+```
+
+```{r CPD_sequence_frequencies_filtered_x2, fig.width = 5, fig.height = 8}
+min5PrimeCutSiteDistance = 15
+max5PrimeCutSiteDistance = 25
+for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]]$ZT2,
+                          title = paste(c("CPD", titleCaseFiltering,
+                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
+                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
+                          minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
+}
+```

### 2022-06-16 R/ArabidopsisDeaminationSequenceAndPositionFigureGeneration.rmd
Various tweaks, bugfixes, and additional filtering

--- 2022-06-14 R/ArabidopsisDeaminationSequenceAndPositionFigureGeneration.rmd
@@
 
+```{r CPD_mismatch_position_frequencies_by_read_length_filtered, fig.width = 5, fig.height = 5}
+for (i in seq_along(CPDMismatchData)) {
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["ZT2"], includedTypes = c("C>T"),
+                                           title = paste(c("CPD", titleCaseFiltering,
+                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
+                                           zScoreTables = CPDMMFreqZScores[[i]])
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["ZT2"], includedTypes = c("C>T"),
+                                           title = paste(c("CPD", titleCaseFiltering,
+                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
+                                           zScoreTables = CPDMMFreqZScores[[i]], posType = FIVE_PRIME)
+}
+```
+
 ```{r read_read_length_counts}

### 2022-06-16 R/ArabidopsisTandemDeaminationFigureGeneration.rmd
Various tweaks, bugfixes, and additional filtering

@@
   plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]], posType = FIVE_PRIME,
+                                           title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                                           "Mismatch Pos Freq", repNames[i]),
+                                                         collapse = ' '),
+                                           zScoreTables = CPDMMFreqZScores[[i]])
+}
+```
+
+```{r CPD_mismatch_position_frequencies_by_read_length_filtered, fig.width = 5, fig.height = 5}
+for (i in seq_along(CPDMismatchData)) {
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["ZT2"],
+                                           title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                                           "Mismatch Pos Freq", repNames[i]),
+                                                         collapse = ' '),
+                                           zScoreTables = CPDMMFreqZScores[[i]])
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["ZT2"], posType = FIVE_PRIME,
                                            title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,

### 2022-06-16 R/CS-BDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Various tweaks, bugfixes, and additional filtering

@@
 ```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 9}
-for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
+for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
   plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]],

### 2022-06-16 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
Various tweaks, bugfixes, and additional filtering

@@
 
-```{r CPD_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
+```{r CPD_mismatch_anchored_purine_frequencies_filtered, fig.width = 11, fig.height = 9}
 min5PrimeCutSiteDistance = 13
@@
 
-```{r CPD_mismatch_anchored_purine_frequencies_x2, fig.width = 5, fig.height = 9}
+```{r CPD_mismatch_anchored_purine_frequencies_filtered_x2, fig.width = 5, fig.height = 9}
 min5PrimeCutSiteDistance = 13
@@
 max5PrimeCutSiteDistance = 25
-for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
+for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
   plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]],
@@
                           expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
-                          minReadLength = min5PrimeCutSiteDistance,
-                          max5PrimeCutSiteDistance = max5PrimeCutSiteDistance)
+                          minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
 }
@@
 max5PrimeCutSiteDistance = 25
-for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
+for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
   plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]]$`1h`,

### 2022-06-16 R/NHF1DeaminationSequenceAndPositionFigureGeneration.rmd
Various tweaks, bugfixes, and additional filtering

--- 2022-06-15 R/NHF1DeaminationSequenceAndPositionFigureGeneration.rmd
@@
 
+```{r CPD_mismatch_position_frequencies_by_read_length_filtered, fig.width = 5, fig.height = 5}
+for (i in seq_along(CPDMismatchData)) {
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["1h"], includedTypes = c("C>T"),
+                                           title = paste(c("CPD", titleCaseFiltering,
+                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
+                                           zScoreTables = CPDMMFreqZScores[[i]])
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["1h"], includedTypes = c("C>T"), posType = FIVE_PRIME,
+                                           title = paste(c("CPD", titleCaseFiltering,
+                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
+                                           zScoreTables = CPDMMFreqZScores[[i]])
+}
+```
+
 ```{r 6-4_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}

### 2022-06-16 R/NHF1TandemDeaminationFigureGeneration.rmd
NHF1 bugfixes and tweaks
Various tweaks, bugfixes, and additional filtering

@@
   plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]], posType = FIVE_PRIME,
+                                           title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                                           "Mismatch Pos Freq", repNames[i]),
+                                                         collapse = ' '),
+                                           zScoreTables = CPDMMFreqZScores[[i]])
+}
+```
+
+```{r CPD_mismatch_position_frequencies_by_read_length_filtered, fig.width = 5, fig.height = 5}
+for (i in seq_along(CPDMismatchData)) {
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["1h"],
+                                           title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                                           "Mismatch Pos Freq", repNames[i]),
+                                                         collapse = ' '),
+                                           zScoreTables = CPDMMFreqZScores[[i]])
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["1h"], posType = FIVE_PRIME,
                                            title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,

### 2022-06-16 R/YeastDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Various tweaks, bugfixes, and additional filtering

--- 2022-06-15 R/YeastDeaminationAnchoredExcisionSiteFigureGeneration.rmd
@@
                           expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
+}
+```
+
+```{r CPD_sequence_frequencies_filtered, fig.width = 11, fig.height = 8}
+min5PrimeCutSiteDistance = 11
+max5PrimeCutSiteDistance = 19
+for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]],
+                          title = paste(c("CPD", titleCaseFiltering,
+                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
+                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
+                          minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
+}
+```
+
+```{r CPD_sequence_frequencies_filtered_x2, fig.width = 5, fig.height = 8}
+min5PrimeCutSiteDistance = 11
+max5PrimeCutSiteDistance = 19
+for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]]$`20min`,
+                          title = paste(c("CPD", titleCaseFiltering,
+                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
+                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
+                          minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
 }

### 2022-06-16 R/YeastDeaminationSequenceAndPositionFigureGeneration.rmd
Various tweaks, bugfixes, and additional filtering

--- 2022-06-15 R/YeastDeaminationSequenceAndPositionFigureGeneration.rmd
@@
 
+```{r CPD_mismatch_position_frequencies_by_read_length_filtered, fig.width = 5, fig.height = 5}
+for (i in seq_along(CPDMismatchData)) {
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["20min"], includedTypes = c("C>T"),
+                                           title = paste(c("CPD", titleCaseFiltering,
+                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
+                                           zScoreTables = CPDMMFreqZScores[[i]])
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["20min"], includedTypes = c("C>T"),
+                                           title = paste(c("CPD", titleCaseFiltering,
+                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
+                                           zScoreTables = CPDMMFreqZScores[[i]], posType = FIVE_PRIME)
+}
+```
+
 ```{r 6-4_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}

### 2022-06-16 R/YeastTandemDeaminationFigureGeneration.rmd
Various tweaks, bugfixes, and additional filtering

@@
   plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]], posType = FIVE_PRIME,
+                                           title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                                           "Mismatch Pos Freq", repNames[i]),
+                                                         collapse = ' '),
+                                           zScoreTables = CPDMMFreqZScores[[i]])
+}
+```
+
+```{r CPD_mismatch_position_frequencies_by_read_length_filtered, fig.width = 5, fig.height = 5}
+for (i in seq_along(CPDMismatchData)) {
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["20min"],
+                                           title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,
+                                                           "Mismatch Pos Freq", repNames[i]),
+                                                         collapse = ' '),
+                                           zScoreTables = CPDMMFreqZScores[[i]])
+  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["20min"], posType = FIVE_PRIME,
                                            title = paste(c("CPD", titleCaseFiltering, titleCaseMismatchType,

### 2022-06-21 R/ArabidopsisDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Various fixes to filtering and axis labels

--- 2022-06-14 R/ArabidopsisDeaminationAnchoredExcisionSiteFigureGeneration.rmd
@@
                                  title = paste(c("CPD", titleCaseFiltering, "5' Anchored Nuc Freq", repNames[i]), collapse = ' '),
-                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                                 secondaryYAxisLabel = "3' Cut Site Distance",
                                  posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
@@
                           title = paste(c("CPD", titleCaseFiltering, "3' Anchored YR Freq", repNames[i]), collapse = ' '),
-                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                          secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
+                          showFivePrimeCutSite = TRUE,
                           expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
@@
 ```
+
+```{r CPD_sequence_frequencies_filtered, fig.width = 11, fig.height = 8}
+min5PrimeCutSiteDistance = 15
+max5PrimeCutSiteDistance = 25
+for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]],
+                          title = paste(c("CPD", titleCaseFiltering,
+                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
+                          secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
+                          showFivePrimeCutSite = TRUE,
+                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
+                          minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
+}
+```
+
+```{r CPD_sequence_frequencies_filtered_x2, fig.width = 5, fig.height = 8}
+min5PrimeCutSiteDistance = 15
+max5PrimeCutSiteDistance = 25
+for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]]$ZT2,
+                          title = paste(c("CPD", titleCaseFiltering,
+                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
+                          secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
+                          showFivePrimeCutSite = TRUE,
+                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
+                          minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
+}
+```

### 2022-06-21 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
Various fixes to filtering and axis labels

--- 2022-06-15 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
@@
                                                  "5' Anchored Nuc Freq", repNames[i]), collapse = ' '),
-                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                                 secondaryYAxisLabel = "3' Cut Site Distance",
                                  posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
@@
                                                  "5' Anchored Nuc Freq", repNames[i]), collapse = ' '),
-                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                                 secondaryYAxisLabel = "3' Cut Site Distance",
+                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
+                                 expansionOffset = expansionOffset,
+                                 minReadLength = min3PrimeCutSiteDistance, maxReadLength = max3PrimeCutSiteDistance)
+}
+```
+
+```{r CPD_mismatch_anchored_nucleotide_frequencies_filtered_x2, fig.width = 5, fig.height = 8}
+min3PrimeCutSiteDistance = 1
+max3PrimeCutSiteDistance = 12
+
+for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]][Timepoint == "1h"], 
+                                 title = paste(c("CPD", titleCaseFiltering,
+                                                 "5' Anchored Nuc Freq", repNames[i]), collapse = ' '),
+                                 secondaryYAxisLabel = "3' Cut Site Distance",
                                  posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
@@
 
+```{r CPD_mismatch_anchored_purine_frequencies_filtered, fig.width = 11, fig.height = 9}
+min3PrimeCutSiteDistance = 1
+max3PrimeCutSiteDistance = 12
+
+for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]], 
+                                 title = paste(c("CPD", titleCaseFiltering,
+                                                 "5' Anchored Purine Freq", repNames[i]), collapse = ' '),
+                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                                 combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
+                                 expansionOffset = expansionOffset,
+                                 minReadLength = min3PrimeCutSiteDistance, maxReadLength = max3PrimeCutSiteDistance)
+}
+```
+
+```{r CPD_mismatch_anchored_purine_frequencies_filtered_x2, fig.width = 5, fig.height = 9}
+min3PrimeCutSiteDistance = 1
+max3PrimeCutSiteDistance = 12
+
+for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]][Timepoint == "1h"], 
+                                 title = paste(c("CPD", titleCaseFiltering,
+                                                 "5' Anchored Purine Freq", repNames[i]), collapse = ' '),
+                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                                 combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
+                                 expansionOffset = expansionOffset,
+                                 minReadLength = min3PrimeCutSiteDistance, maxReadLength = max3PrimeCutSiteDistance)
+}
+```
+
 ```{r 6-4_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 9}
@@
                                           "3' Anchored YR Freq", repNames[i]), collapse = ' '),
-                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
+                          secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
+                          showFivePrimeCutSite = TRUE,
                           expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
@@
                                           "5' Anchored TGG Freq", repNames[i]), collapse = ' '),
-                          secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
+                          secondaryYAxisLabel = "3' Cut Site Distance", yAxisLabel = "YR Frequency",
+                          showThreePrimeCutSite = TRUE,
                           expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
+}
+```
+
+```{r CPD_sequence_frequencies_filtered, fig.width = 11, fig.height = 8}
+min5PrimeCutSiteDistance = 13
+max5PrimeCutSiteDistance = 25
+for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]],
+                          title = paste(c("CPD", titleCaseFiltering,
+                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
+                          secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
+                          showFivePrimeCutSite = TRUE,
+                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
+                          minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
+}
+```
+
+```{r CPD_sequence_frequencies_filtered_x2, fig.width = 5, fig.height = 8}
+min5PrimeCutSiteDistance = 13
+max5PrimeCutSiteDistance = 25
+for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]]$`1h`,
+                          title = paste(c("CPD", titleCaseFiltering,
+                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
+                          secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
+                          showFivePrimeCutSite = TRUE,
+                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
+                          minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
 }

### 2022-06-21 R/YeastDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Various fixes to filtering and axis labels

--- 2022-06-15 R/YeastDeaminationAnchoredExcisionSiteFigureGeneration.rmd
@@
                                           "5' Anchored TGG Freq", repNames[i]), collapse = ' '),
-                          secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
+                          secondaryYAxisLabel = "3' Cut Site Distance", yAxisLabel = "YR Frequency",
+                          showThreePrimeCutSite = TRUE,
                           expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
+}
+```
+
+```{r CPD_sequence_frequencies_filtered, fig.width = 11, fig.height = 8}
+min5PrimeCutSiteDistance = 11
+max5PrimeCutSiteDistance = 19
+for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]],
+                          title = paste(c("CPD", titleCaseFiltering,
+                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
+                          secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
+                          showFivePrimeCutSite = TRUE,
+                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
+                          minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
+}
+```
+
+```{r CPD_sequence_frequencies_filtered_x2, fig.width = 5, fig.height = 8}
+min5PrimeCutSiteDistance = 11
+max5PrimeCutSiteDistance = 19
+for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
+  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]]$`20min`,
+                          title = paste(c("CPD", titleCaseFiltering,
+                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
+                          secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
+                          showFivePrimeCutSite = TRUE,
+                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
+                          minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
 }

### 2022-06-22 R/PaperFigureGeneration.rmd
Intermediate commit

---
title: "Paper Figure Generation"
author: "Ben Morledge-Hampton"
date: "6/21/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

```{r setup_chunk}
library(knitr)

NHF1CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
}

opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
               fig.path = paste0(file.path("deamination_analysis_output","paper_figures"),
                                 .Platform$file.sep))

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data")

NHF1DataDirectory = file.path(deaminationDirectory, "NHF1")
NHF1SequenceAndPositionDataDirectory = file.path(NHF1DataDirectory, "sequence_and_position_analysis")
NHF1ExcisionSiteDataDirectory = file.path(NHF1DataDirectory, "excision_site_analysis")
NHF1GeneralReadSequenceDataDirectory = file.path(NHF1DataDirectory, "general_read_sequences")

arabidopsisDataDirectory = file.path(deaminationDirectory, "Arabidopsis")
arabidopsisSequenceAndPositionDataDirectory = file.path(arabidopsisDataDirectory, "sequence_and_position_analysis")
arabidopsisExcisionSiteDataDirectory = file.path(arabidopsisDataDirectory, "excision_site_analysis")

yeastDataDirectory = file.path(deaminationDirectory, "yeast")
yeastSequenceAndPositionDataDirectory = file.path(yeastDataDirectory, "sequence_and_position_analysis")
yeastExcisionSiteDataDirectory = file.path(yeastDataDirectory, "excision_site_analysis")
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationParseAndFilter.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationSequenceAndPositionAnalysis.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationAnchoredExcisionSiteAnalysis.R"))
```

```{r read_figure_2_data}
NHF1CPDMismatchDataAllReps = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDMismatchDataAllReps)) {
  NHF1CPDMismatchDataAllReps[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "NHF1", lesion = "CPD", timepoint = names(CPDMismatchData)[i], repitition = "all_reps"
  ))
}
```

```{r figure_2}
plotMismatchTypeFrequencies(NHF1CPDMismatchDataAllReps$`1h`,
                            title = "NHF1 CPD 1h All Reps Mismatch Type Frequencies")

plotTrinucleotideContext(NHF1CPDMismatchData$`1h`, includedTypes = c("C>T"),
                         title = "NHF1 CPD 1h All Reps Mismatch Trinuc Context")

plotMismatchPositionFrequencies(NHF1CPDMismatchData$`1h`, includedTypes = c("C>T"),
                                title = "NHF1 CPD 1h All Reps Mismatch Pos Frequencies")
```

```{r read_figure_3_data}
NHF1CPDMMFreqZScoresAllReps = NHF1CPDTimepoints
for (i in seq_along(CPDMMFreqZScores)) {
  NHF1CPDMMFreqZScoresAllReps[[i]] = fread(generateFilePath(
    directory = NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(CPDMMFreqZScores)[i], includedMismatches = c("C>T")
  ))
}

NHF1FivePrimeMismatchCPDNucFreqAllReps = fread(generateFilePath(
  directory = NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
  strandPolarity = "five_prime", anchored = TRUE
))

NHF1CPDTGGSeqFreqAllReps = NHF1CPDTimepoints
for (i in seq_along(CPDTGGSeqFreq)) {
  NHF1CPDTGGSeqFreqAllReps[[i]] = fread(generateFilePath(
    directory = NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(NHF1CPDTGGSeqFreqAllReps)[i], sequence = "TGG"
  ))
}
```

```{r figure_3}
plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Freq",
                                         zScoreTables = CPDMMFreqZScores)

plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h All Reps 5' Anchored Nuc Freq",
                               secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 1, maxReadLength = 12)

plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps$`1h`, title = "NHF1 CPD 1h All Reps General Read TGG Freq",
                        expansionOffset = 10, showThreePrimeCutSite = TRUE,
                        showFivePrimeCutSite = TRUE, querySequences = c("TGG"), minReadLength = 18)
```

```{r figure_3_alt}
plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Freq",
                                         zScoreTables = CPDMMFreqZScores)

plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps, 
                               title = "NHF1 CPD 1h All Reps 5' Anchored Nuc Freq",
                               secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 1, maxReadLength = 12)

plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps, title = "NHF1 CPD 1h All Reps General Read TGG Freq",
                        expansionOffset = 10, showThreePrimeCutSite = TRUE,
                        showFivePrimeCutSite = TRUE, querySequences = c("TGG"), minReadLength = 18)
```

### 2022-06-22 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
Fixing more mistakes...

@@
 ```{r CPD_mismatch_anchored_purine_frequencies_filtered, fig.width = 11, fig.height = 9}
-min3PrimeCutSiteDistance = 1
-max3PrimeCutSiteDistance = 12
+min5PrimeCutSiteDistance = 13
+max5PrimeCutSiteDistance = 25
 
-for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
-  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]], 
+for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq[[i]], 
                                  title = paste(c("CPD", titleCaseFiltering,
-                                                 "5' Anchored Purine Freq", repNames[i]), collapse = ' '),
-                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                                                 "3' Anchored Purine Freq", repNames[i]), collapse = ' '),
+                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                                  combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
+                                 posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
                                  expansionOffset = expansionOffset,
-                                 minReadLength = min3PrimeCutSiteDistance, maxReadLength = max3PrimeCutSiteDistance)
+                                 minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
 }
@@
 ```{r CPD_mismatch_anchored_purine_frequencies_filtered_x2, fig.width = 5, fig.height = 9}
-min3PrimeCutSiteDistance = 1
-max3PrimeCutSiteDistance = 12
+min5PrimeCutSiteDistance = 13
+max5PrimeCutSiteDistance = 25
 
-for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
-  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]][Timepoint == "1h"], 
+for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
+  plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq[[i]][Timepoint == "1h"], 
                                  title = paste(c("CPD", titleCaseFiltering,
-                                                 "5' Anchored Purine Freq", repNames[i]), collapse = ' '),
-                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                                                 "3' Anchored Purine Freq", repNames[i]), collapse = ' '),
+                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                                  combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
+                                 posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
                                  expansionOffset = expansionOffset,
-                                 minReadLength = min3PrimeCutSiteDistance, maxReadLength = max3PrimeCutSiteDistance)
+                                 minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
 }

### 2022-06-22 R/PaperFigureGeneration.rmd
Created PaperFigureGeneration
- This is a dedicated R notebook for generating the figures to be used in the publication associated with the analysis.
- TODO: Need to split up figure generation chunks to account for different figure sizes.

@@
 NHF1CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
+NHF1SixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
+arabidopsisCPDTimepoints = list(`ZT2` = NULL, `ZT14` = NULL)
+yeastCPDTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
+GM12878CisplatinTimepoints = list(`90min` = NULL)
+CSBCPDTimepoints = list(`1h` = NULL)
+XPCCPDTimepoints = list(`1h` = NULL)
 
@@
 
-NHF1DataDirectory = file.path(deaminationDirectory, "NHF1")
+NHF1DataDirectory = file.path(deaminationDataDirectory, "NHF1")
 NHF1SequenceAndPositionDataDirectory = file.path(NHF1DataDirectory, "sequence_and_position_analysis")
@@
 
-arabidopsisDataDirectory = file.path(deaminationDirectory, "Arabidopsis")
+arabidopsisDataDirectory = file.path(deaminationDataDirectory, "Arabidopsis")
 arabidopsisSequenceAndPositionDataDirectory = file.path(arabidopsisDataDirectory, "sequence_and_position_analysis")
@@
 
-yeastDataDirectory = file.path(deaminationDirectory, "yeast")
+yeastDataDirectory = file.path(deaminationDataDirectory, "yeast")
 yeastSequenceAndPositionDataDirectory = file.path(yeastDataDirectory, "sequence_and_position_analysis")
 yeastExcisionSiteDataDirectory = file.path(yeastDataDirectory, "excision_site_analysis")
+
+GM12878DataDirectory = file.path(deaminationDataDirectory, "GM12878")
+GM12878SequenceAndPositionDataDirectory = file.path(GM12878DataDirectory, "sequence_and_position_analysis")
+
+CSBDataDirectory = file.path(deaminationDataDirectory, "CS-B")
+CSBSequenceAndPositionDataDirectory = file.path(CSBDataDirectory, "sequence_and_position_analysis")
+
+XPCDataDirectory = file.path(deaminationDataDirectory, "XP-C")
+XPCSequenceAndPositionDataDirectory = file.path(XPCDataDirectory, "sequence_and_position_analysis")
 ```
@@
     NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
-    cellType = "NHF1", lesion = "CPD", timepoint = names(CPDMismatchData)[i], repitition = "all_reps"
+    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
+    timepoint = names(NHF1CPDMismatchDataAllReps)[i]
   ))
@@
 
-plotTrinucleotideContext(NHF1CPDMismatchData$`1h`, includedTypes = c("C>T"),
+plotTrinucleotideContext(NHF1CPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
                          title = "NHF1 CPD 1h All Reps Mismatch Trinuc Context")
 
-plotMismatchPositionFrequencies(NHF1CPDMismatchData$`1h`, includedTypes = c("C>T"),
+plotMismatchPositionFrequencies(NHF1CPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
                                 title = "NHF1 CPD 1h All Reps Mismatch Pos Frequencies")
@@
 NHF1CPDMMFreqZScoresAllReps = NHF1CPDTimepoints
-for (i in seq_along(CPDMMFreqZScores)) {
+for (i in seq_along(NHF1CPDMMFreqZScoresAllReps)) {
   NHF1CPDMMFreqZScoresAllReps[[i]] = fread(generateFilePath(
@@
     cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
-    timepoint = names(CPDMMFreqZScores)[i], includedMismatches = c("C>T")
+    timepoint = names(NHF1CPDMMFreqZScoresAllReps)[i], includedMismatches = c("C>T")
   ))
@@
 NHF1CPDTGGSeqFreqAllReps = NHF1CPDTimepoints
-for (i in seq_along(CPDTGGSeqFreq)) {
+for (i in seq_along(NHF1CPDTGGSeqFreqAllReps)) {
   NHF1CPDTGGSeqFreqAllReps[[i]] = fread(generateFilePath(
@@
 ```{r figure_3}
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["1h"], includedTypes = c("C>T"),
+### Just the 1h timepoint ###
+plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllReps["1h"], includedTypes = c("C>T"),
                                          title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Freq",
-                                         zScoreTables = CPDMMFreqZScores)
+                                         zScoreTables = NHF1CPDMMFreqZScoresAllReps)
 
@@
                         showFivePrimeCutSite = TRUE, querySequences = c("TGG"), minReadLength = 18)
+
+### All timepoints together ###
+# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllReps, includedTypes = c("C>T"),
+#                                          title = "NHF1 CPD All Reps C>T Mismatch Pos Freq",
+#                                          zScoreTables = NHF1CPDMMFreqZScoresAllReps)
+# 
+# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps, 
+#                                title = "NHF1 CPD All Reps 5' Anchored Nuc Freq",
+#                                secondaryYAxisLabel = "3' Cut Site Distance",
+#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
+#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 12)
+# 
+# plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps, title = "NHF1 CPD All Reps General Read TGG Freq",
+#                         expansionOffset = 10, showThreePrimeCutSite = TRUE,
+#                         showFivePrimeCutSite = TRUE, querySequences = c("TGG"), minReadLength = 18)
 ```
 
-```{r figure_3_alt}
-plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]], includedTypes = c("C>T"),
-                                         title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Freq",
-                                         zScoreTables = CPDMMFreqZScores)
+```{r read_figure_5_data}
+NHF1CPDMismatchDataAllRepsFiltered = NHF1CPDTimepoints
+for (i in seq_along(NHF1CPDMismatchDataAllRepsFiltered)) {
+  NHF1CPDMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
+    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1CPDMismatchDataAllRepsFiltered)[i],
+    repitition = "all_reps", filtering = "TGG_filtered"
+  ))
+}
 
-plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps, 
-                               title = "NHF1 CPD 1h All Reps 5' Anchored Nuc Freq",
+NHF1CPDMMFreqZScoresAllRepsFiltered = NHF1CPDTimepoints
+for (i in seq_along(NHF1CPDMMFreqZScoresAllRepsFiltered)) {
+  NHF1CPDMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
+    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
+    timepoint = names(NHF1CPDMMFreqZScoresAllRepsFiltered)[i], includedMismatches = c("C>T")
+  ))
+}
+
+NHF1CPDGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
+for (i in seq_along(NHF1CPDGroupedStatsAllRepsFiltered)) {
+  NHF1CPDGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
+    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
+    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
+    strandPolarity = names(NHF1CPDGroupedStatsAllRepsFiltered)[i]
+  ))
+}
+
+arabidopsisCPDGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
+for (i in seq_along(arabidopsisCPDGroupedStatsAllRepsFiltered)) {
+  arabidopsisCPDGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
+    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
+    cellType = "Arabidopsis", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
+    strandPolarity = names(arabidopsisCPDGroupedStatsAllRepsFiltered)[i]
+  ))
+}
+
+yeastCPDGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
+for (i in seq_along(yeastCPDGroupedStatsAllRepsFiltered)) {
+  yeastCPDGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
+    yeastSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
+    cellType = "yeast", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
+    strandPolarity = names(yeastCPDGroupedStatsAllRepsFiltered)[i]
+  ))
+}
+```
+
+```{r figure_5}
+### Just the 1h timepoint ###
+plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
+                                         title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
+                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered)
+
+plotGroupedPositionStats(NHF1CPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                         NHF1CPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
+                         POS_DIFF, title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
+                         xAxisBreaks = c(22:30))
+
+plotGroupedPositionStats(arabidopsisCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                         arabidopsisCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
+                         POS_DIFF, title = "Arabidopsis CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
+                         xAxisBreaks = c(24:30))
+
+plotGroupedPositionStats(yeastCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                         yeastCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
+                         POS_DIFF, title = "Yeast CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
+                         xAxisBreaks = c(22:25))
+
+### All timepoints together ###
+# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
+#                                          title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
+#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered)
+# 
+# plotGroupedPositionStats(NHF1CPDGroupedStatsAllRepsFiltered$three_prime,
+#                          NHF1CPDGroupedStatsAllRepsFiltered$five_prime,
+#                          POS_DIFF, title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Diff",
+#                          xAxisBreaks = c(22:30))
+# 
+# plotGroupedPositionStats(arabidopsisCPDGroupedStatsAllRepsFiltered$three_prime,
+#                          arabidopsisCPDGroupedStatsAllRepsFiltered$five_prime,
+#                          POS_DIFF, title = "Arabidopsis CPD All Reps TGG-Filtered C>T Mismatch Pos Diff",
+#                          xAxisBreaks = c(24:30))
+# 
+# plotGroupedPositionStats(yeastCPDGroupedStatsAllRepsFiltered$three_prime,
+#                          yeastCPDGroupedStatsAllRepsFiltered$five_prime,
+#                          POS_DIFF, title = "Yeast CPD All Reps TGG-Filtered C>T Mismatch Pos Diff",
+#                          xAxisBreaks = c(22:25))
+
+```
+
+```{r read_figure_6_data}
+NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
+  NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
+  strandPolarity = "five_prime", anchored = TRUE, filtering = "TGG_filtered"
+))
+
+NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
+  NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
+  strandPolarity = "three_prime", anchored = TRUE, filtering = "TGG_filtered"
+))
+
+NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = NHF1CPDTimepoints
+for (i in seq_along(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
+  NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
+    NHF1ExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
+    timepoint = names(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
+    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
+  ))
+}
+
+```
+
+```{r figure_6}
+### Just the 1h timepoint ###
+plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
+                               title = "NHF1 CPD 1h All Reps TGG-Filtered 5' Anchored Nuc Freq",
                                secondaryYAxisLabel = "3' Cut Site Distance",
@@
 
-plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps, title = "NHF1 CPD 1h All Reps General Read TGG Freq",
-                        expansionOffset = 10, showThreePrimeCutSite = TRUE,
-                        showFivePrimeCutSite = TRUE, querySequences = c("TGG"), minReadLength = 18)
+plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
+                               title = "NHF1 CPD 1h ALL Reps TGG-Filtered 3' Anchored Purine Freq",
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
+                               expansionOffset = 10, minReadLength = 13, maxReadLength = 25)
+
+plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
+                        title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored YR Freq",
+                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
+                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
+                        expansionOffset = 10, minReadLength = 13, maxReadLength = 25)
+
+### All timepoints together ###
+# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered, 
+#                                title = "NHF1 CPD All Reps TGG-Filtered 5' Anchored Nuc Freq",
+#                                secondaryYAxisLabel = "3' Cut Site Distance",
+#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
+#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 12)
+# 
+# plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered, 
+#                                title = "NHF1 CPD ALL Reps TGG-Filtered 3' Anchored Purine Freq",
+#                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
+#                                combineNucleotides = c("AG"), combinedNames = c("Purine"),
+#                                posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
+#                                expansionOffset = 10, minReadLength = 13, maxReadLength = 25)
+# 
+# plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
+#                         title = "NHF1 CPD All Reps TGG-Filtered 3' Anchored YR Freq",
+#                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
+#                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
+#                         expansionOffset = 10, minReadLength = 13, maxReadLength = 25)
 ```
+
+```{r read_figure_8_data}
+NHF1CPDCCtoTTMismatchDataAllRepsFiltered = NHF1CPDTimepoints
+for (i in seq_along(NHF1CPDCCtoTTMismatchDataAllRepsFiltered)) {
+  NHF1CPDCCtoTTMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
+    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
+    filtering = "TGG_filtered", includedMismatches = "CC>TT",
+    timepoint = names(NHF1CPDCCtoTTMismatchDataAllRepsFiltered)[i]
+  ))
+}
+
+NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered = NHF1CPDTimepoints
+for (i in seq_along(NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered)) {
+  NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
+    directory = NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
+    filtering = "TGG_filtered", includedMismatches = "CC>TT",
+    timepoint = names(NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered)[i]
+  ))
+}
+
+NHF1CPDGGtoAAMismatchDataAllRepsFiltered = NHF1CPDTimepoints
+for (i in seq_along(NHF1CPDGGtoAAMismatchDataAllRepsFiltered)) {
+  NHF1CPDGGtoAAMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
+    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
+    filtering = "TGG_filtered", includedMismatches = "GG>AA",
+    timepoint = names(NHF1CPDGGtoAAMismatchDataAllRepsFiltered)[i]
+  ))
+}
+
+NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered = NHF1CPDTimepoints
+for (i in seq_along(NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered)) {
+  NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
+    directory = NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
+    filtering = "TGG_filtered", includedMismatches = "GG>AA",
+    timepoint = names(NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered)[i]
+  ))
+}
+```
+
+```{r figure_8}
+### Just the 1h timepoint ###
+plotPositionAcrossTimepointAndReadLength(NHF1CPDCCtoTTMismatchDataAllRepsFiltered["1h"],
+                                         title = "NHF1 CPD 1h All Reps CC>TT Mismatch Pos Freq",
+                                         zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered)
+
+plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered["1h"],
+                                         title = "NHF1 CPD 1h All Reps GG>AA Mismatch Pos Freq",
+                                         zScoreTables = NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered)
+
+### All timepoints together ###
+# plotPositionAcrossTimepointAndReadLength(NHF1CPDCCtoTTMismatchDataAllRepsFiltered,
+#                                          title = "NHF1 CPD All Reps CC>TT Mismatch Pos Freq",
+#                                          zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered)
+# 
+# plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered,
+#                                          title = "NHF1 CPD All Reps GG>AA Mismatch Pos Freq",
+#                                          zScoreTables = NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered)
+```
+
+```{r read_figure_S1_data}
+NHF1SixFourMismatchDataAllReps = NHF1SixFourTimepoints
+for (i in seq_along(NHF1SixFourMismatchDataAllReps)) {
+  NHF1SixFourMismatchDataAllReps[[i]] = fread(generateFilePath(
+    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+    cellType = "NHF1", lesion = "6-4", repitition = "all_reps",
+    timepoint = names(NHF1SixFourMismatchDataAllReps)[i]
+  ))
+}
+
+GM12878CisplatinMismatchDataAllReps = GM12878CisplatinTimepoints
+for (i in seq_along(GM12878CisplatinMismatchDataAllReps)) {
+  GM12878CisplatinMismatchDataAllReps[[i]] = fread(generateFilePath(
+    GM12878SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+    cellType = "GM12878", lesion = "cisplatin", repitition = "all_reps",
+    timepoint = names(GM12878CisplatinMismatchDataAllReps)[i]
+  ))
+}
+```
+
+```{r figure_S1}
+plotMismatchTypeFrequencies(NHF1SixFourMismatchDataAllReps$`20min`,
+                            title = "NHF1 6-4 20min All Reps Mismatch Type Frequencies")
+
+plotTrinucleotideContext(NHF1SixFourMismatchDataAllReps$`20min`, includedTypes = c("C>T"),
+                         title = "NHF1 6-4 20min All Reps Mismatch Trinuc Context")
+
+plotMismatchPositionFrequencies(NHF1SixFourMismatchDataAllReps$`20min`, includedTypes = c("C>T"),
+                                title = "NHF1 6-4 20min All Reps Mismatch Pos Frequencies")
+
+plotMismatchTypeFrequencies(GM12878CisplatinMismatchDataAllReps$`90min`,
+                            title = "GM12878 Cisplatin 90min All Reps Mismatch Type Frequencies")
+
+plotTrinucleotideContext(GM12878CisplatinMismatchDataAllReps$`90min`, includedTypes = c("C>T"),
+                         title = "GM12878 Cisplatin 90min All Reps Mismatch Trinuc Context")
+
+plotMismatchPositionFrequencies(GM12878CisplatinMismatchDataAllReps$`90min`, includedTypes = c("C>T"),
+                                title = "GM12878 Cisplatin 90min All Reps Mismatch Pos Frequencies")
+```
+
+```{r read_figure_S2_data}
+arabidopsisCPDMismatchDataAllReps = arabidopsisCPDTimepoints
+for (i in seq_along(arabidopsisCPDMismatchDataAllReps)) {
+  arabidopsisCPDMismatchDataAllReps[[i]] = fread(generateFilePath(
+    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+    cellType = "Arabidopsis", lesion = "CPD", repitition = "all_reps",
+    timepoint = names(arabidopsisCPDMismatchDataAllReps)[i]
+  ))
+}
+
+yeastCPDMismatchDataAllReps = yeastCPDTimepoints
+for (i in seq_along(yeastCPDMismatchDataAllReps)) {
+  yeastCPDMismatchDataAllReps[[i]] = fread(generateFilePath(
+    yeastSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+    cellType = "yeast", lesion = "CPD", repitition = "all_reps",
+    timepoint = names(yeastCPDMismatchDataAllReps)[i]
+  ))
+}
+
+CSBCPDMismatchDataAllReps = CSBCPDTimepoints
+for (i in seq_along(CSBCPDMismatchDataAllReps)) {
+  CSBCPDMismatchDataAllReps[[i]] = fread(generateFilePath(
+    CSBSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+    cellType = "CS-B", lesion = "CPD", repitition = "all_reps",
+    timepoint = names(CSBCPDMismatchDataAllReps)[i]
+  ))
+}
+
+XPCCPDMismatchDataAllReps = XPCCPDTimepoints
+for (i in seq_along(XPCCPDMismatchDataAllReps)) {
+  XPCCPDMismatchDataAllReps[[i]] = fread(generateFilePath(
+    XPCSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+    cellType = "XP-C", lesion = "CPD", repitition = "all_reps",
+    timepoint = names(XPCCPDMismatchDataAllReps)[i]
+  ))
+}
+```
+
+```{r figure_S2}
+plotMismatchTypeFrequencies(arabidopsisCPDMismatchDataAllReps$ZT2,
+                            title = "Arabidopsis CPD ZT2 All Reps Mismatch Type Frequencies")
+
+plotTrinucleotideContext(arabidopsisCPDMismatchDataAllReps$ZT2, includedTypes = c("C>T"),
+                         title = "Arabidopsis CPD ZT2 All Reps Mismatch Trinuc Context")
+
+plotMismatchPositionFrequencies(arabidopsisCPDMismatchDataAllReps$ZT2, includedTypes = c("C>T"),
+                                title = "Arabidopsis CPD ZT2 All Reps Mismatch Pos Frequencies")
+
+plotMismatchTypeFrequencies(yeastCPDMismatchDataAllReps$`20min`,
+                            title = "Yeast CPD 20min All Reps Mismatch Type Frequencies")
+
+plotTrinucleotideContext(yeastCPDMismatchDataAllReps$`20min`, includedTypes = c("C>T"),
+                         title = "Yeast CPD 20min All Reps Mismatch Trinuc Context")
+
+plotMismatchPositionFrequencies(yeastCPDMismatchDataAllReps$`20min`, includedTypes = c("C>T"),
+                                title = "Yeast CPD 20min All Reps Mismatch Pos Frequencies")
+
+plotMismatchTypeFrequencies(CSBCPDMismatchDataAllReps$`1h`,
+                            title = "CS-B CPD 1h All Reps Mismatch Type Frequencies")
+
+plotTrinucleotideContext(CSBCPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
+                         title = "CS-B CPD 1h All Reps Mismatch Trinuc Context")
+
+plotMismatchPositionFrequencies(CSBCPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
+                                title = "CS-B CPD 1h All Reps Mismatch Pos Frequencies")
+
+plotMismatchTypeFrequencies(XPCCPDMismatchDataAllReps$`1h`,
+                            title = "XP-C CPD 1h All Reps Mismatch Type Frequencies")
+
+plotTrinucleotideContext(XPCCPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
+                         title = "XP-C CPD 1h All Reps Mismatch Trinuc Context")
+
+plotMismatchPositionFrequencies(XPCCPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
+                                title = "XP-C CPD 1h All Reps Mismatch Pos Frequencies")
+```
+
+```{r read_figure_S3_data}
+arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = arabidopsisCPDTimepoints
+for (i in seq_along(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
+  arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
+    arabidopsisExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+    cellType = "Arabidopsis", lesion = "CPD", repitition = "all_reps",
+    timepoint = names(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
+    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
+  ))
+}
+
+yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = yeastCPDTimepoints
+for (i in seq_along(yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
+  yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
+    yeastExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+    cellType = "yeast", lesion = "CPD", repitition = "all_reps",
+    timepoint = names(yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
+    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
+  ))
+}
+```
+
+```{r figure_S3}
+plotSequenceFrequencies(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$ZT2,
+                        title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered 3' Anchored YR Freq",
+                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
+                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
+                        expansionOffset = 10, minReadLength = 15, maxReadLength = 25)
+
+plotSequenceFrequencies(yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`20min`,
+                        title = "Yeast CPD 20min All Reps TGG-Filtered 3' Anchored YR Freq",
+                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
+                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
+                        expansionOffset = 10, minReadLength = 11, maxReadLength = 19)
+```

### 2022-06-23 R/DeaminationSequenceAndPositionAnalysis.R
Standardize "Relative Frequency" axis labels

@@ -30,7 +30,7 @@ plotMismatchTypeFrequencies = function(mismatchTable, title = "Mismatch Type Fre
   print(
     ggplot(mismatchTable[, .N, by = Mismatch][, Freq := N/sum(N)], aes(x = Mismatch, y = Freq)) +
       geom_bar(stat = "identity") +
-      labs(title = title, x = "Mismatch Type", y = "Frequency") +
+      labs(title = title, x = "Mismatch Type", y = "Relative Frequency") +
       blankBackground + defaultTextScaling + theme(axis.text = element_text(size = 15))
   )
 
@@ -62,7 +62,7 @@ plotMismatchPositionFrequencies = function(mismatchTable, includedTypes = list()
   print(
     ggplot(frequencyData, aes(x = Position, y = Freq)) +
       geom_bar(stat = "identity") +
-      labs(title = title, x = xAxisLabel, y = "Frequency") +
+      labs(title = title, x = xAxisLabel, y = "Relative Frequency") +
       blankBackground + defaultTextScaling
   )
 
@@ -128,7 +128,7 @@ plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTy
   }
 
   plot = ggplot(groupedPositionFrequencies, aes(Position, Frequency)) +
-    labs(title = title, x = xAxisLabel, y = "Relative Mismatch Frequency") +
+    labs(title = title, x = xAxisLabel, y = "Relative Frequency") +
     blankBackground + defaultTextScaling
 
   if (!is.null(zScoreTables)) {
@@ -194,7 +194,7 @@ plotReadLengthFrequencies = function(readLengthCountTables, title = "Read Length
 
   plot = ggplot(readLengthFrequencies, aes(Read_Length, Freq)) +
     geom_bar(stat = "identity") +
-    labs(title = title, x = "Read Length", y = "Frequency") +
+    labs(title = title, x = "Read Length", y = "Relative Frequency") +
     blankBackground + defaultTextScaling
 
   if (!noTimepointInfo) {
@@ -327,7 +327,7 @@ plotTrinucleotideContext = function(simplifiedMismatchTable, includedTypes = lis
   print(
     ggplot(trinucContextFrequencies, aes(Trinuc_Context, Freq, fill = str_sub(Trinuc_Context, 1, 1))) +
       geom_bar(stat = "identity") +
-      labs(title = title, x = "Trinucleotide Context", y = "Frequency") +
[…]

### 2022-06-23 R/UsefulFileSystemFunctions.R
Added new data type string for tandem counts

@@ -12,7 +12,8 @@ dataTypeStrings =
        sequenceFrequency = "sequence_frequency",
        alignedReads = "aligned_reads",
        mismatchFrequencyZScores = "mismatch_frequency_z-scores",
-       readLengthcounts = "read_length_counts")
+       readLengthcounts = "read_length_counts",
+       tandemMismatchCountsComparison = "tandem_mismatch_counts_comparison")
 
 generateFilePath = function(directory, dataTypeString, fileExtension,
                             cellType = NA, lesion = NA, timepoint = NA, repitition = NA,

### 2022-06-23 R/PaperFigureGeneration.rmd
Intermediate commit

@@
 NHF1DataDirectory = file.path(deaminationDataDirectory, "NHF1")
+NHF1MismatchesByReadDataDirectory = file.path(NHF1DataDirectory, "mismatches_by_read")
 NHF1SequenceAndPositionDataDirectory = file.path(NHF1DataDirectory, "sequence_and_position_analysis")
@@
 
-```{r figure_2}
+```{r figure_2A}
 plotMismatchTypeFrequencies(NHF1CPDMismatchDataAllReps$`1h`,
                             title = "NHF1 CPD 1h All Reps Mismatch Type Frequencies")
-
+```
+```{r figure_2B}
 plotTrinucleotideContext(NHF1CPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
-                         title = "NHF1 CPD 1h All Reps Mismatch Trinuc Context")
-
+                         title = "NHF1 CPD 1h All Reps C>T Mismatch Trinuc Context")
+```
+```{r figure_2C}
 plotMismatchPositionFrequencies(NHF1CPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
-                                title = "NHF1 CPD 1h All Reps Mismatch Pos Frequencies")
+                                title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Frequencies")
+```
+```{r figure_2D}
+plotMismatchPositionFrequencies(NHF1CPDMismatchDataAllReps$`1h`, omittedTypes = c("C>T"),
+                                title = "NHF1 CPD 1h All Reps !C>T Mismatch Pos Frequencies")
 ```
@@
 
-```{r figure_3}
+```{r figure_3A}
 ### Just the 1h timepoint ###
@@
 
+### All timepoints together ###
+# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllReps, includedTypes = c("C>T"),
+#                                          title = "NHF1 CPD All Reps C>T Mismatch Pos Freq",
+#                                          zScoreTables = NHF1CPDMMFreqZScoresAllReps)
+```
+```{r figure_3B}
+### Just the 1h timepoint ###
 plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps[Timepoint == "1h"], 
@@
                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
-                               expansionOffset = 10, minReadLength = 1, maxReadLength = 12)
-
-plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps$`1h`, title = "NHF1 CPD 1h All Reps General Read TGG Freq",
-                        expansionOffset = 10, showThreePrimeCutSite = TRUE,
-                        showFivePrimeCutSite = TRUE, querySequences = c("TGG"), minReadLength = 18)
+                               expansionOffset = 10, minReadLength = 1, maxReadLength = 7)
 
 ### All timepoints together ###
-# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllReps, includedTypes = c("C>T"),
-#                                          title = "NHF1 CPD All Reps C>T Mismatch Pos Freq",
-#                                          zScoreTables = NHF1CPDMMFreqZScoresAllReps)
-# 
 # plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps, 
@@
 #                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
-#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 12)
-# 
+#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 7)
+```
+```{r figure_3C}
+### Just the 1h timepoint ###
+plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps$`1h`, title = "NHF1 CPD 1h All Reps General Read TGG Freq",
+                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE, querySequences = c("TGG"),
+                        expansionOffset = 10, minReadLength = 21, maxReadLength = 27)
+
+### All timepoints together ###
 # plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps, title = "NHF1 CPD All Reps General Read TGG Freq",
-#                         expansionOffset = 10, showThreePrimeCutSite = TRUE,
-#                         showFivePrimeCutSite = TRUE, querySequences = c("TGG"), minReadLength = 18)
+#                         showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE, querySequences = c("TGG"),
+#                         expansionOffset = 10, minReadLength = 21, maxReadLength = 27)
 ```
@@
 
+arabidopsisCPDMismatchDataAllRepsFiltered = arabidopsisCPDTimepoints
+for (i in seq_along(arabidopsisCPDMismatchDataAllRepsFiltered)) {
+  arabidopsisCPDMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
+    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+    cellType = "Arabidopsis", lesion = "CPD", timepoint = names(arabidopsisCPDMismatchDataAllRepsFiltered)[i],
+    repitition = "all_reps", filtering = "TGG_filtered"
+  ))
+}
+
+yeastCPDMismatchDataAllRepsFiltered = yeastCPDTimepoints
+for (i in seq_along(yeastCPDMismatchDataAllRepsFiltered)) {
+  yeastCPDMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
+    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+    cellType = "yeast", lesion = "CPD", timepoint = names(yeastCPDMismatchDataAllRepsFiltered)[i],
+    repitition = "all_reps", filtering = "TGG_filtered"
+  ))
+}
+
 NHF1CPDMMFreqZScoresAllRepsFiltered = NHF1CPDTimepoints
@@
     timepoint = names(NHF1CPDMMFreqZScoresAllRepsFiltered)[i], includedMismatches = c("C>T")
+  ))
+}
+
+arabidopsisCPDMMFreqZScoresAllRepsFiltered = arabidopsisCPDTimepoints
+for (i in seq_along(arabidopsisCPDMMFreqZScoresAllRepsFiltered)) {
+  arabidopsisCPDMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
+    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+    cellType = "Arabidopsis", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
+    timepoint = names(arabidopsisCPDMMFreqZScoresAllRepsFiltered)[i], includedMismatches = c("C>T")
+  ))
+}
+
+yeastCPDMMFreqZScoresAllRepsFiltered = yeastCPDTimepoints
+for (i in seq_along(yeastCPDMMFreqZScoresAllRepsFiltered)) {
+  yeastCPDMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
+    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+    cellType = "yeast", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
+    timepoint = names(yeastCPDMMFreqZScoresAllRepsFiltered)[i], includedMismatches = c("C>T")
   ))
@@
 
-```{r figure_5}
+```{r figure_5A}
 ### Just the 1h timepoint ###
@@
                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered)
+plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
+                                         title = "Arabidopsis CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
+                                         zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered)
+plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
+                                         title = "Yeast CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
+                                         zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered)
 
+### All timepoints together ###
+# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
+#                                          title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
+#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered)
+# plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
+#                                          title = "Arabidopsis CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
+#                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered)
+# plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
+#                                          title = "Yeast CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
+#                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered)
+```
+```{r figure_5B}
+### Just the 1h timepoint ###
+plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
+                                         title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
+                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered,
+                                         posType = FIVE_PRIME)
+plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
+                                         title = "Arabidopsis CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
+                                         zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
+                                         posType = FIVE_PRIME)
+plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
+                                         title = "Yeast CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
+                                         zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
+                                         posType = FIVE_PRIME)
+
+### All timepoints together ###
+# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
+#                                          title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
+#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered,
+#                                          posType = FIVE_PRIME)
+# plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
+#                                          title = "Arabidopsis CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
+#                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
+#                                          posType = FIVE_PRIME)
+# plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
+#                                          title = "Yeast CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
+#                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
+#                                          posType = FIVE_PRIME)
+```
+```{r figure_5C}
+### Just the 1h timepoint ###
 plotGroupedPositionStats(NHF1CPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
@@
 ### All timepoints together ###
-# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
-#                                          title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
-#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered)
-# 
 # plotGroupedPositionStats(NHF1CPDGroupedStatsAllRepsFiltered$three_prime,
@@
 #                          xAxisBreaks = c(22:25))
-
 ```
@@
 
-```{r figure_6}
+```{r figure_6A}
 ### Just the 1h timepoint ###
@@
                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
-                               expansionOffset = 10, minReadLength = 1, maxReadLength = 12)
-
-plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
-                               title = "NHF1 CPD 1h ALL Reps TGG-Filtered 3' Anchored Purine Freq",
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
-                               expansionOffset = 10, minReadLength = 13, maxReadLength = 25)
-
-plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
-                        title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored YR Freq",
-                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
-                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
-                        expansionOffset = 10, minReadLength = 13, maxReadLength = 25)
+                               expansionOffset = 10, minReadLength = 1, maxReadLength = 7)
 
@@
 #                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
-#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 12)
-# 
+#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 7)
+```
+```{r figure_6B}
+### Just the 1h timepoint ###
+plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
+                               title = "NHF1 CPD 1h ALL Reps TGG-Filtered 3' Anchored Purine Freq",
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
+                               expansionOffset = 10, minReadLength = 19, maxReadLength = 25)
+
+### All timepoints together ###
 # plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered, 
@@
 #                                posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
-#                                expansionOffset = 10, minReadLength = 13, maxReadLength = 25)
-# 
+#                                expansionOffset = 10, minReadLength = 19, maxReadLength = 25)
+```
+```{r figure_6C}
+### Just the 1h timepoint ###
+plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
+                        title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored YR Freq",
+                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
+                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
+                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25)
+
+### All timepoints together ###
 # plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
@@
 #                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
-#                         expansionOffset = 10, minReadLength = 13, maxReadLength = 25)
+#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25)
+```
+
+```{r read_figure_7_data}
+# Note: This file was created manually by combining/modifying a couple different files counting tandem mismatches.
+NHF1TandemMismatchCountsComparisonAllReps = fread(generateFilePath(
+  NHF1MismatchesByReadDataDirectory, dataTypeStrings$tandemMismatchCountsComparison, ".tsv",
+  cellType = "NHF1", repitition = "all_reps"
+))
+```
+
+```{r figure_7B}
+NHF1TandemMismatchCountsComparisonAllReps = NHF1TandemMismatchCountsComparisonAllReps[
+  Lesion == "CPD", Timepoint = "1h"
+]
+print(
+    ggplot(NHF1TandemMismatchCountsComparisonAllReps, aes(x = Mismatch_Type, y = Tandem_Mismatches_Count)) +
+      geom_bar(aes(fill = Search_Method), stat = "identity", position = "dodge") +
+      labs(title = "NHF1 CPD All Reps Tandem Mismatch Counts", x = "Mismatch Type", y = "Tandem Mismatch Count") +
+      blankBackground + defaultTextScaling
+  )
 ```

### 2022-06-24 R/DeaminationAnchoredExcisionSiteAnalysis.R
Fixes and tweaks to plot coloring
- Fixed an erroneous call to a scale_color function instead of scale_fill.
- Fixed a bug where plots that were supposed to use the default grey color weren't.

@@ -148,7 +148,7 @@ plotNucFreqVsReadLengthBarPlot = function(nucFreqTable, posType = THREE_PRIME,
     scale_x_continuous(breaks = xAxisBreaks)
 
   if (length(unique(nucFreqTable$Nucleotide)) == 1) {
-    plot = plot + theme(legend.position = "none") + scale_fill_grey()
+    plot = plot + theme(legend.position = "none") + scale_fill_manual(values = "grey35")
   } else {
     plot = plot + scale_fill_brewer(palette = "Set1")
   }

### 2022-06-24 R/DeaminationSequenceAndPositionAnalysis.R

@@ -298,10 +298,9 @@ plotGroupedPositionStats = function(threePrimeGroupedStats, fivePrimeGroupedStat
     scale_x_continuous(breaks = xAxisBreaks)
 
   if (all(aggregateData$Timepoint == "NONE")) {
-    groupedStatsPlot = groupedStatsPlot +
-      scale_color_grey(guide = "none")
+    groupedStatsPlot = groupedStatsPlot + scale_color_manual(values = "black")
   } else if (length(unique(aggregateData$Timepoint)) == 1) {
-    groupedStatsPlot = groupedStatsPlot + scale_color_grey()
+    groupedStatsPlot = groupedStatsPlot + scale_color_manual(values = "black")
   } else groupedStatsPlot = groupedStatsPlot + scale_color_brewer(palette = "Set1")
 
   print(groupedStatsPlot)
@@ -330,7 +329,7 @@ plotTrinucleotideContext = function(simplifiedMismatchTable, includedTypes = lis
       labs(title = title, x = "Trinucleotide Context", y = "Relative Frequency") +
       guides(x = guide_axis(angle = 45)) +
       theme(legend.position = "none", axis.text.x = element_text(size = 12)) +
-      blankBackground + defaultTextScaling + scale_color_brewer(palette = "Set1")
+      blankBackground + defaultTextScaling + scale_fill_brewer(palette = "Set1")
   )
 
 }

### 2022-06-24 R/PaperFigureGeneration.rmd
Finished first draft of figures

@@
 
-```{r figure_3A}
+```{r figure_3A, fig.width = 5, fig.height = 5}
 ### Just the 1h timepoint ###
@@
 ```
-```{r figure_3B}
+```{r figure_3B, fig.width = 6, fig.height = 5}
 ### Just the 1h timepoint ###
@@
 ```
-```{r figure_3C}
+```{r figure_3C, fig.width = 5, fig.height = 5}
 ### Just the 1h timepoint ###
@@
   yeastCPDMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
-    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+    yeastSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
     cellType = "yeast", lesion = "CPD", timepoint = names(yeastCPDMismatchDataAllRepsFiltered)[i],
@@
   yeastCPDMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
-    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+    yeastSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
     cellType = "yeast", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
@@
 
-```{r figure_5A}
+```{r figure_5A, fig.width = 5, fig.height = 5}
 ### Just the 1h timepoint ###
@@
                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered)
-plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
-                                         title = "Arabidopsis CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
+plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["ZT2"], includedTypes = c("C>T"),
+                                         title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered)
-plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
-                                         title = "Yeast CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
+plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["20min"], includedTypes = c("C>T"),
+                                         title = "Yeast CPD 20min All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered)
@@
 ```
-```{r figure_5B}
+```{r figure_5B, fig.width = 5, fig.height = 5}
 ### Just the 1h timepoint ###
@@
                                          posType = FIVE_PRIME)
-plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
-                                         title = "Arabidopsis CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
+plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["ZT2"], includedTypes = c("C>T"),
+                                         title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
                                          posType = FIVE_PRIME)
-plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
-                                         title = "Yeast CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
+plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["20min"], includedTypes = c("C>T"),
+                                         title = "Yeast CPD 20min All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
@@
 
-plotGroupedPositionStats(arabidopsisCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
-                         arabidopsisCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
+plotGroupedPositionStats(arabidopsisCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "ZT2"],
+                         arabidopsisCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "ZT2"],
                          POS_DIFF, title = "Arabidopsis CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
@@
 
-plotGroupedPositionStats(yeastCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
-                         yeastCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
+plotGroupedPositionStats(yeastCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "20min"],
+                         yeastCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "20min"],
                          POS_DIFF, title = "Yeast CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
@@
 
-```{r figure_6A}
+```{r figure_6A, fig.width = 6, fig.height = 5}
 ### Just the 1h timepoint ###
@@
 ```
-```{r figure_6B}
+```{r figure_6B, fig.width = 5, fig.height = 5}
 ### Just the 1h timepoint ###
@@
 ```
-```{r figure_6C}
+```{r figure_6C, fig.width = 5, fig.height = 5}
 ### Just the 1h timepoint ###
@@
 
-```{r figure_7B}
+```{r figure_7B, fig.width = 8, fig.height = 5}
 NHF1TandemMismatchCountsComparisonAllReps = NHF1TandemMismatchCountsComparisonAllReps[
-  Lesion == "CPD", Timepoint = "1h"
+  Lesion == "CPD" & Timepoint == "1h"
 ]
 print(
-    ggplot(NHF1TandemMismatchCountsComparisonAllReps, aes(x = Mismatch_Type, y = Tandem_Mismatches_Count)) +
-      geom_bar(aes(fill = Search_Method), stat = "identity", position = "dodge") +
-      labs(title = "NHF1 CPD All Reps Tandem Mismatch Counts", x = "Mismatch Type", y = "Tandem Mismatch Count") +
-      blankBackground + defaultTextScaling
+    ggplot(NHF1TandemMismatchCountsComparisonAllReps, aes(Mismatch_Type, Tandem_Mismatches_Count, fill = Search_Method)) +
+      geom_bar(stat = "identity", position = "dodge") +
+      labs(title = "NHF1 CPD 1h All Reps Tandem Mismatch Counts", x = "Mismatch Type", y = "Tandem Mismatch Count") +
+      geom_text(aes(label=Tandem_Mismatches_Count), position = position_dodge(width = 0.9), vjust = -0.25) +
+      blankBackground + defaultTextScaling + scale_fill_brewer(palette = "Set1")
   )
@@
 
-NHF1CPDGGtoAAMismatchDataAllRepsFiltered = NHF1CPDTimepoints
-for (i in seq_along(NHF1CPDGGtoAAMismatchDataAllRepsFiltered)) {
-  NHF1CPDGGtoAAMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
-    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
-    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
-    filtering = "TGG_filtered", includedMismatches = "GG>AA",
-    timepoint = names(NHF1CPDGGtoAAMismatchDataAllRepsFiltered)[i]
+NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered = NHF1CPDTimepoints
+for (i in seq_along(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered)) {
+  NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
+    NHF1ExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", includedMismatches = "CC>TT",
+    timepoint = names(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered)[i],
+    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
   ))
@@
 
-NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered = NHF1CPDTimepoints
-for (i in seq_along(NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered)) {
-  NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
-    directory = NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
-    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
-    filtering = "TGG_filtered", includedMismatches = "GG>AA",
-    timepoint = names(NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered)[i]
+NHF1CPDCCToTTGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
+for (i in seq_along(NHF1CPDCCToTTGroupedStatsAllRepsFiltered)) {
+  NHF1CPDCCToTTGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
+    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
+    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
+    strandPolarity = names(NHF1CPDCCToTTGroupedStatsAllRepsFiltered)[i], includedMismatches = "CC>TT"
+  ))
+}
+
+arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
+for (i in seq_along(arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered)) {
+  arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
+    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
+    cellType = "Arabidopsis", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
+    strandPolarity = names(arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered)[i], includedMismatches = "CC>TT"
+  ))
+}
+
+yeastCPDCCToTTGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
+for (i in seq_along(yeastCPDCCToTTGroupedStatsAllRepsFiltered)) {
+  yeastCPDCCToTTGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
+    yeastSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
+    cellType = "yeast", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
+    strandPolarity = names(yeastCPDCCToTTGroupedStatsAllRepsFiltered)[i], includedMismatches = "CC>TT"
   ))
@@
 
-```{r figure_8}
+```{r figure_8A, fig.width = 5, fig.height = 5}
 ### Just the 1h timepoint ###
 plotPositionAcrossTimepointAndReadLength(NHF1CPDCCtoTTMismatchDataAllRepsFiltered["1h"],
-                                         title = "NHF1 CPD 1h All Reps CC>TT Mismatch Pos Freq",
+                                         title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT Mismatch Pos Freq",
                                          zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered)
-
-plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered["1h"],
-                                         title = "NHF1 CPD 1h All Reps GG>AA Mismatch Pos Freq",
-                                         zScoreTables = NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered)
 
@@
 # plotPositionAcrossTimepointAndReadLength(NHF1CPDCCtoTTMismatchDataAllRepsFiltered,
-#                                          title = "NHF1 CPD All Reps CC>TT Mismatch Pos Freq",
+#                                          title = "NHF1 CPD All Reps TGG-Filtered CC>TT Mismatch Pos Freq",
 #                                          zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered)
-# 
-# plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered,
-#                                          title = "NHF1 CPD All Reps GG>AA Mismatch Pos Freq",
-#                                          zScoreTables = NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered)
+```
+```{r figure_8B, fig.width = 5, fig.height = 5}
+### Just the 1h timepoint ###
+plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered$`1h`,
+                        title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT 3' Anchored YR Freq",
+                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
+                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
+                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25)
+
+### All timepoints together ###
+# plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered,
+#                         title = "NHF1 CPD All Reps TGG-Filtered CC>TT 3' Anchored YR Freq",
+#                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
+#                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
+#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25)
+```
+```{r figure_8C}
+### Just the 1h timepoint ###
+plotGroupedPositionStats(NHF1CPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                         NHF1CPDCCToTTGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
+                         POS_DIFF, title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
+                         xAxisBreaks = c(22:30))
+
+### All timepoints together ###
+# plotGroupedPositionStats(NHF1CPDCCToTTGroupedStatsAllRepsFiltered$three_prime,
+#                          NHF1CPDCCToTTGroupedStatsAllRepsFiltered$five_prime,
+#                          POS_DIFF, title = "NHF1 CPD All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
+#                          xAxisBreaks = c(22:30))
+```
+```{r figure_8D}
+### Just the 1h timepoint ###
+plotGroupedPositionStats(arabidopsisCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "ZT2"],
+                         arabidopsisCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "ZT2"],
+                         POS_DIFF, title = "Arabidopsis CPD 1h All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
+                         xAxisBreaks = c(24:30))
+
+### All timepoints together ###
+# plotGroupedPositionStats(arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered$three_prime,
+#                          arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered$five_prime,
+#                          POS_DIFF, title = "Arabidopsis CPD All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
+#                          xAxisBreaks = c(24:30))
+```
+```{r figure_8E}
+### Just the 1h timepoint ###
+plotGroupedPositionStats(yeastCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "20min"],
+                         yeastCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "20min"],
+                         POS_DIFF, title = "Yeast CPD 1h All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
+                         xAxisBreaks = c(22:25))
+
+### All timepoints together ###
+# plotGroupedPositionStats(yeastCPDCCToTTGroupedStatsAllRepsFiltered$three_prime,
+#                          yeastCPDCCToTTGroupedStatsAllRepsFiltered$five_prime,
+#                          POS_DIFF, title = "Yeast CPD All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
+#                          xAxisBreaks = c(22:25))
 ```
@@
 
-```{r read_figure_S3_data}
+```{r figure_S3, fig.width = 9, fig.height = 5}
+plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered,
+                               title = "NHF1 CPD ALL Reps TGG-Filtered 5' Anchored Purine Freq",
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
+                               expansionOffset = 10, minReadLength = 1, maxReadLength = 7)
+```
+
+```{r read_figure_S4_data}
 arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = arabidopsisCPDTimepoints
@@
 
-```{r figure_S3}
-plotSequenceFrequencies(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$ZT2,
+```{r figure_S4, fig.width = 9, fig.height = 5}
+plotSequenceFrequencies(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
                         title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered 3' Anchored YR Freq",
@@
                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
-                        expansionOffset = 10, minReadLength = 15, maxReadLength = 25)
+                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25)
 
-plotSequenceFrequencies(yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`20min`,
+plotSequenceFrequencies(yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
                         title = "Yeast CPD 20min All Reps TGG-Filtered 3' Anchored YR Freq",
@@
                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
-                        expansionOffset = 10, minReadLength = 11, maxReadLength = 19)
+                        expansionOffset = 10, minReadLength = 13, maxReadLength = 19)
 ```
+
+```{r read_figure_S5_data}
+NHF1CPDGGtoAAMismatchDataAllRepsFiltered = NHF1CPDTimepoints
+for (i in seq_along(NHF1CPDGGtoAAMismatchDataAllRepsFiltered)) {
+  NHF1CPDGGtoAAMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
+    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
+    filtering = "TGG_filtered", includedMismatches = "GG>AA",
+    timepoint = names(NHF1CPDGGtoAAMismatchDataAllRepsFiltered)[i]
+  ))
+}
+
+NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered = NHF1CPDTimepoints
+for (i in seq_along(NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered)) {
+  NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
+    directory = NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
+    filtering = "TGG_filtered", includedMismatches = "GG>AA",
+    timepoint = names(NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered)[i]
+  ))
+}
+```
+
+```{r figure_S5, fig.width = 9, fig.height = 5}
+plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered,
+                                         title = "NHF1 CPD All Reps GG>AA Mismatch Pos Freq",
+                                         zScoreTables = NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered)
+```

### 2022-06-29 R/PaperFigureGeneration.rmd
Added z-score calculations for sequence frequency plotting
- A background mean and standard deviation are calculated from a given number of bases at the start (near 0) or end of the x-axis. The bar plot is colored based on whether the frequency at each position meets a z-score threshold with respect to this background.
- Implemented the above statistical methods into YR-frequency plots for PaperFigureGeneration.
- Also fixed a bug where mismatch position frequency plotting was using black instead of grey35 bars.

@@
                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
-                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25)
+                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8)
 
@@
 #                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
-#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25)
+#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8)
 ```
@@
                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
-                        expansionOffset = 10, minReadLength = 13, maxReadLength = 19)
+                        expansionOffset = 10, minReadLength = 13, maxReadLength = 19, endBasedBackgroundNum = 8)
 ```

### 2022-06-29 R/DeaminationAnchoredExcisionSiteAnalysis.R

@@ -345,18 +345,27 @@ plotSequenceEnrichment = function(enrichmentTablesByTimepoint, posType = THREE_P
 
 
 # Plot nucleotide frequencies for a series of read lengths.
+# Notes on statistics:
+#   A background mean and standard deviation are calculated from a given number of bases at the
+#   start (near 0) or end of the x-axis. The bar plot is colored based on whether the frequency at each position
+#   meets a z-score threshold with respect to this background.
 plotSequenceFrequencies = function(seqFreqTablesByTimepoint, posType = THREE_PRIME,
                                    title = "Seq Freq by Length and Timepoint", yAxisLabel = "Sequence Frequency",
                                    secondaryYAxisLabel = "Read Length", yStripFontSize = 16,
                                    showThreePrimeCutSite = FALSE, showFivePrimeCutSite = FALSE,
                                    expansionOffset = 0, querySequences = c("TGG"), xAxisBreaks = -3:3*10,
-                                   minReadLength = NULL, maxReadLength = NULL) {
+                                   minReadLength = NULL, maxReadLength = NULL,
+                                   startBasedBackgroundNum = NULL, endBasedBackgroundNum = NULL, zScoreCutoff = 3) {
 
   if (posType == THREE_PRIME) {
     xAxisLabel = "3' Relative Position"
   } else if (posType == FIVE_PRIME) {
     xAxisLabel = "5' Relative Position"
   } else stop("Unrecognized value for posType parameter.")
+
+  if (!is.null(startBasedBackgroundNum) && !is.null(endBasedBackgroundNum)) {
+    stop("Two background position determinants given")
+  }
 
   # If passed a single data.table, no timepoint information is present.
   # Otherwise, combine the given tables into one agggregate table.
@@ -376,10 +385,37 @@ plotSequenceFrequencies = function(seqFreqTablesByTimepoint, posType = THREE_PRI
   if (!is.null(minReadLength)) fullFrequencyTable = fullFrequencyTable[Read_Length >= minReadLength]
   if (!is.null(maxReadLength)) fullFrequencyTable = fullFrequencyTable[Read_Length <= maxReadLength]
 
+  # Determine zScores from background positions, if specified.
+  if (!is.null(startBasedBackgroundNum) || !is.null(endBasedBackgroundNum)) {
+    if (!is.null(startBasedBackgroundNum)) {
[…]

### 2022-06-29 R/DeaminationSequenceAndPositionAnalysis.R

@@ -134,7 +134,7 @@ plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTy
   if (!is.null(zScoreTables)) {
     plot = plot +
       geom_bar(aes(fill = Meets_Cutoff), stat = "identity") +
-      scale_fill_manual(values = c("TRUE" = "red", "FALSE" = "black"), guide = "none")
+      scale_fill_manual(values = c("TRUE" = "red", "FALSE" = "grey35"), guide = "none")
   } else {
     plot = plot + geom_bar(stat = "identity")
   }

### 2022-07-11 R/NHF1DeaminationAnchoredExcisionSiteDataGeneration.rmd
Third generation of figure plots
- Updated plotting notebook
- Added parameters to plotting functions where necessary, such as axis labels or limits.
- Added TG-filtering option in NHF1 notebooks.

@@
     input: select
-    choices: [NONE, TGG_filtered]
+    choices: [NONE, TGG_filtered, TG_filtered]
 ---

### 2022-07-11 R/PaperFigureGeneration.rmd
Third generation of figure plots
- Updated plotting notebook
- Added parameters to plotting functions where necessary, such as axis labels or limits.
- Added TG-filtering option in NHF1 notebooks.

--- 2022-06-24 R/PaperFigureGeneration.rmd
@@
 
-```{r read_figure_2_data}
+```{r read_figure_1_data}
 NHF1CPDMismatchDataAllReps = NHF1CPDTimepoints
@@
 
-```{r figure_2A}
-plotMismatchTypeFrequencies(NHF1CPDMismatchDataAllReps$`1h`,
+```{r figure_1B}
+plotMismatchTypeFrequencies(NHF1CPDMismatchDataAllReps$`1h`, ylim = c(0,0.8),
                             title = "NHF1 CPD 1h All Reps Mismatch Type Frequencies")
 ```
-```{r figure_2B}
+```{r figure_1C}
 plotTrinucleotideContext(NHF1CPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
@@
 ```
-```{r figure_2C}
+```{r figure_1D}
 plotMismatchPositionFrequencies(NHF1CPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
@@
 ```
-```{r figure_2D}
-plotMismatchPositionFrequencies(NHF1CPDMismatchDataAllReps$`1h`, omittedTypes = c("C>T"),
-                                title = "NHF1 CPD 1h All Reps !C>T Mismatch Pos Frequencies")
-```
 
-```{r read_figure_3_data}
+```{r read_figure_2_data}
 NHF1CPDMMFreqZScoresAllReps = NHF1CPDTimepoints
@@
 
-```{r figure_3A, fig.width = 5, fig.height = 5}
+```{r figure_2A, fig.width = 5, fig.height = 6}
 ### Just the 1h timepoint ###
@@
                                          title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Freq",
+                                         yAxisLabel = "Relative C>T Frequency",
                                          zScoreTables = NHF1CPDMMFreqZScoresAllReps)
@@
 #                                          title = "NHF1 CPD All Reps C>T Mismatch Pos Freq",
+#                                          yAxisLabel = "Relative C>T Frequency",
 #                                          zScoreTables = NHF1CPDMMFreqZScoresAllReps)
 ```
-```{r figure_3B, fig.width = 6, fig.height = 5}
+```{r figure_2B, fig.width = 6.5, fig.height = 6}
 ### Just the 1h timepoint ###
@@
                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
-                               expansionOffset = 10, minReadLength = 1, maxReadLength = 7)
+                               expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
+                               xAxisLabel = "Mismatch Relative Position")
 
@@
 #                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
-#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 7)
+#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
+#                                xAxisLabel = "Mismatch Relative Position")
 ```
-```{r figure_3C, fig.width = 5, fig.height = 5}
+```{r figure_2C, fig.width = 5, fig.height = 6}
 ### Just the 1h timepoint ###
@@
                         showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE, querySequences = c("TGG"),
-                        expansionOffset = 10, minReadLength = 21, maxReadLength = 27)
+                        expansionOffset = 10, minReadLength = 20, maxReadLength = 27,
+                        yAxisLabel = "TGG Trinucleotide Frequency", defaultColor = "Black")
 
@@
 #                         showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE, querySequences = c("TGG"),
-#                         expansionOffset = 10, minReadLength = 21, maxReadLength = 27)
+#                         expansionOffset = 10, minReadLength = 21, maxReadLength = 27,
+#                         yAxisLabel = "TGG Trinucleotide Frequency", defaultColor = "Black")
 ```
 
-```{r read_figure_5_data}
-NHF1CPDMismatchDataAllRepsFiltered = NHF1CPDTimepoints
-for (i in seq_along(NHF1CPDMismatchDataAllRepsFiltered)) {
-  NHF1CPDMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
+```{r read_figure_3_data}
+NHF1CPDMismatchDataAllRepsTGGFiltered = NHF1CPDTimepoints
+for (i in seq_along(NHF1CPDMismatchDataAllRepsTGGFiltered)) {
+  NHF1CPDMismatchDataAllRepsTGGFiltered[[i]] = fread(generateFilePath(
     NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
-    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1CPDMismatchDataAllRepsFiltered)[i],
+    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1CPDMismatchDataAllRepsTGGFiltered)[i],
     repitition = "all_reps", filtering = "TGG_filtered"
@@
 
-NHF1CPDMMFreqZScoresAllRepsFiltered = NHF1CPDTimepoints
-for (i in seq_along(NHF1CPDMMFreqZScoresAllRepsFiltered)) {
-  NHF1CPDMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
+NHF1CPDMMFreqZScoresAllRepsTGGFiltered = NHF1CPDTimepoints
+for (i in seq_along(NHF1CPDMMFreqZScoresAllRepsTGGFiltered)) {
+  NHF1CPDMMFreqZScoresAllRepsTGGFiltered[[i]] = fread(generateFilePath(
     NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
     cellType = "NHF1", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
-    timepoint = names(NHF1CPDMMFreqZScoresAllRepsFiltered)[i], includedMismatches = c("C>T")
+    timepoint = names(NHF1CPDMMFreqZScoresAllRepsTGGFiltered)[i], includedMismatches = c("C>T")
   ))
@@
 
-```{r figure_5A, fig.width = 5, fig.height = 5}
+```{r figure_3A, fig.width = 5, fig.height = 5}
 ### Just the 1h timepoint ###
-plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
+plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered["1h"], includedTypes = c("C>T"),
                                          title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
-                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered)
-plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["ZT2"], includedTypes = c("C>T"),
-                                         title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered C>T Mismatch Pos Freq",
-                                         zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered)
-plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["20min"], includedTypes = c("C>T"),
-                                         title = "Yeast CPD 20min All Reps TGG-Filtered C>T Mismatch Pos Freq",
-                                         zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered)
-
-### All timepoints together ###
-# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
-#                                          title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
-#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered)
-# plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
-#                                          title = "Arabidopsis CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
-#                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered)
-# plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
-#                                          title = "Yeast CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
-#                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered)
-```
-```{r figure_5B, fig.width = 5, fig.height = 5}
-### Just the 1h timepoint ###
-plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
-                                         title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
-                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered,
-                                         posType = FIVE_PRIME)
+                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGGFiltered,
+                                         yAxisLabel = "Relative C>T Frequency")
 plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["ZT2"], includedTypes = c("C>T"),
@@
                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
-                                         posType = FIVE_PRIME)
+                                         yAxisLabel = "Relative C>T Frequency")
 plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["20min"], includedTypes = c("C>T"),
@@
                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
-                                         posType = FIVE_PRIME)
+                                         yAxisLabel = "Relative C>T Frequency")
 
 ### All timepoints together ###
-# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
+# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered, includedTypes = c("C>T"),
 #                                          title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
-#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered,
-#                                          posType = FIVE_PRIME)
+#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGGFiltered,
+#                                          yAxisLabel = "Relative C>T Frequency")
 # plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
@@
 #                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
-#                                          posType = FIVE_PRIME)
+#                                          yAxisLabel = "Relative C>T Frequency")
 # plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
@@
 #                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
-#                                          posType = FIVE_PRIME)
+#                                          yAxisLabel = "Relative C>T Frequency")
 ```
-```{r figure_5C}
+```{r figure_3B, fig.width = 5, fig.height = 5}
+### Just the 1h timepoint ###
+plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered["1h"], includedTypes = c("C>T"),
+                                         title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
+                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGGFiltered,
+                                         posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
+plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["ZT2"], includedTypes = c("C>T"),
+                                         title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered C>T Mismatch Pos Freq",
+                                         zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
+                                         posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
+plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["20min"], includedTypes = c("C>T"),
+                                         title = "Yeast CPD 20min All Reps TGG-Filtered C>T Mismatch Pos Freq",
+                                         zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
+                                         posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
+
+### All timepoints together ###
+# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered, includedTypes = c("C>T"),
+#                                          title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
+#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGGFiltered,
+#                                          posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
+# plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
+#                                          title = "Arabidopsis CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
+#                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
+#                                          posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
+# plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
+#                                          title = "Yeast CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
+#                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
+#                                          posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
+```
+```{r figure_3C, fig.width = 7.5, fig.height = 5}
 ### Just the 1h timepoint ###
@@
 
-```{r read_figure_6_data}
-NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
-  NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
-  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
-  strandPolarity = "five_prime", anchored = TRUE, filtering = "TGG_filtered"
-))
-
+```{r read_figure_4_data}
 NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
@@
 }
-
 ```
 
-```{r figure_6A, fig.width = 6, fig.height = 5}
-### Just the 1h timepoint ###
-plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
-                               title = "NHF1 CPD 1h All Reps TGG-Filtered 5' Anchored Nuc Freq",
-                               secondaryYAxisLabel = "3' Cut Site Distance",
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
-                               expansionOffset = 10, minReadLength = 1, maxReadLength = 7)
-
-### All timepoints together ###
-# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered, 
-#                                title = "NHF1 CPD All Reps TGG-Filtered 5' Anchored Nuc Freq",
-#                                secondaryYAxisLabel = "3' Cut Site Distance",
-#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
-#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 7)
-```
-```{r figure_6B, fig.width = 5, fig.height = 5}
+```{r figure_4A, fig.width = 5, fig.height = 6}
 ### Just the 1h timepoint ###
@@
                                posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
-                               expansionOffset = 10, minReadLength = 19, maxReadLength = 25)
+                               expansionOffset = 10, minReadLength = 19, maxReadLength = 25,
+                               xAxisLabel = "Mismatch Relative Position")
 
@@
 #                                posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
-#                                expansionOffset = 10, minReadLength = 19, maxReadLength = 25)
+#                                expansionOffset = 10, minReadLength = 19, maxReadLength = 25,
+#                                xAxisLabel = "Mismatch Relative Position")
 ```
-```{r figure_6C, fig.width = 5, fig.height = 5}
+```{r figure_4B, fig.width = 5, fig.height = 5}
 ### Just the 1h timepoint ###
@@
                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
-                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25)
+                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
+                        endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
 
@@
 #                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
-#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25)
+#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
+#                         endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
 ```
 
-```{r read_figure_7_data}
+```{r read_figure_5_data}
 # Note: This file was created manually by combining/modifying a couple different files counting tandem mismatches.
@@
 
-```{r figure_7B, fig.width = 8, fig.height = 5}
+```{r figure_5B, fig.width = 8, fig.height = 5}
 NHF1TandemMismatchCountsComparisonAllReps = NHF1TandemMismatchCountsComparisonAllReps[
@@
       labs(title = "NHF1 CPD 1h All Reps Tandem Mismatch Counts", x = "Mismatch Type", y = "Tandem Mismatch Count") +
-      geom_text(aes(label=Tandem_Mismatches_Count), position = position_dodge(width = 0.9), vjust = -0.25) +
-      blankBackground + defaultTextScaling + scale_fill_brewer(palette = "Set1")
+      geom_text(aes(label=Tandem_Mismatches_Count), position = position_dodge(width = 0.9), vjust = -0.25, size = 5) +
+      blankBackground + defaultTextScaling + scale_fill_brewer(palette = "Set1") + coord_cartesian(ylim = c(0,200000))
   )
@@
 
-```{r read_figure_8_data}
+```{r read_figure_6_data}
 NHF1CPDCCtoTTMismatchDataAllRepsFiltered = NHF1CPDTimepoints
@@
 
-```{r figure_8A, fig.width = 5, fig.height = 5}
+```{r figure_6A, fig.width = 5, fig.height = 5}
 ### Just the 1h timepoint ###
@@
                                          title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT Mismatch Pos Freq",
-                                         zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered)
+                                         zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered,
+                                         yAxisLabel = "Relative C>T Frequency")
 
@@
 #                                          title = "NHF1 CPD All Reps TGG-Filtered CC>TT Mismatch Pos Freq",
-#                                          zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered)
+#                                          zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered,
+#                                          yAxisLabel = "Relative C>T Frequency")
 ```
-```{r figure_8B, fig.width = 5, fig.height = 5}
+```{r figure_6B, fig.width = 5, fig.height = 5}
 ### Just the 1h timepoint ###
@@
 #                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
-#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25)
+#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
+#                         endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
 ```
-```{r figure_8C}
+```{r figure_6C, fig.width = 7.5, fig.height = 5}
 ### Just the 1h timepoint ###
@@
 ```
-```{r figure_8D}
+```{r figure_6D, fig.width = 7.5, fig.height = 5}
 ### Just the 1h timepoint ###
-plotGroupedPositionStats(arabidopsisCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "ZT2"],
-                         arabidopsisCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "ZT2"],
+plotGroupedPositionStats(arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "ZT2"],
+                         arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered$five_prime[Timepoint == "ZT2"],
                          POS_DIFF, title = "Arabidopsis CPD 1h All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
@@
 ```
-```{r figure_8E}
+```{r figure_6E, fig.width = 7.5, fig.height = 5}
 ### Just the 1h timepoint ###
-plotGroupedPositionStats(yeastCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "20min"],
-                         yeastCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "20min"],
+plotGroupedPositionStats(yeastCPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "20min"],
+                         yeastCPDCCToTTGroupedStatsAllRepsFiltered$five_prime[Timepoint == "20min"],
                          POS_DIFF, title = "Yeast CPD 1h All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
@@
                                 title = "GM12878 Cisplatin 90min All Reps Mismatch Pos Frequencies")
+
+plotMismatchPositionFrequencies(NHF1CPDMismatchDataAllReps$`1h`, omittedTypes = c("C>T"),
+                                title = "NHF1 CPD 1h All Reps !C>T Mismatch Pos Frequencies")
 ```
@@
 plotMismatchPositionFrequencies(CSBCPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
-                                title = "CS-B CPD 1h All Reps Mismatch Pos Frequencies")
+                                title = "CS-B CPD 1h All Reps Mismatch Pos Frequencies",
+                                ylim = c(0,0.25))
 
@@
 plotMismatchPositionFrequencies(XPCCPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
-                                title = "XP-C CPD 1h All Reps Mismatch Pos Frequencies")
+                                title = "XP-C CPD 1h All Reps Mismatch Pos Frequencies",
+                                ylim = c(0,0.25))
 ```
 
-```{r figure_S3, fig.width = 9, fig.height = 5}
-plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered,
+```{r read_figure_S3_data}
+NHF1FivePrimeMismatchCPDNucFreqAllRepsTGGFiltered = fread(generateFilePath(
+  NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
+  strandPolarity = "five_prime", anchored = TRUE, filtering = "TGG_filtered"
+))
+NHF1FivePrimeMismatchCPDNucFreqAllRepsTGFiltered = fread(generateFilePath(
+  NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
+  strandPolarity = "five_prime", anchored = TRUE, filtering = "TG_filtered"
+))
+
+NHF1CPDMismatchDataAllRepsTGFiltered = NHF1CPDTimepoints
+for (i in seq_along(NHF1CPDMismatchDataAllRepsTGFiltered)) {
+  NHF1CPDMismatchDataAllRepsTGFiltered[[i]] = fread(generateFilePath(
+    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1CPDMismatchDataAllRepsTGFiltered)[i],
+    repitition = "all_reps", filtering = "TG_filtered"
+  ))
+}
+
+NHF1CPDMMFreqZScoresAllRepsTGFiltered = NHF1CPDTimepoints
+for (i in seq_along(NHF1CPDMMFreqZScoresAllRepsTGFiltered)) {
+  NHF1CPDMMFreqZScoresAllRepsTGFiltered[[i]] = fread(generateFilePath(
+    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", filtering = "TG_filtered",
+    timepoint = names(NHF1CPDMMFreqZScoresAllRepsTGFiltered)[i], includedMismatches = c("C>T")
+  ))
+}
+```
+
+```{r figure_S3A, fig.width = 6.5, fig.height = 6}
+### Just the 1h timepoint ###
+plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsTGGFiltered[Timepoint == "1h"], 
+                               title = "NHF1 CPD 1h All Reps TGG-Filtered 5' Anchored Nuc Freq",
+                               secondaryYAxisLabel = "3' Cut Site Distance",
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
+                               expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
+                               xAxisLabel = "Mismatch Relative Position")
+
+### All timepoints together ###
+# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsTGGFiltered, 
+#                                title = "NHF1 CPD All Reps TGG-Filtered 5' Anchored Nuc Freq",
+#                                secondaryYAxisLabel = "3' Cut Site Distance",
+#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
+#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
+#                                xAxisLabel = "Mismatch Relative Position")
+```
+
+```{r figure_S3B, fig.width = 6.5, fig.height = 6}
+### Just the 1h timepoint ###
+plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsTGFiltered[Timepoint == "1h"], 
+                               title = "NHF1 CPD 1h All Reps TG-Filtered 5' Anchored Nuc Freq",
+                               secondaryYAxisLabel = "3' Cut Site Distance",
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
+                               expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
+                               xAxisLabel = "Mismatch Relative Position")
+
+### All timepoints together ###
+# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsTGFiltered, 
+#                                title = "NHF1 CPD All Reps TG-Filtered 5' Anchored Nuc Freq",
+#                                secondaryYAxisLabel = "3' Cut Site Distance",
+#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
+#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
+#                                xAxisLabel = "Mismatch Relative Position")
+```
+
+```{r figure_S3D, fig.width = 5, fig.height = 5}
+### Just the 1h timepoint ###
+plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGFiltered["1h"], includedTypes = c("C>T"),
+                                         title = "NHF1 CPD 1h All Reps TG-Filtered C>T Mismatch Pos Freq",
+                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGFiltered,
+                                         posType = THREE_PRIME, yAxisLabel = "Relative C>T Frequency")
+
+### All timepoints together ###
+# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGFiltered, includedTypes = c("C>T"),
+#                                          title = "NHF1 CPD All Reps TG-Filtered C>T Mismatch Pos Freq",
+#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGFiltered,
+#                                          posType = THREE_PRIME, yAxisLabel = "Relative C>T Frequency")
+```
+
+```{r figure_S4, fig.width = 9, fig.height = 5}
+plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsTGGFiltered,
                                title = "NHF1 CPD ALL Reps TGG-Filtered 5' Anchored Purine Freq",
@@
                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
-                               expansionOffset = 10, minReadLength = 1, maxReadLength = 7)
+                               expansionOffset = 10, minReadLength = 1, maxReadLength = 7,
+                               xAxisLabel = "Mismatch Relative Position")
 ```
 
-```{r read_figure_S4_data}
+```{r read_figure_S5_data}
 arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = arabidopsisCPDTimepoints
@@
 
-```{r figure_S4, fig.width = 9, fig.height = 5}
+```{r figure_S5, fig.width = 9, fig.height = 5}
 plotSequenceFrequencies(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
@@
                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
-                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25)
+                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
+                        endBasedCheckPositions = 10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
 
@@
                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
-                        expansionOffset = 10, minReadLength = 13, maxReadLength = 19)
+                        expansionOffset = 10, minReadLength = 13, maxReadLength = 19, endBasedBackgroundNum = 8,
+                        endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
 ```
 
-```{r read_figure_S5_data}
+```{r read_figure_S6_data}
 NHF1CPDGGtoAAMismatchDataAllRepsFiltered = NHF1CPDTimepoints
@@
 
-```{r figure_S5, fig.width = 9, fig.height = 5}
+```{r figure_S6, fig.width = 9, fig.height = 5}
 plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered,
                                          title = "NHF1 CPD All Reps GG>AA Mismatch Pos Freq",
-                                         zScoreTables = NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered)
+                                         zScoreTables = NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered,
+                                         yAxisLabel = "Relative GG>AA Frequency")
 ```

### 2022-07-11 R/DeaminationAnchoredExcisionSiteAnalysis.R

@@ -109,15 +109,17 @@ plotNucFreqVsReadLengthBarPlot = function(nucFreqTable, posType = THREE_PRIME,
                                           yStripFontSize = 16,
                                           combineNucleotides = list(), combinedNames = list(),
                                           showThreePrimeCutSite = FALSE, showFivePrimeCutSite = FALSE,
-                                          expansionOffset = 0, xAxisBreaks = -3:3*10,
+                                          expansionOffset = 0, xAxisBreaks = -3:3*10, xAxisLabel = NULL,
                                           ylim = c(0,1.2), yAxisBreaks = c(0,0.5,1),
                                           minReadLength = NULL, maxReadLength = NULL) {
 
-  if (posType == THREE_PRIME) {
-    xAxisLabel = "3' Relative Position"
-  } else if (posType == FIVE_PRIME) {
-    xAxisLabel = "5' Relative Position"
-  } else stop("Unrecognized value for posType parameter.")
+  if (is.null(xAxisLabel)) {
+    if (posType == THREE_PRIME) {
+      xAxisLabel = "3' Relative Position"
+    } else if (posType == FIVE_PRIME) {
+      xAxisLabel = "5' Relative Position"
+    } else stop("Unrecognized value for posType parameter.")
+  }
 
   if (length(combineNucleotides) > 0) {
     nucFreqTable = combineNucleotideFrequencies(nucFreqTable, combineNucleotides, combinedNames)
@@ -348,20 +350,25 @@ plotSequenceEnrichment = function(enrichmentTablesByTimepoint, posType = THREE_P
 # Notes on statistics:
 #   A background mean and standard deviation are calculated from a given number of bases at the
 #   start (near 0) or end of the x-axis. The bar plot is colored based on whether the frequency at each position
-#   meets a z-score threshold with respect to this background.
+#   meets a z-score threshold with respect to this background. The positions which are checked can be specified
+#   using the same start- or end-based notation.
 plotSequenceFrequencies = function(seqFreqTablesByTimepoint, posType = THREE_PRIME,
                                    title = "Seq Freq by Length and Timepoint", yAxisLabel = "Sequence Frequency",
[…]

### 2022-07-11 R/DeaminationSequenceAndPositionAnalysis.R

@@ -25,11 +25,11 @@ getReadLengthAndGCContent = function(table) {
 
 
 # Displays the frequencies of each mismatch type.
-plotMismatchTypeFrequencies = function(mismatchTable, title = "Mismatch Type Frequency") {
+plotMismatchTypeFrequencies = function(mismatchTable, title = "Mismatch Type Frequency", ylim = NULL) {
 
   print(
     ggplot(mismatchTable[, .N, by = Mismatch][, Freq := N/sum(N)], aes(x = Mismatch, y = Freq)) +
-      geom_bar(stat = "identity") +
+      geom_bar(stat = "identity") + coord_cartesian(ylim = ylim) +
       labs(title = title, x = "Mismatch Type", y = "Relative Frequency") +
       blankBackground + defaultTextScaling + theme(axis.text = element_text(size = 15))
   )
@@ -39,7 +39,7 @@ plotMismatchTypeFrequencies = function(mismatchTable, title = "Mismatch Type Fre
 # Displays the frequencies of positions for the chosen mismatch types.
 # (Types can be chosen by inclusion or omission)
 plotMismatchPositionFrequencies = function(mismatchTable, includedTypes = list(), omittedTypes = list(),
-                                           title = "Position Frequency", posType = THREE_PRIME) {
+                                           title = "Position Frequency", posType = THREE_PRIME, ylim = NULL) {
 
   if (posType == THREE_PRIME) {
     xAxisLabel = "3' Relative Position"
@@ -61,7 +61,7 @@ plotMismatchPositionFrequencies = function(mismatchTable, includedTypes = list()
 
   print(
     ggplot(frequencyData, aes(x = Position, y = Freq)) +
-      geom_bar(stat = "identity") +
+      geom_bar(stat = "identity") + coord_cartesian(ylim = ylim) +
       labs(title = title, x = xAxisLabel, y = "Relative Frequency") +
       blankBackground + defaultTextScaling
   )
@@ -74,7 +74,7 @@ plotMismatchPositionFrequencies = function(mismatchTable, includedTypes = list()
 plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTypes = list(), omittedTypes = list(),
                                                     title = "Mismatch Position Frequencies", posType = THREE_PRIME,
                                                     zScoreTables = NULL, zScoreCutoff = 4, xAxisBreaks = -3:3*10,
[…]

### 2022-07-12 R/PaperFigureGeneration.rmd
Added asterisk display as alternative to p-value

@@
 
-```{r figure_4A, fig.width = 5, fig.height = 6}
+```{r figure_4A, fig.width = 6.5, fig.height = 6}
+### Just the 1h timepoint ###
+plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
+                               title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored Nuc Freq",
+                               secondaryYAxisLabel = "5' Cut Site Distance",
+                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
+                               expansionOffset = 10, minReadLength = 19, maxReadLength = 25,
+                               xAxisLabel = "Mismatch Relative Position")
+
+### All timepoints together ###
+# plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered, 
+#                                title = "NHF1 CPD All Reps TGG-Filtered 3' Anchored Nuc Freq",
+#                                secondaryYAxisLabel = "5' Cut Site Distance",
+#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
+#                                expansionOffset = 10, minReadLength = 19, maxReadLength = 25,
+#                                xAxisLabel = "Mismatch Relative Position")}
+
+```
+
+```{r figure_4B, fig.width = 5, fig.height = 6}
 ### Just the 1h timepoint ###
@@
 ```
-```{r figure_4B, fig.width = 5, fig.height = 5}
-### Just the 1h timepoint ###
+```{r figure_4C, fig.width = 5, fig.height = 5}
+### Just the 1h timepoint (asterisks) ###
 plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
@@
                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
-                        endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
+                        endBasedCheckPositions = -10, xAxisLabel = "Mismatch Relative Position",
+                        significanceAsteriskBreakpoints = c(1e-6, 1e-9))
+
+### Just the 1h timepoint (full p-values) ###
+# plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
+#                         title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored YR Freq",
+#                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
+#                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
+#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
+#                         endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
 

### 2022-07-12 R/DeaminationAnchoredExcisionSiteAnalysis.R

@@ -360,7 +360,7 @@ plotSequenceFrequencies = function(seqFreqTablesByTimepoint, posType = THREE_PRI
                                    minReadLength = NULL, maxReadLength = NULL,
                                    startBasedBackgroundNum = NULL, endBasedBackgroundNum = NULL, zScoreCutoff = 3,
                                    startBasedCheckPositions = NULL, endBasedCheckPositions = NULL, displayPValue = FALSE,
-                                   xAxisLabel = NULL, defaultColor = "grey35") {
+                                   significanceAsteriskBreakpoints = NULL, xAxisLabel = NULL, defaultColor = "grey35") {
 
   if (is.null(xAxisLabel)) {
     if (posType == THREE_PRIME) {
@@ -448,6 +448,13 @@ plotSequenceFrequencies = function(seqFreqTablesByTimepoint, posType = THREE_PRI
   if (displayPValue) {
     plot = plot + geom_text(aes(label = ifelse(Relevant & Significant, paste0("p=",format(signif(P_Value, 3))), '')),
                             size = 3, hjust = 1, vjust = 0, nudge_x = -0.05, nudge_y = 0.05)
+  } else if (!is.null(significanceAsteriskBreakpoints)) {
+    fullFrequencyTable[,Asterisks := ""]
+    for (i in seq_along(significanceAsteriskBreakpoints)) {
+      fullFrequencyTable[Relevant & P_Value < significanceAsteriskBreakpoints[i],
+                         Asterisks := paste0(rep('*',i), collapse = '')]
+    }
+    plot = plot + geom_text(aes(label = Asterisks), size = 4, hjust = 0.5, vjust = 0, nudge_x = 0, nudge_y = -0.05)
   }
 
   if (all(fullFrequencyTable$Timepoint == "NONE")) {

### 2022-07-20 R/5'CutSiteAnalysisDataGeneration.rmd
Created r notebooks for analyzing the 5' cut site
- Specifically, these notebooks examine sequence frequencies across whole aligned read samples, not just mismatch based reads.
- Options are still available for TGG filtering.

---
title: "5'CutSiteAnalysisDataGeneration"
author: "Ben MOrledge-Hampton"
date: '2022-07-14'
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered, TG_filtered]
---

```{r setup_chunk}
library(knitr)

expansionOffset = 10

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
  filtering = readline("Filtering identifier (Input nothing for no filtering):")
  if (filtering == '') filtering = character()
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
  filtering = params$filtering
  if (filtering == "NONE") filtering = character()
}

if (is.na(bioinformaticsDirectory)) stop("No bioinformatics directory given.")

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data")
NHF1GeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "NHF1", "general_read_sequences")
GM12878GeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "GM12878", "general_read_sequences")
DmGeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "Dm", "general_read_sequences")

humanReadMinMax = c(22, 30)
drosophilaReadMinMax = c(23, 32)
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationAnchoredExcisionSiteAnalysis.R"))
```

```{r define_all_that_and_a_bag_of_chips_function}
cutSiteAnalysis = function(lesion, repetition, timepoint, cellType, directory,
                           querySequences, sequencesName, readMinMax) {
  readData = fread(generateFilePath(
    directory, dataTypeStrings$alignedReads, ".bed",
    cellType = cellType, lesion = lesion, timepoint = timepoint,
    repitition = repetition, expansionNum = expansionOffset, filtering = filtering
  ))
  readData = data.table(Read_Length = nchar(readData$V7)-expansionOffset*2, Read_Sequence = readData$V7)
  readData = readData[Read_Length >= readMinMax[1] & Read_Length <= readMinMax[2]]

  seqFreq = getSequenceFreqByReadLengthAndPos(readData, querySequences = querySequences)
  fwrite(seqFreq, sep = '\t', file = generateFilePath(
      directory = directory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = lesion, repitition = repetition,
      timepoint = timepoint, sequence = sequencesName, filtering = filtering))
}
```

```{r compute_and_write_sequence_frequencies}
cutSiteAnalysis("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                c("CG","CA","TG","TA"), "YR", humanReadMinMax)
cutSiteAnalysis("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                c("CAC","CAG","CAT"), "CAB", humanReadMinMax)
cutSiteAnalysis("6-4", "all_reps", "20min", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                c("CG","CA","TG","TA"), "YR", humanReadMinMax)
cutSiteAnalysis("cisplatin", "rep1", "90min", "GM12878", GM12878GeneralReadSequenceDataDirectory,
                c("CG","CA","TG","TA"), "YR", humanReadMinMax)
cutSiteAnalysis("CPD", "all_reps", "30m", "Dm", DmGeneralReadSequenceDataDirectory,
                c("CG","CA","TG","TA"), "YR", drosophilaReadMinMax)
cutSiteAnalysis("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                c("TCAGTC","TCAGTT"), "TCAGTY", humanReadMinMax)
cutSiteAnalysis("CPD", "all_reps", "30m", "Dm", DmGeneralReadSequenceDataDirectory,
                c("TCAGTC","TCAGTT"), "TCAGTY", drosophilaReadMinMax)
```

### 2022-07-20 R/5'CutSiteAnalysisFigureGeneration.rmd
Created r notebooks for analyzing the 5' cut site
- Specifically, these notebooks examine sequence frequencies across whole aligned read samples, not just mismatch based reads.
- Options are still available for TGG filtering.

---
title: "5'CutSiteAnalysisDataGeneration"
author: "Ben MOrledge-Hampton"
date: '2022-07-14'
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered, TG_filtered]
---

```{r setup_chunk}
library(knitr)

expansionOffset = 10

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
  filtering = readline("Filtering identifier (Input nothing for no filtering):")
  if (filtering == '') filtering = character()
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
  filtering = params$filtering
  if (filtering == "NONE") filtering = character()
}

if (length(filtering) > 0) {
  titleCaseFiltering = tools::toTitleCase(gsub('_', ' ', filtering))
} else titleCaseFiltering = character()

if (is.na(bioinformaticsDirectory)) stop("No bioinformatics directory given.")

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data")
NHF1GeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "NHF1", "general_read_sequences")
GM12878GeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "GM12878", "general_read_sequences")
DmGeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "Dm", "general_read_sequences")

humanReadMinMax = c(22, 30)
drosophilaReadMinMax = c(23, 32)

opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
               fig.path = paste0(file.path("deamination_analysis_output",
                                           paste(c(filtering,"5'_cut_site_analysis"), collapse = '_')),
                                 .Platform$file.sep))
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationAnchoredExcisionSiteAnalysis.R"))
```

```{r define_all_that_and_a_bag_of_chips_function}
cutSitePlotting = function(lesion, repetition, timepoint, cellType, directory,
                           sequencesName, readMinMax, plottingPositionsFromEnd) {
  sequenceFrequencyData = fread(generateFilePath(
    directory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = cellType, lesion = lesion, timepoint = timepoint,
    repitition = repetition, sequence = sequencesName, filtering = filtering
  ))

  sequenceFrequencyData[, Position := Position + 10]
  endPositionsByTimepointAndRL = sequenceFrequencyData[, .(End = max(abs(Position))),
                                                        by = Read_Length]
  setkey(endPositionsByTimepointAndRL, Read_Length)
  endPosByFullFreqRow = endPositionsByTimepointAndRL[list(sequenceFrequencyData$Read_Length)]$End
  seqFreqPlottingRows = sequenceFrequencyData[abs(Position) + abs(plottingPositionsFromEnd) > endPosByFullFreqRow]

  plotSequenceFrequencies(seqFreqPlottingRows,
                          title = paste(cellType, lesion, titleCaseFiltering, timepoint),
                          secondaryYAxisLabel = "Read Length", yAxisLabel = paste(sequencesName,"Frequency"),
                          showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"), expansionOffset = 10,
                          minReadLength = readMinMax[1], maxReadLength = readMinMax[2], endBasedBackgroundNum = 8,
                          endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "3' Relative Position")
}
```

```{r sequence_frequency_figures, fig.width = 5, fig.height = 7}
cutSitePlotting("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                "YR", humanReadMinMax, 17)
cutSitePlotting("6-4", "all_reps", "20min", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                "YR", humanReadMinMax, 17)
cutSitePlotting("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                "CAB", humanReadMinMax, 17)
cutSitePlotting("cisplatin", "rep1", "90min", "GM12878", GM12878GeneralReadSequenceDataDirectory,
                "YR", humanReadMinMax, 17)
cutSitePlotting("CPD", "all_reps", "30m", "Dm", DmGeneralReadSequenceDataDirectory,
                "YR", drosophilaReadMinMax, 17)
cutSitePlotting("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                "TCAGTY", humanReadMinMax, 25)
cutSitePlotting("CPD", "all_reps", "30m", "Dm", DmGeneralReadSequenceDataDirectory,
                "TCAGTY", drosophilaReadMinMax, 25)
```

### 2022-07-20 python/FilterOnExpandedContext.py
Companion file no longer required for filtering
- An option was added to the GUI to not check for/filter on unexpanded bed files.
- When the above option is not in effect, the script functions as it did previously.

@@ -12,86 +12,98 @@ from benbiohelpers.CustomErrors import UserInputError
 
 
 def filterOnExpandedContext(expandedContextFilePaths: List[str], threePrimeBlacklist = list(), fivePrimeBlacklist = list(),
-                            customSuffix = ''):
+                            customSuffix = '', filterUnexpandedCompanionFiles = True):
     
     for expandedContextFilePath in expandedContextFilePaths:
         expandedBasename = os.path.basename(expandedContextFilePath)
+        unexpandedBasename, expansionContext = expandedBasename.rsplit("bp_expanded", 1)[0].rsplit('_', 1)
+        outputDirectory = os.path.dirname(expandedContextFilePath)
         print(f"\nWorking with {expandedBasename}")
 
-        # Find the non-extended partner for the expanded context file and generate output file paths.
+        # Generate the relevant output file paths, finding the companion unexpanded filepath if necessary.
         # Also, perform some quality control checks.
         if not "bp_expanded" in expandedBasename:
             raise UserInputError(f"Given file: {expandedContextFilePath} does not appear to have expanded context.")
-        unexpandedBasename, expansionContext = expandedBasename.rsplit("bp_expanded", 1)[0].rsplit('_', 1)
 
-        unexpandedBasename += ".bed"
-        unexpandedFilePath = os.path.join(os.path.dirname(expandedContextFilePath), unexpandedBasename)
-        if not os.path.exists(unexpandedFilePath):
-            raise UserInputError(f"Could not find unexpanded companion file: {unexpandedFilePath}")
+        expandedContextOutputFilePath = os.path.join(outputDirectory, expandedBasename.rsplit('.',1)[0] + customSuffix + ".bed")
+        if filterUnexpandedCompanionFiles:
+            unexpandedBasename += ".bed"
+            unexpandedFilePath = os.path.join(os.path.dirname(expandedContextFilePath), unexpandedBasename)
+            if not os.path.exists(unexpandedFilePath):
+                raise UserInputError(f"Could not find unexpanded companion file: {unexpandedFilePath}")
+            unexpandedOutputFilePath = os.path.join(outputDirectory, unexpandedBasename.rsplit('.',1)[0] + customSuffix + ".bed")
 
         expansionContext = int(expansionContext)
         maxBlacklistSequenceLength = max(len(sequence) for sequence in threePrimeBlacklist + fivePrimeBlacklist)
         if expansionContext < maxBlacklistSequenceLength:
[…]

### 2022-07-20 R/PaperFigureGeneration.rmd
Update PaperFigureGeneration.rmd
Ummm... Lots of changes here. Mainly reorganized/added supplemental figures to emphasize patterns on 5' cut site.

--- 2022-07-11 R/PaperFigureGeneration.rmd
@@
 XPCCPDTimepoints = list(`1h` = NULL)
+EColiCPDTimepoints = list(`5min` = NULL)
 
@@
 GM12878SequenceAndPositionDataDirectory = file.path(GM12878DataDirectory, "sequence_and_position_analysis")
+GM12878GeneralReadSequenceDataDirectory = file.path(GM12878DataDirectory, "general_read_sequences")
 
@@
 XPCSequenceAndPositionDataDirectory = file.path(XPCDataDirectory, "sequence_and_position_analysis")
+
+EColiDataDirectory = file.path(deaminationDataDirectory, "E_coli_WT")
+EColiExcisionSiteDataDirectory = file.path(EColiDataDirectory, "excision_site_analysis")
 ```
@@
 ))
-
 NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = NHF1CPDTimepoints
@@
 ```{r figure_4B, fig.width = 5, fig.height = 5}
-### Just the 1h timepoint ###
+# ### Just the 1h timepoint (asterisks) ###
+# plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
+#                         title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored YR Freq",
+#                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
+#                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
+#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
+#                         endBasedCheckPositions = -10, xAxisLabel = "Mismatch Relative Position",
+#                         significanceAsteriskBreakpoints = c(1e-6, 1e-9))
+
+## Just the 1h timepoint (full p-values) ###
 plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
@@
 ```
-
 ```{r figure_S3B, fig.width = 6.5, fig.height = 6}
@@
 ```
-
 ```{r figure_S3D, fig.width = 5, fig.height = 5}
@@
 
-```{r figure_S4, fig.width = 9, fig.height = 5}
-plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsTGGFiltered,
-                               title = "NHF1 CPD ALL Reps TGG-Filtered 5' Anchored Purine Freq",
+```{r read_figure_S4_data}
+EColiThreePrimeMismatchCPDNucFreqAllReps = fread(generateFilePath(
+  EColiExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+  cellType = "E_coli_WT", lesion = "CPD", repitition = "all_reps",
+  strandPolarity = "three_prime", anchored = TRUE
+))
+EColiThreePrimeMMAnchoredCPDSeqFreqAllReps = EColiCPDTimepoints
+for (i in seq_along(EColiThreePrimeMMAnchoredCPDSeqFreqAllReps)) {
+  EColiThreePrimeMMAnchoredCPDSeqFreqAllReps[[i]] = fread(generateFilePath(
+    EColiExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+    cellType = "E_coli_WT", lesion = "CPD", repitition = "all_reps",
+    timepoint = names(EColiThreePrimeMMAnchoredCPDSeqFreqAllReps)[i],
+    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR"
+  ))
+}
+```
+
+```{r figure_S4A, fig.width = 6.5, fig.height = 6}
+plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
+                               title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored Nuc Freq",
+                               secondaryYAxisLabel = "5' Cut Site Distance",
+                               posType = FIVE_PRIME, showFivePrimeCutSite = TRUE,
+                               expansionOffset = 10, minReadLength = 19, maxReadLength = 25,
+                               xAxisLabel = "Mismatch Relative Position")
+```
+```{r figure_S4B, fig.width = 5, fig.height = 6}
+plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsTGFiltered[Timepoint == "1h"],
+                               title = "NHF1 CPD 1h ALL Reps TG-Filtered 5' Anchored Purine Freq",
                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
@@
                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
-                               expansionOffset = 10, minReadLength = 1, maxReadLength = 7,
+                               expansionOffset = 10, minReadLength = 6, maxReadLength = 13,
                                xAxisLabel = "Mismatch Relative Position")
+```
+```{r figure_S4C}
+plotNucFreqVsReadLengthBarPlot(EColiThreePrimeMismatchCPDNucFreqAllReps,
+                               title = "NHF1 E coli ALL Reps 5' Anchored Purine Freq",
+                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
+                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
+                               posType = FIVE_PRIME, showFivePrimeCutSite = TRUE,
+                               expansionOffset = 10,
+                               xAxisLabel = "Mismatch Relative Position")
+```
+```{r figure_S4D}
+plotSequenceFrequencies(EColiThreePrimeMMAnchoredCPDSeqFreqAllReps,
+                        title = "E coli CPD 30min All Reps 3' Anchored YR Freq",
+                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
+                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
+                        expansionOffset = 10, xAxisLabel = "Mismatch Relative Position")
 ```
@@
 }
+
+NHF1SixFour20MinSeqFreqAllRepsFiltered = fread(generateFilePath(
+  NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+  cellType = "NHF1", lesion = "6-4", timepoint = "20min",
+  repitition = "all_reps", sequence = "YR", filtering = "TGG_filtered"
+))
+NHF1SixFour20MinSeqFreqAllRepsFiltered[, Position := Position + 10]
+endPositionsByTimepointAndRL = NHF1SixFour20MinSeqFreqAllRepsFiltered[, .(End = max(abs(Position))),
+                                                      by = Read_Length]
+setkey(endPositionsByTimepointAndRL, Read_Length)
+endPosByFullFreqRow = endPositionsByTimepointAndRL[list(NHF1SixFour20MinSeqFreqAllRepsFiltered$Read_Length)]$End
+seqFreqPlottingRows = NHF1SixFour20MinSeqFreqAllRepsFiltered[abs(Position) + abs(17) > endPosByFullFreqRow]
+
+GM12878Cisplatin90MinSeqFreqRep1Filtered = fread(generateFilePath(
+  GM12878GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+  cellType = "GM12878", lesion = "cisplatin", timepoint = "90min",
+  repitition = "rep1", sequence = "YR", filtering = "TGG_filtered"
+))
+GM12878Cisplatin90MinSeqFreqRep1Filtered[, Position := Position + 10]
+endPositionsByTimepointAndRL = GM12878Cisplatin90MinSeqFreqRep1Filtered[, .(End = max(abs(Position))),
+                                                      by = Read_Length]
+setkey(endPositionsByTimepointAndRL, Read_Length)
+endPosByFullFreqRow = endPositionsByTimepointAndRL[list(GM12878Cisplatin90MinSeqFreqRep1Filtered$Read_Length)]$End
+seqFreqPlottingRows = GM12878Cisplatin90MinSeqFreqRep1Filtered[abs(Position) + abs(17) > endPosByFullFreqRow]
 ```
 
-```{r figure_S5, fig.width = 9, fig.height = 5}
-plotSequenceFrequencies(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
-                        title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered 3' Anchored YR Freq",
+```{r figure_S5, fig.width = 5, fig.height = 6}
+plotSequenceFrequencies(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$ZT2,
+                        title = "Arabidopsis CPD All Reps TGG-Filtered 3' Anchored YR Freq",
                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
@@
 
-plotSequenceFrequencies(yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
-                        title = "Yeast CPD 20min All Reps TGG-Filtered 3' Anchored YR Freq",
+plotSequenceFrequencies(yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`20min`,
+                        title = "Yeast CPD All Reps TGG-Filtered 3' Anchored YR Freq",
                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
@@
                         endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
+
+plotSequenceFrequencies(NHF1SixFour20MinSeqFreqAllRepsFiltered,
+                        title = "NHF1 6-4 All Reps TGG-Filtered YR Freq",
+                        secondaryYAxisLabel = "Read Length", yAxisLabel = "YR Frequency",
+                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"), expansionOffset = 10,
+                        minReadLength = 22, maxReadLength = 30, endBasedBackgroundNum = 8,
+                        endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "3' Relative Position")
+
+plotSequenceFrequencies(GM12878Cisplatin90MinSeqFreqRep1Filtered,
+                        title = "GM12878 Cisplatin All Reps TGG-Filtered YR Freq",
+                        secondaryYAxisLabel = "Read Length", yAxisLabel = "YR Frequency",
+                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"), expansionOffset = 10,
+                        minReadLength = 22, maxReadLength = 30, endBasedBackgroundNum = 8,
+                        endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "3' Relative Position")
 ```

### 2022-07-20 R/DeaminationAnchoredExcisionSiteAnalysis.R
Works better for small values.

@@ -384,7 +384,7 @@ plotSequenceFrequencies = function(seqFreqTablesByTimepoint, posType = THREE_PRI
     }))
   }
 
-  maxFrequency = round(max(fullFrequencyTable$Frequency),digits = 2)
+  maxFrequency = signif(max(fullFrequencyTable$Frequency),digits = 2)
   yAxisBreaks = c(0, maxFrequency/2, maxFrequency)
 
   maxQueryLength = max(nchar(querySequences))

### 2022-07-28 R/5'CutSiteAnalysisDataGeneration.rmd
Preliminary commit

@@
 
-```{r compute_and_write_sequence_frequencies}
+```{r compute_and_write_sequence_frequencies_OLD}
 cutSiteAnalysis("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
@@
 ```
+
+```{r compute_and_write_sequence_frequencies}
+HYV = c("ACA","ACC","ACG","ATA","ATC","ATG",
+        "CCA","CCC","CCG","CTA","CTC","CTG",
+        "TCA","TCC","TCG","TTA","TTC","TTG")
+cutSiteAnalysis("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
+                HYV, "HYV", humanReadMinMax)
+cutSiteAnalysis("CPD", "all_reps", "30m", "Dm", DmGeneralReadSequenceDataDirectory,
+                c("CG","CA","TG","TA"), "YR", drosophilaReadMinMax)
+
+```

### 2022-07-30 R/5'CutSiteAnalysisDataGeneration.rmd
HYV is better than YR!
Lots of changes to accommodate the change in sequence pattern from YR to HYV:
- Changed sequence frequency generation to except regular expression patterns.
- Updated various plotting and data generation notebooks to generate new HYV plots. This also included updating figure generation.

--- 2022-07-20 R/5'CutSiteAnalysisDataGeneration.rmd
@@
 DmGeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "Dm", "general_read_sequences")
+arabidopsisGeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "Arabidopsis", "general_read_sequences")
+yeastGeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "yeast", "general_read_sequences")
+EColiGeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "E_coli_WT", "general_read_sequences")
 
@@
 drosophilaReadMinMax = c(23, 32)
+arabidopsisReadMinMax = c(24, 30)
+yeastReadMinMax = c(22, 25)
+EColiReadMinMax = c(11, 13)
 ```
@@
 cutSiteAnalysis = function(lesion, repetition, timepoint, cellType, directory,
-                           querySequences, sequencesName, readMinMax) {
+                           queryPattern, sequencesName, readMinMax,
+                           dataTypeString = dataTypeStrings$alignedReads, fileExtension = ".bed") {
   readData = fread(generateFilePath(
-    directory, dataTypeStrings$alignedReads, ".bed",
+    directory, dataTypeString, fileExtension,
     cellType = cellType, lesion = lesion, timepoint = timepoint,
@@
 
-  seqFreq = getSequenceFreqByReadLengthAndPos(readData, querySequences = querySequences)
+  seqFreq = getSequenceFreqByReadLengthAndPos(readData, queryPattern = queryPattern, posType = FIVE_PRIME)
+  seqFreq[, Position := Position - 10]
   fwrite(seqFreq, sep = '\t', file = generateFilePath(
@@
 ```{r compute_and_write_sequence_frequencies}
+HYV = c("ACA","ACC","ACG","ATA","ATC","ATG",
+        "CCA","CCC","CCG","CTA","CTC","CTG",
+        "TCA","TCC","TCG","TTA","TTC","TTG")
+HYVPattern = "^[ACT][CT][ACG]"
+
 cutSiteAnalysis("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
-                c("CG","CA","TG","TA"), "YR", humanReadMinMax)
-cutSiteAnalysis("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
-                c("CAC","CAG","CAT"), "CAB", humanReadMinMax)
+                HYVPattern, "HYV", humanReadMinMax)
 cutSiteAnalysis("6-4", "all_reps", "20min", "NHF1", NHF1GeneralReadSequenceDataDirectory,
-                c("CG","CA","TG","TA"), "YR", humanReadMinMax)
+                HYVPattern, "HYV", humanReadMinMax)
 cutSiteAnalysis("cisplatin", "rep1", "90min", "GM12878", GM12878GeneralReadSequenceDataDirectory,
-                c("CG","CA","TG","TA"), "YR", humanReadMinMax)
-cutSiteAnalysis("CPD", "all_reps", "30m", "Dm", DmGeneralReadSequenceDataDirectory,
-                c("CG","CA","TG","TA"), "YR", drosophilaReadMinMax)
-cutSiteAnalysis("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
-                c("TCAGTC","TCAGTT"), "TCAGTY", humanReadMinMax)
-cutSiteAnalysis("CPD", "all_reps", "30m", "Dm", DmGeneralReadSequenceDataDirectory,
-                c("TCAGTC","TCAGTT"), "TCAGTY", drosophilaReadMinMax)
+                HYVPattern, "HYV", humanReadMinMax)
+cutSiteAnalysis("CPD", "all_reps", "20min", "yeast", yeastGeneralReadSequenceDataDirectory,
+                HYVPattern, "HYV", yeastReadMinMax)
+cutSiteAnalysis("CPD", "all_reps", "ZT2", "Arabidopsis", arabidopsisGeneralReadSequenceDataDirectory,
+                HYVPattern, "HYV", arabidopsisReadMinMax)
+cutSiteAnalysis("CPD", "all_reps", "5min", "E_coli_WT", EColiGeneralReadSequenceDataDirectory,
+                HYVPattern, "HYV", EColiReadMinMax)
 ```

### 2022-07-30 R/5'CutSiteAnalysisFigureGeneration.rmd
HYV is better than YR!
Lots of changes to accommodate the change in sequence pattern from YR to HYV:
- Changed sequence frequency generation to except regular expression patterns.
- Updated various plotting and data generation notebooks to generate new HYV plots. This also included updating figure generation.

@@
 NHF1GeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "NHF1", "general_read_sequences")
+NHF1ExcisionSiteDataDirectory = file.path(deaminationDataDirectory, "NHF1", "excision_site_analysis")
 GM12878GeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "GM12878", "general_read_sequences")
 DmGeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "Dm", "general_read_sequences")
+arabidopsisGeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "Arabidopsis", "general_read_sequences")
+yeastGeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "yeast", "general_read_sequences")
+EColiGeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "E_coli_WT", "general_read_sequences")
 
@@
 drosophilaReadMinMax = c(23, 32)
+arabidopsisReadMinMax = c(24, 30)
+yeastReadMinMax = c(22, 25)
+EColiReadMinMax = c(11, 13)
 
@@
 cutSitePlotting = function(lesion, repetition, timepoint, cellType, directory,
-                           sequencesName, readMinMax, plottingPositionsFromEnd) {
+                           sequencesName, readMinMax, maxPlottingPos, xAxisOffset = 1,
+                           backgroundPositions = -9:-4, checkPositions = -1,
+                           displayPValue = TRUE) {
   sequenceFrequencyData = fread(generateFilePath(
@@
 
-  sequenceFrequencyData[, Position := Position + 10]
-  endPositionsByTimepointAndRL = sequenceFrequencyData[, .(End = max(abs(Position))),
-                                                        by = Read_Length]
-  setkey(endPositionsByTimepointAndRL, Read_Length)
-  endPosByFullFreqRow = endPositionsByTimepointAndRL[list(sequenceFrequencyData$Read_Length)]$End
-  seqFreqPlottingRows = sequenceFrequencyData[abs(Position) + abs(plottingPositionsFromEnd) > endPosByFullFreqRow]
-
-  plotSequenceFrequencies(seqFreqPlottingRows,
+  plotSequenceFrequencies(sequenceFrequencyData[Position <= maxPlottingPos],
                           title = paste(cellType, lesion, titleCaseFiltering, timepoint),
                           secondaryYAxisLabel = "Read Length", yAxisLabel = paste(sequencesName,"Frequency"),
-                          showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"), expansionOffset = 10,
-                          minReadLength = readMinMax[1], maxReadLength = readMinMax[2], endBasedBackgroundNum = 8,
-                          endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "3' Relative Position")
+                          showFivePrimeCutSite = TRUE, querySequences = c("333"), expansionOffset = 10,
+                          minReadLength = readMinMax[1], maxReadLength = readMinMax[2],
+                          backgroundPositions = backgroundPositions, checkPositions = checkPositions,
+                          displayPValue = displayPValue, xAxisLabel = "5' Relative Position",
+                          xAxisOffset = xAxisOffset, xAxisBreaks = c(-8, 0, 8))
 }
@@
 cutSitePlotting("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
-                "YR", humanReadMinMax, 17)
+                "HYV", humanReadMinMax, 7)
 cutSitePlotting("6-4", "all_reps", "20min", "NHF1", NHF1GeneralReadSequenceDataDirectory,
-                "YR", humanReadMinMax, 17)
-cutSitePlotting("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
-                "CAB", humanReadMinMax, 17)
+                "HYV", humanReadMinMax, 7)
 cutSitePlotting("cisplatin", "rep1", "90min", "GM12878", GM12878GeneralReadSequenceDataDirectory,
-                "YR", humanReadMinMax, 17)
-cutSitePlotting("CPD", "all_reps", "30m", "Dm", DmGeneralReadSequenceDataDirectory,
-                "YR", drosophilaReadMinMax, 17)
-cutSitePlotting("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
-                "TCAGTY", humanReadMinMax, 25)
-cutSitePlotting("CPD", "all_reps", "30m", "Dm", DmGeneralReadSequenceDataDirectory,
-                "TCAGTY", drosophilaReadMinMax, 25)
+                "HYV", humanReadMinMax, 7)
+cutSitePlotting("CPD", "all_reps", "20min", "yeast", yeastGeneralReadSequenceDataDirectory,
+                "HYV", yeastReadMinMax, 7)
+cutSitePlotting("CPD", "all_reps", "ZT2", "Arabidopsis", arabidopsisGeneralReadSequenceDataDirectory,
+                "HYV", arabidopsisReadMinMax, 7)
+cutSitePlotting("CPD", "all_reps", "5min", "E_coli_WT", EColiGeneralReadSequenceDataDirectory,
+                "HYV", EColiReadMinMax, 7, 1, NULL, NULL, FALSE)
 ```

### 2022-07-30 R/NHF1DeaminationAnchoredExcisionSiteDataGeneration.rmd
HYV is better than YR!
Lots of changes to accommodate the change in sequence pattern from YR to HYV:
- Changed sequence frequency generation to except regular expression patterns.
- Updated various plotting and data generation notebooks to generate new HYV plots. This also included updating figure generation.

@@
 
+threePrimeMMAnchoredCPDSeqFreq = lapply(threePrimeMismatchAnchoredCPDData, function(mismatchDataRep) {
+  lapply(mismatchDataRep, function(mismatchData) {
+    getSequenceFreqByReadLengthAndPos(mismatchData, queryPattern = "^[ACT][CT][ACG]")
+  })
+})
+for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
+  for (j in seq_along(threePrimeMMAnchoredCPDSeqFreq[[i]])) {
+    fwrite(threePrimeMMAnchoredCPDSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      cellType = cellType, lesion = "CPD", repitition = names(threePrimeMMAnchoredCPDSeqFreq)[i],
+      timepoint = names(threePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "three_prime",
+      anchored = TRUE, sequence = "HYV", filtering = filtering
+    ))
+  }
+}
+
 fivePrimeMMAnchoredCPDSeqFreq = lapply(fivePrimeMismatchAnchoredCPDData, function(mismatchDataRep) {

### 2022-07-30 R/NHF1TandemDeaminationDataGeneration.rmd
HYV is better than YR!
Lots of changes to accommodate the change in sequence pattern from YR to HYV:
- Changed sequence frequency generation to except regular expression patterns.
- Updated various plotting and data generation notebooks to generate new HYV plots. This also included updating figure generation.

@@
 
+threePrimeMMAnchoredCPDSeqFreq = lapply(threePrimeMismatchAnchoredCPDData, function(mismatchDataRep) {
+  lapply(mismatchDataRep, function(mismatchData) {
+    getSequenceFreqByReadLengthAndPos(mismatchData, queryPattern = "^[ACT][CT][ACG]")
+  })
+})
+for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
+  for (j in seq_along(threePrimeMMAnchoredCPDSeqFreq[[i]])) {
+    fwrite(threePrimeMMAnchoredCPDSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
+      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+      cellType = cellType, lesion = "CPD", repitition = names(threePrimeMMAnchoredCPDSeqFreq)[i],
+      timepoint = names(threePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "three_prime",
+      anchored = TRUE, sequence = "HYV", filtering = filtering, includedMismatches = mismatchType
+    ))
+  }
+}
+
 fivePrimeMMAnchoredCPDSeqFreq = lapply(fivePrimeMismatchAnchoredCPDData, function(mismatchDataRep) {

### 2022-07-30 R/PaperFigureGeneration.rmd
HYV is better than YR!
Lots of changes to accommodate the change in sequence pattern from YR to HYV:
- Changed sequence frequency generation to except regular expression patterns.
- Updated various plotting and data generation notebooks to generate new HYV plots. This also included updating figure generation.

--- 2022-07-11 R/PaperFigureGeneration.rmd
@@
 arabidopsisExcisionSiteDataDirectory = file.path(arabidopsisDataDirectory, "excision_site_analysis")
+arabidopsisGeneralReadSequenceDataDirectory = file.path(arabidopsisDataDirectory, "general_read_sequences")
 
@@
 yeastExcisionSiteDataDirectory = file.path(yeastDataDirectory, "excision_site_analysis")
+yeastGeneralReadSequenceDataDirectory = file.path(yeastDataDirectory, "general_read_sequences")
 
@@
 XPCSequenceAndPositionDataDirectory = file.path(XPCDataDirectory, "sequence_and_position_analysis")
+
+EColiDataDirectory = file.path(deaminationDataDirectory, "E_coli_WT")
+EColiExcisionSiteDataDirectory = file.path(EColiDataDirectory, "excision_site_analysis")
+EColiGeneralReadSequenceDataDirectory = file.path(EColiDataDirectory, "general_read_sequences")
 ```
@@
     timepoint = names(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
-    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
+    strandPolarity = "three_prime", anchored = TRUE, sequence = "HYV", filtering = "TGG_filtered"
   ))
 }
+NHF1GeneralReadsCPDSeqFreqAllReps1hFiltered = fread(generateFilePath(
+  NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+  cellType = "NHF1", lesion = "CPD", timepoint = "1h",
+  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered"
+))
+arabidopsisGeneralReadsCPDSeqFreqAllRepsZT2Filtered = fread(generateFilePath(
+  arabidopsisGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+  cellType = "Arabidopsis", lesion = "CPD", timepoint = "ZT2",
+  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered"
+))
+yeastGeneralReadsCPDSeqFreqAllReps20MinFiltered = fread(generateFilePath(
+  yeastGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+  cellType = "yeast", lesion = "CPD", timepoint = "20min",
+  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered"
+))
+EColiGeneralReadsCPDSeqFreqAllReps5MinFiltered = fread(generateFilePath(
+  EColiGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+  cellType = "E_coli_WT", lesion = "CPD", timepoint = "5min",
+  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered"
+))
 ```
 
-```{r figure_4A, fig.width = 5, fig.height = 6}
-### Just the 1h timepoint ###
+```{r figure_4A, fig.width = 6.5, fig.height = 6}
 plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
-                               title = "NHF1 CPD 1h ALL Reps TGG-Filtered 3' Anchored Purine Freq",
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
+                               title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored Nuc Freq",
+                               secondaryYAxisLabel = "5' Cut Site Distance",
+                               posType = FIVE_PRIME, showFivePrimeCutSite = TRUE,
                                expansionOffset = 10, minReadLength = 19, maxReadLength = 25,
                                xAxisLabel = "Mismatch Relative Position")
+```
+```{r figure_4B, fig.width = 5, fig.height = 6}
+# ### Just the 1h timepoint (asterisks) ###
+# plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
+#                         title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored HYV Freq",
+#                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
+#                         showFivePrimeCutSite = TRUE, querySequences = c("333"),
+#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 6,
+#                         endBasedCheckPositions = -9, xAxisLabel = "Mismatch Relative Position",
+#                         significanceAsteriskBreakpoints = c(1e-3, 1e-10, 1e-20))
 
-### All timepoints together ###
-# plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered, 
-#                                title = "NHF1 CPD ALL Reps TGG-Filtered 3' Anchored Purine Freq",
-#                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
-#                                combineNucleotides = c("AG"), combinedNames = c("Purine"),
-#                                posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
-#                                expansionOffset = 10, minReadLength = 19, maxReadLength = 25,
-#                                xAxisLabel = "Mismatch Relative Position")
-```
-```{r figure_4B, fig.width = 5, fig.height = 5}
-### Just the 1h timepoint ###
+## Just the 1h timepoint (full p-values) ###
 plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
-                        title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored YR Freq",
-                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
-                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
-                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
-                        endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
+                        title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored HYV Freq",
+                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "HYV Frequency",
+                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
+                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 6,
+                        endBasedCheckPositions = -9, displayPValue = FALSE, xAxisLabel = "Mismatch Relative Position")
 
@@
 #                         endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
+```
+```{r figure_4C, fig.width = 5, fig.height = 6}
+plotSequenceFrequencies(NHF1GeneralReadsCPDSeqFreqAllReps1hFiltered[Position <= 7],
+                        title = "NHF1 CPD 1h All Reps TGG-Filtered General Reads HYV Freq",
+                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
+                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
+                        expansionOffset = 10, minReadLength = 23, maxReadLength = 29, backgroundPositions = -9:-4,
+                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
+                        xAxisBreaks = c(-8, 0, 8))
+```
+```{r figure_4D, fig.width = 5, fig.height = 6}
+plotSequenceFrequencies(arabidopsisGeneralReadsCPDSeqFreqAllRepsZT2Filtered[Position <= 7],
+                        title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered General Reads HYV Freq",
+                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
+                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
+                        expansionOffset = 10, minReadLength = 24, maxReadLength = 30, backgroundPositions = -9:-4,
+                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
+                        xAxisBreaks = c(-8, 0, 8))
+```
+```{r figure_4E, fig.width = 5, fig.height = 6}
+plotSequenceFrequencies(yeastGeneralReadsCPDSeqFreqAllReps20MinFiltered[Position <= 7],
+                        title = "Yeast CPD 20min All Reps TGG-Filtered General Reads HYV Freq",
+                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
+                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
+                        expansionOffset = 10, minReadLength = 22, maxReadLength = 25, backgroundPositions = -9:-4,
+                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
+                        xAxisBreaks = c(-8, 0, 8))
+```
+```{r figure_4F, fig.width = 5, fig.height = 6}
+plotSequenceFrequencies(EColiGeneralReadsCPDSeqFreqAllReps5MinFiltered[Position <= 7],
+                        title = "E. coli CPD 5min All Reps TGG-Filtered General Reads HYV Freq",
+                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
+                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
+                        expansionOffset = 10, minReadLength = 11, maxReadLength = 13, xAxisLabel = "5' Relative Position",
+                        xAxisBreaks = c(-8, 0, 8))
 ```
@@
     timepoint = names(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered)[i],
-    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
+    strandPolarity = "three_prime", anchored = TRUE, sequence = "HYV", filtering = "TGG_filtered"
   ))
@@
 plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered$`1h`,
-                        title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT 3' Anchored YR Freq",
-                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
-                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
-                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
-                        endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
+                        title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT 3' Anchored HYV Freq",
+                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "HYV Frequency",
+                        showFivePrimeCutSite = TRUE, querySequences = c("333"),
+                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 6,
+                        endBasedCheckPositions = -9, displayPValue = FALSE, xAxisLabel = "Mismatch Relative Position",
+                        xAxisOffset = 1)
 
@@
 
-```{r figure_S4, fig.width = 9, fig.height = 5}
-plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsTGGFiltered,
-                               title = "NHF1 CPD ALL Reps TGG-Filtered 5' Anchored Purine Freq",
-                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
-                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
-                               expansionOffset = 10, minReadLength = 1, maxReadLength = 7,
-                               xAxisLabel = "Mismatch Relative Position")
+```{r read_figure_S4_data}
+NHF1GeneralReadsSixFourSeqFreqAllReps20minFiltered = fread(generateFilePath(
+  NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+  cellType = "NHF1", lesion = "6-4", timepoint = "20min",
+  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered"
+))
+GM12878GeneralReadsCisplatinSeqFreqRep1_90minFiltered = fread(generateFilePath(
+  GM12878GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+  cellType = "GM12878", lesion = "cisplatin", timepoint = "90min",
+  repitition = "rep1", sequence = "HYV", filtering = "TGG_filtered"
+))
+```
+
+```{r figure_S4, fig.width = 5, fig.height = 6}
+plotSequenceFrequencies(NHF1GeneralReadsSixFourSeqFreqAllReps20minFiltered[Position <= 7],
+                        title = "NHF1 6-4 20min All Reps TGG-Filtered General Reads HYV Freq",
+                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
+                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisBreaks = c(-8, 0, 8),
+                        expansionOffset = 10, minReadLength = 23, maxReadLength = 29, backgroundPositions = -9:-4,
+                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
+                        xAxisOffset = 1)
+plotSequenceFrequencies(GM12878GeneralReadsCisplatinSeqFreqRep1_90minFiltered[Position <= 7],
+                        title = "GM12878 cisplatin 90min Rep1 TGG-Filtered General Reads HYV Freq",
+                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
+                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisBreaks = c(-8, 0, 8),
+                        expansionOffset = 10, minReadLength = 23, maxReadLength = 29, backgroundPositions = -9:-4,
+                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
+                        xAxisOffset = 1)
 ```
@@
 ```{r read_figure_S5_data}
-arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = arabidopsisCPDTimepoints
-for (i in seq_along(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
-  arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
-    arabidopsisExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
-    cellType = "Arabidopsis", lesion = "CPD", repitition = "all_reps",
-    timepoint = names(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
-    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
-  ))
-}
-
-yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = yeastCPDTimepoints
-for (i in seq_along(yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
-  yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
-    yeastExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
-    cellType = "yeast", lesion = "CPD", repitition = "all_reps",
-    timepoint = names(yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
-    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
-  ))
-}
-```
-
-```{r figure_S5, fig.width = 9, fig.height = 5}
-plotSequenceFrequencies(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
-                        title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered 3' Anchored YR Freq",
-                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
-                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
-                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
-                        endBasedCheckPositions = 10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
-
-plotSequenceFrequencies(yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
-                        title = "Yeast CPD 20min All Reps TGG-Filtered 3' Anchored YR Freq",
-                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
-                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
-                        expansionOffset = 10, minReadLength = 13, maxReadLength = 19, endBasedBackgroundNum = 8,
-                        endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
-```
-
-```{r read_figure_S6_data}
 NHF1CPDGGtoAAMismatchDataAllRepsFiltered = NHF1CPDTimepoints
@@
 
-```{r figure_S6, fig.width = 9, fig.height = 5}
+```{r figure_S5, fig.width = 9, fig.height = 5}
 plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered,

### 2022-07-30 R/DeaminationAnchoredExcisionSiteAnalysis.R

@@ -208,10 +208,15 @@ orientDataToMismatch = function(simplifiedTable, posType, expansionOffset = 0, h
 # Given one or more nucleotide sequences, determine their frequency in a set of reads
 # across position and read length (may need to be subset by timepoint).
 # Optionally, a table of nucleotide frequencies may be provided to normalize by.
+# If queryPattern is given (not null), querySequences is ignored, and query pattern is
+# used in its place, interpreted as a regular expression (MUCH faster for more complex patterns).
+# It is recommended that these patterns are all preceded by the '^' symbol avoid ambiguity on
+# where the pattern started.
 getSequenceFreqByReadLengthAndPos = function(readSequencesTable, expectedNucleotideFrequencies = NULL,
-                                             querySequences = c("TGG"), posType = THREE_PRIME) {
+                                             querySequences = c("TGG"), posType = THREE_PRIME,
+                                             queryPattern = NULL, maxQueryLength = NULL) {
 
-  maxQueryLength = max(nchar(querySequences))
+  if (is.null(maxQueryLength)) maxQueryLength = max(nchar(querySequences))
 
   # Iterate through all the different read lengths present in the given table(s),
   # Calculating expected and observed frequencies across all the query sequences at each position
@@ -221,6 +226,7 @@ getSequenceFreqByReadLengthAndPos = function(readSequencesTable, expectedNucleot
 
     sequences = readSequencesTable[Read_Length == readLength]$Read_Sequence
     if (!is.null(expectedNucleotideFrequencies)) {
+      if (!is.null(queryPattern)) stop("Background calculation not set up for queryPattern.")
       readLengthSpecificNucFreq = expectedNucleotideFrequencies[Read_Length == readLength]
     }
     if (posType == THREE_PRIME) {
@@ -231,9 +237,15 @@ getSequenceFreqByReadLengthAndPos = function(readSequencesTable, expectedNucleot
 
     frequencies = sapply(positions, function(position) {
 
-      observedFrequency = sum(sapply(querySequences, function(querySequence) {
-        sum(str_sub(sequences, position, position + nchar(querySequence) - 1) == querySequence)/length(sequences)
-      }))
+      if (is.null(queryPattern)) {
[…]

### 2022-08-26 R/5'CutSiteAnalysisDataGeneration.rmd
Read length merging in plotting
- Changed nucleotide frequency and sequence frequency plotting to recognize data with merged read lengths and not stratify along a secondary y-axis.
- Created function for making read-length-merged nucleotide frequency and sequence frequency data anchored to mismatches. (This was a bad idea... data anchored to a mismatch causes variable cut-site positions that when combined destroy any relevant signals.)
- Updated 5' general read sequence analysis to perform nucleotide frequency generation and optionally combine read lengths.
- Updated paper figure generation.

@@
                            queryPattern, sequencesName, readMinMax,
-                           dataTypeString = dataTypeStrings$alignedReads, fileExtension = ".bed") {
+                           alsoComputeCombinedReadLengths = FALSE, alsoComputeNucFreq = FALSE) {
   readData = fread(generateFilePath(
-    directory, dataTypeString, fileExtension,
+    directory, dataTypeStrings$alignedReads , ".bed",
     cellType = cellType, lesion = lesion, timepoint = timepoint,
@@
   seqFreq[, Position := Position - 10]
+
   fwrite(seqFreq, sep = '\t', file = generateFilePath(
@@
     timepoint = timepoint, sequence = sequencesName, filtering = filtering))
+
+  if (alsoComputeNucFreq) {
+
+    nucFreq = tabulateNucFreqByPosTimepointAndLength(setNames(list(readData),timepoint), FIVE_PRIME)
+    nucFreq[, Position := Position - 10]
+
+    fwrite(nucFreq, sep = '\t', file = generateFilePath(
+      directory = directory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+      cellType = cellType, lesion = lesion, repitition = repetition,
+      timepoint = timepoint, filtering = filtering))
+
+  }
+
+  if (alsoComputeCombinedReadLengths) {
+    readData[, Read_Length := NULL]
+    readData[, Read_Length := "combined"]
+
+    seqFreq = getSequenceFreqByReadLengthAndPos(readData, queryPattern = queryPattern, posType = FIVE_PRIME)
+    seqFreq[, Position := Position - 10]
+
+    fwrite(seqFreq, sep = '\t', file = generateFilePath(
+        directory = directory, dataTypeStrings$sequenceFrequency, ".tsv",
+        cellType = cellType, lesion = lesion, repitition = repetition,
+        timepoint = timepoint, sequence = sequencesName, filtering = filtering,
+        additionalInformation = "combined_read_lengths"))
+
+    if (alsoComputeNucFreq) {
+
+      nucFreq = tabulateNucFreqByPosTimepointAndLength(setNames(list(readData),timepoint), FIVE_PRIME)
+      nucFreq[, Position := Position - 10]
+
+      fwrite(nucFreq, sep = '\t', file = generateFilePath(
+        directory = directory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+        cellType = cellType, lesion = lesion, repitition = repetition,
+        timepoint = timepoint, filtering = filtering, additionalInformation = "combined_read_lengths"))
+
+  }
+
+  }
 }
@@
 cutSiteAnalysis("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
-                HYVPattern, "HYV", humanReadMinMax)
+                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombinedReadLengths = TRUE,
+                alsoComputeNucFreq = TRUE)
 cutSiteAnalysis("6-4", "all_reps", "20min", "NHF1", NHF1GeneralReadSequenceDataDirectory,
-                HYVPattern, "HYV", humanReadMinMax)
+                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombineReadLengths = TRUE)
 cutSiteAnalysis("cisplatin", "rep1", "90min", "GM12878", GM12878GeneralReadSequenceDataDirectory,
-                HYVPattern, "HYV", humanReadMinMax)
+                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombinedReadLengths = TRUE)
 cutSiteAnalysis("CPD", "all_reps", "20min", "yeast", yeastGeneralReadSequenceDataDirectory,
-                HYVPattern, "HYV", yeastReadMinMax)
+                HYVPattern, "HYV", yeastReadMinMax, alsoComputeCombinedReadLengths = TRUE)
 cutSiteAnalysis("CPD", "all_reps", "ZT2", "Arabidopsis", arabidopsisGeneralReadSequenceDataDirectory,
-                HYVPattern, "HYV", arabidopsisReadMinMax)
+                HYVPattern, "HYV", arabidopsisReadMinMax, alsoComputeCombinedReadLengths = TRUE)
 cutSiteAnalysis("CPD", "all_reps", "5min", "E_coli_WT", EColiGeneralReadSequenceDataDirectory,
-                HYVPattern, "HYV", EColiReadMinMax)
+                HYVPattern, "HYV", EColiReadMinMax, alsoComputeCombinedReadLengths = TRUE)
 ```

### 2022-08-26 R/CombinedReadLengthMMAnchoredSeqFreqGeneration.rmd
Read length merging in plotting
- Changed nucleotide frequency and sequence frequency plotting to recognize data with merged read lengths and not stratify along a secondary y-axis.
- Created function for making read-length-merged nucleotide frequency and sequence frequency data anchored to mismatches. (This was a bad idea... data anchored to a mismatch causes variable cut-site positions that when combined destroy any relevant signals.)
- Updated 5' general read sequence analysis to perform nucleotide frequency generation and optionally combine read lengths.
- Updated paper figure generation.

---
title: "Combined Read Length Sequence Frequency Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered, TG_filtered]
---

```{r setup_chunk}
library(knitr)

expansionOffset = 10

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
  filtering = readline("Filtering identifier (Input nothing for no filtering):")
  if (filtering == '') filtering = character()
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
  filtering = params$filtering
  if (filtering == "NONE") filtering = character()
}

if (is.na(bioinformaticsDirectory)) stop("No bioinformatics directory given.")

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data")

NHF1DataDirectory = file.path(deaminationDataDirectory, "NHF1")
NHF1MismatchesByReadDataDirectory = file.path(NHF1DataDirectory, "mismatches_by_read")
NHF1SequenceAndPositionDataDirectory = file.path(NHF1DataDirectory, "sequence_and_position_analysis")
NHF1ExcisionSiteDataDirectory = file.path(NHF1DataDirectory, "excision_site_analysis")

arabidopsisDataDirectory = file.path(deaminationDataDirectory, "Arabidopsis")
arabidopsisMismatchesByReadDataDirectory = file.path(arabidopsisDataDirectory, "mismatches_by_read")
arabidopsisSequenceAndPositionDataDirectory = file.path(arabidopsisDataDirectory, "sequence_and_position_analysis")
arabidopsisExcisionSiteDataDirectory = file.path(arabidopsisDataDirectory, "excision_site_analysis")

yeastDataDirectory = file.path(deaminationDataDirectory, "yeast")
yeastMismatchesByReadDataDirectory = file.path(yeastDataDirectory, "mismatches_by_read")
yeastSequenceAndPositionDataDirectory = file.path(yeastDataDirectory, "sequence_and_position_analysis")
yeastExcisionSiteDataDirectory = file.path(yeastDataDirectory, "excision_site_analysis")

GM12878DataDirectory = file.path(deaminationDataDirectory, "GM12878")
GM12878SequenceAndPositionDataDirectory = file.path(GM12878DataDirectory, "sequence_and_position_analysis")

EColiDataDirectory = file.path(deaminationDataDirectory, "E_coli_WT")
EColiExcisionSiteDataDirectory = file.path(EColiDataDirectory, "excision_site_analysis")

humanReadMinMax = c(22, 30)
drosophilaReadMinMax = c(23, 32)
arabidopsisReadMinMax = c(24, 30)
yeastReadMinMax = c(22, 25)
EColiReadMinMax = c(11, 13)
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationParseAndFilter.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationAnchoredExcisionSiteAnalysis.R"))
```

```{r make_the_function}
computeMMAnchoredCombinedReadLengthSeqFreq = function(
    lesion, repetition, timepoint, cellType, mismatchesByReadDirectory, seqAndPosDirectory,
    excisionSiteDirectory, queryPattern, sequencesName, readMinMax, mismatchType = "C>T"
) {

  if (mismatchType == "C>T") {
    fileNamingMismatchType = character()
  } else {
    fileNamingMismatchType = mismatchType
  }

  # Get file paths for the expanded mismatch by read data
  mismatchData = fread(generateFilePath(
    mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
    cellType = cellType, lesion = lesion, timepoint = timepoint, includedMismatches = fileNamingMismatchType,
    repitition = repetition, expansionNum = expansionOffset, filtering = filtering
  ))

  # Filter the reads by length and mismatch type (single C>T).
  mismatchData = filterResults(mismatchData[V5 == mismatchType], minReadLength = readMinMax[1], maxReadLength = readMinMax[2])

  # Simplify the data
  mismatchData = simplifyTable(mismatchData, TRUE, expansionOffset = expansionOffset)

  # Read mismatch frequency z-scores.
  MMFreqZScore = fread(generateFilePath(
    directory = seqAndPosDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
    cellType = cellType, lesion = lesion, repitition = repetition,
    timepoint = timepoint, filtering = filtering, includedMismatches = mismatchType
  ))

  # Further filter data by read position based on length
  mismatchData = filterMismatchesByPositionAndReadLength(mismatchData, MMFreqZScore, expansionOffset = expansionOffset)

  # Orient data to mismatch positions.
  threePrimeMMAnchoredData = orientDataToMismatch(mismatchData, THREE_PRIME, expansionOffset)
  fivePrimeMMAnchoredData = orientDataToMismatch(mismatchData, FIVE_PRIME, expansionOffset)
  mismatchData = NULL

  # Now that the data has been processed, combine read length information.
  threePrimeMMAnchoredData[, Read_Length := NULL]
  threePrimeMMAnchoredData[, Read_Length := "combined"]
  fivePrimeMMAnchoredData[, Read_Length := NULL]
  fivePrimeMMAnchoredData[, Read_Length := "combined"]

  # Generate and write nucleotide frequency data.
  threePrimeMMAnchoredNucFreq = tabulateNucFreqByPosTimepointAndLength(setNames(list(threePrimeMMAnchoredData), timepoint))
  fwrite(threePrimeMMAnchoredNucFreq, sep = '\t', file = generateFilePath(
    directory = excisionSiteDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv", includedMismatches = fileNamingMismatchType,
    cellType = cellType, lesion = lesion, repitition = repetition, timepoint = timepoint, strandPolarity = "three_prime",
    anchored = TRUE, filtering = filtering, additionalInformation = "combined_read_lengths"
  ))
  fivePrimeMMAnchoredNucFreq = tabulateNucFreqByPosTimepointAndLength(setNames(list(fivePrimeMMAnchoredData), timepoint))
  fwrite(fivePrimeMMAnchoredNucFreq, sep = '\t', file = generateFilePath(
    directory = excisionSiteDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv", includedMismatches = fileNamingMismatchType,
    cellType = cellType, lesion = lesion, repitition = repetition, timepoint = timepoint, strandPolarity = "five_prime",
    anchored = TRUE, filtering = filtering, additionalInformation = "combined_read_lengths"
  ))

  # Generate and write sequence frequency data.
  threePrimeMMAnchoredSeqFreq = getSequenceFreqByReadLengthAndPos(threePrimeMMAnchoredData, queryPattern = queryPattern)
  fwrite(threePrimeMMAnchoredSeqFreq, sep = '\t', file = generateFilePath(
    directory = excisionSiteDirectory, dataTypeStrings$sequenceFrequency, ".tsv", includedMismatches = fileNamingMismatchType,
    cellType = cellType, lesion = lesion, repitition = repetition, timepoint = timepoint, strandPolarity = "three_prime",
    anchored = TRUE, sequence = sequencesName, filtering = filtering, additionalInformation = "combined_read_lengths"
  ))

  fivePrimeMMAnchoredSeqFreq = getSequenceFreqByReadLengthAndPos(fivePrimeMMAnchoredData, queryPattern = queryPattern)
  fwrite(fivePrimeMMAnchoredSeqFreq, sep = '\t', file = generateFilePath(
    directory = excisionSiteDirectory, dataTypeStrings$sequenceFrequency, ".tsv", includedMismatches = fileNamingMismatchType,
    cellType = cellType, lesion = lesion, repitition = repetition, timepoint = timepoint, strandPolarity = "five_prime",
    anchored = TRUE, sequence = sequencesName, filtering = filtering, additionalInformation = "combined_read_lengths"
  ))
}
```

```{r compute_and_write_sequence_frequencies}
HYV = c("ACA","ACC","ACG","ATA","ATC","ATG",
        "CCA","CCC","CCG","CTA","CTC","CTG",
        "TCA","TCC","TCG","TTA","TTC","TTG")
HYVPattern = "^[ACT][CT][ACG]"

computeMMAnchoredCombinedReadLengthSeqFreq(
  "CPD", "all_reps", "1h", "NHF1", NHF1MismatchesByReadDataDirectory, NHF1SequenceAndPositionDataDirectory,
  NHF1ExcisionSiteDataDirectory, HYVPattern, "HYV", humanReadMinMax
)
computeMMAnchoredCombinedReadLengthSeqFreq(
  "CPD", "all_reps", "1h", "NHF1", NHF1MismatchesByReadDataDirectory, NHF1SequenceAndPositionDataDirectory,
  NHF1ExcisionSiteDataDirectory, HYVPattern, "HYV", humanReadMinMax, mismatchType = "CC>TT"
)
```

### 2022-08-26 R/PaperFigureGeneration.rmd
Read length merging in plotting
- Changed nucleotide frequency and sequence frequency plotting to recognize data with merged read lengths and not stratify along a secondary y-axis.
- Created function for making read-length-merged nucleotide frequency and sequence frequency data anchored to mismatches. (This was a bad idea... data anchored to a mismatch causes variable cut-site positions that when combined destroy any relevant signals.)
- Updated 5' general read sequence analysis to perform nucleotide frequency generation and optionally combine read lengths.
- Updated paper figure generation.

@@
 }
-NHF1GeneralReadsCPDSeqFreqAllReps1hFiltered = fread(generateFilePath(
+
+NHF1GeneralReadsCPDNucFreqAllReps1hFilteredCombined = fread(generateFilePath(
+  NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+  cellType = "NHF1", lesion = "CPD", repitition = "all_reps", timepoint = "1h",
+  filtering = "TGG_filtered", additionalInformation = "combined_read_lengths"
+))
+NHF1GeneralReadsCPDSeqFreqAllReps1hFilteredCombined = fread(generateFilePath(
   NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
-  cellType = "NHF1", lesion = "CPD", timepoint = "1h",
-  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered"
+  cellType = "NHF1", lesion = "CPD", timepoint = "1h", repitition = "all_reps",
+  sequence = "HYV", filtering = "TGG_filtered", additionalInformation = "combined_read_lengths"
 ))
-arabidopsisGeneralReadsCPDSeqFreqAllRepsZT2Filtered = fread(generateFilePath(
+arabidopsisGeneralReadsCPDSeqFreqAllRepsZT2FilteredCombined = fread(generateFilePath(
   arabidopsisGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
   cellType = "Arabidopsis", lesion = "CPD", timepoint = "ZT2",
-  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered"
+  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered",
+  additionalInformation = "combined_read_lengths"
 ))
-yeastGeneralReadsCPDSeqFreqAllReps20MinFiltered = fread(generateFilePath(
+yeastGeneralReadsCPDSeqFreqAllReps20MinFilteredCombined = fread(generateFilePath(
   yeastGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
   cellType = "yeast", lesion = "CPD", timepoint = "20min",
-  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered"
+  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered",
+  additionalInformation = "combined_read_lengths"
 ))
-EColiGeneralReadsCPDSeqFreqAllReps5MinFiltered = fread(generateFilePath(
+EColiGeneralReadsCPDSeqFreqAllReps5MinFilteredCombined = fread(generateFilePath(
   EColiGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
   cellType = "E_coli_WT", lesion = "CPD", timepoint = "5min",
-  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered"
+  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered",
+  additionalInformation = "combined_read_lengths"
 ))
@@
 ```
-```{r figure_4C, fig.width = 5, fig.height = 6}
-plotSequenceFrequencies(NHF1GeneralReadsCPDSeqFreqAllReps1hFiltered[Position <= 7],
+```{r figure_4C, fig.width = 6.5, fig.height = 4.75}
+plotNucFreqVsReadLengthBarPlot(NHF1GeneralReadsCPDNucFreqAllReps1hFilteredCombined[Position <= 7], 
+                               title = "NHF1 CPD 1h All Reps TGG-Filtered Nuc Freq",
+                               secondaryYAxisLabel = "Read Length", ylim = c(0,1),
+                               posType = FIVE_PRIME, showFivePrimeCutSite = TRUE,
+                               expansionOffset = 10,
+                               xAxisLabel = "Mismatch Relative Position")
+```
+```{r figure_4D, fig.width = 5, fig.height = 4}
+plotSequenceFrequencies(NHF1GeneralReadsCPDSeqFreqAllReps1hFilteredCombined[Position <= 7],
                         title = "NHF1 CPD 1h All Reps TGG-Filtered General Reads HYV Freq",
@@
                         showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
-                        expansionOffset = 10, minReadLength = 23, maxReadLength = 29, backgroundPositions = -9:-4,
+                        expansionOffset = 10, backgroundPositions = -9:-4,
                         checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
-                        xAxisBreaks = c(-8, 0, 8))
+                        xAxisBreaks = c(-8, 0, 8), ylimMax = 0.6, ylimMaxModifier = 1)
 ```
-```{r figure_4D, fig.width = 5, fig.height = 6}
-plotSequenceFrequencies(arabidopsisGeneralReadsCPDSeqFreqAllRepsZT2Filtered[Position <= 7],
+```{r figure_4E, fig.width = 5, fig.height = 4}
+plotSequenceFrequencies(arabidopsisGeneralReadsCPDSeqFreqAllRepsZT2FilteredCombined[Position <= 7],
                         title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered General Reads HYV Freq",
@@
                         showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
-                        expansionOffset = 10, minReadLength = 24, maxReadLength = 30, backgroundPositions = -9:-4,
+                        expansionOffset = 10, backgroundPositions = -9:-4,
                         checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
-                        xAxisBreaks = c(-8, 0, 8))
+                        xAxisBreaks = c(-8, 0, 8), ylimMax = 0.6, ylimMaxModifier = 1)
 ```
-```{r figure_4E, fig.width = 5, fig.height = 6}
-plotSequenceFrequencies(yeastGeneralReadsCPDSeqFreqAllReps20MinFiltered[Position <= 7],
+```{r figure_4F, fig.width = 5, fig.height = 4}
+plotSequenceFrequencies(yeastGeneralReadsCPDSeqFreqAllReps20MinFilteredCombined[Position <= 7],
                         title = "Yeast CPD 20min All Reps TGG-Filtered General Reads HYV Freq",
@@
                         showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
-                        expansionOffset = 10, minReadLength = 22, maxReadLength = 25, backgroundPositions = -9:-4,
+                        expansionOffset = 10, backgroundPositions = -9:-4,
                         checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
-                        xAxisBreaks = c(-8, 0, 8))
+                        xAxisBreaks = c(-8, 0, 8), ylimMax = 0.6, ylimMaxModifier = 1)
 ```
-```{r figure_4F, fig.width = 5, fig.height = 6}
-plotSequenceFrequencies(EColiGeneralReadsCPDSeqFreqAllReps5MinFiltered[Position <= 7],
+```{r figure_4G, fig.width = 5, fig.height = 4}
+plotSequenceFrequencies(EColiGeneralReadsCPDSeqFreqAllReps5MinFilteredCombined[Position <= 7],
                         title = "E. coli CPD 5min All Reps TGG-Filtered General Reads HYV Freq",
@@
                         showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
-                        expansionOffset = 10, minReadLength = 11, maxReadLength = 13, xAxisLabel = "5' Relative Position",
-                        xAxisBreaks = c(-8, 0, 8))
+                        expansionOffset = 10, xAxisLabel = "5' Relative Position",
+                        xAxisBreaks = c(-8, 0, 8), ylimMax = 0.6, ylimMaxModifier = 1)
 ```
@@
 
-NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered = NHF1CPDTimepoints
-for (i in seq_along(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered)) {
-  NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
-    NHF1ExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllReps1hFiltered = fread(generateFilePath(
+    NHF1ExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv", timepoint = "1h",
     cellType = "NHF1", lesion = "CPD", repitition = "all_reps", includedMismatches = "CC>TT",
-    timepoint = names(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered)[i],
-    strandPolarity = "three_prime", anchored = TRUE, sequence = "HYV", filtering = "TGG_filtered"
+    strandPolarity = "three_prime", anchored = TRUE, sequence = "HYV", filtering = "TGG_filtered",
 ))
-}
 
@@
 
-```{r figure_6A, fig.width = 5, fig.height = 5}
+```{r figure_6A, fig.width = 5, fig.height = 5.5}
 ### Just the 1h timepoint ###
@@
                                          zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered,
-                                         yAxisLabel = "Relative C>T Frequency")
+                                         yAxisLabel = "Relative CC>TT Frequency")
 
@@
 #                                          zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered,
-#                                          yAxisLabel = "Relative C>T Frequency")
+#                                          yAxisLabel = "Relative CC>TT Frequency")
 ```
 ```{r figure_6B, fig.width = 5, fig.height = 5}
-### Just the 1h timepoint ###
-plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered$`1h`,
+plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllReps1hFiltered,
                         title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT 3' Anchored HYV Freq",
@@
                         xAxisOffset = 1)
-
-### All timepoints together ###
-# plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered,
-#                         title = "NHF1 CPD All Reps TGG-Filtered CC>TT 3' Anchored YR Freq",
-#                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
-#                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
-#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
-#                         endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
 ```
@@
 ```{r read_figure_S4_data}
-NHF1GeneralReadsSixFourSeqFreqAllReps20minFiltered = fread(generateFilePath(
+NHF1GeneralReadsSixFourSeqFreqAllReps20minFilteredCombined = fread(generateFilePath(
   NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
   cellType = "NHF1", lesion = "6-4", timepoint = "20min",
-  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered"
+  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered",
+  additionalInformation = "combined_read_lengths"
 ))
-GM12878GeneralReadsCisplatinSeqFreqRep1_90minFiltered = fread(generateFilePath(
+GM12878GeneralReadsCisplatinSeqFreqRep1_90minFilteredCombined = fread(generateFilePath(
   GM12878GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
   cellType = "GM12878", lesion = "cisplatin", timepoint = "90min",
-  repitition = "rep1", sequence = "HYV", filtering = "TGG_filtered"
+  repitition = "rep1", sequence = "HYV", filtering = "TGG_filtered",
+  additionalInformation = "combined_read_lengths"
 ))
@@
 
-```{r figure_S4, fig.width = 5, fig.height = 6}
-plotSequenceFrequencies(NHF1GeneralReadsSixFourSeqFreqAllReps20minFiltered[Position <= 7],
+```{r figure_S4, fig.width = 5, fig.height = 4}
+plotSequenceFrequencies(NHF1GeneralReadsSixFourSeqFreqAllReps20minFilteredCombined[Position <= 7],
                         title = "NHF1 6-4 20min All Reps TGG-Filtered General Reads HYV Freq",
@@
                         checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
-                        xAxisOffset = 1)
-plotSequenceFrequencies(GM12878GeneralReadsCisplatinSeqFreqRep1_90minFiltered[Position <= 7],
+                        xAxisOffset = 1, ylimMax = 0.6, ylimMaxModifier = 1)
+plotSequenceFrequencies(GM12878GeneralReadsCisplatinSeqFreqRep1_90minFilteredCombined[Position <= 7],
                         title = "GM12878 cisplatin 90min Rep1 TGG-Filtered General Reads HYV Freq",
@@
                         checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
-                        xAxisOffset = 1)
+                        xAxisOffset = 1, ylimMax = 0.6, ylimMaxModifier = 1)
 ```
@@
 
-```{r figure_S5, fig.width = 9, fig.height = 5}
-plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered,
+```{r figure_S5, fig.width = 5, fig.height = 5.5}
+plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered["1h"],
                                          title = "NHF1 CPD All Reps GG>AA Mismatch Pos Freq",

### 2022-08-26 R/DeaminationAnchoredExcisionSiteAnalysis.R

@@ -106,11 +106,10 @@ combineNucleotideFrequencies = function(frequencyData, combineNucleotides = list
 plotNucFreqVsReadLengthBarPlot = function(nucFreqTable, posType = THREE_PRIME,
                                           title = "Nuc Freq by Length and Timepoint",
                                           yAxisLabel = "Nucleotide Frequency", secondaryYAxisLabel = "Read Length",
-                                          yStripFontSize = 16,
+                                          yStripFontSize = 16, ylim = c(0,1.2), yAxisBreaks = c(0,0.5,1),
                                           combineNucleotides = list(), combinedNames = list(),
                                           showThreePrimeCutSite = FALSE, showFivePrimeCutSite = FALSE,
                                           expansionOffset = 0, xAxisBreaks = -3:3*10, xAxisLabel = NULL,
-                                          ylim = c(0,1.2), yAxisBreaks = c(0,0.5,1),
                                           minReadLength = NULL, maxReadLength = NULL) {
 
   if (is.null(xAxisLabel)) {
@@ -125,18 +124,24 @@ plotNucFreqVsReadLengthBarPlot = function(nucFreqTable, posType = THREE_PRIME,
     nucFreqTable = combineNucleotideFrequencies(nucFreqTable, combineNucleotides, combinedNames)
   }
 
-  if (!is.null(minReadLength)) nucFreqTable = nucFreqTable[Read_Length >= minReadLength]
-  if (!is.null(maxReadLength)) nucFreqTable = nucFreqTable[Read_Length <= maxReadLength]
+  combinedReadLengths = all(nucFreqTable$Read_Length == "combined")
+
+  if (!combinedReadLengths) {
+    if (!is.null(minReadLength)) nucFreqTable = nucFreqTable[Read_Length >= minReadLength]
+    if (!is.null(maxReadLength)) nucFreqTable = nucFreqTable[Read_Length <= maxReadLength]
+  }
 
   plot = ggplot(nucFreqTable, aes(Position, Frequency, fill = Nucleotide)) +
     geom_bar(position = "stack", stat = "identity") +
     labs(title = title, x = xAxisLabel, y = yAxisLabel) +
     blankBackground + defaultTextScaling
 
-  if (all(nucFreqTable$Timepoint == "NONE")) {
[…]

### 2022-09-14 R/PaperFigureGeneration.rmd
Update PaperFigureGeneration.rmd

@@
                                expansionOffset = 10,
-                               xAxisLabel = "Mismatch Relative Position")
+                               xAxisLabel = "5' Relative Position")
 ```

### 2022-12-02 R/DeaminationAnchoredExcisionSiteAnalysis.R
Updates for deprecated ggplot syntax

@@ -145,8 +145,8 @@ plotNucFreqVsReadLengthBarPlot = function(nucFreqTable, posType = THREE_PRIME,
   }
 
   plot = plot +
-    theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
-          strip.background = element_rect(color = "black", size = 1),
+    theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1),
+          strip.background = element_rect(color = "black", linewidth = 1),
           axis.text.y.right = element_blank(), axis.ticks.y.right = element_blank(),
           axis.text.y.left = element_text(size = 10),
           strip.text.y = element_text(size = yStripFontSize)) +
@@ -340,8 +340,8 @@ plotSequenceEnrichment = function(enrichmentTablesByTimepoint, posType = THREE_P
   }
 
   plot = plot +
-    theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
-          strip.background = element_rect(color = "black", size = 1),
+    theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1),
+          strip.background = element_rect(color = "black", linewidth = 1),
           axis.text.y = element_text(size = yAxisTickTextSize),
           axis.ticks.y.right = element_blank(), axis.text.y.right = element_blank(),
           strip.text.y = element_text(size = yStripFontSize)) +
@@ -512,8 +512,8 @@ plotSequenceFrequencies = function(seqFreqTablesByTimepoint, posType = THREE_PRI
   }
 
   plot = plot +
-    theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
-          strip.background = element_rect(color = "black", size = 1),
+    theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1),
+          strip.background = element_rect(color = "black", linewidth = 1),
           axis.text.y = element_text(size = 10),
           axis.text.y.right = element_blank(), axis.ticks.y.right = element_blank(),
           strip.text.y = element_text(size = yStripFontSize)) +

### 2022-12-02 R/DeaminationParseAndFilter.R

@@ -161,12 +161,12 @@ plotZScoreAcrossTimepointAndReadLength = function(zScoreTables, title = "Mismatc
   }
 
   plot = plot +
-    theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
-          strip.background = element_rect(color = "black", size = 1),
+    theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1),
+          strip.background = element_rect(color = "black", linewidth = 1),
           axis.text.y = element_text(size = 12), strip.text.y = element_text(size = 16),
           axis.text.y.right = element_blank(), axis.ticks.y.right = element_blank()) +
     scale_x_continuous(breaks = xAxisBreaks) +
-    geom_hline(yintercept = zScoreCutoff, linetype = 2, size = 0.5)
+    geom_hline(yintercept = zScoreCutoff, linetype = 2, linewidth = 0.5)
 
   print(plot)
 

### 2022-12-02 R/DeaminationSequenceAndPositionAnalysis.R

@@ -161,8 +161,8 @@ plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTy
   }
 
   plot = plot +
-    theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
-          strip.background = element_rect(color = "black", size = 1),
+    theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1),
+          strip.background = element_rect(color = "black", linewidth = 1),
           axis.text.y.right = element_blank(), axis.ticks.y.right = element_blank(),
           strip.text.y = element_text(size = 16)) +
     geom_vline(xintercept = modePosition) +
@@ -202,8 +202,8 @@ plotReadLengthFrequencies = function(readLengthCountTables, title = "Read Length
   }
 
   plot = plot +
-    theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
-          strip.background = element_rect(color = "black", size = 1),
+    theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1),
+          strip.background = element_rect(color = "black", linewidth = 1),
           axis.text = element_text(size = 15), strip.text.y = element_text(size = 16)) +
     scale_y_continuous(breaks = yAxisBreaks)
 
@@ -280,7 +280,7 @@ plotGroupedPositionStats = function(threePrimeGroupedStats, fivePrimeGroupedStat
   if (stat == POS_DIFF) {
     groupedStatsPlot =
       ggplot(aggregateData, aes(Read_Length, Absolute_Pos_Change, color = Timepoint, linetype = Position_Type)) +
-      geom_line(size = 1.5) + theme(legend.key.width = unit(3, "line")) +
+      geom_line(linewidth = 1.5) + theme(legend.key.width = unit(3, "line")) +
       scale_linetype_manual(values = c("3' Relative Position" = "dashed", "5' Relative Position" = "solid"))
   } else if (stat == IQR) {
     groupedStatsPlot =

### 2022-12-02 R/PaperFigureGeneration.rmd
Added new figure (now S5) for 3' nuc freq.

@@
 ```{r read_figure_S5_data}
+NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
+  NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
+  strandPolarity = "five_prime", anchored = TRUE, filtering = "TGG_filtered"
+))
+```
+
+```{r figure_S5, fig.width = 6.5, fig.height = 6}
+plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
+                               title = "NHF1 CPD 1h All Reps TGG-Filtered 5' Anchored Nuc Freq",
+                               secondaryYAxisLabel = "3' Cut Site Distance",
+                               posType = THREE_PRIME, showThreePrimeCutSite = TRUE,
+                               expansionOffset = 10, minReadLength = 6, maxReadLength = 12,
+                               xAxisLabel = "Mismatch Relative Position")
+```
+
+```{r read_figure_S6_data}
 NHF1CPDGGtoAAMismatchDataAllRepsFiltered = NHF1CPDTimepoints
@@
 
-```{r figure_S5, fig.width = 5, fig.height = 5.5}
+```{r figure_S6, fig.width = 5, fig.height = 5.5}
 plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered["1h"],

### 2022-12-02 R/UsefulFileSystemFunctions.R
Added new data type string for sequence logo input

@@ -13,7 +13,8 @@ dataTypeStrings =
        alignedReads = "aligned_reads",
        mismatchFrequencyZScores = "mismatch_frequency_z-scores",
        readLengthcounts = "read_length_counts",
-       tandemMismatchCountsComparison = "tandem_mismatch_counts_comparison")
+       tandemMismatchCountsComparison = "tandem_mismatch_counts_comparison",
+       sequenceLogoInput = "sequence_logo_input")
 
 generateFilePath = function(directory, dataTypeString, fileExtension,
                             cellType = NA, lesion = NA, timepoint = NA, repitition = NA,

### 2022-12-02 R/5'CutSiteAnalysisDataGeneration.rmd
Added code for sequence logo input generation
-Note to self: Don't generate data for a paper again without documenting how it was generated :(
- I should probably rename/rework this script since it doesn't (and probably shouldn't) deal exclusively with the 5' end of sequences.

@@
                            queryPattern, sequencesName, readMinMax,
-                           alsoComputeCombinedReadLengths = FALSE, alsoComputeNucFreq = FALSE) {
+                           alsoComputeCombinedReadLengths = FALSE, alsoComputeNucFreq = FALSE,
+                           alsoCreateSequenceLogoInput = FALSE) {
   readData = fread(generateFilePath(
@@
     timepoint = timepoint, sequence = sequencesName, filtering = filtering))
+
+  if (alsoCreateSequenceLogoInput) {
+    write(str_sub(readData$Read_Sequence, 1, 17), sep = '\n', file = generateFilePath(
+      directory, dataTypeStrings$sequenceLogoInput, ".txt",
+      cellType = cellType, lesion = lesion, repitition = repetition,
+      timepoint = timepoint, strandPolarity = FIVE_PRIME, filtering = filtering
+    ))
+    write(str_sub(readData$Read_Sequence, -14, -1), sep = '\n', file = generateFilePath(
+      generalReadSequenceDataDirectory, dataTypeStrings$sequenceLogoInput, ".txt",
+      cellType = cellType, lesion = lesion, repitition = repetition,
+      timepoint = timepoint, strandPolarity = THREE_PRIME, filtering = filtering
+    ))
+  }
 
@@
                 HYVPattern, "HYV", humanReadMinMax, alsoComputeCombinedReadLengths = TRUE,
-                alsoComputeNucFreq = TRUE)
+                alsoComputeNucFreq = TRUE, alsoCreateSequenceLogoInput = TRUE)
 cutSiteAnalysis("6-4", "all_reps", "20min", "NHF1", NHF1GeneralReadSequenceDataDirectory,
-                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombineReadLengths = TRUE)
+                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombineReadLengths = TRUE,
+                alsoCreateSequenceLogoInput = TRUE)
 cutSiteAnalysis("cisplatin", "rep1", "90min", "GM12878", GM12878GeneralReadSequenceDataDirectory,
-                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombinedReadLengths = TRUE)
+                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombinedReadLengths = TRUE,
+                alsoCreateSequenceLogoInput = TRUE)
 cutSiteAnalysis("CPD", "all_reps", "20min", "yeast", yeastGeneralReadSequenceDataDirectory,
-                HYVPattern, "HYV", yeastReadMinMax, alsoComputeCombinedReadLengths = TRUE)
+                HYVPattern, "HYV", yeastReadMinMax, alsoComputeCombinedReadLengths = TRUE,
+                alsoCreateSequenceLogoInput = TRUE)
 cutSiteAnalysis("CPD", "all_reps", "ZT2", "Arabidopsis", arabidopsisGeneralReadSequenceDataDirectory,
-                HYVPattern, "HYV", arabidopsisReadMinMax, alsoComputeCombinedReadLengths = TRUE)
+                HYVPattern, "HYV", arabidopsisReadMinMax, alsoComputeCombinedReadLengths = TRUE,
+                alsoCreateSequenceLogoInput = TRUE)
 cutSiteAnalysis("CPD", "all_reps", "5min", "E_coli_WT", EColiGeneralReadSequenceDataDirectory,
-                HYVPattern, "HYV", EColiReadMinMax, alsoComputeCombinedReadLengths = TRUE)
+                HYVPattern, "HYV", EColiReadMinMax, alsoComputeCombinedReadLengths = TRUE,
+                alsoCreateSequenceLogoInput = TRUE)
 ```

### 2022-12-06 R/5'CutSiteAnalysisDataGeneration.rmd
Fixed a bug involving a misnamed variable

@@
     write(str_sub(readData$Read_Sequence, -14, -1), sep = '\n', file = generateFilePath(
-      generalReadSequenceDataDirectory, dataTypeStrings$sequenceLogoInput, ".txt",
+      directory, dataTypeStrings$sequenceLogoInput, ".txt",
       cellType = cellType, lesion = lesion, repitition = repetition,

### 2022-12-15 python/CreateWebLogo.py
Create CreateWebLogo.py
Provides a python interface to my preferred weblogo command line arguments. Input should be a text file containing one DNA sequence per line.

@@ -1,0 +1,74 @@
+# Provides a python interface to my preferred weblogo command line arguments.
+# Input should be a text file containing one DNA sequence per line.
+import os, subprocess
+from typing import List
+from benbiohelpers.TkWrappers.TkinterDialog import TkinterDialog
+from benbiohelpers.CustomErrors import InvalidPathError, UserInputError
+FIVE_PRIME = "three_prime"
+THREE_PRIME = "five_prime"
+
+def createWebLogo(inputFilePaths: List[str], composition):
+
+    outputFilePaths: List[str] = list()
+
+    for inputFilePath in inputFilePaths:
+
+        print(f"Working with {os.path.basename(inputFilePath)}...")
+
+        if "three_prime" in os.path.basename(inputFilePath): strandPolarity = THREE_PRIME
+        elif "five_prime" in os.path.basename(inputFilePath): strandPolarity = FIVE_PRIME
+        else: raise InvalidPathError(inputFilePath, "Expected strand polarity in basename of file path")
+
+        outputFilePath = inputFilePath.replace("sequence_logo_input","sequence_logo").replace(".txt", ".png")
+        outputFilePaths.append(outputFilePath)
+
+        webLogoArgs = ["weblogo", "-F", "png", "--errorbars", "NO", "-C", "red", "A", '"Adenine"', "-C", "blue", "C",
+                       '"Cytosine"', "-C", "green", "G", '"Guanine"', "-C", "purple", "T", '"Thymine"', "--aspect-ratio",
+                       '3', "--resolution", "1000", "-S", "0.5", "--annotate"]
+        if strandPolarity == FIVE_PRIME: webLogoArgs.append("-9,-8,-7,-6,-5,-4,-3,-2,-1,0,1,2,3,4,5,6,7")
+        elif strandPolarity == THREE_PRIME: webLogoArgs.append("-4,-3,-2,-1,0,1,2,3,4,5,6,7,8,9") 
+        
+        if composition is None:
+            pass
+        elif type(composition) is int:
+            GCContent = composition
+            ATContent = 100 - GCContent
+            webLogoArgs += ["--composition",
+                            f"\"{{'A':{ATContent/2}, 'C':{GCContent/2}, 'G':{GCContent/2}, 'T':{ATContent/2}}}\""]
+        else:
+            webLogoArgs += ["--composition", f"\"{composition}\""]
+
[…]

### 2022-12-15 python/FilterNonstandardNucleotides.py
Create FilterNonstandardNucleotides.py
Filters a simple text file where each line contains a nucleotide sequence. Sequences with nonstandard nucleotides (i.e. any except A, C, G, T, and N) are removed from the output.

@@ -1,0 +1,37 @@
+# Filters a simple text file where each line contains a nucleotide sequence.
+# Sequences with nonstandard nucleotides (i.e. any except A, C, G, T, and N) are removed from the output.
+import os
+from typing import List
+from benbiohelpers.TkWrappers.TkinterDialog import TkinterDialog
+nucleotides = {'A','C','G','T','N'}
+
+
+def filterNonstandardNucleotides(inputFilePaths: List[str]):
+
+    outputFilePaths: List[str] = list()
+
+    for inputFilePath in inputFilePaths:
+
+        print(f"Working with {os.path.basename(inputFilePath)}...")
+
+        outputFilePath = inputFilePath.rsplit('.', 1)[0] + "_nonstandard_nuc_filtered.txt"
+        outputFilePaths.append(outputFilePath)
+
+        with open(inputFilePath, 'r') as inputFile:
+            with open(outputFilePath, 'w') as outputFile:
+                for line in inputFile:
+                    if nucleotides.issuperset(line.strip()): outputFile.write(line)
+                    else: print(line.strip())
+
+    return outputFilePaths
+
+
+def main():
+
+    with TkinterDialog(workingDirectory = os.path.join(__file__,"..")) as dialog:
+        dialog.createMultipleFileSelector("Simple text nucleotide files:", 0, "simple_nuc.txt", ("text files", ".txt"))
+
+    filterNonstandardNucleotides(dialog.selections.getFilePathGroups()[0])
+
+
+if __name__ == "__main__": main()

### 2022-12-15 R/PaperFigureGeneration.rmd
Update PaperFigureGeneration.rmd
Added nucleotide frequency plots for the 3' cut site of Arabidopsis and yeast

@@
 ))
+arabidopsisFivePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
+  arabidopsisExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+  cellType = "Arabidopsis", lesion = "CPD", repitition = "all_reps",
+  strandPolarity = "five_prime", anchored = TRUE, filtering = "TGG_filtered"
+))
+yeastFivePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
+  yeastExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
+  cellType = "yeast", lesion = "CPD", repitition = "all_reps",
+  strandPolarity = "five_prime", anchored = TRUE, filtering = "TGG_filtered"
+))
 ```
@@
                                title = "NHF1 CPD 1h All Reps TGG-Filtered 5' Anchored Nuc Freq",
+                               secondaryYAxisLabel = "3' Cut Site Distance",
+                               posType = THREE_PRIME, showThreePrimeCutSite = TRUE,
+                               expansionOffset = 10, minReadLength = 6, maxReadLength = 12,
+                               xAxisLabel = "Mismatch Relative Position")
+plotNucFreqVsReadLengthBarPlot(arabidopsisFivePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "ZT2"], 
+                               title = "Arabidopsis CPD 1h All Reps TGG-Filtered 5' Anchored Nuc Freq",
+                               secondaryYAxisLabel = "3' Cut Site Distance",
+                               posType = THREE_PRIME, showThreePrimeCutSite = TRUE,
+                               expansionOffset = 10, minReadLength = 6, maxReadLength = 12,
+                               xAxisLabel = "Mismatch Relative Position")
+plotNucFreqVsReadLengthBarPlot(yeastFivePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "20min"], 
+                               title = "Yeast CPD 1h All Reps TGG-Filtered 5' Anchored Nuc Freq",
                                secondaryYAxisLabel = "3' Cut Site Distance",

### 2023-01-11 R/PaperFigureGeneration.rmd
Axis tweaks for figure generation
Various tweaks to how axes are displayed across figures to enforce consistent conventions. Conventions include:
- Labeling the first nucleotide outside of a repair fragment as position 0 when anchoring at a cut site
- Labeling a mismatch as position 0 when anchoring on that mismatch.
- Not showing a "0" axis label when that position cannot have data for a given graph.

@@
 plotMismatchPositionFrequencies(NHF1CPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
-                                title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Frequencies")
+                                title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Frequencies",
+                                xAxisBreaks = c(-1,-10,-20,-30))
 ```
@@
                                          yAxisLabel = "Relative C>T Frequency",
-                                         zScoreTables = NHF1CPDMMFreqZScoresAllReps)
+                                         zScoreTables = NHF1CPDMMFreqZScoresAllReps,
+                                         xAxisBreaks = c(-1,-10,-20,-30))
 
@@
                                expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
-                               xAxisLabel = "Mismatch Relative Position")
+                               xAxisLabel = "Mismatch Relative Position", positionOffset = -1)
 
@@
                         showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE, querySequences = c("TGG"),
-                        expansionOffset = 10, minReadLength = 20, maxReadLength = 27,
+                        expansionOffset = 10, minReadLength = 20, maxReadLength = 27, positionOffset = 10,
                         yAxisLabel = "TGG Trinucleotide Frequency", defaultColor = "Black")
@@
                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGGFiltered,
-                                         yAxisLabel = "Relative C>T Frequency")
+                                         yAxisLabel = "Relative C>T Frequency", xAxisBreaks = c(-1,-10,-20,-30))
 plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["ZT2"], includedTypes = c("C>T"),
@@
                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
-                                         yAxisLabel = "Relative C>T Frequency")
+                                         yAxisLabel = "Relative C>T Frequency", xAxisBreaks = c(-1,-10,-20,-30))
 plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["20min"], includedTypes = c("C>T"),
@@
                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
-                                         yAxisLabel = "Relative C>T Frequency")
+                                         yAxisLabel = "Relative C>T Frequency", xAxisBreaks = c(-1,-10,-20,-30))
 
@@
                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGGFiltered,
-                                         posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
+                                         posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency",
+                                         xAxisBreaks = c(1,10,20,30))
 plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["ZT2"], includedTypes = c("C>T"),
@@
                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
-                                         posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
+                                         posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency",
+                                         xAxisBreaks = c(1,10,20,30))
 plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["20min"], includedTypes = c("C>T"),
@@
                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
-                                         posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
+                                         posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency",
+                                         xAxisBreaks = c(1,10,20,30))
 
@@
                                expansionOffset = 10, minReadLength = 19, maxReadLength = 25,
-                               xAxisLabel = "Mismatch Relative Position")
+                               xAxisLabel = "Mismatch Relative Position", positionOffset = 1)
 ```
@@
                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 6,
-                        endBasedCheckPositions = -9, displayPValue = FALSE, xAxisLabel = "Mismatch Relative Position")
+                        endBasedCheckPositions = -9, displayPValue = FALSE, xAxisLabel = "Mismatch Relative Position",
+                        xAxisBreaks = c(-2,-10,-20,-30), xlim = c(-35, -4))
 
@@
                                posType = FIVE_PRIME, showFivePrimeCutSite = TRUE,
-                               expansionOffset = 10,
+                               expansionOffset = 10, xAxisBreaks = c(-9,0,7),
                                xAxisLabel = "5' Relative Position")
@@
 ```{r figure_4G, fig.width = 5, fig.height = 4}
-plotSequenceFrequencies(EColiGeneralReadsCPDSeqFreqAllReps5MinFilteredCombined[Position <= 7],
+plotSequenceFrequencies(EColiGeneralReadsCPDSeqFreqAllReps5MinFilteredCombined[Position <= 5],
                         title = "E. coli CPD 5min All Reps TGG-Filtered General Reads HYV Freq",
@@
                         expansionOffset = 10, xAxisLabel = "5' Relative Position",
-                        xAxisBreaks = c(-8, 0, 8), ylimMax = 0.6, ylimMaxModifier = 1)
+                        xlim = c(-9,7), xAxisBreaks = c(-8, 0, 6), ylimMax = 0.6, ylimMaxModifier = 1)
 ```
@@
       geom_text(aes(label=Tandem_Mismatches_Count), position = position_dodge(width = 0.9), vjust = -0.25, size = 5) +
-      blankBackground + defaultTextScaling + scale_fill_brewer(palette = "Set1") + coord_cartesian(ylim = c(0,200000))
+      blankBackground + defaultTextScaling + scale_fill_brewer(palette = "Set1") +
+      coord_cartesian(ylim = c(0,200000), expand = FALSE)
   )
@@
                                          zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered,
-                                         yAxisLabel = "Relative CC>TT Frequency")
+                                         yAxisLabel = "Relative CC>TT Frequency", xAxisBreaks = c(-30,-20,-10,-1))
 
@@
                         endBasedCheckPositions = -9, displayPValue = FALSE, xAxisLabel = "Mismatch Relative Position",
-                        xAxisOffset = 1)
+                        xAxisOffset = 1, xAxisBreaks = c(-2,-10,-20,-30), xlim = c(-35,-4))
 ```
@@
 plotMismatchPositionFrequencies(NHF1SixFourMismatchDataAllReps$`20min`, includedTypes = c("C>T"),
-                                title = "NHF1 6-4 20min All Reps Mismatch Pos Frequencies")
+                                title = "NHF1 6-4 20min All Reps Mismatch Pos Frequencies",
+                                xAxisBreaks = c(-1,-10,-20,-30))
 
@@
 plotMismatchPositionFrequencies(GM12878CisplatinMismatchDataAllReps$`90min`, includedTypes = c("C>T"),
-                                title = "GM12878 Cisplatin 90min All Reps Mismatch Pos Frequencies")
+                                title = "GM12878 Cisplatin 90min All Reps Mismatch Pos Frequencies",
+                                xAxisBreaks = c(-1,-10,-20,-30))
 
 plotMismatchPositionFrequencies(NHF1CPDMismatchDataAllReps$`1h`, omittedTypes = c("C>T"),
-                                title = "NHF1 CPD 1h All Reps !C>T Mismatch Pos Frequencies")
+                                title = "NHF1 CPD 1h All Reps !C>T Mismatch Pos Frequencies",
+                                xAxisBreaks = c(-1,-10,-20,-30))
 ```
@@
 plotMismatchPositionFrequencies(arabidopsisCPDMismatchDataAllReps$ZT2, includedTypes = c("C>T"),
-                                title = "Arabidopsis CPD ZT2 All Reps Mismatch Pos Frequencies")
+                                title = "Arabidopsis CPD ZT2 All Reps Mismatch Pos Frequencies",
+                                xAxisBreaks = c(-1,-10,-20,-30))
 
@@
 plotMismatchPositionFrequencies(yeastCPDMismatchDataAllReps$`20min`, includedTypes = c("C>T"),
-                                title = "Yeast CPD 20min All Reps Mismatch Pos Frequencies")
+                                title = "Yeast CPD 20min All Reps Mismatch Pos Frequencies",
+                                xAxisBreaks = c(-1,-10,-20,-30))
 
@@
                                 title = "CS-B CPD 1h All Reps Mismatch Pos Frequencies",
-                                ylim = c(0,0.25))
+                                ylim = c(0,0.25), xAxisBreaks = c(-1,-10,-20,-30))
 
@@
                                 title = "XP-C CPD 1h All Reps Mismatch Pos Frequencies",
-                                ylim = c(0,0.25))
+                                ylim = c(0,0.25), xAxisBreaks = c(-1,-10,-20,-30))
 ```
@@
 ```
+```{r figure_S3C, fig.width = 5, fig.height = 5}
+### Just the 1h timepoint ###
+plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered["1h"], includedTypes = c("C>T"),
+                                         title = "NHF1 CPD 1h All Reps TG-Filtered C>T Mismatch Pos Freq",
+                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGFiltered,
+                                         posType = THREE_PRIME, yAxisLabel = "Relative C>T Frequency",
+                                         xAxisBreaks = c(-1,-10,-20,-30))
+
+### All timepoints together ###
+# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGFiltered, includedTypes = c("C>T"),
+#                                          title = "NHF1 CPD All Reps TG-Filtered C>T Mismatch Pos Freq",
+#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGFiltered,
+#                                          posType = THREE_PRIME, yAxisLabel = "Relative C>T Frequency")
+```
 ```{r figure_S3D, fig.width = 5, fig.height = 5}
@@
                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGFiltered,
-                                         posType = THREE_PRIME, yAxisLabel = "Relative C>T Frequency")
+                                         posType = THREE_PRIME, yAxisLabel = "Relative C>T Frequency",
+                                         xAxisBreaks = c(-1,-10,-20,-30))
 
@@
                                expansionOffset = 10, minReadLength = 6, maxReadLength = 12,
-                               xAxisLabel = "Mismatch Relative Position")
+                               xAxisLabel = "Mismatch Relative Position", positionOffset = -1)
 plotNucFreqVsReadLengthBarPlot(arabidopsisFivePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "ZT2"], 
@@
                                expansionOffset = 10, minReadLength = 6, maxReadLength = 12,
-                               xAxisLabel = "Mismatch Relative Position")
+                               xAxisLabel = "Mismatch Relative Position", positionOffset = -1)
 plotNucFreqVsReadLengthBarPlot(yeastFivePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "20min"], 
@@
                                expansionOffset = 10, minReadLength = 6, maxReadLength = 12,
-                               xAxisLabel = "Mismatch Relative Position")
+                               xAxisLabel = "Mismatch Relative Position", positionOffset = -1)
 ```
@@
                                          zScoreTables = NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered,
-                                         yAxisLabel = "Relative GG>AA Frequency")
+                                         yAxisLabel = "Relative GG>AA Frequency",
+                                         xAxisBreaks = c(-1,-10,-20,-30))
 ```

### 2023-01-11 R/DeaminationAnchoredExcisionSiteAnalysis.R

@@ -109,8 +109,8 @@ plotNucFreqVsReadLengthBarPlot = function(nucFreqTable, posType = THREE_PRIME,
                                           yStripFontSize = 16, ylim = c(0,1.2), yAxisBreaks = c(0,0.5,1),
                                           combineNucleotides = list(), combinedNames = list(),
                                           showThreePrimeCutSite = FALSE, showFivePrimeCutSite = FALSE,
-                                          expansionOffset = 0, xAxisBreaks = -3:3*10, xAxisLabel = NULL,
-                                          minReadLength = NULL, maxReadLength = NULL) {
+                                          expansionOffset = 0, xlim = NULL, xAxisBreaks = -3:3*10, xAxisLabel = NULL,
+                                          minReadLength = NULL, maxReadLength = NULL, positionOffset = 0) {
 
   if (is.null(xAxisLabel)) {
     if (posType == THREE_PRIME) {
@@ -131,7 +131,12 @@ plotNucFreqVsReadLengthBarPlot = function(nucFreqTable, posType = THREE_PRIME,
     if (!is.null(maxReadLength)) nucFreqTable = nucFreqTable[Read_Length <= maxReadLength]
   }
 
-  plot = ggplot(nucFreqTable, aes(Position, Frequency, fill = Nucleotide)) +
+  if (is.null(xlim)) {
+    xlim = c(min(nucFreqTable$Position)-1 + positionOffset,
+             max(nucFreqTable$Position)+1 + positionOffset)
+  }
+
+  plot = ggplot(nucFreqTable, aes(Position + positionOffset, Frequency, fill = Nucleotide)) +
     geom_bar(position = "stack", stat = "identity") +
     labs(title = title, x = xAxisLabel, y = yAxisLabel) +
     blankBackground + defaultTextScaling
@@ -150,7 +155,7 @@ plotNucFreqVsReadLengthBarPlot = function(nucFreqTable, posType = THREE_PRIME,
           axis.text.y.right = element_blank(), axis.ticks.y.right = element_blank(),
           axis.text.y.left = element_text(size = 10),
           strip.text.y = element_text(size = yStripFontSize)) +
-    coord_cartesian(ylim = ylim) +
+    coord_cartesian(ylim = ylim, xlim = xlim, expand = FALSE) +
     scale_x_continuous(breaks = xAxisBreaks)
 
   if (combinedReadLengths) {
[…]

### 2023-01-11 R/DeaminationSequenceAndPositionAnalysis.R

@@ -39,7 +39,8 @@ plotMismatchTypeFrequencies = function(mismatchTable, title = "Mismatch Type Fre
 # Displays the frequencies of positions for the chosen mismatch types.
 # (Types can be chosen by inclusion or omission)
 plotMismatchPositionFrequencies = function(mismatchTable, includedTypes = list(), omittedTypes = list(),
-                                           title = "Position Frequency", posType = THREE_PRIME, ylim = NULL) {
+                                           title = "Position Frequency", posType = THREE_PRIME, ylim = NULL,
+                                           xAxisBreaks = waiver()) {
 
   if (posType == THREE_PRIME) {
     xAxisLabel = "3' Relative Position"
@@ -62,6 +63,7 @@ plotMismatchPositionFrequencies = function(mismatchTable, includedTypes = list()
   print(
     ggplot(frequencyData, aes(x = Position, y = Freq)) +
       geom_bar(stat = "identity") + coord_cartesian(ylim = ylim) +
+      scale_x_continuous(breaks = xAxisBreaks) +
       labs(title = title, x = xAxisLabel, y = "Relative Frequency") +
       blankBackground + defaultTextScaling
   )
@@ -74,7 +76,8 @@ plotMismatchPositionFrequencies = function(mismatchTable, includedTypes = list()
 plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTypes = list(), omittedTypes = list(),
                                                     title = "Mismatch Position Frequencies", posType = THREE_PRIME,
                                                     zScoreTables = NULL, zScoreCutoff = 4, xAxisBreaks = -3:3*10,
-                                                    yAxisBreaks = NULL, yAxisLabel = "Relative Frequency") {
+                                                    yAxisBreaks = NULL, yAxisLabel = "Relative Frequency",
+                                                    xlim = NULL) {
 
   #If passed a single data.table, wrap it in a list.
   if (is.data.table(simplifiedTables)) {
@@ -92,10 +95,8 @@ plotPositionAcrossTimepointAndReadLength = function(simplifiedTables, includedTy
 
   if (posType == THREE_PRIME) {
     xAxisLabel = "3' Relative Position"
-    xlim = c(min(xAxisBreaks)*1.1,0)
   } else if (posType == FIVE_PRIME) {
[…]

### 2023-02-08 R/DeaminationSequenceAndPositionAnalysis.R
Added option to print dipyrimidine frequency
Added the option to also print the dipyrimidine frequency when plotting trinucleotide context frequencies.

@@ -317,7 +317,7 @@ plotGroupedPositionStats = function(threePrimeGroupedStats, fivePrimeGroupedStat
 
 # Plots the trinucleotide context for a set of mismatches
 plotTrinucleotideContext = function(simplifiedMismatchTable, includedTypes = list(), omittedTypes = list(),
-                                    title = "Trinucleotide Context") {
+                                    title = "Trinucleotide Context", printDipyFreq = FALSE) {
 
   if ( length(includedTypes) > 0 && length(omittedTypes) > 0) {
     stop("Included types and omitted types given simultaneously")
@@ -338,5 +338,9 @@ plotTrinucleotideContext = function(simplifiedMismatchTable, includedTypes = lis
       theme(legend.position = "none", axis.text.x = element_text(size = 12)) +
       blankBackground + defaultTextScaling + scale_fill_brewer(palette = "Set1")
   )
+
+  if (printDipyFreq) {
+    print(sum(trinucContextFrequencies[grepl("[CT][CT]", Trinuc_Context), Freq]))
+  }
 
 }

### 2023-02-08 R/PaperFigureGeneration.rmd
Update PaperFigureGeneration.rmd
- Updated to print dipyrimidine frequencies in conjunction with trinucleotide context frequency plots.
- Rearranged chunks to fit new supplementary figure layouts.

@@
 ```{r figure_1C}
+print("NHF1 CPD 1h all reps C>T mismatch dipyrimidine context frequency:")
 plotTrinucleotideContext(NHF1CPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
-                         title = "NHF1 CPD 1h All Reps C>T Mismatch Trinuc Context")
+                         title = "NHF1 CPD 1h All Reps C>T Mismatch Trinuc Context",
+                         printDipyFreq = TRUE)
 ```
@@
 
-```{r read_figure_S1_data}
+```{r figure_S1}
+plotMismatchPositionFrequencies(NHF1CPDMismatchDataAllReps$`1h`, omittedTypes = c("C>T"),
+                                title = "NHF1 CPD 1h All Reps !C>T Mismatch Pos Frequencies",
+                                xAxisBreaks = c(-1,-10,-20,-30))
+```
+
+```{r read_figure_S2_data}
 NHF1SixFourMismatchDataAllReps = NHF1SixFourTimepoints
@@
 
-```{r figure_S1}
+```{r figure_S2}
 plotMismatchTypeFrequencies(NHF1SixFourMismatchDataAllReps$`20min`,
                             title = "NHF1 6-4 20min All Reps Mismatch Type Frequencies")
+plotMismatchTypeFrequencies(GM12878CisplatinMismatchDataAllReps$`90min`,
+                            title = "GM12878 Cisplatin 90min All Reps Mismatch Type Frequencies")
 
+print("NHF1 6-4 20min all reps C>T mismatch dipyrimidine context frequency:")
 plotTrinucleotideContext(NHF1SixFourMismatchDataAllReps$`20min`, includedTypes = c("C>T"),
-                         title = "NHF1 6-4 20min All Reps Mismatch Trinuc Context")
+                         title = "NHF1 6-4 20min All Reps Mismatch Trinuc Context",
+                         printDipyFreq = TRUE)
+
+print("GM12878 cisplatin 90min all reps C>T mismatch dipyrimidine context frequency:")
+plotTrinucleotideContext(GM12878CisplatinMismatchDataAllReps$`90min`, includedTypes = c("C>T"),
+                         title = "GM12878 Cisplatin 90min All Reps Mismatch Trinuc Context",
+                         printDipyFreq = TRUE)
 
@@
 
-plotMismatchTypeFrequencies(GM12878CisplatinMismatchDataAllReps$`90min`,
-                            title = "GM12878 Cisplatin 90min All Reps Mismatch Type Frequencies")
-
-plotTrinucleotideContext(GM12878CisplatinMismatchDataAllReps$`90min`, includedTypes = c("C>T"),
-                         title = "GM12878 Cisplatin 90min All Reps Mismatch Trinuc Context")
-
 plotMismatchPositionFrequencies(GM12878CisplatinMismatchDataAllReps$`90min`, includedTypes = c("C>T"),
@@
                                 xAxisBreaks = c(-1,-10,-20,-30))
-
-plotMismatchPositionFrequencies(NHF1CPDMismatchDataAllReps$`1h`, omittedTypes = c("C>T"),
-                                title = "NHF1 CPD 1h All Reps !C>T Mismatch Pos Frequencies",
-                                xAxisBreaks = c(-1,-10,-20,-30))
 ```
 
-```{r read_figure_S2_data}
+```{r read_figure_S3_data}
 arabidopsisCPDMismatchDataAllReps = arabidopsisCPDTimepoints
@@
 }
+```
 
+```{r figure_S3}
+plotMismatchTypeFrequencies(arabidopsisCPDMismatchDataAllReps$ZT2,
+                            title = "Arabidopsis CPD ZT2 All Reps Mismatch Type Frequencies")
+
+plotMismatchTypeFrequencies(yeastCPDMismatchDataAllReps$`20min`,
+                            title = "Yeast CPD 20min All Reps Mismatch Type Frequencies")
+
+print("Arabidopsis CPD 30min all reps C>T mismatch dipyrimidine context frequency:")
+plotTrinucleotideContext(arabidopsisCPDMismatchDataAllReps$ZT2, includedTypes = c("C>T"),
+                         title = "Arabidopsis CPD ZT2 All Reps Mismatch Trinuc Context",
+                         printDipyFreq = TRUE)
+
+print("Yeast CPD 20min all reps C>T mismatch dipyrimidine context frequency:")
+plotTrinucleotideContext(yeastCPDMismatchDataAllReps$`20min`, includedTypes = c("C>T"),
+                         title = "Yeast CPD 20min All Reps Mismatch Trinuc Context",
+                         printDipyFreq = TRUE)
+
+plotMismatchPositionFrequencies(arabidopsisCPDMismatchDataAllReps$ZT2, includedTypes = c("C>T"),
+                                title = "Arabidopsis CPD ZT2 All Reps Mismatch Pos Frequencies",
+                                xAxisBreaks = c(-1,-10,-20,-30))
+
+plotMismatchPositionFrequencies(yeastCPDMismatchDataAllReps$`20min`, includedTypes = c("C>T"),
+                                title = "Yeast CPD 20min All Reps Mismatch Pos Frequencies",
+                                xAxisBreaks = c(-1,-10,-20,-30))
+```
+
+```{r read_figure_S4_data}
 CSBCPDMismatchDataAllReps = CSBCPDTimepoints
@@
 
-```{r figure_S2}
-plotMismatchTypeFrequencies(arabidopsisCPDMismatchDataAllReps$ZT2,
-                            title = "Arabidopsis CPD ZT2 All Reps Mismatch Type Frequencies")
-
-plotTrinucleotideContext(arabidopsisCPDMismatchDataAllReps$ZT2, includedTypes = c("C>T"),
-                         title = "Arabidopsis CPD ZT2 All Reps Mismatch Trinuc Context")
-
-plotMismatchPositionFrequencies(arabidopsisCPDMismatchDataAllReps$ZT2, includedTypes = c("C>T"),
-                                title = "Arabidopsis CPD ZT2 All Reps Mismatch Pos Frequencies",
-                                xAxisBreaks = c(-1,-10,-20,-30))
-
-plotMismatchTypeFrequencies(yeastCPDMismatchDataAllReps$`20min`,
-                            title = "Yeast CPD 20min All Reps Mismatch Type Frequencies")
-
-plotTrinucleotideContext(yeastCPDMismatchDataAllReps$`20min`, includedTypes = c("C>T"),
-                         title = "Yeast CPD 20min All Reps Mismatch Trinuc Context")
-
-plotMismatchPositionFrequencies(yeastCPDMismatchDataAllReps$`20min`, includedTypes = c("C>T"),
-                                title = "Yeast CPD 20min All Reps Mismatch Pos Frequencies",
-                                xAxisBreaks = c(-1,-10,-20,-30))
-
+```{r figure_S4}
 plotMismatchTypeFrequencies(CSBCPDMismatchDataAllReps$`1h`,
@@
 
+plotMismatchTypeFrequencies(XPCCPDMismatchDataAllReps$`1h`,
+                            title = "XP-C CPD 1h All Reps Mismatch Type Frequencies")
+
+print("CS-B CPD 1h all reps C>T mismatch dipyrimidine context frequency:")
 plotTrinucleotideContext(CSBCPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
-                         title = "CS-B CPD 1h All Reps Mismatch Trinuc Context")
+                         title = "CS-B CPD 1h All Reps Mismatch Trinuc Context",
+                         printDipyFreq = TRUE)
+
+print("XPC CPD 1h all reps C>T mismatch dipyrimidine context frequency:")
+plotTrinucleotideContext(XPCCPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
+                         title = "XP-C CPD 1h All Reps Mismatch Trinuc Context",
+                         printDipyFreq = TRUE)
 
@@
                                 ylim = c(0,0.25), xAxisBreaks = c(-1,-10,-20,-30))
-
-plotMismatchTypeFrequencies(XPCCPDMismatchDataAllReps$`1h`,
-                            title = "XP-C CPD 1h All Reps Mismatch Type Frequencies")
-
-plotTrinucleotideContext(XPCCPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
-                         title = "XP-C CPD 1h All Reps Mismatch Trinuc Context")
 
@@
 
-```{r read_figure_S3_data}
+```{r read_figure_S5_data}
 NHF1FivePrimeMismatchCPDNucFreqAllRepsTGGFiltered = fread(generateFilePath(
@@
 
-```{r figure_S3A, fig.width = 6.5, fig.height = 6}
+```{r figure_S5A, fig.width = 6.5, fig.height = 6}
 ### Just the 1h timepoint ###
@@
 ```
-```{r figure_S3B, fig.width = 6.5, fig.height = 6}
+```{r figure_S5B, fig.width = 6.5, fig.height = 6}
 ### Just the 1h timepoint ###
@@
 ```
-```{r figure_S3C, fig.width = 5, fig.height = 5}
+```{r figure_S5C, fig.width = 5, fig.height = 5}
 ### Just the 1h timepoint ###
@@
 ```
-```{r figure_S3D, fig.width = 5, fig.height = 5}
+```{r figure_S5D, fig.width = 5, fig.height = 5}
 ### Just the 1h timepoint ###
@@
 
-```{r read_figure_S4_data}
+```{r read_figure_S6_data}
 NHF1GeneralReadsSixFourSeqFreqAllReps20minFilteredCombined = fread(generateFilePath(
@@
 
-```{r figure_S4, fig.width = 5, fig.height = 4}
+```{r figure_S6, fig.width = 5, fig.height = 4}
 plotSequenceFrequencies(NHF1GeneralReadsSixFourSeqFreqAllReps20minFilteredCombined[Position <= 7],
@@
 
-```{r read_figure_S5_data}
+```{r read_figure_S7_data}
 NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
@@
 
-```{r figure_S5, fig.width = 6.5, fig.height = 6}
+```{r figure_S7, fig.width = 6.5, fig.height = 6}
 plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
@@
 
-```{r read_figure_S6_data}
+```{r read_figure_S8_data}
 NHF1CPDGGtoAAMismatchDataAllRepsFiltered = NHF1CPDTimepoints
@@
 
-```{r figure_S6, fig.width = 5, fig.height = 5.5}
+```{r figure_S8, fig.width = 5, fig.height = 5.5}
 plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered["1h"],

### 2023-03-04 R/MismatchComparisons.rmd
Create MismatchComparisons.rmd
This script compares statistics on mismatches and exports them to a tsv file.

---
title: "Mismatch Comparisons"
author: "Ben Morledge-Hampton"
date: "2023-02-18"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered, TG_filtered]
---

```{r setup_chunk}
library(knitr)

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
  filtering = readline("Filtering identifier (Input nothing for no filtering):")
  if (filtering == '') filtering = character()
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
  filtering = params$filtering
  if (filtering == "NONE") filtering = character()
}

if (is.na(bioinformaticsDirectory)) stop("No bioinformatics directory given.")

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data")

NHF1DataDirectory = file.path(deaminationDataDirectory, "NHF1")
NHF1MismatchesByReadDataDirectory = file.path(NHF1DataDirectory, "mismatches_by_read")

NHF1CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
```

```{r parse_mismatches_by_read_metadata}

summarizeMismatchesByReadMetadata = function(dataDirectory, cellType, lesion, timepoint, verbose = FALSE) {

  if (verbose) {
    print(paste0("Working with ", lesion, " lesions in ", cellType, " cells after ", timepoint, " of repair:"))
  }

  rawMetadata = fread(generateFilePath(
    file.path(dataDirectory,"mismatches_by_read"), dataTypeStrings$mismatchesByRead,
    ".metadata", cellType = cellType, lesion = lesion, repitition = "all_reps",
    timepoint = timepoint
  ))

  totalAlignedReads = sum(rawMetadata[V1 == "Total_Aligned_Reads:", V2])
  totalMismatches = sum(rawMetadata[V1 == "Mismatches:", V2])

  singleMismatchesByRead = fread(generateFilePath(
    file.path(dataDirectory,"sequence_and_position_analysis"), dataTypeStrings$simplifiedMismatches,
    ".tsv", cellType = cellType, lesion = lesion, repitition = "all_reps",
    timepoint = timepoint
  ))

  filteredMismatches = singleMismatchesByRead[,.N]
  singleCtoT_Mismatches = singleMismatchesByRead[Mismatch == "C>T" ,.N]

  tandemMismatchesByRead = fread(generateFilePath(
    file.path(dataDirectory,"sequence_and_position_analysis"), dataTypeStrings$simplifiedMismatches,
    ".tsv", cellType = cellType, lesion = lesion, repitition = "all_reps",
    timepoint = timepoint, includedMismatches = "CC>TT"
  ))

  CCtoTT_Mismatches = tandemMismatchesByRead[,.N]

  filteredMismatchesProportion = filteredMismatches/totalMismatches

  singleCtoT_FilteredMismatchProportion = singleCtoT_Mismatches/totalMismatches

  singleCtoT_ReadProportion = singleCtoT_Mismatches/totalAlignedReads
  CCtoTT_ReadProportion = CCtoTT_Mismatches/totalAlignedReads
  singleToTandemRatio = singleCtoT_Mismatches/CCtoTT_Mismatches

  if (verbose) {
    print(paste0("  Total Aligned Reads: ", totalAlignedReads))
    print(paste0("  Total Mismatches: ", totalMismatches))
    print(paste0("  Filtered Mismatches: ", filteredMismatches))
    print(paste0("    Proportion of mismatches retained after filtering: ", filteredMismatchesProportion))
    print(paste0("  Single C>T Mismatches: ", singleCtoT_Mismatches))
    print(paste0("    Proportion of filtered mismatches that are C>T: ", singleCtoT_FilteredMismatchProportion))
    print(paste0("    Proportion of reads with a single C>T mismatch: ", singleCtoT_ReadProportion))
    print(paste0("  Tandem CC>TT Mismatches: ", CCtoTT_Mismatches))
    print(paste0("    Proportion of reads with a tandem CC>TT mismatch: ", CCtoTT_ReadProportion))
    print(paste0("    Ratio of single C>T mismatches to tandem CC>TT mismatches: ", singleToTandemRatio))
  }

  return(data.table(Cell_Type = cellType, Lesion = lesion, Timepoint = timepoint,
                    Total_Aligned_Reads = totalAlignedReads, Total_Mismatches = totalMismatches,
                    Filtered_Mismatches = filteredMismatches, Filtered_Mismatches_Proportion = filteredMismatchesProportion,
                    Single_C_to_T_Mismatches = singleCtoT_Mismatches,
                    Single_C_to_T_Filtered_Mismatch_Proportion = singleCtoT_FilteredMismatchProportion,
                    Single_C_to_T_Read_Proportion = singleCtoT_ReadProportion, CC_to_TT_Mismatches = CCtoTT_Mismatches,
                    CC_to_TT_Read_Proportion = CCtoTT_ReadProportion, Single_To_Tandem_Ratio = singleToTandemRatio))

}
```

```{r Mismatch_Comparisons}

results = rbindlist(lapply(names(NHF1CPDTimepoints), function(timepoint) {
  summarizeMismatchesByReadMetadata(NHF1DataDirectory, "NHF1", "CPD", timepoint, TRUE)
}))

fwrite(results, file.path(NHF1DataDirectory, "mismatches_by_read", "NHF1_CPD_mismatch_metadata_summary.tsv"),
       sep = '\t')

```

### 2023-03-15 R/DeaminationSequenceAndPositionAnalysis.R
Added "ylim" parameters to some plotting functions

@@ -272,7 +272,8 @@ IQR = "IQR"
 STDEV = "Standard Deviation"
 # Plots grouped stats across timepoints and positioning type (3' vs. 5')
 plotGroupedPositionStats = function(threePrimeGroupedStats, fivePrimeGroupedStats, stat,
-                                    title = paste(stat,"Over Time"), xAxisBreaks = waiver()) {
+                                    title = paste(stat,"Over Time"), xAxisBreaks = waiver(),
+                                    yAxisTitle = NULL, ylim = NULL) {
 
   # Combine the two data sets with an extra column for the position type
   threePrimeGroupedStats = copy(threePrimeGroupedStats)
@@ -300,9 +301,11 @@ plotGroupedPositionStats = function(threePrimeGroupedStats, fivePrimeGroupedStat
     stop(paste("Unrecognized stat:",stat))
   }
 
+  if (is.null(yAxisTitle)) yAxisTitle = stat
+
   groupedStatsPlot = groupedStatsPlot + blankBackground + defaultTextScaling +
-    labs(title = title, x = "Read Length", y = stat) +
-    scale_x_continuous(breaks = xAxisBreaks)
+    labs(title = title, x = "Read Length", y = yAxisTitle) +
+    scale_x_continuous(breaks = xAxisBreaks) + coord_cartesian(ylim = ylim)
 
   if (all(aggregateData$Timepoint == "NONE")) {
     groupedStatsPlot = groupedStatsPlot + scale_color_manual(values = "black")
@@ -317,7 +320,7 @@ plotGroupedPositionStats = function(threePrimeGroupedStats, fivePrimeGroupedStat
 
 # Plots the trinucleotide context for a set of mismatches
 plotTrinucleotideContext = function(simplifiedMismatchTable, includedTypes = list(), omittedTypes = list(),
-                                    title = "Trinucleotide Context", printDipyFreq = FALSE) {
+                                    title = "Trinucleotide Context", printDipyFreq = FALSE, ylim = NULL) {
 
   if ( length(includedTypes) > 0 && length(omittedTypes) > 0) {
     stop("Included types and omitted types given simultaneously")
@@ -334,7 +337,7 @@ plotTrinucleotideContext = function(simplifiedMismatchTable, includedTypes = lis
     ggplot(trinucContextFrequencies, aes(Trinuc_Context, Freq, fill = str_sub(Trinuc_Context, 1, 1))) +
       geom_bar(stat = "identity") +
[…]

### 2023-03-15 R/CustomFigureGeneration.rmd
Create CustomFigureGeneration.rmd
This notebook serves as a way to create variations on the figures from the PaperFigureGeneration notebook. (e.g. compressing a plot for a poster).

--- 2022-12-15 R/PaperFigureGeneration.rmd
@@
 ---
-title: "Paper Figure Generation"
+title: "Custom Figure Generation"
 author: "Ben Morledge-Hampton"
@@
 opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
-               fig.path = paste0(file.path("deamination_analysis_output","paper_figures"),
+               fig.path = paste0(file.path("deamination_analysis_output","custom_figures"),
                                  .Platform$file.sep))
@@
 
-```{r read_figure_1_data}
-NHF1CPDMismatchDataAllReps = NHF1CPDTimepoints
-for (i in seq_along(NHF1CPDMismatchDataAllReps)) {
-  NHF1CPDMismatchDataAllReps[[i]] = fread(generateFilePath(
-    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
-    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
-    timepoint = names(NHF1CPDMismatchDataAllReps)[i]
-  ))
-}
-```
-
-```{r figure_1B}
-plotMismatchTypeFrequencies(NHF1CPDMismatchDataAllReps$`1h`, ylim = c(0,0.8),
-                            title = "NHF1 CPD 1h All Reps Mismatch Type Frequencies")
-```
-```{r figure_1C}
-plotTrinucleotideContext(NHF1CPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
-                         title = "NHF1 CPD 1h All Reps C>T Mismatch Trinuc Context")
-```
-```{r figure_1D}
-plotMismatchPositionFrequencies(NHF1CPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
-                                title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Frequencies")
-```
-
-```{r read_figure_2_data}
-NHF1CPDMMFreqZScoresAllReps = NHF1CPDTimepoints
-for (i in seq_along(NHF1CPDMMFreqZScoresAllReps)) {
-  NHF1CPDMMFreqZScoresAllReps[[i]] = fread(generateFilePath(
-    directory = NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
-    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
-    timepoint = names(NHF1CPDMMFreqZScoresAllReps)[i], includedMismatches = c("C>T")
-  ))
-}
-
-NHF1FivePrimeMismatchCPDNucFreqAllReps = fread(generateFilePath(
-  directory = NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
-  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
-  strandPolarity = "five_prime", anchored = TRUE
-))
-
-NHF1CPDTGGSeqFreqAllReps = NHF1CPDTimepoints
-for (i in seq_along(NHF1CPDTGGSeqFreqAllReps)) {
-  NHF1CPDTGGSeqFreqAllReps[[i]] = fread(generateFilePath(
-    directory = NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
-    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
-    timepoint = names(NHF1CPDTGGSeqFreqAllReps)[i], sequence = "TGG"
-  ))
-}
-```
-
-```{r figure_2A, fig.width = 5, fig.height = 6}
-### Just the 1h timepoint ###
-plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllReps["1h"], includedTypes = c("C>T"),
-                                         title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Freq",
-                                         yAxisLabel = "Relative C>T Frequency",
-                                         zScoreTables = NHF1CPDMMFreqZScoresAllReps)
-
-### All timepoints together ###
-# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllReps, includedTypes = c("C>T"),
-#                                          title = "NHF1 CPD All Reps C>T Mismatch Pos Freq",
-#                                          yAxisLabel = "Relative C>T Frequency",
-#                                          zScoreTables = NHF1CPDMMFreqZScoresAllReps)
-```
-```{r figure_2B, fig.width = 6.5, fig.height = 6}
-### Just the 1h timepoint ###
-plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps[Timepoint == "1h"], 
-                               title = "NHF1 CPD 1h All Reps 5' Anchored Nuc Freq",
-                               secondaryYAxisLabel = "3' Cut Site Distance",
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
-                               expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
-                               xAxisLabel = "Mismatch Relative Position")
-
-### All timepoints together ###
-# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps, 
-#                                title = "NHF1 CPD All Reps 5' Anchored Nuc Freq",
-#                                secondaryYAxisLabel = "3' Cut Site Distance",
-#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
-#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
-#                                xAxisLabel = "Mismatch Relative Position")
-```
-```{r figure_2C, fig.width = 5, fig.height = 6}
-### Just the 1h timepoint ###
-plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps$`1h`, title = "NHF1 CPD 1h All Reps General Read TGG Freq",
-                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE, querySequences = c("TGG"),
-                        expansionOffset = 10, minReadLength = 20, maxReadLength = 27,
-                        yAxisLabel = "TGG Trinucleotide Frequency", defaultColor = "Black")
-
-### All timepoints together ###
-# plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps, title = "NHF1 CPD All Reps General Read TGG Freq",
-#                         showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE, querySequences = c("TGG"),
-#                         expansionOffset = 10, minReadLength = 21, maxReadLength = 27,
-#                         yAxisLabel = "TGG Trinucleotide Frequency", defaultColor = "Black")
-```
-
-```{r read_figure_3_data}
-NHF1CPDMismatchDataAllRepsTGGFiltered = NHF1CPDTimepoints
-for (i in seq_along(NHF1CPDMismatchDataAllRepsTGGFiltered)) {
-  NHF1CPDMismatchDataAllRepsTGGFiltered[[i]] = fread(generateFilePath(
-    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
-    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1CPDMismatchDataAllRepsTGGFiltered)[i],
-    repitition = "all_reps", filtering = "TGG_filtered"
-  ))
-}
-
-arabidopsisCPDMismatchDataAllRepsFiltered = arabidopsisCPDTimepoints
-for (i in seq_along(arabidopsisCPDMismatchDataAllRepsFiltered)) {
-  arabidopsisCPDMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
-    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
-    cellType = "Arabidopsis", lesion = "CPD", timepoint = names(arabidopsisCPDMismatchDataAllRepsFiltered)[i],
-    repitition = "all_reps", filtering = "TGG_filtered"
-  ))
-}
-
-yeastCPDMismatchDataAllRepsFiltered = yeastCPDTimepoints
-for (i in seq_along(yeastCPDMismatchDataAllRepsFiltered)) {
-  yeastCPDMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
-    yeastSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
-    cellType = "yeast", lesion = "CPD", timepoint = names(yeastCPDMismatchDataAllRepsFiltered)[i],
-    repitition = "all_reps", filtering = "TGG_filtered"
-  ))
-}
-
-NHF1CPDMMFreqZScoresAllRepsTGGFiltered = NHF1CPDTimepoints
-for (i in seq_along(NHF1CPDMMFreqZScoresAllRepsTGGFiltered)) {
-  NHF1CPDMMFreqZScoresAllRepsTGGFiltered[[i]] = fread(generateFilePath(
-    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
-    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
-    timepoint = names(NHF1CPDMMFreqZScoresAllRepsTGGFiltered)[i], includedMismatches = c("C>T")
-  ))
-}
-
-arabidopsisCPDMMFreqZScoresAllRepsFiltered = arabidopsisCPDTimepoints
-for (i in seq_along(arabidopsisCPDMMFreqZScoresAllRepsFiltered)) {
-  arabidopsisCPDMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
-    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
-    cellType = "Arabidopsis", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
-    timepoint = names(arabidopsisCPDMMFreqZScoresAllRepsFiltered)[i], includedMismatches = c("C>T")
-  ))
-}
-
-yeastCPDMMFreqZScoresAllRepsFiltered = yeastCPDTimepoints
-for (i in seq_along(yeastCPDMMFreqZScoresAllRepsFiltered)) {
-  yeastCPDMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
-    yeastSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
-    cellType = "yeast", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
-    timepoint = names(yeastCPDMMFreqZScoresAllRepsFiltered)[i], includedMismatches = c("C>T")
-  ))
-}
-
+```{r read_custom_figure_3_data}
 NHF1CPDGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
@@
 
-```{r figure_3A, fig.width = 5, fig.height = 5}
-### Just the 1h timepoint ###
-plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered["1h"], includedTypes = c("C>T"),
-                                         title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
-                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGGFiltered,
-                                         yAxisLabel = "Relative C>T Frequency")
-plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["ZT2"], includedTypes = c("C>T"),
-                                         title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered C>T Mismatch Pos Freq",
-                                         zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
-                                         yAxisLabel = "Relative C>T Frequency")
-plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["20min"], includedTypes = c("C>T"),
-                                         title = "Yeast CPD 20min All Reps TGG-Filtered C>T Mismatch Pos Freq",
-                                         zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
-                                         yAxisLabel = "Relative C>T Frequency")
-
-### All timepoints together ###
-# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered, includedTypes = c("C>T"),
-#                                          title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
-#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGGFiltered,
-#                                          yAxisLabel = "Relative C>T Frequency")
-# plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
-#                                          title = "Arabidopsis CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
-#                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
-#                                          yAxisLabel = "Relative C>T Frequency")
-# plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
-#                                          title = "Yeast CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
-#                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
-#                                          yAxisLabel = "Relative C>T Frequency")
-```
-```{r figure_3B, fig.width = 5, fig.height = 5}
-### Just the 1h timepoint ###
-plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered["1h"], includedTypes = c("C>T"),
-                                         title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
-                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGGFiltered,
-                                         posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
-plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["ZT2"], includedTypes = c("C>T"),
-                                         title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered C>T Mismatch Pos Freq",
-                                         zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
-                                         posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
-plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["20min"], includedTypes = c("C>T"),
-                                         title = "Yeast CPD 20min All Reps TGG-Filtered C>T Mismatch Pos Freq",
-                                         zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
-                                         posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
-
-### All timepoints together ###
-# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered, includedTypes = c("C>T"),
-#                                          title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
-#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGGFiltered,
-#                                          posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
-# plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
-#                                          title = "Arabidopsis CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
-#                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
-#                                          posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
-# plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
-#                                          title = "Yeast CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
-#                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
-#                                          posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
-```
-```{r figure_3C, fig.width = 7.5, fig.height = 5}
+```{r figure_3C, fig.width = 8, fig.height = 3}
 ### Just the 1h timepoint ###
@@
                          POS_DIFF, title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
-                         xAxisBreaks = c(22:30))
+                         xAxisBreaks = c(22:30), yAxisTitle = "Pos Diff")
 
@@
                          POS_DIFF, title = "Arabidopsis CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
-                         xAxisBreaks = c(24:30))
+                           xAxisBreaks = c(24:30), yAxisTitle = "Pos Diff")
 
@@
                          POS_DIFF, title = "Yeast CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
-                         xAxisBreaks = c(22:25))
+                         xAxisBreaks = c(22:25), yAxisTitle = "Pos Diff")
 
@@
 ```
-
-```{r read_figure_4_data}
-NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
-  NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
-  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
-  strandPolarity = "three_prime", anchored = TRUE, filtering = "TGG_filtered"
-))
-NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = NHF1CPDTimepoints
-for (i in seq_along(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
-  NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
-    NHF1ExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
-    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
-    timepoint = names(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
-    strandPolarity = "three_prime", anchored = TRUE, sequence = "HYV", filtering = "TGG_filtered"
-  ))
-}
-
-NHF1GeneralReadsCPDNucFreqAllReps1hFilteredCombined = fread(generateFilePath(
-  NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
-  cellType = "NHF1", lesion = "CPD", repitition = "all_reps", timepoint = "1h",
-  filtering = "TGG_filtered", additionalInformation = "combined_read_lengths"
-))
-NHF1GeneralReadsCPDSeqFreqAllReps1hFilteredCombined = fread(generateFilePath(
-  NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
-  cellType = "NHF1", lesion = "CPD", timepoint = "1h", repitition = "all_reps",
-  sequence = "HYV", filtering = "TGG_filtered", additionalInformation = "combined_read_lengths"
-))
-arabidopsisGeneralReadsCPDSeqFreqAllRepsZT2FilteredCombined = fread(generateFilePath(
-  arabidopsisGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
-  cellType = "Arabidopsis", lesion = "CPD", timepoint = "ZT2",
-  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered",
-  additionalInformation = "combined_read_lengths"
-))
-yeastGeneralReadsCPDSeqFreqAllReps20MinFilteredCombined = fread(generateFilePath(
-  yeastGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
-  cellType = "yeast", lesion = "CPD", timepoint = "20min",
-  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered",
-  additionalInformation = "combined_read_lengths"
-))
-EColiGeneralReadsCPDSeqFreqAllReps5MinFilteredCombined = fread(generateFilePath(
-  EColiGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
-  cellType = "E_coli_WT", lesion = "CPD", timepoint = "5min",
-  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered",
-  additionalInformation = "combined_read_lengths"
-))
-```
-
-```{r figure_4A, fig.width = 6.5, fig.height = 6}
-plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
-                               title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored Nuc Freq",
-                               secondaryYAxisLabel = "5' Cut Site Distance",
-                               posType = FIVE_PRIME, showFivePrimeCutSite = TRUE,
-                               expansionOffset = 10, minReadLength = 19, maxReadLength = 25,
-                               xAxisLabel = "Mismatch Relative Position")
-```
-```{r figure_4B, fig.width = 5, fig.height = 6}
-# ### Just the 1h timepoint (asterisks) ###
-# plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
-#                         title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored HYV Freq",
-#                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
-#                         showFivePrimeCutSite = TRUE, querySequences = c("333"),
-#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 6,
-#                         endBasedCheckPositions = -9, xAxisLabel = "Mismatch Relative Position",
-#                         significanceAsteriskBreakpoints = c(1e-3, 1e-10, 1e-20))
-
-## Just the 1h timepoint (full p-values) ###
-plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
-                        title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored HYV Freq",
-                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "HYV Frequency",
-                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
-                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 6,
-                        endBasedCheckPositions = -9, displayPValue = FALSE, xAxisLabel = "Mismatch Relative Position")
-
-### All timepoints together ###
-# plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
-#                         title = "NHF1 CPD All Reps TGG-Filtered 3' Anchored YR Freq",
-#                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
-#                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
-#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
-#                         endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
-```
-```{r figure_4C, fig.width = 6.5, fig.height = 4.75}
-plotNucFreqVsReadLengthBarPlot(NHF1GeneralReadsCPDNucFreqAllReps1hFilteredCombined[Position <= 7], 
-                               title = "NHF1 CPD 1h All Reps TGG-Filtered Nuc Freq",
-                               secondaryYAxisLabel = "Read Length", ylim = c(0,1),
-                               posType = FIVE_PRIME, showFivePrimeCutSite = TRUE,
-                               expansionOffset = 10,
-                               xAxisLabel = "5' Relative Position")
-```
-```{r figure_4D, fig.width = 5, fig.height = 4}
-plotSequenceFrequencies(NHF1GeneralReadsCPDSeqFreqAllReps1hFilteredCombined[Position <= 7],
-                        title = "NHF1 CPD 1h All Reps TGG-Filtered General Reads HYV Freq",
-                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
-                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
-                        expansionOffset = 10, backgroundPositions = -9:-4,
-                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
-                        xAxisBreaks = c(-8, 0, 8), ylimMax = 0.6, ylimMaxModifier = 1)
-```
-```{r figure_4E, fig.width = 5, fig.height = 4}
-plotSequenceFrequencies(arabidopsisGeneralReadsCPDSeqFreqAllRepsZT2FilteredCombined[Position <= 7],
-                        title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered General Reads HYV Freq",
-                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
-                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
-                        expansionOffset = 10, backgroundPositions = -9:-4,
-                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
-                        xAxisBreaks = c(-8, 0, 8), ylimMax = 0.6, ylimMaxModifier = 1)
-```
-```{r figure_4F, fig.width = 5, fig.height = 4}
-plotSequenceFrequencies(yeastGeneralReadsCPDSeqFreqAllReps20MinFilteredCombined[Position <= 7],
-                        title = "Yeast CPD 20min All Reps TGG-Filtered General Reads HYV Freq",
-                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
-                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
-                        expansionOffset = 10, backgroundPositions = -9:-4,
-                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
-                        xAxisBreaks = c(-8, 0, 8), ylimMax = 0.6, ylimMaxModifier = 1)
-```
-```{r figure_4G, fig.width = 5, fig.height = 4}
-plotSequenceFrequencies(EColiGeneralReadsCPDSeqFreqAllReps5MinFilteredCombined[Position <= 7],
-                        title = "E. coli CPD 5min All Reps TGG-Filtered General Reads HYV Freq",
-                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
-                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
-                        expansionOffset = 10, xAxisLabel = "5' Relative Position",
-                        xAxisBreaks = c(-8, 0, 8), ylimMax = 0.6, ylimMaxModifier = 1)
-```
-
-```{r read_figure_5_data}
-# Note: This file was created manually by combining/modifying a couple different files counting tandem mismatches.
-NHF1TandemMismatchCountsComparisonAllReps = fread(generateFilePath(
-  NHF1MismatchesByReadDataDirectory, dataTypeStrings$tandemMismatchCountsComparison, ".tsv",
-  cellType = "NHF1", repitition = "all_reps"
-))
-```
-
-```{r figure_5B, fig.width = 8, fig.height = 5}
-NHF1TandemMismatchCountsComparisonAllReps = NHF1TandemMismatchCountsComparisonAllReps[
-  Lesion == "CPD" & Timepoint == "1h"
-]
-print(
-    ggplot(NHF1TandemMismatchCountsComparisonAllReps, aes(Mismatch_Type, Tandem_Mismatches_Count, fill = Search_Method)) +
-      geom_bar(stat = "identity", position = "dodge") +
-      labs(title = "NHF1 CPD 1h All Reps Tandem Mismatch Counts", x = "Mismatch Type", y = "Tandem Mismatch Count") +
-      geom_text(aes(label=Tandem_Mismatches_Count), position = position_dodge(width = 0.9), vjust = -0.25, size = 5) +
-      blankBackground + defaultTextScaling + scale_fill_brewer(palette = "Set1") + coord_cartesian(ylim = c(0,200000))
-  )
-```
-
-```{r read_figure_6_data}
-NHF1CPDCCtoTTMismatchDataAllRepsFiltered = NHF1CPDTimepoints
-for (i in seq_along(NHF1CPDCCtoTTMismatchDataAllRepsFiltered)) {
-  NHF1CPDCCtoTTMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
-    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
-    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
-    filtering = "TGG_filtered", includedMismatches = "CC>TT",
-    timepoint = names(NHF1CPDCCtoTTMismatchDataAllRepsFiltered)[i]
-  ))
-}
-
-NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered = NHF1CPDTimepoints
-for (i in seq_along(NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered)) {
-  NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
-    directory = NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
-    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
-    filtering = "TGG_filtered", includedMismatches = "CC>TT",
-    timepoint = names(NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered)[i]
-  ))
-}
-
-NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllReps1hFiltered = fread(generateFilePath(
-    NHF1ExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv", timepoint = "1h",
-    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", includedMismatches = "CC>TT",
-    strandPolarity = "three_prime", anchored = TRUE, sequence = "HYV", filtering = "TGG_filtered",
-))
-
-NHF1CPDCCToTTGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
-for (i in seq_along(NHF1CPDCCToTTGroupedStatsAllRepsFiltered)) {
-  NHF1CPDCCToTTGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
-    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
-    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
-    strandPolarity = names(NHF1CPDCCToTTGroupedStatsAllRepsFiltered)[i], includedMismatches = "CC>TT"
-  ))
-}
-
-arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
-for (i in seq_along(arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered)) {
-  arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
-    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
-    cellType = "Arabidopsis", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
-    strandPolarity = names(arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered)[i], includedMismatches = "CC>TT"
-  ))
-}
-
-yeastCPDCCToTTGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
-for (i in seq_along(yeastCPDCCToTTGroupedStatsAllRepsFiltered)) {
-  yeastCPDCCToTTGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
-    yeastSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
-    cellType = "yeast", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
-    strandPolarity = names(yeastCPDCCToTTGroupedStatsAllRepsFiltered)[i], includedMismatches = "CC>TT"
-  ))
-}
-```
-
-```{r figure_6A, fig.width = 5, fig.height = 5.5}
-### Just the 1h timepoint ###
-plotPositionAcrossTimepointAndReadLength(NHF1CPDCCtoTTMismatchDataAllRepsFiltered["1h"],
-                                         title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT Mismatch Pos Freq",
-                                         zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered,
-                                         yAxisLabel = "Relative CC>TT Frequency")
-
-### All timepoints together ###
-# plotPositionAcrossTimepointAndReadLength(NHF1CPDCCtoTTMismatchDataAllRepsFiltered,
-#                                          title = "NHF1 CPD All Reps TGG-Filtered CC>TT Mismatch Pos Freq",
-#                                          zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered,
-#                                          yAxisLabel = "Relative CC>TT Frequency")
-```
-```{r figure_6B, fig.width = 5, fig.height = 5}
-plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllReps1hFiltered,
-                        title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT 3' Anchored HYV Freq",
-                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "HYV Frequency",
-                        showFivePrimeCutSite = TRUE, querySequences = c("333"),
-                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 6,
-                        endBasedCheckPositions = -9, displayPValue = FALSE, xAxisLabel = "Mismatch Relative Position",
-                        xAxisOffset = 1)
-```
-```{r figure_6C, fig.width = 7.5, fig.height = 5}
-### Just the 1h timepoint ###
-plotGroupedPositionStats(NHF1CPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
-                         NHF1CPDCCToTTGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
-                         POS_DIFF, title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
-                         xAxisBreaks = c(22:30))
-
-### All timepoints together ###
-# plotGroupedPositionStats(NHF1CPDCCToTTGroupedStatsAllRepsFiltered$three_prime,
-#                          NHF1CPDCCToTTGroupedStatsAllRepsFiltered$five_prime,
-#                          POS_DIFF, title = "NHF1 CPD All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
-#                          xAxisBreaks = c(22:30))
-```
-```{r figure_6D, fig.width = 7.5, fig.height = 5}
-### Just the 1h timepoint ###
-plotGroupedPositionStats(arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "ZT2"],
-                         arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered$five_prime[Timepoint == "ZT2"],
-                         POS_DIFF, title = "Arabidopsis CPD 1h All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
-                         xAxisBreaks = c(24:30))
-
-### All timepoints together ###
-# plotGroupedPositionStats(arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered$three_prime,
-#                          arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered$five_prime,
-#                          POS_DIFF, title = "Arabidopsis CPD All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
-#                          xAxisBreaks = c(24:30))
-```
-```{r figure_6E, fig.width = 7.5, fig.height = 5}
-### Just the 1h timepoint ###
-plotGroupedPositionStats(yeastCPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "20min"],
-                         yeastCPDCCToTTGroupedStatsAllRepsFiltered$five_prime[Timepoint == "20min"],
-                         POS_DIFF, title = "Yeast CPD 1h All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
-                         xAxisBreaks = c(22:25))
-
-### All timepoints together ###
-# plotGroupedPositionStats(yeastCPDCCToTTGroupedStatsAllRepsFiltered$three_prime,
-#                          yeastCPDCCToTTGroupedStatsAllRepsFiltered$five_prime,
-#                          POS_DIFF, title = "Yeast CPD All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
-#                          xAxisBreaks = c(22:25))
-```
-
-```{r read_figure_S1_data}
-NHF1SixFourMismatchDataAllReps = NHF1SixFourTimepoints
-for (i in seq_along(NHF1SixFourMismatchDataAllReps)) {
-  NHF1SixFourMismatchDataAllReps[[i]] = fread(generateFilePath(
-    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
-    cellType = "NHF1", lesion = "6-4", repitition = "all_reps",
-    timepoint = names(NHF1SixFourMismatchDataAllReps)[i]
-  ))
-}
-
-GM12878CisplatinMismatchDataAllReps = GM12878CisplatinTimepoints
-for (i in seq_along(GM12878CisplatinMismatchDataAllReps)) {
-  GM12878CisplatinMismatchDataAllReps[[i]] = fread(generateFilePath(
-    GM12878SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
-    cellType = "GM12878", lesion = "cisplatin", repitition = "all_reps",
-    timepoint = names(GM12878CisplatinMismatchDataAllReps)[i]
-  ))
-}
-```
-
-```{r figure_S1}
-plotMismatchTypeFrequencies(NHF1SixFourMismatchDataAllReps$`20min`,
-                            title = "NHF1 6-4 20min All Reps Mismatch Type Frequencies")
-
-plotTrinucleotideContext(NHF1SixFourMismatchDataAllReps$`20min`, includedTypes = c("C>T"),
-                         title = "NHF1 6-4 20min All Reps Mismatch Trinuc Context")
-
-plotMismatchPositionFrequencies(NHF1SixFourMismatchDataAllReps$`20min`, includedTypes = c("C>T"),
-                                title = "NHF1 6-4 20min All Reps Mismatch Pos Frequencies")
-
-plotMismatchTypeFrequencies(GM12878CisplatinMismatchDataAllReps$`90min`,
-                            title = "GM12878 Cisplatin 90min All Reps Mismatch Type Frequencies")
-
-plotTrinucleotideContext(GM12878CisplatinMismatchDataAllReps$`90min`, includedTypes = c("C>T"),
-                         title = "GM12878 Cisplatin 90min All Reps Mismatch Trinuc Context")
-
-plotMismatchPositionFrequencies(GM12878CisplatinMismatchDataAllReps$`90min`, includedTypes = c("C>T"),
-                                title = "GM12878 Cisplatin 90min All Reps Mismatch Pos Frequencies")
-
-plotMismatchPositionFrequencies(NHF1CPDMismatchDataAllReps$`1h`, omittedTypes = c("C>T"),
-                                title = "NHF1 CPD 1h All Reps !C>T Mismatch Pos Frequencies")
-```
-
-```{r read_figure_S2_data}
-arabidopsisCPDMismatchDataAllReps = arabidopsisCPDTimepoints
-for (i in seq_along(arabidopsisCPDMismatchDataAllReps)) {
-  arabidopsisCPDMismatchDataAllReps[[i]] = fread(generateFilePath(
-    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
-    cellType = "Arabidopsis", lesion = "CPD", repitition = "all_reps",
-    timepoint = names(arabidopsisCPDMismatchDataAllReps)[i]
-  ))
-}
-
-yeastCPDMismatchDataAllReps = yeastCPDTimepoints
-for (i in seq_along(yeastCPDMismatchDataAllReps)) {
-  yeastCPDMismatchDataAllReps[[i]] = fread(generateFilePath(
-    yeastSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
-    cellType = "yeast", lesion = "CPD", repitition = "all_reps",
-    timepoint = names(yeastCPDMismatchDataAllReps)[i]
-  ))
-}
-
-CSBCPDMismatchDataAllReps = CSBCPDTimepoints
-for (i in seq_along(CSBCPDMismatchDataAllReps)) {
-  CSBCPDMismatchDataAllReps[[i]] = fread(generateFilePath(
-    CSBSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
-    cellType = "CS-B", lesion = "CPD", repitition = "all_reps",
-    timepoint = names(CSBCPDMismatchDataAllReps)[i]
-  ))
-}
-
-XPCCPDMismatchDataAllReps = XPCCPDTimepoints
-for (i in seq_along(XPCCPDMismatchDataAllReps)) {
-  XPCCPDMismatchDataAllReps[[i]] = fread(generateFilePath(
-    XPCSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
-    cellType = "XP-C", lesion = "CPD", repitition = "all_reps",
-    timepoint = names(XPCCPDMismatchDataAllReps)[i]
-  ))
-}
-```
-
-```{r figure_S2}
-plotMismatchTypeFrequencies(arabidopsisCPDMismatchDataAllReps$ZT2,
-                            title = "Arabidopsis CPD ZT2 All Reps Mismatch Type Frequencies")
-
-plotTrinucleotideContext(arabidopsisCPDMismatchDataAllReps$ZT2, includedTypes = c("C>T"),
-                         title = "Arabidopsis CPD ZT2 All Reps Mismatch Trinuc Context")
-
-plotMismatchPositionFrequencies(arabidopsisCPDMismatchDataAllReps$ZT2, includedTypes = c("C>T"),
-                                title = "Arabidopsis CPD ZT2 All Reps Mismatch Pos Frequencies")
-
-plotMismatchTypeFrequencies(yeastCPDMismatchDataAllReps$`20min`,
-                            title = "Yeast CPD 20min All Reps Mismatch Type Frequencies")
-
-plotTrinucleotideContext(yeastCPDMismatchDataAllReps$`20min`, includedTypes = c("C>T"),
-                         title = "Yeast CPD 20min All Reps Mismatch Trinuc Context")
-
-plotMismatchPositionFrequencies(yeastCPDMismatchDataAllReps$`20min`, includedTypes = c("C>T"),
-                                title = "Yeast CPD 20min All Reps Mismatch Pos Frequencies")
-
-plotMismatchTypeFrequencies(CSBCPDMismatchDataAllReps$`1h`,
-                            title = "CS-B CPD 1h All Reps Mismatch Type Frequencies")
-
-plotTrinucleotideContext(CSBCPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
-                         title = "CS-B CPD 1h All Reps Mismatch Trinuc Context")
-
-plotMismatchPositionFrequencies(CSBCPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
-                                title = "CS-B CPD 1h All Reps Mismatch Pos Frequencies",
-                                ylim = c(0,0.25))
-
-plotMismatchTypeFrequencies(XPCCPDMismatchDataAllReps$`1h`,
-                            title = "XP-C CPD 1h All Reps Mismatch Type Frequencies")
-
-plotTrinucleotideContext(XPCCPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
-                         title = "XP-C CPD 1h All Reps Mismatch Trinuc Context")
-
-plotMismatchPositionFrequencies(XPCCPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
-                                title = "XP-C CPD 1h All Reps Mismatch Pos Frequencies",
-                                ylim = c(0,0.25))
-```
-
-```{r read_figure_S3_data}
-NHF1FivePrimeMismatchCPDNucFreqAllRepsTGGFiltered = fread(generateFilePath(
-  NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
-  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
-  strandPolarity = "five_prime", anchored = TRUE, filtering = "TGG_filtered"
-))
-NHF1FivePrimeMismatchCPDNucFreqAllRepsTGFiltered = fread(generateFilePath(
-  NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
-  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
-  strandPolarity = "five_prime", anchored = TRUE, filtering = "TG_filtered"
-))
-
-NHF1CPDMismatchDataAllRepsTGFiltered = NHF1CPDTimepoints
-for (i in seq_along(NHF1CPDMismatchDataAllRepsTGFiltered)) {
-  NHF1CPDMismatchDataAllRepsTGFiltered[[i]] = fread(generateFilePath(
-    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
-    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1CPDMismatchDataAllRepsTGFiltered)[i],
-    repitition = "all_reps", filtering = "TG_filtered"
-  ))
-}
-
-NHF1CPDMMFreqZScoresAllRepsTGFiltered = NHF1CPDTimepoints
-for (i in seq_along(NHF1CPDMMFreqZScoresAllRepsTGFiltered)) {
-  NHF1CPDMMFreqZScoresAllRepsTGFiltered[[i]] = fread(generateFilePath(
-    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
-    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", filtering = "TG_filtered",
-    timepoint = names(NHF1CPDMMFreqZScoresAllRepsTGFiltered)[i], includedMismatches = c("C>T")
-  ))
-}
-```
-
-```{r figure_S3A, fig.width = 6.5, fig.height = 6}
-### Just the 1h timepoint ###
-plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsTGGFiltered[Timepoint == "1h"], 
-                               title = "NHF1 CPD 1h All Reps TGG-Filtered 5' Anchored Nuc Freq",
-                               secondaryYAxisLabel = "3' Cut Site Distance",
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
-                               expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
-                               xAxisLabel = "Mismatch Relative Position")
-
-### All timepoints together ###
-# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsTGGFiltered, 
-#                                title = "NHF1 CPD All Reps TGG-Filtered 5' Anchored Nuc Freq",
-#                                secondaryYAxisLabel = "3' Cut Site Distance",
-#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
-#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
-#                                xAxisLabel = "Mismatch Relative Position")
-```
-```{r figure_S3B, fig.width = 6.5, fig.height = 6}
-### Just the 1h timepoint ###
-plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsTGFiltered[Timepoint == "1h"], 
-                               title = "NHF1 CPD 1h All Reps TG-Filtered 5' Anchored Nuc Freq",
-                               secondaryYAxisLabel = "3' Cut Site Distance",
-                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
-                               expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
-                               xAxisLabel = "Mismatch Relative Position")
-
-### All timepoints together ###
-# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsTGFiltered, 
-#                                title = "NHF1 CPD All Reps TG-Filtered 5' Anchored Nuc Freq",
-#                                secondaryYAxisLabel = "3' Cut Site Distance",
-#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
-#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
-#                                xAxisLabel = "Mismatch Relative Position")
-```
-```{r figure_S3D, fig.width = 5, fig.height = 5}
-### Just the 1h timepoint ###
-plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGFiltered["1h"], includedTypes = c("C>T"),
-                                         title = "NHF1 CPD 1h All Reps TG-Filtered C>T Mismatch Pos Freq",
-                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGFiltered,
-                                         posType = THREE_PRIME, yAxisLabel = "Relative C>T Frequency")
-
-### All timepoints together ###
-# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGFiltered, includedTypes = c("C>T"),
-#                                          title = "NHF1 CPD All Reps TG-Filtered C>T Mismatch Pos Freq",
-#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGFiltered,
-#                                          posType = THREE_PRIME, yAxisLabel = "Relative C>T Frequency")
-```
-
-```{r read_figure_S4_data}
-NHF1GeneralReadsSixFourSeqFreqAllReps20minFilteredCombined = fread(generateFilePath(
-  NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
-  cellType = "NHF1", lesion = "6-4", timepoint = "20min",
-  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered",
-  additionalInformation = "combined_read_lengths"
-))
-GM12878GeneralReadsCisplatinSeqFreqRep1_90minFilteredCombined = fread(generateFilePath(
-  GM12878GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
-  cellType = "GM12878", lesion = "cisplatin", timepoint = "90min",
-  repitition = "rep1", sequence = "HYV", filtering = "TGG_filtered",
-  additionalInformation = "combined_read_lengths"
-))
-```
-
-```{r figure_S4, fig.width = 5, fig.height = 4}
-plotSequenceFrequencies(NHF1GeneralReadsSixFourSeqFreqAllReps20minFilteredCombined[Position <= 7],
-                        title = "NHF1 6-4 20min All Reps TGG-Filtered General Reads HYV Freq",
-                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
-                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisBreaks = c(-8, 0, 8),
-                        expansionOffset = 10, minReadLength = 23, maxReadLength = 29, backgroundPositions = -9:-4,
-                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
-                        xAxisOffset = 1, ylimMax = 0.6, ylimMaxModifier = 1)
-plotSequenceFrequencies(GM12878GeneralReadsCisplatinSeqFreqRep1_90minFilteredCombined[Position <= 7],
-                        title = "GM12878 cisplatin 90min Rep1 TGG-Filtered General Reads HYV Freq",
-                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
-                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisBreaks = c(-8, 0, 8),
-                        expansionOffset = 10, minReadLength = 23, maxReadLength = 29, backgroundPositions = -9:-4,
-                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
-                        xAxisOffset = 1, ylimMax = 0.6, ylimMaxModifier = 1)
-```
-
-```{r read_figure_S5_data}
-NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
-  NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
-  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
-  strandPolarity = "five_prime", anchored = TRUE, filtering = "TGG_filtered"
-))
-arabidopsisFivePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
-  arabidopsisExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
-  cellType = "Arabidopsis", lesion = "CPD", repitition = "all_reps",
-  strandPolarity = "five_prime", anchored = TRUE, filtering = "TGG_filtered"
-))
-yeastFivePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
-  yeastExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
-  cellType = "yeast", lesion = "CPD", repitition = "all_reps",
-  strandPolarity = "five_prime", anchored = TRUE, filtering = "TGG_filtered"
-))
-```
-
-```{r figure_S5, fig.width = 6.5, fig.height = 6}
-plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
-                               title = "NHF1 CPD 1h All Reps TGG-Filtered 5' Anchored Nuc Freq",
-                               secondaryYAxisLabel = "3' Cut Site Distance",
-                               posType = THREE_PRIME, showThreePrimeCutSite = TRUE,
-                               expansionOffset = 10, minReadLength = 6, maxReadLength = 12,
-                               xAxisLabel = "Mismatch Relative Position")
-plotNucFreqVsReadLengthBarPlot(arabidopsisFivePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "ZT2"], 
-                               title = "Arabidopsis CPD 1h All Reps TGG-Filtered 5' Anchored Nuc Freq",
-                               secondaryYAxisLabel = "3' Cut Site Distance",
-                               posType = THREE_PRIME, showThreePrimeCutSite = TRUE,
-                               expansionOffset = 10, minReadLength = 6, maxReadLength = 12,
-                               xAxisLabel = "Mismatch Relative Position")
-plotNucFreqVsReadLengthBarPlot(yeastFivePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "20min"], 
-                               title = "Yeast CPD 1h All Reps TGG-Filtered 5' Anchored Nuc Freq",
-                               secondaryYAxisLabel = "3' Cut Site Distance",
-                               posType = THREE_PRIME, showThreePrimeCutSite = TRUE,
-                               expansionOffset = 10, minReadLength = 6, maxReadLength = 12,
-                               xAxisLabel = "Mismatch Relative Position")
-```
-
-```{r read_figure_S6_data}
-NHF1CPDGGtoAAMismatchDataAllRepsFiltered = NHF1CPDTimepoints
-for (i in seq_along(NHF1CPDGGtoAAMismatchDataAllRepsFiltered)) {
-  NHF1CPDGGtoAAMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
-    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
-    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
-    filtering = "TGG_filtered", includedMismatches = "GG>AA",
-    timepoint = names(NHF1CPDGGtoAAMismatchDataAllRepsFiltered)[i]
-  ))
-}
-
-NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered = NHF1CPDTimepoints
-for (i in seq_along(NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered)) {
-  NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
-    directory = NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
-    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
-    filtering = "TGG_filtered", includedMismatches = "GG>AA",
-    timepoint = names(NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered)[i]
-  ))
-}
-```
-
-```{r figure_S6, fig.width = 5, fig.height = 5.5}
-plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered["1h"],
-                                         title = "NHF1 CPD All Reps GG>AA Mismatch Pos Freq",
-                                         zScoreTables = NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered,
-                                         yAxisLabel = "Relative GG>AA Frequency")
-```

### 2023-04-05 R/PaperFigureGeneration.rmd
A whole bunch of figure changes!
I definitely should have written these commit notes earlier... I think some of these changes pertain to changes in y-axis labels to fully encompass data points. A few figures might have been added, split, shuffled around, etc. I don't think there were any major changes beyond those.

@@
                                 title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Frequencies",
-                                xAxisBreaks = c(-1,-10,-20,-30))
+                                xAxisBreaks = c(-1,-10,-20,-30), ylim = c(0,0.25))
 ```
@@
 ```{r figure_3A, fig.width = 5, fig.height = 5}
-### Just the 1h timepoint ###
 plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered["1h"], includedTypes = c("C>T"),
@@
                                          yAxisLabel = "Relative C>T Frequency", xAxisBreaks = c(-1,-10,-20,-30))
+```
+```{r figure_3B, fig.width = 5, fig.height = 5}
 plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["ZT2"], includedTypes = c("C>T"),
@@
                                          yAxisLabel = "Relative C>T Frequency", xAxisBreaks = c(-1,-10,-20,-30))
-plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["20min"], includedTypes = c("C>T"),
-                                         title = "Yeast CPD 20min All Reps TGG-Filtered C>T Mismatch Pos Freq",
-                                         zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
-                                         yAxisLabel = "Relative C>T Frequency", xAxisBreaks = c(-1,-10,-20,-30))
-
-### All timepoints together ###
-# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered, includedTypes = c("C>T"),
-#                                          title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
-#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGGFiltered,
-#                                          yAxisLabel = "Relative C>T Frequency")
-# plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
-#                                          title = "Arabidopsis CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
-#                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
-#                                          yAxisLabel = "Relative C>T Frequency")
-# plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
-#                                          title = "Yeast CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
-#                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
-#                                          yAxisLabel = "Relative C>T Frequency")
 ```
-```{r figure_3B, fig.width = 5, fig.height = 5}
-### Just the 1h timepoint ###
+```{r figure_3C, fig.width = 5, fig.height = 5}
 plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered["1h"], includedTypes = c("C>T"),
@@
                                          xAxisBreaks = c(1,10,20,30))
+```
+```{r figure_3D, fig.width = 5, fig.height = 5}
 plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["ZT2"], includedTypes = c("C>T"),
@@
                                          xAxisBreaks = c(1,10,20,30))
-plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["20min"], includedTypes = c("C>T"),
-                                         title = "Yeast CPD 20min All Reps TGG-Filtered C>T Mismatch Pos Freq",
-                                         zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
-                                         posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency",
-                                         xAxisBreaks = c(1,10,20,30))
-
-### All timepoints together ###
-# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered, includedTypes = c("C>T"),
-#                                          title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
-#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGGFiltered,
-#                                          posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
-# plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
-#                                          title = "Arabidopsis CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
-#                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
-#                                          posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
-# plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
-#                                          title = "Yeast CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
-#                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
-#                                          posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
 ```
-```{r figure_3C, fig.width = 7.5, fig.height = 5}
-### Just the 1h timepoint ###
+```{r figure_3E, fig.width = 7.5, fig.height = 5}
 plotGroupedPositionStats(NHF1CPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
@@
                          POS_DIFF, title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
-                         xAxisBreaks = c(22:30))
-
+                         xAxisBreaks = c(22:30), ylim = c(0,5))
+```
+```{r figure_3F, fig.width = 7.5, fig.height = 5}
 plotGroupedPositionStats(arabidopsisCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "ZT2"],
@@
                          POS_DIFF, title = "Arabidopsis CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
-                         xAxisBreaks = c(24:30))
-
-plotGroupedPositionStats(yeastCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "20min"],
-                         yeastCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "20min"],
-                         POS_DIFF, title = "Yeast CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
-                         xAxisBreaks = c(22:25))
-
-### All timepoints together ###
-# plotGroupedPositionStats(NHF1CPDGroupedStatsAllRepsFiltered$three_prime,
-#                          NHF1CPDGroupedStatsAllRepsFiltered$five_prime,
-#                          POS_DIFF, title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Diff",
-#                          xAxisBreaks = c(22:30))
-# 
-# plotGroupedPositionStats(arabidopsisCPDGroupedStatsAllRepsFiltered$three_prime,
-#                          arabidopsisCPDGroupedStatsAllRepsFiltered$five_prime,
-#                          POS_DIFF, title = "Arabidopsis CPD All Reps TGG-Filtered C>T Mismatch Pos Diff",
-#                          xAxisBreaks = c(24:30))
-# 
-# plotGroupedPositionStats(yeastCPDGroupedStatsAllRepsFiltered$three_prime,
-#                          yeastCPDGroupedStatsAllRepsFiltered$five_prime,
-#                          POS_DIFF, title = "Yeast CPD All Reps TGG-Filtered C>T Mismatch Pos Diff",
-#                          xAxisBreaks = c(22:25))
+                         xAxisBreaks = c(24:30), ylim = c(0,5))
 ```
@@
                          POS_DIFF, title = "Arabidopsis CPD 1h All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
-                         xAxisBreaks = c(24:30))
+                         xAxisBreaks = c(24:30), ylim = c(0,5))
 
@@
                                 title = "NHF1 CPD 1h All Reps !C>T Mismatch Pos Frequencies",
-                                xAxisBreaks = c(-1,-10,-20,-30))
+                                xAxisBreaks = c(-1,-10,-20,-30), ylim = c(0,0.05))
 ```
 
-```{r read_figure_S2_data}
+```{r figure_S2}
+plotMismatchTypeFrequencies(NHF1CPDMismatchDataAllReps$`8h`, ylim = c(0,0.6),
+                            title = "NHF1 CPD 8h All Reps Mismatch Type Frequencies")
+
+plotMismatchTypeFrequencies(NHF1CPDMismatchDataAllReps$`24h`, ylim = c(0,0.5),
+                            title = "NHF1 CPD 24h All Reps Mismatch Type Frequencies")
+
+plotMismatchTypeFrequencies(NHF1CPDMismatchDataAllReps$`48h`, ylim = c(0,0.4),
+                            title = "NHF1 CPD 48h All Reps Mismatch Type Frequencies")
+
+print("NHF1 CPD81h all reps C>T mismatch dipyrimidine context frequency:")
+plotTrinucleotideContext(NHF1CPDMismatchDataAllReps$`8h`, includedTypes = c("C>T"),
+                         title = "NHF1 CPD 8h All Reps C>T Mismatch Trinuc Context",
+                         printDipyFreq = TRUE, ylim = c(0,0.4))
+
+print("NHF1 CPD 24h all reps C>T mismatch dipyrimidine context frequency:")
+plotTrinucleotideContext(NHF1CPDMismatchDataAllReps$`24h`, includedTypes = c("C>T"),
+                         title = "NHF1 CPD 24h All Reps C>T Mismatch Trinuc Context",
+                         printDipyFreq = TRUE, ylim = c(0,0.25))
+
+print("NHF1 CPD 48h all reps C>T mismatch dipyrimidine context frequency:")
+plotTrinucleotideContext(NHF1CPDMismatchDataAllReps$`48h`, includedTypes = c("C>T"),
+                         title = "NHF1 CPD 48h All Reps C>T Mismatch Trinuc Context",
+                         printDipyFreq = TRUE)
+
+plotMismatchPositionFrequencies(NHF1CPDMismatchDataAllReps$`8h`, includedTypes = c("C>T"),
+                                title = "NHF1 CPD 8h All Reps C>T Mismatch Pos Frequencies",
+                                xAxisBreaks = c(-1,-10,-20,-30), ylim = c(0,0.2))
+
+plotMismatchPositionFrequencies(NHF1CPDMismatchDataAllReps$`24h`, includedTypes = c("C>T"),
+                                title = "NHF1 CPD 24h All Reps C>T Mismatch Pos Frequencies",
+                                xAxisBreaks = c(-1,-10,-20,-30))
+
+plotMismatchPositionFrequencies(NHF1CPDMismatchDataAllReps$`48h`, includedTypes = c("C>T"),
+                                title = "NHF1 CPD 48h All Reps C>T Mismatch Pos Frequencies",
+                                xAxisBreaks = c(-1,-10,-20,-30), ylim = c(0,0.2))
+```
+
+```{r read_figure_S3_data}
 NHF1SixFourMismatchDataAllReps = NHF1SixFourTimepoints
@@
 
-```{r figure_S2}
+```{r figure_S3}
 plotMismatchTypeFrequencies(NHF1SixFourMismatchDataAllReps$`20min`,
@@
                          title = "GM12878 Cisplatin 90min All Reps Mismatch Trinuc Context",
-                         printDipyFreq = TRUE)
+                         printDipyFreq = TRUE, ylim = c(0,0.1))
 
@@
 
-```{r read_figure_S3_data}
+```{r read_figure_S4_data}
 arabidopsisCPDMismatchDataAllReps = arabidopsisCPDTimepoints
@@
 
-```{r figure_S3}
-plotMismatchTypeFrequencies(arabidopsisCPDMismatchDataAllReps$ZT2,
+```{r figure_S4}
+plotMismatchTypeFrequencies(arabidopsisCPDMismatchDataAllReps$ZT2, ylim = c(0,0.8),
                             title = "Arabidopsis CPD ZT2 All Reps Mismatch Type Frequencies")
@@
                          title = "Arabidopsis CPD ZT2 All Reps Mismatch Trinuc Context",
-                         printDipyFreq = TRUE)
+                         printDipyFreq = TRUE, ylim = c(0,0.4))
 
@@
 
-```{r read_figure_S4_data}
+```{r read_figure_S5_data}
 CSBCPDMismatchDataAllReps = CSBCPDTimepoints
@@
 
-```{r figure_S4}
-plotMismatchTypeFrequencies(CSBCPDMismatchDataAllReps$`1h`,
+```{r figure_S5}
+plotMismatchTypeFrequencies(CSBCPDMismatchDataAllReps$`1h`, ylim = c(0,0.8),
                             title = "CS-B CPD 1h All Reps Mismatch Type Frequencies")
 
-plotMismatchTypeFrequencies(XPCCPDMismatchDataAllReps$`1h`,
+plotMismatchTypeFrequencies(XPCCPDMismatchDataAllReps$`1h`, ylim = c(0,0.8),
                             title = "XP-C CPD 1h All Reps Mismatch Type Frequencies")
@@
 
-```{r read_figure_S5_data}
+```{r read_figure_S6_data}
+arabidopsisCPDTGGSeqFreqAllReps = arabidopsisCPDTimepoints
+for (i in seq_along(arabidopsisCPDTGGSeqFreqAllReps)) {
+  arabidopsisCPDTGGSeqFreqAllReps[[i]] = fread(generateFilePath(
+    directory = arabidopsisGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+    cellType = "Arabidopsis", lesion = "CPD", repitition = "all_reps",
+    timepoint = names(arabidopsisCPDTGGSeqFreqAllReps)[i], sequence = "TGG"
+  ))
+}
+
+yeastCPDTGGSeqFreqAllReps = yeastCPDTimepoints
+for (i in seq_along(yeastCPDTGGSeqFreqAllReps)) {
+  yeastCPDTGGSeqFreqAllReps[[i]] = fread(generateFilePath(
+    directory = yeastGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+    cellType = "yeast", lesion = "CPD", repitition = "all_reps",
+    timepoint = names(yeastCPDTGGSeqFreqAllReps)[i], sequence = "TGG"
+  ))
+}
+```
+
+```{r figure_S6, fig.width = 5, fig.height = 6}
+plotSequenceFrequencies(arabidopsisCPDTGGSeqFreqAllReps$ZT2, title = "Arabidopsis CPD ZT2 All Reps General Read TGG Freq",
+                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE, querySequences = c("TGG"),
+                        expansionOffset = 10, minReadLength = 22, maxReadLength = 28, positionOffset = 10,
+                        yAxisLabel = "TGG Trinucleotide Frequency", defaultColor = "Black", ylimMax = 0.15)
+
+plotSequenceFrequencies(yeastCPDTGGSeqFreqAllReps$`20min`, title = "Yeast CPD 20min All Reps General Read TGG Freq",
+                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE, querySequences = c("TGG"),
+                        expansionOffset = 10, minReadLength = 20, maxReadLength = 24, positionOffset = 10,
+                        yAxisLabel = "TGG Trinucleotide Frequency", defaultColor = "Black", ylimMax = 0.15)
+```
+
+```{r read_figure_S7_data}
 NHF1FivePrimeMismatchCPDNucFreqAllRepsTGGFiltered = fread(generateFilePath(
@@
 
-```{r figure_S5A, fig.width = 6.5, fig.height = 6}
+```{r figure_S7A, fig.width = 6.5, fig.height = 6}
 ### Just the 1h timepoint ###
@@
 ```
-```{r figure_S5B, fig.width = 6.5, fig.height = 6}
+```{r figure_S7B, fig.width = 6.5, fig.height = 6}
 ### Just the 1h timepoint ###
@@
 ```
-```{r figure_S5C, fig.width = 5, fig.height = 5}
+```{r figure_S7C, fig.width = 5, fig.height = 5}
 ### Just the 1h timepoint ###
@@
 ```
-```{r figure_S5D, fig.width = 5, fig.height = 5}
+```{r figure_S7D, fig.width = 5, fig.height = 5}
 ### Just the 1h timepoint ###
@@
 
-```{r read_figure_S6_data}
+```{r read_figure_S8_data}
+yeastCPDMismatchDataAllRepsFiltered = yeastCPDTimepoints
+for (i in seq_along(yeastCPDMismatchDataAllRepsFiltered)) {
+  yeastCPDMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
+    yeastSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+    cellType = "yeast", lesion = "CPD", timepoint = names(yeastCPDMismatchDataAllRepsFiltered)[i],
+    repitition = "all_reps", filtering = "TGG_filtered"
+  ))
+}
+
+yeastCPDMMFreqZScoresAllRepsFiltered = yeastCPDTimepoints
+for (i in seq_along(yeastCPDMMFreqZScoresAllRepsFiltered)) {
+  yeastCPDMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
+    yeastSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+    cellType = "yeast", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
+    timepoint = names(yeastCPDMMFreqZScoresAllRepsFiltered)[i], includedMismatches = c("C>T")
+  ))
+}
+
+yeastCPDGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
+for (i in seq_along(yeastCPDGroupedStatsAllRepsFiltered)) {
+  yeastCPDGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
+    yeastSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
+    cellType = "yeast", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
+    strandPolarity = names(yeastCPDGroupedStatsAllRepsFiltered)[i]
+  ))
+}
+```
+
+```{r figure_S8A, fig.width = 5, fig.height = 5}
+plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["20min"], includedTypes = c("C>T"),
+                                         title = "Yeast CPD 20min All Reps TGG-Filtered C>T Mismatch Pos Freq",
+                                         zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
+                                         yAxisLabel = "Relative C>T Frequency", xAxisBreaks = c(-1,-10,-20,-30))
+```
+```{r figure_S8B, fig.width = 5, fig.height = 5}
+plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["20min"], includedTypes = c("C>T"),
+                                         title = "Yeast CPD 20min All Reps TGG-Filtered C>T Mismatch Pos Freq",
+                                         zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
+                                         posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency",
+                                         xAxisBreaks = c(1,10,20,30))
+```
+```{r figure_S8C, fig.width = 7.5, fig.height = 5}
+plotGroupedPositionStats(yeastCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "20min"],
+                         yeastCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "20min"],
+                         POS_DIFF, title = "Yeast CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
+                         xAxisBreaks = c(22:25), ylim = c(0,2.5))
+```
+
+```{r read_figure_S9_data}
 NHF1GeneralReadsSixFourSeqFreqAllReps20minFilteredCombined = fread(generateFilePath(
@@
 
-```{r figure_S6, fig.width = 5, fig.height = 4}
+```{r figure_S9, fig.width = 5, fig.height = 4}
 plotSequenceFrequencies(NHF1GeneralReadsSixFourSeqFreqAllReps20minFilteredCombined[Position <= 7],
@@
 
-```{r read_figure_S7_data}
+```{r read_figure_S10_data}
 NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
@@
 
-```{r figure_S7, fig.width = 6.5, fig.height = 6}
+```{r figure_S10, fig.width = 6.5, fig.height = 6}
 plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
@@
 
-```{r read_figure_S8_data}
+```{r read_figure_S11_data}
 NHF1CPDGGtoAAMismatchDataAllRepsFiltered = NHF1CPDTimepoints
@@
 
-```{r figure_S8, fig.width = 5, fig.height = 5.5}
+```{r figure_S11, fig.width = 5, fig.height = 5.5}
 plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered["1h"],

### 2023-04-05 R/PaperFigureGeneration.rmd
Small paper figure update
Changed the read length range for figure 6B

@@
                         showFivePrimeCutSite = TRUE, querySequences = c("333"),
-                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 6,
+                        expansionOffset = 10, minReadLength = 19, maxReadLength = 24, endBasedBackgroundNum = 6,
                         endBasedCheckPositions = -9, displayPValue = FALSE, xAxisLabel = "Mismatch Relative Position",

### 2023-04-12 R/DeaminationSequenceAndPositionAnalysis.R
Changes to position stats plotting/reporting
- Added the getThreePrimeVariation function for returning the percentage of the variation in read length explained by the 3' end (based on the position difference statistic). This can be computed based solely on the endpoints, across all of the recorded read lengths (area under curve), or across all of the recorded read lengths while taking into account their relative frequencies (weighted area under curve).
- Changed grouped position stats plotting so that timepoint is associated with line type or shape and the color represents strand polarity inst

@@ -286,16 +286,17 @@ plotGroupedPositionStats = function(threePrimeGroupedStats, fivePrimeGroupedStat
 
   if (stat == POS_DIFF) {
     groupedStatsPlot =
-      ggplot(aggregateData, aes(Read_Length, Absolute_Pos_Change, color = Timepoint, linetype = Position_Type)) +
+      ggplot(aggregateData, aes(Read_Length, Absolute_Pos_Change, color = Position_Type, linetype = Timepoint)) +
       geom_line(linewidth = 1.5) + theme(legend.key.width = unit(3, "line")) +
-      scale_linetype_manual(values = c("3' Relative Position" = "dashed", "5' Relative Position" = "solid"))
+      scale_color_brewer(palette = "Set1")
   } else if (stat == IQR) {
     groupedStatsPlot =
-      ggplot(aggregateData, aes(Read_Length, IQR, color = Timepoint, shape = Position_Type)) +
+      ggplot(aggregateData, aes(Read_Length, IQR, shape = Timepoint, color = Position_Type)) +
       geom_jitter(height = 0, size = 3)
   } else if (stat == STDEV) {
     groupedStatsPlot =
-      ggplot(aggregateData, aes(Read_Length, Standard_Deviation, color = Timepoint, shape = Position_Type)) +
+      ggplot(aggregateData, aes(Read_Length, Standard_Deviation, shape = Timepoint, color = Position_Type)) +
+      scale_color_brewer(palette = "Set1") +
       geom_jitter(height = 0, size = 3)
   } else {
     stop(paste("Unrecognized stat:",stat))
@@ -307,13 +308,40 @@ plotGroupedPositionStats = function(threePrimeGroupedStats, fivePrimeGroupedStat
     labs(title = title, x = "Read Length", y = yAxisTitle) +
     scale_x_continuous(breaks = xAxisBreaks) + coord_cartesian(ylim = ylim)
 
-  if (all(aggregateData$Timepoint == "NONE")) {
-    groupedStatsPlot = groupedStatsPlot + scale_color_manual(values = "black")
-  } else if (length(unique(aggregateData$Timepoint)) == 1) {
-    groupedStatsPlot = groupedStatsPlot + scale_color_manual(values = "black")
-  } else groupedStatsPlot = groupedStatsPlot + scale_color_brewer(palette = "Set1")
-
   print(groupedStatsPlot)
+
+}
+
+
[…]

### 2023-04-12 R/PaperFigureGeneration.rmd
Added information on 3' read length variation

@@
                          xAxisBreaks = c(22:30), ylim = c(0,5))
+print(paste("3' endpoint variation: ",
+            getThreePrimeVariation(NHF1CPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                                   NHF1CPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
+                                   endpointVariation = TRUE)))
+print(paste("3' variation (unweighted): ",
+            getThreePrimeVariation(NHF1CPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                                   NHF1CPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"])))
+print(paste("3' variation (weighted): ",
+            getThreePrimeVariation(NHF1CPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                                   NHF1CPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
+                                   mismatchData = NHF1CPDMismatchDataAllRepsTGGFiltered$`1h`)))
 ```
@@
                          xAxisBreaks = c(24:30), ylim = c(0,5))
+print(paste("3' endpoint variation: ",
+            getThreePrimeVariation(arabidopsisCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "ZT2"],
+                                   arabidopsisCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "ZT2"],
+                                   endpointVariation = TRUE)))
+print(paste("3' variation (unweighted): ",
+            getThreePrimeVariation(arabidopsisCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "ZT2"],
+                                   arabidopsisCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "ZT2"])))
+print(paste("3' variation (weighted): ",
+            getThreePrimeVariation(arabidopsisCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "ZT2"],
+                                   arabidopsisCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "ZT2"],
+                                   mismatchData = arabidopsisCPDMismatchDataAllRepsFiltered$ZT2)))
 ```
@@
 
+arabidopsisCPDCCtoTTMismatchDataAllRepsFiltered = arabidopsisCPDTimepoints
+for (i in seq_along(arabidopsisCPDCCtoTTMismatchDataAllRepsFiltered)) {
+  arabidopsisCPDCCtoTTMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
+    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+    cellType = "Arabidopsis", lesion = "CPD", repitition = "all_reps",
+    filtering = "TGG_filtered", includedMismatches = "CC>TT",
+    timepoint = names(arabidopsisCPDCCtoTTMismatchDataAllRepsFiltered)[i]
+  ))
+}
+
 arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
@@
     strandPolarity = names(arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered)[i], includedMismatches = "CC>TT"
+  ))
+}
+
+yeastCPDCCtoTTMismatchDataAllRepsFiltered = yeastCPDTimepoints
+for (i in seq_along(yeastCPDCCtoTTMismatchDataAllRepsFiltered)) {
+  yeastCPDCCtoTTMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
+    yeastSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+    cellType = "yeast", lesion = "CPD", repitition = "all_reps",
+    filtering = "TGG_filtered", includedMismatches = "CC>TT",
+    timepoint = names(yeastCPDCCtoTTMismatchDataAllRepsFiltered)[i]
   ))
@@
 ```{r figure_6C, fig.width = 7.5, fig.height = 5}
-### Just the 1h timepoint ###
 plotGroupedPositionStats(NHF1CPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
@@
 
-### All timepoints together ###
-# plotGroupedPositionStats(NHF1CPDCCToTTGroupedStatsAllRepsFiltered$three_prime,
-#                          NHF1CPDCCToTTGroupedStatsAllRepsFiltered$five_prime,
-#                          POS_DIFF, title = "NHF1 CPD All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
-#                          xAxisBreaks = c(22:30))
+print(paste("3' endpoint variation: ",
+            getThreePrimeVariation(NHF1CPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                                   NHF1CPDCCToTTGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
+                                   endpointVariation = TRUE)))
+print(paste("3' variation (unweighted): ",
+            getThreePrimeVariation(NHF1CPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                                   NHF1CPDCCToTTGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"])))
+print(paste("3' variation (weighted): ",
+            getThreePrimeVariation(NHF1CPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                                   NHF1CPDCCToTTGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
+                                   mismatchData = NHF1CPDCCtoTTMismatchDataAllRepsFiltered$`1h`)))
 ```
 ```{r figure_6D, fig.width = 7.5, fig.height = 5}
-### Just the 1h timepoint ###
 plotGroupedPositionStats(arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "ZT2"],
@@
 
-### All timepoints together ###
-# plotGroupedPositionStats(arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered$three_prime,
-#                          arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered$five_prime,
-#                          POS_DIFF, title = "Arabidopsis CPD All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
-#                          xAxisBreaks = c(24:30))
+print(paste("3' endpoint variation: ",
+            getThreePrimeVariation(arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "ZT2"],
+                                   arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered$five_prime[Timepoint == "ZT2"],
+                                   endpointVariation = TRUE)))
+print(paste("3' variation (unweighted): ",
+            getThreePrimeVariation(arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "ZT2"],
+                                   arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered$five_prime[Timepoint == "ZT2"])))
+print(paste("3' variation (weighted): ",
+            getThreePrimeVariation(arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "ZT2"],
+                                   arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered$five_prime[Timepoint == "ZT2"],
+                                   mismatchData = arabidopsisCPDCCtoTTMismatchDataAllRepsFiltered$ZT2)))
 ```
 ```{r figure_6E, fig.width = 7.5, fig.height = 5}
-### Just the 1h timepoint ###
 plotGroupedPositionStats(yeastCPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "20min"],
@@
 
-### All timepoints together ###
-# plotGroupedPositionStats(yeastCPDCCToTTGroupedStatsAllRepsFiltered$three_prime,
-#                          yeastCPDCCToTTGroupedStatsAllRepsFiltered$five_prime,
-#                          POS_DIFF, title = "Yeast CPD All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
-#                          xAxisBreaks = c(22:25))
+print(paste("3' endpoint variation: ",
+            getThreePrimeVariation(yeastCPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "20min"],
+                                   yeastCPDCCToTTGroupedStatsAllRepsFiltered$five_prime[Timepoint == "20min"],
+                                   endpointVariation = TRUE)))
+print(paste("3' variation (unweighted): ",
+            getThreePrimeVariation(yeastCPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "20min"],
+                                   yeastCPDCCToTTGroupedStatsAllRepsFiltered$five_prime[Timepoint == "20min"])))
+print(paste("3' variation (weighted): ",
+            getThreePrimeVariation(yeastCPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "20min"],
+                                   yeastCPDCCToTTGroupedStatsAllRepsFiltered$five_prime[Timepoint == "20min"],
+                                   mismatchData = yeastCPDCCtoTTMismatchDataAllRepsFiltered$`20min`)))
 ```
@@
                          xAxisBreaks = c(22:25), ylim = c(0,2.5))
+
+print(paste("3' endpoint variation: ",
+            getThreePrimeVariation(yeastCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "20min"],
+                                   yeastCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "20min"],
+                                   endpointVariation = TRUE)))
+print(paste("3' variation (unweighted): ",
+            getThreePrimeVariation(yeastCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "20min"],
+                                   yeastCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "20min"])))
+print(paste("3' variation (weighted): ",
+            getThreePrimeVariation(yeastCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "20min"],
+                                   yeastCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "20min"],
+                                   mismatchData = yeastCPDMismatchDataAllRepsFiltered$`20min`)))
 ```

### 2023-05-08 R/PaperFigureGeneration.rmd
Fixed incorrect figure title

@@
 plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered["1h"], includedTypes = c("C>T"),
-                                         title = "NHF1 CPD 1h All Reps TG-Filtered C>T Mismatch Pos Freq",
+                                         title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGFiltered,

### 2023-07-19 python/PotentialTandemMismatchesSamToBed.py
Tkinter dialog title change

@@ -99,7 +99,7 @@ def potentialTandemMismatchesSamToBed(samFilePaths: List[str], outputDir = None)
 def main():
     # Create the Tkinter dialog.
     with TkinterDialog(workingDirectory=os.path.join(__file__,"..",".."),
-                       title = "Potential Tandem Mismatches: Sam to Bed") as dialog:
+                       title = "Potential Tandem Mismatches Sam to Bed") as dialog:
         dialog.createMultipleFileSelector("Sam Read Files:",0,".sam.gz",("Sam Files",(".sam.gz",".sam")), 
                                         additionalFileEndings = [".sam"])
         with dialog.createDynamicSelector(1, 0) as outputDirDynSel:

### 2023-07-19 R/NHF1_TFBS_DataGeneration.Rmd
Created systems for XR-seq and TFBS analysis
- Created a function to format and filter mismatched reads to be more easily associated with transcription factor binding sites (TFBSs). (May isolate this to its own script in the near future)
- Created a function to associate TFBSs with XR-seq read mismatches. (Will probably generalize this soon to work with other genomic features, like nucleosomes.)
- Added R functions to further format and plot the above data.

---
title: "NHF1_TFBS_DataGeneration"
author: "Ben Morledge-Hampton"
date: "2023-07-18"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered, TG_filtered]
---

```{r setup_chunk}
library(knitr)

cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
mismatchTypes = list(`C>T` = NULL, `CC>TT` = NULL)
TFBSs = list(`CTCF_known1_DHS` = NULL, `CTCF_known1_non-DHS` = NULL)

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
  filtering = readline("Filtering identifier (Input nothing for no filtering):")
  if (filtering == '') filtering = character()
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
  filtering = params$filtering
  if (filtering == "NONE") filtering = character()
}
if (is.na(bioinformaticsDirectory)) stop("No bioinformatics directory given.")

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
mismatchesByReadDirectory = file.path(deaminationDataDirectory, "mismatches_by_read")
tfbsDataDirectory = file.path(deaminationDataDirectory,"TFBS_analysis")
dir.create(tfbsDataDirectory, showWarnings = FALSE, recursive = TRUE)
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationTFBSAnalysis.R"))
```

```{r generate_and_write_TFBS_relative_counts_data}
cpdTfbsRelativeData = copy(CPDTimepoints)
for (i in 1:length(cpdTfbsRelativeData)) {
  cpdTfbsRelativeData[[i]] = copy(mismatchTypes)
  for (j in 1:length(cpdTfbsRelativeData[[i]])) {
    cpdTfbsRelativeData[[i]][[j]] = copy(TFBSs)
    for (k in 1:length(cpdTfbsRelativeData[[i]][[j]])) {
      cpdTfbsRelativeData[[i]][[j]][[k]] = parseMismatchesByTFBS(fread(
        generateFilePath(mismatchesByReadDirectory, dataTypeStrings$mismatchesByReadTfbs, ".bed",
                         cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
                         timepoint = names(cpdTfbsRelativeData)[i], includedMismatches = names(cpdTfbsRelativeData[[i]])[j],
                         additionalInformation = paste0(names(cpdTfbsRelativeData[[i]][[j]])[k],"_related"))
      ))

      fwrite(cpdTfbsRelativeData[[i]][[j]][[k]], sep = '\t', file = generateFilePath(
        tfbsDataDirectory, dataTypeStrings$tfbsRelativeData, ".tsv",
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = names(cpdTfbsRelativeData)[i], includedMismatches = names(cpdTfbsRelativeData[[i]])[j],
        additionalInformation = paste0(names(cpdTfbsRelativeData[[i]][[j]])[k],"_related")
      ))

      fwrite(getTfbsRelativeCounts(cpdTfbsRelativeData[[i]][[j]][[k]], feature = TFBS_RELATIVE_POSITION),
             sep = '\t', file = generateFilePath(
        tfbsDataDirectory, dataTypeStrings$tfbsRelativePositionCounts, ".tsv",
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = names(cpdTfbsRelativeData)[i], includedMismatches = names(cpdTfbsRelativeData[[i]])[j],
        additionalInformation = paste0(names(cpdTfbsRelativeData[[i]][[j]])[k],"_related")
      ))

      fwrite(getTfbsRelativeCounts(cpdTfbsRelativeData[[i]][[j]][[k]], feature = TFBS_RELATIVE_THREE_PRIME_CUT_SITE),
             sep = '\t', file = generateFilePath(
        tfbsDataDirectory, dataTypeStrings$tfbsRelativeCutSiteCounts, ".tsv", strandPolarity = THREE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = names(cpdTfbsRelativeData)[i], includedMismatches = names(cpdTfbsRelativeData[[i]])[j],
        additionalInformation = paste0(names(cpdTfbsRelativeData[[i]][[j]])[k],"_related")
      ))

      fwrite(getTfbsRelativeCounts(cpdTfbsRelativeData[[i]][[j]][[k]], feature = TFBS_RELATIVE_FIVE_PRIME_CUT_SITE),
             sep = '\t', file = generateFilePath(
        tfbsDataDirectory, dataTypeStrings$tfbsRelativeCutSiteCounts, ".tsv", strandPolarity = FIVE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = names(cpdTfbsRelativeData)[i], includedMismatches = names(cpdTfbsRelativeData[[i]])[j],
        additionalInformation = paste0(names(cpdTfbsRelativeData[[i]][[j]])[k],"_related")
      ))
    }
  }
}

```

### 2023-07-19 R/NHF1_TFBS_FigureGeneration.Rmd
Created systems for XR-seq and TFBS analysis
- Created a function to format and filter mismatched reads to be more easily associated with transcription factor binding sites (TFBSs). (May isolate this to its own script in the near future)
- Created a function to associate TFBSs with XR-seq read mismatches. (Will probably generalize this soon to work with other genomic features, like nucleosomes.)
- Added R functions to further format and plot the above data.

---
title: "NHF1_TFBS_FigureGeneration"
author: "Ben Morledge-Hampton"
date: "2023-07-13"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered, TG_filtered]
---

```{r setup_chunk}
library(knitr)

cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
mismatchTypes = list(`C>T` = NULL, `CC>TT` = NULL)
TFBSs = list(`CTCF_known1_DHS` = NULL, `CTCF_known1_non-DHS` = NULL)

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
  filtering = readline("Filtering identifier (Input nothing for no filtering):")
  if (filtering == '') filtering = character()
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
  filtering = params$filtering
  if (filtering == "NONE") filtering = character()
}
if (is.na(bioinformaticsDirectory)) stop("No bioinformatics directory given.")

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
tfbsDataDirectory = file.path(deaminationDataDirectory,"TFBS_analysis")
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationTFBSAnalysis.R"))
```

```{r TFBS_relative_mismatch_position_plots}
xlim = NULL
for (CPDTimepoint in names(CPDTimepoints)) {
  for (mismatchType in names(mismatchTypes)) {
    for (TFBS in names(TFBSs)) {

      cpdTfbsRelativePositionData = fread(generateFilePath(
        tfbsDataDirectory, dataTypeStrings$tfbsRelativePositionCounts, ".tsv",
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(TFBS,"_related")
      ))

      plotTFBSRelativeCounts(cpdTfbsRelativePositionData, TFBS_RELATIVE_POSITION, sameStrand = TRUE, xlim = xlim,
                             title = paste(cellType, "CPD", CPDTimepoint, mismatchType, TFBS, "Same Strand"))
      plotTFBSRelativeCounts(cpdTfbsRelativePositionData, TFBS_RELATIVE_POSITION, sameStrand = FALSE, xlim = xlim,
                             title = paste(cellType, "CPD", CPDTimepoint, mismatchType, TFBS, "Opposite Strand"))
    }
  }
}
```

```{r TFBS_relative_three_prime_cut_site_plots}
xlim = NULL
for (CPDTimepoint in names(CPDTimepoints)) {
  for (mismatchType in names(mismatchTypes)) {
    for (TFBS in names(TFBSs)) {

      cpdTfbsRelativePositionData = fread(generateFilePath(
        tfbsDataDirectory, dataTypeStrings$tfbsRelativeCutSiteCounts, ".tsv", strandPolarity = THREE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(TFBS,"_related")
      ))

      plotTFBSRelativeCounts(cpdTfbsRelativePositionData, TFBS_RELATIVE_THREE_PRIME_CUT_SITE, sameStrand = TRUE, xlim = xlim,
                             title = paste(cellType, "CPD", CPDTimepoint, mismatchType, TFBS, "Same Strand"))
      plotTFBSRelativeCounts(cpdTfbsRelativePositionData, TFBS_RELATIVE_THREE_PRIME_CUT_SITE, sameStrand = FALSE, xlim = xlim,
                             title = paste(cellType, "CPD", CPDTimepoint, mismatchType, TFBS, "Opposite Strand"))
    }
  }
}
```

```{r TFBS_relative_five_prime_cut_site_plots}
xlim = NULL
for (CPDTimepoint in names(CPDTimepoints)) {
  for (mismatchType in names(mismatchTypes)) {
    for (TFBS in names(TFBSs)) {

      cpdTfbsRelativePositionData = fread(generateFilePath(
        tfbsDataDirectory, dataTypeStrings$tfbsRelativeCutSiteCounts, ".tsv", strandPolarity = FIVE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(TFBS,"_related")
      ))

      plotTFBSRelativeCounts(cpdTfbsRelativePositionData, TFBS_RELATIVE_FIVE_PRIME_CUT_SITE, sameStrand = TRUE, xlim = xlim,
                             title = paste(cellType, "CPD", CPDTimepoint, mismatchType, TFBS, "Same Strand"))
      plotTFBSRelativeCounts(cpdTfbsRelativePositionData, TFBS_RELATIVE_FIVE_PRIME_CUT_SITE, sameStrand = FALSE, xlim = xlim,
                             title = paste(cellType, "CPD", CPDTimepoint, mismatchType, TFBS, "Opposite Strand"))
    }
  }
}
```

### 2023-07-19 R/DeaminationTFBSAnalysis.R

@@ -1,0 +1,97 @@
+library(data.table)
+library(stringr)
+library(ggplot2)
+
+THREE_PRIME = "three_prime"
+FIVE_PRIME = "five_prime"
+HALF_MAX = "half_max"
+
+TFBS_RELATIVE_POSITION = "TFBS_Relative_Mismatch_Pos"
+TFBS_RELATIVE_THREE_PRIME_CUT_SITE = "TFBS_Relative_Three_Prime_Cut_Site"
+TFBS_RELATIVE_FIVE_PRIME_CUT_SITE = "TFBS_Relative_Five_Prime_Cut_Site"
+
+
+# Default text scaling
+defaultTextScaling = theme(plot.title = element_text(size = 22, hjust = 0.5),
+                           axis.title = element_text(size = 22), axis.text = element_text(size = 18, color = "black"),
+                           legend.title = element_text(size = 22), legend.text = element_text(size = 18),
+                           strip.text = element_text(size = 22))
+
+# Blank background theme
+blankBackground = theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+                        panel.background = element_blank(), axis.line = element_line(colour = "black"))
+
+
+# Takes a file of mismatches related to TFBSs and extracts information on relative mismatch and cut site location.
+parseMismatchesByTFBS = function(table) {
+  table = copy(table)
+  colnames(table) = c("Chromosome", "Mismatch_Pos_0", "Mismatch_Pos_1", "Read_Relative_Mismatch_Pos", "Mismatch_Type",
+                      "Mismatch_Strand", "Read_Length", "TFBS_Pos", "TFBS_Strand")
+
+  # Record mismatch positions relative to the transcription factor binding site
+  table[TFBS_Strand == '+', TFBS_Relative_Mismatch_Pos := Mismatch_Pos_0 - TFBS_Pos]
+  table[TFBS_Strand == '-', TFBS_Relative_Mismatch_Pos := TFBS_Pos - Mismatch_Pos_0]
+
+  # Record cut sites relative to the transcription factor binding site
+  table[Mismatch_Strand == '+', Three_Prime_Cut_Site := Mismatch_Pos_0 - Read_Relative_Mismatch_Pos - 0.5]
[…]

### 2023-07-19 R/UsefulFileSystemFunctions.R

@@ -4,6 +4,7 @@ library(data.table)
 # A list containing the strings designated to files containing a specific type of data.
 dataTypeStrings =
   list(mismatchesByRead = "mismatches_by_read",
+       mismatchesByReadTfbs = "mismatches_by_read_TFBS_formatted",
        simplifiedMismatches = "simplified_mismatches",
        mismatchPositionStats = "mismatch_position_stats",
        nucleosomePeriodicity = "deamination_periodicity_results",
@@ -14,7 +15,11 @@ dataTypeStrings =
        mismatchFrequencyZScores = "mismatch_frequency_z-scores",
        readLengthcounts = "read_length_counts",
        tandemMismatchCountsComparison = "tandem_mismatch_counts_comparison",
-       sequenceLogoInput = "sequence_logo_input")
+       sequenceLogoInput = "sequence_logo_input",
+       tfbsRelativeData = "TFBS_relative_data",
+       tfbsRelativePositionCounts = "TFBS_relative_position_counts",
+       tfbsRelativeCutSiteCounts = "TFBS_relative_cut_site_counts"
+       )
 
 generateFilePath = function(directory, dataTypeString, fileExtension,
                             cellType = NA, lesion = NA, timepoint = NA, repitition = NA,

### 2023-07-19 python/RelateMismatchesToTFBS.py

@@ -1,0 +1,163 @@
+# This script takes a file of mismatch positions and a file of transcription factor binding sites (must both be sorted)
+# and determines where those mismatches are relative to the TFBSs, within a given radius.
+
+import os, subprocess
+from benbiohelpers.TkWrappers.TkinterDialog import TkinterDialog
+from benbiohelpers.CountThisInThat.Counter import ThisInThatCounter
+from benbiohelpers.CountThisInThat.CounterOutputDataHandler import ENCOMPASSING_DATA, ENCOMPASSED_DATA
+from benbiohelpers.CountThisInThat.SupplementalInformation import SimpleColumnSupInfoHandler
+from benbiohelpers.InputParsing.CheckForNumber import checkForNumber
+from benbiohelpers.InputParsing.ParseToIterable import parseToIterable
+from benbiohelpers.FileSystemHandling.DirectoryHandling import checkDirs, getTempDir
+
+ 
+class MismatchesAroundTFBSCounter(ThisInThatCounter):
+
+    def setupOutputDataStratifiers(self):
+        self.outputDataHandler.addEncompassedFeatureStratifier()
+        self.outputDataHandler.addPlaceholderStratifier()
+        self.outputDataHandler.addCustomSupplementalInformationHandler(SimpleColumnSupInfoHandler(
+            outputName = "Motif_Midpoint", relevantData = ENCOMPASSING_DATA, dataCol = 1, removeDups = False
+        ))
+        self.outputDataHandler.addCustomSupplementalInformationHandler(SimpleColumnSupInfoHandler(
+            outputName = "TFBS_Strand", relevantData = ENCOMPASSING_DATA, dataCol = 5, removeDups = False
+        ))
+
+    def setupOutputDataWriter(self):
+        self.outputDataHandler.createOutputDataWriter(self.outputFilePath, omitFinalStratificationCounts = True)
+
+
+def filterAndFormatMismatches(mismatchesByReadFilePath: str, zScoresFilePath, zScoreCutoff = 4,
+                              acceptableReadLengths = range(22,31), acceptableMismatchTypes = ("C>T", "CC>TT"),
+                              outputSuffix = "_TFBS_formatted", addMismatchTypesToName = False):
+    """
+    Filters mismatches by read to acceptable mismatch patterns in reads of valid length at positions with zscores greater than or equal to the given z-score cutoff.
+    The bed entry is also formatted so that it is focused directly on the mismatched position(s) and read sequence is replaced with its length.
[…]

### 2023-07-24 R/NHF1_FeatureRelativeDataGeneration.Rmd
Major Updates to feature-relative analysis
- Generalized naming and functionality to any genome feature, not just transcription factor binding sites.
- Split the functionality for formatting mismatches and relating genomic features.
- Added several new features, such as the option to enforce a strand for a given genomic feature and an entirely new function for combining single and tandem C>T mismatches.
- R data generation functions can now track mean cut site distance and can strand-align results.
- Updated R figure generation to include mean cut site distance.
- I'm probably forgetting some

---
title: "NHF1_FeatureRelativeDataGeneration"
author: "Ben Morledge-Hampton"
date: "2023-07-18"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered, TG_filtered]
---

```{r setup_chunk}
library(knitr)

cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
mismatchTypes = list(`C>T_CC>TT` = NULL)
features = list(`CTCF_known1_DHS` = NULL, `CTCF_known1_non-DHS` = NULL, `hg19_mnase_all` = NULL)

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
  filtering = readline("Filtering identifier (Input nothing for no filtering):")
  if (filtering == '') filtering = character()
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
  filtering = params$filtering
  if (filtering == "NONE") filtering = character()
}
if (is.na(bioinformaticsDirectory)) stop("No bioinformatics directory given.")

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
mismatchesByReadDirectory = file.path(deaminationDataDirectory, "mismatches_by_read")
featureRelativeDataDirectory = file.path(deaminationDataDirectory,"feature_relative_analysis")
dir.create(featureRelativeDataDirectory, showWarnings = FALSE, recursive = TRUE)
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationFeatureRelativeAnalysis.R"))
```

```{r generate_and_write_feature_relative_counts_data}
cpdFeatureRelativeData = copy(CPDTimepoints)
for (i in 1:length(cpdFeatureRelativeData)) {
  cpdFeatureRelativeData[[i]] = copy(mismatchTypes)
  for (j in 1:length(cpdFeatureRelativeData[[i]])) {
    cpdFeatureRelativeData[[i]][[j]] = copy(features)
    for (k in 1:length(cpdFeatureRelativeData[[i]][[j]])) {
      cpdFeatureRelativeData[[i]][[j]][[k]] = parseMismatchesByFeature(fread(
        generateFilePath(mismatchesByReadDirectory, dataTypeStrings$mismatchesByReadRelationFormatted, ".bed",
                         cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
                         timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
                         additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related"))
      ))

      fwrite(cpdFeatureRelativeData[[i]][[j]][[k]], sep = '\t', file = generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeData, ".tsv",
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
        additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related")
      ))

      fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = FEATURE_RELATIVE_POSITION,
                                      strandAlign = TRUE),
             sep = '\t', file = generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativePositionCounts, ".tsv",
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
        additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related")
      ))

      fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = FEATURE_RELATIVE_THREE_PRIME_CUT_SITE,
                                      strandAlign = TRUE),
             sep = '\t', file = generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeCutSiteCounts, ".tsv", strandPolarity = THREE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
        additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related")
      ))

      fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = FEATURE_RELATIVE_FIVE_PRIME_CUT_SITE,
                                      strandAlign = TRUE),
             sep = '\t', file = generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeCutSiteCounts, ".tsv", strandPolarity = FIVE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
        additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related")
      ))

      fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                                      strandAlign = TRUE),
             sep = '\t', file = generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = THREE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
        additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related")
      ))

      fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = MEAN_FIVE_PRIME_CUT_SITE_DISTANCE,
                                      strandAlign = TRUE),
             sep = '\t', file = generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = FIVE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
        additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related")
      ))

    }
  }
}

```

### 2023-07-24 R/NHF1_FeatureRelativeFigureGeneration.Rmd
Major Updates to feature-relative analysis
- Generalized naming and functionality to any genome feature, not just transcription factor binding sites.
- Split the functionality for formatting mismatches and relating genomic features.
- Added several new features, such as the option to enforce a strand for a given genomic feature and an entirely new function for combining single and tandem C>T mismatches.
- R data generation functions can now track mean cut site distance and can strand-align results.
- Updated R figure generation to include mean cut site distance.
- I'm probably forgetting some

---
title: "NHF1_FeatureRelativeFigureGeneration"
author: "Ben Morledge-Hampton"
date: "2023-07-13"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered, TG_filtered]
---

```{r setup_chunk}
library(knitr)

cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
mismatchTypes = list(`C>T_CC>TT` = NULL)
TFBSs = list(`CTCF_known1_DHS` = NULL, `CTCF_known1_non-DHS` = NULL)
nucMaps = list(`hg19_mnase_all` = NULL)

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
  filtering = readline("Filtering identifier (Input nothing for no filtering):")
  if (filtering == '') filtering = character()
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
  filtering = params$filtering
  if (filtering == "NONE") filtering = character()
}
if (is.na(bioinformaticsDirectory)) stop("No bioinformatics directory given.")

opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
               fig.path = paste0(file.path("deamination_analysis_output",cellType,
                                           paste(c(filtering,"feature_relative_figures"), collapse = '_')),
                                 .Platform$file.sep))

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
featureRelativeDataDirectory = file.path(deaminationDataDirectory,"feature_relative_analysis")
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationFeatureRelativeAnalysis.R"))
```

```{r TFBS_relative_mismatch_position_plots}
xlim = NULL
for (CPDTimepoint in names(CPDTimepoints)) {
  for (mismatchType in names(mismatchTypes)) {
    for (tfbs in names(TFBSs)) {

      featureRelativePositionData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativePositionCounts, ".tsv",
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(tfbs,"_related")
      ))

      meanThreePrimeCutSiteDistanceData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = THREE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(tfbs,"_related")
      ))

      meanFivePrimeCutSiteDistanceData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = FIVE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(tfbs,"_related")
      ))

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION,
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"))

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION, meanThreePrimeCutSiteDistanceData,
                                THREE_PRIME, title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"))

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION, meanFivePrimeCutSiteDistanceData,
                                FIVE_PRIME, title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"))

    }
  }
}
```

```{r nucleosome_relative_mismatch_position_plots}
xlim = NULL
for (CPDTimepoint in names(CPDTimepoints)) {
  for (mismatchType in names(mismatchTypes)) {
    for (nucMap in names(nucMaps)) {

      featureRelativePositionData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativePositionCounts, ".tsv",
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(nucMap,"_related")
      ))

      meanThreePrimeCutSiteDistanceData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = THREE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(nucMap,"_related")
      ))

      meanFivePrimeCutSiteDistanceData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = FIVE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(nucMap,"_related")
      ))

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION,
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"))

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION, meanThreePrimeCutSiteDistanceData,
                                THREE_PRIME, title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"))

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION, meanFivePrimeCutSiteDistanceData,
                                FIVE_PRIME, title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"))

    }
  }
}
```

```{r periodicity analysis}
library(mutperiodR)

for (CPDTimepoint in names(CPDTimepoints)) {
  for (mismatchType in names(mismatchTypes)) {
    for (nucMap in names(nucMaps)) {

        meanThreePrimeCutSiteDistanceData = fread(generateFilePath(
          featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = THREE_PRIME,
          cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
          timepoint = CPDTimepoint, includedMismatches = mismatchType,
          additionalInformation = paste0(nucMap,"_related")
        ))

        meanFivePrimeCutSiteDistanceData = fread(generateFilePath(
          featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = FIVE_PRIME,
          cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
          timepoint = CPDTimepoint, includedMismatches = mismatchType,
          additionalInformation = paste0(nucMap,"_related")
        ))

        print(paste(cellType, CPDTimepoint, mismatchType, nucMap, ":"))

        print("Mean 3` cut site distance:")
        periodAndSNR = getPeakPeriodicityAndSNR(
          meanThreePrimeCutSiteDistanceData[order(Feature_Relative_Mismatch_Pos)][abs(Feature_Relative_Mismatch_Pos) <= 60,
                                                                                  Mean_Three_Prime_Cut_Site_Distance], 5, 25)
        print(paste("  Peak Period:",periodAndSNR[1]))
        print(paste("  SNR:",periodAndSNR[2]))

        print("Mean 5` cut site distance:")
        periodAndSNR = getPeakPeriodicityAndSNR(
          meanFivePrimeCutSiteDistanceData[order(Feature_Relative_Mismatch_Pos)][abs(Feature_Relative_Mismatch_Pos) <= 60,
                                                                                  Mean_Five_Prime_Cut_Site_Distance], 5, 25)
        print(paste("  Peak Period:",periodAndSNR[1]))
        print(paste("  SNR:",periodAndSNR[2]))
        print("")

    }
  }
}

```

### 2023-07-24 R/DeaminationFeatureRelativeAnalysis.R

@@ -1,0 +1,193 @@
+library(data.table)
+library(stringr)
+library(ggplot2)
+
+THREE_PRIME = "three_prime"
+FIVE_PRIME = "five_prime"
+HALF_MAX = "half_max"
+
+FEATURE_RELATIVE_POSITION = "Feature_Relative_Mismatch_Pos"
+FEATURE_RELATIVE_THREE_PRIME_CUT_SITE = "Feature_Relative_Three_Prime_Cut_Site"
+FEATURE_RELATIVE_FIVE_PRIME_CUT_SITE = "Feature_Relative_Five_Prime_Cut_Site"
+MEAN_THREE_PRIME_CUT_SITE_DISTANCE = "Mean_Three_Prime_Cut_Site_Distance"
+MEAN_FIVE_PRIME_CUT_SITE_DISTANCE = "Mean_Five_Prime_Cut_Site_Distance"
+
+
+
+# Default text scaling
+defaultTextScaling = theme(plot.title = element_text(size = 22, hjust = 0.5),
+                           axis.title = element_text(size = 22), axis.text = element_text(size = 18, color = "black"),
+                           legend.title = element_text(size = 22), legend.text = element_text(size = 18),
+                           strip.text = element_text(size = 22))
+
+# Blank background theme
+blankBackground = theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+                        panel.background = element_blank(), axis.line = element_line(colour = "black"))
+
+
+# Takes a file of mismatches related to genome features and extracts information on relative mismatch and cut site location.
+parseMismatchesByFeature = function(table) {
+  table = copy(table)
+  colnames(table) = c("Chromosome", "Mismatch_Pos_0", "Mismatch_Pos_1", "Read_Relative_Mismatch_Pos", "Mismatch_Type",
+                      "Mismatch_Strand", "Read_Length", "Feature_Pos", "Feature_Strand")
+
+  # Record mismatch positions relative to the transcription factor binding site
+  table[Feature_Strand == '+', Feature_Relative_Mismatch_Pos := Mismatch_Pos_0 - Feature_Pos]
+  table[Feature_Strand == '-', Feature_Relative_Mismatch_Pos := Feature_Pos - Mismatch_Pos_0]
+
+  # Record cut sites relative to the transcription factor binding site
[…]

### 2023-07-24 R/DeaminationTFBSAnalysis.R

@@ -1,97 +1,0 @@
-library(data.table)
-library(stringr)
-library(ggplot2)
-
-THREE_PRIME = "three_prime"
-FIVE_PRIME = "five_prime"
-HALF_MAX = "half_max"
-
-TFBS_RELATIVE_POSITION = "TFBS_Relative_Mismatch_Pos"
-TFBS_RELATIVE_THREE_PRIME_CUT_SITE = "TFBS_Relative_Three_Prime_Cut_Site"
-TFBS_RELATIVE_FIVE_PRIME_CUT_SITE = "TFBS_Relative_Five_Prime_Cut_Site"
-
-
-# Default text scaling
-defaultTextScaling = theme(plot.title = element_text(size = 22, hjust = 0.5),
-                           axis.title = element_text(size = 22), axis.text = element_text(size = 18, color = "black"),
-                           legend.title = element_text(size = 22), legend.text = element_text(size = 18),
-                           strip.text = element_text(size = 22))
-
-# Blank background theme
-blankBackground = theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
-                        panel.background = element_blank(), axis.line = element_line(colour = "black"))
-
-
-# Takes a file of mismatches related to TFBSs and extracts information on relative mismatch and cut site location.
-parseMismatchesByTFBS = function(table) {
-  table = copy(table)
-  colnames(table) = c("Chromosome", "Mismatch_Pos_0", "Mismatch_Pos_1", "Read_Relative_Mismatch_Pos", "Mismatch_Type",
-                      "Mismatch_Strand", "Read_Length", "TFBS_Pos", "TFBS_Strand")
-
-  # Record mismatch positions relative to the transcription factor binding site
-  table[TFBS_Strand == '+', TFBS_Relative_Mismatch_Pos := Mismatch_Pos_0 - TFBS_Pos]
-  table[TFBS_Strand == '-', TFBS_Relative_Mismatch_Pos := TFBS_Pos - Mismatch_Pos_0]
-
-  # Record cut sites relative to the transcription factor binding site
-  table[Mismatch_Strand == '+', Three_Prime_Cut_Site := Mismatch_Pos_0 - Read_Relative_Mismatch_Pos - 0.5]
[…]

### 2023-07-24 R/UsefulFileSystemFunctions.R

@@ -4,7 +4,7 @@ library(data.table)
 # A list containing the strings designated to files containing a specific type of data.
 dataTypeStrings =
   list(mismatchesByRead = "mismatches_by_read",
-       mismatchesByReadTfbs = "mismatches_by_read_TFBS_formatted",
+       mismatchesByReadRelationFormatted = "mismatches_by_read_relation_formatted",
        simplifiedMismatches = "simplified_mismatches",
        mismatchPositionStats = "mismatch_position_stats",
        nucleosomePeriodicity = "deamination_periodicity_results",
@@ -16,9 +16,10 @@ dataTypeStrings =
        readLengthcounts = "read_length_counts",
        tandemMismatchCountsComparison = "tandem_mismatch_counts_comparison",
        sequenceLogoInput = "sequence_logo_input",
-       tfbsRelativeData = "TFBS_relative_data",
-       tfbsRelativePositionCounts = "TFBS_relative_position_counts",
-       tfbsRelativeCutSiteCounts = "TFBS_relative_cut_site_counts"
+       featureRelativeData = "feature_relative_data",
+       featureRelativePositionCounts = "feature_relative_position_counts",
+       featureRelativeCutSiteCounts = "feature_relative_cut_site_counts",
+       featureRelativeMeanCutSiteDistance = "feature_relative_mean_cut_site_distance"
        )
 
 generateFilePath = function(directory, dataTypeString, fileExtension,
@@ -33,8 +34,8 @@ generateFilePath = function(directory, dataTypeString, fileExtension,
     stop("Included mismatches and omitted mismatches given simultaneously")
   }
 
-  includedMismatches = lapply(includedMismatches, function(x) str_replace(x, '>', "_to_"))
-  omittedMismatches = lapply(omittedMismatches, function(x) str_replace(x, '>', "_to_"))
+  includedMismatches = lapply(includedMismatches, function(x) str_replace_all(x, '>', "_to_"))
+  omittedMismatches = lapply(omittedMismatches, function(x) str_replace_all(x, '>', "_to_"))
 
   if (!is.na(expansionNum) && expansionNum > 0) expansionText = paste0(expansionNum,"bp_expanded")
   else expansionText = NA

### 2023-07-24 python/FormatMismatchesForRelation.py

@@ -1,0 +1,161 @@
+# This script takes "mismatches by read" files and filters/formats them for use with the RelateMismatchesToFeatures.py script.
+import os, subprocess, shutil
+from typing import List
+from benbiohelpers.FileSystemHandling.DirectoryHandling import getTempDir
+from benbiohelpers.TkWrappers.TkinterDialog import TkinterDialog
+from benbiohelpers.InputParsing.CheckForNumber import checkForNumber
+from benbiohelpers.InputParsing.ParseToIterable import parseToIterable
+
+
+def formatMismatchesForRelation(mismatchesByReadFilePath: str, zScoresFilePath, zScoreCutoff = 4,
+                                acceptableReadLengths = range(22,31), acceptableMismatchTypes: List[str] = ["C>T", "CC>TT"],
+                                outputSuffix = "_relation_formatted", addMismatchTypesToName = True, outputToTmpDir = True,
+                                sortOutput = True, verbose = False):
+    """
+    Filters mismatches by read to acceptable mismatch patterns in reads of valid length at positions with zscores greater than or equal to the given z-score cutoff.
+    The bed entry is also formatted so that it is focused directly on the mismatched position(s) and read sequence is replaced with its length.
+    The resulting file is sorted, first by chromosome, then by start position and end position.
+    The output suffix is appended to the new file path just after "mismatches_by_read".
+    Returns the new file path.
+    """
+
+    # Determine which positions are valid for each read length based on the given z-score cutoff.
+    # Initialize a nested dictionary with one key for read length, another key for position and a final boolean value stating whether the zscore meets the cutoff.
+    if verbose: print("Determining positions with acceptable z-scores...")
+    zscoreDictionary = dict()
+    for readLength in acceptableReadLengths:
+        zscoreDictionary[readLength] = dict()
+
+    # Determine which positions have zscores which meet the cutoff.
+    with open(zScoresFilePath, 'r') as zScoresFile:
+        zScoresFile.readline() # Skip the headers
+        for line in zScoresFile:
+            readLength, position, frequency, zScore = line.split()
+            readLength = int(readLength)
+            if readLength not in acceptableReadLengths: continue
+            else: zscoreDictionary[readLength][float(position)] = float(zScore) >= zScoreCutoff
+
[…]

### 2023-07-24 python/RelateMismatchesToFeature.py

@@ -1,0 +1,84 @@
+# This script takes a file of mismatch positions and a file of genomic features, such as transcription factor binding sites (must both be sorted)
+# and determines where those mismatches are relative to the genomic features, within a given radius.
+
+import os
+from benbiohelpers.TkWrappers.TkinterDialog import TkinterDialog
+from benbiohelpers.CountThisInThat.Counter import ThisInThatCounter
+from benbiohelpers.CountThisInThat.CounterOutputDataHandler import ENCOMPASSING_DATA, ENCOMPASSED_DATA
+from benbiohelpers.CountThisInThat.SupplementalInformation import SimpleColumnSupInfoHandler
+from benbiohelpers.InputParsing.CheckForNumber import checkForNumber
+from benbiohelpers.InputParsing.ParseToIterable import parseToIterable
+from benbiohelpers.FileSystemHandling.DirectoryHandling import getTempDir
+
+ 
+class MismatchesAroundFeatureCounter(ThisInThatCounter):
+
+    def setupOutputDataStratifiers(self):
+        self.outputDataHandler.addEncompassedFeatureStratifier()
+        self.outputDataHandler.addPlaceholderStratifier()
+        self.outputDataHandler.addCustomSupplementalInformationHandler(SimpleColumnSupInfoHandler(
+            outputName = "Teature_Midpoint", relevantData = ENCOMPASSING_DATA, dataCol = 1, removeDups = False
+        ))
+        self.outputDataHandler.addCustomSupplementalInformationHandler(SimpleColumnSupInfoHandler(
+            outputName = "Feature_Strand", relevantData = ENCOMPASSING_DATA, dataCol = 5, removeDups = False
+        ))
+
+    def setupOutputDataWriter(self):
+        self.outputDataHandler.createOutputDataWriter(self.outputFilePath, omitFinalStratificationCounts = True)
+
+
+def relateMismatchesToFeature(formattedMismatchesByReadFilePath: str, featureFilePath: str,
+                              outputSuffix = "_feature_related", midpointRadius = 100, verbose = False,
+                              enforcedStrand = None):
+    """
+    Relates mismatches to nearby genomic features, recording the position of the feature midpoint as well as the strand it's on.
+    Only mismatches that are nearby a feature, as defined by the midpointRadius argument, are tracked.
+    Expects input in the format produced by the formatMismatchesForRelation function.
[…]

### 2023-07-24 python/RelateMismatchesToTFBS.py

@@ -1,163 +1,0 @@
-# This script takes a file of mismatch positions and a file of transcription factor binding sites (must both be sorted)
-# and determines where those mismatches are relative to the TFBSs, within a given radius.
-
-import os, subprocess
-from benbiohelpers.TkWrappers.TkinterDialog import TkinterDialog
-from benbiohelpers.CountThisInThat.Counter import ThisInThatCounter
-from benbiohelpers.CountThisInThat.CounterOutputDataHandler import ENCOMPASSING_DATA, ENCOMPASSED_DATA
-from benbiohelpers.CountThisInThat.SupplementalInformation import SimpleColumnSupInfoHandler
-from benbiohelpers.InputParsing.CheckForNumber import checkForNumber
-from benbiohelpers.InputParsing.ParseToIterable import parseToIterable
-from benbiohelpers.FileSystemHandling.DirectoryHandling import checkDirs, getTempDir
-
- 
-class MismatchesAroundTFBSCounter(ThisInThatCounter):
-
-    def setupOutputDataStratifiers(self):
-        self.outputDataHandler.addEncompassedFeatureStratifier()
-        self.outputDataHandler.addPlaceholderStratifier()
-        self.outputDataHandler.addCustomSupplementalInformationHandler(SimpleColumnSupInfoHandler(
-            outputName = "Motif_Midpoint", relevantData = ENCOMPASSING_DATA, dataCol = 1, removeDups = False
-        ))
-        self.outputDataHandler.addCustomSupplementalInformationHandler(SimpleColumnSupInfoHandler(
-            outputName = "TFBS_Strand", relevantData = ENCOMPASSING_DATA, dataCol = 5, removeDups = False
-        ))
-
-    def setupOutputDataWriter(self):
-        self.outputDataHandler.createOutputDataWriter(self.outputFilePath, omitFinalStratificationCounts = True)
-
-
-def filterAndFormatMismatches(mismatchesByReadFilePath: str, zScoresFilePath, zScoreCutoff = 4,
-                              acceptableReadLengths = range(22,31), acceptableMismatchTypes = ("C>T", "CC>TT"),
-                              outputSuffix = "_TFBS_formatted", addMismatchTypesToName = False):
-    """
-    Filters mismatches by read to acceptable mismatch patterns in reads of valid length at positions with zscores greater than or equal to the given z-score cutoff.
-    The bed entry is also formatted so that it is focused directly on the mismatched position(s) and read sequence is replaced with its length.
[…]

### 2023-07-24 R/PaperFigureGeneration.rmd
Fixed position offsets for HYV plots
Cut site distance and the related incision site were not consistent with previous plots. This is now fixed.

@@
                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "HYV Frequency",
-                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
+                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1, positionOffset = 1,
                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 6,
@@
                         endBasedCheckPositions = -9, displayPValue = FALSE, xAxisLabel = "Mismatch Relative Position",
-                        xAxisOffset = 1, xAxisBreaks = c(-2,-10,-20,-30), xlim = c(-35,-4))
+                        xAxisOffset = 1, positionOffset = 1, xAxisBreaks = c(-2,-10,-20,-30), xlim = c(-35,-4))
 ```

### 2023-07-24 R/5'CutSiteAnalysisDataGeneration.rmd
Add XPC and CSB 5' cut site analysis

@@
 EColiGeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "E_coli_WT", "general_read_sequences")
+CSBGeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "CS-B", "general_read_sequences")
+XPCGeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "XP-C", "general_read_sequences")
 
@@
                 alsoComputeNucFreq = TRUE, alsoCreateSequenceLogoInput = TRUE)
+cutSiteAnalysis("CPD", "all_reps", "1h", "CS-B", CSBGeneralReadSequenceDataDirectory,
+                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombinedReadLengths = TRUE,
+                alsoComputeNucFreq = TRUE, alsoCreateSequenceLogoInput = TRUE)
+cutSiteAnalysis("CPD", "all_reps", "1h", "XP-C", XPCGeneralReadSequenceDataDirectory,
+                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombinedReadLengths = TRUE,
+                alsoComputeNucFreq = TRUE, alsoCreateSequenceLogoInput = TRUE)
 cutSiteAnalysis("6-4", "all_reps", "20min", "NHF1", NHF1GeneralReadSequenceDataDirectory,

### 2023-07-24 R/PaperFigureGeneration.rmd
Added XPC and CSB paper figures
- Added XPC and CSB figures for HYV frequency
- Added XPC and CSB figures for position difference stats (relative 5' and 3' contributions to read length variation)

@@
 CSBSequenceAndPositionDataDirectory = file.path(CSBDataDirectory, "sequence_and_position_analysis")
+CSBGeneralReadSequenceDataDirectory = file.path(CSBDataDirectory, "general_read_sequences")
 
@@
 XPCSequenceAndPositionDataDirectory = file.path(XPCDataDirectory, "sequence_and_position_analysis")
+XPCGeneralReadSequenceDataDirectory = file.path(XPCDataDirectory, "general_read_sequences")
 
@@
 ```
+
+```{r ???_data}
+CSBGeneralReadsCPDSeqFreqAllReps1hFilteredCombined = fread(generateFilePath(
+  CSBGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+  cellType = "CS-B", lesion = "CPD", timepoint = "1h", repitition = "all_reps",
+  sequence = "HYV", filtering = "TGG_filtered", additionalInformation = "combined_read_lengths"
+))
+
+XPCGeneralReadsCPDSeqFreqAllReps1hFilteredCombined = fread(generateFilePath(
+  XPCGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+  cellType = "XP-C", lesion = "CPD", timepoint = "1h", repitition = "all_reps",
+  sequence = "HYV", filtering = "TGG_filtered", additionalInformation = "combined_read_lengths"
+))
+
+CSBCPDGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
+for (i in seq_along(CSBCPDGroupedStatsAllRepsFiltered)) {
+  CSBCPDGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
+    CSBSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
+    cellType = "CS-B", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
+    strandPolarity = names(CSBCPDGroupedStatsAllRepsFiltered)[i]
+  ))
+}
+
+XPCCPDGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
+for (i in seq_along(XPCCPDGroupedStatsAllRepsFiltered)) {
+  XPCCPDGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
+    XPCSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
+    cellType = "XP-C", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
+    strandPolarity = names(XPCCPDGroupedStatsAllRepsFiltered)[i]
+  ))
+}
+```
+
+```{r ???}
+plotSequenceFrequencies(CSBGeneralReadsCPDSeqFreqAllReps1hFilteredCombined[Position <= 7],
+                        title = "CSB CPD 1h All Reps TGG-Filtered General Reads HYV Freq",
+                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
+                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
+                        expansionOffset = 10, backgroundPositions = -9:-4,
+                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
+                        xAxisBreaks = c(-8, 0, 8), ylimMax = 0.6, ylimMaxModifier = 1)
+
+plotSequenceFrequencies(XPCGeneralReadsCPDSeqFreqAllReps1hFilteredCombined[Position <= 7],
+                        title = "XPC CPD 1h All Reps TGG-Filtered General Reads HYV Freq",
+                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
+                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
+                        expansionOffset = 10, backgroundPositions = -9:-4,
+                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
+                        xAxisBreaks = c(-8, 0, 8), ylimMax = 0.6, ylimMaxModifier = 1)
+
+plotGroupedPositionStats(CSBCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                         CSBCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
+                         POS_DIFF, title = "CSB CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
+                         xAxisBreaks = c(22:30), ylim = c(0,5))
+print(paste("3' endpoint variation: ",
+            getThreePrimeVariation(CSBCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                                   CSBCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
+                                   endpointVariation = TRUE)))
+print(paste("3' variation (unweighted): ",
+            getThreePrimeVariation(CSBCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                                   CSBCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"])))
+print(paste("3' variation (weighted): ",
+            getThreePrimeVariation(CSBCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                                   CSBCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
+                                   mismatchData = NHF1CPDMismatchDataAllRepsTGGFiltered$`1h`)))
+
+plotGroupedPositionStats(XPCCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                         XPCCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
+                         POS_DIFF, title = "XPC CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
+                         xAxisBreaks = c(22:30), ylim = c(0,5))
+print(paste("3' endpoint variation: ",
+            getThreePrimeVariation(XPCCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                                   XPCCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
+                                   endpointVariation = TRUE)))
+print(paste("3' variation (unweighted): ",
+            getThreePrimeVariation(XPCCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                                   XPCCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"])))
+print(paste("3' variation (weighted): ",
+            getThreePrimeVariation(XPCCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                                   XPCCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
+                                   mismatchData = NHF1CPDMismatchDataAllRepsTGGFiltered$`1h`)))
+```

### 2023-07-25 R/PaperFigureGeneration.rmd
Incorporated new plots into figures

--- 2023-07-24 R/PaperFigureGeneration.rmd
@@
 ```{r read_figure_S8_data}
+CSBCPDMismatchDataAllRepsTGGFiltered = CSBCPDTimepoints
+for (i in seq_along(CSBCPDMismatchDataAllRepsTGGFiltered)) {
+  CSBCPDMismatchDataAllRepsTGGFiltered[[i]] = fread(generateFilePath(
+    CSBSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+    cellType = "CS-B", lesion = "CPD", timepoint = names(CSBCPDMismatchDataAllRepsTGGFiltered)[i],
+    repitition = "all_reps", filtering = "TGG_filtered"
+  ))
+}
+XPCCPDMismatchDataAllRepsTGGFiltered = XPCCPDTimepoints
+for (i in seq_along(XPCCPDMismatchDataAllRepsTGGFiltered)) {
+  XPCCPDMismatchDataAllRepsTGGFiltered[[i]] = fread(generateFilePath(
+    XPCSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
+    cellType = "XP-C", lesion = "CPD", timepoint = names(XPCCPDMismatchDataAllRepsTGGFiltered)[i],
+    repitition = "all_reps", filtering = "TGG_filtered"
+  ))
+}
+
+CSBCPDMMFreqZScoresAllRepsTGGFiltered = CSBCPDTimepoints
+for (i in seq_along(CSBCPDMMFreqZScoresAllRepsTGGFiltered)) {
+  CSBCPDMMFreqZScoresAllRepsTGGFiltered[[i]] = fread(generateFilePath(
+    CSBSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+    cellType = "CS-B", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
+    timepoint = names(CSBCPDMMFreqZScoresAllRepsTGGFiltered)[i], includedMismatches = c("C>T")
+  ))
+}
+XPCCPDMMFreqZScoresAllRepsTGGFiltered = XPCCPDTimepoints
+for (i in seq_along(XPCCPDMMFreqZScoresAllRepsTGGFiltered)) {
+  XPCCPDMMFreqZScoresAllRepsTGGFiltered[[i]] = fread(generateFilePath(
+    XPCSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
+    cellType = "XP-C", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
+    timepoint = names(XPCCPDMMFreqZScoresAllRepsTGGFiltered)[i], includedMismatches = c("C>T")
+  ))
+}
+
+CSBCPDGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
+for (i in seq_along(CSBCPDGroupedStatsAllRepsFiltered)) {
+  CSBCPDGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
+    CSBSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
+    cellType = "CS-B", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
+    strandPolarity = names(CSBCPDGroupedStatsAllRepsFiltered)[i]
+  ))
+}
+XPCCPDGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
+for (i in seq_along(XPCCPDGroupedStatsAllRepsFiltered)) {
+  XPCCPDGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
+    XPCSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
+    cellType = "XP-C", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
+    strandPolarity = names(XPCCPDGroupedStatsAllRepsFiltered)[i]
+  ))
+}
+```
+
+```{r figure_S8A, fig.width = 5, fig.height = 5}
+plotPositionAcrossTimepointAndReadLength(CSBCPDMismatchDataAllRepsTGGFiltered["1h"], includedTypes = c("C>T"),
+                                         title = "CSB CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
+                                         zScoreTables = CSBCPDMMFreqZScoresAllRepsTGGFiltered,
+                                         yAxisLabel = "Relative C>T Frequency", xAxisBreaks = c(-1,-10,-20,-30))
+```
+```{r figure_S8B, fig.width = 5, fig.height = 5}
+plotPositionAcrossTimepointAndReadLength(XPCCPDMismatchDataAllRepsTGGFiltered["1h"], includedTypes = c("C>T"),
+                                         title = "CSB CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
+                                         zScoreTables = CSBCPDMMFreqZScoresAllRepsTGGFiltered,
+                                         yAxisLabel = "Relative C>T Frequency", xAxisBreaks = c(-1,-10,-20,-30))
+```
+```{r figure_S8C, fig.width = 5, fig.height = 5}
+plotPositionAcrossTimepointAndReadLength(CSBCPDMismatchDataAllRepsTGGFiltered["1h"], includedTypes = c("C>T"),
+                                         title = "CSB CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
+                                         zScoreTables = CSBCPDMMFreqZScoresAllRepsTGGFiltered,
+                                         posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency",
+                                         xAxisBreaks = c(1,10,20,30))
+```
+```{r figure_S8D, fig.width = 5, fig.height = 5}
+plotPositionAcrossTimepointAndReadLength(XPCCPDMismatchDataAllRepsTGGFiltered["1h"], includedTypes = c("C>T"),
+                                         title = "XPC CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
+                                         zScoreTables = XPCCPDMMFreqZScoresAllRepsTGGFiltered,
+                                         posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency",
+                                         xAxisBreaks = c(1,10,20,30))
+```
+```{r figure_S8E, fig.width = 7.5, fig.height = 5}
+plotGroupedPositionStats(CSBCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                         CSBCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
+                         POS_DIFF, title = "CSB CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
+                         xAxisBreaks = c(22:30), ylim = c(0,5))
+print(paste("3' endpoint variation: ",
+            getThreePrimeVariation(CSBCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                                   CSBCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
+                                   endpointVariation = TRUE)))
+print(paste("3' variation (unweighted): ",
+            getThreePrimeVariation(CSBCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                                   CSBCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"])))
+print(paste("3' variation (weighted): ",
+            getThreePrimeVariation(CSBCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                                   CSBCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
+                                   mismatchData = NHF1CPDMismatchDataAllRepsTGGFiltered$`1h`)))
+```
+```{r figure_S8F, fig.width = 7.5, fig.height = 5}
+plotGroupedPositionStats(XPCCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                         XPCCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
+                         POS_DIFF, title = "XPC CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
+                         xAxisBreaks = c(22:30), ylim = c(0,5))
+print(paste("3' endpoint variation: ",
+            getThreePrimeVariation(XPCCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                                   XPCCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
+                                   endpointVariation = TRUE)))
+print(paste("3' variation (unweighted): ",
+            getThreePrimeVariation(XPCCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                                   XPCCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"])))
+print(paste("3' variation (weighted): ",
+            getThreePrimeVariation(XPCCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
+                                   XPCCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
+                                   mismatchData = NHF1CPDMismatchDataAllRepsTGGFiltered$`1h`)))
+```
+
+```{r read_figure_S9_data}
 yeastCPDMismatchDataAllRepsFiltered = yeastCPDTimepoints
@@
 
-```{r figure_S8A, fig.width = 5, fig.height = 5}
+```{r figure_S9A, fig.width = 5, fig.height = 5}
 plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["20min"], includedTypes = c("C>T"),
@@
 ```
-```{r figure_S8B, fig.width = 5, fig.height = 5}
+```{r figure_S9B, fig.width = 5, fig.height = 5}
 plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["20min"], includedTypes = c("C>T"),
@@
 ```
-```{r figure_S8C, fig.width = 7.5, fig.height = 5}
+```{r figure_S9C, fig.width = 7.5, fig.height = 5}
 plotGroupedPositionStats(yeastCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "20min"],
@@
 
-```{r read_figure_S9_data}
+```{r read_figure_S10_data}
 NHF1GeneralReadsSixFourSeqFreqAllReps20minFilteredCombined = fread(generateFilePath(
@@
 ))
-```
-
-```{r figure_S9, fig.width = 5, fig.height = 4}
+CSBGeneralReadsCPDSeqFreqAllReps1hFilteredCombined = fread(generateFilePath(
+  CSBGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+  cellType = "CS-B", lesion = "CPD", timepoint = "1h", repitition = "all_reps",
+  sequence = "HYV", filtering = "TGG_filtered", additionalInformation = "combined_read_lengths"
+))
+XPCGeneralReadsCPDSeqFreqAllReps1hFilteredCombined = fread(generateFilePath(
+  XPCGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
+  cellType = "XP-C", lesion = "CPD", timepoint = "1h", repitition = "all_reps",
+  sequence = "HYV", filtering = "TGG_filtered", additionalInformation = "combined_read_lengths"
+))
+```
+
+```{r figure_S10, fig.width = 5, fig.height = 4}
 plotSequenceFrequencies(NHF1GeneralReadsSixFourSeqFreqAllReps20minFilteredCombined[Position <= 7],
@@
                         xAxisOffset = 1, ylimMax = 0.6, ylimMaxModifier = 1)
-```
-
-```{r read_figure_S10_data}
+plotSequenceFrequencies(CSBGeneralReadsCPDSeqFreqAllReps1hFilteredCombined[Position <= 7],
+                        title = "CSB CPD 1h All Reps TGG-Filtered General Reads HYV Freq",
+                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
+                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
+                        expansionOffset = 10, backgroundPositions = -9:-4,
+                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
+                        xAxisBreaks = c(-8, 0, 8), ylimMax = 0.6, ylimMaxModifier = 1)
+plotSequenceFrequencies(XPCGeneralReadsCPDSeqFreqAllReps1hFilteredCombined[Position <= 7],
+                        title = "XPC CPD 1h All Reps TGG-Filtered General Reads HYV Freq",
+                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
+                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
+                        expansionOffset = 10, backgroundPositions = -9:-4,
+                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
+                        xAxisBreaks = c(-8, 0, 8), ylimMax = 0.6, ylimMaxModifier = 1)
+```
+
+```{r read_figure_S11_data}
 NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
@@
 
-```{r figure_S10, fig.width = 6.5, fig.height = 6}
+```{r figure_S11, fig.width = 6.5, fig.height = 6}
 plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
@@
 
-```{r read_figure_S11_data}
+```{r read_figure_S12_data}
 NHF1CPDGGtoAAMismatchDataAllRepsFiltered = NHF1CPDTimepoints
@@
 
-```{r figure_S11, fig.width = 5, fig.height = 5.5}
+```{r figure_S12, fig.width = 5, fig.height = 5.5}
 plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered["1h"],

### 2023-07-27 R/DeaminationFeatureRelativeAnalysis.R
Various improvements to feature relative analysis
- Counts/mean data is sorted before it is returned.
- Counts data is adjusted to include positions with 0 counts before being returned.
- Many updates to plotting, including the ability to smooth data, plot counts instead of relative frequency, plot a mirror image of the negative position values (to highlight asymmetry), plot as a line instead of bar graph, and other minor changes. Wow!

@@ -11,6 +11,11 @@ FEATURE_RELATIVE_THREE_PRIME_CUT_SITE = "Feature_Relative_Three_Prime_Cut_Site"
 FEATURE_RELATIVE_FIVE_PRIME_CUT_SITE = "Feature_Relative_Five_Prime_Cut_Site"
 MEAN_THREE_PRIME_CUT_SITE_DISTANCE = "Mean_Three_Prime_Cut_Site_Distance"
 MEAN_FIVE_PRIME_CUT_SITE_DISTANCE = "Mean_Five_Prime_Cut_Site_Distance"
+COUNTS = "N"
+RELATIVE_FREQUENCY = "Relative_Frequency"
+
+LINE = "line"
+BAR = "bar"
 
 
 
@@ -98,39 +103,54 @@ getFeatureRelativeCounts = function(table, dataType, strandAlign = FALSE) {
     }
   } else stop("Unrecognized value for feature parameter")
 
-  if (strandAlign) {
-
-    if (dataType == MEAN_THREE_PRIME_CUT_SITE_DISTANCE || dataType == MEAN_FIVE_PRIME_CUT_SITE_DISTANCE) {
-      positionCol = FEATURE_RELATIVE_POSITION
-      dataCol = dataType
-    } else {
-      positionCol = dataType
-      dataCol = "N"
-    }
-
-    return(table[,c(..positionCol, ..dataCol)])
-
+  if (dataType == MEAN_THREE_PRIME_CUT_SITE_DISTANCE || dataType == MEAN_FIVE_PRIME_CUT_SITE_DISTANCE) {
+    positionCol = FEATURE_RELATIVE_POSITION
+    dataCol = dataType
   } else {
-    return(table)
+    positionCol = dataType
+    dataCol = "N"
+  }
+
+  fullRange = data.table(Position = min(table[[positionCol]]):max(table[[positionCol]]))
+  table = merge.data.table(table, fullRange, by.x = positionCol, by.y = "Position", all = TRUE)
+  if (dataCol == "N") {table[is.na(N), N := 0]}
+
+  if (strandAlign) {
+    return(table[order(table[[positionCol]]),c(..positionCol, ..dataCol)])
+  } else {
+    return(table[order(table[[positionCol]])])
   }
 
 }
 
 
 # This function plots counts of feature-relative features, as specified by the "feature" parameter.
-plotFeatureRelativeCounts = function(countsTable, countsDataType,
[…]

### 2023-07-27 R/NHF1_FeatureRelativeDataGeneration.Rmd
Updated feature analysis notebooks
New analysis based on changes to underlying pipeline. (Still in flux)

@@
 
+      for (bool in c(TRUE, FALSE)) {
+
+        if (bool) {strandInfoText = "_strand_aligned"} else {strandInfoText = ""}
+
         fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = FEATURE_RELATIVE_POSITION,
-                                      strandAlign = TRUE),
-             sep = '\t', file = generateFilePath(
+                                        strandAlign = bool),
+               sep = '\t', na = "NA", file = generateFilePath(
           featureRelativeDataDirectory, dataTypeStrings$featureRelativePositionCounts, ".tsv",
@@
           timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
-        additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related")
+          additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related",strandInfoText)
         ))
@@
         fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = FEATURE_RELATIVE_THREE_PRIME_CUT_SITE,
-                                      strandAlign = TRUE),
-             sep = '\t', file = generateFilePath(
+                                        strandAlign = bool),
+               sep = '\t', na = "NA", file = generateFilePath(
           featureRelativeDataDirectory, dataTypeStrings$featureRelativeCutSiteCounts, ".tsv", strandPolarity = THREE_PRIME,
@@
         fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = FEATURE_RELATIVE_FIVE_PRIME_CUT_SITE,
-                                      strandAlign = TRUE),
-             sep = '\t', file = generateFilePath(
+                                        strandAlign = bool),
+               sep = '\t', na = "NA", file = generateFilePath(
           featureRelativeDataDirectory, dataTypeStrings$featureRelativeCutSiteCounts, ".tsv", strandPolarity = FIVE_PRIME,
@@
         fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
-                                      strandAlign = TRUE),
-             sep = '\t', file = generateFilePath(
+                                        strandAlign = bool),
+               sep = '\t', na = "NA", file = generateFilePath(
           featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = THREE_PRIME,
@@
         fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = MEAN_FIVE_PRIME_CUT_SITE_DISTANCE,
-                                      strandAlign = TRUE),
-             sep = '\t', file = generateFilePath(
+                                        strandAlign = bool),
+               sep = '\t', na = "NA", file = generateFilePath(
           featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = FIVE_PRIME,
@@
   }
+}
 

### 2023-07-27 R/NHF1_FeatureRelativeFigureGeneration.Rmd
Updated feature analysis notebooks
New analysis based on changes to underlying pipeline. (Still in flux)

@@
         timepoint = CPDTimepoint, includedMismatches = mismatchType,
-        additionalInformation = paste0(tfbs,"_related")
+        additionalInformation = paste0(tfbs,"_related_strand_aligned")
       ))
@@
       plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION,
+                                plotCountsMirror = TRUE, smoothCountsData = FALSE, mainYAxisLabel = "C>T Mismatches",
+                                countsPlotColor = "black", countsMirrorColor = "gold2",
                                 title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"))
 
-      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION, meanThreePrimeCutSiteDistanceData,
-                                THREE_PRIME, title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"))
-
-      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION, meanFivePrimeCutSiteDistanceData,
-                                FIVE_PRIME, title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"))
+      plotFeatureRelativeCounts(meanThreePrimeCutSiteDistanceData, FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
+                                smoothCountsData = FALSE, countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
+                                meanCutSiteDistanceTable = meanFivePrimeCutSiteDistanceData,
+                                cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
+                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"))
 
@@
         timepoint = CPDTimepoint, includedMismatches = mismatchType,
-        additionalInformation = paste0(nucMap,"_related")
+        additionalInformation = paste0(nucMap,"_related_strand_aligned")
       ))
@@
       plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION,
+                                plotCountsMirror = TRUE, smoothCountsData = FALSE, mainYAxisLabel = "C>T Mismatches",
                                 title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"))
 
-      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION, meanThreePrimeCutSiteDistanceData,
-                                THREE_PRIME, title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"))
-
-      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION, meanFivePrimeCutSiteDistanceData,
-                                FIVE_PRIME, title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"))
+      plotFeatureRelativeCounts(meanThreePrimeCutSiteDistanceData, FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
+                                smoothCountsData = FALSE, countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
+                                meanCutSiteDistanceTable = meanFivePrimeCutSiteDistanceData,
+                                cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
+                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"))
 

### 2023-07-28 R/CutSiteCorrelationAnalysis.rmd
Create CutSiteCorrelationAnalysis.rmd
An R notebook for examining correlations between cut site distances (3' vs 5', relative to the lesion)

---
title: "5'CutSiteAnalysisDataGeneration"
author: "Ben MOrledge-Hampton"
date: '2022-07-14'
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

```{r setup_chunk}
library(knitr)

expansionOffset = 10
filtering = "TGG_filtered"

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
}

if (is.na(bioinformaticsDirectory)) stop("No bioinformatics directory given.")

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data")
NHF1MismatchesByReadDirectory = file.path(deaminationDataDirectory, "NHF1", "mismatches_by_read")

humanReadMinMax = c(22, 30)
drosophilaReadMinMax = c(23, 32)
arabidopsisReadMinMax = c(24, 30)
yeastReadMinMax = c(22, 25)
EColiReadMinMax = c(11, 13)
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationAnchoredExcisionSiteAnalysis.R"))
```

```{r define_all_that_and_a_bag_of_chips_function}
cutSiteCorrelationAnalysis = function(lesion, repetition, timepoint, cellType, directory,
                                      includedMismatches = c("CC>TT")) {
  mismatchesByRead = fread(generateFilePath(
    directory, dataTypeStrings$mismatchesByReadRelationFormatted , ".bed",
    cellType = cellType, lesion = lesion, timepoint = timepoint,
    repitition = repetition, filtering = filtering, includedMismatches = includedMismatches
  ))
  colnames(mismatchesByRead) = c("Chromosome", "Mismatch_Pos_0", "Mismatch_Pos_1", "Three_Prime_Relative_Mismatch_Pos",
                                 "Mismatch_Type", "Mismatch_Strand", "Read_Length")

  mismatchesByRead[,Three_Prime_Cut_Site_Distance := abs(Three_Prime_Relative_Mismatch_Pos)]
  mismatchesByRead[,Five_Prime_Cut_Site_Distance := Read_Length-abs(Three_Prime_Relative_Mismatch_Pos)+1]

  return(cor.test(mismatchesByRead$Three_Prime_Cut_Site_Distance,
                 mismatchesByRead$Five_Prime_Cut_Site_Distance, method = "pearson"))

  #return(mismatchesByRead[,.(Three_Prime_Cut_Site_Distance, Five_Prime_Cut_Site_Distance)])
}
```

```{r compute_and_write_sequence_frequencies}
print(cutSiteCorrelationAnalysis("CPD", "all_reps", "1h", "NHF1", NHF1MismatchesByReadDirectory))
```

### 2023-07-28 R/CutSiteCorrelationAnalysis.R
Create CutSiteCorrelationAnalysis.R
A suite of functions for analyzing potential correlations between cut site distances

@@ -1,0 +1,44 @@
+library(data.table)
+library(ggplot2)
+
+# Default text scaling
+defaultTextScaling = theme(plot.title = element_text(size = 22, hjust = 0.5),
+                           axis.title = element_text(size = 22), axis.text = element_text(size = 18, color = "black"),
+                           legend.title = element_text(size = 22), legend.text = element_text(size = 18),
+                           strip.text = element_text(size = 22))
+
+# Blank background theme
+blankBackground = theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
+                        panel.background = element_blank(), axis.line = element_line(colour = "black"))
+
+
+getPairedCutSiteDistances = function(mismatchesByRead) {
+  # NOTE: Expects mismatches filtered and formatted from the FormatMismatchesForRelation Python script
+  colnames(mismatchesByRead) = c("Chromosome", "Mismatch_Pos_0", "Mismatch_Pos_1", "Three_Prime_Relative_Mismatch_Pos",
+                                 "Mismatch_Type", "Mismatch_Strand", "Read_Length")
+
+  mismatchesByRead[,Three_Prime_Cut_Site_Distance := abs(Three_Prime_Relative_Mismatch_Pos)]
+  mismatchesByRead[,Five_Prime_Cut_Site_Distance := Read_Length-abs(Three_Prime_Relative_Mismatch_Pos)+1]
+
+  return(mismatchesByRead[,.(Three_Prime_Cut_Site_Distance, Five_Prime_Cut_Site_Distance)])
+
+}
+
+getCorrelationResults = function(pairedCutSiteDistances) {
+
+  return(cor.test(pairedCutSiteDistances$Three_Prime_Cut_Site_Distance,
+                  pairedCutSiteDistances$Five_Prime_Cut_Site_Distance, method = "pearson"))
+
+}
+
+plotPairedCutSiteDistances = function(pairedCutSiteDistances,
+                                       xAxisLabel = "3' Cut Site Distance", yAxisLabel = "5' CutSite Distance",
+                                       title = "Paired Cut Site Distances") {
+
+  plot = ggplot(pairedCutSiteDistances, aes(x = Three_Prime_Cut_Site_Distance, y = Five_Prime_Cut_Site_Distance)) +
+    geom_count() + blankBackground + defaultTextScaling +
+    labs(title = title, x = xAxisLabel, y = yAxisLabel)
+
+  print(plot)
+
+}

### 2023-07-28 R/CutSiteCorrelationDataGeneration.rmd
Split correlation analysis for data and figure gen
- Utilized new suite of cut site correlation analysis functions
- may need to further stratify this by cell type at some point...

---
title: "5'CutSiteAnalysisDataGeneration"
author: "Ben MOrledge-Hampton"
date: '2022-07-14'
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

```{r setup_chunk}
library(knitr)

expansionOffset = 10
filtering = "TGG_filtered"

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
}

if (is.na(bioinformaticsDirectory)) stop("No bioinformatics directory given.")

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data")
NHF1MismatchesByReadDirectory = file.path(deaminationDataDirectory, "NHF1", "mismatches_by_read")
NHF1CutSiteCorrelationDirectory = file.path(deaminationDataDirectory, "NHF1", "cut_site_correlation")
dir.create(NHF1CutSiteCorrelationDirectory, showWarnings = FALSE, recursive = TRUE)
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "CutSiteCorrelationAnalysis.R"))
```

```{r define_all_that_and_a_bag_of_chips_function}
cutSiteCorrelationAnalysisDataGeneration = function(lesion, repetition, timepoint, cellType, inputDirectory, outputDirectory,
                                                    includedMismatches = c("CC>TT")) {
  mismatchesByRead = fread(generateFilePath(
    inputDirectory, dataTypeStrings$mismatchesByReadRelationFormatted , ".bed",
    cellType = cellType, lesion = lesion, timepoint = timepoint,
    repitition = repetition, filtering = filtering, includedMismatches = includedMismatches
  ))
  fwrite(getPairedCutSiteDistances(mismatchesByRead),  sep = '\t', file = generateFilePath(
    outputDirectory, dataTypeStrings$pairedCutSiteDistances , ".tsv",
    cellType = cellType, lesion = lesion, timepoint = timepoint,
    repitition = repetition, filtering = filtering, includedMismatches = includedMismatches
  ))

}
```

```{r generate_cut_site_correlation_data}
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory)
```

### 2023-07-28 R/CutSiteCorrelationFigureGeneration.rmd
Split correlation analysis for data and figure gen
- Utilized new suite of cut site correlation analysis functions
- may need to further stratify this by cell type at some point...

--- 2023-07-28 R/CutSiteCorrelationDataGeneration.rmd
@@
 
+opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
+               fig.path = paste0(file.path("deamination_analysis_output","combined",
+                                           paste(c(filtering,"correlation_analysis"), collapse = '_')),
+                                 .Platform$file.sep))
+
 deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data")
-NHF1MismatchesByReadDirectory = file.path(deaminationDataDirectory, "NHF1", "mismatches_by_read")
 NHF1CutSiteCorrelationDirectory = file.path(deaminationDataDirectory, "NHF1", "cut_site_correlation")
-dir.create(NHF1CutSiteCorrelationDirectory, showWarnings = FALSE, recursive = TRUE)
 ```
@@
 ```{r define_all_that_and_a_bag_of_chips_function}
-cutSiteCorrelationAnalysisDataGeneration = function(lesion, repetition, timepoint, cellType, inputDirectory, outputDirectory,
+cutSiteCorrelationAnalysisFigureGeneration = function(lesion, repetition, timepoint, cellType, directory,
                                                     includedMismatches = c("CC>TT")) {
-  mismatchesByRead = fread(generateFilePath(
-    inputDirectory, dataTypeStrings$mismatchesByReadRelationFormatted , ".bed",
-    cellType = cellType, lesion = lesion, timepoint = timepoint,
-    repitition = repetition, filtering = filtering, includedMismatches = includedMismatches
-  ))
-  fwrite(getPairedCutSiteDistances(mismatchesByRead),  sep = '\t', file = generateFilePath(
-    outputDirectory, dataTypeStrings$pairedCutSiteDistances , ".tsv",
+  pairedCutSiteDistances = fread(generateFilePath(
+    directory, dataTypeStrings$pairedCutSiteDistances , ".tsv",
     cellType = cellType, lesion = lesion, timepoint = timepoint,
@@
 
+  print(getCorrelationResults(pairedCutSiteDistances))
+  plotPairedCutSiteDistances(pairedCutSiteDistances,
+                             title = paste(cellType, lesion, timepoint, includedMismatches, "Cut Site Correlation"))
+
 }
@@
 
-```{r generate_cut_site_correlation_data}
-cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
-                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory)
+```{r generate_cut_site_correlation_figures}
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory)
 ```

### 2023-07-28 python/FormatMismatchesForRelation.py
Changed default options for ease of use

@@ -9,7 +9,7 @@ from benbiohelpers.InputParsing.ParseToIterable import parseToIterable
 
 def formatMismatchesForRelation(mismatchesByReadFilePath: str, zScoresFilePath, zScoreCutoff = 4,
                                 acceptableReadLengths = range(22,31), acceptableMismatchTypes: List[str] = ["C>T", "CC>TT"],
-                                outputSuffix = "_relation_formatted", addMismatchTypesToName = True, outputToTmpDir = True,
+                                outputSuffix = "_relation_formatted", addMismatchTypesToName = True, outputToTmpDir = False,
                                 sortOutput = True, verbose = False):
     """
     Filters mismatches by read to acceptable mismatch patterns in reads of valid length at positions with zscores greater than or equal to the given z-score cutoff.

### 2023-07-28 python/FormatMismatchesForRelation.py
Adding 'N' filtering

@@ -13,6 +13,7 @@ def formatMismatchesForRelation(mismatchesByReadFilePath: str, zScoresFilePath, 
                                 sortOutput = True, verbose = False):
     """
     Filters mismatches by read to acceptable mismatch patterns in reads of valid length at positions with zscores greater than or equal to the given z-score cutoff.
+    Also filter reads with sequences containing 'N' nucleotides (to keep things consistent with R pipeline).
     The bed entry is also formatted so that it is focused directly on the mismatched position(s) and read sequence is replaced with its length.
     The resulting file is sorted, first by chromosome, then by start position and end position.
     The output suffix is appended to the new file path just after "mismatches_by_read".
@@ -68,6 +69,8 @@ def formatMismatchesForRelation(mismatchesByReadFilePath: str, zScoresFilePath, 
 
             position = float(splitLine[3])
             if not zscoreDictionary[readLength][position]: continue
+
+            if 'N' in splitLine[6]: continue
 
             # Recenter the coordinates on the mismatch (0-based)
             if splitLine[5] == '+': mismatchCoordinate = int(splitLine[2]) + position

### 2023-07-28 R/DeaminationFeatureRelativeAnalysis.R
Added statistics for mean cut site distance
Standard deviation and standard error of the mean are now included in the outputted tables.

@@ -86,21 +86,27 @@ getFeatureRelativeCounts = function(table, dataType, strandAlign = FALSE) {
   } else if (dataType == MEAN_THREE_PRIME_CUT_SITE_DISTANCE) {
     if (strandAlign) {
       table[Same_Strand == FALSE, Feature_Relative_Mismatch_Pos := -Feature_Relative_Mismatch_Pos]
-      table = table[,.(Mean_Three_Prime_Cut_Site_Distance = mean(abs(Read_Relative_Mismatch_Pos))),
+      table = table[,.(Mean_Three_Prime_Cut_Site_Distance = mean(abs(Read_Relative_Mismatch_Pos)),
+                       Standard_Deviation = sd(abs(Read_Relative_Mismatch_Pos)), N = .N),
                     by = list(Feature_Relative_Mismatch_Pos)]
     } else {
-      table = table[,.(Mean_Three_Prime_Cut_Site_Distance = mean(abs(Read_Relative_Mismatch_Pos))),
+      table = table[,.(Mean_Three_Prime_Cut_Site_Distance = mean(abs(Read_Relative_Mismatch_Pos)),
+                       Standard_Deviation = sd(abs(Read_Relative_Mismatch_Pos)), N = .N),
                     by = list(Feature_Relative_Mismatch_Pos, Same_Strand)]
     }
+    table[,Standard_Error := Standard_Deviation/sqrt(N)]
   } else if (dataType == MEAN_FIVE_PRIME_CUT_SITE_DISTANCE) {
     if (strandAlign) {
       table[Same_Strand == FALSE, Feature_Relative_Mismatch_Pos := -Feature_Relative_Mismatch_Pos]
-      table = table[,.(Mean_Five_Prime_Cut_Site_Distance = mean(Read_Length-abs(Read_Relative_Mismatch_Pos)+1)),
+      table = table[,.(Mean_Five_Prime_Cut_Site_Distance = mean(Read_Length-abs(Read_Relative_Mismatch_Pos)+1),
+                       Standard_Deviation = sd(Read_Length-abs(Read_Relative_Mismatch_Pos)+1), N = .N),
                     by = list(Feature_Relative_Mismatch_Pos)]
     } else {
-      table = table[,.(Mean_Five_Prime_Cut_Site_Distance = mean(Read_Length-abs(Read_Relative_Mismatch_Pos)+1)),
[…]

### 2023-07-28 R/DeaminationFeatureRelativeAnalysis.R
Added xAxisLabel option to relation plotting

@@ -133,7 +133,7 @@ plotFeatureRelativeCounts = function(countsTable, countsDataType, countsYVar = C
                                      meanCutSiteDistanceTable = NULL, cutSiteStrandPolarity = NULL,
                                      smoothMeanCutSiteDistance = FALSE,
                                      title = NULL, sameStrand = NULL, xlim = NULL, xAxisBreaks = waiver(),
-                                     mainYAxisMin = NULL, mainYAxisMax = NULL, mainYAxisLabel = NULL,
+                                     mainYAxisMin = NULL, mainYAxisMax = NULL, xAxisLabel = NULL, mainYAxisLabel = NULL,
                                      meanCutSiteDistanceMin = NULL, meanCutSiteDistanceMax = NULL,
                                      secondaryAxisBreaks = waiver()) {
 
@@ -155,13 +155,13 @@ plotFeatureRelativeCounts = function(countsTable, countsDataType, countsYVar = C
   }
 
   if (countsDataType == FEATURE_RELATIVE_POSITION) {
-    xAxisLabel = "Feature Relative Position"
+    if (is.null(xAxisLabel)) xAxisLabel = "Feature Relative Position"
     if (is.null(title)) title = "Feature Relative Mismatch Position Frequencies"
   } else if (countsDataType == FEATURE_RELATIVE_THREE_PRIME_CUT_SITE){
-    xAxisLabel = "Feature Relative 3' Cut Site"
+    if (is.null(xAxisLabel)) xAxisLabel = "Feature Relative 3' Cut Site"
     if (is.null(title)) title = "Feature Relative 3' Cut Site Position Frequencies"
   } else if (countsDataType == FEATURE_RELATIVE_FIVE_PRIME_CUT_SITE) {
-    xAxisLabel = "Feature Relative 5' Cut Site"
+    if (is.null(xAxisLabel)) xAxisLabel = "Feature Relative 5' Cut Site"
     if (is.null(title)) title = "Feature Relative 5' Cut Site Position Frequencies"
   } else stop("Unrecognized value for data type parameter")
 
@@ -200,12 +200,13 @@ plotFeatureRelativeCounts = function(countsTable, countsDataType, countsYVar = C
   plot = ggplot(countsTable, aes(x = !!sym(countsDataType), y = !!sym(countsYVar)))
 
   if (countsPlotType == BAR) {
[…]

### 2023-07-28 R/NHF1_FeatureRelativeDataGeneration.Rmd
Included new mismatch types in relation data gen

@@
 CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
-mismatchTypes = list(`C>T_CC>TT` = NULL)
+mismatchTypes = list(`C>T` = NULL, `CC>TT` = NULL, `C>T_CC>TT` = NULL)
 features = list(`CTCF_known1_DHS` = NULL, `CTCF_known1_non-DHS` = NULL, `hg19_mnase_all` = NULL)

### 2023-07-28 R/NHF1_FeatureRelativeFigureGeneration.Rmd
More changes to relation figure gen
- New x-axis cutoffs and labels.
- New periodicity analyses

@@
 CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
-mismatchTypes = list(`C>T_CC>TT` = NULL)
+mismatchTypes = list(`C>T` = NULL, `CC>TT` = NULL, `C>T_CC>TT` = NULL)
 TFBSs = list(`CTCF_known1_DHS` = NULL, `CTCF_known1_non-DHS` = NULL)
@@
                                 countsPlotColor = "black", countsMirrorColor = "gold2",
-                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"))
+                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"),
+                                xAxisLabel = "TFBS-Relative Position")
 
@@
                                 cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
-                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"))
+                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"),
+                                xAxisLabel = "TFBS-Relative Position")
 
@@
                                 plotCountsMirror = TRUE, smoothCountsData = FALSE, mainYAxisLabel = "C>T Mismatches",
-                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"))
+                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"),
+                                xAxisLabel = "Dyad-Relative Position", xlim = c(0,300))
 
@@
                                 cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
-                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"))
+                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"),
+                                xAxisLabel = "Dyad-Relative Position", xlim = c(-100, 100))
+
+      plotFeatureRelativeCounts(meanThreePrimeCutSiteDistanceData, FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
+                                smoothCountsData = FALSE, countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
+                                meanCutSiteDistanceTable = meanFivePrimeCutSiteDistanceData,
+                                cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
+                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"),
+                                xAxisLabel = "Dyad-Relative Position", xlim = c(0,300))
 
@@
 
-```{r periodicity analysis}
+```{r single_nucleosome_periodicity_analysis}
 library(mutperiodR)
@@
 ```
+
+```{r linker_region_periodicity_analysis}
+library(mutperiodR)
+
+for (CPDTimepoint in names(CPDTimepoints)) {
+  for (mismatchType in names(mismatchTypes)) {
+    for (nucMap in names(nucMaps)) {
+
+        meanThreePrimeCutSiteDistanceData = fread(generateFilePath(
+          featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = THREE_PRIME,
+          cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
+          timepoint = CPDTimepoint, includedMismatches = mismatchType,
+          additionalInformation = paste0(nucMap,"_related")
+        ))
+
+        meanFivePrimeCutSiteDistanceData = fread(generateFilePath(
+          featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = FIVE_PRIME,
+          cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
+          timepoint = CPDTimepoint, includedMismatches = mismatchType,
+          additionalInformation = paste0(nucMap,"_related")
+        ))
+
+        print(paste(cellType, CPDTimepoint, mismatchType, nucMap, ":"))
+
+        print("Mean 3` cut site distance:")
+        print("  pre-linker:")
+        periodAndSNR = getPeakPeriodicityAndSNR(
+          meanThreePrimeCutSiteDistanceData[
+            Feature_Relative_Mismatch_Pos < -70 & Feature_Relative_Mismatch_Pos > -120,
+            Mean_Three_Prime_Cut_Site_Distance], 5, 25)
+        print(paste("    Peak Period:",periodAndSNR[1]))
+        print(paste("    SNR:",periodAndSNR[2]))
+
+        print("  post-linker:")
+        periodAndSNR = getPeakPeriodicityAndSNR(
+          meanThreePrimeCutSiteDistanceData[
+            Feature_Relative_Mismatch_Pos > 70 & Feature_Relative_Mismatch_Pos < 120,
+            Mean_Three_Prime_Cut_Site_Distance], 5, 25)
+        print(paste("    Peak Period:",periodAndSNR[1]))
+        print(paste("    SNR:",periodAndSNR[2]))
+
+        print("Mean 5` cut site distance:")
+        print("  pre-linker:")
+        periodAndSNR = getPeakPeriodicityAndSNR(
+          meanFivePrimeCutSiteDistanceData[
+            Feature_Relative_Mismatch_Pos < -70 & Feature_Relative_Mismatch_Pos > -120,
+            Mean_Five_Prime_Cut_Site_Distance], 5, 25)
+        print(paste("    Peak Period:",periodAndSNR[1]))
+        print(paste("    SNR:",periodAndSNR[2]))
+
+        print("  post-linker:")
+        periodAndSNR = getPeakPeriodicityAndSNR(
+          meanFivePrimeCutSiteDistanceData[
+            Feature_Relative_Mismatch_Pos > 70 & Feature_Relative_Mismatch_Pos < 120,
+            Mean_Five_Prime_Cut_Site_Distance], 5, 25)
+        print(paste("    Peak Period:",periodAndSNR[1]))
+        print(paste("    SNR:",periodAndSNR[2]))
+
+        print('')
+    }
+  }
+}
+
+```

### 2023-07-28 R/UsefulFileSystemFunctions.R
Added paired cut site distances data type string

@@ -19,7 +19,8 @@ dataTypeStrings =
        featureRelativeData = "feature_relative_data",
        featureRelativePositionCounts = "feature_relative_position_counts",
        featureRelativeCutSiteCounts = "feature_relative_cut_site_counts",
-       featureRelativeMeanCutSiteDistance = "feature_relative_mean_cut_site_distance"
+       featureRelativeMeanCutSiteDistance = "feature_relative_mean_cut_site_distance",
+       pairedCutSiteDistances = "paired_cut_site_distances"
        )
 
 generateFilePath = function(directory, dataTypeString, fileExtension,

### 2023-07-31 R/CutSiteCorrelationDataGeneration.rmd
Improved cut site correlation analysis
- Included option to use normal mismatches by reads files with minimal filtering
- Included analysis of reads with shuffled 3' cut site distances as a negative control (i.e., a sanity check).

@@
 cutSiteCorrelationAnalysisDataGeneration = function(lesion, repetition, timepoint, cellType, inputDirectory, outputDirectory,
-                                                    includedMismatches = c("CC>TT")) {
+                                                    includedMismatches = c("CC>TT"), filteredAndFormattedInput = TRUE,
+                                                    filePathIncludedMismatches = NA) {
+
+  if (length(filePathIncludedMismatches) > 0 && is.na(filePathIncludedMismatches)) {
+    filePathIncludedMismatches = includedMismatches
+  }
+
+  if (filteredAndFormattedInput) {
+    inputType = dataTypeStrings$mismatchesByReadRelationFormatted
+  } else {
+    inputType = dataTypeStrings$mismatchesByRead
+  }
+
   mismatchesByRead = fread(generateFilePath(
-    inputDirectory, dataTypeStrings$mismatchesByReadRelationFormatted , ".bed",
+    inputDirectory, inputType, ".bed",
     cellType = cellType, lesion = lesion, timepoint = timepoint,
-    repitition = repetition, filtering = filtering, includedMismatches = includedMismatches
+    repitition = repetition, filtering = filtering, includedMismatches = filePathIncludedMismatches
   ))
-  fwrite(getPairedCutSiteDistances(mismatchesByRead),  sep = '\t', file = generateFilePath(
+
+  if (filteredAndFormattedInput) {
+    additionalInformation = character()
+  } else {
+    additionalInformation = "minimal_filtering"
+  }
+
+  if (length(filePathIncludedMismatches) != length(includedMismatches)) {
+    mismatchesByRead = mismatchesByRead[V5 %in% includedMismatches]
+    mismatchesByRead[,V4:=as.numeric(V4)]
+  }
+
+  fwrite(getPairedCutSiteDistances(mismatchesByRead, filteredAndFormattedInput), sep = '\t', file = generateFilePath(
     outputDirectory, dataTypeStrings$pairedCutSiteDistances , ".tsv",
     cellType = cellType, lesion = lesion, timepoint = timepoint,
-    repitition = repetition, filtering = filtering, includedMismatches = includedMismatches
+    repitition = repetition, filtering = filtering, includedMismatches = includedMismatches,
+    additionalInformation = additionalInformation
   ))
@@
                                          NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory)
+cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
+                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
+                                         includedMismatches = "C>T")
+cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
+                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
+                                         includedMismatches = "C>T", filteredAndFormattedInput = FALSE,
+                                         filePathIncludedMismatches = character())
+cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
+                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
+                                         includedMismatches = "CC>TT", filteredAndFormattedInput = FALSE)
 ```

### 2023-07-31 R/CutSiteCorrelationFigureGeneration.rmd
Improved cut site correlation analysis
- Included option to use normal mismatches by reads files with minimal filtering
- Included analysis of reads with shuffled 3' cut site distances as a negative control (i.e., a sanity check).

@@
 cutSiteCorrelationAnalysisFigureGeneration = function(lesion, repetition, timepoint, cellType, directory,
-                                                    includedMismatches = c("CC>TT")) {
+                                                      includedMismatches = c("CC>TT"), filteredAndFormattedInput = TRUE,
+                                                      shuffle = FALSE) {
+
+  if (filteredAndFormattedInput) {
+    additionalInformation = character()
+  } else {
+    additionalInformation = "minimal_filtering"
+  }
+
   pairedCutSiteDistances = fread(generateFilePath(
@@
     cellType = cellType, lesion = lesion, timepoint = timepoint,
-    repitition = repetition, filtering = filtering, includedMismatches = includedMismatches
+    repitition = repetition, filtering = filtering, includedMismatches = includedMismatches,
+    additionalInformation = additionalInformation
   ))
 
-  print(getCorrelationResults(pairedCutSiteDistances))
+  if (shuffle) {
+    pairedCutSiteDistances[,Three_Prime_Cut_Site_Distance :=
+                             sample(Three_Prime_Cut_Site_Distance, nrow(pairedCutSiteDistances))]
+  }
+
+  correlationResults = getCorrelationResults(pairedCutSiteDistances)
+  print(correlationResults)
+  print(paste("True p-value:",correlationResults$p.value))
+
   plotPairedCutSiteDistances(pairedCutSiteDistances,
-                             title = paste(cellType, lesion, timepoint, includedMismatches, "Cut Site Correlation"))
+                             title = paste(cellType, lesion, timepoint, includedMismatches,
+                                           "Cut Site Correlation", additionalInformation))
 
@@
 cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory)
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
+                                           includedMismatches = "C>T")
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
+                                           filteredAndFormattedInput = FALSE)
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
+                                           includedMismatches = "C>T", filteredAndFormattedInput = FALSE)
 ```
+
+```{r shuffled_for_sanity_check}
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
+                                           shuffle = TRUE)
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
+                                           includedMismatches = "CC>TT", filteredAndFormattedInput = FALSE,
+                                           shuffle = TRUE)
+```

### 2023-07-31 R/CutSiteCorrelationAnalysis.R

@@ -12,10 +12,17 @@ blankBackground = theme(panel.grid.major = element_blank(), panel.grid.minor = e
                         panel.background = element_blank(), axis.line = element_line(colour = "black"))
 
 
-getPairedCutSiteDistances = function(mismatchesByRead) {
-  # NOTE: Expects mismatches filtered and formatted from the FormatMismatchesForRelation Python script
-  colnames(mismatchesByRead) = c("Chromosome", "Mismatch_Pos_0", "Mismatch_Pos_1", "Three_Prime_Relative_Mismatch_Pos",
-                                 "Mismatch_Type", "Mismatch_Strand", "Read_Length")
+getPairedCutSiteDistances = function(mismatchesByRead, filteredAndFormattedInput = TRUE) {
+
+  if (filteredAndFormattedInput) {
+    colnames(mismatchesByRead) = c("Chromosome", "Mismatch_Pos_0", "Mismatch_Pos_1", "Three_Prime_Relative_Mismatch_Pos",
+                                   "Mismatch_Type", "Mismatch_Strand", "Read_Length")
+  } else {
+    colnames(mismatchesByRead) = c("Chromosome", "Read_Pos_0", "Read_Pos_1", "Three_Prime_Relative_Mismatch_Pos",
+                                   "Mismatch_Type", "Mismatch_Strand", "Read_Sequence")
+
+    mismatchesByRead[,Read_Length := nchar(Read_Sequence)]
+  }
 
   mismatchesByRead[,Three_Prime_Cut_Site_Distance := abs(Three_Prime_Relative_Mismatch_Pos)]
   mismatchesByRead[,Five_Prime_Cut_Site_Distance := Read_Length-abs(Three_Prime_Relative_Mismatch_Pos)+1]

### 2023-07-31 R/CutSiteCorrelationDataGeneration.rmd
Added species for cut site correlation analysis
Added Arabidopsis and yeast

@@
 NHF1CutSiteCorrelationDirectory = file.path(deaminationDataDirectory, "NHF1", "cut_site_correlation")
+arabidopsisMismatchesByReadDirectory = file.path(deaminationDataDirectory, "Arabidopsis", "mismatches_by_read")
+arabidopsisCutSiteCorrelationDirectory = file.path(deaminationDataDirectory, "Arabidopsis", "cut_site_correlation")
+yeastMismatchesByReadDirectory = file.path(deaminationDataDirectory, "yeast", "mismatches_by_read")
+yeastCutSiteCorrelationDirectory = file.path(deaminationDataDirectory, "yeast", "cut_site_correlation")
 dir.create(NHF1CutSiteCorrelationDirectory, showWarnings = FALSE, recursive = TRUE)
+dir.create(arabidopsisCutSiteCorrelationDirectory, showWarnings = FALSE, recursive = TRUE)
+dir.create(yeastCutSiteCorrelationDirectory, showWarnings = FALSE, recursive = TRUE)
 ```
@@
                                          includedMismatches = "CC>TT", filteredAndFormattedInput = FALSE)
+
+cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "ZT2", "Arabidopsis",
+                                         arabidopsisMismatchesByReadDirectory, arabidopsisCutSiteCorrelationDirectory)
+cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "20min", "yeast",
+                                         yeastMismatchesByReadDirectory, yeastCutSiteCorrelationDirectory)
 ```

### 2023-07-31 R/CutSiteCorrelationFigureGeneration.rmd
Added species for cut site correlation analysis
Added Arabidopsis and yeast

@@
 NHF1CutSiteCorrelationDirectory = file.path(deaminationDataDirectory, "NHF1", "cut_site_correlation")
+arabidopsisCutSiteCorrelationDirectory = file.path(deaminationDataDirectory, "Arabidopsis", "cut_site_correlation")
+yeastCutSiteCorrelationDirectory = file.path(deaminationDataDirectory, "yeast", "cut_site_correlation")
 ```
@@
                                            includedMismatches = "C>T", filteredAndFormattedInput = FALSE)
+
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "ZT2", "Arabidopsis", arabidopsisCutSiteCorrelationDirectory)
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "20min", "yeast", yeastCutSiteCorrelationDirectory)
 ```

### 2023-08-02 python/FormatMismatchesForRelation.py
Filter reads by unacceptable mismatches
- Added an option to filter out reads containing certain mismatch types instead of only retaining those types (acceptable vs. unacceptable mismatch types).
- Added an option to filter composite mismatches (i.e., reads with multiple individual mismatches) in order to complement the unacceptable mismatches option, which would otherwise retain composite mismatches.

@@ -5,10 +5,12 @@ from benbiohelpers.FileSystemHandling.DirectoryHandling import getTempDir
 from benbiohelpers.TkWrappers.TkinterDialog import TkinterDialog
 from benbiohelpers.InputParsing.CheckForNumber import checkForNumber
 from benbiohelpers.InputParsing.ParseToIterable import parseToIterable
+from benbiohelpers.CustomErrors import UserInputError
 
 
 def formatMismatchesForRelation(mismatchesByReadFilePath: str, zScoresFilePath, zScoreCutoff = 4,
-                                acceptableReadLengths = range(22,31), acceptableMismatchTypes: List[str] = ["C>T", "CC>TT"],
+                                acceptableReadLengths = range(22,31),acceptableMismatchTypes: List[str] = ["C>T", "CC>TT"],
+                                unacceptableMismatchTypes: List[str] = None, filterCompositeMismatches = True,
                                 outputSuffix = "_relation_formatted", addMismatchTypesToName = True, outputToTmpDir = False,
                                 sortOutput = True, verbose = False):
     """
@@ -20,21 +22,27 @@ def formatMismatchesForRelation(mismatchesByReadFilePath: str, zScoresFilePath, 
     Returns the new file path.
     """
 
-    # Determine which positions are valid for each read length based on the given z-score cutoff.
-    # Initialize a nested dictionary with one key for read length, another key for position and a final boolean value stating whether the zscore meets the cutoff.
-    if verbose: print("Determining positions with acceptable z-scores...")
-    zscoreDictionary = dict()
-    for readLength in acceptableReadLengths:
-        zscoreDictionary[readLength] = dict()
+    # Make sure invalid arguments were not given.
+    if acceptableMismatchTypes is not None and unacceptableMismatchTypes is not None:
+        raise UserInputError("Acceptable mismatch types and unacceptable mismatch types are incompatible and cannot both have values.")
 
-    # Determine which positions have zscores which meet the cutoff.
-    with open(zScoresFilePath, 'r') as zScoresFile:
-        zScoresFile.readline() # Skip the headers
-        for line in zScoresFile:
-            readLength, position, frequency, zScore = line.split()
-            readLength = int(readLength)
-            if readLength not in acceptableReadLengths: continue
-            else: zscoreDictionary[readLength][float(position)] = float(zScore) >= zScoreCutoff
+
+    # Determine which positions are valid for each read length based on the given z-score cutoff.
[…]

### 2023-08-02 R/CutSiteCorrelationDataGeneration.rmd
General updates to R cut site correlation pipeline
- Included C>T-omitted data
- Diversified functions to optionally use either 3' cut site distance or read length as the dependent variable.
- Incorporated linear regression into output and figures.
- Changed scale for points in plots so that sparsely populated points appear as such.
- Probably some other small changes I'm missing

@@
 library(knitr)
+library(stringr)
 
@@
 cutSiteCorrelationAnalysisDataGeneration = function(lesion, repetition, timepoint, cellType, inputDirectory, outputDirectory,
-                                                    includedMismatches = c("CC>TT"), filteredAndFormattedInput = TRUE,
-                                                    filePathIncludedMismatches = NA) {
+                                                    includedMismatches = character(), omittedMismatches = character(),
+                                                    filteredAndFormattedInput = TRUE,
+                                                    filePathIncludedMismatches = NULL, filePathOmittedMismatches = NULL) {
 
-  if (length(filePathIncludedMismatches) > 0 && is.na(filePathIncludedMismatches)) {
+  if (is.null(filePathIncludedMismatches)) {
     filePathIncludedMismatches = includedMismatches
+  }
+  if (is.null(filePathOmittedMismatches)) {
+    filePathOmittedMismatches = omittedMismatches
   }
@@
     cellType = cellType, lesion = lesion, timepoint = timepoint,
-    repitition = repetition, filtering = filtering, includedMismatches = filePathIncludedMismatches
+    repitition = repetition, filtering = filtering,
+    includedMismatches = filePathIncludedMismatches, omittedMismatches = filePathOmittedMismatches
   ))
@@
 
+  if (!filteredAndFormattedInput) {mismatchesByRead = mismatchesByRead[str_count(V5, ':') == 0]}
+
   if (length(filePathIncludedMismatches) != length(includedMismatches)) {
     mismatchesByRead = mismatchesByRead[V5 %in% includedMismatches]
+    mismatchesByRead[,V4:=as.numeric(V4)]
+  } else if (length(filePathOmittedMismatches) != length(omittedMismatches)) {
+    mismatchesByRead = mismatchesByRead[!V5 %in% omittedMismatches]
     mismatchesByRead[,V4:=as.numeric(V4)]
@@
     cellType = cellType, lesion = lesion, timepoint = timepoint,
-    repitition = repetition, filtering = filtering, includedMismatches = includedMismatches,
+    repitition = repetition, filtering = filtering,
+    includedMismatches = includedMismatches, omittedMismatches = omittedMismatches,
     additionalInformation = additionalInformation
@@
 cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
-                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory)
+                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
+                                         includedMismatches = "CC>TT")
 cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
@@
                                          includedMismatches = "C>T")
+cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
+                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
+                                         omittedMismatches = "C>T")
+cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
+                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
+                                         includedMismatches = "CC>TT", filteredAndFormattedInput = FALSE)
 cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
@@
                                          NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
-                                         includedMismatches = "CC>TT", filteredAndFormattedInput = FALSE)
+                                         omittedMismatches = "C>T", filteredAndFormattedInput = FALSE,
+                                         filePathOmittedMismatches = character())
 
 cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "ZT2", "Arabidopsis",
-                                         arabidopsisMismatchesByReadDirectory, arabidopsisCutSiteCorrelationDirectory)
+                                         arabidopsisMismatchesByReadDirectory, arabidopsisCutSiteCorrelationDirectory,
+                                         includedMismatches = "CC>TT")
+cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "ZT2", "Arabidopsis",
+                                         arabidopsisMismatchesByReadDirectory, arabidopsisCutSiteCorrelationDirectory,
+                                         includedMismatches = "C>T")
+cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "ZT2", "Arabidopsis",
+                                         arabidopsisMismatchesByReadDirectory, arabidopsisCutSiteCorrelationDirectory,
+                                         omittedMismatches = "C>T")
+
 cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "20min", "yeast",
-                                         yeastMismatchesByReadDirectory, yeastCutSiteCorrelationDirectory)
+                                         yeastMismatchesByReadDirectory, yeastCutSiteCorrelationDirectory,
+                                         includedMismatches = "CC>TT")
+cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "20min", "yeast",
+                                         yeastMismatchesByReadDirectory, yeastCutSiteCorrelationDirectory,
+                                         includedMismatches = "C>T")
+cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "20min", "yeast",
+                                         yeastMismatchesByReadDirectory, yeastCutSiteCorrelationDirectory,
+                                         omittedMismatches = "C>T")
+
 ```

### 2023-08-02 R/CutSiteCorrelationFigureGeneration.rmd
General updates to R cut site correlation pipeline
- Included C>T-omitted data
- Diversified functions to optionally use either 3' cut site distance or read length as the dependent variable.
- Incorporated linear regression into output and figures.
- Changed scale for points in plots so that sparsely populated points appear as such.
- Probably some other small changes I'm missing

--- 2023-07-28 R/CutSiteCorrelationFigureGeneration.rmd
@@
 cutSiteCorrelationAnalysisFigureGeneration = function(lesion, repetition, timepoint, cellType, directory,
-                                                    includedMismatches = c("CC>TT")) {
+                                                      includedMismatches = character(), omittedMismatches = character(),
+                                                      filteredAndFormattedInput = TRUE, shuffle = FALSE) {
+
+  if (filteredAndFormattedInput) {
+    additionalInformation = character()
+  } else {
+    additionalInformation = "minimal_filtering"
+  }
+
   pairedCutSiteDistances = fread(generateFilePath(
@@
     cellType = cellType, lesion = lesion, timepoint = timepoint,
-    repitition = repetition, filtering = filtering, includedMismatches = includedMismatches
+    repitition = repetition, filtering = filtering,
+    includedMismatches = includedMismatches, omittedMismatches = omittedMismatches,
+    additionalInformation = additionalInformation
   ))
 
-  print(getCorrelationResults(pairedCutSiteDistances))
-  plotPairedCutSiteDistances(pairedCutSiteDistances,
-                             title = paste(cellType, lesion, timepoint, includedMismatches, "Cut Site Correlation"))
+  if (shuffle) {
+    pairedCutSiteDistances[,Three_Prime_Cut_Site_Distance :=
+                             sample(Three_Prime_Cut_Site_Distance, nrow(pairedCutSiteDistances))]
+    pairedCutSiteDistances[,Read_Length := Three_Prime_Cut_Site_Distance + Five_Prime_Cut_Site_Distance]
+    additionalInformation = paste(additionalInformation,"5'_shuffled")
+  }
 
+  if (length(includedMismatches) > 0) {
+    mismatchText = includedMismatches
+  } else if (length(omittedMismatches) > 0) {
+    mismatchText = paste0("non-",paste(omittedMismatches,collapse = '-'))
+  } else {
+    mismatchText = ''
+  }
+
+  print(paste(cellType, lesion, timepoint, mismatchText, additionalInformation))
+
+  print("  3' cut site model:")
+  correlationResults = getCorrelationResults(pairedCutSiteDistances, THREE_PRIME_CUT_SITE_DISTANCE)
+  print(paste0("    r = ",correlationResults$estimate, "; p = ",correlationResults$p.value))
+  linearModel = lm(Three_Prime_Cut_Site_Distance ~ Five_Prime_Cut_Site_Distance, pairedCutSiteDistances)
+  print(paste0("    Slope = ",linearModel$coefficients[2], "; p = ", summary(linearModel)$coefficients[8]))
+
+  plotPairedCutSiteDistances(pairedCutSiteDistances, THREE_PRIME_CUT_SITE_DISTANCE,
+                             title = paste(cellType, lesion, timepoint, mismatchText,
+                                           "Cut Site Correlation", additionalInformation))
+
+  print("  Read length model:")
+  correlationResults = getCorrelationResults(pairedCutSiteDistances, READ_LENGTH)
+  print(paste0("    r = ",correlationResults$estimate, "; p = ",correlationResults$p.value))
+  linearModel = lm(Read_Length ~ Five_Prime_Cut_Site_Distance, pairedCutSiteDistances)
+  print(paste0("    Slope = ",linearModel$coefficients[2], "; p = ", summary(linearModel)$coefficients[8]))
+
+  plotPairedCutSiteDistances(pairedCutSiteDistances, READ_LENGTH,
+                             title = paste(cellType, lesion, timepoint, mismatchText,
+                                           "Cut Site Correlation", additionalInformation))
 }
@@
 
-```{r generate_cut_site_correlation_figures}
-cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory)
+```{r NHF1_cut_site_correlation_figures}
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
+                                           includedMismatches = "CC>TT")
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
+                                           includedMismatches = "C>T")
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
+                                           omittedMismatches = "C>T")
+
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
+                                           includedMismatches = "CC>TT", shuffle = TRUE)
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
+                                           includedMismatches = "C>T", shuffle = TRUE)
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
+                                           omittedMismatches = "C>T", shuffle = TRUE)
+
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
+                                           includedMismatches = "CC>TT", filteredAndFormattedInput = FALSE)
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
+                                           includedMismatches = "C>T", filteredAndFormattedInput = FALSE)
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
+                                           omittedMismatches = "C>T", filteredAndFormattedInput = FALSE)
 ```
+
+```{r Arabidopsis_cut_site_correlation_figures}
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "ZT2", "Arabidopsis", arabidopsisCutSiteCorrelationDirectory,
+                                           includedMismatches = "CC>TT")
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "ZT2", "Arabidopsis", arabidopsisCutSiteCorrelationDirectory,
+                                           includedMismatches = "C>T")
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "ZT2", "Arabidopsis", arabidopsisCutSiteCorrelationDirectory,
+                                           omittedMismatches = "C>T")
+
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "ZT2", "Arabidopsis", arabidopsisCutSiteCorrelationDirectory,
+                                           includedMismatches = "CC>TT", shuffle = TRUE)
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "ZT2", "Arabidopsis", arabidopsisCutSiteCorrelationDirectory,
+                                           includedMismatches = "C>T", shuffle = TRUE)
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "ZT2", "Arabidopsis", arabidopsisCutSiteCorrelationDirectory,
+                                           omittedMismatches = "C>T", shuffle = TRUE)
+```
+
+```{r yeast_cut_site_correlation_figures}
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "20min", "yeast", yeastCutSiteCorrelationDirectory,
+                                           includedMismatches = "CC>TT")
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "20min", "yeast", yeastCutSiteCorrelationDirectory,
+                                           includedMismatches = "C>T")
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "20min", "yeast", yeastCutSiteCorrelationDirectory,
+                                           omittedMismatches = "C>T")
+
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "20min", "yeast", yeastCutSiteCorrelationDirectory,
+                                           includedMismatches = "CC>TT", shuffle = TRUE)
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "20min", "yeast", yeastCutSiteCorrelationDirectory,
+                                           includedMismatches = "C>T", shuffle = TRUE)
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "20min", "yeast", yeastCutSiteCorrelationDirectory,
+                                           omittedMismatches = "C>T", shuffle = TRUE)
+```

### 2023-08-02 R/CutSiteCorrelationAnalysis.R

@@ -11,6 +11,8 @@ defaultTextScaling = theme(plot.title = element_text(size = 22, hjust = 0.5),
 blankBackground = theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
                         panel.background = element_blank(), axis.line = element_line(colour = "black"))
 
+THREE_PRIME_CUT_SITE_DISTANCE = "Three_Prime_Cut_Site_Distance"
+READ_LENGTH = "Read_Length"
 
 getPairedCutSiteDistances = function(mismatchesByRead, filteredAndFormattedInput = TRUE) {
 
@@ -27,24 +29,34 @@ getPairedCutSiteDistances = function(mismatchesByRead, filteredAndFormattedInput
   mismatchesByRead[,Three_Prime_Cut_Site_Distance := abs(Three_Prime_Relative_Mismatch_Pos)]
   mismatchesByRead[,Five_Prime_Cut_Site_Distance := Read_Length-abs(Three_Prime_Relative_Mismatch_Pos)+1]
 
-  return(mismatchesByRead[,.(Three_Prime_Cut_Site_Distance, Five_Prime_Cut_Site_Distance)])
+  return(mismatchesByRead[,.(Three_Prime_Cut_Site_Distance, Five_Prime_Cut_Site_Distance, Read_Length)])
 
 }
 
-getCorrelationResults = function(pairedCutSiteDistances) {
+getCorrelationResults = function(pairedCutSiteDistances, dependentVariable) {
 
-  return(cor.test(pairedCutSiteDistances$Three_Prime_Cut_Site_Distance,
+  return(cor.test(pairedCutSiteDistances[[dependentVariable]],
                   pairedCutSiteDistances$Five_Prime_Cut_Site_Distance, method = "pearson"))
 
 }
 
-plotPairedCutSiteDistances = function(pairedCutSiteDistances,
-                                       xAxisLabel = "3' Cut Site Distance", yAxisLabel = "5' CutSite Distance",
-                                       title = "Paired Cut Site Distances") {
+plotPairedCutSiteDistances = function(pairedCutSiteDistances, dependentVariable,
+                                      xAxisLabel = "5' Cut Site Distance", yAxisLabel = NULL,
+                                      title = "Paired Cut Site Distances", sizeRange = c(0.1,5),
+                                      xlim = NULL, ylim = NULL) {
 
[…]

### 2023-08-03 R/PaperFigureGeneration.rmd
Updated cut site distances on CC>TT figure

@@
                         showFivePrimeCutSite = TRUE, querySequences = c("333"),
-                        expansionOffset = 10, minReadLength = 19, maxReadLength = 24, endBasedBackgroundNum = 6,
+                        expansionOffset = 10, minReadLength = 19.5, maxReadLength = 24.5, endBasedBackgroundNum = 6,
                         endBasedCheckPositions = -9, displayPValue = FALSE, xAxisLabel = "Mismatch Relative Position",
-                        xAxisOffset = 1, positionOffset = 1, xAxisBreaks = c(-2,-10,-20,-30), xlim = c(-35,-4))
+                        xAxisOffset = 1, positionOffset = 0.5, readLengthOffset = 0.5,
+                        xAxisBreaks = c(-2,-10,-20,-30), xlim = c(-35,-3.5))
 ```

### 2023-08-03 R/DeaminationFeatureRelativeAnalysis.R
Feature relative plots can display significance
- Uses a simple test of the standard error and mean of a single point against the median. But...
- Turns out this is shoddy statistics. This will be changed shortly to use an actual t-test.

@@ -129,6 +129,7 @@ getFeatureRelativeCounts = function(table, dataType, strandAlign = FALSE) {
 # This function plots counts of feature-relative features, as specified by the "feature" parameter.
 plotFeatureRelativeCounts = function(countsTable, countsDataType, countsYVar = COUNTS,
                                      plotCountsMirror = FALSE, smoothCountsData = FALSE,
+                                     plotCutSiteSignificance = TRUE, zScoreCutoff = 4, significanceColor = "black",
                                      countsPlotType = LINE, countsPlotColor = "black", countsMirrorColor = "gray",
                                      meanCutSiteDistanceTable = NULL, cutSiteStrandPolarity = NULL,
                                      smoothMeanCutSiteDistance = FALSE,
@@ -167,6 +168,17 @@ plotFeatureRelativeCounts = function(countsTable, countsDataType, countsYVar = C
     }
   }
 
+  if (plotCutSiteSignificance && (
+    countsYVar == MEAN_THREE_PRIME_CUT_SITE_DISTANCE || countsYVar == MEAN_FIVE_PRIME_CUT_SITE_DISTANCE)
+  ) {
+    if (smoothCountsData) {
+      warning("Plotting significance with smoothed data is ill-advised, as SEM is calculated before smoothing.")
+    }
+    thisMedian = median(countsTable[[countsYVar]])
+    countsTable[,Main_Z_Score := (thisMedian - countsTable[[countsYVar]]) / Standard_Error]
+    countsTable[,Main_Significant := abs(Main_Z_Score) > zScoreCutoff]
+  }
+
   if (countsDataType == FEATURE_RELATIVE_POSITION) {
     if (is.null(xAxisLabel)) xAxisLabel = "Feature Relative Position"
     if (is.null(title)) title = "Feature Relative Mismatch Position Frequencies"
@@ -200,6 +212,16 @@ plotFeatureRelativeCounts = function(countsTable, countsDataType, countsYVar = C
       meanCutSiteDistanceCol = paste0(meanCutSiteDistanceCol,"_Smoothed")
     }
     meanCutSiteDistanceTable = meanCutSiteDistanceTable[complete.cases(meanCutSiteDistanceTable)]
+
+    if (plotCutSiteSignificance) {
+      if (smoothMeanCutSiteDistance) {
+        warning("Plotting significance with smoothed data is ill-advised, as SEM is calculated before smoothing.")
[…]

### 2023-08-03 R/DeaminationAnchoredExcisionSiteAnalysis.R
plotSeqFreq now accepts a read length offset
Used to update cut sites for tandem CC>TT data so that half-base positions are used.

@@ -395,7 +395,8 @@ plotSequenceFrequencies = function(seqFreqTablesByTimepoint, posType = THREE_PRI
                                    startBasedBackgroundNum = NULL, endBasedBackgroundNum = NULL, backgroundPositions = NULL,
                                    startBasedCheckPositions = NULL, endBasedCheckPositions = NULL, checkPositions = NULL,
                                    displayPValue = FALSE, zScoreCutoff = 4, significanceAsteriskBreakpoints = NULL,
-                                   xAxisLabel = NULL, xAxisOffset = 0, positionOffset = 0, defaultColor = "grey35") {
+                                   xAxisLabel = NULL, xAxisOffset = 0, positionOffset = 0, readLengthOffset = 0,
+                                   defaultColor = "grey35") {
 
   if (is.null(xAxisLabel)) {
     if (posType == THREE_PRIME) {
@@ -431,6 +432,7 @@ plotSequenceFrequencies = function(seqFreqTablesByTimepoint, posType = THREE_PRI
   maxQueryLength = max(nchar(querySequences))
 
   if (!combinedReadLengths) {
+    fullFrequencyTable[,Read_Length := Read_Length + readLengthOffset]
     if (!is.null(minReadLength)) fullFrequencyTable = fullFrequencyTable[Read_Length >= minReadLength]
     if (!is.null(maxReadLength)) fullFrequencyTable = fullFrequencyTable[Read_Length <= maxReadLength]
   }

### 2023-08-03 R/CutSiteCorrelationAnalysis.R
Update core cut site correlation functions
- Added options for axis breaks when plotting paired cut sites
- Created functions for getting coupling rate and shuffling cut site distances.

@@ -33,6 +33,14 @@ getPairedCutSiteDistances = function(mismatchesByRead, filteredAndFormattedInput
 
 }
 
+getShufflePairedCutSiteDistances = function(pairedCutSiteDistances) {
+  pairedCutSiteDistances = copy(pairedCutSiteDistances)
+  pairedCutSiteDistances[,Three_Prime_Cut_Site_Distance :=
+                           sample(Three_Prime_Cut_Site_Distance, nrow(pairedCutSiteDistances))]
+  pairedCutSiteDistances[,Read_Length := Three_Prime_Cut_Site_Distance + Five_Prime_Cut_Site_Distance - 1]
+  return(pairedCutSiteDistances)
+}
+
 getCorrelationResults = function(pairedCutSiteDistances, dependentVariable) {
 
   return(cor.test(pairedCutSiteDistances[[dependentVariable]],
@@ -40,10 +48,15 @@ getCorrelationResults = function(pairedCutSiteDistances, dependentVariable) {
 
 }
 
+getCouplingRate = function(pairedCutSiteDistances) {
+  linearModel = lm(Three_Prime_Cut_Site_Distance ~ Five_Prime_Cut_Site_Distance, pairedCutSiteDistances)
+  return(linearModel$coefficients[2])
+}
+
 plotPairedCutSiteDistances = function(pairedCutSiteDistances, dependentVariable,
                                       xAxisLabel = "5' Cut Site Distance", yAxisLabel = NULL,
                                       title = "Paired Cut Site Distances", sizeRange = c(0.1,5),
-                                      xlim = NULL, ylim = NULL) {
+                                      xlim = NULL, ylim = NULL, xAxisBreaks = waiver(), yAxisBreaks = waiver()) {
 
   if (is.null(yAxisLabel)) {
     if (dependentVariable == THREE_PRIME_CUT_SITE_DISTANCE) {
@@ -55,8 +68,9 @@ plotPairedCutSiteDistances = function(pairedCutSiteDistances, dependentVariable,
 
   plot = ggplot(pairedCutSiteDistances, aes(x = Five_Prime_Cut_Site_Distance, y = !!sym(dependentVariable))) +
     geom_count() + scale_size(range = sizeRange) + blankBackground + defaultTextScaling +
-    geom_smooth(method = "lm", formula = y~x, color = "red2") +
[…]

### 2023-08-03 R/CutSiteCorrelationDataGeneration.rmd
Generate cut site correlation data for NHF1 8h

@@
 
+cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "8h", "NHF1",
+                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
+                                         includedMismatches = "CC>TT")
+cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "8h", "NHF1",
+                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
+                                         includedMismatches = "C>T")
+cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "8h", "NHF1",
+                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
+                                         omittedMismatches = "C>T")
+
 cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "ZT2", "Arabidopsis",

### 2023-08-03 R/CutSiteCorrelationFigureGeneration.rmd
Basic updates to cut site correlation plotting
- Now utilizing shuffling function in associated R script.
- Added figure generation for NHF1 8h timepoint.

@@
   if (shuffle) {
-    pairedCutSiteDistances[,Three_Prime_Cut_Site_Distance :=
-                             sample(Three_Prime_Cut_Site_Distance, nrow(pairedCutSiteDistances))]
-    pairedCutSiteDistances[,Read_Length := Three_Prime_Cut_Site_Distance + Five_Prime_Cut_Site_Distance]
+    pairedCutSiteDistances = getShufflePairedCutSiteDistances(pairedCutSiteDistances)
     additionalInformation = paste(additionalInformation,"5'_shuffled")
@@
 
-```{r NHF1_cut_site_correlation_figures}
+```{r NHF1_1h_cut_site_correlation_figures}
 cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
@@
                                            omittedMismatches = "C>T", filteredAndFormattedInput = FALSE)
+```
+
+```{r NHF1_8h_cut_site_correlation_figures}
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "8h", "NHF1", NHF1CutSiteCorrelationDirectory,
+                                           includedMismatches = "CC>TT")
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "8h", "NHF1", NHF1CutSiteCorrelationDirectory,
+                                           includedMismatches = "C>T")
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "8h", "NHF1", NHF1CutSiteCorrelationDirectory,
+                                           omittedMismatches = "C>T")
+
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "8h", "NHF1", NHF1CutSiteCorrelationDirectory,
+                                           includedMismatches = "CC>TT", shuffle = TRUE)
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "8h", "NHF1", NHF1CutSiteCorrelationDirectory,
+                                           includedMismatches = "C>T", shuffle = TRUE)
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "8h", "NHF1", NHF1CutSiteCorrelationDirectory,
+                                           omittedMismatches = "C>T", shuffle = TRUE)
 ```

### 2023-08-03 R/PaperFigureGeneration.rmd
Added cut site correlation and nucleosome figures
These are still in their early stages and will be updated soon

@@
 NHF1GeneralReadSequenceDataDirectory = file.path(NHF1DataDirectory, "general_read_sequences")
+NHF1CutSiteCorrelationDirectory = file.path(deaminationDataDirectory, "NHF1", "cut_site_correlation")
+NHF1FeatureRelativeDataDirectory = file.path(deaminationDataDirectory, "NHF1", "feature_relative_analysis")
 
@@
 arabidopsisGeneralReadSequenceDataDirectory = file.path(arabidopsisDataDirectory, "general_read_sequences")
+arabidopsisCutSiteCorrelationDirectory = file.path(deaminationDataDirectory, "Arabidopsis", "cut_site_correlation")
 
@@
 yeastGeneralReadSequenceDataDirectory = file.path(yeastDataDirectory, "general_read_sequences")
+yeastCutSiteCorrelationDirectory = file.path(deaminationDataDirectory, "yeast", "cut_site_correlation")
 
@@
                  "DeaminationAnchoredExcisionSiteAnalysis.R"))
+source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
+                 "CutSiteCorrelationAnalysis.R"))
+source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
+                 "DeaminationFeatureRelativeAnalysis.R"))
 ```
@@
                                    mismatchData = yeastCPDCCtoTTMismatchDataAllRepsFiltered$`20min`)))
+```
+
+```{r read_figure_7_data}
+set.seed(8785)
+NHF1PairedCutSiteDistances = list(`1h` = NULL, `8h` = NULL)
+NHF1ShuffledCutSiteDistances = list(`1h` = NULL, `8h` = NULL)
+for (i in seq_along(NHF1PairedCutSiteDistances)) {
+  NHF1PairedCutSiteDistances[[i]] = list(CC_to_TT = NULL, non_C_to_T = NULL)
+  NHF1PairedCutSiteDistances[[i]]$CC_to_TT = fread(generateFilePath(
+    NHF1CutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances , ".tsv",
+    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1PairedCutSiteDistances)[i],
+    repitition = "all_reps", filtering = "TGG_filtered",
+    includedMismatches = "CC>TT"
+  ))
+  NHF1ShuffledCutSiteDistances[[i]] = getShufflePairedCutSiteDistances(NHF1PairedCutSiteDistances[[i]]$CC_to_TT)
+  NHF1PairedCutSiteDistances[[i]]$non_C_to_T = fread(generateFilePath(
+    NHF1CutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances , ".tsv",
+    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1PairedCutSiteDistances)[i],
+    repitition = "all_reps", filtering = "TGG_filtered",
+    omittedMismatches = "C>T"
+  ))
+}
+
+arabidopsisPairedCutSiteDistances = list(ZT2 = NULL)
+arabidopsisShuffledCutSiteDistances = list(ZT2 = NULL)
+arabidopsisPairedCutSiteDistances$ZT2 = list(CC_to_TT = NULL, non_C_to_T = NULL)
+arabidopsisPairedCutSiteDistances$ZT2$CC_to_TT = fread(generateFilePath(
+  arabidopsisCutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances , ".tsv",
+  cellType = "Arabidopsis", lesion = "CPD", timepoint = "ZT2",
+  repitition = "all_reps", filtering = "TGG_filtered",
+  includedMismatches = "CC>TT"
+))
+arabidopsisShuffledCutSiteDistances$ZT2 = getShufflePairedCutSiteDistances(arabidopsisPairedCutSiteDistances$ZT2$CC_to_TT)
+arabidopsisPairedCutSiteDistances$ZT2$non_C_to_T = fread(generateFilePath(
+  arabidopsisCutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances , ".tsv",
+  cellType = "Arabidopsis", lesion = "CPD", timepoint = "ZT2",
+  repitition = "all_reps", filtering = "TGG_filtered",
+  omittedMismatches = "C>T"
+))
+
+```
+
+```{r figure_7A, fig.width = 6, fig.height = 5}
+print(paste0("Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`1h`$CC_to_TT)*-100, '%'))
+plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$CC_to_TT, THREE_PRIME_CUT_SITE_DISTANCE,
+                           title = "NHF1 1h CC>TT All Reps TGG-filtered",
+                           xlim = c(12,26), ylim = c(0,14.5),
+                           xAxisBreaks = seq(12,26,2), yAxisBreaks = seq(0,14,2))
+```
+```{r figure_7B, fig.width = 6, fig.height = 5}
+print(paste0("Coupling: ", getCouplingRate(NHF1ShuffledCutSiteDistances$`1h`)*-100, '%'))
+plotPairedCutSiteDistances(NHF1ShuffledCutSiteDistances$`1h`, THREE_PRIME_CUT_SITE_DISTANCE,
+                           title = "NHF1 1h CC>TT All Reps TGG-filtered Shuffled",
+                           xlim = c(12,26), ylim = c(0,14.5),
+                           xAxisBreaks = seq(12,26,2), yAxisBreaks = seq(0,14,2))
+```
+```{r figure_7C, fig.width = 6, fig.height = 5}
+print(paste0("Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`1h`$non_C_to_T)*-100, '%'))
+plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$non_C_to_T, THREE_PRIME_CUT_SITE_DISTANCE,
+                           title = "NHF1 1h Non-C>T All Reps TGG-filtered",
+                           xlim = c(0,31), ylim = c(0,31))
+```
+```{r figure_7D, fig.width = 6, fig.height = 5}
+print(paste0("Coupling: ", getCouplingRate(arabidopsisPairedCutSiteDistances$ZT2$CC_to_TT)*-100, '%'))
+plotPairedCutSiteDistances(arabidopsisPairedCutSiteDistances$ZT2$CC_to_TT, THREE_PRIME_CUT_SITE_DISTANCE,
+                           title = "Arabidopsis ZT2 CC>TT All Reps TGG-filtered",
+                           xlim = c(15,25.5), ylim = c(4,12.5))
+```
+```{r figure_7E, fig.width = 6, fig.height = 5}
+print(paste0("Coupling: ", getCouplingRate(arabidopsisShuffledCutSiteDistances$ZT2)*-100, '%'))
+plotPairedCutSiteDistances(arabidopsisShuffledCutSiteDistances$ZT2, THREE_PRIME_CUT_SITE_DISTANCE,
+                           title = "Arabidopsis ZT2 CC>TT All Reps TGG-filtered Shuffled",
+                           xlim = c(15,25.5), ylim = c(4,12.5))
+```
+```{r figure_7F, fig.width = 6, fig.height = 5}
+print(paste0("Coupling: ", getCouplingRate(arabidopsisPairedCutSiteDistances$ZT2$non_C_to_T)*-100, '%'))
+plotPairedCutSiteDistances(arabidopsisPairedCutSiteDistances$ZT2$non_C_to_T, THREE_PRIME_CUT_SITE_DISTANCE,
+                           title = "Arabidopsis ZT2 Non-C>T All Reps TGG-filtered",
+                           xlim = c(0,31), ylim = c(0,31))
+```
+
+```{r read_figure_8_data}
+NHF1NucleosomeRelativeCutSiteDistances = NHF1CPDTimepoints
+for (i in seq_along(NHF1NucleosomeRelativeCutSiteDistances)) {
+  NHF1NucleosomeRelativeCutSiteDistances[[i]] = list(three_prime = NULL, five_prime = NULL)
+  NHF1NucleosomeRelativeCutSiteDistances[[i]]$three_prime = fread(generateFilePath(
+    NHF1FeatureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv",
+    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1NucleosomeRelativeCutSiteDistances)[i],
+    strandPolarity = THREE_PRIME, repitition = "all_reps", filtering = "TGG_filtered",
+    includedMismatches = "C>T", additionalInformation = "hg19_mnase_all_related_strand_aligned"
+  ))
+  NHF1NucleosomeRelativeCutSiteDistances[[i]]$five_prime = fread(generateFilePath(
+    NHF1FeatureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv",
+    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1NucleosomeRelativeCutSiteDistances)[i],
+    strandPolarity = FIVE_PRIME, repitition = "all_reps", filtering = "TGG_filtered",
+    includedMismatches = "C>T", additionalInformation = "hg19_mnase_all_related_strand_aligned"
+  ))
+}
+```
+
+```{r figure_8A, fig.width = 10, fig.height = 5}
+plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`1h`$three_prime,
+                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
+                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
+                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
+                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
+                          title = "NHF1 1h C>T All Reps TGG-Filtered Strand-Aligned",
+                          xAxisLabel = "Dyad-Relative Position", xlim = c(-200, 200),
+                          secondaryAxisBreaks = seq(19,19.8,0.2),
+                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
+```
+```{r figure_8B}
+plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`1h`$three_prime,
+                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
+                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
+                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
+                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
+                          title = "NHF1 1h C>T All Reps TGG-Filtered Strand-Aligned",
+                          xAxisLabel = "Dyad-Relative Position", xlim = c(-100, -40),
+                          secondaryAxisBreaks = seq(19,19.8,0.2),
+                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
+```
+```{r figure_8C}
+plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`1h`$three_prime,
+                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
+                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
+                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
+                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
+                          title = "NHF1 1h C>T All Reps TGG-Filtered Strand-Aligned",
+                          xAxisLabel = "Dyad-Relative Position", xlim = c(40, 100),
+                          secondaryAxisBreaks = seq(19,19.8,0.2),
+                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
 ```
@@
 ```
+
+```{r figure_S13, fig.width = 6, fig.height = 5}
+print(paste0("CC>TT Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`8h`$CC_to_TT)*-100, '%'))
+plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$CC_to_TT, THREE_PRIME_CUT_SITE_DISTANCE,
+                           title = "NHF1 8h CC>TT All Reps TGG-filtered",
+                           xlim = c(12,26), ylim = c(0,14.5),
+                           xAxisBreaks = seq(12,26,2), yAxisBreaks = seq(0,14,2))
+print(paste0("Shuffled CC>TT Coupling: ", getCouplingRate(NHF1ShuffledCutSiteDistances$`8h`)*-100, '%'))
+plotPairedCutSiteDistances(NHF1ShuffledCutSiteDistances$`1h`, THREE_PRIME_CUT_SITE_DISTANCE,
+                           title = "NHF1 8h CC>TT All Reps TGG-filtered Shuffled",
+                           xlim = c(12,26), ylim = c(0,14.5),
+                           xAxisBreaks = seq(12,26,2), yAxisBreaks = seq(0,14,2))
+print(paste0("Non-C>T Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`8h`$non_C_to_T)*-100, '%'))
+plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$non_C_to_T, THREE_PRIME_CUT_SITE_DISTANCE,
+                           title = "NHF1 8h Non-C>T All Reps TGG-filtered",
+                           xlim = c(0,31), ylim = c(0,31))
+```
+
+```{r read_figure_S14_data}
+yeastPairedCutSiteDistances = list(`20min` = NULL)
+yeastShuffledCutSiteDistances = list(`20min` = NULL)
+yeastPairedCutSiteDistances$`20min` = list(CC_to_TT = NULL, non_C_to_T = NULL)
+yeastPairedCutSiteDistances$`20min`$CC_to_TT = fread(generateFilePath(
+  yeastCutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances, ".tsv",
+  cellType = "yeast", lesion = "CPD", timepoint = "20min",
+  repitition = "all_reps", filtering = "TGG_filtered",
+  includedMismatches = "CC>TT"
+))
+yeastShuffledCutSiteDistances$`20min` = getShufflePairedCutSiteDistances(yeastPairedCutSiteDistances$`20min`$CC_to_TT)
+yeastPairedCutSiteDistances$`20min`$non_C_to_T = fread(generateFilePath(
+  yeastCutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances, ".tsv",
+  cellType = "yeast", lesion = "CPD", timepoint = "20min",
+  repitition = "all_reps", filtering = "TGG_filtered",
+  omittedMismatches = "C>T"
+))
+```
+
+```{r figure_S14, fig.width = 6, fig.height = 5}
+print(paste0("CC>TT Coupling: ", getCouplingRate(yeastPairedCutSiteDistances$`20min`$CC_to_TT)*-100, '%'))
+plotPairedCutSiteDistances(yeastPairedCutSiteDistances$`20min`$CC_to_TT, THREE_PRIME_CUT_SITE_DISTANCE,
+                           title = "Yeast 20min CC>TT All Reps TGG-filtered",
+                           xlim = c(11,19.5), ylim = c(5,14), yAxisBreaks = c(5,7,9,11,13))
+print(paste0("Shuffled CC>TT Coupling: ", getCouplingRate(yeastShuffledCutSiteDistances$`20min`)*-100, '%'))
+plotPairedCutSiteDistances(yeastShuffledCutSiteDistances$`20min`, THREE_PRIME_CUT_SITE_DISTANCE,
+                           title = "Yeast 20min CC>TT All Reps TGG-filtered Shuffled",
+                           xlim = c(11,19.5), ylim = c(5,14), yAxisBreaks = c(5,7,9,11,13))
+print(paste0("Non-C>T Coupling: ", getCouplingRate(yeastPairedCutSiteDistances$`20min`$non_C_to_T)*-100, '%'))
+plotPairedCutSiteDistances(yeastPairedCutSiteDistances$`20min`$non_C_to_T, THREE_PRIME_CUT_SITE_DISTANCE,
+                           title = "Yeast 20min Non-C>T All Reps TGG-filtered",
+                           xlim = c(0,26), ylim = c(0,26))
+```
+
+```{r figure_S15A, fig.width = 10, fig.height = 5}
+plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,
+                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
+                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
+                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
+                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
+                          title = "NHF1 8h C>T All Reps TGG-Filtered Strand-Aligned",
+                          xAxisLabel = "Dyad-Relative Position", xlim = c(-200, 200),
+                          secondaryAxisBreaks = seq(19,19.8,0.2),
+                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
+```
+```{r figure_S15B}
+plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,
+                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
+                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
+                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
+                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
+                          title = "NHF1 8h C>T All Reps TGG-Filtered Strand-Aligned",
+                          xAxisLabel = "Dyad-Relative Position", xlim = c(-100, -40),
+                          secondaryAxisBreaks = seq(19,19.8,0.2),
+                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
+```
+```{r figure_S15C}
+plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,
+                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
+                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
+                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
+                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
+                          title = "NHF1 8h C>T All Reps TGG-Filtered Strand-Aligned",
+                          xAxisLabel = "Dyad-Relative Position", xlim = c(40, 100),
+                          secondaryAxisBreaks = seq(19,19.8,0.2),
+                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
+```

### 2023-08-08 R/CutSiteCorrelationDataGeneration.rmd
Added no-position-filtering control

@@
                                                     includedMismatches = character(), omittedMismatches = character(),
-                                                    filteredAndFormattedInput = TRUE,
+                                                    filteredAndFormattedInput = TRUE, noPositionFiltering = FALSE,
                                                     filePathIncludedMismatches = NULL, filePathOmittedMismatches = NULL) {
@@
   if (filteredAndFormattedInput) {
+    if (noPositionFiltering) {
+      inputType = paste0(dataTypeStrings$mismatchesByReadRelationFormatted,"_no_position_filtering")
+    } else {
       inputType = dataTypeStrings$mismatchesByReadRelationFormatted
+    }
   } else {
@@
   if (filteredAndFormattedInput) {
+    if (noPositionFiltering) {
+      additionalInformation = "no_position_filtering"
+    } else {
       additionalInformation = character()
+    }
   } else {
@@
                                          filePathOmittedMismatches = character())
+cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
+                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
+                                         includedMismatches = "CC>TT", noPositionFiltering = TRUE)
+cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
+                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
+                                         includedMismatches = "C>T", noPositionFiltering = TRUE)
 

### 2023-08-08 R/CutSiteCorrelationFigureGeneration.rmd
Added no-position-filtering control

@@
                                                       includedMismatches = character(), omittedMismatches = character(),
-                                                      filteredAndFormattedInput = TRUE, shuffle = FALSE) {
+                                                      filteredAndFormattedInput = TRUE, noPositionFiltering = FALSE,
+                                                      shuffle = FALSE) {
 
   if (filteredAndFormattedInput) {
+    if (noPositionFiltering) {
+      additionalInformation = "no_position_filtering"
+    } else {
       additionalInformation = character()
+    }
   } else {
@@
                                            omittedMismatches = "C>T", filteredAndFormattedInput = FALSE)
+
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
+                                           includedMismatches = "CC>TT", noPositionFiltering = TRUE)
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
+                                           includedMismatches = "C>T", noPositionFiltering = TRUE)
 ```

### 2023-08-08 R/CutSiteCorrelationAnalysis.R
Added getReadLengthSlope function
This function returns the slope of the read length vs. 5' cut site distance linear regression.

@@ -53,6 +53,11 @@ getCouplingRate = function(pairedCutSiteDistances) {
   return(linearModel$coefficients[2])
 }
 
+getReadLengthSlope = function(pairedCutSiteDistances) {
+  linearModel = lm(Read_Length ~ Five_Prime_Cut_Site_Distance, pairedCutSiteDistances)
+  return(linearModel$coefficients[2])
+}
+
 plotPairedCutSiteDistances = function(pairedCutSiteDistances, dependentVariable,
                                       xAxisLabel = "5' Cut Site Distance", yAxisLabel = NULL,
                                       title = "Paired Cut Site Distances", sizeRange = c(0.1,5),

### 2023-08-08 R/PaperFigureGeneration.rmd
Updates to feature relative and correlation figs

--- 2023-08-03 R/PaperFigureGeneration.rmd
@@
                                    mismatchData = yeastCPDCCtoTTMismatchDataAllRepsFiltered$`20min`)))
+```
+
+```{r read_figure_7_data}
+set.seed(8785)
+NHF1PairedCutSiteDistances = list(`1h` = NULL, `8h` = NULL)
+NHF1ShuffledCutSiteDistances = list(`1h` = NULL, `8h` = NULL)
+for (i in seq_along(NHF1PairedCutSiteDistances)) {
+  NHF1PairedCutSiteDistances[[i]] = list(CC_to_TT = NULL, C_to_T = NULL, non_C_to_T = NULL)
+  NHF1PairedCutSiteDistances[[i]]$CC_to_TT = fread(generateFilePath(
+    NHF1CutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances , ".tsv",
+    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1PairedCutSiteDistances)[i],
+    repitition = "all_reps", filtering = "TGG_filtered",
+    includedMismatches = "CC>TT"
+  ))
+  NHF1ShuffledCutSiteDistances[[i]] = getShufflePairedCutSiteDistances(NHF1PairedCutSiteDistances[[i]]$CC_to_TT)
+
+  NHF1PairedCutSiteDistances[[i]]$C_to_T = fread(generateFilePath(
+    NHF1CutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances , ".tsv",
+    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1PairedCutSiteDistances)[i],
+    repitition = "all_reps", filtering = "TGG_filtered",
+    includedMismatches = "C>T"
+  ))
+
+  NHF1PairedCutSiteDistances[[i]]$non_C_to_T = fread(generateFilePath(
+    NHF1CutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances , ".tsv",
+    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1PairedCutSiteDistances)[i],
+    repitition = "all_reps", filtering = "TGG_filtered",
+    omittedMismatches = "C>T"
+  ))
+}
+
+```
+
+```{r figure_7A, fig.width = 6, fig.height = 5}
+print(paste0("Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`1h`$CC_to_TT)))
+plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$CC_to_TT, READ_LENGTH,
+                           title = "NHF1 1h CC>TT All Reps TGG-filtered",
+                           xlim = c(12, 26), ylim = c(18.5, 32.5), xAxisBreaks = seq(13,25,3))
+```
+```{r figure_7B, fig.width = 6, fig.height = 5}
+print(paste0("Read Length SLope: ", getReadLengthSlope(NHF1ShuffledCutSiteDistances$`1h`)))
+plotPairedCutSiteDistances(NHF1ShuffledCutSiteDistances$`1h`, READ_LENGTH,
+                           title = "NHF1 1h CC>TT All Reps TGG-filtered Shuffled",
+                           xlim = c(6,30), ylim = c(13,37))
+```
+```{r figure_7C, fig.width = 6, fig.height = 5}
+print(paste0("Read length slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`1h`$non_C_to_T)))
+plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$non_C_to_T, READ_LENGTH,
+                           title = "NHF1 1h Non-C>T All Reps TGG-filtered",
+                           xlim = c(0,31), ylim = c(15,31))
+```
+```{r figure_7D, fig.width = 6, fig.height = 5}
+print(paste0("Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`1h`$CC_to_TT)*-100, '%'))
+plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$CC_to_TT, THREE_PRIME_CUT_SITE_DISTANCE,
+                           title = "NHF1 1h CC>TT All Reps TGG-filtered",
+                           xlim = c(12,26), ylim = c(0,14.5),
+                           xAxisBreaks = seq(12,26,2), yAxisBreaks = seq(0,14,2))
+```
+```{r figure_7E, fig.width = 6, fig.height = 5}
+print(paste0("Coupling: ", getCouplingRate(NHF1ShuffledCutSiteDistances$`1h`)*-100, '%'))
+plotPairedCutSiteDistances(NHF1ShuffledCutSiteDistances$`1h`, THREE_PRIME_CUT_SITE_DISTANCE,
+                           title = "NHF1 1h CC>TT All Reps TGG-filtered Shuffled",
+                           xlim = c(12,26), ylim = c(0,14.5),
+                           xAxisBreaks = seq(12,26,2), yAxisBreaks = seq(0,14,2))
+```
+```{r figure_7F, fig.width = 6, fig.height = 5}
+print(paste0("Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`1h`$non_C_to_T)*-100, '%'))
+plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$non_C_to_T, THREE_PRIME_CUT_SITE_DISTANCE,
+                           title = "NHF1 1h Non-C>T All Reps TGG-filtered",
+                           xlim = c(0,31), ylim = c(0,31))
+```
+
+```{r read_figure_8_data}
+NHF1NucleosomeRelativeCutSiteDistances = list(`1h` = NULL, `8h` = NULL)
+for (i in seq_along(NHF1NucleosomeRelativeCutSiteDistances)) {
+  NHF1NucleosomeRelativeCutSiteDistances[[i]] = list(three_prime = NULL, five_prime = NULL)
+  NHF1NucleosomeRelativeCutSiteDistances[[i]]$three_prime = fread(generateFilePath(
+    NHF1FeatureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv",
+    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1NucleosomeRelativeCutSiteDistances)[i],
+    strandPolarity = THREE_PRIME, repitition = "all_reps", filtering = "TGG_filtered",
+    includedMismatches = "C>T", additionalInformation = "hg19_mnase_all_related_strand_aligned"
+  ))
+  NHF1NucleosomeRelativeCutSiteDistances[[i]]$five_prime = fread(generateFilePath(
+    NHF1FeatureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv",
+    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1NucleosomeRelativeCutSiteDistances)[i],
+    strandPolarity = FIVE_PRIME, repitition = "all_reps", filtering = "TGG_filtered",
+    includedMismatches = "C>T", additionalInformation = "hg19_mnase_all_related_strand_aligned"
+  ))
+}
+```
+
+```{r figure_8A, fig.width = 10, fig.height = 5}
+plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`1h`$three_prime,
+                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
+                          plotCutSiteSignificance = FALSE,
+                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
+                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
+                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
+                          title = "NHF1 1h C>T All Reps TGG-Filtered Strand-Aligned",
+                          xAxisLabel = "Dyad-Relative Position", xlim = c(-200, 200),
+                          mainYAxisMin = 7.08, mainYAxisBreaks = seq(7.1,7.8,0.1),
+                          secondaryAxisBreaks = seq(19,19.8,0.2),
+                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
+```
+```{r figure_8B}
+plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`1h`$three_prime,
+                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
+                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
+                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
+                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
+                          title = "NHF1 1h C>T All Reps TGG-Filtered Strand-Aligned",
+                          xAxisLabel = "Dyad-Relative Position", xlim = c(-100, -40),
+                          mainYAxisMin = 7.08, mainYAxisBreaks = seq(7.1,7.8,0.1),
+                          secondaryAxisBreaks = seq(19,19.8,0.2),
+                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
+```
+```{r figure_8C}
+plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`1h`$three_prime,
+                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
+                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
+                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
+                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
+                          title = "NHF1 1h C>T All Reps TGG-Filtered Strand-Aligned",
+                          xAxisLabel = "Dyad-Relative Position", xlim = c(40, 100),
+                          mainYAxisMin = 7.08, mainYAxisBreaks = seq(7.1,7.8,0.1),
+                          secondaryAxisBreaks = seq(19,19.8,0.2), 
+                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
 ```
@@
 ```
+
+```{r figure_S13, fig.width = 6, fig.height = 5}
+print(paste0("1h C>T Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`1h`$C_to_T)))
+plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$C_to_T, READ_LENGTH,
+                           title = "NHF1 1h C>T All Reps TGG-filtered",
+                           xlim = c(10.5, 26.5), ylim = c(17.5, 33.5),
+                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(18,33,3))
+print(paste0("1h C>T Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`1h`$C_to_T)*-100, '%'))
+plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$C_to_T, THREE_PRIME_CUT_SITE_DISTANCE,
+                           title = "NHF1 1h C>T All Reps TGG-filtered",
+                           xlim = c(10.5,26.5), ylim = c(0,16),
+                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(0,15,3))
+
+print(paste0("8h CC>TT Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`8h`$CC_to_TT)))
+plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`8h`$CC_to_TT, READ_LENGTH,
+                           title = "NHF1 8h CC>TT All Reps TGG-filtered",
+                           xlim = c(10.5, 26.5), ylim = c(17.5, 33.5),
+                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(18,33,3))
+print(paste0("8h CC>TT Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`8h`$CC_to_TT)*-100, '%'))
+plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`8h`$CC_to_TT, THREE_PRIME_CUT_SITE_DISTANCE,
+                           title = "NHF1 8h CC>TT All Reps TGG-filtered",
+                           xlim = c(10.5,26.5), ylim = c(0,16),
+                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(0,15,3))
+```
+
+```{r read_figure_S14_data}
+yeastPairedCutSiteDistances = list(`20min` = NULL)
+yeastPairedCutSiteDistances$`20min` = list(CC_to_TT = NULL, non_C_to_T = NULL)
+yeastPairedCutSiteDistances$`20min`$CC_to_TT = fread(generateFilePath(
+  yeastCutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances, ".tsv",
+  cellType = "yeast", lesion = "CPD", timepoint = "20min",
+  repitition = "all_reps", filtering = "TGG_filtered",
+  includedMismatches = "CC>TT"
+))
+
+arabidopsisPairedCutSiteDistances = list(ZT2 = NULL)
+arabidopsisPairedCutSiteDistances$ZT2 = list(CC_to_TT = NULL, non_C_to_T = NULL)
+arabidopsisPairedCutSiteDistances$ZT2$CC_to_TT = fread(generateFilePath(
+  arabidopsisCutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances , ".tsv",
+  cellType = "Arabidopsis", lesion = "CPD", timepoint = "ZT2",
+  repitition = "all_reps", filtering = "TGG_filtered",
+  includedMismatches = "CC>TT"
+))
+
+```
+
+```{r figure_S14, fig.width = 6, fig.height = 5}
+print(paste0("Arabidopsis CC>TT read length slope: ", getReadLengthSlope(arabidopsisPairedCutSiteDistances$ZT2$CC_to_TT)))
+plotPairedCutSiteDistances(arabidopsisPairedCutSiteDistances$ZT2$CC_to_TT, READ_LENGTH,
+                           title = "Arabidopsis ZT2 CC>TT All Reps TGG-filtered",
+                           xlim = c(15,25), ylim = c(22,32), yAxisBreaks = c(23,25,27,29,31))
+print(paste0("Arabidopsis CC>TT Coupling: ", getCouplingRate(arabidopsisPairedCutSiteDistances$ZT2$CC_to_TT)*-100, '%'))
+plotPairedCutSiteDistances(arabidopsisPairedCutSiteDistances$ZT2$CC_to_TT, THREE_PRIME_CUT_SITE_DISTANCE,
+                           title = "Arabidopsis ZT2 CC>TT All Reps TGG-filtered",
+                           xlim = c(15,25), ylim = c(3,13), yAxisBreaks = c(4,6,8,10,12))
+
+print(paste0("Yeast CC>TT read length slope: ", getReadLengthSlope(yeastPairedCutSiteDistances$`20min`$CC_to_TT)))
+plotPairedCutSiteDistances(yeastPairedCutSiteDistances$`20min`$CC_to_TT, READ_LENGTH,
+                           title = "Yeast 20min CC>TT All Reps TGG-filtered",
+                           xlim = c(11,19), ylim = c(19.5,27.5), yAxisBreaks = waiver())
+print(paste0("Yeast CC>TT Coupling: ", getCouplingRate(yeastPairedCutSiteDistances$`20min`$CC_to_TT)*-100, '%'))
+plotPairedCutSiteDistances(yeastPairedCutSiteDistances$`20min`$CC_to_TT, THREE_PRIME_CUT_SITE_DISTANCE,
+                           title = "Yeast 20min CC>TT All Reps TGG-filtered",
+                           xlim = c(11,20), ylim = c(5,14),
+                           xAxisBreaks = c(11,13,15,17,19), yAxisBreaks = c(5,7,9,11,13))
+```
+
+```{r figure_S15A, fig.width = 10, fig.height = 5}
+plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,
+                          plotCutSiteSignificance = FALSE,
+                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
+                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
+                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
+                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
+                          title = "NHF1 8h C>T All Reps TGG-Filtered Strand-Aligned",
+                          xAxisLabel = "Dyad-Relative Position", xlim = c(-200, 200),
+                          secondaryAxisBreaks = seq(19,19.8,0.2),
+                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
+```
+```{r figure_S15B}
+plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,
+                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
+                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
+                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
+                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
+                          title = "NHF1 8h C>T All Reps TGG-Filtered Strand-Aligned",
+                          xAxisLabel = "Dyad-Relative Position", xlim = c(-100, -40),
+                          secondaryAxisBreaks = seq(19,19.8,0.2),
+                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
+```
+```{r figure_S15C}
+plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,
+                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
+                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
+                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
+                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
+                          title = "NHF1 8h C>T All Reps TGG-Filtered Strand-Aligned",
+                          xAxisLabel = "Dyad-Relative Position", xlim = c(40, 100),
+                          secondaryAxisBreaks = seq(19,19.8,0.2),
+                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
+```

### 2023-08-08 R/PaperFigureGeneration.rmd
Added plot to figure 6 (CC>TT suite)
Added a plot for 5'-relative cut site distances stratified by read length in order to be more consistent with figure 3.

@@
 ```
-```{r figure_6B, fig.width = 5, fig.height = 5}
+```{r figure_6B, fig.width = 5, fig.height = 5.5}
+### Just the 1h timepoint ###
+plotPositionAcrossTimepointAndReadLength(NHF1CPDCCtoTTMismatchDataAllRepsFiltered["1h"], posType = FIVE_PRIME,
+                                         title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT Mismatch Pos Freq",
+                                         zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered,
+                                         yAxisLabel = "Relative CC>TT Frequency", xAxisBreaks = c(1,10,20,30))
+
+### All timepoints together ###
+# plotPositionAcrossTimepointAndReadLength(NHF1CPDCCtoTTMismatchDataAllRepsFiltered,
+#                                          title = "NHF1 CPD All Reps TGG-Filtered CC>TT Mismatch Pos Freq",
+#                                          zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered,
+#                                          yAxisLabel = "Relative CC>TT Frequency")
+```
+```{r figure_6C, fig.width = 5, fig.height = 5}
 plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllReps1hFiltered,
@@
 ```
-```{r figure_6C, fig.width = 7.5, fig.height = 5}
+```{r figure_6D, fig.width = 7.5, fig.height = 5}
 plotGroupedPositionStats(NHF1CPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
@@
 ```
-```{r figure_6D, fig.width = 7.5, fig.height = 5}
+```{r figure_6E, fig.width = 7.5, fig.height = 5}
 plotGroupedPositionStats(arabidopsisCPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "ZT2"],
@@
 ```
-```{r figure_6E, fig.width = 7.5, fig.height = 5}
+```{r figure_6F, fig.width = 7.5, fig.height = 5}
 plotGroupedPositionStats(yeastCPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "20min"],

### 2023-08-15 R/CutSiteCorrelationDataGeneration.rmd
Added E coli and atypical position filtering
- Added E coli data to the cut site correlation analysis.
- Added "atypical position filtering" for non-C>T data. This is position filtering based on the C>T data.

--- 2023-08-03 R/CutSiteCorrelationDataGeneration.rmd
@@
 yeastCutSiteCorrelationDirectory = file.path(deaminationDataDirectory, "yeast", "cut_site_correlation")
+eColiMismatchesByReadDirectory = file.path(deaminationDataDirectory, "E_coli_WT", "mismatches_by_read")
+eColiCutSiteCorrelationDirectory = file.path(deaminationDataDirectory, "E_coli_WT", "cut_site_correlation")
 dir.create(NHF1CutSiteCorrelationDirectory, showWarnings = FALSE, recursive = TRUE)
@@
 dir.create(yeastCutSiteCorrelationDirectory, showWarnings = FALSE, recursive = TRUE)
+dir.create(eColiCutSiteCorrelationDirectory, showWarnings = FALSE, recursive = TRUE)
 ```
@@
                                                     includedMismatches = character(), omittedMismatches = character(),
-                                                    filteredAndFormattedInput = TRUE,
-                                                    filePathIncludedMismatches = NULL, filePathOmittedMismatches = NULL) {
+                                                    filteredAndFormattedInput = TRUE, noPositionFiltering = FALSE,
+                                                    filePathIncludedMismatches = NULL, filePathOmittedMismatches = NULL,
+                                                    atypicalPositionFiltering = FALSE) {
 
@@
   if (filteredAndFormattedInput) {
+    if (noPositionFiltering) {
+      inputType = paste0(dataTypeStrings$mismatchesByReadRelationFormatted,"_no_position_filtering")
+    } else if (atypicalPositionFiltering) {
+      inputType = paste0(dataTypeStrings$mismatchesByReadRelationFormatted,"_atypical_position_filtering")
+    } else {
       inputType = dataTypeStrings$mismatchesByReadRelationFormatted
+    }
   } else {
@@
   if (filteredAndFormattedInput) {
+    if (noPositionFiltering) {
+      additionalInformation = "no_position_filtering"
+    } else if (atypicalPositionFiltering) {
+      additionalInformation = "atypical_position_filtering"
+    } else {
       additionalInformation = character()
+    }
   } else {
@@
                                          omittedMismatches = "C>T")
+
 cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
@@
                                          filePathOmittedMismatches = character())
+
+cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
+                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
+                                         includedMismatches = "CC>TT", noPositionFiltering = TRUE)
+cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
+                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
+                                         includedMismatches = "C>T", noPositionFiltering = TRUE)
+cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
+                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
+                                         omittedMismatches = "C>T", atypicalPositionFiltering = TRUE)
 
@@
 
+cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "5min", "E_coli_WT",
+                                         eColiMismatchesByReadDirectory, eColiCutSiteCorrelationDirectory,
+                                         includedMismatches = "CC>TT", noPositionFiltering = TRUE)
+cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "5min", "E_coli_WT",
+                                         eColiMismatchesByReadDirectory, eColiCutSiteCorrelationDirectory,
+                                         includedMismatches = "C>T", noPositionFiltering = TRUE)
+cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "5min", "E_coli_WT",
+                                         eColiMismatchesByReadDirectory, eColiCutSiteCorrelationDirectory,
+                                         omittedMismatches = "C>T")
+
 ```

### 2023-08-15 R/CutSiteCorrelationFigureGeneration.rmd
Added E coli and atypical position filtering
- Added E coli data to the cut site correlation analysis.
- Added "atypical position filtering" for non-C>T data. This is position filtering based on the C>T data.

@@
 yeastCutSiteCorrelationDirectory = file.path(deaminationDataDirectory, "yeast", "cut_site_correlation")
+eColiCutSiteCorrelationDirectory = file.path(deaminationDataDirectory, "E_coli_WT", "cut_site_correlation")
 ```
@@
                                                       filteredAndFormattedInput = TRUE, noPositionFiltering = FALSE,
+                                                      atypicalPositionFiltering = FALSE,
                                                       shuffle = FALSE) {
@@
       additionalInformation = "no_position_filtering"
+    } else if (atypicalPositionFiltering) {
+      additionalInformation = "atypical_position_filtering"
     } else {
@@
                                            includedMismatches = "C>T", noPositionFiltering = TRUE)
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
+                                           omittedMismatches = "C>T", atypicalPositionFiltering = TRUE)
 ```
@@
 ```
+
+```{r E_coli_cut_site_correlation_figures}
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "5min", "E_coli_WT", eColiCutSiteCorrelationDirectory,
+                                           includedMismatches = "CC>TT", noPositionFiltering = TRUE)
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "5min", "E_coli_WT", eColiCutSiteCorrelationDirectory,
+                                           includedMismatches = "C>T", noPositionFiltering = TRUE)
+cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "5min", "E_coli_WT", eColiCutSiteCorrelationDirectory,
+                                           omittedMismatches = "C>T")
+```

### 2023-08-15 R/PaperFigureGeneration.rmd
Added atypical position filtering figure

@@
 
+```{r read_figure_S13_data}
+NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered = fread(generateFilePath(
+  NHF1CutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances, ".tsv",
+  cellType = "NHF1", lesion = "CPD", timepoint = "1h",
+  repitition = "all_reps", filtering = "TGG_filtered",
+  omittedMismatches = "C>T", additionalInformation = "atypical_position_filtering"
+))
+```
+
 ```{r figure_S13, fig.width = 6, fig.height = 5}
+print(paste0("1h non-C>T Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered)))
+plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered, READ_LENGTH,
+                           title = "NHF1 1h Non-C>T Position-Filtered All Reps TGG-filtered",
+                           xlim = c(10.5, 26.5), ylim = c(17.5, 33.5),
+                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(18,33,3))
+print(paste0("1h non-C>T Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered)))
+plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered, THREE_PRIME_CUT_SITE_DISTANCE,
+                           title = "NHF1 1h Non-C>T Position-Filtered All Reps TGG-filtered",
+                           xlim = c(10.5,26.5), ylim = c(0,16),
+                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(0,15,3))
+```
+
+```{r figure_S14, fig.width = 6, fig.height = 5}
 print(paste0("1h C>T Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`1h`$C_to_T)))
@@
 
-```{r figure_S14, fig.width = 6, fig.height = 5}
+```{r figure_S15, fig.width = 6, fig.height = 5}
 print(paste0("Arabidopsis CC>TT read length slope: ", getReadLengthSlope(arabidopsisPairedCutSiteDistances$ZT2$CC_to_TT)))
@@
 
-```{r figure_S15A, fig.width = 10, fig.height = 5}
+```{r figure_S16A, fig.width = 10, fig.height = 5}
 plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,
@@
 ```
-```{r figure_S15B}
+```{r figure_S16B}
 plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,
@@
 ```
-```{r figure_S15C}
+```{r figure_S16C}
 plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,

### 2023-08-17 R/CutSiteCorrelationAnalysis.R
Custom breaks option for paired cut site fig gen

@@ -61,7 +61,8 @@ getReadLengthSlope = function(pairedCutSiteDistances) {
 plotPairedCutSiteDistances = function(pairedCutSiteDistances, dependentVariable,
                                       xAxisLabel = "5' Cut Site Distance", yAxisLabel = NULL,
                                       title = "Paired Cut Site Distances", sizeRange = c(0.1,5),
-                                      xlim = NULL, ylim = NULL, xAxisBreaks = waiver(), yAxisBreaks = waiver()) {
+                                      xlim = NULL, ylim = NULL, xAxisBreaks = waiver(), yAxisBreaks = waiver(),
+                                      breaks = waiver()) {
 
   if (is.null(yAxisLabel)) {
     if (dependentVariable == THREE_PRIME_CUT_SITE_DISTANCE) {
@@ -72,10 +73,10 @@ plotPairedCutSiteDistances = function(pairedCutSiteDistances, dependentVariable,
   }
 
   plot = ggplot(pairedCutSiteDistances, aes(x = Five_Prime_Cut_Site_Distance, y = !!sym(dependentVariable))) +
-    geom_count() + scale_size(range = sizeRange) + blankBackground + defaultTextScaling +
+    geom_count() + scale_size(range = sizeRange) + scale_size_continuous(breaks = breaks) +
     geom_smooth(method = "lm", formula = y~x, color = "red2", se = FALSE) +
     labs(title = title, x = xAxisLabel, y = yAxisLabel) + coord_cartesian(xlim = xlim, ylim = ylim, expand = FALSE) +
-    scale_x_continuous(breaks = xAxisBreaks) + scale_y_continuous(breaks = yAxisBreaks)
+    scale_x_continuous(breaks = xAxisBreaks) + scale_y_continuous(breaks = yAxisBreaks) + blankBackground + defaultTextScaling
 
   print(plot)
 

### 2023-08-17 R/PaperFigureGeneration.rmd
General figure updates
Moved some plots around. Added 8h C>T cut site correlation plots.

@@
 for (i in seq_along(NHF1PairedCutSiteDistances)) {
-  NHF1PairedCutSiteDistances[[i]] = list(CC_to_TT = NULL, C_to_T = NULL, non_C_to_T = NULL)
+  NHF1PairedCutSiteDistances[[i]] = list(CC_to_TT = NULL, C_to_T = NULL, Non_C_to_T_Position_Filtered = NULL)
   NHF1PairedCutSiteDistances[[i]]$CC_to_TT = fread(generateFilePath(
@@
   ))
-
-  NHF1PairedCutSiteDistances[[i]]$non_C_to_T = fread(generateFilePath(
+}
+
+NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered = fread(generateFilePath(
   NHF1CutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances , ".tsv",
-    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1PairedCutSiteDistances)[i],
+  cellType = "NHF1", lesion = "CPD", timepoint = "1h",
   repitition = "all_reps", filtering = "TGG_filtered",
-    omittedMismatches = "C>T"
-  ))
-}
+  omittedMismatches = "C>T", additionalInformation = "atypical_position_filtering"
+))
 
@@
 ```{r figure_7C, fig.width = 6, fig.height = 5}
-print(paste0("Read length slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`1h`$non_C_to_T)))
-plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$non_C_to_T, READ_LENGTH,
-                           title = "NHF1 1h Non-C>T All Reps TGG-filtered",
-                           xlim = c(0,31), ylim = c(15,31))
+print(paste0("Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered)))
+plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered, READ_LENGTH,
+                           title = "NHF1 1h Non-C>T Position-Filtered All Reps TGG-filtered",
+                           xlim = c(10.5, 26.5), ylim = c(17.5, 33.5),
+                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(18,33,3))
 ```
@@
 ```{r figure_7F, fig.width = 6, fig.height = 5}
-print(paste0("Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`1h`$non_C_to_T)*-100, '%'))
-plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$non_C_to_T, THREE_PRIME_CUT_SITE_DISTANCE,
-                           title = "NHF1 1h Non-C>T All Reps TGG-filtered",
-                           xlim = c(0,31), ylim = c(0,31))
+print(paste0("Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered)*-100, '%'))
+plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered, THREE_PRIME_CUT_SITE_DISTANCE,
+                           title = "NHF1 1h Non-C>T Position-Filtered All Reps TGG-filtered",
+                           xlim = c(10.5,26.5), ylim = c(0,16),
+                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(0,15,3))
 ```
@@
 
-```{r read_figure_S13_data}
-NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered = fread(generateFilePath(
-  NHF1CutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances, ".tsv",
-  cellType = "NHF1", lesion = "CPD", timepoint = "1h",
-  repitition = "all_reps", filtering = "TGG_filtered",
-  omittedMismatches = "C>T", additionalInformation = "atypical_position_filtering"
-))
-```
-
 ```{r figure_S13, fig.width = 6, fig.height = 5}
-print(paste0("1h non-C>T Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered)))
-plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered, READ_LENGTH,
-                           title = "NHF1 1h Non-C>T Position-Filtered All Reps TGG-filtered",
+print(paste0("8h CC>TT Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`8h`$CC_to_TT)))
+plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`8h`$CC_to_TT, READ_LENGTH,
+                           title = "NHF1 8h CC>TT All Reps TGG-filtered",
                            xlim = c(10.5, 26.5), ylim = c(17.5, 33.5),
                            xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(18,33,3))
-print(paste0("1h non-C>T Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered)))
-plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$Non_C_to_T_Position_Filtered, THREE_PRIME_CUT_SITE_DISTANCE,
-                           title = "NHF1 1h Non-C>T Position-Filtered All Reps TGG-filtered",
+print(paste0("8h CC>TT Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`8h`$CC_to_TT)*-100, '%'))
+plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`8h`$CC_to_TT, THREE_PRIME_CUT_SITE_DISTANCE,
+                           title = "NHF1 8h CC>TT All Reps TGG-filtered",
                            xlim = c(10.5,26.5), ylim = c(0,16),
@@
                            xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(0,15,3))
-
-print(paste0("8h CC>TT Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`8h`$CC_to_TT)))
-plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`8h`$CC_to_TT, READ_LENGTH,
-                           title = "NHF1 8h CC>TT All Reps TGG-filtered",
+print(paste0("8h C>T Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`8h`$C_to_T)))
+plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`8h`$C_to_T, READ_LENGTH,
+                           title = "NHF1 8h C>T All Reps TGG-filtered",
                            xlim = c(10.5, 26.5), ylim = c(17.5, 33.5),
-                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(18,33,3))
-print(paste0("8h CC>TT Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`8h`$CC_to_TT)*-100, '%'))
-plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`8h`$CC_to_TT, THREE_PRIME_CUT_SITE_DISTANCE,
-                           title = "NHF1 8h CC>TT All Reps TGG-filtered",
+                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(18,33,3),
+                           breaks = c(25000, 50000, 75000, 100000))
+print(paste0("8h C>T Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`8h`$C_to_T)*-100, '%'))
+plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`8h`$C_to_T, THREE_PRIME_CUT_SITE_DISTANCE,
+                           title = "NHF1 8h C>T All Reps TGG-filtered",
                            xlim = c(10.5,26.5), ylim = c(0,16),
-                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(0,15,3))
-```
-
-```{r read_figure_S14_data}
+                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(0,15,3),
+                           breaks = c(25000, 50000, 75000, 100000))
+```
+
+```{r read_figure_S15_data}
 yeastPairedCutSiteDistances = list(`20min` = NULL)

### 2023-08-18 R/DeaminationFeatureRelativeAnalysis.R
Added option for marking nucleosome boundaries

@@ -150,7 +150,8 @@ plotFeatureRelativeCounts = function(countsTable, countsDataType, countsYVar = C
                                      mainYAxisMin = NULL, mainYAxisMax = NULL,
                                      centerMainYAxis = TRUE, mainYAxisBreaks = waiver(),
                                      meanCutSiteDistanceMin = NULL, meanCutSiteDistanceMax = NULL,
-                                     centerMeanCutSiteDistanceAxis = TRUE, secondaryAxisBreaks = waiver()) {
+                                     centerMeanCutSiteDistanceAxis = TRUE, secondaryAxisBreaks = waiver(),
+                                     markFirstNucleosomeBoundaries = FALSE) {
 
   if (plotCutSiteSignificance && (smoothCountsData || smoothMeanCutSiteDistance)) {
     warning("Plotting significance with smoothed data is ill-advised, as the t-test is performed before smoothing.")
@@ -302,6 +303,10 @@ plotFeatureRelativeCounts = function(countsTable, countsDataType, countsYVar = C
                                data = countsTable[Secondary_Significant==TRUE],
                                shape = 21, color = lineColor, fill = "white", size = 1.5, stroke = 1.5)
     }
+  }
+
+  if (markFirstNucleosomeBoundaries) {
+    plot = plot + geom_vline(xintercept = c(-73,73), linetype = "dashed")
   }
 
   print(plot)

### 2023-08-18 R/PaperFigureGeneration.rmd
Marked nucleosome boundaries in relevant plots

@@
                           secondaryAxisBreaks = seq(19,19.8,0.2),
-                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
+                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975,
+                          markFirstNucleosomeBoundaries = TRUE)
 ```

### 2023-09-27 R/FeatureRelativeDataGeneration_VALIDATION.Rmd
Validation of feature relative analysis
- Created test data for validation of the feature relative analysis pipeline, including the FilterAndFormat script.
- Test data is given in the validation/feature_relative_analysis directory and is annotated in validation_explanation.bed to describe expected values.
- Jupyter and R markdown notebooks run the validation data through the pipeline.

---
title: "FeatureRelativeDataGeneration_VALIDATION"
author: "Ben Morledge-Hampton"
date: "2023-09-25"
output: html_document
---

```{r setup_chunk}
bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
filtering = "TGG_filtered"
validationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", "validation")
```

```{r source_functions}
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "UsefulFileSystemFunctions.R"))
source(file.path(bioinformaticsDirectory, "deamination_determination", 'R',
                 "DeaminationFeatureRelativeAnalysis.R"))
```

```{r generate_and_write_feature_relative_counts_data}
featureRelativeData = parseMismatchesByFeature(fread(generateFilePath(
  validationDataDirectory, dataTypeStrings$mismatchesByReadRelationFormatted, ".bed",
  cellType = "validation", filtering = filtering, includedMismatches = "C>T",
  additionalInformation = "nucleosome_related"
)))

fwrite(featureRelativeData, sep = '\t', file = generateFilePath(
  validationDataDirectory, dataTypeStrings$featureRelativeData, ".tsv",
  cellType = "validation", filtering = filtering, includedMismatches = "C>T",
  additionalInformation = "nucleosome_related"
))

fwrite(getFeatureRelativeCounts(featureRelativeData, dataType = MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                                strandAlign = TRUE),
       sep = '\t', na = "NA", file = generateFilePath(
  validationDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = THREE_PRIME,
  cellType = "validation", filtering = filtering, includedMismatches = "C>T",
  additionalInformation = "nucleosome_related_strand_aligned"
))

fwrite(getFeatureRelativeCounts(featureRelativeData, dataType = MEAN_FIVE_PRIME_CUT_SITE_DISTANCE,
                                strandAlign = TRUE),
       sep = '\t', na = "NA", file = generateFilePath(
  validationDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = FIVE_PRIME,
  cellType = "validation", filtering = filtering, includedMismatches = "C>T",
  additionalInformation = "nucleosome_related_strand_aligned"
))
```

### 2023-11-27 R/NHF1_FeatureRelativeDataGeneration.Rmd
Added analysis with updated nucleosome map
- The previous nucleosome map (hg19_mnase_all) was not well documented. The new nucleosome map (hg19_LCL_mnase_all_mappable) has much clearer documentation on its origins.
- This new map also has blacklisted regions removed, using Dr. Wyrick's intersect_MNasenucs_Blacklist.pl script and the DAC_Duke_hg19_excludable regions, which were also added to the new "perl" directory.
- R scripts were also altered slightly to remove whitespace, standardize spacing after commas, etc.
- Lastly, a bug was discovered and fixed in the figure S16 generation code. (5'

--- 2023-07-24 R/NHF1_FeatureRelativeDataGeneration.Rmd
@@
     label: "Bioinformatics Projects Directory"
-    value: C:/Bioinformatics_Projects
+    value: ~/bioinformatics
     input: select
-    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
+    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects, ~/bioinformatics]
   filtering:
     label: "Filtering"
-    value: NONE
+    value: TGG_filtered
     input: select
@@
 CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
-mismatchTypes = list(`C>T_CC>TT` = NULL)
-features = list(`CTCF_known1_DHS` = NULL, `CTCF_known1_non-DHS` = NULL, `hg19_mnase_all` = NULL)
+mismatchTypes = list(`C>T` = NULL, `CC>TT` = NULL, `C>T_CC>TT` = NULL)
+# features = list(`CTCF_known1_DHS` = NULL, `CTCF_known1_non-DHS` = NULL,
+#                 `hg19_mnase_all` = NULL, `hg19_LCL_mnase_all` = NULL, `hg19_LCL_mnase_all_mappable` = NULL)
+features = list(`hg19_LCL_mnase_all_mappable_100bp` = NULL)
 
@@
 mismatchesByReadDirectory = file.path(deaminationDataDirectory, "mismatches_by_read")
-featureRelativeDataDirectory = file.path(deaminationDataDirectory,"feature_relative_analysis")
+featureRelativeDataDirectory = file.path(deaminationDataDirectory, "feature_relative_analysis")
 dir.create(featureRelativeDataDirectory, showWarnings = FALSE, recursive = TRUE)
@@
                          timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
-                         additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related"))
+                         additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k], "_related"))
       ))
@@
         timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
-        additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related")
+        additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k], "_related")
       ))
 
+      for (bool in c(TRUE, FALSE)) {
+
+        if (bool) strandInfoText = "_strand_aligned" else strandInfoText = ""
+
         fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = FEATURE_RELATIVE_POSITION,
-                                      strandAlign = TRUE),
-             sep = '\t', file = generateFilePath(
+                                        strandAlign = bool),
+               sep = '\t', na = "NA", file = generateFilePath(
           featureRelativeDataDirectory, dataTypeStrings$featureRelativePositionCounts, ".tsv",
@@
           timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
-        additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related")
+          additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k], "_related", strandInfoText)
         ))
@@
   }
-
+}
 ```

### 2023-11-27 R/NHF1_FeatureRelativeFigureGeneration.Rmd
Added analysis with updated nucleosome map
- The previous nucleosome map (hg19_mnase_all) was not well documented. The new nucleosome map (hg19_LCL_mnase_all_mappable) has much clearer documentation on its origins.
- This new map also has blacklisted regions removed, using Dr. Wyrick's intersect_MNasenucs_Blacklist.pl script and the DAC_Duke_hg19_excludable regions, which were also added to the new "perl" directory.
- R scripts were also altered slightly to remove whitespace, standardize spacing after commas, etc.
- Lastly, a bug was discovered and fixed in the figure S16 generation code. (5'

--- 2023-07-24 R/NHF1_FeatureRelativeFigureGeneration.Rmd
@@
 CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
-mismatchTypes = list(`C>T_CC>TT` = NULL)
+mismatchTypes = list(`C>T` = NULL, `CC>TT` = NULL, `C>T_CC>TT` = NULL)
 TFBSs = list(`CTCF_known1_DHS` = NULL, `CTCF_known1_non-DHS` = NULL)
-nucMaps = list(`hg19_mnase_all` = NULL)
+nucMaps = list(`hg19_mnase_all` = NULL, `hg19_LCL_mnase_all` = NULL, `hg19_LCL_mnase_all_mappable` = NULL)
 
@@
 opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5,
-               fig.path = paste0(file.path("deamination_analysis_output",cellType,
-                                           paste(c(filtering,"feature_relative_figures"), collapse = '_')),
+               fig.path = paste0(file.path("deamination_analysis_output", cellType,
+                                           paste(c(filtering, "feature_relative_figures"), collapse = '_')),
                                  .Platform$file.sep))
@@
 deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data", cellType)
-featureRelativeDataDirectory = file.path(deaminationDataDirectory,"feature_relative_analysis")
+featureRelativeDataDirectory = file.path(deaminationDataDirectory, "feature_relative_analysis")
 ```
@@
         timepoint = CPDTimepoint, includedMismatches = mismatchType,
-        additionalInformation = paste0(tfbs,"_related")
+        additionalInformation = paste0(tfbs, "_related_strand_aligned")
       ))
@@
       plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION,
-                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"))
+                                plotCountsMirror = TRUE, smoothCountsData = FALSE, mainYAxisLabel = "C>T Mismatches",
+                                countsPlotColor = "black", countsMirrorColor = "gold2",
+                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"),
+                                xAxisLabel = "TFBS-Relative Position")
 
-      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION, meanThreePrimeCutSiteDistanceData,
-                                THREE_PRIME, title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"))
-
-      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION, meanFivePrimeCutSiteDistanceData,
-                                FIVE_PRIME, title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"))
+      plotFeatureRelativeCounts(meanThreePrimeCutSiteDistanceData, FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
+                                smoothCountsData = FALSE, countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
+                                meanCutSiteDistanceTable = meanFivePrimeCutSiteDistanceData,
+                                cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
+                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"),
+                                xAxisLabel = "TFBS-Relative Position")
 
@@
         timepoint = CPDTimepoint, includedMismatches = mismatchType,
-        additionalInformation = paste0(nucMap,"_related")
+        additionalInformation = paste0(nucMap, "_related_strand_aligned")
       ))
@@
       plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION,
-                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"))
+                                plotCountsMirror = TRUE, smoothCountsData = FALSE, mainYAxisLabel = "C>T Mismatches",
+                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"),
+                                xAxisLabel = "Dyad-Relative Position", xlim = c(0, 300))
 
-      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION, meanThreePrimeCutSiteDistanceData,
-                                THREE_PRIME, title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"))
+      plotFeatureRelativeCounts(meanThreePrimeCutSiteDistanceData, FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
+                                smoothCountsData = FALSE, countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
+                                meanCutSiteDistanceTable = meanFivePrimeCutSiteDistanceData,
+                                cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
+                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"),
+                                xAxisLabel = "Dyad-Relative Position", xlim = c(-100, 100))
 
-      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION, meanFivePrimeCutSiteDistanceData,
-                                FIVE_PRIME, title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"))
+      plotFeatureRelativeCounts(meanThreePrimeCutSiteDistanceData, FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
+                                smoothCountsData = FALSE, countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
+                                meanCutSiteDistanceTable = meanFivePrimeCutSiteDistanceData,
+                                cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
+                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"),
+                                xAxisLabel = "Dyad-Relative Position", xlim = c(0, 300))
 
@@
           timepoint = CPDTimepoint, includedMismatches = mismatchType,
-          additionalInformation = paste0(nucMap,"_related")
+          additionalInformation = paste0(nucMap, "_related")
         ))
@@
                                                                                   Mean_Three_Prime_Cut_Site_Distance], 5, 25)
-        print(paste("  Peak Period:",periodAndSNR[1]))
-        print(paste("  SNR:",periodAndSNR[2]))
+        print(paste("  Peak Period:", periodAndSNR[1]))
+        print(paste("  SNR:", periodAndSNR[2]))
 
@@
                                                                                   Mean_Five_Prime_Cut_Site_Distance], 5, 25)
-        print(paste("  Peak Period:",periodAndSNR[1]))
-        print(paste("  SNR:",periodAndSNR[2]))
+        print(paste("  Peak Period:", periodAndSNR[1]))
+        print(paste("  SNR:", periodAndSNR[2]))
         print("")
@@
 ```
+
+```{r linker_region_periodicity_analysis}
+library(mutperiodR)
+
+for (CPDTimepoint in names(CPDTimepoints)) {
+  for (mismatchType in names(mismatchTypes)) {
+    for (nucMap in names(nucMaps)) {
+
+        meanThreePrimeCutSiteDistanceData = fread(generateFilePath(
+          featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = THREE_PRIME,
+          cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
+          timepoint = CPDTimepoint, includedMismatches = mismatchType,
+          additionalInformation = paste0(nucMap, "_related")
+        ))
+
+        meanFivePrimeCutSiteDistanceData = fread(generateFilePath(
+          featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = FIVE_PRIME,
+          cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
+          timepoint = CPDTimepoint, includedMismatches = mismatchType,
+          additionalInformation = paste0(nucMap, "_related")
+        ))
+
+        print(paste(cellType, CPDTimepoint, mismatchType, nucMap, ":"))
+
+        print("Mean 3` cut site distance:")
+        print("  pre-linker:")
+        periodAndSNR = getPeakPeriodicityAndSNR(
+          meanThreePrimeCutSiteDistanceData[
+            Feature_Relative_Mismatch_Pos < -70 & Feature_Relative_Mismatch_Pos > -120,
+            Mean_Three_Prime_Cut_Site_Distance], 5, 25)
+        print(paste("    Peak Period:", periodAndSNR[1]))
+        print(paste("    SNR:", periodAndSNR[2]))
+
+        print("  post-linker:")
+        periodAndSNR = getPeakPeriodicityAndSNR(
+          meanThreePrimeCutSiteDistanceData[
+            Feature_Relative_Mismatch_Pos > 70 & Feature_Relative_Mismatch_Pos < 120,
+            Mean_Three_Prime_Cut_Site_Distance], 5, 25)
+        print(paste("    Peak Period:", periodAndSNR[1]))
+        print(paste("    SNR:", periodAndSNR[2]))
+
+        print("Mean 5` cut site distance:")
+        print("  pre-linker:")
+        periodAndSNR = getPeakPeriodicityAndSNR(
+          meanFivePrimeCutSiteDistanceData[
+            Feature_Relative_Mismatch_Pos < -70 & Feature_Relative_Mismatch_Pos > -120,
+            Mean_Five_Prime_Cut_Site_Distance], 5, 25)
+        print(paste("    Peak Period:", periodAndSNR[1]))
+        print(paste("    SNR:", periodAndSNR[2]))
+
+        print("  post-linker:")
+        periodAndSNR = getPeakPeriodicityAndSNR(
+          meanFivePrimeCutSiteDistanceData[
+            Feature_Relative_Mismatch_Pos > 70 & Feature_Relative_Mismatch_Pos < 120,
+            Mean_Five_Prime_Cut_Site_Distance], 5, 25)
+        print(paste("    Peak Period:", periodAndSNR[1]))
+        print(paste("    SNR:", periodAndSNR[2]))
+
+        print('')
+    }
+  }
+}
+```

### 2023-11-27 R/PaperFigureGeneration.rmd
Added analysis with updated nucleosome map
- The previous nucleosome map (hg19_mnase_all) was not well documented. The new nucleosome map (hg19_LCL_mnase_all_mappable) has much clearer documentation on its origins.
- This new map also has blacklisted regions removed, using Dr. Wyrick's intersect_MNasenucs_Blacklist.pl script and the DAC_Duke_hg19_excludable regions, which were also added to the new "perl" directory.
- R scripts were also altered slightly to remove whitespace, standardize spacing after commas, etc.
- Lastly, a bug was discovered and fixed in the figure S16 generation code. (5'

--- 2023-08-17 R/PaperFigureGeneration.rmd
@@
     label: "Bioinformatics Projects Directory"
-    value: C:/Bioinformatics_Projects
+    value: ~/bioinformatics
     input: select
-    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
+    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects, ~/bioinformatics]
 ---
@@
 opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5,
-               fig.path = paste0(file.path("deamination_analysis_output","paper_figures"),
+               fig.path = paste0(file.path("deamination_analysis_output", "paper_figures"),
                                  .Platform$file.sep))
@@
       labs(title = "NHF1 CPD 1h All Reps Tandem Mismatch Counts", x = "Mismatch Type", y = "Tandem Mismatch Count") +
-      geom_text(aes(label=Tandem_Mismatches_Count), position = position_dodge(width = 0.9), vjust = -0.25, size = 5) +
+      geom_text(aes(label = Tandem_Mismatches_Count), position = position_dodge(width = 0.9), vjust = -0.25, size = 5) +
       blankBackground + defaultTextScaling + scale_fill_brewer(palette = "Set1") +
@@
 ```{r read_figure_8_data}
-NHF1NucleosomeRelativeCutSiteDistances = list(`1h` = NULL, `8h` = NULL)
+NHF1NucleosomeRelativeCutSiteDistances = list(hg19_LCL_mnase_all_mappable = NULL)
+for (j in seq_along(NHF1NucleosomeRelativeCutSiteDistances)) {
+  NHF1NucleosomeRelativeCutSiteDistances[[j]] = list(`1h` = NULL, `8h` = NULL)
+  for (i in seq_along(NHF1NucleosomeRelativeCutSiteDistances[[j]])) {
+    NHF1NucleosomeRelativeCutSiteDistances[[j]][[i]] = list(three_prime = NULL, five_prime = NULL)
+    NHF1NucleosomeRelativeCutSiteDistances[[j]][[i]]$three_prime = fread(generateFilePath(
+      NHF1FeatureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv",
+      cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1NucleosomeRelativeCutSiteDistances[[j]])[i],
+      strandPolarity = THREE_PRIME, repitition = "all_reps", filtering = "TGG_filtered",
+      includedMismatches = "C>T", additionalInformation = paste0(names(NHF1NucleosomeRelativeCutSiteDistances)[j],
+                                                                 "_related_strand_aligned")
+    ))
+    NHF1NucleosomeRelativeCutSiteDistances[[j]][[i]]$five_prime = fread(generateFilePath(
+      NHF1FeatureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv",
+      cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1NucleosomeRelativeCutSiteDistances[[j]])[i],
+      strandPolarity = FIVE_PRIME, repitition = "all_reps", filtering = "TGG_filtered",
+      includedMismatches = "C>T", additionalInformation = paste0(names(NHF1NucleosomeRelativeCutSiteDistances)[j],
+                                                                 "_related_strand_aligned")
+    ))
+  }
+}
+```
+
+```{r figure_8A, fig.width = 10, fig.height = 5}
 for (i in seq_along(NHF1NucleosomeRelativeCutSiteDistances)) {
-  NHF1NucleosomeRelativeCutSiteDistances[[i]] = list(three_prime = NULL, five_prime = NULL)
-  NHF1NucleosomeRelativeCutSiteDistances[[i]]$three_prime = fread(generateFilePath(
-    NHF1FeatureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv",
-    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1NucleosomeRelativeCutSiteDistances)[i],
-    strandPolarity = THREE_PRIME, repitition = "all_reps", filtering = "TGG_filtered",
-    includedMismatches = "C>T", additionalInformation = "hg19_mnase_all_related_strand_aligned"
-  ))
-  NHF1NucleosomeRelativeCutSiteDistances[[i]]$five_prime = fread(generateFilePath(
-    NHF1FeatureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv",
-    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1NucleosomeRelativeCutSiteDistances)[i],
-    strandPolarity = FIVE_PRIME, repitition = "all_reps", filtering = "TGG_filtered",
-    includedMismatches = "C>T", additionalInformation = "hg19_mnase_all_related_strand_aligned"
-  ))
-}
-```
-
-```{r figure_8A, fig.width = 10, fig.height = 5}
-plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`1h`$three_prime,
+  plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances[[i]]$`1h`$three_prime,
                             FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
@@
                             countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
-                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
+                            meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances[[i]]$`1h`$five_prime,
                             cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
@@
                             secondaryAxisBreaks = seq(19,19.8,0.2),
-                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
+                            meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975,
+                            markFirstNucleosomeBoundaries = TRUE)
+}
 ```
 ```{r figure_8B}
-plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`1h`$three_prime,
+for (i in seq_along(NHF1NucleosomeRelativeCutSiteDistances)) {
+  plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances[[i]]$`1h`$three_prime,
                             FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                             countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
-                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
+                            meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances[[i]]$`1h`$five_prime,
                             cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
@@
                             meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
+}
 ```
 ```{r figure_8C}
-plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`1h`$three_prime,
+for (i in seq_along(NHF1NucleosomeRelativeCutSiteDistances)) {
+  plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances[[i]]$`1h`$three_prime,
                             FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                             countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
-                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
+                            meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances[[i]]$`1h`$five_prime,
                             cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
@@
                             meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
+}
 ```
@@
 ```{r figure_S16A, fig.width = 10, fig.height = 5}
-plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,
+for (i in seq_along(NHF1NucleosomeRelativeCutSiteDistances)) {
+  plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances[[i]]$`8h`$three_prime,
                             plotCutSiteSignificance = FALSE,
@@
                             countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
-                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
+                            meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances[[i]]$`8h`$five_prime,
                             cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
@@
                             secondaryAxisBreaks = seq(19,19.8,0.2),
-                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
+                            meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975,
+                            markFirstNucleosomeBoundaries = TRUE)
+}
 ```
 ```{r figure_S16B}
-plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,
+for (i in seq_along(NHF1NucleosomeRelativeCutSiteDistances)) {
+  plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances[[i]]$`8h`$three_prime,
                             FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                             countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
-                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
+                            meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances[[i]]$`8h`$five_prime,
                             cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
@@
                             meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
+}
 ```
 ```{r figure_S16C}
-plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,
+for (i in seq_along(NHF1NucleosomeRelativeCutSiteDistances)) {
+  plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances[[i]]$`8h`$three_prime,
                             FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                             countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
-                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
+                            meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances[[i]]$`8h`$five_prime,
                             cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
@@
                             meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
-```
+}
+```

### 2023-11-27 perl/intersect_MNasenucs_Blacklist.pl

@@ -1,0 +1,114 @@
+#!/usr/bin/perl 
+# intersect_TFBS_Blacklist_100bp_window.pl
+
+use strict;
+use warnings;
+
+print STDERR "Enter filename of TFBS to intersect with BLIST coordinates\n";
+my $tfbs_file = <STDIN>;
+chomp $tfbs_file;
+open ( TFBS, $tfbs_file ) || die "Couldn't open file: $tfbs_file\n";
+
+# open BLIST coordinates
+print STDERR "Enter filename of BlackList coordinate file:\n";
+my $blist_file = <STDIN>;
+chomp $blist_file;
+open (BLIST, $blist_file) || die "Couldn't open promoter file: $blist_file\n";
+print STDERR "processing BlackList coordinates...\n";
+
+my $window = 73;
+# process promoters into lookup hash (1 => promoter, undef/not exist ==> not promoter)
+my %BLIST_coord;
+my $chr = "";
+while ( my $line = <BLIST> )
+{
+	chomp $line;
+	my @fields = split /\t/, $line;
+	if ( $fields[0] =~ /(chr[0-9A-Za-z_]+)/ )
+	{
+		my $temp = $1;
+		if ( $chr ne $temp )
+		{
+			print STDERR "Starting to process $temp\n";
+			$chr = $temp;
+		}
+
+		push @{$BLIST_coord{$chr}}, [$fields[1], $fields[2]];
+	}
+	else
+	{
+		print STDERR "Misformatted line: $line\n";
+	}
+}
+close (BLIST);
+
+# intersect TF coordinates with BLIST --> any overlap means active BLIST TF
+
+$tfbs_file =~ s/\.txt//;
+
+my $InBLIST_file = $tfbs_file . "_BLIST.txt";
+my $notInBLIST_file = $tfbs_file . "_notBLIST.txt";
+
+open (BLIST, ">$InBLIST_file") || die "Couldn't open InBLIST file: $InBLIST_file\n";
+open (NOTBLIST, ">$notInBLIST_file") || die "Couldn't open NOTInBLIST file: $notInBLIST_file\n";
+
+print STDERR "Starting processing TFBS coordinates...\n";
+$chr = "";
+my %BLIST_lookup;
+while ( my $line = <TFBS>)
+{
+	chomp $line;
+	my @fields = split /\t/, $line;
+        if ( $fields[0] =~ /(chr[0-9A-Za-z_]+)/ )
+        {
+		my $temp = $1;
[…]
